### 2018-03-11 Skew_Normal_CCF.tex
Added Xavier's files.

\documentclass{aa}
%\documentclass[referee]{aa}
\usepackage{natbib}
%\usepackage{lscape}
\usepackage{pdflscape} % or {lscape}
\usepackage{wasysym}
\usepackage[varg]{txfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
\usepackage{longtable}

\usepackage{afterpage}

\usepackage[usenames,dvipsnames]{color}
\definecolor{mygreen}{rgb}{0,0.5,0}
\definecolor{myorange}{rgb}{0.5,0.5,0}
\definecolor{myred}{rgb}{0.5,0,0}

%\newcommand{\ep}[1]{\textcolor{red}{#1}}
%\newcommand{\epp}[1]{\textcolor{blue}{#1}}

\newcommand{\fo}{f_\mathrm{o}}
\newcommand{\fu}{f_\mathrm{u}}
\newcommand{\ic}{I_\mathrm{c}}
\newcommand{\rc}{R_\mathrm{c}}
\newcommand{\uspec}{U_\mathrm{spec}}
\newcommand{\lambdac}{\lambda_\mathrm{c}}
\newcommand{\mplanet}{M_\mathrm{p}}
\newcommand{\mearth}{M_\oplus}
\newcommand{\rearth}{R_\oplus}
\newcommand{\msun}{M_\odot}
\newcommand{\rsun}{R_\odot}
\newcommand{\mstar}{M_\star}
\newcommand{\rstar}{R_\star}
\newcommand{\mjup}{M_\mathrm{jup}}
\newcommand{\rjup}{R_\mathrm{jup}}
\newcommand{\rplanet}{R_\mathrm{p}}
\newcommand{\rplanetzero}{R_\mathrm{p,0}}
\newcommand{\rhoplanet}{\rho_\mathrm{p}}
\newcommand{\de}{\mathrm{d}}
\newcommand{\teq}{T_\mathrm{eq}}
\newcommand{\kb}{k_\mathrm{b}}
\newcommand{\htwo}{\mathrm{H}_2}
\newcommand{\htwoo}{\mathrm{H}_2\mathrm{O}}
\newcommand{\chfour}{\mathrm{CH}_4}
\newcommand{\der}{\de\rplanet/\de\ln\!\lambda }
\newcommand{\chisq}{\chi^2}
\newcommand{\chisqr}{\chi^2_\mathrm{r}}
\newcommand{\teff}{T_\mathrm{eff}}
\newcommand{\logg}{\log g}
\newcommand{\feh}{[\mathrm{Fe}/\mathrm{H}]}

\def\ms{\hbox{\,m\,s$^{-1}$}}         %m.s -1
\def\cms{\hbox{\,cm\,s$^{-1}$}}       %cm.s -1
\def\m2s2{\hbox{\,m$^{2}$\,s$^{-2}$}} %m2.s -2
\def\kms{\hbox{\,km\,s$^{-1}$}}       %km.s -1
\def\vsini{\hbox{$v$\,sin\,$i$\,}}      %vsini
\def\sini{\hbox{sin\,$i$}}      %vsini
\def\Msun{\hbox{$\mathrm{M}_{\odot}$}}             %Msun
\def\Rsun{\hbox{$\mathrm{R}_{\odot}$}}
\def\Mjup{\hbox{$\mathrm{M}_{\rm Jup}$}}
\def\Rjup{\hbox{$\mathrm{R}_{\rm Jup}$}}
\def\degr{\hbox{$^\circ$}}
\def\chisq{\mbox{$\chi^2$}}
%\def\mp{$M_{\rm p}$}
%\def\rp{$R_{\rm p}$}
\def\mp{M_{\rm p}}
\def\rp{R_{\rm p}}
\def\logrhk{$\log$(R$^{\prime}_{HK}$)}

\begin{document}

\title{Cross correlation function line-profile variations in radial-velocity measurements by fitting a Skew Normal distribution
\thanks{Based on observations collected at the La Silla Parana Observatory,
ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}}

%\subtitle{II. First results of the analysis of the data set}

\author{U. Simola \inst{1,2}
	    \thanks{\email{umberto.simola@yale.edu}}
	    \and X. Dumusque\inst{3}
	    \thanks{Society in Science -- Branco Weiss Fellow (url: \url{http://www.society-in-science.org})}    
	    \and Jessi Cisewski\inst{2}
	    }

\institute{Department of Statistical Sciences, University of Padua, Padua, Italy
	      \and Department of Statistics and Data Science, Yale University, New Haven, CT, USA
	      \and Observatoire de Gen\`eve, Universit\'e de Gen\`eve, 51 ch. des Maillettes, CH-1290 Versoix, Switzerland 
	      }

\date{Received XXX; accepted XXX}

\abstract
% Context, Aims, Methods, Results, Conclu (not mandatory)
{{\bf An exoplanet or stellar companion will induce a variation in the radial velocity (RV) of its host star, which will translate into a pure-Doppler shift of the stellar spectrum and thus a velocity shift of the cross-correlation function (CCF) without changing its shape. The barycenter of the CCF is therefore a measure of the stellar RV. We generally measure this barycenter by fitting a Normal distribution to the CCF and then retreving its first moment, i.e. its mean. However, some astrophysical processes, like oscillations, granulation, stellar activity and single-lined spectroscopic binaries will modify the asymetry of the CCF, which will introduce a spurious radial-velocity variation and perturb the detection of exoplanets. To decorrelate the signals introduced by exoplanets from the one introduced by other astrophysical processes, we use the higher moments of the CCF. Note that in the case of high-precision RV surveys, mainly focusing on non-blended GKM dwarfs, stellar activity is the main perturbing signal.}}
{We propose here to measure the moment of the CCF using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, provides an extra parameter to model the CCF natural asymmetry.}
{We analyzed 5 stars with different activity levels and different signal-to-noise ratio levels. In each case, we compare the results obtained from the Normal fitting of the CCF and from the SN fitting. We also estimate rigorous errors for the different moments of the CCF using a bootstrap analysis.}
{The correlations between the RVs and the CCF asymmetry or RVs and the CCF width is always stronger when using the parameters derived from the SN. Therefore all the moments of the CCF are more sensitive to activity, which is a huge gain to probe stellar activity. RVs derived from a SN distribution are more sensitive to activity, which is interesting when looking for rotational periods or characterizing better stellar activity. However, once correcting the RVs from stellar activity signanol using a linear combination of the CCF asymmetry and width, the RV residuals obtained from a Normal or SN fitting are very similar. The precision on the asymmetric parameter derived from the SN is also 15\% better than the one derived on the common Bisector Inverse Slope Span (BIS SPAN). Besides all these advantages, the errors on the RVs measured by the SN are 60\% greater. This is not a problem at signal-to-noise ratio levels $>$ 150 because other noise sources dominate in this regime, however we have to be careful when deriving precise RVs for low SNR measurements. We also found that in the case of low SNR measurements, errors measured by bootstrap analysis can be 50\% more precise than errors measured using the derivative of the CCF.}
{We strongly encourage the use of the SN distribution to derive the different moments of the CCF, because the derived moments probe better stellar activity signals than when using a Normal distribution.}

\keywords{techniques: radial velocities -- planetary systems -- stars: activity -- methods: data analysis}

\titlerunning{Fitting a SN distribution to CCF}
\authorrunning{U. Simola, X. Dumusque and J. Cisewski}
\maketitle

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Introduction}
\label{intro}

By measuring the radial-velocity of a star, it is possible to detect the stellar wobble induced by the gravitational pull of orbiting planets. This so-called radial-velocity (RV) technique is an indirect method as the planet cannot be seen. This poses some difficulties as the RV technique is not only sensitive to planetary signals, but also to different stellar signals. At the meter-per-second level, RV measurements are affected by oscillations \citep[][]{Arentoft-2008,Kjeldsen-1995,Mayor-2003}, granulation \citep[][]{Meunier-2016,Dumusque-2011a,Lindegren-2003,Del-Moro-2004} and activity signals \citep[][]{Dumusque-2014,Meunier-2011,Saar-2009,Desort-2007,Saar-1997}. Other effects can also introduce RV variations, like single-lined spectroscopic binaries (SB1). High-precision RV surveys tends to avoid targeting any SB1 and to observe GKM dwarfs to minimize the impact of oscillations and granulation. High-precision RV surveys also tend to observe quiet stars in terms of stellar activity, however, as most of the star present solar-like magnetic cycles \citep[][]{Lovis-2011b}, it is not possible to observe the same star at a quiet stage for several continous years.
Stellar activity is therefore the main limitation to the detection of Earth-like planey

While the gravitational pull of an orbiting planets introduces a pure-Doppler

The radial velocity (RV) technique is an indirect method to detect exoplanets.

By measuring the radial velocity induced by the stellar wobble induced by a planet orbiting its host star

%The radial velocity (RV) of a star is defined to be the velocity of the center of mass of the star along our line of sight. This quantity can be derived precisely by measuring the Doppler shift of spectral lines produced in stellar atmospheres. For spectrographs that are not stabilised in temperature and pressure, the iodine technique is used, where the light of the star passes through a iodine cell before getting into the spectrograph to imprint the absorption spectrum of iodine on top of the stellar spectrum (The Hamilton spectrograph \citep{Vogt1987} at Lick Observatory, HIRES \citep{Vogt1994} on the Keck 10-m telescope, the Tull spectrograph  \citep{Tull1995}, the High Resolution Spectrograph HRS  \citep{Tull1998}). In this case, if the spectrograph shifts due to changing atmospheric conditions, the iodine and stellar spectra are shifted in the same way. This leads to some complications when reducing the data because one has to decorrelate the iodine spectrum from the stellar spectrum. For spectrographs that are stabilised, the spectrum of a calibration lamp is recorded close to the stellar spectrum on the CCD, which prevents contamination of the stellar spectrum (CORALIE \citep{Queloz-2000a}, The High Accuracy Radial Velocity Planet Searcher (HARPS) \citep{Mayor-2003}, HARPS- N \citep{Cosentino-2012}, SOPHIE \citep{Bouchy:2013aa}, CARMENES \citep{Quirrenbach:2014aa}). For those instruments, reducing the data is easier as the stellar spectrum is not contaminated with iodine absorption lines.

%For stabilised spectrographs, the RV is derived by first correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}, which gives an average line profile, generally called Cross Correlation Function (CCF). Then a Normal distribution is fitted to this average profile to get the mean, namely the RV, and the full width at half maximum (FWHM) of the profile. The CCF technique allows for an averaging out of the RV information of thousands of lines and therefore reach a very high signal-to-noise ratio (SNR), which is essential for a good RV precision.

The convection in external layers of solar type stars is responsible for the granulation pattern than can be seen at high spatial resolution on the surface of the Sun. The differences in flux and velocity between upflows and downflows change the Normal profile of spectral lines that become asymmetric with a "C"-shaped profile \citep[][]{Dravins-1981}. The strength of the asymmetry depends on the velocity of the convection, approximately 300\ms for the Sun, but also on the formation depth of spectral lines \citep{Gray-2009}. Since the CCF is an average of all the spectral lines, some strongly asymmetric and some not, its asymmetry is rather small, which is why a Normal distribution is a proper model to fit the CCF. 
%This small asymmetry modifies however slightly the estimated RVs of the star, reducing the accuracy of the measurement, but if this asymmetry does not vary with time, the precision is kept.

Convection is not the only phenomenon responsible for asymmetries in the single spectral line and the CCF. Stellar activity is responsible for the appearance of dark spots and bright faculae on the stellar photosphere, which breaks the flux balance between the red-shifted and the blue-shifted halves of a rotating star and therefore induce an asymmetry of spectral lines and thus of the CCF. As the star rotates, spots and faculae move across the stellar disk, modifying the line asymmetry and thus producing an apparent Doppler shift \citep{Saar-1997b,Hatzes-2002,Kurster2003,Desort-2007,Lagrange-2010,Boisse-2012b}. Spots and faculae are also regions where the magnetic field is strong. Strong magnetic fields reduce stellar convection, which in turn modifies the asymmetry of spectral lines \citep[][]{Cavallini-1985a,Dravins-1981,Lindegren-2003,Meunier-2010a,Dumusque-2014b}.

Stellar activity induces RV variations by a modification of the spectral line asymmetry, while an orbiting companion only induces a pure Doppler shift on spectral lines without modifying their shape.
Therefore, assuming that there is no instrumental systematics, stellar activity will induce a variation in line asymmetry or FWHM of the CCF. The line asymmetry is commonly retrieved by calculating the bisector of the CCF \citep[][]{Voigt1956} and deriving the bisector curvature \citep[][]{Hatzes1996} or the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}. \citet{Figueira-2013} proposed different indicators, including a bi-Gaussian fitting of the CCF. Unfortunately, when analyzing slow rotators stars such as the Sun, due to the limited spectral resolution of the spectrographs and the limited precision in RV, it becomes difficult to measure the line asymmetry, resulting in complications for detecting very small-mass planets with the RV technique.

In the procedure described above, the measurement of the RV and the FWHM is done separately from the measurement of the line asymmetry. All those parameters are correlated when stellar activity is dominant, and performing a step-by-step approach makes it difficult to correctly derive the errors on the different parameters retrieved. In addition, the Normal distribution cannot take into account the natural asymmetry of the CCF, leaving correlated noise in the residuals, which also complicates the determination of errors. We propose to overcome these problems by fitting a SN (SN) distribution to the CCF, which naturally includes a skewness parameter \citep[][]{Azzalini1985}.

The paper is organized as follow. In Sec.~\ref{sec:2} we introduce the SN distribution and motivate its use for fitting the CCF. In Sec.~\ref{sec:3} we show that the SN distribution is a better representation of observed CCF and we study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF. In Sec.~\ref{sec:31} we present a simple model to correct for stellar activity. In Sec.~\ref{sec:4}, we compare on real observations the sensitivity of the SN parameters to stellar activity with respect to other existing indicators. In Sec.~\ref{sec:5} we derive error bars for the different CCF parameters, and finally we discuss our results and conclude in Sec.~\ref{sec:discu} and Sec.~\ref{sec:conclu}.

%When the observed RV for each spectrum is computed by using the cross-correlation function (CCF) technique, the determination of the radial velocity of the star has operatively done by measuring the Doppler shift of spectral lines produced in the stellar atmosphere. Doppler measurements are obtained combining each spectrum with a mask template (a very common choice is a binary template, which is a sum of $\delta$-function profiles corresponding to 1 for the line wavelength, with a base of two (spectral) points, and 0 elsewhere \citep{Fiorenzano2005}). The computation of the radial velocity of the star for each spectrum with the CCF technique involves the evaluation of the correlation among thousands of spectral lines and the CCF function represents a mean spectral-line profile of all of the lines selected by the template. The radial velocity of the star for a particular spectrum is obtained by fitting the spectral-line profile with a proper probability distribution, usually the normal one (even if a well approximation is given also by using a Voigt function). The radial velocity is finally the mean of the fitted curve.

%By using the CCF technique, if changes occur in the spectral-line profiles of the star, the measured Doppler shifts may not correspond precisely to the velocity of the center of mass of the star (which is a common situation for pulsating stars with very active atmosphere). This behavior can be explained by the presence of active regions such as spots and faculae on the surface of the star \citep{Saar1997, Hatzes2002, Kurster2003}. To interpret the observed radial-velocity variations as true changes in the velocity of the star, it is necessary to show how the observed variations do not stem from changes in the stellar atmosphere. It is worthy of mention the fact that the radial velocity measurements are affected by changes of the profile line if its changes in a particular spectrum affect all of the spectral lines in a similar way.

%A first indicator derived by the CCF is the the full width at half-maximum of the CCF (FWHM) by\cite{Desort2007}. Since the FWHM is determined by the stellar rotation rate, fast rotating stars tend to be more active. The FWHM changes if a spot or a faculae region is present, in order to conserve the area enclosed by the line profile. This indicator has been used by \cite{Queloz2009} and \cite{Hatzes2010}.
%
%A more sophisticated indicator which provides the general asymmetry of the lines of a spectrum is line bisector, first introduced by \cite{Voigt1956}. The line bisector of an absorption line is defined as the middle point of the horizontal segment connecting points on the left and right sides of the profile with the same flux level. The line bisector is hence obtained by combining bisector points ranging from the core toward the wings of the line. Any correlation between radial velocity changes and line bisector orientation provides an element which disqualifies the interpretation of the observed radial-velocity variations as true changes in the velocity of the star. Generally speaking if the radial velocity variations are due to changes by its center of mass, the bisectors would oscillate to the left and right of the mean bisector with no change in shape or orientation. To the calculation of the asymmetry of the spectral lines the bisector velocity span \cite{Toner1988} is usually retrieved by considering a top zone near the wings and a bottom zone close to the core of the lines. The difference of the average values of velocities in the top and bottom zones, $V_{T}$ and $V_{B}$ respectively, determine the bisector velocity span (BVS). This is actually a measurement of the inverse of the mean slope of the bisector. According to \cite{Gray1989}, to establish the error for the bisector velocity span, the following expression is used:
%
%\begin{equation}
%\delta V = \left(\frac{S}{N}\right)^{-1} \left(2nF \frac{\Delta F}{x} \frac{dF}{dV} \right)^{-1/2},
%\label{eq:gray}
%\end{equation}
%where $S/N$ is the signal-to-noise of the spectrum, $n$ is the number of lines in the mask for the CCF, $F$ is the central flux of the zone of analysis, $\Delta F$ is the interval of flux determining the zone, $x$ is the scale of the spectrum based on the linear dispersion of the instrument and finally $dF/dV$ gives the slope of the profile in the zone being analyzed.
%
%Other quantities derived by the bisector are the curvature of the line bisector \citep{Hatzes1996}, the bisector inverse slope \citep{Queloz2001} and the bi-Gaussian cross-correlation function \cite{Figueira2013}. According to Desort et al. (2007), the FWHM, the BIS and photometric variations are not sufficient for providing enough information for slowly rotating stars (as for instance the Sun). When this is the case, to disentangle stellar activity from the Doppler effect caused by a ``Earth-like'' is not possible with the already known instruments.

%The procedure to retrieve the RV by fitting with a normal distribution the CCF and then calculating its first moment and the line bisector present a number of disadvantages. First of all the two procedures for recovering respectively the radial velocity of the star and evaluating the general asymmetry of the lines of the spectrum have done separately, whereas an eventual asymmetry of the spectral-line profile has an impact on the evaluation of the mean of the fitted curve. We note that by fitting the spectral-line profile with a symmetric distribution as the normal one, there is no way to access in one step an evaluation for both the radial velocity of the star and an indication of the stellar activity. Secondly, cause the way the line bisector is obtained, beyond the measurement errors coming from the observation of the star a further error according to (\ref{eq:gray}) has to be considered. For these two reasons we propose the evaluation of the CCF with a straightforward 1 step analysis, based on the implementation of the Skew Normal distribution, which eliminates both the disadvantages of the classic approach, providing moreover in a natural way an evaluation of the asymmetry caused by the stellar activity. 
%
%The paper is organized as follow. In Section $2$ the Skew Normal distribution is introduced, motivating its use for fitting the CCF. Section $3$ is dedicated to real case studies where an evaluation between the common analysis and the proposed one has done. Concluding remarks are presented in Section $4$.

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{The Skew Normal distribution} \label{sec:2}

The Skew Normal (SN) distribution, introduced by \cite{Azzalini1985}, is a class of probability distributions which includes the Normal distribution as a special case. The SN distribution has, in addition to a position and a scale parameter, a third parameter which describes the asymmetry of the distribution.

Formally the density function of the SN distribution for a random variable $Z \in \mathbb R$ is defined as:
\begin{equation} \label{def:snd}
SN(z; \alpha) = 2\phi(z)\Phi(\alpha z),
\end{equation}
where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN. It is possible to provide a general expression where both the location and the scale parameters are included. If $Z \sim SN(\alpha)$, $\xi \in \mathbb R$ and $\omega \in \mathbb R^{+}$, the density of $Y = \xi + \omega Z$ is defined as:

\begin{equation} \label{def:snd_gen}
SN(z;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\alpha\frac{y-\xi}{\omega}\right)
\end{equation}
and $Y \sim SN(\xi, \omega^{2}, \alpha)$.

From both a mathematical and an inferential viewpoint, the SN distribution has useful properties; the details can be found in \citet{Azzalini1985}. As previously mentioned, the Normal distribution is included in the SN family when $\alpha=0$. The parameter $\alpha$ provides information about the asymmetry of the curve. In Figure \ref{fig:SN.plot}, we plot the density function of the SN distribution for different values of $\alpha$.

\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{Skew_normal_densities.pdf} 
   \caption{Density function of a $SN(\alpha)$ for different choices of $\alpha$. For negative values of $\alpha$ the asymmetry will be on the left tail of the distribution.}
   \label{fig:SN.plot}
\end{figure}

By using the so-called direct parameterization (DP) defined in Eq. \ref{def:snd_gen} problems with parameters estimation arise in the evaluation of the likelihood function in a neighborhood of $\alpha=0$, where the presence of a stationary point complicates the achievement of the maximum likelihood or least squares estimates. In order to solve this problem, \citet{Azzalini1985} proposed to pass from the direct parameterization having parameters $\xi, \omega$ and $\alpha$ to the so-called centred parameterization (CP), which is introduced below.

According to Eq. \ref{def:snd_gen}, $Y = \xi + \omega Z = \mu + \sigma Z_{0} $, where $Z \sim SN(\alpha)$ and $Z_{0}$ is defined below. Hence the first two moments of $Z$ are defined simply with:

\begin{eqnarray}
\mu_{z} &=& E(Z) = b\delta, \nonumber\\
\sigma_{z} &=& var(Z) = 1-(b\delta)^2,\nonumber
\end{eqnarray}
where $b=\sqrt{2/\pi}$, $\delta = \alpha / \sqrt{1+\alpha^{2}}$ and $Z_{0}$, which is the standardization of $Z$, is defined as:

\begin{equation} \label{eq:snd_cp}
Z_{0}=\frac{1}{\sigma_{z}}\left(Z-\mu_{z}\right).
\end{equation}

By using Eq. \ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution. In fact, as it happens in the Normal case, $\mu$ and $\sigma^2$ indicate exactly the mean and the variance of the distribution, while $\gamma$ naturally represents an index for evaluating the asymmetry of the SN, making its interpretation simpler than the one available when $\alpha$ is considered. In order to completely define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of the one used in the DP $(\xi, \omega^2, \alpha)$:
%
\begin{eqnarray} \label{eq:1}
\mu &=& E(Y) = \xi + \omega \mu_{z}, \\
\sigma^{2} &=& var(Y) = \omega^{2} (1-\mu_{z})^2, \nonumber\\
\gamma &=& \frac{4-\pi}{2} \frac{\mu_{z}^{3}}{\left(1-\mu_{z}^2\right)^{3/2}}. \nonumber
\end{eqnarray}

By simple algebra, we can invert those equations to get the DP parameters as a function of the CP ones.
%
\begin{eqnarray} \label{eq:2}
\xi &=& \mu - b\omega\delta, \\
\omega &=& \frac{\sigma}{\sqrt{1 - b^2\,\delta^2}}, \nonumber\\
\alpha &=& \frac{R}{\sqrt{b^2 - (1-b^2)\,R^2}},\,R = sign(\gamma) \left[\frac{2\,|\gamma|}{4-\pi}\right]^{\frac{1}{3}}. \nonumber
\end{eqnarray}
%
The CP allows us to use the usual methods offered by the inferential theory and we will use this parametrisation for the rest of the paper. Further details about DP, CP and statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Fitting the Skew Normal distribution to the CCF} \label{sec:3}

%The CCF represents the average shape of spectral lines and is expressed in flux as a function of radial-velocity.
We fit the following function to the CCF:
%
\begin{eqnarray} \label{eq:3}
\mathrm{C} - \mathrm{A} \times SN(y;\mu, \sigma^2, \gamma),
\end{eqnarray}
%
where C is a constant fitting the continuum of the CCF, A is an amplitude parameter and $y$ is the RV of each point of the CCF. Note that the CCF is expressed in flux as a function of the lag of the cross-correlation template, expressed in RV.

We use least squares to fit the SN distribution to the CCF. Since each point of the CCF has a measurement error, we include this information in the specification of the SN distribution by introducing the following heteroskedastic function for the variance:
%
\begin{equation}
var(Y_{i})=\sigma^{2}+\sigma_{i}^{2}, i = 1, \dots, n,
\label{eq:vaf}
\end{equation}
%
where n corresponds to the number of points of the CCF and $\sigma_{i}$ represents the measurement error for each available point. By using Eq. \ref{eq:vaf} we can interpret the parameter $\sigma^{2}$ as a measure of the pure variability present in the evaluation of the CCF. However, although useful for estimating correct error bars in the case where the different $\sigma_{i}$ do not include all systematic, this heteroskedastic function only consider Gaussian distributed residuals. As the CCF is the result of a cross correlation, we expect the residuals of a Normal or a SN fit to show some red noise. For this reason, we first calculated the best fit for each CCF using a Normal or a SN distribution assuming Gaussian distributed noise. We then subtracted the median of the residuals obtained for all CCFs before performing a second fitting round. The result of this procedure is illustrated in Fig.~\ref{fig:Residual.comparison}. We see in the lower left panel that the residuals of a simple fit of a Normal or a SN distribution are strongly correlated. After removing the median of the residuals, in the lower right panel, the final residuals of the SN have nearly no correlation, while the final residuals of the Normal still present a small systematic component. This comes from the fact that because of the asymmetric nature of the CCF (see Sec. \ref{intro}), the SN distribution is a more flexible model than the Normal one.
%including the correct measurement errors in the analysis if , Eq. \ref{eq:vaf} assumes common variance for all the $n$ points of the CCF. Since the CCF is retrieved introducing different lags in the template, the latter assumption is not accurate, since unknown correlations will be produced as an effect of the procedure for retrieving the CCF. For this reason, in evaluating each CCF, we subtracted to each CCF its residuals, running the SN fit a second time with a ``decorrelated'' CCF as displayed in Fig.~\ref{fig:Residual.comparison}.

%Looking at Fig.~\ref{fig:Residual.comparison}, also after removing the correlations due to the CCF, a clear systematic trend is visible in the residuals when a Normal distribution is fitted, suggesting how by using simply a location and a scale parameter relevant aspects of the CCF are not explained. The behaviour of the residuals for the SN analysis suggests that the inclusion of a skewness parameter helps for explaining the characteristics of the CCF, although a small systematic component is still present in the residuals.

When using the least squares estimate for fitting the CCF with the SN distribution, we have to take into account the stationary problem in $\gamma=0$ due to the presence of the function $sign(\gamma)$ in Equation (\ref{eq:2}). Depending on the initial values of the numerical minimization for the least squares estimate of $\gamma$, the presence of this stationary point when evaluating $\gamma$ can lead to an incorrect estimation of the asymmetry parameter of the SN. In order to resolve this problem, we implemented two functions for retrieving the best least squares solution. In the first function we allowed for only positive solutions of $\gamma_1$ (with an upper limit of $0.995$), while in the second function only negative solutions are allowed (with a lower limit of $\gamma= -0.995$). The chosen solution is the estimate which has smallest residuals.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{[1]Plot_Fitting_and_Residuals_2run.pdf} 
   \caption{Comparison between the Normal and the Skew Normal fit for a particular CCF for the star Tau Ceti. The first run corresponds to fitting a Normal or a SN to the raw CCF. The second run corresponds to fitting the same function to the CCF after removing the median of all the residuals obtained in the first run. The SN residuals of the second run present a tiny correlation, whereas the Normal residuals present still a clear systematic component.}
   \label{fig:Residual.comparison}
\end{figure*}

In the following of the paper, we define the RV as the mean of the Normal or the mean of the SN (defined as SN RV). For the width of the CCF, we use the FWHM of the Normal, defined as $2\sqrt(2\ln2)\sigma$. The width of the SN, SN FWHM, is defined in the same way\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum linke in the Normal case.}. In the Normal case, it is not possible to retrieve an asymmetric parameter and therefore we use BIS SPAN. This will be compared to the asymmetric parameter $\gamma_1$ of the SN.

\section{Effect of stellar activity on radial velocities and correction} \label{sec:31}

Exoplanets will only produce a RV variation induced by a pure Doppler shift of stellar spectra. Stellar activity, on the contrary, does not produce a blueshift or redshift of the spectra, but creates a spurious RV signal by modifying the shape of spectral lines. To track these changes in line shape, we generally use the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} that give an information on the average width and asymmetry of the CCF. A strong correlation between the RVs and one or more of these parameters is a sign that the RVs are significantly affected by stellar activity signals.

To test the strength of the correlation between RVs and the different activity indicators, we calculated the Pearson correlation coefficient defined as:
%
\begin{equation}
R (x,y)= \frac{cov(x,y)}{\sigma(x),\sigma(y)},
\label{eq:Pearson:corr}
\end{equation}
where $x$ and $y$ are two quantitative variables, $cov(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represents their standard deviation. 
A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided, along with a $95\,\%$ confidence interval for $R$.
%

To correct for stellar activity signals, it is common to consider a linear combination of the RVs with the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case):
%
\begin{equation}
RV= \beta_{0} + \beta_{1}  \gamma + \beta_{2} FWHM + \epsilon,
\label{eq:RV:correction}
\end{equation}
%
where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ is the identity matrix). When the Normal fit is used, the parameter $\gamma_1$ is replaced by the BIS SPAN and SN FWHM by FWHM. In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,1,2$. The level for not rejecting the null hypothesis is fixed equal to $0.05$. Pearson correlation coefficient $R^{2}$ is considered for explaining how well this linear combination explains the variability of the RVs of the star due to stellar activity.

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Illustrative Examples} \label{sec:4}

In this Section we present the analyses of five stars, showing the advantages of fitting the CCF using the SN distribution defined in Section \ref{sec:3}.

A comparison with the results obtained by the classic approach is done, where the RVs of the star are estimated by the mean of the Normal distribution used to fit the CCF along with the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}.

\subsection{Alpha Centauri B} \label{sec:alphacentb}

We first analyze Alpha Centauri B, where $1816$ CCFs in 2010 are considered. Several measurement in 2010 are contaminated by light from Alpha Centauri A. To remove contaminated spectra and thus CCFs, we performed the same selection as presented in \citet{Dumusque-2012}.

We begin by evaluating the correlation between $\gamma$ and the classic BIS SPAN. In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.933$ and a strong Pearson correlation coefficient of $0.958$. 
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{HD12862_[2]gamma_vs_bisspan.pdf} 
   \caption{Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.}
   \label{fig:alphacent:corr.gamma}
\end{figure}

Figure \ref{fig:alphacent:diff:RV} shows the comparison between the RVs retrieved using the SN distribution and the ones obtained with the Normal distribution. This data set for Alpha Centauri B, used in \citet{Dumusque-2012} and \citet{Thompson-2017}, present a strong stellar activity signal. We see that the RVs measured by the SN fitting show more variations than the RVs measured by the Normal fitting. The SN fit is therefore significantly more sensitive to stellar activity. This can be explained by the fact that because the SN includes an asymmetry parameter, the RV defined as the mean of the SN distribution gets more shifted in the direction of the asymmetry induced by stellar activity.

We show the correction of stellar activity using Eq. \ref{eq:RV:correction} in Fig.~\ref{fig:alphacent:correctionRV}. We see that after correcting for stellar activity, the rms of the RV residuals in the Normal and SN analysis are extremely similar. However, we note that when using the SN analysis, the correction is more important. This is confirmed by the statistical tests on the significance of the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ whose results are summarized in Table \ref{table:alfa:test}. The intercept and both the variables $\gamma$ and SN FWHM are necessary for correcting the RVs retrieved using a SN and Normal fitting. The comparison of $R^2$ shows as well that the SN case accounts for a higher percentage of  variability in RVs.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
   \caption{RVs and RV differences for Alpha Centauri B considering a Normal and a SN fitting.}
   \label{fig:alphacent:diff:RV}
\end{figure*}

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD12862_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{RVs of Alpha Centauri B using a Normal and a SN fitting before and after correcting for stellar activity using Eq. \ref{eq:RV:correction}.}
   \label{fig:alphacent:correctionRV}
\end{figure*}

\begin{table}[!t]
\begin{tabular}{|c|c|c|}
\hline
Parameter          & Normal Fitting         &   Skew Normal Fitting \\
\hline
$\beta_{0}$            &    $0.0066$    & $2.29e-11$ \\
\hline
$\beta_{1}$            &    $0.022$    & $2.22e-16$ \\
\hline
$\beta_{2}$            &     $2.22e-16$   &  $ 2.22e-16 $ \\
\hline
$R^{2}$      &     $0.49$    &  $0.77$   \\
\hline
\end{tabular}
\caption{\textbf{Alpha Centauri B}: Evaluation of the linear combination used for correcting the RVs from stellar activity, according to Eq. \ref{eq:RV:correction}. The p-values for the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ for both the methodologies are summarized, as well as the $R^2$. Although more significant for the SN, all parameters are useful in explaining the variability of the RVs of the star. The evaluation of the $R^2$ shows how the linear combination better explains the variability in RVs due to stellar activity coming from the SN analysis.}
\label{table:alfa:test}
\end{table}

We compare the correlation between the different activity indicators and the RVs of the star in Fig.~\ref{fig:alphacent:corrPlot}. The correlation between $\gamma_1$ and RVs is much stronger, almost twice, than the correlation calculated between the other asymmetry parameters and their corresponding RVs. The correlation between FWHM and the RVs is as well stronger when fitting a SN distribution. All the correlations are statistically different from $0$.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD12862_[4]Comparison_para.pdf}  
   \caption{Correlation between the asymmetry parameters and the RVs for Alpha Centauri B. The last two plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN and the Normal fits.}
   \label{fig:alphacent:corrPlot}
\end{figure*}

By looking closer to the data in Fig.~\ref{fig:alphacent:clusters}, we saw that there are three distinct temporal clusters in the Alpha Centauri B measurements and those clusters have a different linear relationship between $\gamma_1$ and RVs (and also SN FWHM and RVs, though not displayed here). When considering Eq. \ref{eq:RV:correction} and the subsequent inferences, this clustering is not accounted for in the model. A slightly more general linear model that allows for different intercepts and different slopes for the three clusters for $\gamma_1$ and SN FWHM can be considered.  Adjusting the RVs for stellar activity using this expanded model produces the corrected radial velocities displayed in the left plot of Fig.~\ref{fig:alphacent:clusters_residuals}.  Those corrected RVs are different from those displayed in the lower left plot of Fig.~\ref{fig:alphacent:correctionRV} (which apply the correction derived from Eq. \ref{eq:RV:correction}); the right plot of Fig.~\ref{fig:alphacent:clusters_residuals} displays the difference between the two sets of corrected RVs. The long-term trend can be explained by the fact that the RV drift induced by the companion Alpha Centauri A is not well corrected, however the shorter-term variations show that stellar activity varies as a function of time, with spots and faculae evolving, and therefore modifies the dependence of the RVs with respect to $\gamma_1$ and SN FWHM. These temporal variations is something that we want to explore more, however this work presents a significant effort that we want to address in a future paper.

\begin{figure*}[htbp]
   \centering
\includegraphics[width = 6in]{AlphaCenB_clusters.pdf}  
   \caption{The RVs as a function of time (left) and the RVs plotted against $\gamma_1$ (right) with colors and plot symbol according to its temporal cluster assignment for Alpha Centauri B. The RVs are expressed in \ms.}
   \label{fig:alphacent:clusters}
\end{figure*}

\begin{figure*}[htbp]
   \centering
\includegraphics[width = 6in]{AlphaCenB_clusters_residuals.pdf}  
   \caption{The RV for Alpha Centauri B corrected for stellar activity using the SN fit and accounting for the temporal clusters (left), and the difference between those values on in the left plot and the analogous values without accounting for the temporal clusters (right) which are displayed in the lower left plot of Figure~\ref{fig:alphacent:correctionRV}. The RVs are expressed in \ms.}
   \label{fig:alphacent:clusters_residuals}
\end{figure*}

\subsection{HD192310}  \label{sec:Gl785}

We present now the results of the analysis for the star HD192310 (i.e. Gliese 785). The dataset consists in $1588$ CCFs. Figure \ref{fig:Gliese785:corr.gamma} shows the correlation between $\gamma$ and BIS SPAN to understand the link between those two parameters. It is interesting to see that, in this case, the slope of $0.645$ is significantly different from the one found for Alpha Centauri B in Fig.~\ref{fig:alphacent:corr.gamma}.
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{HD19231_[2]gamma_vs_bisspan.pdf} 
   \caption{Correlation between $\gamma$ and the BIS SPAN for HD192310.}
   \label{fig:Gliese785:corr.gamma}
\end{figure}

In Fig.~\ref{fig:Gliese785:correctionRV}, we see like for Alpha Centauri B that the RVs obtained with the SN analysis present a larger rms than the RVs obtained with the Normal fitting. However, once correcting for stellar activity using a linear correlation with $\gamma$ and SN FWHM (or BIS SPAN and FWHM, see Eq.~\ref{eq:RV:correction}), the rms of the residuals are comparable. We note that when correcting for stellar activity, the BIS SPAN is not statistically significant (see Table~\ref{table:Gliese785:test}). Like for Alpha Centauri B, the Pearson correlation coefficient $R^{2}$ shows  that the model we used to correct for stellar activity is a better one in the SN case than in the Normal case.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Radial Velocities for HD192310 using the Normal and the Skew Normal fitting before and after correcting the analyses from the stellar activity.}
   \label{fig:Gliese785:correctionRV}
\end{figure*}
%
\begin{table}[!t]
\begin{tabular}{|c|c|c|}
\hline
Parameter          & Normal Fitting         &   Skew Normal Fitting \\
\hline
$\beta_{0}$            &    $2e-16$    & $2.22e-16$ \\
\hline
$\beta_{1}$            &    $0.18$    & $2.22e-16$ \\
\hline
$\beta_{2}$            &     $2e-10$   &  $2.22e-16$ \\
\hline
$R^{2}$      &     $0.23$    &  $0.48$   \\
\hline
\end{tabular}
\caption{\textbf{HD192310}: Evaluation of the linear combination used for correcting the RVs from stellar activity, according to Eq. \ref{eq:RV:correction}. The p-values for the parameters  $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ for both the methodologies are summarized, as well as the $R^2$. Concerning the Normal fitting, the BIS SPAN is not statistically useful in explaining the variability of the RVs of the star, whereas for the SN analyses all the variables are statistically different from $0$. The evaluation of the $R^2$ shows how the linear combination better explains the variability in RVs due to stellar activity coming from the SN analysis.}
\label{table:Gliese785:test}
\end{table}

The comparison between the asymmetry parameters and the RVs are presented in Figure \ref{fig:Gliese785:corrPlot}. The $\gamma$ parameter shows a stronger correlation with the RVs ($0.587$) than the other asymmetric parameters. The correlation between the CCF width and the RVs is also stronger when fitting a SN rather than a Normal.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
   \caption{Correlation between the asymmetry parameters and the RVs for HD 192310. The last two plots show the correlation between the FWHM and the RVs for HD 192310 using respectively the SN and the Normal fits.}
   \label{fig:Gliese785:corrPlot}
\end{figure*}

\subsection{Tau Ceti}  \label{sec:Taucet}

The analysis of the star HD10700 (i.e. Tau Ceti) consists of $7963$ CCFs. Figure \ref{fig:Tau:corr.gamma} shows the relationship between $\gamma$ and the BIS SPAN, with a correlation of $0.605$ and a slope of the fitted line of $0.566$. Although still significant, we see that this correlation is weaker than in the case of Alpha Centauri B or HD192310. This is probably because HD10700 is at a very low activity level, similar to the Sun at its minimum activity phase.
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{HD10700_[2]gamma_vs_bisspan.pdf} 
   \caption{Correlation between $\gamma$ and the BIS SPAN for Tau Ceti.}
   \label{fig:Tau:corr.gamma}
\end{figure}

The RVs derived with the SN present a slightly more important rms as we can see in Fig.~\ref{fig:Tau:correctionRV}, and after correcting for stellar activity, the rms of the RV residuals are extremely similar. In Table~\ref{table:Tau:test}, we see that in the Normal and SN analysis, the intercept, the width and the asymmetry of the CCF (measured with FWHM or SN FWHM and $\gamma$ or BIS SPAN) can explain part of the RV variability measured. Looking at $R^2$, the RVs derived with the SN present a stronger relationship with acticity parameters than the RVs derived in the Normal.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{RVs for HD10700 using the Normal and the Skew Normal fitting before and after correcting for stellar activity.}
   \label{fig:Tau:correctionRV}
\end{figure*}
%
\begin{table}[!t]
\begin{tabular}{|c|c|c|}
\hline
Parameter          & Normal Fitting         &   Skew Normal Fitting \\
\hline
$\beta_{0}$            &    $0.00013$    & $2.22e-16$ \\
\hline
$\beta_{1}$            &    $4.83e-6$    & $2.22e-16$ \\
\hline
$\beta_{2}$            &     $2.22e-16$   &  $ 2.22e-16 $ \\
\hline
$R^{2}$      &     $0.27$    &  $0.43$   \\
\hline
\end{tabular}
\caption{\textbf{HD10700}: Evaluation of the linear combination used for correcting the RVs from stellar activity, according to Eq. \ref{eq:RV:correction}. The p-values for the parameters  $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ for both the methodologies are summarized, as well as the $R^2$. For both the analyses, all the variables are helpful, although the linear combination is statistically more significant when working with the SN parameters.}
\label{table:Tau:test}
\end{table}

The evaluation of the correlation between the asymmetry parameters and the SN RVs shows how using the SN procedure leads to much stronger correlations. The correlation between $\gamma$ and the RVs is $0.566$, whereas the correlation between the common asymmetry statistics with their corresponding RVs result in values close to $0$. The correlation between the FWHM and the RVs of HD10700 for the SN and the Normal are similar. 
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
   \caption{Correlation between the asymmetry parameters and the RVs for Tau Ceti. The last two plots show the correlation between the FWHM and the RVs for Tau Ceti using respectively the SN and the Normal fits.}
   \label{fig:Tau:corrPlot}
\end{figure*}

\subsection{HD215152}  \label{sec:HD215152}

The analysis of the star HD215152 consists in 284 CCFs and Figure \ref{fig:HD215152:corr.gamma} shows that the slope of the linear regression between $\gamma$ and the BIS SPAN is $0.591$ with a Pearson correlation coefficient of $0.767$.

\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{HD21515_[2]gamma_vs_bisspan.pdf} 
   \caption{Correlation between $\gamma$ and the BIS SPAN for HD 215152.}
   \label{fig:HD215152:corr.gamma}
\end{figure}

In the case of HD215152, we see in Fig.~\ref{fig:HD215152:correctionRV} that the RVs measured with the SN or the Normal, and the corresponding RV residuals after activity correction all present very similar RV rms. Thus activity correction does not seem to be very efficient at understand the RV variation. This is probably because of the presence of planetary signals in the RV data \citep[][]{Mayor-2011}. Note however that the information on the orbital phase of the planets is not present in \citet{Mayor-2011} and we cannot therefore remove those signals. The significance of $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ in Table~\ref{table:HD215152:test} shows that in the Normal case BIS SPAN is not significantly correlated with the RVs, while for the intercept and the FWHM the test with level $0.05$ is barely significant. In the SN case it is the intercept and FWHM that are not significantly correlated. The Pearson correlation coefficient $R^2$ shows that the RV derived from the SN fit are more affected by stellar activity than the RVs measured with the Normal, although the correlation is low at a level of 0.15.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Radial Velocities for HD 215152 using the Normal and the Skew Normal fitting before and after correcting the analyses from the stellar activity.}
   \label{fig:HD215152:correctionRV}
\end{figure*}

\begin{table}[!t]
\begin{tabular}{|c|c|c|}
\hline
Parameter          & Normal Fitting         &   Skew Normal Fitting \\
\hline
$\beta_{0}$            &    $0.041$    & $0.11$ \\
\hline
$\beta_{1}$            &    $0.79$    & $4.12e-11$ \\
\hline
$\beta_{2}$            &     $0.042$   &  $0.11$ \\
\hline
$R^{2}$      &     $0.020$    &  $0.15$   \\
\hline
\end{tabular}
\caption{\textbf{HD215152}: Evaluation of the linear combination used for correcting the RVs from stellar activity, according to Eq. \ref{eq:RV:correction}. The p-values for the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ for both the methodologies are summarized, as well as the $R^2$. Concerning the Normal fitting, the intercept and the FWHM are statistically significant at explaining the RV variations at level $0.05$ but not at level $0.01$, explaining why the $R^{2}$ is only $0.02$. The BIS SPAN is however not significant. For the SN case, it is the contrary, $\gamma_1$ is significant in explaining the SN RV variations, while the FWHM and the intercept are not. When looking at the value of 
$R^2$, although the correlation is stronger for the SN case, is stay low at a level below 0.15.}
\label{table:HD215152:test}
\end{table}

The correlations among the asymmetry parameters and the RVs shows also in this case that using the SN fitting provides a stronger result. The correlation between $\gamma$ and the RVs is $0.38$, whereas the correlation between the common asymmetry statistics and their corresponding radial velocities is smaller than $0.30$. The SN FWHM or the FWHM are not significantly correlated to the SN RVs or the RVs.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
   \caption{Correlation between the asymmetry parameters and the RVs for HD 215152. The last two plots show the correlation between the FWHM and the RVs for HD 215152 using respectively the SN and the Normal fits.}
   \label{fig:HD215152:corrPlot}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Corot-7}  \label{sec:Corot7}

The final star considered is Corot-7 which has low signal to noise. A total of $180$ CCFs have been analysed and Fig.~\ref{fig:Corot7:corr.gamma} shows the correlation between $\gamma$ the BIS SPAN with a linear regression slope of $0.596$.
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{LRa01_E_[2]gamma_vs_bisspan.pdf} 
   \caption{Correlation between $\gamma$ and the BIS SPAN for Corot-7.}
   \label{fig:Corot7:corr.gamma}
\end{figure}

The RVs obtained with the SN show more variability than the RVs derived with the Normal. After correcting for stellar activity using Eq.~\ref{eq:RV:correction}, the RV residuals with both distributions are similar. In Table~\ref{table:Corot7:test}, we see that in the Normal and the SN analyses, the intercept, the width and the asymmetry of the CCF (measured with FWHM or SN FWHM and $\gamma$ or BIS SPAN) can explain part of the RV variability measured. Looking at $R^2$, the RVs derived with the SN present like for all the stars in this paper a stronger correlation with $\gamma_1$ and SN FWHM than the RV derived in the Normal case.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{LRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Radial velocities for Corot-7 using the Normal and the Skew Normal fitting before and after correcting the analyses from the stellar activity.}
   \label{fig:Corot7:correctionRV}
\end{figure*}

\begin{table}[!t]
\begin{tabular}{|c|c|c|}
\hline
Parameter          & Normal Fitting         &   Skew Normal Fitting \\
\hline
$\beta_{0}$            &    $2e-16$    & $2.22e-16$ \\
\hline
$\beta_{1}$            &    $0.0067$    & $0.00054$ \\
\hline
$\beta_{2}$            &     $2.22e-16$   &  $2.22e-16$ \\
\hline
$R^{2}$      &     $0.36$    &  $0.47$   \\
\hline
\end{tabular}
\caption{\textbf{Corot-7}: Evaluation of the linear combination used for correcting the RVs from stellar activity, according to Eq.~\ref{eq:RV:correction}. The p-values for the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ for both the methodologies are summarized, as well as the $R^2$. For both the analyses, all the variables are helpful, although the linear combination is more useful in explaining the RV variability when working with the SN fitting.}
\label{table:Corot7:test}
\end{table}

The correlation between $\gamma$ and the SN RVs of Corot-7 is much stronger than the correlation between  the RVs and other asymmetric indicators (see Fig.~\ref{fig:Corot7:corrPlot}). The correlation between $\gamma$ and the SN RVs is $0.462$, whereas the correlation between the other asymmetry statistics with their corresponding RVs result in values close to $0$. Also the correlation between the FWHM and the RVs of Corot-7 when using the SN fitting is stronger. These significant correlations for the SN parameters and non-significant for the Normal parameters suggest that for low signal to noise measurement, using the SN fitting improves our power in detecting stellar activity signals. 
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
   \caption{Correlation between the asymmetry parameters and the RVs for Corot-7. The last two plots show the correlation between the FWHM and the RVs for Corot-7 using respectively the SN and the Normal fits.}
   \label{fig:Corot7:corrPlot}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Estimation of standard errors for the CCF parameters} \label{sec:5}

The HARPS reduction pipeline gives the pure photon-noise error estimate on the RVs. This error, called \emph{noise}, is not derived from the Normal fit to the CCF but from the method described in \citet{Bouchy-2001b} using the CCF derivative. Then \emph{noise} is associated to the RV error, $2\times$\emph{noise} to the BIS SPAN error and $2.35\times$\emph{noise} to the FWHM error.

In this section, we do a bootstrap analysis to measure the standard errors on the RVs or SN RVs, the FWHM or SN FWHM, and BIS SPAN or $\gamma_1$. Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other. Therefore, we cannot do a bootstrap analysis on perturbing independently each CCF point with a Gaussian distribution scaled to the error of each given point. To bypass this problem, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF. We then fit a Normal or a SN to each of these CCFs, and the standard deviation of the distribution for the mean (RV or SN RV), the width parameter (FWHM or SN FWHM) and the asymmetric parameter ($\gamma_1$ or BIS SPAN) is associated to the error on each of these parameters.

In the top plots of Fig.~\ref{fig:se} we show the different errors for the RVs, the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels. The parameter SN50 corresponds to the SNR in order 50, which corresponds to a wavelength of 550\,nm. In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN or the Normal and the \emph{noise} parameter extracted from the HARPS reduction pipeline. We first see that the errors on the CCF parameters only depends on the SNR and do not depend on the spectral type. This is true if the spectral type are not too different though, like here where we show the results for G and K dwarfs.

We see that for the RV errors, the ratio between the \emph{noise} parameter and the the RV error measured by the bootstrap using the Normal fitting is around 1, meaning that those two estimates of the RV errors are similar. However when fitting a SN to the CCF, we have RV errors that are on average 60\% greater. Thus, the RVs measured by the SN do not have the same precision than the RVs calculated using the Normal. This can be explained by the fact that in the case of the SN, variations in the asymmetry parameter $\gamma_1$ induce variations in the SN RV measured due to the strong correlation between those two parameters. Therefore, the errors in $\gamma_1$ propagate to the error in the SN RVs.

Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal or the SN are equivalent to 2.35$\times$\emph{noise}. Therefore, the precision in CCF width is the same if we fit a Normal or a SN to the CCF.

Finally, for the errors in CCF asymmetry, we see that the boostrap analysis using the Normal fitting gives the same precision as using 2$\times$\emph{noise}, which is the common errors used for BIS SPAN. However, when fitting the SN to the CCF, the asymmetry errors are 15\% smaller. Therefore, the SN fit gives a better precision in CCF asymmetry than what can be reached using BIS SPAN.

Another interesting point is the behavior of the ratio of the bootstrap errors over the \emph{noise} parameter as a function of SNR (see bottom plots in Fig.~\ref{fig:se} for the RVs, CCF width and CCF asymmetry). We see that at low SNR, the bootstrap analysis gives a better precision, which can be explained by the fact that the \emph{noise} parameter is estimated using the CCF derivative. Calculating the derivative of the CCF increases the noise and therefore explain this behavior at low SNR. For SNR below 200, the bootstrap analysis gives a better precision than the \emph{noise} parameter.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
   \caption{Comparison between the standard errors using the bootstrap analysis and the parameter $noise$ for the RVs, $2.35\times$\emph{noise} for the width, and $2\times$\emph{noise} for the asymmetry parameter. Note that for the asymmetry, the error in BIS SPAN is in \kms. To be able to compare the errors in $\gamma_1$ and BIS SPAN, we multiplied the error in $\gamma_1$ by the slope of the correlation between $\gamma_1$ and BIS SPAN.}
   \label{fig:se}
\end{figure*}

%, using the spectrum derivative
%, the pure photon-noise error on RV measured 
%Together with the pointwise estimates, retrieving the standard errors for the RVs of the star, $\gamma$ and the FWHM provides information about the uncertainties associated to each parameter. Since the procedure for retrieving the RVs of the star consists in fitting with a density function a CCF, getting the standard errors for all the parameter of interests cannot be done by using the common asymptotic theory. The implementation of a standard bootstrap analysis cannot as well be done, because the points of the CCF are highly correlated. In the analysis of the present work, in order to get the standard errors for the parameters of interest for a particular CCF, we moved each point of this CCF according to its measurement errors, producing $100$ simulated CCFs from the original one. Then we run both the Normal and the SN analyses on these simulated CCFs, letting us to retrieve an evaluation of the standard errors. This operation has been repeated for all the CCFs available for the analyzed stars. The comparison between the standard errors retrieved in this way with the classic noise parameter, {\color{red} obtained by using the Gray's equation cit. Gray (1983)} are presented in Figure \ref{fig:se}.  {\color{red} Xavier: Is it correct how the noise parameter is obtained? Or it is simply $\sqrt(photons)$?}

%Given the strong correlation between the $\gamma$ parameter of the SN and its mean, the standard errors are larger respect the Normal fitting analysis. This fact confirms how correcting the RVs for stellar activity using Eq. \ref{eq:RV:correction} is more helpful when using the SN fitting. The standard errors for the FWHM are comparable for both the SN and the Normal analyses, whereas an improvement is clearly measurable for the standard errors associated to the asymmetry indicators. The last plot in Fig.~\ref{fig:se} shows that the standard errors for $\gamma$ are $10 \%$ smaller than the ones retrieved for the BIS SPAN.

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Discussion} \label{sec:discu}

An analysis of the CCF residuals after fitting a Normal or SN distribution show that the SN is a better model to explain the shape of the CCF. This comes from the fact that CCFs present a natural asymmetry due the convective blueshift.

We compared for five stars the difference between the RVs, FWHM and asymmetry (BIS SPAN in the Normal case and parameter $\gamma_1$ in the SN case) as measured we a Normal or a SN fitting to the CCF. The $\gamma_1$ parameter is linearly dependant on the BIS SPAN, with always a strong correlation coefficient. 
%To compare $\gamma_1$, that do not have any units, with BIS SPAN expressed in \kms, one has simply to multiply $\gamma_1$ by the slope of the linear dependence between $\gamma_1$ and BIS SPAN. 
The slope of this linear correlation change depending on the star studied. This is probably because the spectral type is different, therefore the effects from stellar activity are different.

When comparing the RV as measured by the Normal and the SN fitting, we always see that the rms of the latter is larger. Thus fitting the SN to the CCF gives RV measurements that are more sensitive to activity. This comes from the fact the the asymmetry parameter of the SN will modify as well the mean of the distribution, thus the RV. This is a positive point as it is easier to correct for a signal that is at a high SNR rather that a signal that is at a SNR of one, which is generally the case for the low-activity stars that are followed for RV surveys.

The RVs derived using the SN fitting present a higher sensitivity to stellar activity. However, once correcting the RVs from stellar activity using a linear combination of the width and asymmetry parameter of the CCF (FWHM and BIS SPAN in the Normal case, and SN FWHM and $\gamma_1$ in the SN case), the RV residuals in both the Normal and SN case show similar scatter. Therefore, the SN fitting does not improve stellar activity correction when using a simple linear combination with the width and asymmetry of the CCF. However, because the amplitude of the variations is larger in the raw SN RVs, correction techniques based on Gaussian Processes might be more efficient \citep[][]{Haywood-2014,Faria-2016a,Dumusque:2017aa}.

When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma_1$ in the SN case) with respect to the RVs (RVs in the Normal case or SN RVs in the SN case), we observe that the correlations are always stronger for the parameters of the SN. Therefore, the SN parameters are more sensitive to activity. In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of 0.57 between $\gamma_1$ and SN RV, while for all the other asymmetric parametrisation, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.21.

We also studied the behavior of the noise on the different parameters of the Normal and the SN as a function of SNR. By performing a bootstrap analysis, we confirmed that in the case of the Normal, using the \emph{noise} parameter as returned by the HARPS pipeline gives a correct estimate of the errors measured on the RVs, FWHM and BIS SPAN for SNR $>150$. For the RVs, the errors are equivalent to \emph{noise}, for the FWHM to 2.35$\times$\emph{noise} and for the BIS SPAN to 2$\times$\emph{noise}. For lower SNR though, the bootstrap analysis gives better results, and this comes from the fact the the \emph{noise} parameter is estimated using the derivative of the CCF, which increase the noise \citep[][]{Bouchy-2001b}. For very low SNR, the improvement of the bootstrap analysis can be as high as 50\%. Therefore, although taking much more time, we encourage the use of bootstrapping when calculating errors for the different parameters of the CCF.

In the case of the errors when using the SN fitting, the precision on the SN RVs is however 60\% worse than for the RVs. This comes from the fact that because the asymmetry is accounted for in the SN and because the SN RVs and $\gamma_1$ are strongly correlated, the errors in $\gamma_1$ propagates to the errors in SN RVs. This is not so important for SNR $>$ 150 for which the errors are below the \ms precision of HARPS and the \ms variation induced by stellar activity signals even in low activity cases \footnote{As we can see in papers publishing HARPS results using an additional jitter to consider stellar activity noise not accounted for in the \emph{noise} parameter, the extra jitter is always greater than 0.8\ms \citep[e.g.][]{Udry:2017aa,Feng:2017aa,Diaz:2016ab}.}. These larger errors in RVs can be a problem for low SNR measurements. In the case of the CCF width, the error derived when using the Normal or SN fitting are very similar. Finally for the asymetry, we see that the error in $\gamma_1$ is $\sim$15\% smaller than the error in BIS SPAN.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion} \label{sec:conclu}

In this paper we introduced a novel approach based on the Skew Normal (SN) distribution for deriving RVs and shape variations in the CCF of stars. When searching for small-mass exoplanets using the RV technique, it is essential to understand the shape variation of the CCF, which is a proxy for stellar activity effects. The standard approach consist in first to adjust a Normal distribution to the CCF to get the RV and FWHM, defined as the mean and the FWHM of the Normal distribution, and then to measure the asymmetry by calculating BIS SPAN. FWHM and BIS SPAN give us information on the line shape that are used to probe stellar activity signals. In this paper we demonstrate that by using the SN distribution to fit CCFs, we can measure simultaneously the RV of the star with the width and asymmetry of the CCF.

Using the SN to fit CCFs brings a significant improvement in probing stellar activity. The correlations between SN RV and SN FWHM, and SN RV and the asymmetric parameter $\gamma_1$ are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}). The RVs derived by the SN are also more sensitive to activity and the precision on the asymmetry measured by $\gamma_1$ is greater than the one on BIS SPAN by $\sim$15\%. Therefore when searching for rotational periods in the data, or applying Gaussian Processes to account for stellar activity signals, the SN parameters should be used.

At first glance, one downside of using the SN comes from the RV errors that are greater by 60\% relative to the RV errors measured when considering a Normal. This is due to the strong correlation between SN RV and $\gamma_1$ and this can be a problem for low SNR measurements. However, in the regime of SNR $>$ 150, which is the aim of all RV surveys at high precision, the precision of the SN RVs is below the \ms, which is thus below the instrumental precision of HARPS and below the RV perturbations induced by stellar activity.

Finally, we also encourage the use of bootstrapping to estimate more realistic errors on the different parameters of the Normal or SN fitted to the CCF, mainly in the low SNR regime where a gain of 50\% can be reached. This takes significantly more time, but note that 100 realization are enough to get a good estimation of errors.

%the RVs of the star can be calculated as the mean of the SN, whereas its asymmetry parameter $\gamma$ can be naturally used for retrieving information about the asymmetry of the CCF. Because of the natural correlation between the RVs and the asymmetry parameter, a linear combination of both $\gamma$ and the FWHM has been implemented for correcting the RVs from stellar activity, allowing us to retrieve a more precise RVs.

%In order to get the standard errors for the estimated parameters, rather than using the common $noise$ statistic, we created a simulated procedure based on perturbing each point of the CCF according to its measurement error. Then, by getting from the original profile line $100$ simulated profiles, we run the SN fitting analyses, allowing us retrieving for all the parameter of interests an estimation for their standard errors. Concerning the standard error associated to the means of the distributions, the SN fit leads to slightly larger standard errors respect when running the Normal fit. This fact can be explained by noticing that as a simulated CCF is created according to the procedure described above, we expect slightly differences on the asymmetry of the CCF as well. The natural correlation between the RVs of the star and $\gamma$, where the mean of the SN is shifted in the direction of the asymmetry of the distribution, leads to larger uncertainties related to the RVs of the star. The latter consideration provides a further justification for correcting the RVs of the star from stellar activity and explains why this correction is more helpful when running the proposed analysis rather than the classic Normal fit. Concerning the standard errors related to the asymmetry parameters, when using the SN fit the uncertainties are $10 \%$ smaller than using the classic BIS SPAN. In conclusion, we showed how using the SN fit provides in an unique step a better understanding of the stellar activity through using the asymmetry parameter $\gamma$ rather than using the common statistics such as the BIS SPAN or other indicators. On top of that, when focusing on low signal to noise cases, the SN procedure showed how statistically significant results are retrieved with the proposed approach in terms of correlation between the asymmetry of the profile line and the RVs, whereas for the previous analyses this correlation does not result statistically significant.

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Acknowledgements}

We are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
XD is grateful to the Society in Science--The Branco Weiss Fellowship for its financial support.

%%-----------------------------------------------------------------------------------------------------------------------------------------------
\bibliographystyle{aa}
\bibliography{dumusque_bibliography}

%\begin{appendix}
%\end{appendix}

\end{document}

### 2018-03-15 manuscript.tex
Added new .tex file for paper

--- 2018-03-11 Skew_Normal_CCF.tex
@@
-\documentclass{aa}
-%\documentclass[referee]{aa}
+\documentclass[11pt, oneside]{article}   
+\usepackage{geometry}                		
+\geometry{letterpaper}                   		
+\usepackage{graphicx}
+
+\usepackage{amssymb}
+
 \usepackage{natbib}
-%\usepackage{lscape}
-\usepackage{pdflscape} % or {lscape}
+\bibliographystyle{abbrvnat}
+\usepackage{aas_macros} % AAS journal abbreviations
+
+\usepackage{lscape}
+%\usepackage{pdflscape} % or {lscape}
 \usepackage{wasysym}
@@
 \usepackage{longtable}
-
 \usepackage{afterpage}
-
 \usepackage[usenames,dvipsnames]{color}
@@
 
-\begin{document}
-
-\title{Cross correlation function line-profile variations in radial-velocity measurements by fitting a Skew Normal distribution
-\thanks{Based on observations collected at the La Silla Parana Observatory,
-ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}}
+\title{Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution}
+%\thanks{Based on observations collected at the La Silla Parana Observatory,
+%ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}}
 
@@
 
-\author{U. Simola \inst{1,2}
-	    \thanks{\email{umberto.simola@yale.edu}}
-	    \and X. Dumusque\inst{3}
-	    \thanks{Society in Science -- Branco Weiss Fellow (url: \url{http://www.society-in-science.org})}    
-	    \and Jessi Cisewski\inst{2}
+\author{U. Simola
+	    \and X. Dumusque
+	    \and Jessi Cisewski-Kehe
 	    }
 
-\institute{Department of Statistical Sciences, University of Padua, Padua, Italy
-	      \and Department of Statistics and Data Science, Yale University, New Haven, CT, USA
-	      \and Observatoire de Gen\`eve, Universit\'e de Gen\`eve, 51 ch. des Maillettes, CH-1290 Versoix, Switzerland 
-	      }
+%\author{U. Simola \inst{1,2}
+%	    \thanks{\email{umberto.simola@yale.edu}}
+%	    \and X. Dumusque\inst{3}
+%	    \thanks{Society in Science -- Branco Weiss Fellow (url: \url{http://www.society-in-science.org})}    
+%	    \and Jessi Cisewski\inst{2}
+%	    }
+%
+%\institute{Department of Statistical Sciences, University of Padua, Padua, Italy
+%	      \and Department of Statistics and Data Science, Yale University, New Haven, CT, USA
+%	      \and Observatoire de Gen\`eve, Universit\'e de Gen\`eve, 51 ch. des Maillettes, CH-1290 Versoix, Switzerland 
+%	      }
 
-\date{Received XXX; accepted XXX}
+\begin{document}
+\maketitle
 
-\abstract
+%\abstract
+{\bf Abstract}\\
 % Context, Aims, Methods, Results, Conclu (not mandatory)
-{{\bf An exoplanet or stellar companion will induce a variation in the radial velocity (RV) of its host star, which will translate into a pure-Doppler shift of the stellar spectrum and thus a velocity shift of the cross-correlation function (CCF) without changing its shape.
-The barycenter of the CCF is therefore a measure of the stellar RV.
-We generally measure this barycenter by fitting a Normal distribution to the CCF and then retreving its first moment, i.e.
-its mean.
-However, some astrophysical processes, like oscillations, granulation, stellar activity and single-lined spectroscopic binaries will modify the asymetry of the CCF, which will introduce a spurious radial-velocity variation and perturb the detection of exoplanets.
-To decorrelate the signals introduced by exoplanets from the one introduced by other astrophysical processes, we use the higher moments of the CCF.
-Note that in the case of high-precision RV surveys, mainly focusing on non-blended GKM dwarfs, stellar activity is the main perturbing signal.}}
-{We propose here to measure the moment of the CCF using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, provides an extra parameter to model the CCF natural asymmetry.}
+{When working with radial velocities for detecting Extrasolar planets and when using data from stabilized spectrographs,
+the different moments of the cross-correlation function (CCF) are used to measure the radial velocity of the star but also the changes in the shape of the CCF.
+Those changes are due to stellar activity and therefore the best precision on these moments is required to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.}
+{We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, provides an extra parameter to model the CCF natural asymmetry.}
 {We analyzed 5 stars with different activity levels and different signal-to-noise ratio levels.
@@
 RVs derived from a SN distribution are more sensitive to activity, which is interesting when looking for rotational periods or characterizing better stellar activity.
-However, once correcting the RVs from stellar activity signanol using a linear combination of the CCF asymmetry and width, the RV residuals obtained from a Normal or SN fitting are very similar.
+However, once correcting the RVs from stellar activity signal using a linear combination of the CCF asymmetry and width, the RV residuals obtained from a Normal or SN fitting are very similar.
 The precision on the asymmetric parameter derived from the SN is also 15\% better than the one derived on the common Bisector Inverse Slope Span (BIS SPAN).
@@
 
-\keywords{techniques: radial velocities -- planetary systems -- stars: activity -- methods: data analysis}
+%\keywords{techniques: radial velocities -- planetary systems -- stars: activity -- methods: data analysis}
 
-\titlerunning{Fitting a SN distribution to CCF}
-\authorrunning{U. Simola, X. Dumusque and J. Cisewski}
-\maketitle
-
-%-----------------------------------------------------------------------------------------------------------------------------------------------
 \section{Introduction}
@@
 
-By measuring the radial-velocity of a star, it is possible to detect the stellar wobble induced by the gravitational pull of orbiting planets.
-This so-called radial-velocity (RV) technique is an indirect method as the planet cannot be seen.
-This poses some difficulties as the RV technique is not only sensitive to planetary signals, but also to different stellar signals.
-At the meter-per-second level, RV measurements are affected by oscillations \citep[][]{Arentoft-2008,Kjeldsen-1995,Mayor-2003}, granulation \citep[][]{Meunier-2016,Dumusque-2011a,Lindegren-2003,Del-Moro-2004} and activity signals \citep[][]{Dumusque-2014,Meunier-2011,Saar-2009,Desort-2007,Saar-1997}.
-Other effects can also introduce RV variations, like single-lined spectroscopic binaries (SB1).
-High-precision RV surveys tends to avoid targeting any SB1 and to observe GKM dwarfs to minimize the impact of oscillations and granulation.
-High-precision RV surveys also tend to observe quiet stars in terms of stellar activity, however, as most of the star present solar-like magnetic cycles \citep[][]{Lovis-2011b}, it is not possible to observe the same star at a quiet stage for several continous years.
-Stellar activity is therefore the main limitation to the detection of Earth-like planey
-
-While the gravitational pull of an orbiting planets introduces a pure-Doppler
-
-The radial velocity (RV) technique is an indirect method to detect exoplanets.
-
-By measuring the radial velocity induced by the stellar wobble induced by a planet orbiting its host star
-
-%The radial velocity (RV) of a star is defined to be the velocity of the center of mass of the star along our line of sight.
+The radial velocity (RV) of a star is defined to be the velocity of the center of mass of the star along our line of sight.
 This quantity can be derived precisely by measuring the Doppler shift of spectral lines produced in stellar atmospheres.
@@
 
-%For stabilised spectrographs, the RV is derived by first correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}, which gives an average line profile, generally called Cross Correlation Function (CCF).
+For stabilized spectrographs, the RV is derived by first correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}, which gives an average line profile, generally called Cross Correlation Function (CCF).
 Then a Normal distribution is fitted to this average profile to get the mean, namely the RV, and the full width at half maximum (FWHM) of the profile.
@@
 The differences in flux and velocity between upflows and downflows change the Normal profile of spectral lines that become asymmetric with a "C"-shaped profile \citep[][]{Dravins-1981}.
-The strength of the asymmetry depends on the velocity of the convection, approximately 300\ms for the Sun, but also on the formation depth of spectral lines \citep{Gray-2009}.
+The strength of the asymmetry depends on the velocity of the convection, approximatively 300\ms for the Sun, but also on the formation depth of spectral lines \citep{Gray-2009}.
 Since the CCF is an average of all the spectral lines, some strongly asymmetric and some not, its asymmetry is rather small, which is why a Normal distribution is a proper model to fit the CCF.
-%This small asymmetry modifies however slightly the estimated RVs of the star, reducing the accuracy of the measurement, but if this asymmetry does not vary with time, the precision is kept.
+This small asymmetry modifies however slightly the estimated RVs of the star, reducing the accuracy of the measurement, but if this asymmetry does not vary with time, the precision is kept.
 
@@
 %
-The CP allows us to use the usual methods offered by the inferential theory and we will use this parametrisation for the rest of the paper.
+The CP allows us to use the usual methods offered by the inferential theory and we will use this parameterization for the rest of the paper.
 Further details about DP, CP and statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
+
 %-----------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-Finally, for the errors in CCF asymmetry, we see that the boostrap analysis using the Normal fitting gives the same precision as using 2$\times$\emph{noise}, which is the common errors used for BIS SPAN.
+Finally, for the errors in CCF asymmetry, we see that the bootstrap analysis using the Normal fitting gives the same precision as using 2$\times$\emph{noise}, which is the common errors used for BIS SPAN.
 However, when fitting the SN to the CCF, the asymmetry errors are 15\% smaller.
@@
 Therefore, the SN fitting does not improve stellar activity correction when using a simple linear combination with the width and asymmetry of the CCF.
-However, because the amplitude of the variations is larger in the raw SN RVs, correction techniques based on Gaussian Processes might be more efficient \citep[][]{Haywood-2014,Faria-2016a,Dumusque:2017aa}.
+However, because the amplitude of the variations is larger in the raw SN RVs, correction techniques based on Gaussian Processes might be more efficient \citep[][]{Haywood-2014,Faria-2016a}.
 
@@
 Therefore, the SN parameters are more sensitive to activity.
-In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of 0.57 between $\gamma_1$ and SN RV, while for all the other asymmetric parametrisation, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.21.
+In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of 0.57 between $\gamma_1$ and SN RV, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.21.
 
@@
 This comes from the fact that because the asymmetry is accounted for in the SN and because the SN RVs and $\gamma_1$ are strongly correlated, the errors in $\gamma_1$ propagates to the errors in SN RVs.
-This is not so important for SNR $>$ 150 for which the errors are below the \ms precision of HARPS and the \ms variation induced by stellar activity signals even in low activity cases \footnote{As we can see in papers publishing HARPS results using an additional jitter to consider stellar activity noise not accounted for in the \emph{noise} parameter, the extra jitter is always greater than 0.8\ms \citep[e.g.][]{Udry:2017aa,Feng:2017aa,Diaz:2016ab}.}.
+This is not so important for SNR $>$ 150 for which the errors are below the \ms precision of HARPS and the \ms variation induced by stellar activity signals even in low activity cases \footnote{As we can see in papers publishing HARPS results using an additional jitter to consider stellar activity noise not accounted for in the \emph{noise} parameter, the extra jitter is always greater than 0.8\ms \citep[e.g.][]{Diaz:2016ab}.}.
 These larger errors in RVs can be a problem for low SNR measurements.
@@
 \bibliography{dumusque_bibliography}
+%\bibliography{mybib-SNCCF}
 

### 2018-03-15 manuscript_umberto.tex
Added new .tex file for paper

--- 2018-03-15 manuscript.tex
@@
-\documentclass[11pt, oneside]{article}   
-\usepackage{geometry}                		
-\geometry{letterpaper}                   		
-\usepackage{graphicx}
-
-\usepackage{amssymb}
-
+\documentclass{aa}
+%\documentclass[referee]{aa}
 \usepackage{natbib}
 \bibliographystyle{abbrvnat}
-\usepackage{aas_macros} % AAS journal abbreviations
-
 \usepackage{lscape}
@@
 
-\title{Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution}
-%\thanks{Based on observations collected at the La Silla Parana Observatory,
-%ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}}
+\begin{document}
+
+\title{Cross correlation function line-profile variations in radial-velocity measurements by fitting a Skew Normal distribution
+\thanks{Based on observations collected at the La Silla Parana Observatory,
+ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}}
 
@@
 
-\author{U. Simola
-	    \and X. Dumusque
-	    \and Jessi Cisewski-Kehe
+\author{U. Simola \inst{1,2}
+	    \thanks{\email{umberto.simola@yale.edu}}
+	    \and X. Dumusque\inst{3}
+	    \thanks{Society in Science -- Branco Weiss Fellow (url: \url{http://www.society-in-science.org})}    
+	    \and Jessi Cisewski\inst{2}
 	    }
 
-%\author{U. Simola \inst{1,2}
-%	    \thanks{\email{umberto.simola@yale.edu}}
-%	    \and X. Dumusque\inst{3}
-%	    \thanks{Society in Science -- Branco Weiss Fellow (url: \url{http://www.society-in-science.org})}    
-%	    \and Jessi Cisewski\inst{2}
-%	    }
-%
-%\institute{Department of Statistical Sciences, University of Padua, Padua, Italy
-%	      \and Department of Statistics and Data Science, Yale University, New Haven, CT, USA
-%	      \and Observatoire de Gen\`eve, Universit\'e de Gen\`eve, 51 ch. des Maillettes, CH-1290 Versoix, Switzerland 
-%	      }
+\institute{Department of Statistical Sciences, University of Padua, Padua, Italy
+	      \and Department of Statistics and Data Science, Yale University, New Haven, CT, USA
+	      \and Observatoire de Gen\`eve, Universit\'e de Gen\`eve, 51 ch. des Maillettes, CH-1290 Versoix, Switzerland 
+	      }
 
-\begin{document}
-\maketitle
+\date{Received XXX; accepted XXX}
 
-%\abstract
-{\bf Abstract}\\
+\abstract
 % Context, Aims, Methods, Results, Conclu (not mandatory)
@@
 
-%\keywords{techniques: radial velocities -- planetary systems -- stars: activity -- methods: data analysis}
+\keywords{techniques: radial velocities -- planetary systems -- stars: activity -- methods: data analysis}
 
+\titlerunning{Fitting a SN distribution to CCF}
+\authorrunning{U. Simola, X. Dumusque and J. Cisewski}
+\maketitle
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
 \section{Introduction}

### 2018-03-15 manuscript.tex
Added Umberto's bib and updated manuscript.tex
Added referee comments to sec 1 - 2

@@
 
+\newcommand{\jessi}[1]{{\color{Purple}[[\textbf{Jessi: }#1]]}}
+\newcommand{\xavier}[1]{{\color{blue}[[\textbf{Xavier: }#1]]}}
+\newcommand{\umberto}[1]{{\color{green}[[\textbf{Umberto: }#1]]}}
+\newcommand{\comment}[1]{{\color{red}[[\textbf{Referee: }#1]]}}
+
 \title{Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution}
@@
 The radial velocity (RV) of a star is defined to be the velocity of the center of mass of the star along our line of sight. 
+\comment{No, the radial velocity you measure of the star has many components that contribute to the RV: the space motion (present even if there is no companion), the motion about the center of mass (the so-called ?-velocity), oscillations, convective blue shift, etc.
+You are just assuming that you are measuring the reflex motion of a star-planet system. There are many physical processes that produce a Doppler shift besides exoplanets.}
 This quantity can be derived precisely by measuring the Doppler shift of spectral lines produced in stellar atmospheres. 
+\comment{Well, not if you have a poor measurement precision. You only get a "precise" measurement with simultaneous wavelength calibration. Again, the authors are not being very "precise" here.}
 For spectrographs that are not stabilised in temperature and pressure, the iodine technique is used, where the light of the star passes through a iodine cell before getting into the spectrograph to imprint the absorption spectrum of iodine on top of the stellar spectrum (The Hamilton spectrograph \citep{Vogt1987} at Lick Observatory, HIRES \citep{Vogt1994} on the Keck 10-m telescope, the Tull spectrograph  \citep{Tull1995}, the High Resolution Spectrograph HRS  \citep{Tull1998}).
+
 In this case, if the spectrograph shifts due to changing atmospheric conditions, the iodine and stellar spectra are shifted in the same way.
 This leads to some complications when reducing the data because one has to decorrelate the iodine spectrum from the stellar spectrum.
+\comment{This is a poorly expressed thought that is technically wrong.
+The spectrograph does not shift due to changing atmospheric conditions (earth's atmosphere?).
+It changes because of mechanical shifts (vibrations, temperature changes in spectrograph housing, changes in instrumental profile) as well as movement of the image on the slit or fiber which yes, does affect stellar and iodine lines in the same way.}
+\comment{No, you do not decorrelate (and I am not sure what the authors mean by this word) the iodine from the stellar spectrum.
+The authors show that they have no understanding how the method works.
+What is actually done is that a high-resolution iodine spectrum is combined with a spectrum of the star without iodine lines and a fit is made to the observed star+iodine spectrum.
+It is not decorrelation, but rather $\chi^2$ fitting.}
+
 For spectrographs that are stabilised, the spectrum of a calibration lamp is recorded close to the stellar spectrum on the CCD, which prevents contamination of the stellar spectrum (CORALIE \citep{Queloz-2000a}, The High Accuracy Radial Velocity Planet Searcher (HARPS) \citep{Mayor-2003}, HARPS- N \citep{Cosentino-2012}, SOPHIE \citep{Bouchy:2013aa}, CARMENES \citep{Quirrenbach:2014aa}).
 For those instruments, reducing the data is easier as the stellar spectrum is not contaminated with iodine absorption lines.
+\comment{This is not true!
+I have taken spectra with HARPS and there is cross-talk between spectra and Th-Ar particularly for strong emission lines.
+So there is some contamination.
+Furthermore, this "preventing of contamination" as the authors state has nothing to do with the spectrograph being stablized, it has to do with the simultaneous wavelength calibration using two fibers.
+In fact one reference the authors give, CORALIE, is not a stabilized spectrograph!}
+\comment{In paragraph 1 you give two lists of spectrographs.
+I presume the first one is a list spectrographs that use the iodine method, although that is not explicitly expressed.
+The authors talk about the iodine cell and then just give a parenthetical list of spectrographs.
+There is no explicit statement that these spectrographs, designed for other purposes, are all equipped with an iodine cell.
+The reader must assume this.
+Furthermore, the list is not all-inclusive.
+I can think of a dozen facilities that use iodine cells.
+So you should say, "For example" or..."to name a few"
+The second list it is for simultaneous Th-Ar calibration.
+Not all of these are "stabilized" like the authors claim.
+CORALIE, if I am not mistaken, was simultaneous Th-Ar without stabilization.
+That is why they built HARPS.
+Furthermore, all of theses spectrographs were designed for precise stellar RVs, unlike the spectrographs listed for the iodine method.}
 
@@
 The differences in flux and velocity between upflows and downflows change the Normal profile of spectral lines that become asymmetric with a "C"-shaped profile \citep[][]{Dravins-1981}.
+\comment{Regarding the C-shape of the bisector. The classic C-shape is only for late-type stars. In fact for hotter stars (F-type) it reverses.
+The strength of the asymmetry depends not just on the velocities, it is more complicated than that.
+It also depends on the flux ratio between hot cells and cool lanes, as well as the ratio of surface areas between the two.}
 The strength of the asymmetry depends on the velocity of the convection, approximatively 300\ms for the Sun, but also on the formation depth of spectral lines \citep{Gray-2009}.
@@
 This small asymmetry modifies however slightly the estimated RVs of the star, reducing the accuracy of the measurement, but if this asymmetry does not vary with time, the precision is kept.
+\comment{But the activity causes the asymmetry to change due to rotation, spot evolution, etc.
+The authors are confusing the readers here.
+They talk about a changing activity signal, but now argue that the precision is only kept if the asymmetry is constant, which it is not.
+I think what they want to say is that you measure a precise stellar radial velocity, but the activity makes its own contribution which reduces the accuracy of the RV determination for the barycentric motion due to a planet.}
 
@@
 The line asymmetry is commonly retrieved by calculating the bisector of the CCF \citep[][]{Voigt1956} and deriving the bisector curvature \citep[][]{Hatzes1996} or the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
+
 \citet{Figueira-2013} proposed different indicators, including a bi-Gaussian fitting of the CCF.
 Unfortunately, when analyzing slow rotators stars such as the Sun, due to the limited spectral resolution of the spectrographs and the limited precision in RV, it becomes difficult to measure the line asymmetry, resulting in complications for detecting very small-mass planets with the RV technique.
-
+\comment{It is the slope or span, not both. And you generally do not calculate the inverse, just the
+span. This may be correlated or inversely correlated with the RV.}
 In the procedure described above, the measurement of the RV and the FWHM is done separately from the measurement of the line asymmetry.
 All those parameters are correlated when stellar activity is dominant, and performing a step-by-step approach makes it difficult to correctly derive the errors on the different parameters retrieved.
+\comment{I simply do not understand this statement, possibly because it does not follow a standard English construction.
+You have a CCF and you measure a width and bisector span.
+This is a measurement error determined by the S/N, the resolution, and the stability of the spectrograph.
+You can determine an error in a quantity (RV and BIS).
+You can also have an uncertainty in the contribution of activity to the RV signal, but that is not a formal error.
+True errors come from photon statistics, systematic errors, instrumental errors, etc.
+You can attempt to remove the signal due to activity and that has an associated error, but that error is due to your lack of knowledge of the surface structure causing this RV and the exact value of the contribution to the RV.
+This is different from a measurement error.
+Maybe that is what you mean here, but it is not clear from what is written.}
 In addition, the Normal distribution cannot take into account the natural asymmetry of the CCF, leaving correlated noise in the residuals, which also complicates the determination of errors.
@@
 \section{The Skew Normal distribution} \label{sec:2}
+
+\comment{17) I cannot find where R, R+, x and w were defined. It is a common practice when you introduce variables in a paper, these should all be defined.
+18) Paragraph 4: "By using the so-called direct parameterization (DP) defined in Eq.
+2 problems with parameters estimation arise in the evaluation of the likelihood function in a neighborhood of $\alpha$ = 0, where the presence of a stationary point complicates the achievement of the maximum likelihood or least squares estimates."
+A poorly constructed sentence that simply confuses me! The authors are trying to say too many things in one sentence which loses the reader.
+19) To be honest, I could not follow all the mathematics. I really would have to read the referenced material, but I had little time. Maybe the details can be put in an appendix?}
 
@@
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-\section{Illustrative Examples} \label{sec:4}
+\section{Simulated data examples} \label{sec:soap}
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
+\section{Real data applications} \label{sec:4}
 
@@
 \bibliographystyle{aa}
-\bibliography{dumusque_bibliography}
-%\bibliography{mybib-SNCCF}
+%\bibliography{dumusque_bibliography}
+\bibliography{mybib-SNCCF}
 

### 2018-03-15 manuscript.tex
Added more of the referee comments

@@
 To correct for stellar activity signals, it is common to consider a linear combination of the RVs with the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case):
+\comment{Is this really common?
+I am not aware of it having wide use in the community.
+If so, references would support this.
+The authors have to distinguish what their research group and collaborators do from what the rest of the community does.}
 %
@@
 where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ is the identity matrix). 
+\comment{Is this expression just for the RV from activity alone, or the measured RV from the star (contribution of all phenomena)?
+If it is just activity, you should put a subscript otherwise the readers will be confused.
+In the text you refer to the variable ?1, but Eq.
+9 has no subscript in ?.
+You give one equation for Normal and SN, but in the text you state these variables have to be replaced by such and such when using SN, etc.
+It will be less confusing if you simply have two equations, one for Normal and one for SN and with their respective variables.}
 When the Normal fit is used, the parameter $\gamma_1$ is replaced by the BIS SPAN and SN FWHM by FWHM.
@@
 We see that the RVs measured by the SN fitting show more variations than the RVs measured by the Normal fitting.
+\comment{This is not at all clear from the figure. Is there a way to quantify this?}
 The SN fit is therefore significantly more sensitive to stellar activity. 
+\comment{How can you be sure that the higher scatter in your measurement error is not simply due to the fact that you have an inferior measurement technique?
+This can be answered by isolating the RV contribution from activity (from the asymmetry).
+Is this random (noise) or is there structure (activity).}
+\comment{If you are interested in using the RV signal due to activity to measure the rotation period, effects of activity, etc., why not just show the RVs due to the activity signal alone.?}
 This can be explained by the fact that because the SN includes an asymmetry parameter, the RV defined as the mean of the SN distribution gets more shifted in the direction of the asymmetry induced by stellar activity.
@@
 \includegraphics[height = 6in]{HD12862_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{RVs of Alpha Centauri B using a Normal and a SN fitting before and after correcting for stellar activity using Eq. \ref{eq:RV:correction}.}
+   \caption{RVs of Alpha Centauri B using a Normal and a SN fitting before and after correcting for stellar activity using Eq. \ref{eq:RV:correction}.
+ \comment{Fig 5. The differences in the results of the two methods appear negligible to me}
+   }
    \label{fig:alphacent:correctionRV}
@@
 It is interesting to see that, in this case, the slope of $0.645$ is significantly different from the one found for Alpha Centauri B in Fig.~\ref{fig:alphacent:corr.gamma}.
+\comment{Why is this interesting? You would expect it to be given that this is a different star! If something is interesting you have to point out to the reader why.}
 %
@@
 Like for Alpha Centauri B, the Pearson correlation coefficient $R^{2}$ shows  that the model we used to correct for stellar activity is a better one in the SN case than in the Normal case.
+\comment{So if I understand this correctly, SN gives higher scatter in the RV, but you make a bigger correction to the activity.
+In the end you arrive at the same answer as the Normal distribution and using Eq.
+9 .
+So why use SN?}
 %
@@
 \subsection{Tau Ceti}  \label{sec:Taucet}
-
+\comment{If you are going to refer to the star as HD 10700 you should use the same name in the section heading.}
 The analysis of the star HD10700 (i.e.
@@
 This is probably because HD10700 is at a very low activity level, similar to the Sun at its minimum activity phase.
+\comment{And how exactly do you arrive at this conclusion?
+It is ok to hypothesize that the star has a low activity level.
+But to claim it has the same activity level as the sun at solar minimum is completely unqualified and should be supported by evidence.
+This is especially true since HD 10700 is a late F-type star and thus may have a different activity behavior from a G2 star.}
 %
@@
 The RVs derived with the SN present a slightly more important rms as we can see in Fig.~\ref{fig:Tau:correctionRV}, and after correcting for stellar activity, the rms of the RV residuals are extremely similar.
+\comment{And just what is a "more important" rms compared to a less important one? The rms is a measurement of the properties of the data often with respect to a fit.}
 In Table~\ref{table:Tau:test}, we see that in the Normal and SN analysis, the intercept, the width and the asymmetry of the CCF (measured with FWHM or SN FWHM and $\gamma$ or BIS SPAN) can explain part of the RV variability measured.
@@
 Thus activity correction does not seem to be very efficient at understand the RV variation.
+\comment{Poor English. How can a correction be "efficient at understand [SIC] a variation?"
+Revised construction: "Thus the activity correction does not seem to be useful in helping us understand the RV variations."}
 This is probably because of the presence of planetary signals in the RV data \citep[][]{Mayor-2011}. 
+\comment{So there is a planetary signal in the data but you do not have an orbit that gives you a phase? Then this is not a confirmed planetary signal and thus cannot support you claim}
 Note however that the information on the orbital phase of the planets is not present in \citet{Mayor-2011} and we cannot therefore remove those signals.
@@
 The final star considered is Corot-7 which has low signal to noise. 
+\comment{A star cannot have a "low signal to noise" only data has that. And what data are you referring to photometry (from CoRoT) RVs, from HARPS? You need to be clear.}
 A total of $180$ CCFs have been analysed and Fig.~\ref{fig:Corot7:corr.gamma} shows the correlation between $\gamma$ the BIS SPAN with a linear regression slope of $0.596$.
+\comment{"Figure 9 shows the correlation between and BIS SPAN to understand the link Grammatically incorrect sentence: "Fig. 9 shows to understand"?
+You need an alternate construction: "Figure 9 shows the correlation between BIS SPAN and ?? which helps us to understand...."
+Note: there is a correlation between two quantities which is not expressed in the original text.}
 %
@@
 The RVs obtained with the SN show more variability than the RVs derived with the Normal. 
+\comment{Hasn't this been the case for virtually all the stars you looked at?}
 After correcting for stellar activity using Eq.~\ref{eq:RV:correction}, the RV residuals with both distributions are similar.
@@
 We then fit a Normal or a SN to each of these CCFs, and the standard deviation of the distribution for the mean (RV or SN RV), the width parameter (FWHM or SN FWHM) and the asymmetric parameter ($\gamma_1$ or BIS SPAN) is associated to the error on each of these parameters.
+\comment{It is not clear what you are doing here.
+I can understand bootstrapping a time series: you shuffle all the values keeping the time stamps fixed.
+How do you bootstrap a stellar spectrum?
+Do you shuffle the intensity values keeping the wavelengths fixed?
+That would produce a mess.
+Do you just add different levels of random noise?
+But the spectra already have noise in them, they are real observations.
+You need to state more clearly here what you did.}
 
@@
 However when fitting a SN to the CCF, we have RV errors that are on average 60\% greater.
+
 Thus, the RVs measured by the SN do not have the same precision than the RVs calculated using the Normal.
@@
 Therefore, the errors in $\gamma_1$ propagate to the error in the SN RVs.
-
+\comment{This seems to be the case in all your stars. I do not consider a method that delivers errors that are 60\% larger to be a very effective method.}
 Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal or the SN are equivalent to 2.35$\times$\emph{noise}.
@@
 Therefore, the SN fitting does not improve stellar activity correction when using a simple linear combination with the width and asymmetry of the CCF.
+\comment{In this statement you have basically admitted that your method is not very useful. I do not see why anyone would be compelled to use it!
+So, the bottom line is that you have introduced a method which produces similar results to the standard one.
+The only useful result of this paper is to convey to the readers that there is no significant advantage in implementing the SN method!}
 However, because the amplitude of the variations is larger in the raw SN RVs, correction techniques based on Gaussian Processes might be more efficient \citep[][]{Haywood-2014,Faria-2016a}.

### 2018-03-15 manuscript.tex
Added some comments to SN section.

@@
 \section{The Skew Normal distribution} \label{sec:2}
-
+\jessi{This section is too complicated.
+I suggest we define the skew normal in terms of the parameters that are used later, then relegate additional details, including the optimization, to an appendix section.}
 \comment{17) I cannot find where R, R+, x and w were defined. It is a common practice when you introduce variables in a paper, these should all be defined.
@@
 
-The Skew Normal (SN) distribution, introduced by \cite{Azzalini1985}, is a class of probability distributions which includes the Normal distribution as a special case.
+The Skew Normal (SN) distribution, introduced by \cite{Azzalini1985}
+\jessi{Wikipedia says this was introduced in O'Hagan and Leonard (1976), Bayes estimation subject to uncertainty about parameter constraints.
+However, it seems this may just be a 2-parameter class.
+I don't know that we need to get into the history anyway, we can just discuss the SN and reference the Azzalini paper.}
+, is a class of probability distributions which includes the Normal distribution as a special case.
 The SN distribution has, in addition to a position and a scale parameter, a third parameter which describes the asymmetry of the distribution.
@@
 %-----------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Doppler shift added to Alpha Centauri B} \label{sec:soap_real}
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
 \section{Real data applications} \label{sec:4}
+\jessi{I suggest we include one real-date application (whichever is used in \S\ref{sec:soap_real} (Alpha Centauri B?) and then add the other examples to an appendix}
 

### 2018-03-15 manuscript.tex
Added a few more comments to manuscript

@@
 % Context, Aims, Methods, Results, Conclu (not mandatory)
-{When working with radial velocities for detecting Extrasolar planets and when using data from stabilized spectrographs,
+When working with radial velocities for detecting Extrasolar planets and when using data from stabilized spectrographs,
 the different moments of the cross-correlation function (CCF) are used to measure the radial velocity of the star but also the changes in the shape of the CCF.
-Those changes are due to stellar activity and therefore the best precision on these moments is required to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.}
-{We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, provides an extra parameter to model the CCF natural asymmetry.}
-{We analyzed 5 stars with different activity levels and different signal-to-noise ratio levels.
+Those changes are due to stellar activity and therefore the best precision on these moments is required to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
+We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, provides an extra parameter to model the CCF natural asymmetry.
+We analyzed 5 stars with different activity levels and different signal-to-noise ratio levels.
 In each case, we compare the results obtained from the Normal fitting of the CCF and from the SN fitting.
-We also estimate rigorous errors for the different moments of the CCF using a bootstrap analysis.}
-{The correlations between the RVs and the CCF asymmetry or RVs and the CCF width is always stronger when using the parameters derived from the SN.
+We also estimate rigorous errors for the different moments of the CCF using a bootstrap analysis.
+The correlations between the RVs and the CCF asymmetry or RVs and the CCF width is always stronger when using the parameters derived from the SN.
 Therefore all the moments of the CCF are more sensitive to activity, which is a huge gain to probe stellar activity.
 RVs derived from a SN distribution are more sensitive to activity, which is interesting when looking for rotational periods or characterizing better stellar activity.
+\comment{" interesting" is a highly subjective and not very precise or quantitative expression.
+Interesting in what sense?
+I would term this a "sentence of no value", i.e.
+one that conveys not useful information to the reader.}
 However, once correcting the RVs from stellar activity signal using a linear combination of the CCF asymmetry and width, the RV residuals obtained from a Normal or SN fitting are very similar.
@@
 Besides all these advantages, the errors on the RVs measured by the SN are 60\% greater.
+\comment{To me this statement alone tells me that the SN method is not very useful, and not one that I would use.
+Any method that produces larger errors *before* correcting for the activity is not a very useful method.
+Why should the reader continue beyond this point?}
 This is not a problem at signal-to-noise ratio levels $>$ 150 because other noise sources dominate in this regime, however we have to be careful when deriving precise RVs for low SNR measurements.
-We also found that in the case of low SNR measurements, errors measured by bootstrap analysis can be 50\% more precise than errors measured using the derivative of the CCF.}
-{We strongly encourage the use of the SN distribution to derive the different moments of the CCF, because the derived moments probe better stellar activity signals than when using a Normal distribution.}
-
+We also found that in the case of low SNR measurements, errors measured by bootstrap analysis can be 50\% more precise than errors measured using the derivative of the CCF.
+We strongly encourage the use of the SN distribution to derive the different moments of the CCF, because the derived moments probe better stellar activity signals than when using a Normal distribution.
+\comment{You simply cannot make this claim.
+What you have shown is that the SN method produces errors that are 60\% larger than the Normal distribution and you hint that this is due to it being more sensitive to activity.
+You have not demonstrated this by looking at the "activity" signal that the SN isolates to see if it is actually more sensitive at finding rotation periods, activity cycles, etc.
+Where is the sensitivity in actually getting out useful information?
+Furthermore, after correcting the SN RVs for the activity, you arrive at the same answer as the Normal distribution method.
+I would conclude that the SN offers no real advantages over Normal so the community can continue to use the standard method.
+Grammatically this is an ambiguous statement.
+Are you looking for "better signals", i.e.
+ones that you like, or probing stellar signals in a better way?
+(This is what you meant, but not what was stated.)}
 %\keywords{techniques: radial velocities -- planetary systems -- stars: activity -- methods: data analysis}

### 2018-03-16 plots_jessi.R
added some R code for a plot

@@ -1,0 +1,18 @@
+
+
+library(sn)
+
+
+
+x <- seq(-3.25, 3.25, length.out = 1000)
+xi <- 0
+omega <- 1
+alpha <- c(-3,0, 2,6,10)
+dx <- lapply(1:length(alpha), function(ii) dsn(x, xi, omega, alpha[ii], tau=0, dp=NULL, log=FALSE))
+
+
+par.index <- c(2,1,3,4,5)
+par(mar = c(4,4,1,1), lwd = 8, cex = 2)
+plot(x, dx[[1]], "n", xlab = "Y", ylab = "Density", ylim = c(0,.8))
+temp <- sapply(1:length(alpha), function(ii) lines(x, dx[[ii]], col = par.index[ii], lty = par.index[ii]))
+legend("topleft", legend = alpha, col = par.index, lty = par.index, lwd = 5, title = expression(alpha), cex = 1.75)

### 2018-03-16 manuscript.tex
Updated some parts of the SN intro
added updated manuscript.tex

@@
 19) To be honest, I could not follow all the mathematics. I really would have to read the referenced material, but I had little time. Maybe the details can be put in an appendix?}
-
-The Skew Normal (SN) distribution, introduced by \cite{Azzalini1985}
 \jessi{Wikipedia says this was introduced in O'Hagan and Leonard (1976), Bayes estimation subject to uncertainty about parameter constraints.
@@
 I don't know that we need to get into the history anyway, we can just discuss the SN and reference the Azzalini paper.}
-, is a class of probability distributions which includes the Normal distribution as a special case.
-The SN distribution has, in addition to a position and a scale parameter, a third parameter which describes the asymmetry of the distribution.
-
-Formally the density function of the SN distribution for a random variable $Z \in \mathbb R$ is defined as:
-\begin{equation} \label{def:snd}
-SN(z; \alpha) = 2\phi(z)\Phi(\alpha z),
-\end{equation}
-where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN.
-It is possible to provide a general expression where both the location and the scale parameters are included.
-If $Z \sim SN(\alpha)$, $\xi \in \mathbb R$ and $\omega \in \mathbb R^{+}$, the density of $Y = \xi + \omega Z$ is defined as:
-
+
+The Skew Normal (SN) distribution is a class of probability distributions which includes the Normal distribution as a special case \cite{Azzalini1985}.
+The SN distribution has, in addition to a location and a scale parameter, a third parameter which describes the asymmetry, or the skewness, of the distribution.
+
+Considering a random variable $Y\in \mathbb R$ which follows a skew normal distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density can be written as
 \begin{equation} \label{def:snd_gen}
@@
 \end{equation}
-and $Y \sim SN(\xi, \omega^{2}, \alpha)$.
+where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution\footnote{A standard normal distribution is a Gaussian distribution with a mean of 0 and a standard deviation of 1.}
+ and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN.
+We then write $Y \sim SN(\xi, \omega^{2}, \alpha)$ to mean that the random variable $Y$ follows the noted SN distribution.
+Examples of SN densities under different skewness parameter values and the same location and scale parameters are displayed in Figure \ref{fig:SN.plot}.
+
+%Formally the density function of the SN distribution for a random variable $Z \in \mathbb R$ is defined as:
+%\begin{equation} \label{def:snd}
+%SN(z; \alpha) = 2\phi(z)\Phi(\alpha z),
+%\end{equation}
+%where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN.
+It is possible to provide a general expression where both the location and the scale parameters are included.
+If $Z \sim SN(\alpha)$, $\xi \in \mathbb R$ and $\omega \in \mathbb R^{+}$, the density of $Y = \xi + \omega Z$ is defined as:
+%\begin{equation} \label{def:snd_gen}
+%SN(z;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\alpha\frac{y-\xi}{\omega}\right)
+%\end{equation}
+%and $Y \sim SN(\xi, \omega^{2}, \alpha)$.
 
@@
    \centering
-\includegraphics[height = 3in]{Skew_normal_densities.pdf} 
+\includegraphics[height = 3in]{Skew_normal_densities_jjck.pdf} 
    \caption{Density function of a $SN(\alpha)$ for different choices of $\alpha$. For negative values of $\alpha$ the asymmetry will be on the left tail of the distribution.}

### 2018-03-16 manuscript.tex
sn section updates

@@
 \usepackage{amssymb}
-
+\usepackage{amsmath}
 \usepackage{natbib}
@@
 19) To be honest, I could not follow all the mathematics. I really would have to read the referenced material, but I had little time. Maybe the details can be put in an appendix?}
-\jessi{Wikipedia says this was introduced in O'Hagan and Leonard (1976), Bayes estimation subject to uncertainty about parameter constraints.
-However, it seems this may just be a 2-parameter class.
-I don't know that we need to get into the history anyway, we can just discuss the SN and reference the Azzalini paper.}
-
-The Skew Normal (SN) distribution is a class of probability distributions which includes the Normal distribution as a special case \cite{Azzalini1985}.
-The SN distribution has, in addition to a location and a scale parameter, a third parameter which describes the asymmetry, or the skewness, of the distribution.
-
-Considering a random variable $Y\in \mathbb R$ which follows a skew normal distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density can be written as
+
+The Skew Normal (SN) distribution is a class of probability distributions which includes the normal distribution as a special case \citep{Azzalini1985}.
+The SN distribution has, in addition to a location and a scale parameter analogous to the normal distribution's mean and standard deviation, a third parameter which describes the asymmetry, or the skewness, of the distribution.
+
+Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $Y = y$ can be written as
 \begin{equation} \label{def:snd_gen}
-SN(z;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\alpha\frac{y-\xi}{\omega}\right)
+SN(y;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\frac{\alpha(y-\xi)}{\omega}\right)
 \end{equation}
-where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution\footnote{A standard normal distribution is a Gaussian distribution with a mean of 0 and a standard deviation of 1.}
+where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a \emph{standard} normal distribution\footnote{A standard normal distribution is a normal distribution with a mean of 0 and a standard deviation of 1.}
  and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN.
 We then write $Y \sim SN(\xi, \omega^{2}, \alpha)$ to mean that the random variable $Y$ follows the noted SN distribution.
-Examples of SN densities under different skewness parameter values and the same location and scale parameters are displayed in Figure \ref{fig:SN.plot}.
+Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Figure \ref{fig:SN.plot}.
+A usual normal distribution is the special case of the SN distribution when the skewness parameter, $\alpha$, is equal to 0.\footnote{This can be seen from Equation~\eqref{def:snd_gen}.
+If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0)$; this is the the probability a standard normal random variable is less than or equal to 0, which is $0.5$.
+The $0.5$ cancels with the $2$ in the denominator and what remains is the usual normal density, $\frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$}
 
@@
 %and $Y \sim SN(\xi, \omega^{2}, \alpha)$.
-
-From both a mathematical and an inferential viewpoint, the SN distribution has useful properties; the details can be found in \citet{Azzalini1985}.
+%
+%From both a mathematical and an inferential viewpoint, the SN distribution has useful properties; the details can be found in \citet{Azzalini1985}.
 As previously mentioned, the Normal distribution is included in the SN family when $\alpha=0$.
@@
 \includegraphics[height = 3in]{Skew_normal_densities_jjck.pdf} 
-   \caption{Density function of a $SN(\alpha)$ for different choices of $\alpha$. For negative values of $\alpha$ the asymmetry will be on the left tail of the distribution.}
+   \caption{Density function of a random variable $Y \sim SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$, and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
+Note that the solid black line has an $\alpha = 0$ making it a normal distribution.   
+   }
    \label{fig:SN.plot}
 \end{figure}
+
+For reasons related to the interpretation of the parameters in Equation~\eqref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used, which is referred to as the \emph{centered parametrization} (CP).
 

### 2018-03-16 manuscript.tex
sn updates

@@
 The $0.5$ cancels with the $2$ in the denominator and what remains is the usual normal density, $\frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$}
-
-%Formally the density function of the SN distribution for a random variable $Z \in \mathbb R$ is defined as:
-%\begin{equation} \label{def:snd}
-%SN(z; \alpha) = 2\phi(z)\Phi(\alpha z),
-%\end{equation}
-%where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN.
-It is possible to provide a general expression where both the location and the scale parameters are included.
-If $Z \sim SN(\alpha)$, $\xi \in \mathbb R$ and $\omega \in \mathbb R^{+}$, the density of $Y = \xi + \omega Z$ is defined as:
-%\begin{equation} \label{def:snd_gen}
-%SN(z;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\alpha\frac{y-\xi}{\omega}\right)
-%\end{equation}
-%and $Y \sim SN(\xi, \omega^{2}, \alpha)$.
-%
-%From both a mathematical and an inferential viewpoint, the SN distribution has useful properties; the details can be found in \citet{Azzalini1985}.
-As previously mentioned, the Normal distribution is included in the SN family when $\alpha=0$.
-The parameter $\alpha$ provides information about the asymmetry of the curve.
-In Figure \ref{fig:SN.plot}, we plot the density function of the SN distribution for different values of $\alpha$.
-
+%
 \begin{figure}[htbp]
@@
 For reasons related to the interpretation of the parameters in Equation~\eqref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used, which is referred to as the \emph{centered parametrization} (CP).
-
-By using the so-called direct parameterization (DP) defined in Eq.
-\ref{def:snd_gen} problems with parameters estimation arise in the evaluation of the likelihood function in a neighborhood of $\alpha=0$, where the presence of a stationary point complicates the achievement of the maximum likelihood or least squares estimates.
-In order to solve this problem, \citet{Azzalini1985} proposed to pass from the direct parameterization having parameters $\xi, \omega$ and $\alpha$ to the so-called centred parameterization (CP), which is introduced below.
-
-According to Eq. \ref{def:snd_gen}, $Y = \xi + \omega Z = \mu + \sigma Z_{0} $, where $Z \sim SN(\alpha)$ and $Z_{0}$ is defined below. Hence the first two moments of $Z$ are defined simply with:
-
-\begin{eqnarray}
-\mu_{z} &=& E(Z) = b\delta, \nonumber\\
-\sigma_{z} &=& var(Z) = 1-(b\delta)^2,\nonumber
-\end{eqnarray}
-where $b=\sqrt{2/\pi}$, $\delta = \alpha / \sqrt{1+\alpha^{2}}$ and $Z_{0}$, which is the standardization of $Z$, is defined as:
-
+We will be using the CP in this work, which includes a mean parameter $\mu$, a variance parameter $\sigma^2$, and a skewness parameter $\gamma$.
+In order to define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of the one used in the Equation~\eqref{def:snd_gen} with $(\xi, \omega^2, \alpha)$ by
+%
 \begin{equation} \label{eq:snd_cp}
-Z_{0}=\frac{1}{\sigma_{z}}\left(Z-\mu_{z}\right).
+\mu = \xi + \omega \beta, \quad \sigma^{2} = \omega^{2}(1-\beta^2), \quad \gamma = \frac{1}{2}(4-\pi) \beta^{3}\left(1-\beta^2\right)^{-3/2}
 \end{equation}
+where $\beta = \sqrt{\frac{2}{\pi}\left(\frac{\alpha^2}{1+\alpha^2}\right)}$.
 
@@
 \ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution.
-In fact, as it happens in the Normal case, $\mu$ and $\sigma^2$ indicate exactly the mean and the variance of the distribution, while $\gamma$ naturally represents an index for evaluating the asymmetry of the SN, making its interpretation simpler than the one available when $\alpha$ is considered.
-In order to completely define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of the one used in the DP $(\xi, \omega^2, \alpha)$:
-%
-\begin{eqnarray} \label{eq:1}
-\mu &=& E(Y) = \xi + \omega \mu_{z}, \\
-\sigma^{2} &=& var(Y) = \omega^{2} (1-\mu_{z})^2, \nonumber\\
-\gamma &=& \frac{4-\pi}{2} \frac{\mu_{z}^{3}}{\left(1-\mu_{z}^2\right)^{3/2}}. \nonumber
-\end{eqnarray}
-
-By simple algebra, we can invert those equations to get the DP parameters as a function of the CP ones.
-%
-\begin{eqnarray} \label{eq:2}
-\xi &=& \mu - b\omega\delta, \\
-\omega &=& \frac{\sigma}{\sqrt{1 - b^2\,\delta^2}}, \nonumber\\
-\alpha &=& \frac{R}{\sqrt{b^2 - (1-b^2)\,R^2}},\,R = sign(\gamma) \left[\frac{2\,|\gamma|}{4-\pi}\right]^{\frac{1}{3}}. \nonumber
-\end{eqnarray}
-%
-The CP allows us to use the usual methods offered by the inferential theory and we will use this parameterization for the rest of the paper.
-Further details about DP, CP and statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
+In particular, $\mu$ and $\sigma^2$ are the actual mean and the variance of the distribution (rather than simply a location and scale parameter), and $\gamma$ becomes an index for evaluating the asymmetry of the SN.
+%
+Further details about the parametrization from Equation~\eqref{def:snd_gen} (called the \emph{Direct Parametrization}), the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
 

### 2018-03-16 manuscript.tex
more updates to sn section

@@
 \ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution.
+For the $\alpha$ values used in Figure~\ref{fig:SN.plot}, the corresponding values of $\mu$, $\sigma^2$, $\gamma$ are displayed in Table~\ref{tab:cp_values}.
 In particular, $\mu$ and $\sigma^2$ are the actual mean and the variance of the distribution (rather than simply a location and scale parameter), and $\gamma$ becomes an index for evaluating the asymmetry of the SN.
+The index behavior of $\gamma$ can be seen by the values displayed in Table~\ref{tab:cp_values} because the $\gamma$ values are ordered by the magnitude of the skewness of $\alpha$ rather than taking into account the direction of the skewness.
+%% Requires the booktabs if the memoir class is not being used
+\begin{table}[htbp]
+   \centering
+   %\topcaption{Table captions are better up top} % requires the topcapt package
+   \begin{tabular}{|cccc|} % Column formatting, @{} suppresses leading/trailing space
+\hline
+$\alpha$ & $\mu$ & $\sigma^2$ & $\gamma$ \\
+\hline
+ -3 	&	 0.757	&	 0.427	&	 0.881 \\
+0	&	 0.000 	&	1.000	&	 0.000 \\
+2	&	 0.714	&	 0.491	&	 0.636 \\
+6	&	 0.787	&	 0.381	&	 1.132\\
+10	&	 0.794	&	 0.370	&	 1.204\\
+\hline
+   \end{tabular}
+   \caption{CP values, $(\mu, \sigma^2, \gamma)$, corresponding to the $\alpha$ values from Figure~\ref{fig:SN.plot} (with location parameter $\xi = 0$ and scale parameter $\omega = 1$) using Equation~\eqref{eq:snd_cp}.
+Values are rounded to three decimal places.}
+   \label{tab:cp_values}
+\end{table}
 %

### 2018-03-16 plots_jessi.R

@@ -16,3 +16,9 @@ par(mar = c(4,4,1,1), lwd = 8, cex = 2)
 plot(x, dx[[1]], "n", xlab = "Y", ylab = "Density", ylim = c(0,.8))
 temp <- sapply(1:length(alpha), function(ii) lines(x, dx[[ii]], col = par.index[ii], lty = par.index[ii]))
 legend("topleft", legend = alpha, col = par.index, lty = par.index, lwd = 5, title = expression(alpha), cex = 1.75)
+
+
+beta <- function(a){sqrt(2/pi*a^2/(1+a^2))}
+mu <- xi + omega*beta
+sig2 <- omega^2*(1-beta^2)
+gamma <- function(b){0.5*(4 - pi)*b^2*(1-b^2)^(-3/2)}

### 2018-03-16 manuscript.tex
Section 2 updates

@@
 \section{The Skew Normal distribution} \label{sec:2}
-\jessi{This section is too complicated.
-I suggest we define the skew normal in terms of the parameters that are used later, then relegate additional details, including the optimization, to an appendix section.}
+\jessi{I re-wrote this section to hopefully address the referees concerns along with removing elements that are not needed}
 \comment{17) I cannot find where R, R+, x and w were defined. It is a common practice when you introduce variables in a paper, these should all be defined.
@@
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-\section{Fitting the Skew Normal distribution to the CCF} \label{sec:3}
+\subsection{Fitting the Skew Normal distribution to the CCF} \label{sec:3}
 
 %The CCF represents the average shape of spectral lines and is expressed in flux as a function of radial-velocity.
-We fit the following function to the CCF:
+The SN density shape is used to model the CCF.  In particular, the following function is fit using least-squares estimation,
 %
 \begin{eqnarray} \label{eq:3}
-\mathrm{C} - \mathrm{A} \times SN(y;\mu, \sigma^2, \gamma),
+f_{CCF}(y_i) = \mathrm{C} - \mathrm{A} \times SN(y_i;\mu, \sigma^2, \gamma), \quad i = 1, \ldots, n
 \end{eqnarray}
 %
-where C is a constant fitting the continuum of the CCF, A is an amplitude parameter and $y$ is the RV of each point of the CCF.
+where C is a constant fitting the continuum of the CCF \jessi{The C is unclear to me - can more intuition be added here?
+Are C and A considered known?}, A is an amplitude parameter, and $y_1, \ldots, y_n$ are the set of RV's considered for the CCF.
 Note that the CCF is expressed in flux as a function of the lag of the cross-correlation template, expressed in RV.
 
-We use least squares to fit the SN distribution to the CCF.
-Since each point of the CCF has a measurement error, we include this information in the specification of the SN distribution by introducing the following heteroskedastic function for the variance:
+Since each point of the CCF has a measurement error, this information is included in the specification of the SN distribution by introducing the following heteroskedastic function for the variance,
 %
 \begin{equation}
-var(Y_{i})=\sigma^{2}+\sigma_{i}^{2}, i = 1, \dots, n,
+\text{var}(Y_{i})=\sigma^{2}+\sigma_{i}^{2}, \quad i = 1, \dots, n,
 \label{eq:vaf}
@@
 %
-where n corresponds to the number of points of the CCF and $\sigma_{i}$ represents the measurement error for each available point.
+where $\sigma_{i}$ represents the measurement error for each point of the CCF.
 By using Eq.
-\ref{eq:vaf} we can interpret the parameter $\sigma^{2}$ as a measure of the pure variability present in the evaluation of the CCF.
-However, although useful for estimating correct error bars in the case where the different $\sigma_{i}$ do not include all systematic, this heteroskedastic function only consider Gaussian distributed residuals.
-As the CCF is the result of a cross correlation, we expect the residuals of a Normal or a SN fit to show some red noise.
-For this reason, we first calculated the best fit for each CCF using a Normal or a SN distribution assuming Gaussian distributed noise.
-We then subtracted the median of the residuals obtained for all CCFs before performing a second fitting round.
-The result of this procedure is illustrated in Fig.~\ref{fig:Residual.comparison}.
-We see in the lower left panel that the residuals of a simple fit of a Normal or a SN distribution are strongly correlated.
-After removing the median of the residuals, in the lower right panel, the final residuals of the SN have nearly no correlation, while the final residuals of the Normal still present a small systematic component.
-This comes from the fact that because of the asymmetric nature of the CCF (see Sec.
-\ref{intro}), the SN distribution is a more flexible model than the Normal one.
-%including the correct measurement errors in the analysis if , Eq.
-\ref{eq:vaf} assumes common variance for all the $n$ points of the CCF.
-Since the CCF is retrieved introducing different lags in the template, the latter assumption is not accurate, since unknown correlations will be produced as an effect of the procedure for retrieving the CCF.
-For this reason, in evaluating each CCF, we subtracted to each CCF its residuals, running the SN fit a second time with a ``decorrelated'' CCF as displayed in Fig.~\ref{fig:Residual.comparison}.
-
-%Looking at Fig.~\ref{fig:Residual.comparison}, also after removing the correlations due to the CCF, a clear systematic trend is visible in the residuals when a Normal distribution is fitted, suggesting how by using simply a location and a scale parameter relevant aspects of the CCF are not explained.
-The behaviour of the residuals for the SN analysis suggests that the inclusion of a skewness parameter helps for explaining the characteristics of the CCF, although a small systematic component is still present in the residuals.
-
-When using the least squares estimate for fitting the CCF with the SN distribution, we have to take into account the stationary problem in $\gamma=0$ due to the presence of the function $sign(\gamma)$ in Equation (\ref{eq:2}).
+\ref{eq:vaf} we can interpret the parameter $\sigma^{2}$ \jessi{this is going to be confusing given the CP parametrization of the SN - one needs to be changes} as a measure of the pure variability present in the evaluation of the CCF.
+However, although useful for estimating correct error bars in the case where the different $\sigma_{i}$ do not include all systematics, this heteroskedastic function only considers Gaussian distributed residuals.
+\jessi{the previous statement is unclear}
+%
+
+The CCF is the result of a cross correlation so the residuals of a normal or a SN fit are expected to show correlated noise.
+To investigate this issue, we considered example CCFs from the star Tau Ceti.
+The CCFs were modeled using a normal or a SN shape, and assuming independent normally-distributed noise around the modeled shape.
+%
+We then subtracted the median of the residuals (the original data minus the fit function) obtained for all CCFs before performing a second round of fitting.
+The result of this procedure is illustrated in Figure~\ref{fig:Residual.comparison}.
+The lower left panel displays the residuals of a simple fit of a normal or a SN distribution, which appear to be strongly correlated.
+%
+After removing the median of the residuals, in the lower right panel, the final residuals of the SN procedure have almost no apparent correlation, while the final residuals of the normal procedure still present a small systematic component.
+This seems to be due to the asymmetric nature of the CCF (see Section~\ref{intro}), which is not captured in a symmetric distribution like the normal distribution.
+This exercise highlights that the SN density shape better captures the shape of a CCF compared to a normal density shape.
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 6in]{[1]Plot_Fitting_and_Residuals_2run.pdf} 
+   \caption{Comparison between the normal and the SN procedures for modeling a collection of CCFs for the star Tau Ceti.
+Two stages of modeling are carried out with the first stage results displayed in the left column and the second stage in the right column.
+   The first run corresponds to fitting a normal or a SN shape to the raw CCF.
+The second run corresponds to fitting the same shape to the CCF after removing the median of all the residuals obtained in the first run.
+The SN residuals of the second run present minimal correlations, whereas the normal residuals present still a clear systematic component.}
+   \label{fig:Residual.comparison}
+\end{figure*}
+%When using the least squares estimate for fitting the CCF with the SN distribution, we have to take into account the stationary problem in $\gamma=0$ due to the presence of the function $sign(\gamma)$ in Equation (\ref{eq:2}).
 Depending on the initial values of the numerical minimization for the least squares estimate of $\gamma$, the presence of this stationary point when evaluating $\gamma$ can lead to an incorrect estimation of the asymmetry parameter of the SN.
@@
 
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{[1]Plot_Fitting_and_Residuals_2run.pdf} 
-   \caption{Comparison between the Normal and the Skew Normal fit for a particular CCF for the star Tau Ceti.
-The first run corresponds to fitting a Normal or a SN to the raw CCF.
-The second run corresponds to fitting the same function to the CCF after removing the median of all the residuals obtained in the first run.
-The SN residuals of the second run present a tiny correlation, whereas the Normal residuals present still a clear systematic component.}
-   \label{fig:Residual.comparison}
-\end{figure*}
-
-In the following of the paper, we define the RV as the mean of the Normal or the mean of the SN (defined as SN RV).
+In the following of the paper, we define the RV as the mean of the normal or the mean of the SN (defined as SN RV).
 For the width of the CCF, we use the FWHM of the Normal, defined as $2\sqrt(2\ln2)\sigma$.
-The width of the SN, SN FWHM, is defined in the same way\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum linke in the Normal case.}.
-In the Normal case, it is not possible to retrieve an asymmetric parameter and therefore we use BIS SPAN.
+The width of the SN, SN FWHM, is defined in the same way\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the normal case.}.
+In the normal case, it is not possible to retrieve an asymmetric parameter and therefore we use BIS SPAN.
 This will be compared to the asymmetric parameter $\gamma_1$ of the SN.

### 2018-03-16 plots_jessi.R
code update to include CP computations

@@ -18,7 +18,14 @@ temp <- sapply(1:length(alpha), function(ii) lines(x, dx[[ii]], col = par.index[
 legend("topleft", legend = alpha, col = par.index, lty = par.index, lwd = 5, title = expression(alpha), cex = 1.75)
 
 
-beta <- function(a){sqrt(2/pi*a^2/(1+a^2))}
+fbeta <- function(a){sqrt(2/pi*a^2/(1+a^2))}
+fgamma <- function(b){0.5*(4 - pi)*b^2*(1-b^2)^(-3/2)}
+beta <- fbeta(alpha)
+gamma <- fgamma(beta)
 mu <- xi + omega*beta
 sig2 <- omega^2*(1-beta^2)
-gamma <- function(b){0.5*(4 - pi)*b^2*(1-b^2)^(-3/2)}
+
+round(cbind(alpha, mu, sig2, gamma),3)
+
+
+

### 2018-03-16 plots_jessi.R
fixed issue in sn table

@@ -18,7 +18,7 @@ temp <- sapply(1:length(alpha), function(ii) lines(x, dx[[ii]], col = par.index[
 legend("topleft", legend = alpha, col = par.index, lty = par.index, lwd = 5, title = expression(alpha), cex = 1.75)
 
 
-fbeta <- function(a){sqrt(2/pi*a^2/(1+a^2))}
+fbeta <- function(a){sqrt(2/pi)*a/sqrt(1+a^2)}
 fgamma <- function(b){0.5*(4 - pi)*b^2*(1-b^2)^(-3/2)}
 beta <- fbeta(alpha)
 gamma <- fgamma(beta)

### 2018-03-16 manuscript.tex
fixed issue in sn table
fixed some issues

@@
 \newcommand{\comment}[1]{{\color{red}[[\textbf{Referee: }#1]]}}
+\newcommand{\todo}[1]{{\color{cyan}[[\textbf{TODO: }#1]]}}
 
@@
 \label{intro}
+\jessi{I added subsections here for our reference to make sure the bases are covered, but we should remove them before submission.}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Goal of RV analysis}
 The radial velocity (RV) of a star is defined to be the velocity of the center of mass of the star along our line of sight. 
@@
 For spectrographs that are not stabilised in temperature and pressure, the iodine technique is used, where the light of the star passes through a iodine cell before getting into the spectrograph to imprint the absorption spectrum of iodine on top of the stellar spectrum (The Hamilton spectrograph \citep{Vogt1987} at Lick Observatory, HIRES \citep{Vogt1994} on the Keck 10-m telescope, the Tull spectrograph  \citep{Tull1995}, the High Resolution Spectrograph HRS  \citep{Tull1998}).
-
+\jessi{we should mention the new spectrographs like EXPRES}
 In this case, if the spectrograph shifts due to changing atmospheric conditions, the iodine and stellar spectra are shifted in the same way.
@@
 
-For spectrographs that are stabilised, the spectrum of a calibration lamp is recorded close to the stellar spectrum on the CCD, which prevents contamination of the stellar spectrum (CORALIE \citep{Queloz-2000a}, The High Accuracy Radial Velocity Planet Searcher (HARPS) \citep{Mayor-2003}, HARPS- N \citep{Cosentino-2012}, SOPHIE \citep{Bouchy:2013aa}, CARMENES \citep{Quirrenbach:2014aa}).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Stellar activity effect on CCF, normal fit plus FWHM indicator}
+\jessi{Eventually three methods are introduced for detecting CCF asymmetry:  FWHM, bisector span, and the Figueira approach - it seems that these methods need to be better explained.
+Somewhere in the intro it needs to become clear that we are (i) providing a new way of measuring CCF asymmetry, (ii) this is a unified approach that also provides an RV estimate, and (iii) it (hopefully) provides a better indicator.}
+For spectrographs that are stabilized, the spectrum of a calibration lamp is recorded close to the stellar spectrum on the CCD, which prevents contamination of the stellar spectrum (CORALIE \citep{Queloz-2000a}, The High Accuracy Radial Velocity Planet Searcher (HARPS) \citep{Mayor-2003}, HARPS- N \citep{Cosentino-2012}, SOPHIE \citep{Bouchy:2013aa}, CARMENES \citep{Quirrenbach:2014aa}).
 For those instruments, reducing the data is easier as the stellar spectrum is not contaminated with iodine absorption lines.
@@
 
-For stabilized spectrographs, the RV is derived by first correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}, which gives an average line profile, generally called Cross Correlation Function (CCF).
-Then a Normal distribution is fitted to this average profile to get the mean, namely the RV, and the full width at half maximum (FWHM) of the profile.
-The CCF technique allows for an averaging out of the RV information of thousands of lines and therefore reach a very high signal-to-noise ratio (SNR), which is essential for a good RV precision.
+For stabilized spectrographs, the RV is derived by first correlating a stellar spectrum at a particular time with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}, which gives an average line profile, generally called Cross Correlation Function (CCF).
+The CCF is a function of RV, and the RV corresponding to the minimum of the CCF is the estimated RV for that spectrum.
+However, this would give a noisy estimate so first a normal density shape is fitted to the CCF, and then the estimated mean of the normal density is used as the estimate of the RV.
+The full width at half maximum (FWHM) of the normal fit is also used as an indicator of spectral line asymmetry.
+The CCF technique allows for an averaging of thousands of spectral lines and can therefore reach a very high signal-to-noise ratio (SNR), which is essential for a good RV precision.
 
@@
 The strength of the asymmetry depends on the velocity of the convection, approximatively 300\ms for the Sun, but also on the formation depth of spectral lines \citep{Gray-2009}.
-Since the CCF is an average of all the spectral lines, some strongly asymmetric and some not, its asymmetry is rather small, which is why a Normal distribution is a proper model to fit the CCF.
+Since the CCF is an average of all the spectral lines, some strongly asymmetric and some not, its asymmetry is rather small, which is why a normal distribution can be an appropriate model for the CCF.
 This small asymmetry modifies however slightly the estimated RVs of the star, reducing the accuracy of the measurement, but if this asymmetry does not vary with time, the precision is kept.
@@
 
-Stellar activity induces RV variations by a modification of the spectral line asymmetry, while an orbiting companion only induces a pure Doppler shift on spectral lines without modifying their shape.
-Therefore, assuming that there is no instrumental systematics, stellar activity will induce a variation in line asymmetry or FWHM of the CCF.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Bisector span indicators of stellar activity}
+\jessi{Its seems that more details should be added here}
+Stellar activity can induce RV variations by a modification of the spectral line asymmetry, while any orbiting companions would induce a pure Doppler shift on \emph{all} spectral lines without modifying their shape.
+Therefore, assuming that there is no instrumental systematics, stellar activity generally induces a variation in line asymmetry that can be observed in the  FWHM of the CCF. 
 The line asymmetry is commonly retrieved by calculating the bisector of the CCF \citep[][]{Voigt1956} and deriving the bisector curvature \citep[][]{Hatzes1996} or the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
-
-\citet{Figueira-2013} proposed different indicators, including a bi-Gaussian fitting of the CCF.
-Unfortunately, when analyzing slow rotators stars such as the Sun, due to the limited spectral resolution of the spectrographs and the limited precision in RV, it becomes difficult to measure the line asymmetry, resulting in complications for detecting very small-mass planets with the RV technique.
 \comment{It is the slope or span, not both. And you generally do not calculate the inverse, just the
 span. This may be correlated or inversely correlated with the RV.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Figueira indicators of stellar activity}
+\citet{Figueira-2013} proposed different indicators, including a bi-Gaussian fitting of the CCF \jessi{this needs to be better explained}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Issues with detecting stellar activity}
+Unfortunately, when analyzing slow rotators stars such as the Sun, due to the limited spectral resolution of the spectrographs and the limited precision in RV, it becomes difficult to measure the line asymmetry, resulting in complications for detecting very small-mass planets with the RV technique.
 In the procedure described above, the measurement of the RV and the FWHM is done separately from the measurement of the line asymmetry.
@@
 Maybe that is what you mean here, but it is not clear from what is written.}
-In addition, the Normal distribution cannot take into account the natural asymmetry of the CCF, leaving correlated noise in the residuals, which also complicates the determination of errors.
+In addition, the normal distribution cannot take into account the natural asymmetry of the CCF, leaving correlated noise in the residuals, which also complicates the determination of errors.
 We propose to overcome these problems by fitting a SN (SN) distribution to the CCF, which naturally includes a skewness parameter \citep[][]{Azzalini1985}.
 
-The paper is organized as follow.
-In Sec.~\ref{sec:2} we introduce the SN distribution and motivate its use for fitting the CCF.
-In Sec.~\ref{sec:3} we show that the SN distribution is a better representation of observed CCF and we study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Outline of paper}
+\todo{This paragraph will need to be updated once the rest is finished.} The paper is organized as follow.
+In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  show that the SN density is a better representation of observed CCF than a normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
 In Sec.~\ref{sec:31} we present a simple model to correct for stellar activity.
@@
 In Sec.~\ref{sec:5} we derive error bars for the different CCF parameters, and finally we discuss our results and conclude in Sec.~\ref{sec:discu} and Sec.~\ref{sec:conclu}.
-
-%When the observed RV for each spectrum is computed by using the cross-correlation function (CCF) technique, the determination of the radial velocity of the star has operatively done by measuring the Doppler shift of spectral lines produced in the stellar atmosphere.
-Doppler measurements are obtained combining each spectrum with a mask template (a very common choice is a binary template, which is a sum of $\delta$-function profiles corresponding to 1 for the line wavelength, with a base of two (spectral) points, and 0 elsewhere \citep{Fiorenzano2005}).
-The computation of the radial velocity of the star for each spectrum with the CCF technique involves the evaluation of the correlation among thousands of spectral lines and the CCF function represents a mean spectral-line profile of all of the lines selected by the template.
-The radial velocity of the star for a particular spectrum is obtained by fitting the spectral-line profile with a proper probability distribution, usually the normal one (even if a well approximation is given also by using a Voigt function).
-The radial velocity is finally the mean of the fitted curve.
-
-%By using the CCF technique, if changes occur in the spectral-line profiles of the star, the measured Doppler shifts may not correspond precisely to the velocity of the center of mass of the star (which is a common situation for pulsating stars with very active atmosphere).
-This behavior can be explained by the presence of active regions such as spots and faculae on the surface of the star \citep{Saar1997, Hatzes2002, Kurster2003}.
-To interpret the observed radial-velocity variations as true changes in the velocity of the star, it is necessary to show how the observed variations do not stem from changes in the stellar atmosphere.
-It is worthy of mention the fact that the radial velocity measurements are affected by changes of the profile line if its changes in a particular spectrum affect all of the spectral lines in a similar way.
-
-%A first indicator derived by the CCF is the the full width at half-maximum of the CCF (FWHM) by\cite{Desort2007}.
-Since the FWHM is determined by the stellar rotation rate, fast rotating stars tend to be more active.
-The FWHM changes if a spot or a faculae region is present, in order to conserve the area enclosed by the line profile.
-This indicator has been used by \cite{Queloz2009} and \cite{Hatzes2010}.
-%
-%A more sophisticated indicator which provides the general asymmetry of the lines of a spectrum is line bisector, first introduced by \cite{Voigt1956}.
-The line bisector of an absorption line is defined as the middle point of the horizontal segment connecting points on the left and right sides of the profile with the same flux level.
-The line bisector is hence obtained by combining bisector points ranging from the core toward the wings of the line.
-Any correlation between radial velocity changes and line bisector orientation provides an element which disqualifies the interpretation of the observed radial-velocity variations as true changes in the velocity of the star.
-Generally speaking if the radial velocity variations are due to changes by its center of mass, the bisectors would oscillate to the left and right of the mean bisector with no change in shape or orientation.
-To the calculation of the asymmetry of the spectral lines the bisector velocity span \cite{Toner1988} is usually retrieved by considering a top zone near the wings and a bottom zone close to the core of the lines.
-The difference of the average values of velocities in the top and bottom zones, $V_{T}$ and $V_{B}$ respectively, determine the bisector velocity span (BVS).
-This is actually a measurement of the inverse of the mean slope of the bisector.
-According to \cite{Gray1989}, to establish the error for the bisector velocity span, the following expression is used:
-%
-%\begin{equation}
-%\delta V = \left(\frac{S}{N}\right)^{-1} \left(2nF \frac{\Delta F}{x} \frac{dF}{dV} \right)^{-1/2},
-%\label{eq:gray}
-%\end{equation}
-%where $S/N$ is the signal-to-noise of the spectrum, $n$ is the number of lines in the mask for the CCF, $F$ is the central flux of the zone of analysis, $\Delta F$ is the interval of flux determining the zone, $x$ is the scale of the spectrum based on the linear dispersion of the instrument and finally $dF/dV$ gives the slope of the profile in the zone being analyzed.
-%
-%Other quantities derived by the bisector are the curvature of the line bisector \citep{Hatzes1996}, the bisector inverse slope \citep{Queloz2001} and the bi-Gaussian cross-correlation function \cite{Figueira2013}.
-According to Desort et al.
-(2007), the FWHM, the BIS and photometric variations are not sufficient for providing enough information for slowly rotating stars (as for instance the Sun).
-When this is the case, to disentangle stellar activity from the Doppler effect caused by a ``Earth-like'' is not possible with the already known instruments.
-
-%The procedure to retrieve the RV by fitting with a normal distribution the CCF and then calculating its first moment and the line bisector present a number of disadvantages.
-First of all the two procedures for recovering respectively the radial velocity of the star and evaluating the general asymmetry of the lines of the spectrum have done separately, whereas an eventual asymmetry of the spectral-line profile has an impact on the evaluation of the mean of the fitted curve.
-We note that by fitting the spectral-line profile with a symmetric distribution as the normal one, there is no way to access in one step an evaluation for both the radial velocity of the star and an indication of the stellar activity.
-Secondly, cause the way the line bisector is obtained, beyond the measurement errors coming from the observation of the star a further error according to (\ref{eq:gray}) has to be considered.
-For these two reasons we propose the evaluation of the CCF with a straightforward 1 step analysis, based on the implementation of the Skew Normal distribution, which eliminates both the disadvantages of the classic approach, providing moreover in a natural way an evaluation of the asymmetry caused by the stellar activity.
-%
-%The paper is organized as follow.
-In Section $2$ the Skew Normal distribution is introduced, motivating its use for fitting the CCF.
-Section $3$ is dedicated to real case studies where an evaluation between the common analysis and the proposed one has done.
-Concluding remarks are presented in Section $4$.
 
@@
 \end{equation}
-where $\beta = \sqrt{\frac{2}{\pi}\left(\frac{\alpha^2}{1+\alpha^2}\right)}$.
+where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$.
 
@@
 In particular, $\mu$ and $\sigma^2$ are the actual mean and the variance of the distribution (rather than simply a location and scale parameter), and $\gamma$ becomes an index for evaluating the asymmetry of the SN.
-The index behavior of $\gamma$ can be seen by the values displayed in Table~\ref{tab:cp_values} because the $\gamma$ values are ordered by the magnitude of the skewness of $\alpha$ rather than taking into account the direction of the skewness.
 %% Requires the booktabs if the memoir class is not being used
@@
 \hline
- -3 	&	 0.757	&	 0.427	&	 0.881 \\
+ -3 	&	 -0.757	&	 0.427	&	 -0.667 \\
 0	&	 0.000 	&	1.000	&	 0.000 \\
-2	&	 0.714	&	 0.491	&	 0.636 \\
-6	&	 0.787	&	 0.381	&	 1.132\\
-10	&	 0.794	&	 0.370	&	 1.204\\
+2	&	 0.714	&	 0.491	&	 0.454\\
+6	&	 0.787	&	 0.381	&	 0.891\\
+10	&	 0.794	&	 0.370	&	 0.956\\
 \hline
@@
 \end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Estimation of standard errors for the CCF parameters} \label{sec:5}
+
+The HARPS reduction pipeline gives the pure photon-noise error estimate on the RVs.
+This error, called \emph{noise}, is not derived from the Normal fit to the CCF but from the method described in \citet{Bouchy-2001b} using the CCF derivative.
+Then \emph{noise} is associated to the RV error, $2\times$\emph{noise} to the BIS SPAN error and $2.35\times$\emph{noise} to the FWHM error.
+
+In this section, we do a bootstrap analysis to measure the standard errors on the RVs or SN RVs, the FWHM or SN FWHM, and BIS SPAN or $\gamma_1$.
+Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
+Therefore, we cannot do a bootstrap analysis on perturbing independently each CCF point with a Gaussian distribution scaled to the error of each given point.
+To bypass this problem, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF.
+We then fit a Normal or a SN to each of these CCFs, and the standard deviation of the distribution for the mean (RV or SN RV), the width parameter (FWHM or SN FWHM) and the asymmetric parameter ($\gamma_1$ or BIS SPAN) is associated to the error on each of these parameters.
+\comment{It is not clear what you are doing here.
+I can understand bootstrapping a time series: you shuffle all the values keeping the time stamps fixed.
+How do you bootstrap a stellar spectrum?
+Do you shuffle the intensity values keeping the wavelengths fixed?
+That would produce a mess.
+Do you just add different levels of random noise?
+But the spectra already have noise in them, they are real observations.
+You need to state more clearly here what you did.}
+
+In the top plots of Fig.~\ref{fig:se} we show the different errors for the RVs, the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels.
+The parameter SN50 corresponds to the SNR in order 50, which corresponds to a wavelength of 550\,nm.
+In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN or the Normal and the \emph{noise} parameter extracted from the HARPS reduction pipeline.
+We first see that the errors on the CCF parameters only depends on the SNR and do not depend on the spectral type.
+This is true if the spectral type are not too different though, like here where we show the results for G and K dwarfs.
+
+We see that for the RV errors, the ratio between the \emph{noise} parameter and the the RV error measured by the bootstrap using the Normal fitting is around 1, meaning that those two estimates of the RV errors are similar.
+However when fitting a SN to the CCF, we have RV errors that are on average 60\% greater.
+
+Thus, the RVs measured by the SN do not have the same precision than the RVs calculated using the Normal.
+This can be explained by the fact that in the case of the SN, variations in the asymmetry parameter $\gamma_1$ induce variations in the SN RV measured due to the strong correlation between those two parameters.
+Therefore, the errors in $\gamma_1$ propagate to the error in the SN RVs.
+\comment{This seems to be the case in all your stars. I do not consider a method that delivers errors that are 60\% larger to be a very effective method.}
+Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal or the SN are equivalent to 2.35$\times$\emph{noise}.
+Therefore, the precision in CCF width is the same if we fit a Normal or a SN to the CCF.
+
+Finally, for the errors in CCF asymmetry, we see that the bootstrap analysis using the Normal fitting gives the same precision as using 2$\times$\emph{noise}, which is the common errors used for BIS SPAN.
+However, when fitting the SN to the CCF, the asymmetry errors are 15\% smaller.
+Therefore, the SN fit gives a better precision in CCF asymmetry than what can be reached using BIS SPAN.
+
+Another interesting point is the behavior of the ratio of the bootstrap errors over the \emph{noise} parameter as a function of SNR (see bottom plots in Fig.~\ref{fig:se} for the RVs, CCF width and CCF asymmetry).
+We see that at low SNR, the bootstrap analysis gives a better precision, which can be explained by the fact that the \emph{noise} parameter is estimated using the CCF derivative.
+Calculating the derivative of the CCF increases the noise and therefore explain this behavior at low SNR.
+For SNR below 200, the bootstrap analysis gives a better precision than the \emph{noise} parameter.
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
+   \caption{Comparison between the standard errors using the bootstrap analysis and the parameter $noise$ for the RVs, $2.35\times$\emph{noise} for the width, and $2\times$\emph{noise} for the asymmetry parameter.
+Note that for the asymmetry, the error in BIS SPAN is in \kms.
+To be able to compare the errors in $\gamma_1$ and BIS SPAN, we multiplied the error in $\gamma_1$ by the slope of the correlation between $\gamma_1$ and BIS SPAN.}
+   \label{fig:se}
+\end{figure*}
+
+%, using the spectrum derivative
+%, the pure photon-noise error on RV measured 
+%Together with the pointwise estimates, retrieving the standard errors for the RVs of the star, $\gamma$ and the FWHM provides information about the uncertainties associated to each parameter.
+Since the procedure for retrieving the RVs of the star consists in fitting with a density function a CCF, getting the standard errors for all the parameter of interests cannot be done by using the common asymptotic theory.
+The implementation of a standard bootstrap analysis cannot as well be done, because the points of the CCF are highly correlated.
+In the analysis of the present work, in order to get the standard errors for the parameters of interest for a particular CCF, we moved each point of this CCF according to its measurement errors, producing $100$ simulated CCFs from the original one.
+Then we run both the Normal and the SN analyses on these simulated CCFs, letting us to retrieve an evaluation of the standard errors.
+This operation has been repeated for all the CCFs available for the analyzed stars.
+The comparison between the standard errors retrieved in this way with the classic noise parameter, {\color{red} obtained by using the Gray's equation cit.
+Gray (1983)} are presented in Figure \ref{fig:se}.
+{\color{red} Xavier: Is it correct how the noise parameter is obtained?
+Or it is simply $\sqrt(photons)$?}
+
+%Given the strong correlation between the $\gamma$ parameter of the SN and its mean, the standard errors are larger respect the Normal fitting analysis.
+This fact confirms how correcting the RVs for stellar activity using Eq.
+\ref{eq:RV:correction} is more helpful when using the SN fitting.
+The standard errors for the FWHM are comparable for both the SN and the Normal analyses, whereas an improvement is clearly measurable for the standard errors associated to the asymmetry indicators.
+The last plot in Fig.~\ref{fig:se} shows that the standard errors for $\gamma$ are $10 \%$ smaller than the ones retrieved for the BIS SPAN.
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
+\section{Discussion} \label{sec:discu}
+
+An analysis of the CCF residuals after fitting a Normal or SN distribution show that the SN is a better model to explain the shape of the CCF.
+This comes from the fact that CCFs present a natural asymmetry due the convective blueshift.
+
+We compared for five stars the difference between the RVs, FWHM and asymmetry (BIS SPAN in the Normal case and parameter $\gamma_1$ in the SN case) as measured we a Normal or a SN fitting to the CCF.
+The $\gamma_1$ parameter is linearly dependant on the BIS SPAN, with always a strong correlation coefficient.
+%To compare $\gamma_1$, that do not have any units, with BIS SPAN expressed in \kms, one has simply to multiply $\gamma_1$ by the slope of the linear dependence between $\gamma_1$ and BIS SPAN. 
+The slope of this linear correlation change depending on the star studied. This is probably because the spectral type is different, therefore the effects from stellar activity are different.
+
+When comparing the RV as measured by the Normal and the SN fitting, we always see that the rms of the latter is larger.
+Thus fitting the SN to the CCF gives RV measurements that are more sensitive to activity.
+This comes from the fact the the asymmetry parameter of the SN will modify as well the mean of the distribution, thus the RV.
+This is a positive point as it is easier to correct for a signal that is at a high SNR rather that a signal that is at a SNR of one, which is generally the case for the low-activity stars that are followed for RV surveys.
+
+The RVs derived using the SN fitting present a higher sensitivity to stellar activity.
+However, once correcting the RVs from stellar activity using a linear combination of the width and asymmetry parameter of the CCF (FWHM and BIS SPAN in the Normal case, and SN FWHM and $\gamma_1$ in the SN case), the RV residuals in both the Normal and SN case show similar scatter.
+Therefore, the SN fitting does not improve stellar activity correction when using a simple linear combination with the width and asymmetry of the CCF.
+\comment{In this statement you have basically admitted that your method is not very useful. I do not see why anyone would be compelled to use it!
+So, the bottom line is that you have introduced a method which produces similar results to the standard one.
+The only useful result of this paper is to convey to the readers that there is no significant advantage in implementing the SN method!}
+However, because the amplitude of the variations is larger in the raw SN RVs, correction techniques based on Gaussian Processes might be more efficient \citep[][]{Haywood-2014,Faria-2016a}.
+
+When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma_1$ in the SN case) with respect to the RVs (RVs in the Normal case or SN RVs in the SN case), we observe that the correlations are always stronger for the parameters of the SN.
+Therefore, the SN parameters are more sensitive to activity.
+In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of 0.57 between $\gamma_1$ and SN RV, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.21.
+
+We also studied the behavior of the noise on the different parameters of the Normal and the SN as a function of SNR.
+By performing a bootstrap analysis, we confirmed that in the case of the Normal, using the \emph{noise} parameter as returned by the HARPS pipeline gives a correct estimate of the errors measured on the RVs, FWHM and BIS SPAN for SNR $>150$.
+For the RVs, the errors are equivalent to \emph{noise}, for the FWHM to 2.35$\times$\emph{noise} and for the BIS SPAN to 2$\times$\emph{noise}.
+For lower SNR though, the bootstrap analysis gives better results, and this comes from the fact the the \emph{noise} parameter is estimated using the derivative of the CCF, which increase the noise \citep[][]{Bouchy-2001b}.
+For very low SNR, the improvement of the bootstrap analysis can be as high as 50\%.
+Therefore, although taking much more time, we encourage the use of bootstrapping when calculating errors for the different parameters of the CCF.
+
+In the case of the errors when using the SN fitting, the precision on the SN RVs is however 60\% worse than for the RVs.
+This comes from the fact that because the asymmetry is accounted for in the SN and because the SN RVs and $\gamma_1$ are strongly correlated, the errors in $\gamma_1$ propagates to the errors in SN RVs.
+This is not so important for SNR $>$ 150 for which the errors are below the \ms precision of HARPS and the \ms variation induced by stellar activity signals even in low activity cases \footnote{As we can see in papers publishing HARPS results using an additional jitter to consider stellar activity noise not accounted for in the \emph{noise} parameter, the extra jitter is always greater than 0.8\ms \citep[e.g.][]{Diaz:2016ab}.}.
+These larger errors in RVs can be a problem for low SNR measurements.
+In the case of the CCF width, the error derived when using the Normal or SN fitting are very similar.
+Finally for the asymetry, we see that the error in $\gamma_1$ is $\sim$15\% smaller than the error in BIS SPAN.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion} \label{sec:conclu}
+
+In this paper we introduced a novel approach based on the Skew Normal (SN) distribution for deriving RVs and shape variations in the CCF of stars.
+When searching for small-mass exoplanets using the RV technique, it is essential to understand the shape variation of the CCF, which is a proxy for stellar activity effects.
+The standard approach consist in first to adjust a Normal distribution to the CCF to get the RV and FWHM, defined as the mean and the FWHM of the Normal distribution, and then to measure the asymmetry by calculating BIS SPAN.
+FWHM and BIS SPAN give us information on the line shape that are used to probe stellar activity signals.
+In this paper we demonstrate that by using the SN distribution to fit CCFs, we can measure simultaneously the RV of the star with the width and asymmetry of the CCF.
+
+Using the SN to fit CCFs brings a significant improvement in probing stellar activity.
+The correlations between SN RV and SN FWHM, and SN RV and the asymmetric parameter $\gamma_1$ are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
+The RVs derived by the SN are also more sensitive to activity and the precision on the asymmetry measured by $\gamma_1$ is greater than the one on BIS SPAN by $\sim$15\%.
+Therefore when searching for rotational periods in the data, or applying Gaussian Processes to account for stellar activity signals, the SN parameters should be used.
+
+At first glance, one downside of using the SN comes from the RV errors that are greater by 60\% relative to the RV errors measured when considering a Normal.
+This is due to the strong correlation between SN RV and $\gamma_1$ and this can be a problem for low SNR measurements.
+However, in the regime of SNR $>$ 150, which is the aim of all RV surveys at high precision, the precision of the SN RVs is below the \ms, which is thus below the instrumental precision of HARPS and below the RV perturbations induced by stellar activity.
+
+Finally, we also encourage the use of bootstrapping to estimate more realistic errors on the different parameters of the Normal or SN fitted to the CCF, mainly in the low SNR regime where a gain of 50\% can be reached.
+This takes significantly more time, but note that 100 realization are enough to get a good estimation of errors.
+
+%the RVs of the star can be calculated as the mean of the SN, whereas its asymmetry parameter $\gamma$ can be naturally used for retrieving information about the asymmetry of the CCF.
+Because of the natural correlation between the RVs and the asymmetry parameter, a linear combination of both $\gamma$ and the FWHM has been implemented for correcting the RVs from stellar activity, allowing us to retrieve a more precise RVs.
+
+%In order to get the standard errors for the estimated parameters, rather than using the common $noise$ statistic, we created a simulated procedure based on perturbing each point of the CCF according to its measurement error.
+Then, by getting from the original profile line $100$ simulated profiles, we run the SN fitting analyses, allowing us retrieving for all the parameter of interests an estimation for their standard errors.
+Concerning the standard error associated to the means of the distributions, the SN fit leads to slightly larger standard errors respect when running the Normal fit.
+This fact can be explained by noticing that as a simulated CCF is created according to the procedure described above, we expect slightly differences on the asymmetry of the CCF as well.
+The natural correlation between the RVs of the star and $\gamma$, where the mean of the SN is shifted in the direction of the asymmetry of the distribution, leads to larger uncertainties related to the RVs of the star.
+The latter consideration provides a further justification for correcting the RVs of the star from stellar activity and explains why this correction is more helpful when running the proposed analysis rather than the classic Normal fit.
+Concerning the standard errors related to the asymmetry parameters, when using the SN fit the uncertainties are $10 \%$ smaller than using the classic BIS SPAN.
+In conclusion, we showed how using the SN fit provides in an unique step a better understanding of the stellar activity through using the asymmetry parameter $\gamma$ rather than using the common statistics such as the BIS SPAN or other indicators.
+On top of that, when focusing on low signal to noise cases, the SN procedure showed how statistically significant results are retrieved with the proposed approach in terms of correlation between the asymmetry of the profile line and the RVs, whereas for the previous analyses this correlation does not result statistically significant.
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
+\section{Acknowledgements}
+
+We are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
+XD is grateful to the Society in Science--The Branco Weiss Fellowship for its financial support.
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
+%\section{Appendix}
+\appendix
+\section{Appendix}
+
+\jessi{Add intro to appendix}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Estimation of standard errors for the CCF parameters} \label{sec:5}
-
-The HARPS reduction pipeline gives the pure photon-noise error estimate on the RVs.
-This error, called \emph{noise}, is not derived from the Normal fit to the CCF but from the method described in \citet{Bouchy-2001b} using the CCF derivative.
-Then \emph{noise} is associated to the RV error, $2\times$\emph{noise} to the BIS SPAN error and $2.35\times$\emph{noise} to the FWHM error.
-
-In this section, we do a bootstrap analysis to measure the standard errors on the RVs or SN RVs, the FWHM or SN FWHM, and BIS SPAN or $\gamma_1$.
-Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
-Therefore, we cannot do a bootstrap analysis on perturbing independently each CCF point with a Gaussian distribution scaled to the error of each given point.
-To bypass this problem, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF.
-We then fit a Normal or a SN to each of these CCFs, and the standard deviation of the distribution for the mean (RV or SN RV), the width parameter (FWHM or SN FWHM) and the asymmetric parameter ($\gamma_1$ or BIS SPAN) is associated to the error on each of these parameters.
-\comment{It is not clear what you are doing here.
-I can understand bootstrapping a time series: you shuffle all the values keeping the time stamps fixed.
-How do you bootstrap a stellar spectrum?
-Do you shuffle the intensity values keeping the wavelengths fixed?
-That would produce a mess.
-Do you just add different levels of random noise?
-But the spectra already have noise in them, they are real observations.
-You need to state more clearly here what you did.}
-
-In the top plots of Fig.~\ref{fig:se} we show the different errors for the RVs, the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels.
-The parameter SN50 corresponds to the SNR in order 50, which corresponds to a wavelength of 550\,nm.
-In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN or the Normal and the \emph{noise} parameter extracted from the HARPS reduction pipeline.
-We first see that the errors on the CCF parameters only depends on the SNR and do not depend on the spectral type.
-This is true if the spectral type are not too different though, like here where we show the results for G and K dwarfs.
-
-We see that for the RV errors, the ratio between the \emph{noise} parameter and the the RV error measured by the bootstrap using the Normal fitting is around 1, meaning that those two estimates of the RV errors are similar.
-However when fitting a SN to the CCF, we have RV errors that are on average 60\% greater.
-
-Thus, the RVs measured by the SN do not have the same precision than the RVs calculated using the Normal.
-This can be explained by the fact that in the case of the SN, variations in the asymmetry parameter $\gamma_1$ induce variations in the SN RV measured due to the strong correlation between those two parameters.
-Therefore, the errors in $\gamma_1$ propagate to the error in the SN RVs.
-\comment{This seems to be the case in all your stars. I do not consider a method that delivers errors that are 60\% larger to be a very effective method.}
-Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal or the SN are equivalent to 2.35$\times$\emph{noise}.
-Therefore, the precision in CCF width is the same if we fit a Normal or a SN to the CCF.
-
-Finally, for the errors in CCF asymmetry, we see that the bootstrap analysis using the Normal fitting gives the same precision as using 2$\times$\emph{noise}, which is the common errors used for BIS SPAN.
-However, when fitting the SN to the CCF, the asymmetry errors are 15\% smaller.
-Therefore, the SN fit gives a better precision in CCF asymmetry than what can be reached using BIS SPAN.
-
-Another interesting point is the behavior of the ratio of the bootstrap errors over the \emph{noise} parameter as a function of SNR (see bottom plots in Fig.~\ref{fig:se} for the RVs, CCF width and CCF asymmetry).
-We see that at low SNR, the bootstrap analysis gives a better precision, which can be explained by the fact that the \emph{noise} parameter is estimated using the CCF derivative.
-Calculating the derivative of the CCF increases the noise and therefore explain this behavior at low SNR.
-For SNR below 200, the bootstrap analysis gives a better precision than the \emph{noise} parameter.
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
-   \caption{Comparison between the standard errors using the bootstrap analysis and the parameter $noise$ for the RVs, $2.35\times$\emph{noise} for the width, and $2\times$\emph{noise} for the asymmetry parameter.
-Note that for the asymmetry, the error in BIS SPAN is in \kms.
-To be able to compare the errors in $\gamma_1$ and BIS SPAN, we multiplied the error in $\gamma_1$ by the slope of the correlation between $\gamma_1$ and BIS SPAN.}
-   \label{fig:se}
-\end{figure*}
-
-%, using the spectrum derivative
-%, the pure photon-noise error on RV measured 
-%Together with the pointwise estimates, retrieving the standard errors for the RVs of the star, $\gamma$ and the FWHM provides information about the uncertainties associated to each parameter.
-Since the procedure for retrieving the RVs of the star consists in fitting with a density function a CCF, getting the standard errors for all the parameter of interests cannot be done by using the common asymptotic theory.
-The implementation of a standard bootstrap analysis cannot as well be done, because the points of the CCF are highly correlated.
-In the analysis of the present work, in order to get the standard errors for the parameters of interest for a particular CCF, we moved each point of this CCF according to its measurement errors, producing $100$ simulated CCFs from the original one.
-Then we run both the Normal and the SN analyses on these simulated CCFs, letting us to retrieve an evaluation of the standard errors.
-This operation has been repeated for all the CCFs available for the analyzed stars.
-The comparison between the standard errors retrieved in this way with the classic noise parameter, {\color{red} obtained by using the Gray's equation cit.
-Gray (1983)} are presented in Figure \ref{fig:se}.
-{\color{red} Xavier: Is it correct how the noise parameter is obtained?
-Or it is simply $\sqrt(photons)$?}
-
-%Given the strong correlation between the $\gamma$ parameter of the SN and its mean, the standard errors are larger respect the Normal fitting analysis.
-This fact confirms how correcting the RVs for stellar activity using Eq.
-\ref{eq:RV:correction} is more helpful when using the SN fitting.
-The standard errors for the FWHM are comparable for both the SN and the Normal analyses, whereas an improvement is clearly measurable for the standard errors associated to the asymmetry indicators.
-The last plot in Fig.~\ref{fig:se} shows that the standard errors for $\gamma$ are $10 \%$ smaller than the ones retrieved for the BIS SPAN.
-
-%-----------------------------------------------------------------------------------------------------------------------------------------------
-\section{Discussion} \label{sec:discu}
-
-An analysis of the CCF residuals after fitting a Normal or SN distribution show that the SN is a better model to explain the shape of the CCF.
-This comes from the fact that CCFs present a natural asymmetry due the convective blueshift.
-
-We compared for five stars the difference between the RVs, FWHM and asymmetry (BIS SPAN in the Normal case and parameter $\gamma_1$ in the SN case) as measured we a Normal or a SN fitting to the CCF.
-The $\gamma_1$ parameter is linearly dependant on the BIS SPAN, with always a strong correlation coefficient.
-%To compare $\gamma_1$, that do not have any units, with BIS SPAN expressed in \kms, one has simply to multiply $\gamma_1$ by the slope of the linear dependence between $\gamma_1$ and BIS SPAN. 
-The slope of this linear correlation change depending on the star studied. This is probably because the spectral type is different, therefore the effects from stellar activity are different.
-
-When comparing the RV as measured by the Normal and the SN fitting, we always see that the rms of the latter is larger.
-Thus fitting the SN to the CCF gives RV measurements that are more sensitive to activity.
-This comes from the fact the the asymmetry parameter of the SN will modify as well the mean of the distribution, thus the RV.
-This is a positive point as it is easier to correct for a signal that is at a high SNR rather that a signal that is at a SNR of one, which is generally the case for the low-activity stars that are followed for RV surveys.
-
-The RVs derived using the SN fitting present a higher sensitivity to stellar activity.
-However, once correcting the RVs from stellar activity using a linear combination of the width and asymmetry parameter of the CCF (FWHM and BIS SPAN in the Normal case, and SN FWHM and $\gamma_1$ in the SN case), the RV residuals in both the Normal and SN case show similar scatter.
-Therefore, the SN fitting does not improve stellar activity correction when using a simple linear combination with the width and asymmetry of the CCF.
-\comment{In this statement you have basically admitted that your method is not very useful. I do not see why anyone would be compelled to use it!
-So, the bottom line is that you have introduced a method which produces similar results to the standard one.
-The only useful result of this paper is to convey to the readers that there is no significant advantage in implementing the SN method!}
-However, because the amplitude of the variations is larger in the raw SN RVs, correction techniques based on Gaussian Processes might be more efficient \citep[][]{Haywood-2014,Faria-2016a}.
-
-When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma_1$ in the SN case) with respect to the RVs (RVs in the Normal case or SN RVs in the SN case), we observe that the correlations are always stronger for the parameters of the SN.
-Therefore, the SN parameters are more sensitive to activity.
-In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of 0.57 between $\gamma_1$ and SN RV, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.21.
-
-We also studied the behavior of the noise on the different parameters of the Normal and the SN as a function of SNR.
-By performing a bootstrap analysis, we confirmed that in the case of the Normal, using the \emph{noise} parameter as returned by the HARPS pipeline gives a correct estimate of the errors measured on the RVs, FWHM and BIS SPAN for SNR $>150$.
-For the RVs, the errors are equivalent to \emph{noise}, for the FWHM to 2.35$\times$\emph{noise} and for the BIS SPAN to 2$\times$\emph{noise}.
-For lower SNR though, the bootstrap analysis gives better results, and this comes from the fact the the \emph{noise} parameter is estimated using the derivative of the CCF, which increase the noise \citep[][]{Bouchy-2001b}.
-For very low SNR, the improvement of the bootstrap analysis can be as high as 50\%.
-Therefore, although taking much more time, we encourage the use of bootstrapping when calculating errors for the different parameters of the CCF.
-
-In the case of the errors when using the SN fitting, the precision on the SN RVs is however 60\% worse than for the RVs.
-This comes from the fact that because the asymmetry is accounted for in the SN and because the SN RVs and $\gamma_1$ are strongly correlated, the errors in $\gamma_1$ propagates to the errors in SN RVs.
-This is not so important for SNR $>$ 150 for which the errors are below the \ms precision of HARPS and the \ms variation induced by stellar activity signals even in low activity cases \footnote{As we can see in papers publishing HARPS results using an additional jitter to consider stellar activity noise not accounted for in the \emph{noise} parameter, the extra jitter is always greater than 0.8\ms \citep[e.g.][]{Diaz:2016ab}.}.
-These larger errors in RVs can be a problem for low SNR measurements.
-In the case of the CCF width, the error derived when using the Normal or SN fitting are very similar.
-Finally for the asymetry, we see that the error in $\gamma_1$ is $\sim$15\% smaller than the error in BIS SPAN.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion} \label{sec:conclu}
-
-In this paper we introduced a novel approach based on the Skew Normal (SN) distribution for deriving RVs and shape variations in the CCF of stars.
-When searching for small-mass exoplanets using the RV technique, it is essential to understand the shape variation of the CCF, which is a proxy for stellar activity effects.
-The standard approach consist in first to adjust a Normal distribution to the CCF to get the RV and FWHM, defined as the mean and the FWHM of the Normal distribution, and then to measure the asymmetry by calculating BIS SPAN.
-FWHM and BIS SPAN give us information on the line shape that are used to probe stellar activity signals.
-In this paper we demonstrate that by using the SN distribution to fit CCFs, we can measure simultaneously the RV of the star with the width and asymmetry of the CCF.
-
-Using the SN to fit CCFs brings a significant improvement in probing stellar activity.
-The correlations between SN RV and SN FWHM, and SN RV and the asymmetric parameter $\gamma_1$ are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
-The RVs derived by the SN are also more sensitive to activity and the precision on the asymmetry measured by $\gamma_1$ is greater than the one on BIS SPAN by $\sim$15\%.
-Therefore when searching for rotational periods in the data, or applying Gaussian Processes to account for stellar activity signals, the SN parameters should be used.
-
-At first glance, one downside of using the SN comes from the RV errors that are greater by 60\% relative to the RV errors measured when considering a Normal.
-This is due to the strong correlation between SN RV and $\gamma_1$ and this can be a problem for low SNR measurements.
-However, in the regime of SNR $>$ 150, which is the aim of all RV surveys at high precision, the precision of the SN RVs is below the \ms, which is thus below the instrumental precision of HARPS and below the RV perturbations induced by stellar activity.
-
-Finally, we also encourage the use of bootstrapping to estimate more realistic errors on the different parameters of the Normal or SN fitted to the CCF, mainly in the low SNR regime where a gain of 50\% can be reached.
-This takes significantly more time, but note that 100 realization are enough to get a good estimation of errors.
-
-%the RVs of the star can be calculated as the mean of the SN, whereas its asymmetry parameter $\gamma$ can be naturally used for retrieving information about the asymmetry of the CCF.
-Because of the natural correlation between the RVs and the asymmetry parameter, a linear combination of both $\gamma$ and the FWHM has been implemented for correcting the RVs from stellar activity, allowing us to retrieve a more precise RVs.
-
-%In order to get the standard errors for the estimated parameters, rather than using the common $noise$ statistic, we created a simulated procedure based on perturbing each point of the CCF according to its measurement error.
-Then, by getting from the original profile line $100$ simulated profiles, we run the SN fitting analyses, allowing us retrieving for all the parameter of interests an estimation for their standard errors.
-Concerning the standard error associated to the means of the distributions, the SN fit leads to slightly larger standard errors respect when running the Normal fit.
-This fact can be explained by noticing that as a simulated CCF is created according to the procedure described above, we expect slightly differences on the asymmetry of the CCF as well.
-The natural correlation between the RVs of the star and $\gamma$, where the mean of the SN is shifted in the direction of the asymmetry of the distribution, leads to larger uncertainties related to the RVs of the star.
-The latter consideration provides a further justification for correcting the RVs of the star from stellar activity and explains why this correction is more helpful when running the proposed analysis rather than the classic Normal fit.
-Concerning the standard errors related to the asymmetry parameters, when using the SN fit the uncertainties are $10 \%$ smaller than using the classic BIS SPAN.
-In conclusion, we showed how using the SN fit provides in an unique step a better understanding of the stellar activity through using the asymmetry parameter $\gamma$ rather than using the common statistics such as the BIS SPAN or other indicators.
-On top of that, when focusing on low signal to noise cases, the SN procedure showed how statistically significant results are retrieved with the proposed approach in terms of correlation between the asymmetry of the profile line and the RVs, whereas for the previous analyses this correlation does not result statistically significant.
-
-%-----------------------------------------------------------------------------------------------------------------------------------------------
-\section{Acknowledgements}
-
-We are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
-XD is grateful to the Society in Science--The Branco Weiss Fellowship for its financial support.
-
 %%-----------------------------------------------------------------------------------------------------------------------------------------------

### 2018-03-16 plots_jessi.R

@@ -29,3 +29,44 @@ round(cbind(alpha, mu, sig2, gamma),3)
 
 
 
+
+
+
+################  Exploration of robust (wrt skewness) parameters
+x <- seq(-3.25, 3.25, length.out = 1000)
+xi <- 0
+omega <- 1
+alpha <- seq(0, 5, by = 0.25)
+dx <- lapply(1:length(alpha), function(ii) dsn(x, xi, omega, alpha[ii], tau=0, dp=NULL, log=FALSE))
+medx <- sapply(1:length(alpha), function(ii) qsn(.5, xi, omega, alpha[ii], tau=0, dp=NULL, log=FALSE))
+fbeta <- function(a){sqrt(2/pi)*a/sqrt(1+a^2)}
+fgamma <- function(b){0.5*(4 - pi)*b^2*(1-b^2)^(-3/2)}
+beta <- fbeta(alpha)
+gamma <- fgamma(beta)
+meanx <- xi + omega*beta
+
+par(mfrow = c(1,2), mar = c(4,4,1,1), lwd = 3, cex = 2)
+#Median
+plot(x, dx[[1]], "n", xlab = "Y", ylab = "Density", ylim = c(0,.8), main = "Median = vertical lines")
+temp <- sapply(1:length(alpha), function(ii) lines(x, dx[[ii]], col = ii, lty = ii))
+abline(v = medx, col = 1:length(alpha), lwd = 3, lty = 1)
+legend("topleft", legend = alpha, col = 1:length(alpha), lty = 1:length(alpha), lwd = 2, title = expression(alpha), cex = .5)
+#Mean
+plot(x, dx[[1]], "n", xlab = "Y", ylab = "Density", ylim = c(0,.8), main = "Mean = vertical lines")
+temp <- sapply(1:length(alpha), function(ii) lines(x, dx[[ii]], col = ii, lty = ii))
+abline(v = meanx, col = 1:length(alpha), lwd = 3, lty = 1)
+
+plot(meanx, medx)
+abline(a = 0, b = 1)
+
+
+
+
+
+
+
+
+
+
+
+

### 2018-03-20 manuscript.tex
added comments and made some modifications

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Stellar activity effect on CCF, normal fit plus FWHM indicator}
+\subsection{Stellar activity effect on CCF, Normal fit plus FWHM indicator}
 \jessi{Eventually three methods are introduced for detecting CCF asymmetry:  FWHM, bisector span, and the Figueira approach - it seems that these methods need to be better explained.
@@
 However, this would give a noisy estimate so first a normal density shape is fitted to the CCF, and then the estimated mean of the normal density is used as the estimate of the RV.
-The full width at half maximum (FWHM) of the normal fit is also used as an indicator of spectral line asymmetry.
+The full width at half maximum (FWHM) of the Normal fit is also used as an indicator of spectral line asymmetry.
 The CCF technique allows for an averaging of thousands of spectral lines and can therefore reach a very high signal-to-noise ratio (SNR), which is essential for a good RV precision.
@@
 
-The CCF is the result of a cross correlation so the residuals of a normal or a SN fit are expected to show correlated noise.
+The CCF is the result of a cross correlation so the residuals of a Normal or a SN fit are expected to show correlated noise.
 To investigate this issue, we considered example CCFs from the star Tau Ceti.
@@
 %
-After removing the median of the residuals, in the lower right panel, the final residuals of the SN procedure have almost no apparent correlation, while the final residuals of the normal procedure still present a small systematic component.
+After removing the median of the residuals, in the lower right panel, the final residuals of the SN procedure have almost no apparent correlation, while the final residuals of the Normal procedure still present a small systematic component.
 This seems to be due to the asymmetric nature of the CCF (see Section~\ref{intro}), which is not captured in a symmetric distribution like the normal distribution.
@@
 \includegraphics[height = 6in]{[1]Plot_Fitting_and_Residuals_2run.pdf} 
-   \caption{Comparison between the normal and the SN procedures for modeling a collection of CCFs for the star Tau Ceti.
+   \caption{Comparison between the Normal and the SN procedures for modeling a collection of CCFs for the star Tau Ceti.
 Two stages of modeling are carried out with the first stage results displayed in the left column and the second stage in the right column.
@@
 In the following of the paper, we define the RV as the mean of the normal or the mean of the SN (defined as SN RV).
-For the width of the CCF, we use the FWHM of the Normal, defined as $2\sqrt(2\ln2)\sigma$.
-The width of the SN, SN FWHM, is defined in the same way\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the normal case.}.
-In the normal case, it is not possible to retrieve an asymmetric parameter and therefore we use BIS SPAN.
+For the width of the CCF, we use the FWHM of the Normal, which is $2\sqrt(2\ln2)\sigma$.
+The width of the SN, SN FWHM, is defined in the same way\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}.
+In the Normal case, there is not an asymmetric parameter so we use BIS SPAN.
 This will be compared to the asymmetric parameter $\gamma_1$ of the SN.
+\jessi{Why use FWHM at all?
+Why not just use the standard deviation since the FWHM just includes a multiplicative factor that is the same for all of them.}
 
@@
 
-Exoplanets will only produce a RV variation induced by a pure Doppler shift of stellar spectra.
-Stellar activity, on the contrary, does not produce a blueshift or redshift of the spectra, but creates a spurious RV signal by modifying the shape of spectral lines.
-To track these changes in line shape, we generally use the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} that give an information on the average width and asymmetry of the CCF.
-A strong correlation between the RVs and one or more of these parameters is a sign that the RVs are significantly affected by stellar activity signals.
+An orbiting exoplanet will produce an RV variation induced by a pure Doppler shift of \emph{all} the spectral lines of each stellar spectrum. 
+Stellar activity, however, does not produce a blueshift or redshift of the spectra, but can create a spurious RV signal by modifying the shape of spectral lines.
+To track changes in line shape, the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} are often used, \jessi{citations are needed here} which provide information on the average width and asymmetry of the CCF.
+A strong correlation between the estimated RVs and one or more of these parameters is a sign that the estimated RVs may be contaminated by stellar activity.
 
-To test the strength of the correlation between RVs and the different activity indicators, we calculated the Pearson correlation coefficient defined as:
-%
-\begin{equation}
-R (x,y)= \frac{cov(x,y)}{\sigma(x),\sigma(y)},
-\label{eq:Pearson:corr}
-\end{equation}
-where $x$ and $y$ are two quantitative variables, $cov(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represents their standard deviation. 
-A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided, along with a $95\,\%$ confidence interval for $R$.
-%
+To test the strength of the correlation between RVs and the different activity indicators, we calculated the Pearson correlation coefficient, $R$.
+A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ (i.e., no correlation) is provided, along with a $95\,\%$ confidence interval for $R$.
 
@@
 In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,1,2$.
+\jessi{the estimated values and p-values of the $\beta$'s does \underline{not} show goodness of fit.}
 The level for not rejecting the null hypothesis is fixed equal to $0.05$.
 Pearson correlation coefficient $R^{2}$ is considered for explaining how well this linear combination explains the variability of the RVs of the star due to stellar activity.
+\jessi{$R^2$ is the coefficient of determination, and this should be explained better because it is not commonly used in astronomy as an assessment of the amount of variability explained by the model.}
 
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-\section{Simulated data examples} \label{sec:soap}
+\section{Simulation Study} \label{sec:soap}
+In order to evaluate the performance of the proposed SN approach for modeling the CCF, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}...
+
+We also consider a real-data example using HARPS spectra from the star Alpha Centauri B with an imputed Doppler shift added...
 
@@
 
-In this Section we present the analyses of five stars, showing the advantages of fitting the CCF using the SN distribution defined in Section \ref{sec:3}.
+In this Section we present the analyses of five stars comparing the result of fitting a CCF using the SN distribution defined in Section \ref{sec:3} versus the Normal approach.
 
@@
 
-We first analyze Alpha Centauri B, where $1816$ CCFs in 2010 are considered.
+Alpha Centauri B $1816$ CCFs in 2010 are considered.
 Several measurement in 2010 are contaminated by light from Alpha Centauri A.
@@
 
-We begin by evaluating the correlation between $\gamma$ and the classic BIS SPAN.
+We begin by evaluating the correlation between $\gamma$ and the BIS SPAN.
 In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.933$ and a strong Pearson correlation coefficient of $0.958$.
+\jessi{It would be good to explain why you care about this.}
 %
@@
 
-Figure \ref{fig:alphacent:diff:RV} shows the comparison between the RVs retrieved using the SN distribution and the ones obtained with the Normal distribution.
-This data set for Alpha Centauri B, used in \citet{Dumusque-2012} and \citet{Thompson-2017}, present a strong stellar activity signal.
+Figure \ref{fig:alphacent:diff:RV} shows the comparison between the RVs retrieved using the SN shape and the ones obtained with the normal shape.
+This data set for Alpha Centauri B, used in \citet{Dumusque-2012} and \citet{Thompson-2017} \jessi{It seems that this should be mentioned at the beginning of this section}, present a strong stellar activity signal.
 We see that the RVs measured by the SN fitting show more variations than the RVs measured by the Normal fitting.
@@
 
-By looking closer to the data in Fig.~\ref{fig:alphacent:clusters}, we saw that there are three distinct temporal clusters in the Alpha Centauri B measurements and those clusters have a different linear relationship between $\gamma_1$ and RVs (and also SN FWHM and RVs, though not displayed here).
+%By looking closer to the data in Fig.~\ref{fig:alphacent:clusters}, we saw that there are three distinct temporal clusters in the Alpha Centauri B measurements and those clusters have a different linear relationship between $\gamma_1$ and RVs (and also SN FWHM and RVs, though not displayed here).
 When considering Eq.
@@
 
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[width = 6in]{AlphaCenB_clusters.pdf}  
-   \caption{The RVs as a function of time (left) and the RVs plotted against $\gamma_1$ (right) with colors and plot symbol according to its temporal cluster assignment for Alpha Centauri B.
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[width = 6in]{AlphaCenB_clusters.pdf}  
+%   \caption{The RVs as a function of time (left) and the RVs plotted against $\gamma_1$ (right) with colors and plot symbol according to its temporal cluster assignment for Alpha Centauri B.
 The RVs are expressed in \ms.}
-   \label{fig:alphacent:clusters}
-\end{figure*}
-
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[width = 6in]{AlphaCenB_clusters_residuals.pdf}  
-   \caption{The RV for Alpha Centauri B corrected for stellar activity using the SN fit and accounting for the temporal clusters (left), and the difference between those values on in the left plot and the analogous values without accounting for the temporal clusters (right) which are displayed in the lower left plot of Figure~\ref{fig:alphacent:correctionRV}.
+%   \label{fig:alphacent:clusters}
+%\end{figure*}
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[width = 6in]{AlphaCenB_clusters_residuals.pdf}  
+%   \caption{The RV for Alpha Centauri B corrected for stellar activity using the SN fit and accounting for the temporal clusters (left), and the difference between those values on in the left plot and the analogous values without accounting for the temporal clusters (right) which are displayed in the lower left plot of Figure~\ref{fig:alphacent:correctionRV}.
 The RVs are expressed in \ms.}
-   \label{fig:alphacent:clusters_residuals}
-\end{figure*}
+%   \label{fig:alphacent:clusters_residuals}
+%\end{figure*}
 

### 2018-03-20 plots_jessi.R

@@ -19,7 +19,7 @@ legend("topleft", legend = alpha, col = par.index, lty = par.index, lwd = 5, tit
 
 
 fbeta <- function(a){sqrt(2/pi)*a/sqrt(1+a^2)}
-fgamma <- function(b){0.5*(4 - pi)*b^2*(1-b^2)^(-3/2)}
+fgamma <- function(b){0.5*(4 - pi)*b^3*(1-b^2)^(-3/2)}
 beta <- fbeta(alpha)
 gamma <- fgamma(beta)
 mu <- xi + omega*beta
@@ -63,10 +63,23 @@ abline(a = 0, b = 1)
 
 
 
+################  FWHM
+x <- seq(-3.25, 3.25, length.out = 1000)
+xi <- 0
+omega <- 1
+alpha <- seq(0, 5, by = 1)
+dx <- lapply(1:length(alpha), function(ii) dsn(x, xi, omega, alpha[ii], tau=0, dp=NULL, log=FALSE))
+medx <- sapply(1:length(alpha), function(ii) qsn(.5, xi, omega, alpha[ii], tau=0, dp=NULL, log=FALSE))
+fbeta <- function(a){sqrt(2/pi)*a/sqrt(1+a^2)}
+fgamma <- function(b){0.5*(4 - pi)*b^2*(1-b^2)^(-3/2)}
+beta <- fbeta(alpha)
+gamma <- fgamma(beta)
+meanx <- xi + omega*beta
+ffwhm <- function(sig){2*sqrt(2*log(2))*sig}
+sig2 <- omega^2*(1-beta^2)
+ffwhm(sqrt(sig2))
 
-
-
-
-
-
+par(mfrow = c(1,1), mar = c(4,4,1,1), lwd = 3, cex = 1)
+plot(x, dx[[1]], "n", xlab = "Y", ylab = "Density", ylim = c(0,.8), main = "FWHM")
+temp <- sapply(1:length(alpha), function(ii) lines(x, dx[[ii]], col = ii, lty = ii))
 

### 2018-03-21 plots_jessi.R
r code updates

@@ -63,7 +63,7 @@ abline(a = 0, b = 1)
 
 
 
-################  FWHM
+################  Stable
 x <- seq(-3.25, 3.25, length.out = 1000)
 xi <- 0
 omega <- 1
@@ -79,7 +79,48 @@ ffwhm <- function(sig){2*sqrt(2*log(2))*sig}
 sig2 <- omega^2*(1-beta^2)
 ffwhm(sqrt(sig2))
 
+dx_rm <- lapply(1:length(alpha), function(ii) pnorm(alpha[ii]*(x-xi)/omega,0,1))
+
 par(mfrow = c(1,1), mar = c(4,4,1,1), lwd = 3, cex = 1)
-plot(x, dx[[1]], "n", xlab = "Y", ylab = "Density", ylim = c(0,.8), main = "FWHM")
+plot(x, dx[[1]], "n", xlab = "Y", ylab = "Density", ylim = c(0,.8), main = "")
 temp <- sapply(1:length(alpha), function(ii) lines(x, dx[[ii]], col = ii, lty = ii))
+
+# Remove skew portion
+temp <- sapply(1:length(alpha), function(ii) lines(x, dx[[ii]]/dx_rm[[ii]], col = ii, lty = ii))
+
+
+
+
+### Remove skew portion
+
+x <- seq(0, 8, length.out = 1000)
+xi <- 4
+omega <- 1
+alpha <- 8
+dx <- dsn(x, xi, omega, alpha, tau=0, dp=NULL, log=FALSE)
+dx_rm <- pnorm(alpha*(x-xi)/omega,0,1)
+medx <- sapply(1:length(alpha), function(ii) qsn(.5, xi, omega, alpha[ii], tau=0, dp=NULL, log=FALSE))
+fbeta <- function(a){sqrt(2/pi)*a/sqrt(1+a^2)}
+fgamma <- function(b){0.5*(4 - pi)*b^2*(1-b^2)^(-3/2)}
+beta <- fbeta(alpha)
+gamma <- fgamma(beta)
+meanx <- xi + omega*beta
+sig2 <- omega^2*(1-beta^2)
+
+
+
+plot(x, dx, "l", col = 1, lwd = 3, xlab = "Y", ylab = "Density", ylim = range(dx, dx/dx_rm))
+lines(x, dx/dx_rm, col = 2, lty = 2, lwd = 3)
[…]

### 2018-04-10 manuscript_update.tex
Add files via upload
manuscript updated: new methodology (to be finished)

--- 2018-03-20 manuscript.tex
@@
 
+\umberto{We considered CCFs having SNR larger than 10.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
    \centering
-\includegraphics[height = 3in]{Skew_normal_densities_jjck.pdf} 
+\includegraphics[height = 4in]{Skew_normal_densities_jjck.pdf} 
    \caption{Density function of a random variable $Y \sim SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$, and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
@@
 In particular, $\mu$ and $\sigma^2$ are the actual mean and the variance of the distribution (rather than simply a location and scale parameter), and $\gamma$ becomes an index for evaluating the asymmetry of the SN.
+Beyond the mean of the SN, it is convenient to introduce a second location parameter that will be used in the analyses: the median.
+The median of the SN is defined as that value $m$ such that
+%
+\begin{equation} \label{eq:snmed}
+\int_{-\infty}^{m} SN(y;\xi, \omega, \alpha) = \frac{1}{2},
+\end{equation}
+%
+where $SN(y;\xi, \omega, \alpha)$ follows Equation \ref{def:snd_gen}.\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}
+
 %% Requires the booktabs if the memoir class is not being used
@@
 
+\umberto{Insert here a comparison of the N residuals and SN residuals?
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{[1]HD128621Residuals.pdf} 
+   \caption{Comparison between the Normal and the SN procedures for modeling a collection of CCFs for the star Alpha Centauri b.}
+    \label{fig:Residual.comparison}
+\end{figure*}
+
+}
+
+%\umberto{here were discussed the implementation of the heteroskedastic function for the variance and the second run once removed the residuals median. Both these steps won't be in the new analyses.}
+%%%%%% April 5th, 2018
+%%% in the new Analyses both the heteroskedastic function for the variance and the second run are not considered
+%%%%%%
+\iffalse
 Since each point of the CCF has a measurement error, this information is included in the specification of the SN distribution by introducing the following heteroskedastic function for the variance,
@@
    \centering
-\includegraphics[height = 6in]{[1]Plot_Fitting_and_Residuals_2run.pdf} 
+\includegraphics[height = 4in]{[1]Plot_Fitting_and_Residuals_2run.pdf} 
    \caption{Comparison between the Normal and the SN procedures for modeling a collection of CCFs for the star Tau Ceti.
@@
 In order to resolve this problem, we implemented two functions for retrieving the best least squares solution.
-In the first function we allowed for only positive solutions of $\gamma_1$ (with an upper limit of $0.995$), while in the second function only negative solutions are allowed (with a lower limit of $\gamma= -0.995$).
+In the first function we allowed for only positive solutions of $\gamma$ (with an upper limit of $0.995$), while in the second function only negative solutions are allowed (with a lower limit of $\gamma= -0.995$).
 The chosen solution is the estimate which has smallest residuals.
-
-In the following of the paper, we define the RV as the mean of the normal or the mean of the SN (defined as SN RV).
+\fi
+%%%%%%
+%%%
+%%%%%% April 5th, 2018
+
+In the following of the paper, we define RV as the mean of the normal.
+Concerning the fit of the CCF using the SN, we present at first $2$ indicators that define the RV of the star: the mean of the SN, defined as SN mean RV and the median of the SN, defined as SN median RV.
+We will discuss the advantages of using this choice in the examples.
 For the width of the CCF, we use the FWHM of the Normal, which is $2\sqrt(2\ln2)\sigma$.
@@
 In the Normal case, there is not an asymmetric parameter so we use BIS SPAN.
-This will be compared to the asymmetric parameter $\gamma_1$ of the SN.
+This will be compared to the asymmetric parameter $\gamma$ of the SN, called SN GAMMA.
 \jessi{Why use FWHM at all?
@@
 
+%\umberto{here the correction for stellar activity was discussed. In the new analyses we are using the median of the SN as indicator for RV of the star.}
+%%%%%% April 5th, 2018
+%%% in the new Analyses both the is no correction for stellar activity: the median of the SN is used
+%%%%%%
+\iffalse
 To correct for stellar activity signals, it is common to consider a linear combination of the RVs with the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case):
@@
 It will be less confusing if you simply have two equations, one for Normal and one for SN and with their respective variables.}
-When the Normal fit is used, the parameter $\gamma_1$ is replaced by the BIS SPAN and SN FWHM by FWHM.
+When the Normal fit is used, the parameter $\gamma$ is replaced by the BIS SPAN and SN FWHM by FWHM.
 In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,1,2$.
@@
 \jessi{$R^2$ is the coefficient of determination, and this should be explained better because it is not commonly used in astronomy as an assessment of the amount of variability explained by the model.}
+\fi
+%%%%%%
+%%%
+%%%%%% April 5th, 2018
 
@@
 
-Alpha Centauri B $1816$ CCFs in 2010 are considered.
+A total of $1808$ CCFs measured in $2010$ have been analysed from the star Alpha Centauri B.
 Several measurement in 2010 are contaminated by light from Alpha Centauri A.
@@
 We begin by evaluating the correlation between $\gamma$ and the BIS SPAN.
-In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.933$ and a strong Pearson correlation coefficient of $0.958$.
-\jessi{It would be good to explain why you care about this.}
+In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.99$ and a strong Pearson correlation coefficient of $0.96$.
+\jessi{It would be good to explain why you care about this.} This comparison is useful because $\gamma$ is an adimensional parameter taking information about the asymmetry of the SN while the BIS SPAN, beyond this, has got unit of measure of $km/s$.
+In other words, by using Fig.~\ref{fig:alphacent:corr.gamma}, it is possible to provide to $\gamma$ a physical meaning.
 %
@@
    \centering
-\includegraphics[height = 3in]{HD12862_[2]gamma_vs_bisspan.pdf} 
+\includegraphics[height = 4in]{HD12862_[2]gamma_vs_bisspan.pdf} 
    \caption{Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.}
@@
 
+%%%%%%April 5th, 2018
+%%% correction for stellar activity
+%%%%%%
+\iffalse
 We show the correction of stellar activity using Eq.
@@
 The comparison of $R^2$ shows as well that the SN case accounts for a higher percentage of  variability in RVs.
-
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
+\fi
+%%%%%%
+%%%
+%%%%%% April 5th, 2018
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{HD12862_[2]RadialVelocityDifferences.pdf} 
    \caption{RVs and RV differences for Alpha Centauri B considering a Normal and a SN fitting.}
@@
 
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD12862_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+%%%%%%April 5th, 2018
+%%% correction for stellar activity
+%%%%%%
+\iffalse
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{HD12862_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
    \caption{RVs of Alpha Centauri B using a Normal and a SN fitting before and after correcting for stellar activity using Eq. \ref{eq:RV:correction}.
@@
 \end{table}
+\fi
+%%%%%%
+%%%
+%%%%%% April 5th, 2018
 
 We compare the correlation between the different activity indicators and the RVs of the star in Fig.~\ref{fig:alphacent:corrPlot}.
-The correlation between $\gamma_1$ and RVs is much stronger, almost twice, than the correlation calculated between the other asymmetry parameters and their corresponding RVs.
+The correlation between $\gamma$ and RVs is much stronger, almost twice, than the correlation calculated between the other asymmetry parameters and their corresponding RVs.
 The correlation between FWHM and the RVs is as well stronger when fitting a SN distribution.
@@
    \centering
-\includegraphics[height = 6in]{HD12862_[4]Comparison_para.pdf}  
+\includegraphics[height = 4in]{HD12862_[4]Comparison_para.pdf}  
    \caption{Correlation between the asymmetry parameters and the RVs for Alpha Centauri B.
@@
 
-%By looking closer to the data in Fig.~\ref{fig:alphacent:clusters}, we saw that there are three distinct temporal clusters in the Alpha Centauri B measurements and those clusters have a different linear relationship between $\gamma_1$ and RVs (and also SN FWHM and RVs, though not displayed here).
+%By looking closer to the data in Fig.~\ref{fig:alphacent:clusters}, we saw that there are three distinct temporal clusters in the Alpha Centauri B measurements and those clusters have a different linear relationship between $\gamma$ and RVs (and also SN FWHM and RVs, though not displayed here).
 When considering Eq.
 \ref{eq:RV:correction} and the subsequent inferences, this clustering is not accounted for in the model.
-A slightly more general linear model that allows for different intercepts and different slopes for the three clusters for $\gamma_1$ and SN FWHM can be considered.
+A slightly more general linear model that allows for different intercepts and different slopes for the three clusters for $\gamma$ and SN FWHM can be considered.
 Adjusting the RVs for stellar activity using this expanded model produces the corrected radial velocities displayed in the left plot of Fig.~\ref{fig:alphacent:clusters_residuals}.
@@
 \ref{eq:RV:correction}); the right plot of Fig.~\ref{fig:alphacent:clusters_residuals} displays the difference between the two sets of corrected RVs.
-The long-term trend can be explained by the fact that the RV drift induced by the companion Alpha Centauri A is not well corrected, however the shorter-term variations show that stellar activity varies as a function of time, with spots and faculae evolving, and therefore modifies the dependence of the RVs with respect to $\gamma_1$ and SN FWHM.
+The long-term trend can be explained by the fact that the RV drift induced by the companion Alpha Centauri A is not well corrected, however the shorter-term variations show that stellar activity varies as a function of time, with spots and faculae evolving, and therefore modifies the dependence of the RVs with respect to $\gamma$ and SN FWHM.
 These temporal variations is something that we want to explore more, however this work presents a significant effort that we want to address in a future paper.
@@
 %\includegraphics[width = 6in]{AlphaCenB_clusters.pdf}  
-%   \caption{The RVs as a function of time (left) and the RVs plotted against $\gamma_1$ (right) with colors and plot symbol according to its temporal cluster assignment for Alpha Centauri B.
+%   \caption{The RVs as a function of time (left) and the RVs plotted against $\gamma$ (right) with colors and plot symbol according to its temporal cluster assignment for Alpha Centauri B.
 The RVs are expressed in \ms.}
@@
 
-In this section, we do a bootstrap analysis to measure the standard errors on the RVs or SN RVs, the FWHM or SN FWHM, and BIS SPAN or $\gamma_1$.
+In this section, we do a bootstrap analysis to measure the standard errors on the RVs or SN RVs, the FWHM or SN FWHM, and BIS SPAN or $\gamma$.
 Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
@@
 To bypass this problem, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF.
-We then fit a Normal or a SN to each of these CCFs, and the standard deviation of the distribution for the mean (RV or SN RV), the width parameter (FWHM or SN FWHM) and the asymmetric parameter ($\gamma_1$ or BIS SPAN) is associated to the error on each of these parameters.
+We then fit a Normal or a SN to each of these CCFs, and the standard deviation of the distribution for the mean (RV or SN RV), the width parameter (FWHM or SN FWHM) and the asymmetric parameter ($\gamma$ or BIS SPAN) is associated to the error on each of these parameters.
 \comment{It is not clear what you are doing here.
@@
 Thus, the RVs measured by the SN do not have the same precision than the RVs calculated using the Normal.
-This can be explained by the fact that in the case of the SN, variations in the asymmetry parameter $\gamma_1$ induce variations in the SN RV measured due to the strong correlation between those two parameters.
-Therefore, the errors in $\gamma_1$ propagate to the error in the SN RVs.
+This can be explained by the fact that in the case of the SN, variations in the asymmetry parameter $\gamma$ induce variations in the SN RV measured due to the strong correlation between those two parameters.
+Therefore, the errors in $\gamma$ propagate to the error in the SN RVs.
 \comment{This seems to be the case in all your stars. I do not consider a method that delivers errors that are 60\% larger to be a very effective method.}
@@
    \centering
-\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
+\includegraphics[height = 4in]{[5]Errors_vs_SNR_all_stars.pdf} 
    \caption{Comparison between the standard errors using the bootstrap analysis and the parameter $noise$ for the RVs, $2.35\times$\emph{noise} for the width, and $2\times$\emph{noise} for the asymmetry parameter.
 Note that for the asymmetry, the error in BIS SPAN is in \kms.
-To be able to compare the errors in $\gamma_1$ and BIS SPAN, we multiplied the error in $\gamma_1$ by the slope of the correlation between $\gamma_1$ and BIS SPAN.}
+To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
    \label{fig:se}
@@
 
-We compared for five stars the difference between the RVs, FWHM and asymmetry (BIS SPAN in the Normal case and parameter $\gamma_1$ in the SN case) as measured we a Normal or a SN fitting to the CCF.
-The $\gamma_1$ parameter is linearly dependant on the BIS SPAN, with always a strong correlation coefficient.
-%To compare $\gamma_1$, that do not have any units, with BIS SPAN expressed in \kms, one has simply to multiply $\gamma_1$ by the slope of the linear dependence between $\gamma_1$ and BIS SPAN. 
+We compared for five stars the difference between the RVs, FWHM and asymmetry (BIS SPAN in the Normal case and parameter $\gamma$ in the SN case) as measured we a Normal or a SN fitting to the CCF.
+The $\gamma$ parameter is linearly dependant on the BIS SPAN, with always a strong correlation coefficient.
+%To compare $\gamma$, that do not have any units, with BIS SPAN expressed in \kms, one has simply to multiply $\gamma$ by the slope of the linear dependence between $\gamma$ and BIS SPAN. 
 The slope of this linear correlation change depending on the star studied. This is probably because the spectral type is different, therefore the effects from stellar activity are different.
@@
 The RVs derived using the SN fitting present a higher sensitivity to stellar activity.
-However, once correcting the RVs from stellar activity using a linear combination of the width and asymmetry parameter of the CCF (FWHM and BIS SPAN in the Normal case, and SN FWHM and $\gamma_1$ in the SN case), the RV residuals in both the Normal and SN case show similar scatter.
+However, once correcting the RVs from stellar activity using a linear combination of the width and asymmetry parameter of the CCF (FWHM and BIS SPAN in the Normal case, and SN FWHM and $\gamma$ in the SN case), the RV residuals in both the Normal and SN case show similar scatter.
 Therefore, the SN fitting does not improve stellar activity correction when using a simple linear combination with the width and asymmetry of the CCF.
@@
 
-When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma_1$ in the SN case) with respect to the RVs (RVs in the Normal case or SN RVs in the SN case), we observe that the correlations are always stronger for the parameters of the SN.
+When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma$ in the SN case) with respect to the RVs (RVs in the Normal case or SN RVs in the SN case), we observe that the correlations are always stronger for the parameters of the SN.
 Therefore, the SN parameters are more sensitive to activity.
-In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of 0.57 between $\gamma_1$ and SN RV, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.21.
+In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of 0.57 between $\gamma$ and SN RV, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.21.
 
@@
 In the case of the errors when using the SN fitting, the precision on the SN RVs is however 60\% worse than for the RVs.
-This comes from the fact that because the asymmetry is accounted for in the SN and because the SN RVs and $\gamma_1$ are strongly correlated, the errors in $\gamma_1$ propagates to the errors in SN RVs.
+This comes from the fact that because the asymmetry is accounted for in the SN and because the SN RVs and $\gamma$ are strongly correlated, the errors in $\gamma$ propagates to the errors in SN RVs.
 This is not so important for SNR $>$ 150 for which the errors are below the \ms precision of HARPS and the \ms variation induced by stellar activity signals even in low activity cases \footnote{As we can see in papers publishing HARPS results using an additional jitter to consider stellar activity noise not accounted for in the \emph{noise} parameter, the extra jitter is always greater than 0.8\ms \citep[e.g.][]{Diaz:2016ab}.}.
@@
 In the case of the CCF width, the error derived when using the Normal or SN fitting are very similar.
-Finally for the asymetry, we see that the error in $\gamma_1$ is $\sim$15\% smaller than the error in BIS SPAN.
+Finally for the asymetry, we see that the error in $\gamma$ is $\sim$15\% smaller than the error in BIS SPAN.
 
@@
 Using the SN to fit CCFs brings a significant improvement in probing stellar activity.
-The correlations between SN RV and SN FWHM, and SN RV and the asymmetric parameter $\gamma_1$ are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
-The RVs derived by the SN are also more sensitive to activity and the precision on the asymmetry measured by $\gamma_1$ is greater than the one on BIS SPAN by $\sim$15\%.
+The correlations between SN RV and SN FWHM, and SN RV and the asymmetric parameter $\gamma$ are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
+The RVs derived by the SN are also more sensitive to activity and the precision on the asymmetry measured by $\gamma$ is greater than the one on BIS SPAN by $\sim$15\%.
 Therefore when searching for rotational periods in the data, or applying Gaussian Processes to account for stellar activity signals, the SN parameters should be used.
@@
 At first glance, one downside of using the SN comes from the RV errors that are greater by 60\% relative to the RV errors measured when considering a Normal.
-This is due to the strong correlation between SN RV and $\gamma_1$ and this can be a problem for low SNR measurements.
+This is due to the strong correlation between SN RV and $\gamma$ and this can be a problem for low SNR measurements.
 However, in the regime of SNR $>$ 150, which is the aim of all RV surveys at high precision, the precision of the SN RVs is below the \ms, which is thus below the instrumental precision of HARPS and below the RV perturbations induced by stellar activity.
@@
 
+\umberto{I suggest to outline here shortly the characteristics of the considered stars. Then we summarize/compare the results presenting Table \ref{table:summaryStars} and finally we show the plots.}
+\umberto{for each star there are always the same $3$ plots: 
+\begin{itemize}
+\item RVs vs. JD
+\item $\gamma$ vs. Bis-Span
+\item Comparison on the correlation between asymmetry parameters (or FWHM) and RV.
+\end{itemize}
+
+Do we need to show all these plots?}
+
+\small{
+\begin{table}[!t]
+\scalebox{0.5}{
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+\hline
+\textbf{Star}          &\textbf{ \# CCFs}  &   \textbf{$\text{R}(\text{SN }\gamma, \text{Bis-Span})$} & \textbf{$\text{slope}(\text{SN }\gamma, \text{Bis-Span})$} &   \textbf{$\text{R}(\text{SN }\gamma, \text{SN mean RV})$} & \textbf{$\text{R}(\text{Bis-Span}, \text{RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{SN mean RV})$}  & \textbf{$\text{R}(\text{FWHM}, \text{RV})$} \\
+\hline
+ $\text{HD}192310  $          &    $1576$    & $0.883$ & $0.812$ & $0.682 (0.655; 0.707)$ & $0.33 (0.285; 0.373)$  & $-0.335 (-0.378; -0.29)$ & $0.677 (0.650; 0.703)$ & $0.475 (0.436; 0.513)$\\
+\hline
+ $\text{HD}10700 $            &    $7928$    & $0.795$ & $0.749$ & $0.436 (0.418; 0.454)$ & $-0.073 (-0.095; -0.0051)$ & $0.127 (0.105; 0.148)$ & $0.291 (0.270; 0.311)$ & $0.529 (0.513; 0.545)$ \\
+\hline
+ $\text{HD}215152 $          &     $273$   &  $ 0.763$ & $0.794$ & $0.571 (0.485; 0.646)$ & $-0.067 (-0.184; 0.052)$  & $0.269 (0.155; 0.376)$ & $0.210 (0.094; 0.321)$ & $-0.138 (-0.253; -0.020)$ \\
+\hline
+ $\text{Corot }7$     &     $173$    &  $0.797$  & $0.64$ & $0.561 (0.450; 0.656)$ & $0.092 (-0.058; 0.238)$ & $-0.335 (-0.228; -0.082)$ & $-0.709 (0.626;0.776)$ & $0.595 (0.489; 0.683)$ \\
+\hline
+\end{tabular}
+}
+\caption{Subset of notable correlations between the asymmetry parameter (and the FWHM) and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.}
+\label{table:summaryStars}
+\end{table}
+}
+
 \subsection{HD192310}  \label{sec:Gl785}
-
-We present now the results of the analysis for the star HD192310 (i.e.
-Gliese 785).
-The dataset consists in $1588$ CCFs.
-Figure \ref{fig:Gliese785:corr.gamma} shows the correlation between $\gamma$ and BIS SPAN to understand the link between those two parameters.
-It is interesting to see that, in this case, the slope of $0.645$ is significantly different from the one found for Alpha Centauri B in Fig.~\ref{fig:alphacent:corr.gamma}.
-\comment{Why is this interesting? You would expect it to be given that this is a different star! If something is interesting you have to point out to the reader why.}
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{[0]HD19231_vs_time.pdf} 
+   \caption{RVs comparison for HD192310 considering a Normal and a SN fitting (using both the mean and the median).}
+   \label{fig:HD192310:RV}
+\end{figure*}
 %
@@
    \centering
-\includegraphics[height = 3in]{HD19231_[2]gamma_vs_bisspan.pdf} 
+\includegraphics[height = 4in]{HD19231_[2]gamma_vs_bisspan.pdf} 
    \caption{Correlation between $\gamma$ and the BIS SPAN for HD192310.}
@@
 \end{figure}
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{HD19231_[4]Comparison_para.pdf} 
+   \caption{Correlation between the asymmetry parameters and the RVs for HD 192310.
+The last two plots show the correlation between the FWHM and the RVs for HD 192310 using respectively the SN and the Normal fits.}
+   \label{fig:Gliese785:corrPlot}
+\end{figure*}
+
+%%%%%%April 5th, 2018
+%%% correction for stellar activity
+%%%%%%
+\iffalse
+We present now the results of the analysis for the star HD192310 (i.e.
+Gliese 785).
+The dataset consists in $1576$ CCFs.
+Figure \ref{fig:Gliese785:corr.gamma} shows the correlation between $\gamma$ and BIS SPAN to understand the link between those two parameters.
+It is interesting to see that, in this case, the slope of $0.812$ is significantly different from the one found for Alpha Centauri B in Fig.~\ref{fig:alphacent:corr.gamma}.
+\comment{Why is this interesting? You would expect it to be given that this is a different star! If something is interesting you have to point out to the reader why.}
 
@@
    \centering
-\includegraphics[height = 6in]{HD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+\includegraphics[height = 4in]{HD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
    \caption{Radial Velocities for HD192310 using the Normal and the Skew Normal fitting before and after correcting the analyses from the stellar activity.}
@@
 The correlation between the CCF width and the RVs is also stronger when fitting a SN rather than a Normal.
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RVs for HD 192310.
-The last two plots show the correlation between the FWHM and the RVs for HD 192310 using respectively the SN and the Normal fits.}
-   \label{fig:Gliese785:corrPlot}
-\end{figure*}
+\fi
+%%%%%%
+%%%
+%%%%%% April 5th, 2018
 
 \subsection{Tau Ceti}  \label{sec:Taucet}
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{[0]TauCeti_vs_time.pdf} 
+   \caption{RVs comparison for Tau Ceti considering a Normal and a SN fitting (using both the mean and the median).}
+   \label{fig:Tau Ceti:RV}
+\end{figure*}
+%
+\begin{figure}[htbp]
+   \centering
+\includegraphics[height = 4in]{HD10700_[2]gamma_vs_bisspan.pdf} 
+   \caption{Correlation between $\gamma$ and the BIS SPAN for Tau Ceti.}
+   \label{fig:Tau:corr.gamma}
+\end{figure}
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{HD10700_[4]Comparison_para.pdf}  
+   \caption{Correlation between the asymmetry parameters and the RVs for Tau Ceti.
+The last two plots show the correlation between the FWHM and the RVs for Tau Ceti using respectively the SN and the Normal fits.}
+   \label{fig:Tau:corrPlot}
+\end{figure*}
+
+%%%%%%April 5th, 2018
+%%% correction for stellar activity
+%%%%%%
+\iffalse
 \comment{If you are going to refer to the star as HD 10700 you should use the same name in the section heading.}
 The analysis of the star HD10700 (i.e.
-Tau Ceti) consists of $7963$ CCFs.
-Figure \ref{fig:Tau:corr.gamma} shows the relationship between $\gamma$ and the BIS SPAN, with a correlation of $0.605$ and a slope of the fitted line of $0.566$.
+Tau Ceti) consists of $7928$ CCFs.
+Figure \ref{fig:Tau:corr.gamma} shows the relationship between $\gamma$ and the BIS SPAN, with a correlation of $0.795$ and a slope of the fitted line of $0.749$.
 Although still significant, we see that this correlation is weaker than in the case of Alpha Centauri B or HD192310.
@@
 This is especially true since HD 10700 is a late F-type star and thus may have a different activity behavior from a G2 star.}
-%
-\begin{figure}[htbp]
-   \centering
-\includegraphics[height = 3in]{HD10700_[2]gamma_vs_bisspan.pdf} 
-   \caption{Correlation between $\gamma$ and the BIS SPAN for Tau Ceti.}
-   \label{fig:Tau:corr.gamma}
-\end{figure}
 
@@
    \centering
-\includegraphics[height = 6in]{HD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+\includegraphics[height = 4in]{HD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
    \caption{RVs for HD10700 using the Normal and the Skew Normal fitting before and after correcting for stellar activity.}
@@
 The correlation between the FWHM and the RVs of HD10700 for the SN and the Normal are similar.
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RVs for Tau Ceti.
-The last two plots show the correlation between the FWHM and the RVs for Tau Ceti using respectively the SN and the Normal fits.}
-   \label{fig:Tau:corrPlot}
-\end{figure*}
+\fi
+%%%%%%
+%%%
+%%%%%% April 5th, 2018
 
 \subsection{HD215152}  \label{sec:HD215152}
-
-The analysis of the star HD215152 consists in 284 CCFs and Figure \ref{fig:HD215152:corr.gamma} shows that the slope of the linear regression between $\gamma$ and the BIS SPAN is $0.591$ with a Pearson correlation coefficient of $0.767$.
-
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{[0]HD21515_vs_time.pdf} 
+   \caption{RVs comparison for HD215152 considering a Normal and a SN fitting (using both the mean and the median).}
+   \label{fig:HD215152:RV}
+\end{figure*}
+%
 \begin{figure}[htbp]
    \centering
-\includegraphics[height = 3in]{HD21515_[2]gamma_vs_bisspan.pdf} 
+\includegraphics[height = 4in]{HD21515_[2]gamma_vs_bisspan.pdf} 
    \caption{Correlation between $\gamma$ and the BIS SPAN for HD 215152.}
@@
 \end{figure}
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{HD21515_[4]Comparison_para.pdf}  
+   \caption{Correlation between the asymmetry parameters and the RVs for HD 215152.
+The last two plots show the correlation between the FWHM and the RVs for HD 215152 using respectively the SN and the Normal fits.}
+   \label{fig:HD215152:corrPlot}
+\end{figure*}
+
+%%%%%%April 5th, 2018
+%%% correction for stellar activity
+%%%%%%
+\iffalse
+The analysis of the star HD215152 consists in $273$ CCFs and Figure \ref{fig:HD215152:corr.gamma} shows that the slope of the linear regression between $\gamma$ and the BIS SPAN is $0.591$ with a Pearson correlation coefficient of $0.767$.
 
@@
    \centering
-\includegraphics[height = 6in]{HD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+\includegraphics[height = 4in]{HD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
    \caption{Radial Velocities for HD 215152 using the Normal and the Skew Normal fitting before and after correcting the analyses from the stellar activity.}
@@
 The BIS SPAN is however not significant.
-For the SN case, it is the contrary, $\gamma_1$ is significant in explaining the SN RV variations, while the FWHM and the intercept are not.
+For the SN case, it is the contrary, $\gamma$ is significant in explaining the SN RV variations, while the FWHM and the intercept are not.
 When looking at the value of
@@
 The SN FWHM or the FWHM are not significantly correlated to the SN RVs or the RVs.
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RVs for HD 215152.
-The last two plots show the correlation between the FWHM and the RVs for HD 215152 using respectively the SN and the Normal fits.}
-   \label{fig:HD215152:corrPlot}
-\end{figure*}
+\fi
+%%%%%%
+%%%
+%%%%%% April 5th, 2018
 
@@
 \subsection{Corot-7}  \label{sec:Corot7}
-
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{[0]LRa01_E_vs_time.pdf} 
+   \caption{RVs comparison for Corot-7 considering a Normal and a SN fitting (using both the mean and the median).}
+   \label{fig:corot7:RV}
+\end{figure*}
+%
+\begin{figure}[htbp]
+   \centering
+\includegraphics[height = 4in]{LRa01_E_[2]gamma_vs_bisspan.pdf} 
+   \caption{Correlation between $\gamma$ and the BIS SPAN for Corot-7.}
+   \label{fig:Corot7:corr.gamma}
+\end{figure}
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{LRa01_E_[4]Comparison_para.pdf} 
+   \caption{Correlation between the asymmetry parameters and the RVs for Corot-7.
+The last two plots show the correlation between the FWHM and the RVs for Corot-7 using respectively the SN and the Normal fits.}
+   \label{fig:Corot7:corrPlot}
+\end{figure*}
+%
+
+%%%%%%April 5th, 2018
+%%% correction for stellar activity
+%%%%%%
+\iffalse
 The final star considered is Corot-7 which has low signal to noise. 
 \comment{A star cannot have a "low signal to noise" only data has that. And what data are you referring to photometry (from CoRoT) RVs, from HARPS? You need to be clear.}
+
 A total of $180$ CCFs have been analysed and Fig.~\ref{fig:Corot7:corr.gamma} shows the correlation between $\gamma$ the BIS SPAN with a linear regression slope of $0.596$.
@@
 Note: there is a correlation between two quantities which is not expressed in the original text.}
-%
-\begin{figure}[htbp]
-   \centering
-\includegraphics[height = 3in]{LRa01_E_[2]gamma_vs_bisspan.pdf} 
-   \caption{Correlation between $\gamma$ and the BIS SPAN for Corot-7.}
-   \label{fig:Corot7:corr.gamma}
-\end{figure}
 
@@
 In Table~\ref{table:Corot7:test}, we see that in the Normal and the SN analyses, the intercept, the width and the asymmetry of the CCF (measured with FWHM or SN FWHM and $\gamma$ or BIS SPAN) can explain part of the RV variability measured.
-Looking at $R^2$, the RVs derived with the SN present like for all the stars in this paper a stronger correlation with $\gamma_1$ and SN FWHM than the RV derived in the Normal case.
-
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{LRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+Looking at $R^2$, the RVs derived with the SN present like for all the stars in this paper a stronger correlation with $\gamma$ and SN FWHM than the RV derived in the Normal case.
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{LRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
    \caption{Radial velocities for Corot-7 using the Normal and the Skew Normal fitting before and after correcting the analyses from the stellar activity.}
@@
 These significant correlations for the SN parameters and non-significant for the Normal parameters suggest that for low signal to noise measurement, using the SN fitting improves our power in detecting stellar activity signals.
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RVs for Corot-7.
-The last two plots show the correlation between the FWHM and the RVs for Corot-7 using respectively the SN and the Normal fits.}
-   \label{fig:Corot7:corrPlot}
-\end{figure*}
+\fi
+%%%%%%
+%%%
+%%%%%% April 5th, 2018
 

### 2018-04-13 manuscript.tex
Add files via upload
updated manuscript

@@
 The CCF is a function of RV, and the RV corresponding to the minimum of the CCF is the estimated RV for that spectrum.
-However, this would give a noisy estimate so first a normal density shape is fitted to the CCF, and then the estimated mean of the normal density is used as the estimate of the RV.
+However, this would give a noisy estimate so first a Normal density shape is fitted to the CCF, and then the estimated mean of the Normal density is used as the estimate of the RV.
 The full width at half maximum (FWHM) of the Normal fit is also used as an indicator of spectral line asymmetry.
@@
 The strength of the asymmetry depends on the velocity of the convection, approximatively 300\ms for the Sun, but also on the formation depth of spectral lines \citep{Gray-2009}.
-Since the CCF is an average of all the spectral lines, some strongly asymmetric and some not, its asymmetry is rather small, which is why a normal distribution can be an appropriate model for the CCF.
+Since the CCF is an average of all the spectral lines, some strongly asymmetric and some not, its asymmetry is rather small, which is why a Normal distribution can be an appropriate model for the CCF.
 This small asymmetry modifies however slightly the estimated RVs of the star, reducing the accuracy of the measurement, but if this asymmetry does not vary with time, the precision is kept.
@@
 Maybe that is what you mean here, but it is not clear from what is written.}
-In addition, the normal distribution cannot take into account the natural asymmetry of the CCF, leaving correlated noise in the residuals, which also complicates the determination of errors.
+In addition, the Normal distribution cannot take into account the natural asymmetry of the CCF, leaving correlated noise in the residuals, which also complicates the determination of errors.
 We propose to overcome these problems by fitting a SN (SN) distribution to the CCF, which naturally includes a skewness parameter \citep[][]{Azzalini1985}.
+
+\umberto{We considered CCFs having SNR larger than 10.}
 
@@
 \todo{This paragraph will need to be updated once the rest is finished.} The paper is organized as follow.
-In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  show that the SN density is a better representation of observed CCF than a normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
+In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  show that the SN density is a better representation of observed CCF than a Normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
 In Sec.~\ref{sec:31} we present a simple model to correct for stellar activity.
@@
 \section{The Skew Normal distribution} \label{sec:2}
-\jessi{I re-wrote this section to hopefully address the referees concerns along with removing elements that are not needed}
-\comment{17) I cannot find where R, R+, x and w were defined. It is a common practice when you introduce variables in a paper, these should all be defined.
-18) Paragraph 4: "By using the so-called direct parameterization (DP) defined in Eq.
-2 problems with parameters estimation arise in the evaluation of the likelihood function in a neighborhood of $\alpha$ = 0, where the presence of a stationary point complicates the achievement of the maximum likelihood or least squares estimates."
-A poorly constructed sentence that simply confuses me! The authors are trying to say too many things in one sentence which loses the reader.
-19) To be honest, I could not follow all the mathematics. I really would have to read the referenced material, but I had little time. Maybe the details can be put in an appendix?}
 
-The Skew Normal (SN) distribution is a class of probability distributions which includes the normal distribution as a special case \citep{Azzalini1985}.
-The SN distribution has, in addition to a location and a scale parameter analogous to the normal distribution's mean and standard deviation, a third parameter which describes the asymmetry, or the skewness, of the distribution.
-
+The Skew Normal (SN) distribution is a class of probability distributions which includes the Normal distribution as a special case \citep{Azzalini1985}.
+The SN distribution has, in addition to a location and a scale parameter analogous to the Normal distribution's mean and standard deviation, a third parameter which describes the asymmetry, or the skewness, of the distribution.
 Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $Y = y$ can be written as
@@
 \end{equation}
-where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a \emph{standard} normal distribution\footnote{A standard normal distribution is a normal distribution with a mean of 0 and a standard deviation of 1.}
+where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a \emph{standard} Normal distribution\footnote{A standard Normal distribution is a Normal distribution with a mean of 0 and a standard deviation of 1.}
  and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN.
 We then write $Y \sim SN(\xi, \omega^{2}, \alpha)$ to mean that the random variable $Y$ follows the noted SN distribution.
-Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Figure \ref{fig:SN.plot}.
-A usual normal distribution is the special case of the SN distribution when the skewness parameter, $\alpha$, is equal to 0.\footnote{This can be seen from Equation~\eqref{def:snd_gen}.
-If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0)$; this is the the probability a standard normal random variable is less than or equal to 0, which is $0.5$.
-The $0.5$ cancels with the $2$ in the denominator and what remains is the usual normal density, $\frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$}
+Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Fig.~ \ref{fig:SN.plot}.
+A usual Normal distribution is the special case of the SN distribution when the skewness parameter, $\alpha$, is equal to 0.\footnote{This can be seen from Equation~\eqref{def:snd_gen}.
+If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0)$; this is the the probability a standard Normal random variable is less than or equal to 0, which is $0.5$.
+The $0.5$ cancels with the $2$ in the denominator and what remains is the usual Normal density, $\frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$}
 %
@@
    \centering
-\includegraphics[height = 3in]{Skew_normal_densities_jjck.pdf} 
+\includegraphics[height = 3in]{Skew_Normal_densities_jjck.pdf} 
    \caption{Density function of a random variable $Y \sim SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$, and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
-Note that the solid black line has an $\alpha = 0$ making it a normal distribution.   
+Note that the solid black line has an $\alpha = 0$ making it a Normal distribution.   
    }
@@
 \end{figure}
-
+%
 For reasons related to the interpretation of the parameters in Equation~\eqref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used, which is referred to as the \emph{centered parametrization} (CP).
@@
 \end{equation}
+%
 where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$.
@@
 \ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution.
-For the $\alpha$ values used in Figure~\ref{fig:SN.plot}, the corresponding values of $\mu$, $\sigma^2$, $\gamma$ are displayed in Table~\ref{tab:cp_values}.
-In particular, $\mu$ and $\sigma^2$ are the actual mean and the variance of the distribution (rather than simply a location and scale parameter), and $\gamma$ becomes an index for evaluating the asymmetry of the SN.
+For the $\alpha$ values used in Fig.~~\ref{fig:SN.plot}, the corresponding values of $\mu$, $\sigma^2$, $\gamma$ are displayed in Table~\ref{tab:cp_values}.
+In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution (rather than simply a location and scale parameter), and $\gamma$ becomes an index for evaluating the asymmetry of the SN.
+
+Beyond the mean of the SN, it is convenient to introduce a second location parameter that will be largely used in the analyses: the median. The median of the SN is defined as that value $m$ such that 
+%
+\begin{equation} \label{eq:snmed}
+\int_{-\infty}^{m} SN(y;\xi, \omega, \alpha) = \frac{1}{2},
+\end{equation}
+%
+where $SN(y;\xi, \omega, \alpha)$ follows Equation \ref{def:snd_gen}.\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}
+
 %% Requires the booktabs if the memoir class is not being used
@@
    \end{tabular}
-   \caption{CP values, $(\mu, \sigma^2, \gamma)$, corresponding to the $\alpha$ values from Figure~\ref{fig:SN.plot} (with location parameter $\xi = 0$ and scale parameter $\omega = 1$) using Equation~\eqref{eq:snd_cp}.
+   \caption{CP values, $(\mu, \sigma^2, \gamma)$, corresponding to the $\alpha$ values from Fig.~~\ref{fig:SN.plot} (with location parameter $\xi = 0$ and scale parameter $\omega = 1$) using Equation~\eqref{eq:snd_cp}.
 Values are rounded to three decimal places.}
@@
 %
-Further details about the parametrization from Equation~\eqref{def:snd_gen} (called the \emph{Direct Parametrization}), the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
+Further details about the parametrization from Equation~\eqref{def:snd_gen} (called \emph{Direct Parametrization} or DP), the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
 
@@
 where C is a constant fitting the continuum of the CCF \jessi{The C is unclear to me - can more intuition be added here?
-Are C and A considered known?}, A is an amplitude parameter, and $y_1, \ldots, y_n$ are the set of RV's considered for the CCF.
+Are C and A considered known?}, A is an unknown amplitude parameter, and $y_1, \ldots, y_n$ are the set of RV's considered for the CCF.
 Note that the CCF is expressed in flux as a function of the lag of the cross-correlation template, expressed in RV.
 
-Since each point of the CCF has a measurement error, this information is included in the specification of the SN distribution by introducing the following heteroskedastic function for the variance,
-%
-\begin{equation}
-\text{var}(Y_{i})=\sigma^{2}+\sigma_{i}^{2}, \quad i = 1, \dots, n,
-\label{eq:vaf}
-\end{equation}
-%
-where $\sigma_{i}$ represents the measurement error for each point of the CCF.
-By using Eq.
-\ref{eq:vaf} we can interpret the parameter $\sigma^{2}$ \jessi{this is going to be confusing given the CP parametrization of the SN - one needs to be changes} as a measure of the pure variability present in the evaluation of the CCF.
-However, although useful for estimating correct error bars in the case where the different $\sigma_{i}$ do not include all systematics, this heteroskedastic function only considers Gaussian distributed residuals.
-\jessi{the previous statement is unclear}
-%
-
-The CCF is the result of a cross correlation so the residuals of a Normal or a SN fit are expected to show correlated noise.
-To investigate this issue, we considered example CCFs from the star Tau Ceti.
-The CCFs were modeled using a normal or a SN shape, and assuming independent normally-distributed noise around the modeled shape.
-%
-We then subtracted the median of the residuals (the original data minus the fit function) obtained for all CCFs before performing a second round of fitting.
-The result of this procedure is illustrated in Figure~\ref{fig:Residual.comparison}.
-The lower left panel displays the residuals of a simple fit of a normal or a SN distribution, which appear to be strongly correlated.
-%
-After removing the median of the residuals, in the lower right panel, the final residuals of the SN procedure have almost no apparent correlation, while the final residuals of the Normal procedure still present a small systematic component.
-This seems to be due to the asymmetric nature of the CCF (see Section~\ref{intro}), which is not captured in a symmetric distribution like the normal distribution.
-This exercise highlights that the SN density shape better captures the shape of a CCF compared to a normal density shape.
+Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution can better catch this aspect, together with other changes in asymmetry, respect the Normal fit.
+To check this assumption, we compared the CCF residuals after fitting a Normal and a SN distribution for 2 stars.
+The first star is Alpha Centauri b, whose CCFs have high signal to noise ratio (SNR).
+The second star is Corot-7, whose CCFs have low SNR.
+Fig.~ \ref{fig:Residual.comparison} shows that the SN seems to be a slightly better model to explain the shape of the CCF, in particular as the SNR decreases.
 %
@@
    \centering
-\includegraphics[height = 6in]{[1]Plot_Fitting_and_Residuals_2run.pdf} 
-   \caption{Comparison between the Normal and the SN procedures for modeling a collection of CCFs for the star Tau Ceti.
-Two stages of modeling are carried out with the first stage results displayed in the left column and the second stage in the right column.
-   The first run corresponds to fitting a normal or a SN shape to the raw CCF.
-The second run corresponds to fitting the same shape to the CCF after removing the median of all the residuals obtained in the first run.
-The SN residuals of the second run present minimal correlations, whereas the normal residuals present still a clear systematic component.}
+\includegraphics[height = 2.5in]{[1]HD128621Residuals.pdf} 
+\includegraphics[height = 2.5in]{[1]LRa01_E2Residuals.pdf} 
+   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCFs of the star Alpha Centauri b (left) and Corot-7 (right).
+The results are comparable looking at the residuals corresponding to the tails of the CCF but the SN fit leads to slightly better results in the center of the CCF for both the stars.
+As the signal to noise decreases, as happens when analyzing the star Corot-7, the SN distribution leads to better residuals respect using the Normal.}
     \label{fig:Residual.comparison}
 \end{figure*}
-%When using the least squares estimate for fitting the CCF with the SN distribution, we have to take into account the stationary problem in $\gamma=0$ due to the presence of the function $sign(\gamma)$ in Equation (\ref{eq:2}).
-Depending on the initial values of the numerical minimization for the least squares estimate of $\gamma$, the presence of this stationary point when evaluating $\gamma$ can lead to an incorrect estimation of the asymmetry parameter of the SN.
-In order to resolve this problem, we implemented two functions for retrieving the best least squares solution.
-In the first function we allowed for only positive solutions of $\gamma_1$ (with an upper limit of $0.995$), while in the second function only negative solutions are allowed (with a lower limit of $\gamma= -0.995$).
-The chosen solution is the estimate which has smallest residuals.
+%
 
-In the following of the paper, we define the RV as the mean of the normal or the mean of the SN (defined as SN RV).
-For the width of the CCF, we use the FWHM of the Normal, which is $2\sqrt(2\ln2)\sigma$.
-The width of the SN, SN FWHM, is defined in the same way\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}.
-In the Normal case, there is not an asymmetric parameter so we use BIS SPAN.
-This will be compared to the asymmetric parameter $\gamma_1$ of the SN.
-\jessi{Why use FWHM at all?
-Why not just use the standard deviation since the FWHM just includes a multiplicative factor that is the same for all of them.}
-
-\section{Effect of stellar activity on radial velocities and correction} \label{sec:31}
+\subsection{Effect of stellar activity on the CCF} \label{sec:31}
 
@@
 Stellar activity, however, does not produce a blueshift or redshift of the spectra, but can create a spurious RV signal by modifying the shape of spectral lines.
-To track changes in line shape, the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} are often used, \jessi{citations are needed here} which provide information on the average width and asymmetry of the CCF.
+To track changes in line shape, the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} are often used, which provide information on the average width and asymmetry of the CCF \citep{Hatzes1996, fiorenzano2005line, Queloz-2001}.
 A strong correlation between the estimated RVs and one or more of these parameters is a sign that the estimated RVs may be contaminated by stellar activity.
-
 To test the strength of the correlation between RVs and the different activity indicators, we calculated the Pearson correlation coefficient, $R$.
@@
 
-To correct for stellar activity signals, it is common to consider a linear combination of the RVs with the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case):
-\comment{Is this really common?
-I am not aware of it having wide use in the community.
-If so, references would support this.
-The authors have to distinguish what their research group and collaborators do from what the rest of the community does.}
-%
-\begin{equation}
-RV= \beta_{0} + \beta_{1}  \gamma + \beta_{2} FWHM + \epsilon,
-\label{eq:RV:correction}
-\end{equation}
-%
-where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ is the identity matrix). 
-\comment{Is this expression just for the RV from activity alone, or the measured RV from the star (contribution of all phenomena)?
-If it is just activity, you should put a subscript otherwise the readers will be confused.
-In the text you refer to the variable ?1, but Eq.
-9 has no subscript in ?.
-You give one equation for Normal and SN, but in the text you state these variables have to be replaced by such and such when using SN, etc.
-It will be less confusing if you simply have two equations, one for Normal and one for SN and with their respective variables.}
-When the Normal fit is used, the parameter $\gamma_1$ is replaced by the BIS SPAN and SN FWHM by FWHM.
-In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,1,2$.
-\jessi{the estimated values and p-values of the $\beta$'s does \underline{not} show goodness of fit.}
-The level for not rejecting the null hypothesis is fixed equal to $0.05$.
-Pearson correlation coefficient $R^{2}$ is considered for explaining how well this linear combination explains the variability of the RVs of the star due to stellar activity.
-\jessi{$R^2$ is the coefficient of determination, and this should be explained better because it is not commonly used in astronomy as an assessment of the amount of variability explained by the model.}
+In the following of the paper, we define RV as the mean of the Normal.
+Concerning the fit of the CCF using the SN, we present at first $2$ indicators that define the RV of the star: the mean of the SN, defined as SN mean RV and the median of the SN, defined as SN median RV (i.e.
+looking at Equation \eqref{eq:snmed}, $m$ = SN median RV).
+We will discuss advantages and limits for both these choices in the examples.
+For the width of the CCF, we use the FWHM of the Normal, which is $2\sqrt(2\ln2)\sigma$.
+The width of the SN, SN FWHM, is defined in the same way\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}.
+Being a Normal distribution symmetric, there is not such a parameter that evaluates the asymmetry of the distribution, so the BIS SPAN is used.
+This will be compared to the asymmetric parameter $\gamma$ of the SN, called SN GAMMA.
 
@@
 \section{Real data applications} \label{sec:4}
-\jessi{I suggest we include one real-date application (whichever is used in \S\ref{sec:soap_real} (Alpha Centauri B?) and then add the other examples to an appendix}
 
-In this Section we present the analyses of five stars comparing the result of fitting a CCF using the SN distribution defined in Section \ref{sec:3} versus the Normal approach.
-
-A comparison with the results obtained by the classic approach is done, where the RVs of the star are estimated by the mean of the Normal distribution used to fit the CCF along with the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}.
+In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN distribution defined in Section \ref{sec:3} versus the Normal approach.
+Other 4 stars have been analyzed with the proposed methods and details can be found in the Appendix \ref{appendix}.
+A comparison with the results obtained by the classic approach is done, where the RVs of the star are estimated by retrieving the mean of the Normal distribution used to fit the CCF, along with the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}.
+The latter parameters are calculated separately from the Normal fit that leads to the RV of the star.
 
@@
 
-Alpha Centauri B $1816$ CCFs in 2010 are considered.
+A total of $1808$ CCFs measured in $2010$ have been analysed from the star Alpha Centauri B.
 Several measurement in 2010 are contaminated by light from Alpha Centauri A.
 To remove contaminated spectra and thus CCFs, we performed the same selection as presented in \citet{Dumusque-2012}.
+Moreover, as noted in \citet{Dumusque-2012} and \citet{Thompson-2017}, this dataset presents a strong stellar activity signal.
 
 We begin by evaluating the correlation between $\gamma$ and the BIS SPAN.
-In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.933$ and a strong Pearson correlation coefficient of $0.958$.
-\jessi{It would be good to explain why you care about this.}
+In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.99$ and a strong Pearson correlation coefficient of $0.96$.
+This comparison is useful because $\gamma$ is an adimensional parameter taking information about the asymmetry of the SN while the BIS SPAN, beyond this, has got unit of measure of \kms.
+In other words, by using Fig.~\ref{fig:alphacent:corr.gamma}, it is possible to provide to $\gamma$ a physical meaning.
 %
@@
 \includegraphics[height = 3in]{HD12862_[2]gamma_vs_bisspan.pdf} 
-   \caption{Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.}
+   \caption{Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
+Because $\gamma$ is adimensional, retrieving the slope between $\gamma$ and the BIS SPAN, which is expressed in \kms, allows us to provide physical meaning to $\gamma$.}
    \label{fig:alphacent:corr.gamma}
 \end{figure}
+%
 
-Figure \ref{fig:alphacent:diff:RV} shows the comparison between the RVs retrieved using the SN shape and the ones obtained with the normal shape.
-This data set for Alpha Centauri B, used in \citet{Dumusque-2012} and \citet{Thompson-2017} \jessi{It seems that this should be mentioned at the beginning of this section}, present a strong stellar activity signal.
-We see that the RVs measured by the SN fitting show more variations than the RVs measured by the Normal fitting.
-\comment{This is not at all clear from the figure. Is there a way to quantify this?}
-The SN fit is therefore significantly more sensitive to stellar activity. 
+Fig.~ \ref{fig:alphacent:diff:RV} shows the comparison between the RVs retrieved using the SN shape and the ones obtained with the Normal shape.
+It is possible to appreciate the presence of a strong stellar activity signal, as expected \citep{Dumusque-2012,Thompson-2017}.
+When using SN mean RV, it is possible to observe more variations than the one present in the RVs measured by the Normal fitting.
+\comment{This is not at all clear from the figure.
+Is there a way to quantify this?}This happens because the mean of the SN is more sensitive to stellar activity.
+In fact, because the SN includes an asymmetry parameter, a RV defined as SN mean gets more shifted in the direction of the asymmetry induced by stellar activity.
+On the other hand, when using SN median RV, smaller variations in RV are caused by changes in the asymmetry of the CCF, because this second location parameter is a more robust indicator than the mean.
+The bottom plot of Fig.~ \ref{fig:alphacent:diff:RV} captures this aspect.
+Both indicators can be used to capture and summarise the different information available in the CCF, as will be shown in the remainder of this work.
 \comment{How can you be sure that the higher scatter in your measurement error is not simply due to the fact that you have an inferior measurement technique?
 This can be answered by isolating the RV contribution from activity (from the asymmetry).
-Is this random (noise) or is there structure (activity).}
-\comment{If you are interested in using the RV signal due to activity to measure the rotation period, effects of activity, etc., why not just show the RVs due to the activity signal alone.?}
-This can be explained by the fact that because the SN includes an asymmetry parameter, the RV defined as the mean of the SN distribution gets more shifted in the direction of the asymmetry induced by stellar activity.
-
-We show the correction of stellar activity using Eq.
-\ref{eq:RV:correction} in Fig.~\ref{fig:alphacent:correctionRV}.
-We see that after correcting for stellar activity, the rms of the RV residuals in the Normal and SN analysis are extremely similar.
-However, we note that when using the SN analysis, the correction is more important.
-This is confirmed by the statistical tests on the significance of the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ whose results are summarized in Table \ref{table:alfa:test}.
-The intercept and both the variables $\gamma$ and SN FWHM are necessary for correcting the RVs retrieved using a SN and Normal fitting.
-The comparison of $R^2$ shows as well that the SN case accounts for a higher percentage of  variability in RVs.
-
+Is this random (noise) or is there structure (activity).} \comment{If you are interested in using the RV signal due to activity to measure the rotation period, effects of activity, etc., why not just show the RVs due to the activity signal alone.?}
+%
 \begin{figure*}[htbp]
    \centering
-\includegraphics[height = 6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
-   \caption{RVs and RV differences for Alpha Centauri B considering a Normal and a SN fitting.}
+\includegraphics[height = 3in]{HD12862_[2]RadialVelocityDifferences.pdf} 
+   \caption{(top) RVs as function of Julian Day for Alpha Centauri b.
+The RVs are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses).
+(bottom) RV differences between Normal RV and SN mean RV (black circles) and between Normal RV and a SN median RV (cyan crosses).}
    \label{fig:alphacent:diff:RV}
 \end{figure*}
+%
 
+Similar to \citet{Figueira-2013}, we compare the correlation between the different activity indicators and the RVs of the star in Fig.~\ref{fig:alphacent:corrPlot}.
+The correlation between $\gamma$ and SN mean RV and the correlation between $\gamma$ and SN median RV are much stronger than the correlation calculated between the other asymmetry parameters and their corresponding RVs.
+In particular the correlation between $\gamma$ and SN mean RV is almost twice the correlation between the other asymmetry parameters and their corresponding RVs.
+
+Because the median is a more rubust index than the mean, the correlation between $\gamma$ and SN median RV is not as large as the correlation between $\gamma$ and SN mean RV, but it is nonetheless $1.5$ times larger than the correlation between the other common asymmetry parameters and their corresponding RVs.
+In other words, changes in the asymmetry of the CCF are better captured when using the SN mean RV.
+The correlation between FWHM and the RVs, either by using SN mean RV or SN median RV, is as well stronger when fitting a SN distribution rather than a Normal.
+All the correlations are statistically different from $0$.
+%
 \begin{figure*}[htbp]
    \centering
-\includegraphics[height = 6in]{HD12862_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{RVs of Alpha Centauri B using a Normal and a SN fitting before and after correcting for stellar activity using Eq. \ref{eq:RV:correction}.
- \comment{Fig 5. The differences in the results of the two methods appear negligible to me}
-   }
-   \label{fig:alphacent:correctionRV}
-\end{figure*}
-
-\begin{table}[!t]
-\begin{tabular}{|c|c|c|}
-\hline
-Parameter          & Normal Fitting         &   Skew Normal Fitting \\
-\hline
-$\beta_{0}$            &    $0.0066$    & $2.29e-11$ \\
-\hline
-$\beta_{1}$            &    $0.022$    & $2.22e-16$ \\
-\hline
-$\beta_{2}$            &     $2.22e-16$   &  $ 2.22e-16 $ \\
-\hline
-$R^{2}$      &     $0.49$    &  $0.77$   \\
-\hline
-\end{tabular}
-\caption{\textbf{Alpha Centauri B}: Evaluation of the linear combination used for correcting the RVs from stellar activity, according to Eq.
-\ref{eq:RV:correction}.
-The p-values for the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ for both the methodologies are summarized, as well as the $R^2$.
-Although more significant for the SN, all parameters are useful in explaining the variability of the RVs of the star.
-The evaluation of the $R^2$ shows how the linear combination better explains the variability in RVs due to stellar activity coming from the SN analysis.}
-\label{table:alfa:test}
-\end{table}
-
-We compare the correlation between the different activity indicators and the RVs of the star in Fig.~\ref{fig:alphacent:corrPlot}.
-The correlation between $\gamma_1$ and RVs is much stronger, almost twice, than the correlation calculated between the other asymmetry parameters and their corresponding RVs.
-The correlation between FWHM and the RVs is as well stronger when fitting a SN distribution.
-All the correlations are statistically different from $0$.
-
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD12862_[4]Comparison_para.pdf}  
+\includegraphics[height = 3in]{HD12862_[4]Comparison_para.pdf}  
    \caption{Correlation between the asymmetry parameters and the RVs for Alpha Centauri B.
-The last two plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN and the Normal fits.}
+The last three plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN (SN mean RV and SN median RV) and the Normal fits.}
    \label{fig:alphacent:corrPlot}
 \end{figure*}
+%
 
-%By looking closer to the data in Fig.~\ref{fig:alphacent:clusters}, we saw that there are three distinct temporal clusters in the Alpha Centauri B measurements and those clusters have a different linear relationship between $\gamma_1$ and RVs (and also SN FWHM and RVs, though not displayed here).
-When considering Eq.
-\ref{eq:RV:correction} and the subsequent inferences, this clustering is not accounted for in the model.
-A slightly more general linear model that allows for different intercepts and different slopes for the three clusters for $\gamma_1$ and SN FWHM can be considered.
-Adjusting the RVs for stellar activity using this expanded model produces the corrected radial velocities displayed in the left plot of Fig.~\ref{fig:alphacent:clusters_residuals}.
-Those corrected RVs are different from those displayed in the lower left plot of Fig.~\ref{fig:alphacent:correctionRV} (which apply the correction derived from Eq.
-\ref{eq:RV:correction}); the right plot of Fig.~\ref{fig:alphacent:clusters_residuals} displays the difference between the two sets of corrected RVs.
-The long-term trend can be explained by the fact that the RV drift induced by the companion Alpha Centauri A is not well corrected, however the shorter-term variations show that stellar activity varies as a function of time, with spots and faculae evolving, and therefore modifies the dependence of the RVs with respect to $\gamma_1$ and SN FWHM.
-These temporal variations is something that we want to explore more, however this work presents a significant effort that we want to address in a future paper.
+Both the proposed indicators coming from the SN distribution have desirable and undesirable behaviors: the SN mean RV better catches changes in the asymmetry of the CCF but the resulting set of RVs ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Section \ref{sec:31}.
+When using SN median RV, the final set of radial velocity is less affected by those spurious shifts caused by stellar activity, but at the same time this indicator is not able to catch as well as SN mean RV changes in the shape of the CCF.
+Anyway, both SN mean RV and SN median RV are useful to catch different aspects of the CCF and our suggestion is to use SN mean RV when interested to retrieve information about changes in the shape of the CCF.
+In order to provide a set of RVs containing the smallest amount of spurious contamination imputable to stellar activity, our suggestion is instead to use SN median RV.
 
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[width = 6in]{AlphaCenB_clusters.pdf}  
-%   \caption{The RVs as a function of time (left) and the RVs plotted against $\gamma_1$ (right) with colors and plot symbol according to its temporal cluster assignment for Alpha Centauri B.
-The RVs are expressed in \ms.}
-%   \label{fig:alphacent:clusters}
-%\end{figure*}
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[width = 6in]{AlphaCenB_clusters_residuals.pdf}  
-%   \caption{The RV for Alpha Centauri B corrected for stellar activity using the SN fit and accounting for the temporal clusters (left), and the difference between those values on in the left plot and the analogous values without accounting for the temporal clusters (right) which are displayed in the lower left plot of Figure~\ref{fig:alphacent:correctionRV}.
-The RVs are expressed in \ms.}
-%   \label{fig:alphacent:clusters_residuals}
-%\end{figure*}
+In the next Section we further motivate the reasons for defining as RV the median of the SN by retrieving the standard errors associated with the RV defined as the mean of the Normal, SN mean and SN median.
 
@@
 
+%%%%%% April 13th, 2018
+%%% in the new Analyses we do not use the noise parameter
+%%%%%%
+\iffalse
 The HARPS reduction pipeline gives the pure photon-noise error estimate on the RVs.
@@
 Then \emph{noise} is associated to the RV error, $2\times$\emph{noise} to the BIS SPAN error and $2.35\times$\emph{noise} to the FWHM error.
+\fi
+%%%%%%
+%%%
+%%%%%% April 13th, 2018
 
-In this section, we do a bootstrap analysis to measure the standard errors on the RVs or SN RVs, the FWHM or SN FWHM, and BIS SPAN or $\gamma_1$.
+In this section, we perform a bootstrap analysis to measure the standard errors associate to the RVs, SN mean RVs and SN median RV, the FWHM or SN FWHM and the BIS SPAN or $\gamma$.
 Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
@@
 
-In the top plots of Fig.~\ref{fig:se} we show the different errors for the RVs, the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels.
+In the top plots of Fig.~\ref{fig:se} we show the different errors for the RV, either defined as mean of the Normal (red triangles), mean of the SN (black circles) or median of the SN (cyan crosses), the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels.
 The parameter SN50 corresponds to the SNR in order 50, which corresponds to a wavelength of 550\,nm.
-In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN or the Normal and the \emph{noise} parameter extracted from the HARPS reduction pipeline.
+In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameter derived from the bootstrap analysis fitting the Normal distribution.
 We first see that the errors on the CCF parameters only depends on the SNR and do not depend on the spectral type.
@@
 
-We see that for the RV errors, the ratio between the \emph{noise} parameter and the the RV error measured by the bootstrap using the Normal fitting is around 1, meaning that those two estimates of the RV errors are similar.
-However when fitting a SN to the CCF, we have RV errors that are on average 60\% greater.
+Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.6$ when using the mean of the SN and $0.9$ when using the median of the SN.
+In other words, by using the median of the SN as parameter for defining the radial velocity, we get standard errors $10\%$ smaller than using the Normal fit.
 
-Thus, the RVs measured by the SN do not have the same precision than the RVs calculated using the Normal.
-This can be explained by the fact that in the case of the SN, variations in the asymmetry parameter $\gamma_1$ induce variations in the SN RV measured due to the strong correlation between those two parameters.
-Therefore, the errors in $\gamma_1$ propagate to the error in the SN RVs.
-\comment{This seems to be the case in all your stars. I do not consider a method that delivers errors that are 60\% larger to be a very effective method.}
-Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal or the SN are equivalent to 2.35$\times$\emph{noise}.
+Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal or the SN are comparable.
 Therefore, the precision in CCF width is the same if we fit a Normal or a SN to the CCF.
 
-Finally, for the errors in CCF asymmetry, we see that the bootstrap analysis using the Normal fitting gives the same precision as using 2$\times$\emph{noise}, which is the common errors used for BIS SPAN.
-However, when fitting the SN to the CCF, the asymmetry errors are 15\% smaller.
+Finally, for the errors in CCF asymmetry, we see that, when fitting the SN to the CCF, the asymmetry errors are $15\%$ smaller.
 Therefore, the SN fit gives a better precision in CCF asymmetry than what can be reached using BIS SPAN.
+We recall moreover that, using the SN, all parameters are automatically retrieved in 1 single step, while in the common approach the RV and the BIS SPAN are calculated separately.
 
-Another interesting point is the behavior of the ratio of the bootstrap errors over the \emph{noise} parameter as a function of SNR (see bottom plots in Fig.~\ref{fig:se} for the RVs, CCF width and CCF asymmetry).
-We see that at low SNR, the bootstrap analysis gives a better precision, which can be explained by the fact that the \emph{noise} parameter is estimated using the CCF derivative.
-Calculating the derivative of the CCF increases the noise and therefore explain this behavior at low SNR.
-For SNR below 200, the bootstrap analysis gives a better precision than the \emph{noise} parameter.
 %
@@
    \centering
-\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
-   \caption{Comparison between the standard errors using the bootstrap analysis and the parameter $noise$ for the RVs, $2.35\times$\emph{noise} for the width, and $2\times$\emph{noise} for the asymmetry parameter.
+\includegraphics[height = 3in]{[5]Errors_vs_SNR_all_stars.pdf} 
+   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
+When using as parameter for the RV the mean of the SN (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, once the RV is defined as the median of the SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+To use as asymmetry parameter the $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
 Note that for the asymmetry, the error in BIS SPAN is in \kms.
-To be able to compare the errors in $\gamma_1$ and BIS SPAN, we multiplied the error in $\gamma_1$ by the slope of the correlation between $\gamma_1$ and BIS SPAN.}
+To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
    \label{fig:se}
@@
 The comparison between the standard errors retrieved in this way with the classic noise parameter, {\color{red} obtained by using the Gray's equation cit.
-Gray (1983)} are presented in Figure \ref{fig:se}.
+Gray (1983)} are presented in Fig.~ \ref{fig:se}.
 {\color{red} Xavier: Is it correct how the noise parameter is obtained?
@@
 
-An analysis of the CCF residuals after fitting a Normal or SN distribution show that the SN is a better model to explain the shape of the CCF.
+An analysis of the CCF residuals after fitting a Normal or SN distribution show that the SN is a slightly better model to explain the shape of the CCF.
 This comes from the fact that CCFs present a natural asymmetry due the convective blueshift.
 
-We compared for five stars the difference between the RVs, FWHM and asymmetry (BIS SPAN in the Normal case and parameter $\gamma_1$ in the SN case) as measured we a Normal or a SN fitting to the CCF.
-The $\gamma_1$ parameter is linearly dependant on the BIS SPAN, with always a strong correlation coefficient.
-%To compare $\gamma_1$, that do not have any units, with BIS SPAN expressed in \kms, one has simply to multiply $\gamma_1$ by the slope of the linear dependence between $\gamma_1$ and BIS SPAN. 
-The slope of this linear correlation change depending on the star studied. This is probably because the spectral type is different, therefore the effects from stellar activity are different.
+\umberto{add conclusions on SOAP}
 
-When comparing the RV as measured by the Normal and the SN fitting, we always see that the rms of the latter is larger.
-Thus fitting the SN to the CCF gives RV measurements that are more sensitive to activity.
-This comes from the fact the the asymmetry parameter of the SN will modify as well the mean of the distribution, thus the RV.
-This is a positive point as it is easier to correct for a signal that is at a high SNR rather that a signal that is at a SNR of one, which is generally the case for the low-activity stars that are followed for RV surveys.
+We compared for five stars the difference between the RVs (defined as mean of a Normal, mean of the SN or median of the SN), FWHM and asymmetry (BIS SPAN in the Normal case and $\gamma$ in the SN case).
+The $\gamma$ parameter is linearly dependant on the BIS SPAN, with always a strong correlation coefficient.
+%To compare $\gamma$, that do not have any units, with BIS SPAN expressed in \kms, one has simply to multiply $\gamma$ by the slope of the linear dependence between $\gamma$ and BIS SPAN. 
+The slope of this linear correlation changes depending on the studied star. This is probably because the spectral type is different, therefore the effects from stellar activity are different.
 
-The RVs derived using the SN fitting present a higher sensitivity to stellar activity.
-However, once correcting the RVs from stellar activity using a linear combination of the width and asymmetry parameter of the CCF (FWHM and BIS SPAN in the Normal case, and SN FWHM and $\gamma_1$ in the SN case), the RV residuals in both the Normal and SN case show similar scatter.
-Therefore, the SN fitting does not improve stellar activity correction when using a simple linear combination with the width and asymmetry of the CCF.
-\comment{In this statement you have basically admitted that your method is not very useful. I do not see why anyone would be compelled to use it!
-So, the bottom line is that you have introduced a method which produces similar results to the standard one.
-The only useful result of this paper is to convey to the readers that there is no significant advantage in implementing the SN method!}
-However, because the amplitude of the variations is larger in the raw SN RVs, correction techniques based on Gaussian Processes might be more efficient \citep[][]{Haywood-2014,Faria-2016a}.
-
-When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma_1$ in the SN case) with respect to the RVs (RVs in the Normal case or SN RVs in the SN case), we observe that the correlations are always stronger for the parameters of the SN.
+When using as parameter for the RV the mean of the SN, the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal.
+However, once the RV is defined as the median of the SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma$ in the SN case) with respect to the RVs (RVs in the Normal case or SN RVs in the SN case), we observe that the correlations are always stronger for the parameters of the SN.
 Therefore, the SN parameters are more sensitive to activity.
-In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of 0.57 between $\gamma_1$ and SN RV, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.21.
-
-We also studied the behavior of the noise on the different parameters of the Normal and the SN as a function of SNR.
-By performing a bootstrap analysis, we confirmed that in the case of the Normal, using the \emph{noise} parameter as returned by the HARPS pipeline gives a correct estimate of the errors measured on the RVs, FWHM and BIS SPAN for SNR $>150$.
-For the RVs, the errors are equivalent to \emph{noise}, for the FWHM to 2.35$\times$\emph{noise} and for the BIS SPAN to 2$\times$\emph{noise}.
-For lower SNR though, the bootstrap analysis gives better results, and this comes from the fact the the \emph{noise} parameter is estimated using the derivative of the CCF, which increase the noise \citep[][]{Bouchy-2001b}.
-For very low SNR, the improvement of the bootstrap analysis can be as high as 50\%.
-Therefore, although taking much more time, we encourage the use of bootstrapping when calculating errors for the different parameters of the CCF.
-
-In the case of the errors when using the SN fitting, the precision on the SN RVs is however 60\% worse than for the RVs.
-This comes from the fact that because the asymmetry is accounted for in the SN and because the SN RVs and $\gamma_1$ are strongly correlated, the errors in $\gamma_1$ propagates to the errors in SN RVs.
-This is not so important for SNR $>$ 150 for which the errors are below the \ms precision of HARPS and the \ms variation induced by stellar activity signals even in low activity cases \footnote{As we can see in papers publishing HARPS results using an additional jitter to consider stellar activity noise not accounted for in the \emph{noise} parameter, the extra jitter is always greater than 0.8\ms \citep[e.g.][]{Diaz:2016ab}.}.
-These larger errors in RVs can be a problem for low SNR measurements.
-In the case of the CCF width, the error derived when using the Normal or SN fitting are very similar.
-Finally for the asymetry, we see that the error in $\gamma_1$ is $\sim$15\% smaller than the error in BIS SPAN.
+In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of $0.436$ between $\gamma$ and SN mean RV, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.$225$.
 
@@
 When searching for small-mass exoplanets using the RV technique, it is essential to understand the shape variation of the CCF, which is a proxy for stellar activity effects.
-The standard approach consist in first to adjust a Normal distribution to the CCF to get the RV and FWHM, defined as the mean and the FWHM of the Normal distribution, and then to measure the asymmetry by calculating BIS SPAN.
+The standard approach consist at first to adjust a Normal distribution to the CCF to get the RV and FWHM, defined as the mean and the FWHM of the Normal distribution, and then to measure the asymmetry by calculating BIS SPAN.
 FWHM and BIS SPAN give us information on the line shape that are used to probe stellar activity signals.
-In this paper we demonstrate that by using the SN distribution to fit CCFs, we can measure simultaneously the RV of the star with the width and asymmetry of the CCF.
+
+In this paper we propose to conduct the analysis fitting a SN distribution to the CCF.
+Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution can better catch these aspects respect the Normal fit.
+On top of that, by using the SN distribution to fit CCFs, we can measure simultaneously the RV of the star, the width and the asymmetry of the CCF.
 
 Using the SN to fit CCFs brings a significant improvement in probing stellar activity.
-The correlations between SN RV and SN FWHM, and SN RV and the asymmetric parameter $\gamma_1$ are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
-The RVs derived by the SN are also more sensitive to activity and the precision on the asymmetry measured by $\gamma_1$ is greater than the one on BIS SPAN by $\sim$15\%.
+While for the Normal distribution mean and median are equivalent, using the SN fit different location parameters can be tested.
+While the median of the SN is more robust respect variations in the shape of the CCF, the mean of the SN is more sensible to changes in the asymmetry of the CCF.
+We suggest to use as parameter that defines the RV of the star the median of the SN, since the standard errors related to this parameter are $10\%$ smaller than the standard errors retrieved using the Normal distribution.
+For evaluating changes in the asymmetry of the CCF, we suggest to use the mean of the SN.
+The correlations between SN mean RV and SN FWHM, and SN mean RV and $\gamma$ (the asymmetry parameter of the SN) are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
+The precision on the asymmetry measured by $\gamma$ is greater than the one on BIS SPAN by $\sim$15\%.
 Therefore when searching for rotational periods in the data, or applying Gaussian Processes to account for stellar activity signals, the SN parameters should be used.
-
-At first glance, one downside of using the SN comes from the RV errors that are greater by 60\% relative to the RV errors measured when considering a Normal.
-This is due to the strong correlation between SN RV and $\gamma_1$ and this can be a problem for low SNR measurements.
-However, in the regime of SNR $>$ 150, which is the aim of all RV surveys at high precision, the precision of the SN RVs is below the \ms, which is thus below the instrumental precision of HARPS and below the RV perturbations induced by stellar activity.
 
@@
 \appendix
-\section{Appendix}
+\section{Appendix} \label{appendix}
 
@@
 
+\umberto{I suggest to outline here shortly the characteristics of the considered stars. Then we summarize/compare the results presenting Table \ref{table:summaryStars} and finally we show the plots.}
+\umberto{for each star there are always the same $3$ plots: 
+\begin{itemize}
+\item RVs vs. JD
+\item $\gamma$ vs. Bis-Span
+\item Comparison on the correlation between asymmetry parameters (or FWHM) and RV.
+\end{itemize}
+
+Do we need to show all these plots?}
+
+\small{
+\begin{table}[!t]
+\scalebox{0.5}{
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+\hline
+\textbf{Star}          &\textbf{ \# CCFs}  &   \textbf{$\text{R}(\text{SN }\gamma, \text{Bis-Span})$} & \textbf{$\text{slope}(\text{SN }\gamma, \text{Bis-Span})$} &   \textbf{$\text{R}(\text{SN }\gamma, \text{SN mean RV})$} & \textbf{$\text{R}(\text{Bis-Span}, \text{RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{SN mean RV})$}  & \textbf{$\text{R}(\text{FWHM}, \text{RV})$} \\
+\hline
+ $\text{HD}192310  $          &    $1576$    & $0.883$ & $0.812$ & $0.682 (0.655; 0.707)$ & $0.33 (0.285; 0.373)$  & $-0.335 (-0.378; -0.29)$ & $0.677 (0.650; 0.703)$ & $0.475 (0.436; 0.513)$\\
+\hline
+ $\text{HD}10700 $            &    $7928$    & $0.795$ & $0.749$ & $0.436 (0.418; 0.454)$ & $-0.073 (-0.095; -0.0051)$ & $0.127 (0.105; 0.148)$ & $0.291 (0.270; 0.311)$ & $0.529 (0.513; 0.545)$ \\
+\hline
+ $\text{HD}215152 $          &     $273$   &  $ 0.763$ & $0.794$ & $0.571 (0.485; 0.646)$ & $-0.067 (-0.184; 0.052)$  & $0.269 (0.155; 0.376)$ & $0.210 (0.094; 0.321)$ & $-0.138 (-0.253; -0.020)$ \\
+\hline
+ $\text{Corot }7$     &     $173$    &  $0.797$  & $0.64$ & $0.561 (0.450; 0.656)$ & $0.092 (-0.058; 0.238)$ & $-0.335 (-0.228; -0.082)$ & $-0.709 (0.626;0.776)$ & $0.595 (0.489; 0.683)$ \\
+\hline
+\end{tabular}
+}
+\caption{Subset of notable correlations between the asymmetry parameter (and the FWHM) and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.}
+\label{table:summaryStars}
+\end{table}
+}
+
 \subsection{HD192310}  \label{sec:Gl785}
-
-We present now the results of the analysis for the star HD192310 (i.e.
-Gliese 785).
-The dataset consists in $1588$ CCFs.
-Figure \ref{fig:Gliese785:corr.gamma} shows the correlation between $\gamma$ and BIS SPAN to understand the link between those two parameters.
-It is interesting to see that, in this case, the slope of $0.645$ is significantly different from the one found for Alpha Centauri B in Fig.~\ref{fig:alphacent:corr.gamma}.
-\comment{Why is this interesting? You would expect it to be given that this is a different star! If something is interesting you have to point out to the reader why.}
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 3in]{[0]HD19231_vs_time.pdf} 
+   \caption{RVs comparison for HD192310 considering a Normal and a SN fitting (using both the mean and the median).}
+   \label{fig:HD192310:RV}
+\end{figure*}
 %
@@
 \end{figure}
-
-In Fig.~\ref{fig:Gliese785:correctionRV}, we see like for Alpha Centauri B that the RVs obtained with the SN analysis present a larger rms than the RVs obtained with the Normal fitting.
-However, once correcting for stellar activity using a linear correlation with $\gamma$ and SN FWHM (or BIS SPAN and FWHM, see Eq.~\ref{eq:RV:correction}), the rms of the residuals are comparable.
-We note that when correcting for stellar activity, the BIS SPAN is not statistically significant (see Table~\ref{table:Gliese785:test}).
-Like for Alpha Centauri B, the Pearson correlation coefficient $R^{2}$ shows  that the model we used to correct for stellar activity is a better one in the SN case than in the Normal case.
-\comment{So if I understand this correctly, SN gives higher scatter in the RV, but you make a bigger correction to the activity.
-In the end you arrive at the same answer as the Normal distribution and using Eq.
-9 .
-So why use SN?}
 %
@@
    \centering
-\includegraphics[height = 6in]{HD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Radial Velocities for HD192310 using the Normal and the Skew Normal fitting before and after correcting the analyses from the stellar activity.}
-   \label{fig:Gliese785:correctionRV}
-\end{figure*}
-%
-\begin{table}[!t]
-\begin{tabular}{|c|c|c|}
-\hline
-Parameter          & Normal Fitting         &   Skew Normal Fitting \\
-\hline
-$\beta_{0}$            &    $2e-16$    & $2.22e-16$ \\
-\hline
-$\beta_{1}$            &    $0.18$    & $2.22e-16$ \\
-\hline
-$\beta_{2}$            &     $2e-10$   &  $2.22e-16$ \\
-\hline
-$R^{2}$      &     $0.23$    &  $0.48$   \\
-\hline
-\end{tabular}
-\caption{\textbf{HD192310}: Evaluation of the linear combination used for correcting the RVs from stellar activity, according to Eq.
-\ref{eq:RV:correction}.
-The p-values for the parameters  $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ for both the methodologies are summarized, as well as the $R^2$.
-Concerning the Normal fitting, the BIS SPAN is not statistically useful in explaining the variability of the RVs of the star, whereas for the SN analyses all the variables are statistically different from $0$.
-The evaluation of the $R^2$ shows how the linear combination better explains the variability in RVs due to stellar activity coming from the SN analysis.}
-\label{table:Gliese785:test}
-\end{table}
-
-The comparison between the asymmetry parameters and the RVs are presented in Figure \ref{fig:Gliese785:corrPlot}.
-The $\gamma$ parameter shows a stronger correlation with the RVs ($0.587$) than the other asymmetric parameters.
-The correlation between the CCF width and the RVs is also stronger when fitting a SN rather than a Normal.
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
+\includegraphics[height = 3in]{HD19231_[4]Comparison_para.pdf} 
    \caption{Correlation between the asymmetry parameters and the RVs for HD 192310.
@@
 \subsection{Tau Ceti}  \label{sec:Taucet}
-\comment{If you are going to refer to the star as HD 10700 you should use the same name in the section heading.}
-The analysis of the star HD10700 (i.e.
-Tau Ceti) consists of $7963$ CCFs.
-Figure \ref{fig:Tau:corr.gamma} shows the relationship between $\gamma$ and the BIS SPAN, with a correlation of $0.605$ and a slope of the fitted line of $0.566$.
-Although still significant, we see that this correlation is weaker than in the case of Alpha Centauri B or HD192310.
-This is probably because HD10700 is at a very low activity level, similar to the Sun at its minimum activity phase.
-\comment{And how exactly do you arrive at this conclusion?
-It is ok to hypothesize that the star has a low activity level.
-But to claim it has the same activity level as the sun at solar minimum is completely unqualified and should be supported by evidence.
-This is especially true since HD 10700 is a late F-type star and thus may have a different activity behavior from a G2 star.}
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 3in]{[0]TauCeti_vs_time.pdf} 
+   \caption{RVs comparison for Tau Ceti considering a Normal and a SN fitting (using both the mean and the median).}
+   \label{fig:Tau Ceti:RV}
+\end{figure*}
 %
@@
 \end{figure}
-
-The RVs derived with the SN present a slightly more important rms as we can see in Fig.~\ref{fig:Tau:correctionRV}, and after correcting for stellar activity, the rms of the RV residuals are extremely similar.
-\comment{And just what is a "more important" rms compared to a less important one? The rms is a measurement of the properties of the data often with respect to a fit.}
-In Table~\ref{table:Tau:test}, we see that in the Normal and SN analysis, the intercept, the width and the asymmetry of the CCF (measured with FWHM or SN FWHM and $\gamma$ or BIS SPAN) can explain part of the RV variability measured.
-Looking at $R^2$, the RVs derived with the SN present a stronger relationship with acticity parameters than the RVs derived in the Normal.
 %
@@
    \centering
-\includegraphics[height = 6in]{HD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{RVs for HD10700 using the Normal and the Skew Normal fitting before and after correcting for stellar activity.}
-   \label{fig:Tau:correctionRV}
-\end{figure*}
-%
-\begin{table}[!t]
-\begin{tabular}{|c|c|c|}
-\hline
-Parameter          & Normal Fitting         &   Skew Normal Fitting \\
-\hline
-$\beta_{0}$            &    $0.00013$    & $2.22e-16$ \\
-\hline
-$\beta_{1}$            &    $4.83e-6$    & $2.22e-16$ \\
-\hline
-$\beta_{2}$            &     $2.22e-16$   &  $ 2.22e-16 $ \\
-\hline
-$R^{2}$      &     $0.27$    &  $0.43$   \\
-\hline
-\end{tabular}
-\caption{\textbf{HD10700}: Evaluation of the linear combination used for correcting the RVs from stellar activity, according to Eq.
-\ref{eq:RV:correction}.
-The p-values for the parameters  $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ for both the methodologies are summarized, as well as the $R^2$.
-For both the analyses, all the variables are helpful, although the linear combination is statistically more significant when working with the SN parameters.}
-\label{table:Tau:test}
-\end{table}
-
-The evaluation of the correlation between the asymmetry parameters and the SN RVs shows how using the SN procedure leads to much stronger correlations.
-The correlation between $\gamma$ and the RVs is $0.566$, whereas the correlation between the common asymmetry statistics with their corresponding RVs result in values close to $0$.
-The correlation between the FWHM and the RVs of HD10700 for the SN and the Normal are similar.
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
+\includegraphics[height = 3in]{HD10700_[4]Comparison_para.pdf}  
    \caption{Correlation between the asymmetry parameters and the RVs for Tau Ceti.
@@
 \subsection{HD215152}  \label{sec:HD215152}
-
-The analysis of the star HD215152 consists in 284 CCFs and Figure \ref{fig:HD215152:corr.gamma} shows that the slope of the linear regression between $\gamma$ and the BIS SPAN is $0.591$ with a Pearson correlation coefficient of $0.767$.
-
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 3in]{[0]HD21515_vs_time.pdf} 
+   \caption{RVs comparison for HD215152 considering a Normal and a SN fitting (using both the mean and the median).}
+   \label{fig:HD215152:RV}
+\end{figure*}
+%
 \begin{figure}[htbp]
@@
 \end{figure}
-
-In the case of HD215152, we see in Fig.~\ref{fig:HD215152:correctionRV} that the RVs measured with the SN or the Normal, and the corresponding RV residuals after activity correction all present very similar RV rms.
-Thus activity correction does not seem to be very efficient at understand the RV variation.
-\comment{Poor English. How can a correction be "efficient at understand [SIC] a variation?"
-Revised construction: "Thus the activity correction does not seem to be useful in helping us understand the RV variations."}
-This is probably because of the presence of planetary signals in the RV data \citep[][]{Mayor-2011}. 
-\comment{So there is a planetary signal in the data but you do not have an orbit that gives you a phase? Then this is not a confirmed planetary signal and thus cannot support you claim}
-Note however that the information on the orbital phase of the planets is not present in \citet{Mayor-2011} and we cannot therefore remove those signals.
-The significance of $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ in Table~\ref{table:HD215152:test} shows that in the Normal case BIS SPAN is not significantly correlated with the RVs, while for the intercept and the FWHM the test with level $0.05$ is barely significant.
-In the SN case it is the intercept and FWHM that are not significantly correlated.
-The Pearson correlation coefficient $R^2$ shows that the RV derived from the SN fit are more affected by stellar activity than the RVs measured with the Normal, although the correlation is low at a level of 0.15.
 %
@@
    \centering
-\includegraphics[height = 6in]{HD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Radial Velocities for HD 215152 using the Normal and the Skew Normal fitting before and after correcting the analyses from the stellar activity.}
-   \label{fig:HD215152:correctionRV}
-\end{figure*}
-
-\begin{table}[!t]
-\begin{tabular}{|c|c|c|}
-\hline
-Parameter          & Normal Fitting         &   Skew Normal Fitting \\
-\hline
-$\beta_{0}$            &    $0.041$    & $0.11$ \\
-\hline
-$\beta_{1}$            &    $0.79$    & $4.12e-11$ \\
-\hline
-$\beta_{2}$            &     $0.042$   &  $0.11$ \\
-\hline
-$R^{2}$      &     $0.020$    &  $0.15$   \\
-\hline
-\end{tabular}
-\caption{\textbf{HD215152}: Evaluation of the linear combination used for correcting the RVs from stellar activity, according to Eq.
-\ref{eq:RV:correction}.
-The p-values for the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ for both the methodologies are summarized, as well as the $R^2$.
-Concerning the Normal fitting, the intercept and the FWHM are statistically significant at explaining the RV variations at level $0.05$ but not at level $0.01$, explaining why the $R^{2}$ is only $0.02$.
-The BIS SPAN is however not significant.
-For the SN case, it is the contrary, $\gamma_1$ is significant in explaining the SN RV variations, while the FWHM and the intercept are not.
-When looking at the value of
-$R^2$, although the correlation is stronger for the SN case, is stay low at a level below 0.15.}
-\label{table:HD215152:test}
-\end{table}
-
-The correlations among the asymmetry parameters and the RVs shows also in this case that using the SN fitting provides a stronger result.
-The correlation between $\gamma$ and the RVs is $0.38$, whereas the correlation between the common asymmetry statistics and their corresponding radial velocities is smaller than $0.30$.
-The SN FWHM or the FWHM are not significantly correlated to the SN RVs or the RVs.
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
+\includegraphics[height = 3in]{HD21515_[4]Comparison_para.pdf}  
    \caption{Correlation between the asymmetry parameters and the RVs for HD 215152.
@@
 \subsection{Corot-7}  \label{sec:Corot7}
-
-The final star considered is Corot-7 which has low signal to noise. 
-\comment{A star cannot have a "low signal to noise" only data has that. And what data are you referring to photometry (from CoRoT) RVs, from HARPS? You need to be clear.}
-A total of $180$ CCFs have been analysed and Fig.~\ref{fig:Corot7:corr.gamma} shows the correlation between $\gamma$ the BIS SPAN with a linear regression slope of $0.596$.
-\comment{"Figure 9 shows the correlation between and BIS SPAN to understand the link Grammatically incorrect sentence: "Fig. 9 shows to understand"?
-You need an alternate construction: "Figure 9 shows the correlation between BIS SPAN and ?? which helps us to understand...."
-Note: there is a correlation between two quantities which is not expressed in the original text.}
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 3in]{[0]LRa01_E_vs_time.pdf} 
+   \caption{RVs comparison for Corot-7 considering a Normal and a SN fitting (using both the mean and the median).}
+   \label{fig:corot7:RV}
+\end{figure*}
 %
@@
 \end{figure}
-
-The RVs obtained with the SN show more variability than the RVs derived with the Normal. 
-\comment{Hasn't this been the case for virtually all the stars you looked at?}
-After correcting for stellar activity using Eq.~\ref{eq:RV:correction}, the RV residuals with both distributions are similar.
-In Table~\ref{table:Corot7:test}, we see that in the Normal and the SN analyses, the intercept, the width and the asymmetry of the CCF (measured with FWHM or SN FWHM and $\gamma$ or BIS SPAN) can explain part of the RV variability measured.
-Looking at $R^2$, the RVs derived with the SN present like for all the stars in this paper a stronger correlation with $\gamma_1$ and SN FWHM than the RV derived in the Normal case.
-
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{LRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Radial velocities for Corot-7 using the Normal and the Skew Normal fitting before and after correcting the analyses from the stellar activity.}
-   \label{fig:Corot7:correctionRV}
-\end{figure*}
-
-\begin{table}[!t]
-\begin{tabular}{|c|c|c|}
-\hline
-Parameter          & Normal Fitting         &   Skew Normal Fitting \\
-\hline
-$\beta_{0}$            &    $2e-16$    & $2.22e-16$ \\
-\hline
-$\beta_{1}$            &    $0.0067$    & $0.00054$ \\
-\hline
-$\beta_{2}$            &     $2.22e-16$   &  $2.22e-16$ \\
-\hline
-$R^{2}$      &     $0.36$    &  $0.47$   \\
-\hline
-\end{tabular}
-\caption{\textbf{Corot-7}: Evaluation of the linear combination used for correcting the RVs from stellar activity, according to Eq.~\ref{eq:RV:correction}.
-The p-values for the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ for both the methodologies are summarized, as well as the $R^2$.
-For both the analyses, all the variables are helpful, although the linear combination is more useful in explaining the RV variability when working with the SN fitting.}
-\label{table:Corot7:test}
-\end{table}
-
-The correlation between $\gamma$ and the SN RVs of Corot-7 is much stronger than the correlation between  the RVs and other asymmetric indicators (see Fig.~\ref{fig:Corot7:corrPlot}).
-The correlation between $\gamma$ and the SN RVs is $0.462$, whereas the correlation between the other asymmetry statistics with their corresponding RVs result in values close to $0$.
-Also the correlation between the FWHM and the RVs of Corot-7 when using the SN fitting is stronger.
-These significant correlations for the SN parameters and non-significant for the Normal parameters suggest that for low signal to noise measurement, using the SN fitting improves our power in detecting stellar activity signals.
 %
@@
    \centering
-\includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
+\includegraphics[height = 3in]{LRa01_E_[4]Comparison_para.pdf} 
    \caption{Correlation between the asymmetry parameters and the RVs for Corot-7.
@@
 \end{figure*}
+%
 

### 2018-04-13 manuscript.tex
Add files via upload

@@
 % Context, Aims, Methods, Results, Conclu (not mandatory)
-When working with radial velocities for detecting Extrasolar planets and when using data from stabilized spectrographs,
-the different moments of the cross-correlation function (CCF) are used to measure the radial velocity of the star but also the changes in the shape of the CCF.
+When working with radial velocities for detecting Extrasolar planets and when using data from stabilized spectrographs, the different moments of the cross-correlation function (CCF) are used to measure the radial velocity of the star and also changes in the shape of the CCF.
 Those changes are due to stellar activity and therefore the best precision on these moments is required to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
-We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, provides an extra parameter to model the CCF natural asymmetry.
-We analyzed 5 stars with different activity levels and different signal-to-noise ratio levels.
-In each case, we compare the results obtained from the Normal fitting of the CCF and from the SN fitting.
+
+We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, naturally provides an extra parameter to model the CCF natural asymmetry.
+Moreover, since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution seems to provide a more realistic model to the CCF.
+
+We analyze 5 stars with different activity levels and different signal-to-noise ratio levels.
+In each case, we compare the results obtained by fitting to the CCF respectively a Normal and a SN.
 We also estimate rigorous errors for the different moments of the CCF using a bootstrap analysis.
+
 The correlations between the RVs and the CCF asymmetry or RVs and the CCF width is always stronger when using the parameters derived from the SN.
@@
 one that conveys not useful information to the reader.}
-However, once correcting the RVs from stellar activity signal using a linear combination of the CCF asymmetry and width, the RV residuals obtained from a Normal or SN fitting are very similar.
-The precision on the asymmetric parameter derived from the SN is also 15\% better than the one derived on the common Bisector Inverse Slope Span (BIS SPAN).
-Besides all these advantages, the errors on the RVs measured by the SN are 60\% greater.
-\comment{To me this statement alone tells me that the SN method is not very useful, and not one that I would use.
-Any method that produces larger errors *before* correcting for the activity is not a very useful method.
-Why should the reader continue beyond this point?}
-This is not a problem at signal-to-noise ratio levels $>$ 150 because other noise sources dominate in this regime, however we have to be careful when deriving precise RVs for low SNR measurements.
-We also found that in the case of low SNR measurements, errors measured by bootstrap analysis can be 50\% more precise than errors measured using the derivative of the CCF.
-We strongly encourage the use of the SN distribution to derive the different moments of the CCF, because the derived moments probe better stellar activity signals than when using a Normal distribution.
+The precision on the asymmetry parameter derived from the SN is on average $15\%$ better than the one calculated on the common Bisector Inverse Slope Span (BIS SPAN).
+When using the median of the SN as parameter defining the radial velocity of the star, the errors on the RVs measured by the SN are on average $10\%$ smaller than the errors calculated on the mean of the Normal.
+
+We strongly encourage the use of the SN distribution to retrieve in 1 single fit the different moments of the CCF, because the derived moments probe better stellar activity signals than when using a Normal distribution, leading as well to smaller standard errors associated to the radial velocity and the asymmetry parameters.
 \comment{You simply cannot make this claim.
@@
 The line asymmetry is commonly retrieved by calculating the bisector of the CCF \citep[][]{Voigt1956} and deriving the bisector curvature \citep[][]{Hatzes1996} or the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
+An orbiting exoplanet will produce an RV variation induced by a pure Doppler shift of \emph{all} the spectral lines of each stellar spectrum. 
+Stellar activity, however, does not produce a blueshift or redshift of the spectra, but can create a spurious RV signal by modifying the shape of spectral lines.
+To track changes in line shape, the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} are often used, which provide information on the average width and asymmetry of the CCF \citep{Hatzes1996, fiorenzano2005line, Queloz-2001}.
+A strong correlation between the estimated RVs and one or more of these parameters is a sign that the estimated RVs may be contaminated by stellar activity.
 \comment{It is the slope or span, not both. And you generally do not calculate the inverse, just the
@@
 
-\umberto{We considered CCFs having SNR larger than 10.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  show that the SN density is a better representation of observed CCF than a Normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
-In Sec.~\ref{sec:31} we present a simple model to correct for stellar activity.
+In Sec.~\ref{intro} we present a simple model to correct for stellar activity.
 In Sec.~\ref{sec:4}, we compare on real observations the sensitivity of the SN parameters to stellar activity with respect to other existing indicators.
@@
    \centering
-\includegraphics[height = 3in]{Skew_Normal_densities_jjck.pdf} 
+\includegraphics[height = 4in]{Skew_Normal_densities_jjck.pdf} 
    \caption{Density function of a random variable $Y \sim SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$, and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
@@
 To check this assumption, we compared the CCF residuals after fitting a Normal and a SN distribution for 2 stars.
-The first star is Alpha Centauri b, whose CCFs have high signal to noise ratio (SNR).
+The first star is Alpha Centauri b, whose CCFs have high signal-to-noise ratio (SNR).
 The second star is Corot-7, whose CCFs have low SNR.
@@
 \includegraphics[height = 2.5in]{[1]LRa01_E2Residuals.pdf} 
-   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCFs of the star Alpha Centauri b (left) and Corot-7 (right).
+   \caption{\umberto{create with subfig in order to show left plot is Alpha Cent b, right plot is Corot-7} Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCFs of the star Alpha Centauri b (left) and Corot-7 (right).
 The results are comparable looking at the residuals corresponding to the tails of the CCF but the SN fit leads to slightly better results in the center of the CCF for both the stars.
-As the signal to noise decreases, as happens when analyzing the star Corot-7, the SN distribution leads to better residuals respect using the Normal.}
+As the signal-to-noise decreases, as happens when analyzing the star Corot-7, the SN distribution leads to better residuals respect using the Normal.}
     \label{fig:Residual.comparison}
@@
 %
-
-\subsection{Effect of stellar activity on the CCF} \label{sec:31}
-
-An orbiting exoplanet will produce an RV variation induced by a pure Doppler shift of \emph{all} the spectral lines of each stellar spectrum. 
-Stellar activity, however, does not produce a blueshift or redshift of the spectra, but can create a spurious RV signal by modifying the shape of spectral lines.
-To track changes in line shape, the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} are often used, which provide information on the average width and asymmetry of the CCF \citep{Hatzes1996, fiorenzano2005line, Queloz-2001}.
-A strong correlation between the estimated RVs and one or more of these parameters is a sign that the estimated RVs may be contaminated by stellar activity.
-To test the strength of the correlation between RVs and the different activity indicators, we calculated the Pearson correlation coefficient, $R$.
-A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ (i.e., no correlation) is provided, along with a $95\,\%$ confidence interval for $R$.
 
@@
 This will be compared to the asymmetric parameter $\gamma$ of the SN, called SN GAMMA.
+To test the strength of the correlation between the RVs and the different activity indicators, we calculated the Pearson correlation coefficient, $R$.
+A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ (i.e., no correlation) is provided, along with a $95\,\%$ confidence interval for $R$.
 
@@
 Other 4 stars have been analyzed with the proposed methods and details can be found in the Appendix \ref{appendix}.
+For all the stars that have been considered in the present work, we selected those CCFs having SNR larger than 10.
+
  A comparison with the results obtained by the classic approach is done, where the RVs of the star are estimated by retrieving the mean of the Normal distribution used to fit the CCF, along with the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}.
@@
    \centering
-\includegraphics[height = 3in]{HD12862_[2]gamma_vs_bisspan.pdf} 
+\includegraphics[height = 4in]{HD12862_[2]gamma_vs_bisspan.pdf} 
    \caption{Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
@@
    \centering
-\includegraphics[height = 3in]{HD12862_[2]RadialVelocityDifferences.pdf} 
+\includegraphics[height = 4in]{HD12862_[2]RadialVelocityDifferences.pdf} 
    \caption{(top) RVs as function of Julian Day for Alpha Centauri b.
@@
    \centering
-\includegraphics[height = 3in]{HD12862_[4]Comparison_para.pdf}  
+\includegraphics[height = 4in]{HD12862_[4]Comparison_para.pdf}  
    \caption{Correlation between the asymmetry parameters and the RVs for Alpha Centauri B.
@@
 
-Both the proposed indicators coming from the SN distribution have desirable and undesirable behaviors: the SN mean RV better catches changes in the asymmetry of the CCF but the resulting set of RVs ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Section \ref{sec:31}.
+Both the proposed indicators coming from the SN distribution have desirable and undesirable behaviors: the SN mean RV better catches changes in the asymmetry of the CCF but the resulting set of RVs ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Section \ref{intro}.
 When using SN median RV, the final set of radial velocity is less affected by those spurious shifts caused by stellar activity, but at the same time this indicator is not able to catch as well as SN mean RV changes in the shape of the CCF.
@@
    \centering
-\includegraphics[height = 3in]{[5]Errors_vs_SNR_all_stars.pdf} 
+\includegraphics[height = 4in]{[5]Errors_vs_SNR_all_stars.pdf} 
    \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
@@
 
-\umberto{add conclusions on SOAP}
+\umberto{add discussions on SOAP example}
 
@@
 
+\umberto{add conclusions on SOAP example}
+
 Using the SN to fit CCFs brings a significant improvement in probing stellar activity.
@@
 In conclusion, we showed how using the SN fit provides in an unique step a better understanding of the stellar activity through using the asymmetry parameter $\gamma$ rather than using the common statistics such as the BIS SPAN or other indicators.
-On top of that, when focusing on low signal to noise cases, the SN procedure showed how statistically significant results are retrieved with the proposed approach in terms of correlation between the asymmetry of the profile line and the RVs, whereas for the previous analyses this correlation does not result statistically significant.
+On top of that, when focusing on low signal-to-noise cases, the SN procedure showed how statistically significant results are retrieved with the proposed approach in terms of correlation between the asymmetry of the profile line and the RVs, whereas for the previous analyses this correlation does not result statistically significant.
 
@@
    \centering
-\includegraphics[height = 3in]{[0]HD19231_vs_time.pdf} 
+\includegraphics[height = 4in]{[0]HD19231_vs_time.pdf} 
    \caption{RVs comparison for HD192310 considering a Normal and a SN fitting (using both the mean and the median).}
@@
    \centering
-\includegraphics[height = 3in]{HD19231_[4]Comparison_para.pdf} 
+\includegraphics[height = 4in]{HD19231_[4]Comparison_para.pdf} 
    \caption{Correlation between the asymmetry parameters and the RVs for HD 192310.
@@
    \centering
-\includegraphics[height = 3in]{[0]TauCeti_vs_time.pdf} 
+\includegraphics[height = 4in]{[0]TauCeti_vs_time.pdf} 
    \caption{RVs comparison for Tau Ceti considering a Normal and a SN fitting (using both the mean and the median).}
@@
    \centering
-\includegraphics[height = 3in]{HD10700_[2]gamma_vs_bisspan.pdf} 
+\includegraphics[height = 4in]{HD10700_[2]gamma_vs_bisspan.pdf} 
    \caption{Correlation between $\gamma$ and the BIS SPAN for Tau Ceti.}
@@
    \centering
-\includegraphics[height = 3in]{HD10700_[4]Comparison_para.pdf}  
+\includegraphics[height = 4in]{HD10700_[4]Comparison_para.pdf}  
    \caption{Correlation between the asymmetry parameters and the RVs for Tau Ceti.
@@
    \centering
-\includegraphics[height = 3in]{[0]HD21515_vs_time.pdf} 
+\includegraphics[height = 4in]{[0]HD21515_vs_time.pdf} 
    \caption{RVs comparison for HD215152 considering a Normal and a SN fitting (using both the mean and the median).}
@@
    \centering
-\includegraphics[height = 3in]{HD21515_[2]gamma_vs_bisspan.pdf} 
+\includegraphics[height = 4in]{HD21515_[2]gamma_vs_bisspan.pdf} 
    \caption{Correlation between $\gamma$ and the BIS SPAN for HD 215152.}
@@
    \centering
-\includegraphics[height = 3in]{HD21515_[4]Comparison_para.pdf}  
+\includegraphics[height = 4in]{HD21515_[4]Comparison_para.pdf}  
    \caption{Correlation between the asymmetry parameters and the RVs for HD 215152.
@@
    \centering
-\includegraphics[height = 3in]{[0]LRa01_E_vs_time.pdf} 
+\includegraphics[height = 4in]{[0]LRa01_E_vs_time.pdf} 
    \caption{RVs comparison for Corot-7 considering a Normal and a SN fitting (using both the mean and the median).}
@@
    \centering
-\includegraphics[height = 3in]{LRa01_E_[2]gamma_vs_bisspan.pdf} 
+\includegraphics[height = 4in]{LRa01_E_[2]gamma_vs_bisspan.pdf} 
    \caption{Correlation between $\gamma$ and the BIS SPAN for Corot-7.}
@@
    \centering
-\includegraphics[height = 3in]{LRa01_E_[4]Comparison_para.pdf} 
+\includegraphics[height = 4in]{LRa01_E_[4]Comparison_para.pdf} 
    \caption{Correlation between the asymmetry parameters and the RVs for Corot-7.

### 2018-04-13 manuscript.tex
Add files via upload

@@
 
+\subsection{Faculae} \label{sec:soap.faculae}
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 2.5in]{RV_comparison_FACULAE.pdf} 
+\includegraphics[height = 2.5in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
+   \caption{SOAP FACULAE}
+    \label{fig:faculae}
+\end{figure*}
+
+\subsection{Spot} \label{sec:soap.spot}
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 2.5in]{RV_comparison_SPOT.pdf} 
+\includegraphics[height = 2.5in]{SOAP_SPOT_Comparison_para_SN.pdf} 
+   \caption{SOAP SPOT}
+    \label{fig:spot}
+\end{figure*}
+
+\subsection{Spot and planet} \label{sec:soap.spot.planet}
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 2.5in]{RV_comparison_PLANET_SPOT.pdf} 
+\includegraphics[height = 2.5in]{SOAP_SPOT_PLANET_Comparison_para_SN.pdf} 
+   \caption{SOAP PLANET and SPOT}
+    \label{fig:spot.plus.planet}
+\end{figure*}
+
 We also consider a real-data example using HARPS spectra from the star Alpha Centauri B with an imputed Doppler shift added...

### 2018-05-08 manuscript.tex
Add files via upload
paper update at May 7th

@@
 %
-where C is a constant fitting the continuum of the CCF \jessi{The C is unclear to me - can more intuition be added here?
-Are C and A considered known?}, A is an unknown amplitude parameter, and $y_1, \ldots, y_n$ are the set of RV's considered for the CCF.
+where C is an unknown offset fitting the continuum of the CCF, A is an unknown amplitude parameter, and $y_1, \ldots, y_n$ are the set of RV's considered for the CCF.
 Note that the CCF is expressed in flux as a function of the lag of the cross-correlation template, expressed in RV.
@@
 \includegraphics[height = 2.5in]{[1]LRa01_E2Residuals.pdf} 
-   \caption{\umberto{create with subfig in order to show left plot is Alpha Cent b, right plot is Corot-7} Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCFs of the star Alpha Centauri b (left) and Corot-7 (right).
+   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCFs of the star Alpha Centauri b (left) and Corot-7 (right).
 The results are comparable looking at the residuals corresponding to the tails of the CCF but the SN fit leads to slightly better results in the center of the CCF for both the stars.
@@
 
+\umberto{specify characteristic of the faculae}
+
+Figure \ref{fig:faculae} shows the results obtained when a faculae is present on the photosphere of the star.
+It is possible to note that, although there is not a planet, the presence of the faculae leads to spurious variations in RVs for all the proposed indicator.
+The evaluation of the standard errors, which details will be discussed in Section \ref{sec:5}, shows that the RV defined as mean SN has the largest variability.
+The standard errors associates with median SN and mean Normal are comparable, although the standard errors retrieved when the RV is defined as the median of the SN are $10 \%$ smaller.
+
+Since in this case we know that the variations in RV are only caused by the faculae, the evaluation of the correlation between the set of RVs and the asymmetry parameters is important.
+Figure \ref{fig:faculae.corr} summarises the correlations obtained using as RV respectively mean SN, median SN and mean Normal.
+The $\gamma$ parameter shows a stronger correlation with the median SN ($-0.944$) than what the other asymmetry indicators do with their corresponding RVs.
+The correlation between the CCF width and the RVs is also stronger when fitting a SN rather than a Normal.
+
 \begin{figure*}[htbp]
@@
 \includegraphics[height = 2.5in]{RV_comparison_FACULAE.pdf} 
-\includegraphics[height = 2.5in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
-   \caption{SOAP FACULAE}
+\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
+   \caption{(left) RVs changes as function of the phase in the case in which a faculae is present on the photosphere of the star.
+(right) Evaluation of the standard errors corresponding to the defined RVs.}
     \label{fig:faculae}
+\end{figure*}
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
+   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a faculae is present on the photosphere of the star.}
+    \label{fig:faculae.corr}
 \end{figure*}
@@
 
+\umberto{specify characteristic of the spot}
+
+Figure \ref{fig:spot} shows the results obtained when a spot is present on the photosphere of the star.
+Similarly to the previous case, the presence of the spot leads to spurious variations in RVs for all the proposed indicator.
+The evaluation of the standard errors shows that the RV defined as mean SN has the largest variability and, as before, the standard errors associated with the median SN are $10 \%$ smaller than the standard errors associated with the mean Normal.
+
+Figure \ref{fig:spot.corr} summarises the correlations obtained using as RV respectively mean SN, median SN and mean Normal.
+It is possible to see that the correlation between the asymmetry parameters and the RVs are weaker than the previous case, because of the presence of the planet.
+The correlation between the CCF width and the RVs is slightly stronger when fitting a SN rather than a Normal, although in this latter case the presence of the spot is largely masquerade from the planet.
+
 \begin{figure*}[htbp]
@@
 \includegraphics[height = 2.5in]{RV_comparison_SPOT.pdf} 
-\includegraphics[height = 2.5in]{SOAP_SPOT_Comparison_para_SN.pdf} 
-   \caption{SOAP SPOT}
+\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
+   \caption{(left) RVs changes as function of the phase in the case in which a spot is present on the photosphere of the star.
+(right) Evaluation of the standard errors corresponding to the defined RVs.}
     \label{fig:spot}
+\end{figure*}
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{SOAP_SPOT_Comparison_para_SN.pdf} 
+   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a spot is present on the photosphere of the star.}
+    \label{fig:spot.corr}
 \end{figure*}
@@
 
+Figure \ref{fig:spot.plus.planet} shows the results obtained when not only a spot is present on the photosphere of the star but, respect to the previous case, a planet is injected.
+The planet has amplitude equal to 10 \ms.
+The evaluation of the standard errors shows that the RV defined as mean SN has the largest variability and, as before, the standard errors associated with the median SN are $10 \%$ smaller than the standard errors associated with the mean Normal.
+
+Figure \ref{fig:spot.plus.planet.corr} summarises the correlations obtained using as RV respectively mean SN, median SN and mean Normal.
+The $\gamma$ parameter shows a stronger correlation with the median SN ($-0.89$) than what the other asymmetry indicators do with their corresponding RVs.
+The correlation between the CCF width and the RVs is also stronger when fitting a SN rather than a Normal.
+
 \begin{figure*}[htbp]
@@
 \includegraphics[height = 2.5in]{RV_comparison_PLANET_SPOT.pdf} 
-\includegraphics[height = 2.5in]{SOAP_SPOT_PLANET_Comparison_para_SN.pdf} 
-   \caption{SOAP PLANET and SPOT}
+\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
+   \caption{(left) RVs changes as function of the phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
+(right) Evaluation of the standard errors corresponding to the defined RVs}
     \label{fig:spot.plus.planet}
@@
 
-We also consider a real-data example using HARPS spectra from the star Alpha Centauri B with an imputed Doppler shift added...
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{SOAP_SPOT_PLANET_Comparison_para_SN.pdf} 
+   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a spot is present on the photosphere of the star and a planet is injected.}
+    \label{fig:spot.plus.planet.corr}
+\end{figure*}
+
+As final step, we removed to the RVs obtained in this case and shown in Figure \ref{fig:spot.plus.planet}(left), the signals coming from the spot, whose spurious RV effects were displayed in Figure \ref{fig:spot}.
+The results, presented in Figure \ref{fig:planet-spot}, show that the periodic pure doppler shift caused by the planet is detected.
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 2.5in]{RV_comparison_PLANET.pdf} 
+%\includegraphics[height = 2.5in]{SOAP_PLANET_Comparison_para_SN.pdf} 
+   \caption{RVs changes as function of the phase after removed the spurious effect of the spot. In green the real signal of the planet is displayed.}
+    \label{fig:planet-spot}
+\end{figure*}
 
@@
 
+We also consider a real-data example using HARPS spectra from the star Alpha Centauri B with an imputed Doppler shift added...
+
+\umberto{to be done}
+
 %-----------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN distribution defined in Section \ref{sec:3} versus the Normal approach.
-Other 4 stars have been analyzed with the proposed methods and details can be found in the Appendix \ref{appendix}.
+In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN distribution defined in Section \ref{sec:3} with the Normal approach.
+Other 4 stars have been analyzed with the proposed method and details can be found in the Appendix \ref{appendix}.
 For all the stars that have been considered in the present work, we selected those CCFs having SNR larger than 10.
@@
  A comparison with the results obtained by the classic approach is done, where the RVs of the star are estimated by retrieving the mean of the Normal distribution used to fit the CCF, along with the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}.
-The latter parameters are calculated separately from the Normal fit that leads to the RV of the star.
+The latter parameters are calculated separately from the Normal fit that leads to the set of RVs of the star.
 
@@
 
-We begin by evaluating the correlation between $\gamma$ and the BIS SPAN.
-In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.99$ and a strong Pearson correlation coefficient of $0.96$.
+We begin the analyses by evaluating the correlation between $\gamma$ and the BIS SPAN.
+In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.72$ and a strong Pearson correlation coefficient of $0.954$.
 This comparison is useful because $\gamma$ is an adimensional parameter taking information about the asymmetry of the SN while the BIS SPAN, beyond this, has got unit of measure of \kms.
-In other words, by using Fig.~\ref{fig:alphacent:corr.gamma}, it is possible to provide to $\gamma$ a physical meaning.
+In other words, by using Fig.~\ref{fig:alphacent:corr.gamma}, it is possible to provide a physical meaning to $\gamma$.
 %
@@
 When using SN mean RV, it is possible to observe more variations than the one present in the RVs measured by the Normal fitting.
-\comment{This is not at all clear from the figure.
-Is there a way to quantify this?}This happens because the mean of the SN is more sensitive to stellar activity.
+In Section \ref{sec:5} we will discuss in detail the reasons leading to this aspect.
+This happens because the mean of the SN is more sensitive to stellar activity.
 In fact, because the SN includes an asymmetry parameter, a RV defined as SN mean gets more shifted in the direction of the asymmetry induced by stellar activity.
@@
 Both indicators can be used to capture and summarise the different information available in the CCF, as will be shown in the remainder of this work.
-\comment{How can you be sure that the higher scatter in your measurement error is not simply due to the fact that you have an inferior measurement technique?
-This can be answered by isolating the RV contribution from activity (from the asymmetry).
-Is this random (noise) or is there structure (activity).} \comment{If you are interested in using the RV signal due to activity to measure the rotation period, effects of activity, etc., why not just show the RVs due to the activity signal alone.?}
 %
@@
 
-\jessi{Add intro to appendix}
-
-\umberto{I suggest to outline here shortly the characteristics of the considered stars. Then we summarize/compare the results presenting Table \ref{table:summaryStars} and finally we show the plots.}
-\umberto{for each star there are always the same $3$ plots: 
-\begin{itemize}
-\item RVs vs. JD
-\item $\gamma$ vs. Bis-Span
-\item Comparison on the correlation between asymmetry parameters (or FWHM) and RV.
-\end{itemize}
-
-Do we need to show all these plots?}
+In this Appendix we summarized the analyses run on other 4 stars: HD192310, HD10700, HD215152 and finally Corot-7.
+Table \ref{table:summaryStars} outlines the comparison between the results obtained by the SN fits and the ones based on the Normal distribution.
+The results are all consistent with the conclusions presented in the paper.
+The correlation between $\gamma$ and the parameter SN mean RV is stronger than the correlation between the BIS SPAN and the mean of the Normal for all the considered stars.
 
@@
 \begin{table}[!t]
-\scalebox{0.5}{
+\scalebox{0.45}{
 \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
@@
 \hline
- $\text{HD}192310  $          &    $1576$    & $0.883$ & $0.812$ & $0.682 (0.655; 0.707)$ & $0.33 (0.285; 0.373)$  & $-0.335 (-0.378; -0.29)$ & $0.677 (0.650; 0.703)$ & $0.475 (0.436; 0.513)$\\
+ $\text{HD}192310  $          &    $1577$    & $0.888$ & $0.786$ & $0.669 (0.64; 0.695)$ & $0.329 (0.285; 0.373)$  & $-0.333 (-0.376; -0.289)$ & $0.666 (0.637; 0.692)$ & $0.476 (0.4367 0.514)$\\
 \hline
- $\text{HD}10700 $            &    $7928$    & $0.795$ & $0.749$ & $0.436 (0.418; 0.454)$ & $-0.073 (-0.095; -0.0051)$ & $0.127 (0.105; 0.148)$ & $0.291 (0.270; 0.311)$ & $0.529 (0.513; 0.545)$ \\
+ $\text{HD}10700 $            &    $7928$    & $0.78$ & $0.604$ & $0.322 (0.302; 0.342)$ & $-0.073 (-0.095; -0.0051)$ & $0.127 (0.105; 0.148)$ & $0.421 (0.403; 0.439)$ & $0.529 (0.513; 0.545)$ \\
 \hline
@@
 \hline
- $\text{Corot }7$     &     $173$    &  $0.797$  & $0.64$ & $0.561 (0.450; 0.656)$ & $0.092 (-0.058; 0.238)$ & $-0.335 (-0.228; -0.082)$ & $-0.709 (0.626;0.776)$ & $0.595 (0.489; 0.683)$ \\
+ $\text{Corot }7$     &     $173$    &  $0.814$  & $0.607$ & $0.561 (0.450; 0.656)$ & $0.092 (-0.058; 0.238)$ & $-0.335 (-0.228; -0.082)$ & $-0.709 (0.626;0.776)$ & $0.595 (0.489; 0.683)$ \\
 \hline
@@
 
-\subsection{HD192310}  \label{sec:Gl785}
+%\subsection{HD192310}  \label{sec:Gl785}
 %
@@
    \centering
-\includegraphics[height = 4in]{[0]HD19231_vs_time.pdf} 
+\includegraphics[height = 3in]{[0]HD19231_HistogramsDiff.pdf} 
    \caption{RVs comparison for HD192310 considering a Normal and a SN fitting (using both the mean and the median).}
@@
    \centering
-\includegraphics[height = 4in]{HD19231_[2]gamma_vs_bisspan.pdf} 
+\includegraphics[height = 3in]{HD19231_[2]gamma_vs_bisspan.pdf} 
    \caption{Correlation between $\gamma$ and the BIS SPAN for HD192310.}
@@
    \centering
-\includegraphics[height = 4in]{HD19231_[4]Comparison_para.pdf} 
+\includegraphics[height = 3in]{HD19231_[4]Comparison_para.pdf} 
    \caption{Correlation between the asymmetry parameters and the RVs for HD 192310.
@@
 
-\subsection{Tau Ceti}  \label{sec:Taucet}
+%\subsection{Tau Ceti}  \label{sec:Taucet}
 %
@@
    \centering
-\includegraphics[height = 4in]{[0]TauCeti_vs_time.pdf} 
+\includegraphics[height = 3in]{[0]TauCeti_HistogramsDiff.pdf} 
    \caption{RVs comparison for Tau Ceti considering a Normal and a SN fitting (using both the mean and the median).}
@@
    \centering
-\includegraphics[height = 4in]{HD10700_[2]gamma_vs_bisspan.pdf} 
+\includegraphics[height = 3in]{HD10700_[2]gamma_vs_bisspan.pdf} 
    \caption{Correlation between $\gamma$ and the BIS SPAN for Tau Ceti.}
@@
    \centering
-\includegraphics[height = 4in]{HD10700_[4]Comparison_para.pdf}  
+\includegraphics[height = 3in]{HD10700_[4]Comparison_para.pdf}  
    \caption{Correlation between the asymmetry parameters and the RVs for Tau Ceti.
@@
 
-\subsection{HD215152}  \label{sec:HD215152}
+%\subsection{HD215152}  \label{sec:HD215152}
 %
@@
    \centering
-\includegraphics[height = 4in]{[0]HD21515_vs_time.pdf} 
+\includegraphics[height = 3in]{[0]HD21515_HistogramsDiff.pdf} 
    \caption{RVs comparison for HD215152 considering a Normal and a SN fitting (using both the mean and the median).}
@@
    \centering
-\includegraphics[height = 4in]{HD21515_[2]gamma_vs_bisspan.pdf} 
+\includegraphics[height = 3in]{HD21515_[2]gamma_vs_bisspan.pdf} 
    \caption{Correlation between $\gamma$ and the BIS SPAN for HD 215152.}
@@
    \centering
-\includegraphics[height = 4in]{HD21515_[4]Comparison_para.pdf}  
+\includegraphics[height = 3in]{HD21515_[4]Comparison_para.pdf}  
    \caption{Correlation between the asymmetry parameters and the RVs for HD 215152.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Corot-7}  \label{sec:Corot7}
+%\subsection{Corot-7}  \label{sec:Corot7}
 %
@@
    \centering
-\includegraphics[height = 4in]{[0]LRa01_E_vs_time.pdf} 
+\includegraphics[height = 3in]{[0]LRa01_E_HistogramsDiff.pdf} 
    \caption{RVs comparison for Corot-7 considering a Normal and a SN fitting (using both the mean and the median).}
@@
    \centering
-\includegraphics[height = 4in]{LRa01_E_[2]gamma_vs_bisspan.pdf} 
+\includegraphics[height = 3in]{LRa01_E_[2]gamma_vs_bisspan.pdf} 
    \caption{Correlation between $\gamma$ and the BIS SPAN for Corot-7.}
@@
    \centering
-\includegraphics[height = 4in]{LRa01_E_[4]Comparison_para.pdf} 
+\includegraphics[height = 3in]{LRa01_E_[4]Comparison_para.pdf} 
    \caption{Correlation between the asymmetry parameters and the RVs for Corot-7.

### 2018-05-08 manuscript.tex
Add files via upload

@@
 \begin{equation} \label{def:snd_gen}
-SN(y;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\frac{\alpha(y-\xi)}{\omega}\right)
+SN(y;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\frac{\alpha(y-\xi)}{\omega}\right),
 \end{equation}
@@
 We then write $Y \sim SN(\xi, \omega^{2}, \alpha)$ to mean that the random variable $Y$ follows the noted SN distribution.
-Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Fig.~ \ref{fig:SN.plot}.
-A usual Normal distribution is the special case of the SN distribution when the skewness parameter, $\alpha$, is equal to 0.\footnote{This can be seen from Equation~\eqref{def:snd_gen}.
+Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Fig.~\ref{fig:SN.plot}.
+A usual Normal distribution is the special case of the SN distribution when the skewness parameter, $\alpha$, is equal to 0.\footnote{This can be seen from Eq.~\eqref{def:snd_gen}.
 If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0)$; this is the the probability a standard Normal random variable is less than or equal to 0, which is $0.5$.
@@
    \centering
-\includegraphics[height = 4in]{Skew_Normal_densities_jjck.pdf} 
-   \caption{Density function of a random variable $Y \sim SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$, and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
-Note that the solid black line has an $\alpha = 0$ making it a Normal distribution.   
-   }
+\includegraphics[height = 3in]{Skew_Normal_densities_jjck.pdf} 
+   \caption{Density function of a random variable $Y \sim SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
+Note that the solid black line has an $\alpha = 0$, making it a Normal distribution.}
    \label{fig:SN.plot}
@@
 For reasons related to the interpretation of the parameters in Equation~\eqref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used, which is referred to as the \emph{centered parametrization} (CP).
-We will be using the CP in this work, which includes a mean parameter $\mu$, a variance parameter $\sigma^2$, and a skewness parameter $\gamma$.
+We will be using the CP in this work, which includes a mean parameter $\mu$, a variance parameter $\sigma^2$ and a skewness parameter $\gamma$.
 In order to define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of the one used in the Equation~\eqref{def:snd_gen} with $(\xi, \omega^2, \alpha)$ by
@@
 \begin{equation} \label{eq:snd_cp}
-\mu = \xi + \omega \beta, \quad \sigma^{2} = \omega^{2}(1-\beta^2), \quad \gamma = \frac{1}{2}(4-\pi) \beta^{3}\left(1-\beta^2\right)^{-3/2}
+\mu = \xi + \omega \beta, \quad \sigma^{2} = \omega^{2}(1-\beta^2), \quad \gamma = \frac{1}{2}(4-\pi) \beta^{3}\left(1-\beta^2\right)^{-3/2},
 \end{equation}
@@
 
-By using Eq.
-\ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution.
-For the $\alpha$ values used in Fig.~~\ref{fig:SN.plot}, the corresponding values of $\mu$, $\sigma^2$, $\gamma$ are displayed in Table~\ref{tab:cp_values}.
-In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution (rather than simply a location and scale parameter), and $\gamma$ becomes an index for evaluating the asymmetry of the SN.
+By using Eq.~\eqref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution.
+For the $\alpha$ values used in Fig.~\ref{fig:SN.plot}, the corresponding values of $\mu$, $\sigma^2$, $\gamma$ are displayed in Table~\ref{tab:cp_values}.
+In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution (rather than simply a location and scale parameter) and $\gamma$ becomes an index for evaluating the skewness of the SN.
 
-Beyond the mean of the SN, it is convenient to introduce a second location parameter that will be largely used in the analyses: the median. The median of the SN is defined as that value $m$ such that 
+Beyond the mean of the SN, we introduce a second location parameter that will be largely used in the analyses: the median.
+The median of the SN, and in general the median of an absolute continuous random variable, is defined as that value $m$ such that
 %
@@
 %
-where $SN(y;\xi, \omega, \alpha)$ follows Equation \ref{def:snd_gen}.\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}
+where $SN(y;\xi, \omega, \alpha)$ follows Eq.~\eqref{def:snd_gen}.\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}
 
@@
    \end{tabular}
-   \caption{CP values, $(\mu, \sigma^2, \gamma)$, corresponding to the $\alpha$ values from Fig.~~\ref{fig:SN.plot} (with location parameter $\xi = 0$ and scale parameter $\omega = 1$) using Equation~\eqref{eq:snd_cp}.
+   \caption{CP values, $(\mu, \sigma^2, \gamma)$, corresponding to the $\alpha$ values from Fig.~\ref{fig:SN.plot} (with location parameter $\xi = 0$ and scale parameter $\omega = 1$) using Eq.~\eqref{eq:snd_cp}.
 Values are rounded to three decimal places.}
@@
 %
-Further details about the parametrization from Equation~\eqref{def:snd_gen} (called \emph{Direct Parametrization} or DP), the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
+Further details about the parametrization from Eq.~\eqref{def:snd_gen} (called \emph{Direct Parametrization} or DP), the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
 
@@
 %The CCF represents the average shape of spectral lines and is expressed in flux as a function of radial-velocity.
-The SN density shape is used to model the CCF.  In particular, the following function is fit using least-squares estimation,
+The SN density shape is used to model the CCF.  In particular, using least-squares algorithm, we fit the following function:
 %
@@
 %
-where C is an unknown offset fitting the continuum of the CCF, A is an unknown amplitude parameter, and $y_1, \ldots, y_n$ are the set of RV's considered for the CCF.
+where C is an unknown offset fitting the continuum of the CCF, A is an unknown amplitude parameter and $y_1, \ldots, y_n$ are the set of RV's considered for the CCF.
 Note that the CCF is expressed in flux as a function of the lag of the cross-correlation template, expressed in RV.
 
-Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution can better catch this aspect, together with other changes in asymmetry, respect the Normal fit.
-To check this assumption, we compared the CCF residuals after fitting a Normal and a SN distribution for 2 stars.
+Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution should in principle better catch this aspect, together with other changes in asymmetry, respect the Normal fit.
+To initially check this assumption, we compared the CCF residuals after fitting a Normal and a SN distribution for 2 stars.
 The first star is Alpha Centauri b, whose CCFs have high signal-to-noise ratio (SNR).
 The second star is Corot-7, whose CCFs have low SNR.
-Fig.~ \ref{fig:Residual.comparison} shows that the SN seems to be a slightly better model to explain the shape of the CCF, in particular as the SNR decreases.
+Fig.~\ref{fig:Residual.comparison} shows that the SN seems to be a slightly better model to explain the shape of the CCF, in particular as the SNR decreases.
 %
@@
 \includegraphics[height = 2.5in]{[1]LRa01_E2Residuals.pdf} 
-   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCFs of the star Alpha Centauri b (left) and Corot-7 (right).
-The results are comparable looking at the residuals corresponding to the tails of the CCF but the SN fit leads to slightly better results in the center of the CCF for both the stars.
-As the signal-to-noise decreases, as happens when analyzing the star Corot-7, the SN distribution leads to better residuals respect using the Normal.}
+   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCFs from the star Alpha Centauri b (left) and Corot-7 (right).
+When looking at the residuals corresponding to the tails of the CCF, the results derived by the two fits are comparable.
+However, when focusing on the center of the CCF, the SN fit leads to slightly better results for both the stars.
+Moreover, as the SNR decreases, the SN distribution shows smaller residuals respect the Normal ones.}
     \label{fig:Residual.comparison}
@@
 
-In the following of the paper, we define RV as the mean of the Normal.
-Concerning the fit of the CCF using the SN, we present at first $2$ indicators that define the RV of the star: the mean of the SN, defined as SN mean RV and the median of the SN, defined as SN median RV (i.e.
-looking at Equation \eqref{eq:snmed}, $m$ = SN median RV).
-We will discuss advantages and limits for both these choices in the examples.
+In the following of the paper, we define RV as the mean of the Normal distribution.
+Concerning the fit of the CCF using the SN, we present at first $2$ indicators that define the RV of the star: the mean of the SN, defined as RV mean SN and the median of the SN, defined as RV median SN (i.e.
+realling Eq.\eqref{eq:snmed}, $m$ = RV median SN).
+We will discuss advantages and limits for both these choices in Section \ref{sec:4} and Section \ref{sec:5}.
 For the width of the CCF, we use the FWHM of the Normal, which is $2\sqrt(2\ln2)\sigma$.
@@
 Being a Normal distribution symmetric, there is not such a parameter that evaluates the asymmetry of the distribution, so the BIS SPAN is used.
-This will be compared to the asymmetric parameter $\gamma$ of the SN, called SN GAMMA.
-To test the strength of the correlation between the RVs and the different activity indicators, we calculated the Pearson correlation coefficient, $R$.
+The BIS SPAN will be compared to the asymmetric parameter $\gamma$ of the SN, named SN GAMMA.
+To test the strength of the correlation between the RVs and the different indicators for stellar activity, we calculated the Pearson correlation coefficient, $R$.
 A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ (i.e., no correlation) is provided, along with a $95\,\%$ confidence interval for $R$.
@@
 \section{Simulation Study} \label{sec:soap}
-In order to evaluate the performance of the proposed SN approach for modeling the CCF, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}...
+In order to evaluate the performance of the proposed SN approach for modeling the CCF, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.
+
+\umberto{Add more information on SOAP, the way we retrieve the CCFs with SOAP, the characteristics of the CCF (i.e. how many points, ...) and the reasons why we need CCFs simulated with SOAP.}
+\umberto{Specify characteristic of the star.}
+
+\umberto{Add info on the standard errors about the asymmetry parameter and the width and make a comparison with the results from the bootstrap. Then right discussions and conclusions,}
 
@@
 
-\umberto{specify characteristic of the faculae}
+\umberto{Specify characteristic of the faculae.}
 
-Figure \ref{fig:faculae} shows the results obtained when a faculae is present on the photosphere of the star.
-It is possible to note that, although there is not a planet, the presence of the faculae leads to spurious variations in RVs for all the proposed indicator.
-The evaluation of the standard errors, which details will be discussed in Section \ref{sec:5}, shows that the RV defined as mean SN has the largest variability.
-The standard errors associates with median SN and mean Normal are comparable, although the standard errors retrieved when the RV is defined as the median of the SN are $10 \%$ smaller.
+Fig.~\ref{fig:faculae} shows the results obtained when a faculae is present on the photosphere of the star.
+It is possible to note that, although there is not a planet, the presence of the faculae leads to spurious variations in RVs for all the proposed indicators.
+SN mean RV seems to have the smallest spurious variations caused by the faculae.
+Anyway, the evaluation of the standard errors retrieved by using a bootstrap analysis that will be detailed discussed in Section \ref{sec:5}, shows that RV mean SN has the largest related uncertainties.
+The standard errors associates with RV median SN and RV are comparable, although the standard errors retrieved when the RV is defined as the median of the SN are $10 \%$ smaller than the standard errors derived for RV.
 
-Since in this case we know that the variations in RV are only caused by the faculae, the evaluation of the correlation between the set of RVs and the asymmetry parameters is important.
-Figure \ref{fig:faculae.corr} summarises the correlations obtained using as RV respectively mean SN, median SN and mean Normal.
-The $\gamma$ parameter shows a stronger correlation with the median SN ($-0.944$) than what the other asymmetry indicators do with their corresponding RVs.
-The correlation between the CCF width and the RVs is also stronger when fitting a SN rather than a Normal.
+Since in this case we know that the variations in RV are only caused by the faculae, the evaluation of the correlations between the set of RVs and the asymmetry parameters can provide relevant information to understand the cause of the variations observed in RVs.
+Fig.~\ref{fig:faculae.corr} shows the correlations obtained using as RV respectively RV mean SN, RV median SN and RV.
+The $\gamma$ parameter shows a correlation with RV median SN equal to $-0.944$, which is stronger than the correlations between the other asymmetry indicators and their estimated RVs.
+The correlation between the width of the CCF and RV mean SN is the strongest one ($R^{2}=0.655$).
 
@@
 \includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
-   \caption{(left) RVs changes as function of the phase in the case in which a faculae is present on the photosphere of the star.
-(right) Evaluation of the standard errors corresponding to the defined RVs.}
+   \caption{(left) RVs changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
+SN mean RV seems to have the smallest spurious variations caused by the faculae.
+(right) Evaluation of the standard errors corresponding to the defined RVs.
+The standard errors retrieved for RV median SN are $10 \%$ smaller than the standard errors derived for RV.
+RV mean SN has the largest related uncertainties.}
     \label{fig:faculae}
@@
 \includegraphics[height = 4in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
-   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a faculae is present on the photosphere of the star.}
+   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a faculae is present on the photosphere of the star.
+In this case both the shape and the width of the CCF changes as the faculae moves, producing statistically significative correlation between the RVs and respectively the asymmetry parameter and the width parameter.}
     \label{fig:faculae.corr}
@@
 
-\umberto{specify characteristic of the spot}
+\umberto{Specify characteristic of the spot.}
 
-Figure \ref{fig:spot} shows the results obtained when a spot is present on the photosphere of the star.
-Similarly to the previous case, the presence of the spot leads to spurious variations in RVs for all the proposed indicator.
-The evaluation of the standard errors shows that the RV defined as mean SN has the largest variability and, as before, the standard errors associated with the median SN are $10 \%$ smaller than the standard errors associated with the mean Normal.
+Fig.~\ref{fig:spot} shows the results obtained when a spot is present on the photosphere of the star.
+Similarly to the previous case, the presence of the spot leads to spurious variations in RVs for all the proposed indicators, but N mean RV seems to have the smallest ones.
+The evaluation of the standard errors, as before, shows that RV mean SN has the largest variability, while the standard errors associated with RV median SN are $10 \%$ smaller than the standard errors associated with RV.
 
-Figure \ref{fig:spot.corr} summarises the correlations obtained using as RV respectively mean SN, median SN and mean Normal.
-It is possible to see that the correlation between the asymmetry parameters and the RVs are weaker than the previous case, because of the presence of the planet.
-The correlation between the CCF width and the RVs is slightly stronger when fitting a SN rather than a Normal, although in this latter case the presence of the spot is largely masquerade from the planet.
+Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and respectively RV mean SN, RV median SN and RV.
+The correlation between $\gamma$ and RV median SN is equal to $-0.89$ while the correlation between $\gamma$ and RV median SN is equal to $-0.82$.
+Both these correlations are stronger than the correlation between the BIS SPAN and RV ($R^2=-0.77$).
+The correlations between the width of the CCF and the corresponding RVs are slightly stronger when fitting a SN rather than a Normal distribution, as shown in the left series of plots in Fig.~\ref{fig:spot.corr}.
+The results shows anyway a correlation close to $0$, suggesting that the presence of a spot on the photosphere of star changes the shape of the CCF rather than its width.
 
@@
 \includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
-   \caption{(left) RVs changes as function of the phase in the case in which a spot is present on the photosphere of the star.
-(right) Evaluation of the standard errors corresponding to the defined RVs.}
+   \caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
+SN mean RV seems to have the smallest spurious variations caused by the faculae.
+(right) Evaluation of the standard errors corresponding to the defined RVs.
+The standard errors retrieved for RV median SN are $10 \%$ smaller than the standard errors derived for RV.
+RV mean SN has the largest related uncertainties.}
     \label{fig:spot}
@@
 \includegraphics[height = 4in]{SOAP_SPOT_Comparison_para_SN.pdf} 
-   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a spot is present on the photosphere of the star.}
+   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a spot is present on the photosphere of the star.
+In this case only the shape of the CCF changes as the spot moves, producing statistically significative correlations only between the RVs and the asymmetry parameter.}
     \label{fig:spot.corr}
@@
 
-Figure \ref{fig:spot.plus.planet} shows the results obtained when not only a spot is present on the photosphere of the star but, respect to the previous case, a planet is injected.
-The planet has amplitude equal to 10 \ms.
-The evaluation of the standard errors shows that the RV defined as mean SN has the largest variability and, as before, the standard errors associated with the median SN are $10 \%$ smaller than the standard errors associated with the mean Normal.
+\umberto{Specify characteristic of the spot.}
 
-Figure \ref{fig:spot.plus.planet.corr} summarises the correlations obtained using as RV respectively mean SN, median SN and mean Normal.
-The $\gamma$ parameter shows a stronger correlation with the median SN ($-0.89$) than what the other asymmetry indicators do with their corresponding RVs.
-The correlation between the CCF width and the RVs is also stronger when fitting a SN rather than a Normal.
+Fig.~\ref{fig:spot.plus.planet} shows the results obtained when a spot is present on the photosphere of the star and a planet is injected.
+The planet, having an amplitude of 10 \ms, produces a pure doppler shift on the CCF, without further changing its shape.
+In this case N mean RV seems to have the largest variations caused by the combined action of spot and planet.
+The evaluation of the standard errors leads to the same conclusions reported for the two previous cases: RV mean SN has the largest related uncertainties and the standard errors associates with RV median SN are $10 \%$ smaller than the standard errors derived for RV.
+
+Fig.~\ref{fig:spot.plus.planet.corr} shows the correlations between $\gamma$ and respectively RV mean SN and RV median SN and the correlation between BIS SPAN and RV.
+In this case the correlations are weaker than the ones derived when only a spot is present on the photosphere of the star.
+Anyway the $\gamma$ parameter shows a correlation with the median SN of $-0.433$, which is stronger than what the correlation between the other asymmetry indicators and their corresponding RVs.
+The correlations between the width of the CCF and the corresponding RVs are comparable and, similarly to the previous case, close to $0$.
 
@@
 \includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
-   \caption{(left) RVs changes as function of the phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
-(right) Evaluation of the standard errors corresponding to the defined RVs}
+   \caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
+N mean RV seems to have the largest variations caused by the combined action of spot and planet.
+(right) Evaluation of the standard errors corresponding to the defined RVs.
+The standard errors retrieved for RV median SN are $10 \%$ smaller than the standard errors derived for RV.
+RV mean SN has the largest related uncertainties}
     \label{fig:spot.plus.planet}
@@
 \includegraphics[height = 4in]{SOAP_SPOT_PLANET_Comparison_para_SN.pdf} 
-   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a spot is present on the photosphere of the star and a planet is injected.}
+   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a spot is present on the photosphere of the star and a planet is injected.
+In this case only the shape of the CCF changes as the spot moves, producing statistically significative correlations only between the RVs and the asymmetry parameter.
+The correlations between the RVs and the width parameter of the CCF is weaker than the previous case that considers only the presence of a spot on the photosphere of the star.}
     \label{fig:spot.plus.planet.corr}
@@
 
-As final step, we removed to the RVs obtained in this case and shown in Figure \ref{fig:spot.plus.planet}(left), the signals coming from the spot, whose spurious RV effects were displayed in Figure \ref{fig:spot}.
-The results, presented in Figure \ref{fig:planet-spot}, show that the periodic pure doppler shift caused by the planet is detected.
+As final step we removed to the RVs obtained in this case those spurious signals coming from the spot.
+The results, presented in Fig.~\ref{fig:planet-spot}, show that the periodic pure doppler shift caused by the planet is detected.
 
@@
    \centering
-\includegraphics[height = 2.5in]{RV_comparison_PLANET.pdf} 
+\includegraphics[height = 3in]{RV_comparison_PLANET.pdf} 
 %\includegraphics[height = 2.5in]{SOAP_PLANET_Comparison_para_SN.pdf} 
-   \caption{RVs changes as function of the phase after removed the spurious effect of the spot. In green the real signal of the planet is displayed.}
+   \caption{RVs changes as function of the orbital phase after removed the spurious effect of the spot. In green the real signal of the planet is displayed.}
     \label{fig:planet-spot}
 \end{figure*}
+
+In this Section we presented a first implementation of the SN fit to CCF, using the simulation environment SOAP.
+Before moving to the next Section, where the analyses on five real stars are presented, we need to provide further considerations.
+First of all, looking ad the analyses conducted with SOAP, it seems that the largest correlation between an asymmetry parameter and a set of RVs happens to be when respectively $\gamma$ and RV median SN are used.
+This is a bit surprising, since as the shape of the CCF changes, we expect RV median SN to be more robust than RV mean SN.
+\umberto{A possible justification of this ...}.
+As second, the standard errors that have been retrieved suggest that using RV median SN can minimize the uncertainties respect using both RV mean SN and RV.
+We will present details of this in Section \ref{sec:5}.
+As third, when searching for stellar activity by deriving the correlation between the set of RVs and either an asymmetry parameter or the width of the CCF, the latter leads to weaker and hence less conclusive results if the active region is a spot.
+When stellar activity is dominated by faculae, both the shape and the width of the CCF changes as the faculae evolves on the photosphere of the star.
+Finally, the correlations involving the common indicators (i.e.
+RV, FWHM and BIS SPAN) are systematically weaker than the correlations obtained by fitting the SN to the CCF, suggesting that this distribution could be helpful when searching for active regions.
+We recall moreover that all the quantities needed for conducting the analyses of the CCF are directly available by just fitting the SN.
 
@@
 
-In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN distribution defined in Section \ref{sec:3} with the Normal approach.
-Other 4 stars have been analyzed with the proposed method and details can be found in the Appendix \ref{appendix}.
+In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN distribution defined in Section \ref{sec:3} with the approach based on the Normal distribution.
+Other four stars have been analyzed with the proposed method and details can be found in the Appendix \ref{appendix}.
 For all the stars that have been considered in the present work, we selected those CCFs having SNR larger than 10.
@@
 
-Fig.~ \ref{fig:alphacent:diff:RV} shows the comparison between the RVs retrieved using the SN shape and the ones obtained with the Normal shape.
+Fig.~\ref{fig:alphacent:diff:RV} shows the comparison between the RVs retrieved using the SN shape and the ones obtained with the Normal shape.
 It is possible to appreciate the presence of a strong stellar activity signal, as expected \citep{Dumusque-2012,Thompson-2017}.
-When using SN mean RV, it is possible to observe more variations than the one present in the RVs measured by the Normal fitting.
-In Section \ref{sec:5} we will discuss in detail the reasons leading to this aspect.
+When using RV mean SN, it is possible to observe more variations than the ones measured by the Normal fitting.
 This happens because the mean of the SN is more sensitive to stellar activity.
-In fact, because the SN includes an asymmetry parameter, a RV defined as SN mean gets more shifted in the direction of the asymmetry induced by stellar activity.
-On the other hand, when using SN median RV, smaller variations in RV are caused by changes in the asymmetry of the CCF, because this second location parameter is a more robust indicator than the mean.
-The bottom plot of Fig.~ \ref{fig:alphacent:diff:RV} captures this aspect.
+In fact, because the SN includes an asymmetry parameter, RV mean SN gets more shifted in the direction of the asymmetry induced by stellar activity.
+On the other hand, when using RV median SN, smaller variations in RV are caused by changes in the asymmetry of the CCF, because this second location parameter is a more robust indicator than the mean.
+The bottom plot of Fig.~\ref{fig:alphacent:diff:RV} captures this aspect.
 Both indicators can be used to capture and summarise the different information available in the CCF, as will be shown in the remainder of this work.
@@
    \caption{(top) RVs as function of Julian Day for Alpha Centauri b.
-The RVs are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses).
-(bottom) RV differences between Normal RV and SN mean RV (black circles) and between Normal RV and a SN median RV (cyan crosses).}
+The RVs are retrieved using the mean of the Normal (red triangles), RV mean SN (black circles), RV median SN (cyan crosses).
+(bottom) RV differences between Normal RV and RV mean SN (black circles) and between Normal RV and a RV median SN (cyan crosses).}
    \label{fig:alphacent:diff:RV}
@@
 Similar to \citet{Figueira-2013}, we compare the correlation between the different activity indicators and the RVs of the star in Fig.~\ref{fig:alphacent:corrPlot}.
-The correlation between $\gamma$ and SN mean RV and the correlation between $\gamma$ and SN median RV are much stronger than the correlation calculated between the other asymmetry parameters and their corresponding RVs.
-In particular the correlation between $\gamma$ and SN mean RV is almost twice the correlation between the other asymmetry parameters and their corresponding RVs.
+The correlation between $\gamma$ and RV mean SN and the correlation between $\gamma$ and RV median SN are much stronger than the correlations calculated between the other asymmetry parameters and their corresponding RVs.
+In particular the correlation between $\gamma$ and RV mean SN is almost twice the correlation between the other asymmetry parameters and their corresponding RVs.
 
-Because the median is a more rubust index than the mean, the correlation between $\gamma$ and SN median RV is not as large as the correlation between $\gamma$ and SN mean RV, but it is nonetheless $1.5$ times larger than the correlation between the other common asymmetry parameters and their corresponding RVs.
-In other words, changes in the asymmetry of the CCF are better captured when using the SN mean RV.
-The correlation between FWHM and the RVs, either by using SN mean RV or SN median RV, is as well stronger when fitting a SN distribution rather than a Normal.
+Because the median is a more rubust index than the mean, the correlation between $\gamma$ and RV median SN is not as large as the correlation between $\gamma$ and RV mean SN, but it is nonetheless $1.5$ times larger than the correlation between the other common asymmetry parameters and their corresponding RVs.
+In other words, changes in the asymmetry of the CCF are better captured when using the RV mean SN.
+The correlation between FWHM and the RVs, either by using RV mean SN or RV median SN, is as well stronger when fitting a SN distribution rather than a Normal.
 All the correlations are statistically different from $0$.
+Recalling the analyses presented in Section \ref{sec:soap}, we could infer that Alpha Centauri b is dominated by faculae, because the correlations between the RVs and the width of the CCF are strong (in particular the correlation between RV mean SN and SN FWHM is $0.817$).
 %
@@
    \caption{Correlation between the asymmetry parameters and the RVs for Alpha Centauri B.
-The last three plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN (SN mean RV and SN median RV) and the Normal fits.}
+The last three plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN (RV mean SN and RV median SN) and the Normal fits.
+The correlations are always stronger when using parameters derived from the SN fit than the Normal one.}
    \label{fig:alphacent:corrPlot}
@@
 
-Both the proposed indicators coming from the SN distribution have desirable and undesirable behaviors: the SN mean RV better catches changes in the asymmetry of the CCF but the resulting set of RVs ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Section \ref{intro}.
-When using SN median RV, the final set of radial velocity is less affected by those spurious shifts caused by stellar activity, but at the same time this indicator is not able to catch as well as SN mean RV changes in the shape of the CCF.
-Anyway, both SN mean RV and SN median RV are useful to catch different aspects of the CCF and our suggestion is to use SN mean RV when interested to retrieve information about changes in the shape of the CCF.
-In order to provide a set of RVs containing the smallest amount of spurious contamination imputable to stellar activity, our suggestion is instead to use SN median RV.
+Both the proposed indicators coming from the SN distribution have desirable and undesirable behaviors: RV mean SN better catches changes in the asymmetry of the CCF but the resulting set of RVs ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Section \ref{intro}.
+When using RV median SN, the final set of radial velocity is less affected by those spurious shifts caused by stellar activity, but at the same time this indicator is not able to catch as well as RV mean SN changes in the shape and in the width of the CCF.
+Anyway, both RV mean SN and RV median SN are useful to catch different aspects of the CCF and our suggestion is to use RV mean SN when interested in retrieving information about changes in the shape and/or the width of the CCF.
+In order to provide a set of RVs containing the smallest amount of spurious contamination imputable to stellar activity, our suggestion is to use instead RV median SN.
 
-In the next Section we further motivate the reasons for defining as RV the median of the SN by retrieving the standard errors associated with the RV defined as the mean of the Normal, SN mean and SN median.
+In the next Section we further motivate the reasons to define the RVs derived by the CCF by calculating RV median SN.
+In order to do that, we retrieve the standard errors associated with RV mean SN, RV median SN and RV.
 
@@
 
-In this section, we perform a bootstrap analysis to measure the standard errors associate to the RVs, SN mean RVs and SN median RV, the FWHM or SN FWHM and the BIS SPAN or $\gamma$.
+In this section, we perform a bootstrap analysis to measure the standard errors associated to RV mean SN, RV median SN, RV, FWHM, SN FWHM, BIS SPAN and $\gamma$.
 Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
@@
 To bypass this problem, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF.
-We then fit a Normal or a SN to each of these CCFs, and the standard deviation of the distribution for the mean (RV or SN RV), the width parameter (FWHM or SN FWHM) and the asymmetric parameter ($\gamma$ or BIS SPAN) is associated to the error on each of these parameters.
+We then fit a Normal or a SN to each of these CCFs and then calculate the standard deviations of the distribution for the location parameters (RV mean SN, RV median SN, RV), the width parameters (FWHM or SN FWHM) and the parameters of asymmetry ($\gamma$ or BIS SPAN).
 \comment{It is not clear what you are doing here.
@@
 
-In the top plots of Fig.~\ref{fig:se} we show the different errors for the RV, either defined as mean of the Normal (red triangles), mean of the SN (black circles) or median of the SN (cyan crosses), the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels.
-The parameter SN50 corresponds to the SNR in order 50, which corresponds to a wavelength of 550\,nm.
-In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameter derived from the bootstrap analysis fitting the Normal distribution.
+In the top plots of Fig.~\ref{fig:se} we show the different errors for the RVs, either defined as RV (red triangles), RV mean SN (black circles) or RV median SN (cyan crosses), the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels.
+The parameter SN50 corresponds to the SNR in order 50, which defines a wavelength of 550\,nm.
+In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameters derived from the bootstrap analysis fitting the Normal distribution.
 We first see that the errors on the CCF parameters only depends on the SNR and do not depend on the spectral type.
@@
 
-Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.6$ when using the mean of the SN and $0.9$ when using the median of the SN.
-In other words, by using the median of the SN as parameter for defining the radial velocity, we get standard errors $10\%$ smaller than using the Normal fit.
+Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.6$ when using RV mean SN and $0.9$ when using RV median SN.
+In other words, by using RV median SN as parameter that defines the radial velocity of the star given a CCF, we get standard errors $10\%$ smaller than using the Normal fit and its corresponding mean.
+This result is consistent with what we observed with the simulation from SOAP presented in Section \ref{sec:soap}.
 
-Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal or the SN are comparable.
-Therefore, the precision in CCF width is the same if we fit a Normal or a SN to the CCF.
+Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable.
+Therefore, the precision in the width of the CCF is the comparable if we fit a Normal or a SN to the CCF.
 
-Finally, for the errors in CCF asymmetry, we see that, when fitting the SN to the CCF, the asymmetry errors are $15\%$ smaller.
+Finally, for the errors in evaluating the asymmetry of the CCF, we see that, when fitting the SN to the CCF, the asymmetry errors are $15\%$ smaller.
 Therefore, the SN fit gives a better precision in CCF asymmetry than what can be reached using BIS SPAN.
@@
    \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
-When using as parameter for the RV the mean of the SN (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, once the RV is defined as the median of the SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
-To use as asymmetry parameter the $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
+When using RV mean SN (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using RV median SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
 Note that for the asymmetry, the error in BIS SPAN is in \kms.
@@
 
-An analysis of the CCF residuals after fitting a Normal or SN distribution show that the SN is a slightly better model to explain the shape of the CCF.
+An analysis of the CCF residuals after fitting a Normal or SN distribution shows that the SN is a slightly better model to explain the shape of the CCF.
 This comes from the fact that CCFs present a natural asymmetry due the convective blueshift.
@@
 Therefore, the SN parameters are more sensitive to activity.
-In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of $0.436$ between $\gamma$ and SN mean RV, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.$225$.
+In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of $0.436$ between $\gamma$ and RV mean SN, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.$225$.
 
@@
 For evaluating changes in the asymmetry of the CCF, we suggest to use the mean of the SN.
-The correlations between SN mean RV and SN FWHM, and SN mean RV and $\gamma$ (the asymmetry parameter of the SN) are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
+The correlations between RV mean SN and SN FWHM, and RV mean SN and $\gamma$ (the asymmetry parameter of the SN) are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
 The precision on the asymmetry measured by $\gamma$ is greater than the one on BIS SPAN by $\sim$15\%.
@@
 
-In this Appendix we summarized the analyses run on other 4 stars: HD192310, HD10700, HD215152 and finally Corot-7.
-Table \ref{table:summaryStars} outlines the comparison between the results obtained by the SN fits and the ones based on the Normal distribution.
-The results are all consistent with the conclusions presented in the paper.
-The correlation between $\gamma$ and the parameter SN mean RV is stronger than the correlation between the BIS SPAN and the mean of the Normal for all the considered stars.
+In this Appendix we present the analyses conducted on other 4 stars: HD192310, HD10700, HD215152 and finally Corot-7.
+
+\umberto{Add further information about the stars here presented.}
+
+Table \ref{table:summaryStars} summarizes the results obtained by the SN fit and the some of the results based on the Normal fit.
+The results are all consistent with the conclusions derived by the analyses on Alpha Centauri b.
+The correlation between $\gamma$ and RV mean SN is stronger than the correlation between the BIS SPAN and RV for all the considered stars.
+The correlation between SN FWHM and RV mean SN is stronger than the correlation between FWHM and RV for three of the four stars.
+The analyses of the correlations for the four stars are are presented Fig.
+\ref{fig:Gliese785:corrPlot}, \ref{fig:Tau:corrPlot}, \ref{fig:HD215152:corrPlot} and \ref{fig:Corot7:corrPlot}.
 
@@
 \hline
-\textbf{Star}          &\textbf{ \# CCFs}  &   \textbf{$\text{R}(\text{SN }\gamma, \text{Bis-Span})$} & \textbf{$\text{slope}(\text{SN }\gamma, \text{Bis-Span})$} &   \textbf{$\text{R}(\text{SN }\gamma, \text{SN mean RV})$} & \textbf{$\text{R}(\text{Bis-Span}, \text{RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{SN mean RV})$}  & \textbf{$\text{R}(\text{FWHM}, \text{RV})$} \\
+\textbf{Star}          &\textbf{ \# CCFs}  &   \textbf{$\text{R}(\text{SN }\gamma, \text{Bis-Span})$} & \textbf{$\text{slope}(\text{SN }\gamma, \text{Bis-Span})$} &   \textbf{$\text{R}(\text{SN }\gamma, \text{RV mean SN})$} & \textbf{$\text{R}(\text{Bis-Span}, \text{RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{RV mean SN})$}  & \textbf{$\text{R}(\text{FWHM}, \text{RV})$} \\
 \hline
@@
 
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{HD19231_[4]Comparison_para.pdf} 
+   \caption{Correlation between the asymmetry parameters and the RVs for HD 192310.
+The last three plots show the correlation between the FWHM and the RVs for HD 192310 using respectively the SN and the Normal fits.
+\umberto{faculae???}}
+   \label{fig:Gliese785:corrPlot}
+\end{figure*}
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{HD10700_[4]Comparison_para.pdf}  
+   \caption{Correlation between the asymmetry parameters and the RVs for Tau Ceti.
+The last three plots show the correlation between the FWHM and the RVs for Tau Ceti using respectively the SN and the Normal fits.\umberto{faculae???}}
+   \label{fig:Tau:corrPlot}
+\end{figure*}
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{HD21515_[4]Comparison_para.pdf}  
+   \caption{Correlation between the asymmetry parameters and the RVs for HD 215152.
+The last three plots show the correlation between the FWHM and the RVs for HD 215152 using respectively the SN and the Normal fits.\umberto{spot???}}
+   \label{fig:HD215152:corrPlot}
+\end{figure*}
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{LRa01_E_[4]Comparison_para.pdf} 
+   \caption{Correlation between the asymmetry parameters and the RVs for Corot-7.
+The last three plots show the correlation between the FWHM and the RVs for Corot-7 using respectively the SN and the Normal fits.\umberto{faculae???}}
+   \label{fig:Corot7:corrPlot}
+\end{figure*}
+
+%%%%%%
+\iffalse
 %\subsection{HD192310}  \label{sec:Gl785}
@@
 %
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 3in]{HD19231_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RVs for HD 192310.
-The last two plots show the correlation between the FWHM and the RVs for HD 192310 using respectively the SN and the Normal fits.}
-   \label{fig:Gliese785:corrPlot}
-\end{figure*}
 
@@
 %
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 3in]{HD10700_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RVs for Tau Ceti.
-The last two plots show the correlation between the FWHM and the RVs for Tau Ceti using respectively the SN and the Normal fits.}
-   \label{fig:Tau:corrPlot}
-\end{figure*}
 
@@
 %
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 3in]{HD21515_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RVs for HD 215152.
-The last two plots show the correlation between the FWHM and the RVs for HD 215152 using respectively the SN and the Normal fits.}
-   \label{fig:HD215152:corrPlot}
-\end{figure*}
 
@@
 %
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 3in]{LRa01_E_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RVs for Corot-7.
-The last two plots show the correlation between the FWHM and the RVs for Corot-7 using respectively the SN and the Normal fits.}
-   \label{fig:Corot7:corrPlot}
-\end{figure*}
+\fi
 %

### 2018-05-10 manuscript.tex
Add files via upload

@@
 SN mean RV seems to have the smallest spurious variations caused by the faculae.
-Anyway, the evaluation of the standard errors retrieved by using a bootstrap analysis that will be detailed discussed in Section \ref{sec:5}, shows that RV mean SN has the largest related uncertainties.
+%Anyway, the evaluation of the standard errors retrieved by using a bootstrap analysis that will be detailed discussed in Section \ref{sec:5}, shows that RV mean SN has the largest related uncertainties.
 The standard errors associates with RV median SN and RV are comparable, although the standard errors retrieved when the RV is defined as the median of the SN are $10 \%$ smaller than the standard errors derived for RV.
@@
    \centering
-\includegraphics[height = 2.5in]{RV_comparison_FACULAE.pdf} 
-\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
-   \caption{(left) RVs changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
+\includegraphics[height = 4in]{RV_comparison_FACULAE.pdf} 
+%\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
+\caption{(RVs changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
+SN mean RV seems to have the smallest spurious variations caused by the faculae.}
+   %\caption{(left) RVs changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
 SN mean RV seems to have the smallest spurious variations caused by the faculae.
@@
    \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a faculae is present on the photosphere of the star.
-In this case both the shape and the width of the CCF changes as the faculae moves, producing statistically significative correlation between the RVs and respectively the asymmetry parameter and the width parameter.}
+In this case both the shape and the width of the CCF changes as the faculae moves, producing statistically significative correlations between the RVs and respectively the asymmetry parameter and the width parameter.}
     \label{fig:faculae.corr}
@@
 Similarly to the previous case, the presence of the spot leads to spurious variations in RVs for all the proposed indicators, but N mean RV seems to have the smallest ones.
-The evaluation of the standard errors, as before, shows that RV mean SN has the largest variability, while the standard errors associated with RV median SN are $10 \%$ smaller than the standard errors associated with RV.
+We note however that in this case all the three indicators are similarly effected by the spurious changes in RVs caused by the spot.
+%The evaluation of the standard errors, as before, shows that RV mean SN has the largest variability, while the standard errors associated with RV median SN are $10 \%$ smaller than the standard errors associated with RV.
 
@@
    \centering
-\includegraphics[height = 2.5in]{RV_comparison_SPOT.pdf} 
-\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
-   \caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
+\includegraphics[height = 4in]{RV_comparison_SPOT.pdf} 
+%\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
+\caption{RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
+SN mean RV seems to have the smallest spurious variations caused by the faculae.}
+   %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
 SN mean RV seems to have the smallest spurious variations caused by the faculae.
@@
 In this case N mean RV seems to have the largest variations caused by the combined action of spot and planet.
-The evaluation of the standard errors leads to the same conclusions reported for the two previous cases: RV mean SN has the largest related uncertainties and the standard errors associates with RV median SN are $10 \%$ smaller than the standard errors derived for RV.
+%The evaluation of the standard errors leads to the same conclusions reported for the two previous cases: RV mean SN has the largest related uncertainties and the standard errors associates with RV median SN are $10 \%$ smaller than the standard errors derived for RV.
 
@@
    \centering
-\includegraphics[height = 2.5in]{RV_comparison_PLANET_SPOT.pdf} 
-\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
-   \caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
+\includegraphics[height = 4in]{RV_comparison_PLANET_SPOT.pdf} 
+%\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
+ \caption{RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
+N mean RV seems to have the largest variations caused by the combined action of spot and planet.}
+   %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
 N mean RV seems to have the largest variations caused by the combined action of spot and planet.
@@
 The standard errors retrieved for RV median SN are $10 \%$ smaller than the standard errors derived for RV.
-RV mean SN has the largest related uncertainties}
+RV mean SN has the largest related uncertainties.}
     \label{fig:spot.plus.planet}
@@
    \centering
-\includegraphics[height = 3in]{RV_comparison_PLANET.pdf} 
+\includegraphics[height = 4in]{RV_comparison_PLANET.pdf} 
 %\includegraphics[height = 2.5in]{SOAP_PLANET_Comparison_para_SN.pdf} 
@@
 \umberto{A possible justification of this ...}.
-As second, the standard errors that have been retrieved suggest that using RV median SN can minimize the uncertainties respect using both RV mean SN and RV.
-We will present details of this in Section \ref{sec:5}.
-As third, when searching for stellar activity by deriving the correlation between the set of RVs and either an asymmetry parameter or the width of the CCF, the latter leads to weaker and hence less conclusive results if the active region is a spot.
+As second, when searching for stellar activity by deriving the correlation between the set of RVs and either an asymmetry parameter or the width of the CCF, the latter leads to weaker and hence less conclusive results if the active region is a spot.
 When stellar activity is dominated by faculae, both the shape and the width of the CCF changes as the faculae evolves on the photosphere of the star.
@@
 
-%-----------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Doppler shift added to Alpha Centauri B} \label{sec:soap_real}
-
-We also consider a real-data example using HARPS spectra from the star Alpha Centauri B with an imputed Doppler shift added...
-
-\umberto{to be done}
+We remand the reader to Section \ref{sec:5} for the evaluation of the standard errors associated with the parameters estimated for all the three presented cases.
+This step will point out how RV median SN minimizes the uncertainties respect using both RV mean SN and RV, therefore suggesting its use in order to properly define the set of RVs of the star.
 
@@
 
+%-----------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Doppler shift added to Alpha Centauri B} \label{sec:soap_real}
+
+We also consider a real-data example using HARPS spectra from the star Alpha Centauri B with an imputed Doppler shift added...
+
+\umberto{to be done}
+
 In the next Section we further motivate the reasons to define the RVs derived by the CCF by calculating RV median SN.
@@
 
-%%%%%% April 13th, 2018
-%%% in the new Analyses we do not use the noise parameter
-%%%%%%
-\iffalse
-The HARPS reduction pipeline gives the pure photon-noise error estimate on the RVs.
-This error, called \emph{noise}, is not derived from the Normal fit to the CCF but from the method described in \citet{Bouchy-2001b} using the CCF derivative.
-Then \emph{noise} is associated to the RV error, $2\times$\emph{noise} to the BIS SPAN error and $2.35\times$\emph{noise} to the FWHM error.
-\fi
-%%%%%%
-%%%
-%%%%%% April 13th, 2018
-
 In this section, we perform a bootstrap analysis to measure the standard errors associated to RV mean SN, RV median SN, RV, FWHM, SN FWHM, BIS SPAN and $\gamma$.
@@
 To bypass this problem, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF.
-We then fit a Normal or a SN to each of these CCFs and then calculate the standard deviations of the distribution for the location parameters (RV mean SN, RV median SN, RV), the width parameters (FWHM or SN FWHM) and the parameters of asymmetry ($\gamma$ or BIS SPAN).
+We then fit a Normal or a SN to each of these CCFs and then calculate the standard deviations of the distribution for the location parameters (RV, RV mean SN or RV median SN), the width parameters (FWHM or SN FWHM) and the parameters of asymmetry (BIS SPAN or $\gamma$).
 \comment{It is not clear what you are doing here.
@@
 
+\subsection{Estimation of standard errors for the CCF parameters for the simulation study} \label{sec:bootstrap_soap}
+
+We start by calculating the standard errors of the parameters retrieved in Section \ref{sec:soap}, where with SOAP we produced CCFs contaminated by a faculae or a spot.
+In the third and final case we considered, beyond the spot, a planetary signal that produces pure doppler shifts i the CCFs.
+
+Fig.~\ref{fig:se.soap.faculae} shows the results of the bootstrap analysis performed when a faculae is present on the photosphere of the star.
+The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} show the different errors for the RVs, defined as RV (red triangles), RV mean SN (black circles) or RV median SN (cyan crosses), the width and the asymmetry of the CCFs.
+In the three plots in the bottomof Fig.~\ref{fig:se.soap.faculae} we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameters derived from the bootstrap analysis fitting the Normal distribution.
+Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.5$ when using RV mean SN and $0.9$ when using RV median SN.
+By using RV median SN we get standard errors $10\%$ smaller than using the Normal fit and its corresponding mean.
+Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable.
+Therefore, the precision in the width of the CCF is the comparable if we fit a Normal or a SN to the CCF.
+Finally, for the errors in evaluating the asymmetry of the CCF, we see that, when fitting the SN to the CCF, the asymmetry errors are $20\%$ smaller.
+Therefore, the SN fit gives a better precision in CCF asymmetry than what can be reached using BIS SPAN.
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{RV_comparison_FACULAE_standard_errors.pdf} 
+   \caption{Faculae Case.
+Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
+When using RV mean SN (black circles), the standard errors are in average $50\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using RV median SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN.
+\umberto{explain what happens for those CCF 15 to 19 where s.e.
+decrease.} Note that for the asymmetry, the error in BIS SPAN is in \kms.
+To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
+   \label{fig:se.soap.faculae}
+\end{figure*}
+
+Fig.~\ref{fig:se.soap.spot} shows the results of the bootstrap analysis performed when a spot is present on the photosphere of the star.
+The series of plots follows the specifications outlined for the previous case.
+Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$ when using RV mean SN and $0.9$ when using RV median SN.
+Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable.
+Therefore, the precision in the width of the CCF is the comparable if we fit a Normal or a SN to the CCF.
+Finally, for the errors in evaluating the asymmetry of the CCF, we see that, when fitting the SN to the CCF, the asymmetry errors are $20\%$ smaller.
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{RV_comparison_SPOT_standard_errors.pdf} 
+   \caption{Spot case.
+Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
+When using RV mean SN (black circles), the standard errors are in average $40\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using RV median SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN.
+Note that for the asymmetry, the error in BIS SPAN is in \kms.
+To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
+   \label{fig:se.soap.spot}
+\end{figure*}
+
+Fig.~\ref{fig:se.soap.spot.planet} shows the results of the bootstrap analysis performed when a spot is present on the photosphere of the star.
+The series of plots follows the specifications outlined for the previous two cases.
+The conclusions are comparable to the case in which only a spot is present on the photosphere of the star.
+The ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$ when using RV mean SN and $0.9$ when using RV median SN.
+The errors in width of the CCF are comparable and the errors in evaluating the asymmetry of the CCF are $20\%$ smaller when using the asymmetry parameter $\gamma$ of the SN.
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{RV_comparison_SPOT_PLANET_standard_errors.pdf} 
+   \caption{Spot and Planet case.
+Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
+When using RV mean SN (black circles), the standard errors are in average $50\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using RV median SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN.
+Note that for the asymmetry, the error in BIS SPAN is in \kms.
+To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
+   \label{fig:se.soap.spot.planet}
+\end{figure*}
+
+\subsection{Estimation of standard errors for the CCF parameters for real stars} \label{sec:bootstrap_real_star}
 In the top plots of Fig.~\ref{fig:se} we show the different errors for the RVs, either defined as RV (red triangles), RV mean SN (black circles) or RV median SN (cyan crosses), the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels.
@@
 
-\umberto{add discussions on SOAP example}
-
-We compared for five stars the difference between the RVs (defined as mean of a Normal, mean of the SN or median of the SN), FWHM and asymmetry (BIS SPAN in the Normal case and $\gamma$ in the SN case).
-The $\gamma$ parameter is linearly dependant on the BIS SPAN, with always a strong correlation coefficient.
+We tested at first our assumptions by using simulated CCFs retrieved using the software SOAP 2.0.
+We then compared for five real stars the difference between the RVs (defined as mean of a Normal, mean of the SN or median of the SN), FWHM and asymmetry (BIS SPAN in the Normal case and $\gamma$ in the SN case).
+The $\gamma$ parameter is linearly dependent on the BIS SPAN, with always a strong correlation coefficient.
 %To compare $\gamma$, that do not have any units, with BIS SPAN expressed in \kms, one has simply to multiply $\gamma$ by the slope of the linear dependence between $\gamma$ and BIS SPAN. 
@@
 Therefore, the SN parameters are more sensitive to activity.
-In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of $0.436$ between $\gamma$ and RV mean SN, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.$225$.
+In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of $0.322$ between $\gamma$ and RV mean SN, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.$225$.
 
@@
 
-\umberto{add conclusions on SOAP example}
-
-Using the SN to fit CCFs brings a significant improvement in probing stellar activity.
+Starting from the simulation environment SOAP and then moving to real stars, we showed that using the SN distribution to fit CCFs brings a significant improvement in probing stellar activity.
 While for the Normal distribution mean and median are equivalent, using the SN fit different location parameters can be tested.

### 2018-05-13 manuscript.tex
working on intro

@@
 
-\title{Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution}
+%\title{Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution}
+\title{\xavier{Measuring precise radia velocities and cross-correlation function line-profile variations using a Skew Normal distribution}}
 %\thanks{Based on observations collected at the La Silla Parana Observatory,
@@
 % Context, Aims, Methods, Results, Conclu (not mandatory)
-When working with radial velocities for detecting Extrasolar planets and when using data from stabilized spectrographs, the different moments of the cross-correlation function (CCF) are used to measure the radial velocity of the star and also changes in the shape of the CCF.
-Those changes are due to stellar activity and therefore the best precision on these moments is required to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
+\xavier{Stellar activity is the main limitation to the detection of small-mass exoplanets using the radial-velocity (RV) technique.
+Stellar activity can be probed by measuring the cross-correlation function (CCF) shape variations as a function of time.
+Those variations are measured using the different moments of the CCF, therefore measuring with the best precision all the different moments of the CCF is crucial} to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
 
 We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, naturally provides an extra parameter to model the CCF natural asymmetry.
-Moreover, since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution seems to provide a more realistic model to the CCF.
+Since the CCF presents a natural asymmetry due to convective blueshift, the SN distribution seems to provide a more realistic model to the CCF.
 
@@
 
-The correlations between the RVs and the CCF asymmetry or RVs and the CCF width is always stronger when using the parameters derived from the SN.
-Therefore all the moments of the CCF are more sensitive to activity, which is a huge gain to probe stellar activity.
-RVs derived from a SN distribution are more sensitive to activity, which is interesting when looking for rotational periods or characterizing better stellar activity.
-\comment{" interesting" is a highly subjective and not very precise or quantitative expression.
-Interesting in what sense?
-I would term this a "sentence of no value", i.e.
-one that conveys not useful information to the reader.}
-The precision on the asymmetry parameter derived from the SN is on average $15\%$ better than the one calculated on the common Bisector Inverse Slope Span (BIS SPAN).
-When using the median of the SN as parameter defining the radial velocity of the star, the errors on the RVs measured by the SN are on average $10\%$ smaller than the errors calculated on the mean of the Normal.
+The correlations between the RVs and the CCF asymmetry or RVs and the CCF width is always stronger when using the parameters derived from the SN \xavier{in the case of real observations}.
+Therefore the CCF asymmetry and width derived using a SN are more sensitive to stellar activity, which \xavier{allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals.}
+\xavier{The precision on the RVs, derived using the median of the fitted SN distributions} are on average $10\%$ smaller than the RV errors calculated on the mean of the Normal.
+In addition, the asymmetry parameter derived from the SN is on average $15\%$ better than the one calculated on the common Bisector Inverse Slope Span (BIS SPAN).
 
-We strongly encourage the use of the SN distribution to retrieve in 1 single fit the different moments of the CCF, because the derived moments probe better stellar activity signals than when using a Normal distribution, leading as well to smaller standard errors associated to the radial velocity and the asymmetry parameters.
+We strongly encourage the use of the SN distribution to retrieve in one single fit the different moments of the CCF, because the derived moments probe better stellar activity signals than when using a Normal distribution, leading as well to smaller standard errors associated to the radial velocity and the asymmetry parameters.
 \comment{You simply cannot make this claim.
@@
 \subsection{Goal of RV analysis}
-The radial velocity (RV) of a star is defined to be the velocity of the center of mass of the star along our line of sight. 
-\comment{No, the radial velocity you measure of the star has many components that contribute to the RV: the space motion (present even if there is no companion), the motion about the center of mass (the so-called ?-velocity), oscillations, convective blue shift, etc.
-You are just assuming that you are measuring the reflex motion of a star-planet system. There are many physical processes that produce a Doppler shift besides exoplanets.}
-This quantity can be derived precisely by measuring the Doppler shift of spectral lines produced in stellar atmospheres. 
-\comment{Well, not if you have a poor measurement precision. You only get a "precise" measurement with simultaneous wavelength calibration. Again, the authors are not being very "precise" here.}
-For spectrographs that are not stabilised in temperature and pressure, the iodine technique is used, where the light of the star passes through a iodine cell before getting into the spectrograph to imprint the absorption spectrum of iodine on top of the stellar spectrum (The Hamilton spectrograph \citep{Vogt1987} at Lick Observatory, HIRES \citep{Vogt1994} on the Keck 10-m telescope, the Tull spectrograph  \citep{Tull1995}, the High Resolution Spectrograph HRS  \citep{Tull1998}).
-\jessi{we should mention the new spectrographs like EXPRES}
-In this case, if the spectrograph shifts due to changing atmospheric conditions, the iodine and stellar spectra are shifted in the same way.
+
+\xavier{When working with radial velocities, the main limitation to the detection of small-mass exoplanets is not anymore the precision of the instruments used, but the different noises induce by the stars we are observing \citep[][]{Dumusque:2017aa}.
+Indeed, stellar oscillations, granulation phenomena and stellar activity all induce RV signals \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a} that are beyond the meter-per-second precision reached by the best high-resolution spectrographs.
+It is therefore mandatory to understand better stellar signals and to find ways to correct for them if in the near future, we want to detect or confirm an Earth-twin planet.
+This is even more true now that instrument like ESPRESSO \citep{Pepe-2014} and EXPRESS \citep{Fischer:2017aa} should have the stability to detect such signals.
+However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging.
+
+%for detecting Extrasolar planets and when using data from stabilized spectrographs, the different moments of the cross-correlation function (CCF) are used to measure the radial velocity of the star but also variations in the shape of the CCF \citep{Baranne-1996, Pepe-2002a}.
+As a planet induces a pure Doppler shift of its host star, the shape of the CCF should not vary with time.
+If it does, it is either due to instrumental systematics, or due to stellar signals \citep{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2014b}.
+On extremely stabilized spectrographs like HARPS and HARPS-N, and soon ESPRESSO, the variations observed in the shape of the CCF or mainly due to stellar activity.
+Therefore, measuring with the best precision all the different moments of the CCF is crucial to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.}
+
+%The radial velocity (RV) of a star is defined to be the velocity of the center of mass of the star along our line of sight. 
+%\comment{No, the radial velocity you measure of the star has many components that contribute to the RV: the space motion (present even if there is no companion), the motion about the center of mass (the so-called ?-velocity), oscillations, convective blue shift, etc.
+%You are just assuming that you are measuring the reflex motion of a star-planet system. There are many physical processes that produce a Doppler shift besides exoplanets.}
+%This quantity can be derived precisely by measuring the Doppler shift of spectral lines produced in stellar atmospheres. 
+%\comment{Well, not if you have a poor measurement precision. You only get a "precise" measurement with simultaneous wavelength calibration. Again, the authors are not being very "precise" here.}
+%For spectrographs that are not stabilised in temperature and pressure, the iodine technique is used, where the light of the star passes through a iodine cell before getting into the spectrograph to imprint the absorption spectrum of iodine on top of the stellar spectrum (The Hamilton spectrograph \citep{Vogt1987} at Lick Observatory, HIRES \citep{Vogt1994} on the Keck 10-m telescope, the Tull spectrograph  \citep{Tull1995}, the High Resolution Spectrograph HRS  \citep{Tull1998}).
+%\jessi{we should mention the new spectrographs like EXPRES}
+%In this case, if the spectrograph shifts due to changing atmospheric conditions, the iodine and stellar spectra are shifted in the same way.
 This leads to some complications when reducing the data because one has to decorrelate the iodine spectrum from the stellar spectrum.
-\comment{This is a poorly expressed thought that is technically wrong.
+%\comment{This is a poorly expressed thought that is technically wrong.
 The spectrograph does not shift due to changing atmospheric conditions (earth's atmosphere?).
 It changes because of mechanical shifts (vibrations, temperature changes in spectrograph housing, changes in instrumental profile) as well as movement of the image on the slit or fiber which yes, does affect stellar and iodine lines in the same way.}
-\comment{No, you do not decorrelate (and I am not sure what the authors mean by this word) the iodine from the stellar spectrum.
+%\comment{No, you do not decorrelate (and I am not sure what the authors mean by this word) the iodine from the stellar spectrum.
 The authors show that they have no understanding how the method works.
@@
 Somewhere in the intro it needs to become clear that we are (i) providing a new way of measuring CCF asymmetry, (ii) this is a unified approach that also provides an RV estimate, and (iii) it (hopefully) provides a better indicator.}
-For spectrographs that are stabilized, the spectrum of a calibration lamp is recorded close to the stellar spectrum on the CCD, which prevents contamination of the stellar spectrum (CORALIE \citep{Queloz-2000a}, The High Accuracy Radial Velocity Planet Searcher (HARPS) \citep{Mayor-2003}, HARPS- N \citep{Cosentino-2012}, SOPHIE \citep{Bouchy:2013aa}, CARMENES \citep{Quirrenbach:2014aa}).
+
+Among the different stellar signals we are aware of, the one that is the most difficult to characterize and to correct for is the signal induced by stellar activity.
+Stellar activity creates magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, inducing spurious RV variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b}.
+To differentiate between the signal induced by a planet and the one induced by stellar activity, a common technique used is tu study the different moments of the cross-correlation function (CCF).
+The CCF, obtained by
+
+%For spectrographs that are stabilized, the spectrum of a calibration lamp is recorded close to the stellar spectrum on the CCD, which prevents contamination of the stellar spectrum (CORALIE \citep{Queloz-2000a}, The High Accuracy Radial Velocity Planet Searcher (HARPS) \citep{Mayor-2003}, HARPS- N \citep{Cosentino-2012}, SOPHIE \citep{Bouchy:2013aa}, CARMENES \citep{Quirrenbach:2014aa}).
 For those instruments, reducing the data is easier as the stellar spectrum is not contaminated with iodine absorption lines.
-\comment{This is not true!
+%\comment{This is not true!
 I have taken spectra with HARPS and there is cross-talk between spectra and Th-Ar particularly for strong emission lines.
@@
 In fact one reference the authors give, CORALIE, is not a stabilized spectrograph!}
-\comment{In paragraph 1 you give two lists of spectrographs.
+%\comment{In paragraph 1 you give two lists of spectrographs.
 I presume the first one is a list spectrographs that use the iodine method, although that is not explicitly expressed.
@@
 So you should say, "For example" or..."to name a few"
-The second list it is for simultaneous Th-Ar calibration.
+%The second list it is for simultaneous Th-Ar calibration.
 Not all of these are "stabilized" like the authors claim.

### 2018-05-15 manuscript.tex
Intro updated

@@
 Stellar activity can be probed by measuring the cross-correlation function (CCF) shape variations as a function of time.
-Those variations are measured using the different moments of the CCF, therefore measuring with the best precision all the different moments of the CCF is crucial} to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
+Those variations are measured using the different moments of the CCF, therefore measuring with the best precision those moments is crucial} to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
 
-We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, naturally provides an extra parameter to model the CCF natural asymmetry.
-Since the CCF presents a natural asymmetry due to convective blueshift, the SN distribution seems to provide a more realistic model to the CCF.
+We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, naturally provides an extra parameter to model the CCF natural asymmetry induced by convective blueshift.
+%. Since the CCF presents a natural asymmetry due to convective blueshift, the SN distribution seems to provide a more realistic model to the CCF.
 
@@
 
-We strongly encourage the use of the SN distribution to retrieve in one single fit the different moments of the CCF, because the derived moments probe better stellar activity signals than when using a Normal distribution, leading as well to smaller standard errors associated to the radial velocity and the asymmetry parameters.
-\comment{You simply cannot make this claim.
+\xavier{We strongly encourage the use of the SN distribution rather than the Normal distribution, because this allows to retrieve in one single fit the different moments of the CCF, because the derived moments probe better stellar activity signals and because the standard errors on the RV and the the asymmetry are smaller.}
+% than when using a Normal distribution, leading as well to smaller standard errors associated to the radial velocity and the asymmetry parameters.
+\xavier{I just left this comment here so that we can check at the end that we answered to all referee's major comments, however, I believe it is not relevant anymore with our new analysis.}\comment{You simply cannot make this claim.
 What you have shown is that the SN method produces errors that are 60\% larger than the Normal distribution and you hint that this is due to it being more sensitive to activity.
@@
 \xavier{When working with radial velocities, the main limitation to the detection of small-mass exoplanets is not anymore the precision of the instruments used, but the different noises induce by the stars we are observing \citep[][]{Dumusque:2017aa}.
-Indeed, stellar oscillations, granulation phenomena and stellar activity all induce RV signals \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a} that are beyond the meter-per-second precision reached by the best high-resolution spectrographs.
-It is therefore mandatory to understand better stellar signals and to find ways to correct for them if in the near future, we want to detect or confirm an Earth-twin planet.
+Indeed, stellar oscillations, granulation phenomena and stellar activity all induce RV signals \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are beyond the meter-per-second precision reached by the best high-resolution spectrographs.
+It is therefore mandatory to understand better stellar signals and to find ways to correct for them, if in the near future we want to detect or confirm an Earth-twin planet using the RV technique.
 This is even more true now that instrument like ESPRESSO \citep{Pepe-2014} and EXPRESS \citep{Fischer:2017aa} should have the stability to detect such signals.
-However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging.
+However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Stellar activity effect on CCF, Normal fit plus FWHM indicator}
+\subsection{Stellar activity effect on CCF, Normal fit plus FWHM and BIS SPAN indicators}
 \jessi{Eventually three methods are introduced for detecting CCF asymmetry:  FWHM, bisector span, and the Figueira approach - it seems that these methods need to be better explained.
@@
 
-Among the different stellar signals we are aware of, the one that is the most difficult to characterize and to correct for is the signal induced by stellar activity.
-Stellar activity creates magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, inducing spurious RV variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b}.
-To differentiate between the signal induced by a planet and the one induced by stellar activity, a common technique used is tu study the different moments of the cross-correlation function (CCF).
-The CCF, obtained by
+\xavier{Among the different stellar signals we are aware of, the one that is the most difficult to characterize and to correct for is the signal induced by stellar activity.
+Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, inducing spurious RV variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b}.
+In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, that will shift the entire stellar spectrum, and stellar activity that modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}.
+However, on quiet GKM dwarfs, the main target for precise RV measurements, stellar activity induce signals of a few \ms.
+This corresponds physically to variations smaller than 1/100th of a pixel on the detector.
+% and at this level it is extremely difficult to differentiate between a pure shift and a change in line shape. 
+To be able to measure such tiny variations, we average the information of all the line in the spectrum by cross correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}.
+%Although this process allows to measure spectral shifts at the level smaller than the meter-per-second, by averaging all the lines together we also average out line shape variation which make it more difficult to differentiate between a pure Dopler-shift and line shape variation.
+The result of this operation gives us the cross-correlation function (CCF).
+To measure the Doppler-shift between different spectra, and therefore get the RV of a star as a function of time, we calculate the variations of the CCF barycenter.
+The barycenter is generally estimated by fitting a Normal distribution to the CCF, and taking its mean.
+Variation in line shape between different spectra, which indicate the presence of signals induced by stellar activity, is measured by analysing the different moments of the CCF.
+Generally, the width of the CCF is estimated using the FWHM of the fitted Normal distribution, and its asymmetry using the the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
+%bisector \citep[][]{Voigt1956}, the bisector curvature \citep[][]{Hatzes1996} or the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
+}
+
+\subsection{Why FWHM and BIS SPAN important?}
+
+\xavier{If a RV signal is induced by activity, generally a strong correlation will be observed between the RV and chromospheric activity indicators like \logrhk\,or H-$\alpha$ \citep[e.g.][]{Boisse-2009,Dumusque-2012,Robertson-2014}, but also between the RV and the FWHM of the CCF or its BIS SPAN \citep[][]{Queloz-2001,Boisse-2009,Queloz-2009,Dumusque-2016a}.
+It is therefore common now, that when fitting for a planetray signal, in addition to a Keplerian, the model includes in addition linear dependancies with the \logrhk, the FWHM and the BIS SPAN \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
+It is also common to add a Gaussian process to the model to account for the correlated noise induced by stellar activity.
+The hyperparameters of the Gaussian process are generally trained on the different activity indicators \citep[e.g.][]{Haywood-2014,Rajpaul-2015}.
+It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated to the RVs but also for which we can obtain the best precision.}
+
+\subsection{Figueira indicators of stellar activity + other}
+\xavier{Several works have derived indicators that are more sensitive to line asymmetry than the BIS SPAN.
+In \citet{Boisse-2011}, the authors develop $V_{span}$ a new indicator to derive the CCF asymmetry, that is more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR).
+\citet{Figueira-2013} studied the use of two new indicators, bi-Gauss and $V_{asy}$.
+The authors were able to show that when using bi-Gauss, the amplitude in asymmetry is 30\% larger, therefore allowing the detection of smaller-amplitude correlations with radial-velocity variations.
+They also demonstrated that $V_{asy}$ seems to be the best indicator of line asymmetry at high SNR, as its correlation with RV is more significant than any other asymmetry indictors.
+}
+
+\subsection{Why using a SN distribution?}
+\xavier{In all the method described above, the RV and the FWHM is derived using a Normal distribution fitted to the CCF, and the asymmetry is estimated using another approach.
+In this paper we propose to use a Skew Normal (SN) distribution to derive at the same time the RV, the FWHM and the asymmetry of the CCF, as this function includes a skewness parameter \citep[][]{Azzalini1985}.
+In addition, we know that for solar-type stars and cooler dwarfs, the bisector of the CCF as a "C"-shape due to convective blueshift \citep[e.g.][]{Dravins-1981, Gray-2009}.
+Therefore, fitting the CCF using a model that naturally includes an asymmetry, like the SN distribution, should give more precise results.
+}
 
@@
 
-For stabilized spectrographs, the RV is derived by first correlating a stellar spectrum at a particular time with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}, which gives an average line profile, generally called Cross Correlation Function (CCF).
+%For stabilized spectrographs, the RV is derived by first correlating a stellar spectrum at a particular time with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}, which gives an average line profile, generally called Cross Correlation Function (CCF).
 The CCF is a function of RV, and the RV corresponding to the minimum of the CCF is the estimated RV for that spectrum.
-However, this would give a noisy estimate so first a Normal density shape is fitted to the CCF, and then the estimated mean of the Normal density is used as the estimate of the RV.
+However, this would give a noisy estimate so first a Normal distribution shape is fitted to the CCF, and then the estimated mean of the Normal distribution is used as the estimate of the RV.
 The full width at half maximum (FWHM) of the Normal fit is also used as an indicator of spectral line asymmetry.
-The CCF technique allows for an averaging of thousands of spectral lines and can therefore reach a very high signal-to-noise ratio (SNR), which is essential for a good RV precision.
+%The CCF technique allows for an averaging of thousands of spectral lines and can therefore reach a very high signal-to-noise ratio (SNR), which is essential for a good RV precision.
 
-The convection in external layers of solar type stars is responsible for the granulation pattern than can be seen at high spatial resolution on the surface of the Sun.
+%The convection in external layers of solar type stars is responsible for the granulation pattern than can be seen at high spatial resolution on the surface of the Sun.
 The differences in flux and velocity between upflows and downflows change the Normal profile of spectral lines that become asymmetric with a "C"-shaped profile \citep[][]{Dravins-1981}.
-\comment{Regarding the C-shape of the bisector. The classic C-shape is only for late-type stars. In fact for hotter stars (F-type) it reverses.
-The strength of the asymmetry depends not just on the velocities, it is more complicated than that.
+%\comment{Regarding the C-shape of the bisector. The classic C-shape is only for late-type stars. In fact for hotter stars (F-type) it reverses.
+%The strength of the asymmetry depends not just on the velocities, it is more complicated than that.
 It also depends on the flux ratio between hot cells and cool lanes, as well as the ratio of surface areas between the two.}
-The strength of the asymmetry depends on the velocity of the convection, approximatively 300\ms for the Sun, but also on the formation depth of spectral lines \citep{Gray-2009}.
+%The strength of the asymmetry depends on the velocity of the convection, approximatively 300\ms for the Sun, but also on the formation depth of spectral lines \citep{Gray-2009}.
 Since the CCF is an average of all the spectral lines, some strongly asymmetric and some not, its asymmetry is rather small, which is why a Normal distribution can be an appropriate model for the CCF.
 This small asymmetry modifies however slightly the estimated RVs of the star, reducing the accuracy of the measurement, but if this asymmetry does not vary with time, the precision is kept.
-\comment{But the activity causes the asymmetry to change due to rotation, spot evolution, etc.
+%\comment{But the activity causes the asymmetry to change due to rotation, spot evolution, etc.
 The authors are confusing the readers here.
@@
 I think what they want to say is that you measure a precise stellar radial velocity, but the activity makes its own contribution which reduces the accuracy of the RV determination for the barycentric motion due to a planet.}
-
-Convection is not the only phenomenon responsible for asymmetries in the single spectral line and the CCF.
+%
+%
+%Convection is not the only phenomenon responsible for asymmetries in the single spectral line and the CCF.
 Stellar activity is responsible for the appearance of dark spots and bright faculae on the stellar photosphere, which breaks the flux balance between the red-shifted and the blue-shifted halves of a rotating star and therefore induce an asymmetry of spectral lines and thus of the CCF.
@@
 Strong magnetic fields reduce stellar convection, which in turn modifies the asymmetry of spectral lines \citep[][]{Cavallini-1985a,Dravins-1981,Lindegren-2003,Meunier-2010a,Dumusque-2014b}.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Bisector span indicators of stellar activity}
+%\jessi{Its seems that more details should be added here}
+%Stellar activity can induce RV variations by a modification of the spectral line asymmetry, while any orbiting companions would induce a pure Doppler shift on \emph{all} spectral lines without modifying their shape.
+%Therefore, assuming that there is no instrumental systematics, stellar activity generally induces a variation in line asymmetry that can be observed in the  FWHM of the CCF. 
+%The line asymmetry is commonly retrieved by calculating the bisector of the CCF \citep[][]{Voigt1956} and deriving the bisector curvature \citep[][]{Hatzes1996} or the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
+%An orbiting exoplanet will produce an RV variation induced by a pure Doppler shift of \emph{all} the spectral lines of each stellar spectrum. 
+%Stellar activity, however, does not produce a blueshift or redshift of the spectra, but can create a spurious RV signal by modifying the shape of spectral lines.
+To track changes in line shape, the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} are often used, which provide information on the average width and asymmetry of the CCF \citep{Hatzes1996, fiorenzano2005line, Queloz-2001}.
+A strong correlation between the estimated RVs and one or more of these parameters is a sign that the estimated RVs may be contaminated by stellar activity.
+%\comment{It is the slope or span, not both. And you generally do not calculate the inverse, just the
+%span. This may be correlated or inversely correlated with the RV.}
+%
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Figueira indicators of stellar activity}
+%\citet{Figueira-2013} proposed different indicators, including a bi-Gaussian fitting of the CCF \jessi{this needs to be better explained}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Bisector span indicators of stellar activity}
-\jessi{Its seems that more details should be added here}
-Stellar activity can induce RV variations by a modification of the spectral line asymmetry, while any orbiting companions would induce a pure Doppler shift on \emph{all} spectral lines without modifying their shape.
-Therefore, assuming that there is no instrumental systematics, stellar activity generally induces a variation in line asymmetry that can be observed in the  FWHM of the CCF. 
-The line asymmetry is commonly retrieved by calculating the bisector of the CCF \citep[][]{Voigt1956} and deriving the bisector curvature \citep[][]{Hatzes1996} or the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
-An orbiting exoplanet will produce an RV variation induced by a pure Doppler shift of \emph{all} the spectral lines of each stellar spectrum. 
-Stellar activity, however, does not produce a blueshift or redshift of the spectra, but can create a spurious RV signal by modifying the shape of spectral lines.
-To track changes in line shape, the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} are often used, which provide information on the average width and asymmetry of the CCF \citep{Hatzes1996, fiorenzano2005line, Queloz-2001}.
-A strong correlation between the estimated RVs and one or more of these parameters is a sign that the estimated RVs may be contaminated by stellar activity.
-\comment{It is the slope or span, not both. And you generally do not calculate the inverse, just the
-span. This may be correlated or inversely correlated with the RV.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Figueira indicators of stellar activity}
-\citet{Figueira-2013} proposed different indicators, including a bi-Gaussian fitting of the CCF \jessi{this needs to be better explained}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Issues with detecting stellar activity}
-Unfortunately, when analyzing slow rotators stars such as the Sun, due to the limited spectral resolution of the spectrographs and the limited precision in RV, it becomes difficult to measure the line asymmetry, resulting in complications for detecting very small-mass planets with the RV technique.
-In the procedure described above, the measurement of the RV and the FWHM is done separately from the measurement of the line asymmetry.
+%\subsection{Issues with detecting stellar activity}
+%Unfortunately, when analyzing slow rotators stars such as the Sun, due to the limited spectral resolution of the spectrographs and the limited precision in RV, it becomes difficult to measure the line asymmetry, resulting in complications for detecting very small-mass planets with the RV technique.
+%In the procedure described above, the measurement of the RV and the FWHM is done separately from the measurement of the line asymmetry.
 All those parameters are correlated when stellar activity is dominant, and performing a step-by-step approach makes it difficult to correctly derive the errors on the different parameters retrieved.
-\comment{I simply do not understand this statement, possibly because it does not follow a standard English construction.
+%\comment{I simply do not understand this statement, possibly because it does not follow a standard English construction.
 You have a CCF and you measure a width and bisector span.
@@
 Maybe that is what you mean here, but it is not clear from what is written.}
-In addition, the Normal distribution cannot take into account the natural asymmetry of the CCF, leaving correlated noise in the residuals, which also complicates the determination of errors.
+%In addition, the Normal distribution cannot take into account the natural asymmetry of the CCF, leaving correlated noise in the residuals, which also complicates the determination of errors.
 We propose to overcome these problems by fitting a SN (SN) distribution to the CCF, which naturally includes a skewness parameter \citep[][]{Azzalini1985}.
@@
 \todo{This paragraph will need to be updated once the rest is finished.} The paper is organized as follow.
-In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  show that the SN density is a better representation of observed CCF than a Normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
+In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  show that the SN distribution is a better representation of observed CCF than a Normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
 In Sec.~\ref{intro} we present a simple model to correct for stellar activity.

### 2018-05-17 manuscript.tex
Add files via upload

@@
 
-%\title{Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution}
-\title{\xavier{Measuring precise radia velocities and cross-correlation function line-profile variations using a Skew Normal distribution}}
+\title{Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal distribution}
 %\thanks{Based on observations collected at the La Silla Parana Observatory,
@@
 % Context, Aims, Methods, Results, Conclu (not mandatory)
-\xavier{Stellar activity is the main limitation to the detection of small-mass exoplanets using the radial-velocity (RV) technique.
+Stellar activity is the main limitation to the detection of small-mass exoplanets using the radial-velocity (RV) technique.
 Stellar activity can be probed by measuring the cross-correlation function (CCF) shape variations as a function of time.
-Those variations are measured using the different moments of the CCF, therefore measuring with the best precision those moments is crucial} to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
+Those variations are measured using the different moments of the CCF, therefore measuring with the best precision those moments is crucial to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
 
 We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, naturally provides an extra parameter to model the CCF natural asymmetry induced by convective blueshift.
-%. Since the CCF presents a natural asymmetry due to convective blueshift, the SN distribution seems to provide a more realistic model to the CCF.
 
@@
 
-The correlations between the RVs and the CCF asymmetry or RVs and the CCF width is always stronger when using the parameters derived from the SN \xavier{in the case of real observations}.
-Therefore the CCF asymmetry and width derived using a SN are more sensitive to stellar activity, which \xavier{allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals.}
-\xavier{The precision on the RVs, derived using the median of the fitted SN distributions} are on average $10\%$ smaller than the RV errors calculated on the mean of the Normal.
+The correlations between the RVs and the CCF asymmetry or RVs and the CCF width is always stronger when using the parameters derived from the SN in the case of real observations.
+Therefore the CCF asymmetry and width derived using a SN are more sensitive to stellar activity, which allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals.
+The precision on the RVs, derived using the median of the fitted SN distributions are on average $10\%$ smaller than the RV errors calculated on the mean of the Normal.
 In addition, the asymmetry parameter derived from the SN is on average $15\%$ better than the one calculated on the common Bisector Inverse Slope Span (BIS SPAN).
-
-\xavier{We strongly encourage the use of the SN distribution rather than the Normal distribution, because this allows to retrieve in one single fit the different moments of the CCF, because the derived moments probe better stellar activity signals and because the standard errors on the RV and the the asymmetry are smaller.}
-% than when using a Normal distribution, leading as well to smaller standard errors associated to the radial velocity and the asymmetry parameters.
-\xavier{I just left this comment here so that we can check at the end that we answered to all referee's major comments, however, I believe it is not relevant anymore with our new analysis.}\comment{You simply cannot make this claim.
-What you have shown is that the SN method produces errors that are 60\% larger than the Normal distribution and you hint that this is due to it being more sensitive to activity.
-You have not demonstrated this by looking at the "activity" signal that the SN isolates to see if it is actually more sensitive at finding rotation periods, activity cycles, etc.
-Where is the sensitivity in actually getting out useful information?
-Furthermore, after correcting the SN RVs for the activity, you arrive at the same answer as the Normal distribution method.
-I would conclude that the SN offers no real advantages over Normal so the community can continue to use the standard method.
-Grammatically this is an ambiguous statement.
-Are you looking for "better signals", i.e.
-ones that you like, or probing stellar signals in a better way?
-(This is what you meant, but not what was stated.)}
+We strongly encourage the use of the SN distribution rather than the Normal distribution, because this allows to retrieve in one single fit the different moments of the CCF, because the derived moments probe better stellar activity signals and because the standard errors on the RV and the the asymmetry are smaller.
+
 %\keywords{techniques: radial velocities -- planetary systems -- stars: activity -- methods: data analysis}
 
-\section{Introduction}
-\label{intro}
-\jessi{I added subsections here for our reference to make sure the bases are covered, but we should remove them before submission.}
+\section{Introduction} \label{intro}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Goal of RV analysis}
-
-\xavier{When working with radial velocities, the main limitation to the detection of small-mass exoplanets is not anymore the precision of the instruments used, but the different noises induce by the stars we are observing \citep[][]{Dumusque:2017aa}.
+%\subsection{Goal of RV analysis}
+
+When working with radial velocities, the main limitation to the detection of small-mass exoplanets is not anymore the precision of the instruments used, but the different noises induce by the stars we are observing \citep[][]{Dumusque:2017aa}.
 Indeed, stellar oscillations, granulation phenomena and stellar activity all induce RV signals \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are beyond the meter-per-second precision reached by the best high-resolution spectrographs.
@@
 This is even more true now that instrument like ESPRESSO \citep{Pepe-2014} and EXPRESS \citep{Fischer:2017aa} should have the stability to detect such signals.
-However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging.}
-
-%for detecting Extrasolar planets and when using data from stabilized spectrographs, the different moments of the cross-correlation function (CCF) are used to measure the radial velocity of the star but also variations in the shape of the CCF \citep{Baranne-1996, Pepe-2002a}.
-As a planet induces a pure Doppler shift of its host star, the shape of the CCF should not vary with time.
-If it does, it is either due to instrumental systematics, or due to stellar signals \citep{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2014b}.
-On extremely stabilized spectrographs like HARPS and HARPS-N, and soon ESPRESSO, the variations observed in the shape of the CCF or mainly due to stellar activity.
-Therefore, measuring with the best precision all the different moments of the CCF is crucial to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.}
-
-%The radial velocity (RV) of a star is defined to be the velocity of the center of mass of the star along our line of sight. 
-%\comment{No, the radial velocity you measure of the star has many components that contribute to the RV: the space motion (present even if there is no companion), the motion about the center of mass (the so-called ?-velocity), oscillations, convective blue shift, etc.
-%You are just assuming that you are measuring the reflex motion of a star-planet system. There are many physical processes that produce a Doppler shift besides exoplanets.}
-%This quantity can be derived precisely by measuring the Doppler shift of spectral lines produced in stellar atmospheres. 
-%\comment{Well, not if you have a poor measurement precision. You only get a "precise" measurement with simultaneous wavelength calibration. Again, the authors are not being very "precise" here.}
-%For spectrographs that are not stabilised in temperature and pressure, the iodine technique is used, where the light of the star passes through a iodine cell before getting into the spectrograph to imprint the absorption spectrum of iodine on top of the stellar spectrum (The Hamilton spectrograph \citep{Vogt1987} at Lick Observatory, HIRES \citep{Vogt1994} on the Keck 10-m telescope, the Tull spectrograph  \citep{Tull1995}, the High Resolution Spectrograph HRS  \citep{Tull1998}).
-%\jessi{we should mention the new spectrographs like EXPRES}
-%In this case, if the spectrograph shifts due to changing atmospheric conditions, the iodine and stellar spectra are shifted in the same way.
-This leads to some complications when reducing the data because one has to decorrelate the iodine spectrum from the stellar spectrum.
-%\comment{This is a poorly expressed thought that is technically wrong.
-The spectrograph does not shift due to changing atmospheric conditions (earth's atmosphere?).
-It changes because of mechanical shifts (vibrations, temperature changes in spectrograph housing, changes in instrumental profile) as well as movement of the image on the slit or fiber which yes, does affect stellar and iodine lines in the same way.}
-%\comment{No, you do not decorrelate (and I am not sure what the authors mean by this word) the iodine from the stellar spectrum.
-The authors show that they have no understanding how the method works.
-What is actually done is that a high-resolution iodine spectrum is combined with a spectrum of the star without iodine lines and a fit is made to the observed star+iodine spectrum.
-It is not decorrelation, but rather $\chi^2$ fitting.}
+However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Stellar activity effect on CCF, Normal fit plus FWHM and BIS SPAN indicators}
-\jessi{Eventually three methods are introduced for detecting CCF asymmetry:  FWHM, bisector span, and the Figueira approach - it seems that these methods need to be better explained.
-Somewhere in the intro it needs to become clear that we are (i) providing a new way of measuring CCF asymmetry, (ii) this is a unified approach that also provides an RV estimate, and (iii) it (hopefully) provides a better indicator.}
-
-\xavier{Among the different stellar signals we are aware of, the one that is the most difficult to characterize and to correct for is the signal induced by stellar activity.
+%\subsection{Stellar activity effect on CCF, Normal fit plus FWHM and BIS SPAN indicators}
+
+Among the different stellar signals we are aware of, the one that is the most difficult to characterize and to correct for is the signal induced by stellar activity.
 Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, inducing spurious RV variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b}.
@@
 This corresponds physically to variations smaller than 1/100th of a pixel on the detector.
-% and at this level it is extremely difficult to differentiate between a pure shift and a change in line shape. 
+
 To be able to measure such tiny variations, we average the information of all the line in the spectrum by cross correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}.
-%Although this process allows to measure spectral shifts at the level smaller than the meter-per-second, by averaging all the lines together we also average out line shape variation which make it more difficult to differentiate between a pure Dopler-shift and line shape variation.
+
 The result of this operation gives us the cross-correlation function (CCF).
@@
 Generally, the width of the CCF is estimated using the FWHM of the fitted Normal distribution, and its asymmetry using the the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
-%bisector \citep[][]{Voigt1956}, the bisector curvature \citep[][]{Hatzes1996} or the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
-}
-
-\subsection{Why FWHM and BIS SPAN important?}
-
-\xavier{If a RV signal is induced by activity, generally a strong correlation will be observed between the RV and chromospheric activity indicators like \logrhk\,or H-$\alpha$ \citep[e.g.][]{Boisse-2009,Dumusque-2012,Robertson-2014}, but also between the RV and the FWHM of the CCF or its BIS SPAN \citep[][]{Queloz-2001,Boisse-2009,Queloz-2009,Dumusque-2016a}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Why FWHM and BIS SPAN important?}
+
+If a RV signal is induced by activity, generally a strong correlation will be observed between the RV and chromospheric activity indicators like \logrhk\,or H-$\alpha$ \citep[e.g.][]{Boisse-2009,Dumusque-2012,Robertson-2014}, but also between the RV and the FWHM of the CCF or its BIS SPAN \citep[][]{Queloz-2001,Boisse-2009,Queloz-2009,Dumusque-2016a}.
 It is therefore common now, that when fitting for a planetray signal, in addition to a Keplerian, the model includes in addition linear dependancies with the \logrhk, the FWHM and the BIS SPAN \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
@@
 The hyperparameters of the Gaussian process are generally trained on the different activity indicators \citep[e.g.][]{Haywood-2014,Rajpaul-2015}.
-It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated to the RVs but also for which we can obtain the best precision.}
-
-\subsection{Figueira indicators of stellar activity + other}
-\xavier{Several works have derived indicators that are more sensitive to line asymmetry than the BIS SPAN.
+It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated to the RVs but also for which we can obtain the best precision.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Figueira indicators of stellar activity + other}
+Several works have derived indicators that are more sensitive to line asymmetry than the BIS SPAN.
 In \citet{Boisse-2011}, the authors develop $V_{span}$ a new indicator to derive the CCF asymmetry, that is more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR).
@@
 They also demonstrated that $V_{asy}$ seems to be the best indicator of line asymmetry at high SNR, as its correlation with RV is more significant than any other asymmetry indictors.
-}
-
-\subsection{Why using a SN distribution?}
-\xavier{In all the method described above, the RV and the FWHM is derived using a Normal distribution fitted to the CCF, and the asymmetry is estimated using another approach.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Why using a SN distribution?}
+In all the method described above, the RV and the FWHM is derived using a Normal distribution fitted to the CCF, and the asymmetry is estimated using another approach.
 In this paper we propose to use a Skew Normal (SN) distribution to derive at the same time the RV, the FWHM and the asymmetry of the CCF, as this function includes a skewness parameter \citep[][]{Azzalini1985}.
@@
 Therefore, fitting the CCF using a model that naturally includes an asymmetry, like the SN distribution, should give more precise results.
-}
-
-%For spectrographs that are stabilized, the spectrum of a calibration lamp is recorded close to the stellar spectrum on the CCD, which prevents contamination of the stellar spectrum (CORALIE \citep{Queloz-2000a}, The High Accuracy Radial Velocity Planet Searcher (HARPS) \citep{Mayor-2003}, HARPS- N \citep{Cosentino-2012}, SOPHIE \citep{Bouchy:2013aa}, CARMENES \citep{Quirrenbach:2014aa}).
-For those instruments, reducing the data is easier as the stellar spectrum is not contaminated with iodine absorption lines.
-%\comment{This is not true!
-I have taken spectra with HARPS and there is cross-talk between spectra and Th-Ar particularly for strong emission lines.
-So there is some contamination.
-Furthermore, this "preventing of contamination" as the authors state has nothing to do with the spectrograph being stablized, it has to do with the simultaneous wavelength calibration using two fibers.
-In fact one reference the authors give, CORALIE, is not a stabilized spectrograph!}
-%\comment{In paragraph 1 you give two lists of spectrographs.
-I presume the first one is a list spectrographs that use the iodine method, although that is not explicitly expressed.
-The authors talk about the iodine cell and then just give a parenthetical list of spectrographs.
-There is no explicit statement that these spectrographs, designed for other purposes, are all equipped with an iodine cell.
-The reader must assume this.
-Furthermore, the list is not all-inclusive.
-I can think of a dozen facilities that use iodine cells.
-So you should say, "For example" or..."to name a few"
-%The second list it is for simultaneous Th-Ar calibration.
-Not all of these are "stabilized" like the authors claim.
-CORALIE, if I am not mistaken, was simultaneous Th-Ar without stabilization.
-That is why they built HARPS.
-Furthermore, all of theses spectrographs were designed for precise stellar RVs, unlike the spectrographs listed for the iodine method.}
-
-%For stabilized spectrographs, the RV is derived by first correlating a stellar spectrum at a particular time with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}, which gives an average line profile, generally called Cross Correlation Function (CCF).
-The CCF is a function of RV, and the RV corresponding to the minimum of the CCF is the estimated RV for that spectrum.
-However, this would give a noisy estimate so first a Normal distribution shape is fitted to the CCF, and then the estimated mean of the Normal distribution is used as the estimate of the RV.
-The full width at half maximum (FWHM) of the Normal fit is also used as an indicator of spectral line asymmetry.
-%The CCF technique allows for an averaging of thousands of spectral lines and can therefore reach a very high signal-to-noise ratio (SNR), which is essential for a good RV precision.
-
-%The convection in external layers of solar type stars is responsible for the granulation pattern than can be seen at high spatial resolution on the surface of the Sun.
-The differences in flux and velocity between upflows and downflows change the Normal profile of spectral lines that become asymmetric with a "C"-shaped profile \citep[][]{Dravins-1981}.
-%\comment{Regarding the C-shape of the bisector. The classic C-shape is only for late-type stars. In fact for hotter stars (F-type) it reverses.
-%The strength of the asymmetry depends not just on the velocities, it is more complicated than that.
-It also depends on the flux ratio between hot cells and cool lanes, as well as the ratio of surface areas between the two.}
-%The strength of the asymmetry depends on the velocity of the convection, approximatively 300\ms for the Sun, but also on the formation depth of spectral lines \citep{Gray-2009}.
-Since the CCF is an average of all the spectral lines, some strongly asymmetric and some not, its asymmetry is rather small, which is why a Normal distribution can be an appropriate model for the CCF.
-This small asymmetry modifies however slightly the estimated RVs of the star, reducing the accuracy of the measurement, but if this asymmetry does not vary with time, the precision is kept.
-%\comment{But the activity causes the asymmetry to change due to rotation, spot evolution, etc.
-The authors are confusing the readers here.
-They talk about a changing activity signal, but now argue that the precision is only kept if the asymmetry is constant, which it is not.
-I think what they want to say is that you measure a precise stellar radial velocity, but the activity makes its own contribution which reduces the accuracy of the RV determination for the barycentric motion due to a planet.}
-%
-%
-%Convection is not the only phenomenon responsible for asymmetries in the single spectral line and the CCF.
-Stellar activity is responsible for the appearance of dark spots and bright faculae on the stellar photosphere, which breaks the flux balance between the red-shifted and the blue-shifted halves of a rotating star and therefore induce an asymmetry of spectral lines and thus of the CCF.
-As the star rotates, spots and faculae move across the stellar disk, modifying the line asymmetry and thus producing an apparent Doppler shift \citep{Saar-1997b,Hatzes-2002,Kurster2003,Desort-2007,Lagrange-2010,Boisse-2012b}.
-Spots and faculae are also regions where the magnetic field is strong.
-Strong magnetic fields reduce stellar convection, which in turn modifies the asymmetry of spectral lines \citep[][]{Cavallini-1985a,Dravins-1981,Lindegren-2003,Meunier-2010a,Dumusque-2014b}.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Bisector span indicators of stellar activity}
-%\jessi{Its seems that more details should be added here}
-%Stellar activity can induce RV variations by a modification of the spectral line asymmetry, while any orbiting companions would induce a pure Doppler shift on \emph{all} spectral lines without modifying their shape.
-%Therefore, assuming that there is no instrumental systematics, stellar activity generally induces a variation in line asymmetry that can be observed in the  FWHM of the CCF. 
-%The line asymmetry is commonly retrieved by calculating the bisector of the CCF \citep[][]{Voigt1956} and deriving the bisector curvature \citep[][]{Hatzes1996} or the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
-%An orbiting exoplanet will produce an RV variation induced by a pure Doppler shift of \emph{all} the spectral lines of each stellar spectrum. 
-%Stellar activity, however, does not produce a blueshift or redshift of the spectra, but can create a spurious RV signal by modifying the shape of spectral lines.
-To track changes in line shape, the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} are often used, which provide information on the average width and asymmetry of the CCF \citep{Hatzes1996, fiorenzano2005line, Queloz-2001}.
-A strong correlation between the estimated RVs and one or more of these parameters is a sign that the estimated RVs may be contaminated by stellar activity.
-%\comment{It is the slope or span, not both. And you generally do not calculate the inverse, just the
-%span. This may be correlated or inversely correlated with the RV.}
-%
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Figueira indicators of stellar activity}
-%\citet{Figueira-2013} proposed different indicators, including a bi-Gaussian fitting of the CCF \jessi{this needs to be better explained}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Issues with detecting stellar activity}
-%Unfortunately, when analyzing slow rotators stars such as the Sun, due to the limited spectral resolution of the spectrographs and the limited precision in RV, it becomes difficult to measure the line asymmetry, resulting in complications for detecting very small-mass planets with the RV technique.
-%In the procedure described above, the measurement of the RV and the FWHM is done separately from the measurement of the line asymmetry.
-All those parameters are correlated when stellar activity is dominant, and performing a step-by-step approach makes it difficult to correctly derive the errors on the different parameters retrieved.
-%\comment{I simply do not understand this statement, possibly because it does not follow a standard English construction.
-You have a CCF and you measure a width and bisector span.
-This is a measurement error determined by the S/N, the resolution, and the stability of the spectrograph.
-You can determine an error in a quantity (RV and BIS).
-You can also have an uncertainty in the contribution of activity to the RV signal, but that is not a formal error.
-True errors come from photon statistics, systematic errors, instrumental errors, etc.
-You can attempt to remove the signal due to activity and that has an associated error, but that error is due to your lack of knowledge of the surface structure causing this RV and the exact value of the contribution to the RV.
-This is different from a measurement error.
-Maybe that is what you mean here, but it is not clear from what is written.}
-%In addition, the Normal distribution cannot take into account the natural asymmetry of the CCF, leaving correlated noise in the residuals, which also complicates the determination of errors.
-We propose to overcome these problems by fitting a SN (SN) distribution to the CCF, which naturally includes a skewness parameter \citep[][]{Azzalini1985}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Outline of paper}
-\todo{This paragraph will need to be updated once the rest is finished.} The paper is organized as follow.
-In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  show that the SN distribution is a better representation of observed CCF than a Normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
-In Sec.~\ref{intro} we present a simple model to correct for stellar activity.
+%\subsection{Outline of paper}
+The paper is organized as follow.
+In Sec.~\ref{sec:2} and in Sec.~\ref{sec:3} we introduce the SN distribution and describe its applicability for modeling the CCF,  showing that the SN distribution is a better representation of observed CCF than a Normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
+In Sec.~\ref{sec:3.1} we present a simple model to correct from stellar activity.
+In Sec.~\ref{sec:soap} we study the SN fit to the CCF using simulation coming from SOAP 2.0.
 In Sec.~\ref{sec:4}, we compare on real observations the sensitivity of the SN parameters to stellar activity with respect to other existing indicators.
@@
 %-----------------------------------------------------------------------------------------------------------------------------------------------
+\section{Radial Velocity correction function for stellar activity} \label{sec:31}
+
+Exoplanets will only produce a variation in RV's induced by a pure doppler shift of stellar spectra.
+Stellar activity and in particular the presence of active regions on the photosphere of the star, on the contrary, does not produce a blueshift or redshift of the spectra, but creates spurious RV's signal by modifying the shape of the spectral lines.
+To track these changes in the shape of the line profile, the general approach consists in using the FWHM, the BIS SPAN or the indicators introduced by \citep{Figueira-2013}, which provide an information on the average width and asymmetry of the CCF.
+A strong correlation between the estimated set of RV's and one or more of these parameters provides an indication that the RV's are affected by stellar activity signals.
+
+To test the strength of the correlation between the estimated RV's and the different indicators used to evaluate stellar activity, we calculated the Pearson correlation coefficient, which in its general form is defined as:
+%
+\begin{equation}
+R (x,y)= \frac{cov(x,y)}{\sigma(x),\sigma(y)},
+\label{eq:Pearson:corr}
+\end{equation}
+where $x$ and $y$ are two quantitative variables, $cov(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represent their standard deviations. 
+A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided, along with a $95\,\%$ confidence interval for $R$.
+%
+Because of the spurious variations in RV's caused by active regions, a crucial step of the entire analysis is to correct the initially estimated RV's in order to retrieve a set of RV's containing ideally only the possibly pure doppler shift coming from the exoplanets.
+In order to reach this goal, we propose to consider a linear combination of the RV's having as covariates the amplitude parameter A, the BIS SPAN, the FWHM and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM and the interaction between $\gamma$ and SN FWHM in the SN case), as shown in Eq.~\eqref{eq:RV:correction}.
+%
+\begin{equation}
+RV_{\text{stellar activity}}= \beta_{0} + \beta_{1} A + \beta_{2} \gamma + \beta_{3} \text{SN FWHM} + \beta_{4} (\gamma  \text{SN FWHM})+\epsilon,
+\label{eq:RV:correction}
+\end{equation}
+%
+where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix).
+
+While the parameters $\gamma$ (or BIS SPAN) and SN FWHM (or FWHM) have already been introduced, in Eq.~\eqref{eq:RV:correction} we propose also two include the amplitude parameter $A$ and a variable that quantifies the interaction between $\gamma$ (or BIS SPAN) and SN FWHM (or FWHM).
+The inclusion of the amplitude parameter A is justified by the expected behavior of the CCF in presence of active regions.
+Fig.~\ref{fig:spotA} show that the presence for instance of a spot produces also changes on the amplitude of the CCF and not only on its asymmetry or width.
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
+   \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF and not only on its asymmetry or width.}
+    \label{fig:spotA}
+\end{figure*}
+%
+The reasons for including in Eq.~\eqref{eq:RV:correction} a variable that quantifies the interaction between $\gamma$ (or BIS SPAN) and SN FWHM (or FWHM) will be clarified in the next Section and are related to a first attempt to disentangle spots from faculae.
+
+In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$, $\beta_{2}$, $\beta_{3}$ and $\beta_{4}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,\dots,4$.
+The level for not rejecting the null hypothesis is fixed equal to $0.05$.
+The coefficient of multiple correlation $R^2$ is introduced in order to explain how well this linear combination addresses the variability of the RV's of the star as caused by stellar activity.
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
 \section{Simulation Study} \label{sec:soap}
@@
 \umberto{Specify characteristic of the star.}
-
-\umberto{Add info on the standard errors about the asymmetry parameter and the width and make a comparison with the results from the bootstrap. Then right discussions and conclusions,}
 
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
-\caption{(RVs changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
+\caption{RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
 SN mean RV seems to have the smallest spurious variations caused by the faculae.}
-   %\caption{(left) RVs changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
+   %\caption{(left) RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
 SN mean RV seems to have the smallest spurious variations caused by the faculae.
@@
 
+Since all the variations in RV's displayed in Fig.~\ref{fig:faculae} are caused by the presence of a faculae on the photosphere of the star, we corrected the originally estimated set of RV's by using Eq.~\eqref{eq:RV:correction}).
+The results of the correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the parameters involved in Eq.~\eqref{eq:RV:correction}) are summarized in Table \ref{table:faculae.test}.
+It is straightforward noticing that the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the faculae.
+In particular the $R^{2}$ is extremely high regardless the fit that has been use (Normal or SN).
+We note also that the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) is not statistically significant to explain spurious variations caused by a faculae.
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.~\eqref{eq:RV:correction}).}
+    \label{fig:faculae.correction}
+\end{figure*}
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+Parameter          & RV         &   SN mean RV &   SN median RV \\
+\hline
+$\beta_{0}$            &    $1.93e-09$    & $0.03563$ & $0.03600$ \\
+\hline
+$\beta_{1}$            &    $3.75e-05$    & $0.00681$ & $0.00684$ \\
+\hline
+$\beta_{2}$            &     $0.423$   &  $ 0.24128 $ & $ 0.24112$\\
+\hline
+$\beta_{3}$            &     $0.281$   &  $ 0.00168 $ & $  0.00169 $\\
+\hline
+$\beta_{4}$            &     $0.526 $   &  $ 0.22108 $ & $ 0.21188 $\\
+\hline
+$R^{2}$      &     $0.9967$    &  $0.9571$ & $0.977$  \\
+\hline
+\end{tabular}
+\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a faculae, according to Eq.~\eqref{eq:RV:correction}).}
+\label{table:faculae.test}
+\end{table}
+
 \subsection{Spot} \label{sec:soap.spot}
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
-\caption{RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
+\caption{RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
 SN mean RV seems to have the smallest spurious variations caused by the faculae.}
-   %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
+   %\caption{(left) RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
 SN mean RV seems to have the smallest spurious variations caused by the faculae.
@@
 
+As before, we corrected the originally estimated set of RV's by using Eq.~\eqref{eq:RV:correction}).
+The results of the correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the parameters involved in Eq.~\eqref{eq:RV:correction}) are summarized in Table \ref{table:spot.test}.
+Also in this case the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the spot.
+The $R^{2}$ is extremely high regardless the fit that has been use (Normal or SN).
+The main difference respect to the previous case is that the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) is statistically significant to explain spurious variations caused by a spot.
+This information could be useful in the future for disentangle spots from facuale.
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.~\eqref{eq:RV:correction}).}
+    \label{fig:spot.correction}
+\end{figure*}
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+Parameter          & RV         &   SN mean RV &   SN median RV \\
+\hline
+$\beta_{0}$            &    $8.62e-10 $    & $7.24e-09$ & $7.19e-09$ \\
+\hline
+$\beta_{1}$            &    $0.000354$    & $0.0639$ & $0.0638 $ \\
+\hline
+$\beta_{2}$            &     $1.04e-07$   &  $ 2.67e-08 $ & $ 2.66e-08$\\
+\hline
+$\beta_{3}$            &     $ 2.26e-06$   &  $ 1.72e-07 $ & $  1.72e-07 $\\
+\hline
+$\beta_{4}$            &     $1.11e-07 $   &  $ 2.85e-08 $ & $ 2.87e-08 $\\
+\hline
+$R^{2}$      &     $0.9897$    &  $0.9914$ & $0.9929$  \\
+\hline
+\end{tabular}
+\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\eqref{eq:RV:correction}).}
+\label{table:spot.test}
+\end{table}
+
 \subsection{Spot and planet} \label{sec:soap.spot.planet}
 
-\umberto{Specify characteristic of the spot.}
+The last presented simulation example consists in having not only spurious variations caused by the presence of a spot on the photosphere of the star but also artificially injecting a planet.
+The purpose of this example is to check if we are able to disentangle the two difference sources of variations in the set of RV's.
 
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
- \caption{RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
+ \caption{RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
 N mean RV seems to have the largest variations caused by the combined action of spot and planet.}
-   %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
+   %\caption{(left) RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
 N mean RV seems to have the largest variations caused by the combined action of spot and planet.
@@
 
-As final step we removed to the RVs obtained in this case those spurious signals coming from the spot.
-The results, presented in Fig.~\ref{fig:planet-spot}, show that the periodic pure doppler shift caused by the planet is detected.
-
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 4in]{RV_comparison_PLANET.pdf} 
-%\includegraphics[height = 2.5in]{SOAP_PLANET_Comparison_para_SN.pdf} 
-   \caption{RVs changes as function of the orbital phase after removed the spurious effect of the spot. In green the real signal of the planet is displayed.}
-    \label{fig:planet-spot}
-\end{figure*}
+In order to correct the estimated set of RV's from spurious variations caused by the spot, we need to generalize Eq.~\eqref{eq:RV:correction}), in order to consider also the possibly presence of an exoplanet.
+Hence, rather than just using Eq.~\eqref{eq:RV:correction}) we add the following function, which represents the pure doppler shift of the exoplanet under the assumption of circular orbit:
+%
+\begin{equation}
+RV_{\text{exoplanet}}= K \sin \left(\frac{2 \pi}{P} (t - t_{0})\right),
+\label{eq:RV:correction.planet}
+\end{equation}
+%
+where the amplitude $K$, the orbital period $P$ and the epoch at the periapsis $t_{0}$ are three unknown parameters that define the presence of the exoplanet.
+Overall, the variations in RV's of the star can be defined as
+%
+\begin{equation}
+RV= RV_{\text{stellar activity}} + RV_{\text{exoplanet}}.
+\label{eq:RV:correction.overall}
+\end{equation}
+%
+
+We note that the p-value associated with the amplitude parameter $K$ is particularly relevant for rejecting or not rejecting the assumption about the presence of an orbiting companion.
+Finally we note also that Eq.~\eqref{eq:RV:correction.planet}) is non linear, meaning that the estimation of all the parameters involved in Equation  (\ref{eq:RV:correction.overall}) has to be done numerically.
+We used non linear least squares and the results are displayed in Fig..~\ref{fig:spotplanet.correction}.
+We can see how in this case we are able to disentangle the spurious variations in RV's caused by stellar activity from the pure doppler shift due to the planet.
+The statistical tests conducted on the parameters, whose results are summarized in Table \ref{table:spotplanet.test}, are significant.
+We note in particular that the p-value associate to the amplitude parameter $K$ is $2e-16$.
+This result can be justify by the fact that the planet artificially injected has amplitude $K=10 \ms$.
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 4in]{SPOT_PLANET_NEW_CORRECTION.pdf} 
+   \caption{Set of  variations in RV's estimated using a Normal and a SN fit before and once corrected from stellar activity.
+In this case there are spurious variations caused by the spot and pure doppler shift due to the planet.
+The correction is done using Eq.~\eqref{eq:RV:correction.overall}).}
+    \label{fig:spotplanet.correction}
+\end{figure*}
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+Parameter          & RV         &   SN mean RV &   SN median RV \\
+\hline
+$\beta_{0}$            &    $2.89e-09$    & $2.02e-07 $  & $2.00e-07$ \\
+\hline
+$\beta_{1}$            &    $0.00105$    & $0.005216 $  & $0.005211$ \\
+\hline
+$\beta_{2}$            &     $6.31e-07$   & $7.33e-06$ & $ 7.32e-06$\\
+\hline
+$\beta_{3}$            &     $ 2.34e-05$   &  $ 0.000315$  & $ 0.000315 $\\
+\hline
+$\beta_{4}$            &     $6.73e-07$   &  $7.78e-06$ & $ 7.82e-06 $\\
+\hline
+K            &     $2e-16$   &  $2e-16$   & $ 2e-16 $\\
+\hline
+P            &     $2e-16$   &  $2e-16$ & $2e-16 $\\
+\hline
+$t_{0}$            &     $2e-16$   &  $2e-16$ & $2e-16 $\\
+\hline
+\end{tabular}
+\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\eqref{eq:RV:correction.overall}).
+All the parameters are statistically significants, in particular the amplitude parameter $K$ that provides relevance about the possibly presence of the exoplanet.
+Note that since non linear least squares are required, the $R^2$ is not displayed.}
+\label{table:spotplanet.test}
+\end{table}
 
@@
 When stellar activity is dominated by faculae, both the shape and the width of the CCF changes as the faculae evolves on the photosphere of the star.
+The proposed function to correct for stellar activity addressed high level of spurious variations in RV's caused by active regions.
+In particular, respect to other common linear interpolation, we proposed to use as covariates also the amplitude parameter of the CCF and the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM).
 Finally, the correlations involving the common indicators (i.e.
@@
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-\section{Real data applications} \label{sec:4}
+\section{Real data application} \label{sec:4}
 
@@
 
+Using Equation (\ref{eq:RV:correction}), we provide a new set of RV's corrected from stellar activity.
+The results are shown in Figure ~\ref{fig:alphacent:correctionRV}.
+We see that, once corrected for stellar activity, the residuals in the Normal and SN analysis are comparable.
+However, we note that when using SN mean RV, the correction is more important.
+In fact, the comparison of $R^2$ shows that the SN fit accounts for a higher percentage of variability caused by stellar activity (i.e.
+spurious variations in RV's).
+
+\begin{figure} 
+   \centering
+\includegraphics[height = 6in]{NEW_CORRECTIONHD12862_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of RV's for Alpha Centauri B using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Equation (\ref{eq:RV:correction}).
+Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
+   \label{fig:alphacent:correctionRV}
+\end{figure}
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+Parameter          & RV         &   SN mean RV &   SN median RV \\
+\hline
+$\beta_{0}$            &    $2.22e-16$    & $2.22e-16 $  & $2.22e-16$ \\
+\hline
+$\beta_{1}$            &    $2.22e-16$    & $2.22e-16 $  & $2.22e-16$ \\
+\hline
+$\beta_{2}$            &     $2.22e-16$   & $2.22e-16 $ & $2.22e-16$\\
+\hline
+$\beta_{3}$            &     $ 2.22e-16$   &  $2.22e-16 $  & $ 2.22e-16$\\
+\hline
+$\beta_{4}$            &     $2.22e-16$   &  $2.22e-16 $ & $ 2.22e-16 $\\
+\hline
+$R^{2}$      &     $0.57$    &  $0.78$ & $0.67$  \\
+\hline
+\end{tabular}
+\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\eqref{eq:RV:correction}).
+All the parameters are useful in explaining variations in RV's of the star that can be caused by stellar activity.
+The evaluation of the $R^2$ shows that the proposed linear combination better explains variations in RV's due to stellar activity coming from the SN analysis that uses SN mean RV.}
+\label{table:alphacent.test}
+\end{table}
+
 Both the proposed indicators coming from the SN distribution have desirable and undesirable behaviors: RV mean SN better catches changes in the asymmetry of the CCF but the resulting set of RVs ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Section \ref{intro}.
@@
 \umberto{to be done}
+\umberto{add here correction for stellar activity: table + plot to check if we get the planet}
 

### 2018-05-21 manuscript.tex
Add files via upload

@@
 %
-%\institute{Department of Statistical Sciences, University of Padua, Padua, Italy
+%\institute{Department of Mathematic and Statistics, University of Helsinki, Helsinki, Finland
 %	      \and Department of Statistics and Data Science, Yale University, New Haven, CT, USA
@@
 Stellar activity is the main limitation to the detection of small-mass exoplanets using the radial-velocity (RV) technique.
-Stellar activity can be probed by measuring the cross-correlation function (CCF) shape variations as a function of time.
+Stellar activity can be probed by measuring variations in the shape of the cross-correlation function (CCF) as a function of time.
 Those variations are measured using the different moments of the CCF, therefore measuring with the best precision those moments is crucial to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
 
-We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, naturally provides an extra parameter to model the CCF natural asymmetry induced by convective blueshift.
-
-We analyze 5 stars with different activity levels and different signal-to-noise ratio levels.
+We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, naturally provides an extra parameter to model the natural asymmetry of the CCF induced by convective blueshift.
+
+We analyze 5 stars with different activity levels and different signal-to-noise ratio (SNR) levels.
 In each case, we compare the results obtained by fitting to the CCF respectively a Normal and a SN.
@@
 
-The correlations between the RVs and the CCF asymmetry or RVs and the CCF width is always stronger when using the parameters derived from the SN in the case of real observations.
-Therefore the CCF asymmetry and width derived using a SN are more sensitive to stellar activity, which allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals.
-The precision on the RVs, derived using the median of the fitted SN distributions are on average $10\%$ smaller than the RV errors calculated on the mean of the Normal.
+The correlation between the RV's and the CCF asymmetry or the correlation between the RV's and the CCF width are always stronger when using the parameters derived from the SN in the case of real observations.
+Therefore the CCF asymmetry and the CCF width derived using a SN are more sensitive to stellar activity, which allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals.
+The precision on the estimated set of RV's, derived using the median of the fitted SN distributions are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
 In addition, the asymmetry parameter derived from the SN is on average $15\%$ better than the one calculated on the common Bisector Inverse Slope Span (BIS SPAN).
-We strongly encourage the use of the SN distribution rather than the Normal distribution, because this allows to retrieve in one single fit the different moments of the CCF, because the derived moments probe better stellar activity signals and because the standard errors on the RV and the the asymmetry are smaller.
+We strongly encourage the use of the SN distribution rather than the Normal distribution, because this allows us to retrieve in one single fit the different moments of the CCF, because the derived moments better catch stellar activity signals and finally because the standard errors on the RV's and the the asymmetry parameter are smaller than the one estimated with the Normal fit.
 
@@
 
-When working with radial velocities, the main limitation to the detection of small-mass exoplanets is not anymore the precision of the instruments used, but the different noises induce by the stars we are observing \citep[][]{Dumusque:2017aa}.
+When working with radial velocities (RV's), the main limitation to the detection of small-mass exoplanets is not anymore the precision of the instruments used, but the different noises induced by the stars we are observing \citep[][]{Dumusque:2017aa}.
 Indeed, stellar oscillations, granulation phenomena and stellar activity all induce RV signals \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are beyond the meter-per-second precision reached by the best high-resolution spectrographs.
@@
 Among the different stellar signals we are aware of, the one that is the most difficult to characterize and to correct for is the signal induced by stellar activity.
-Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, inducing spurious RV variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b}.
+Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, inducing spurious RV's variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b}.
 In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, that will shift the entire stellar spectrum, and stellar activity that modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}.
-However, on quiet GKM dwarfs, the main target for precise RV measurements, stellar activity induce signals of a few \ms.
+However, on quiet GKM dwarfs, the main target for precise RV's measurements, stellar activity induce signals of a few \ms.
 This corresponds physically to variations smaller than 1/100th of a pixel on the detector.
@@
 To be able to measure such tiny variations, we average the information of all the line in the spectrum by cross correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}.
-
 The result of this operation gives us the cross-correlation function (CCF).
-To measure the Doppler-shift between different spectra, and therefore get the RV of a star as a function of time, we calculate the variations of the CCF barycenter.
+To measure the Doppler-shift between different spectra, and therefore get the RV's of a star as a function of time, we calculate the variations of the CCF barycenter.
 The barycenter is generally estimated by fitting a Normal distribution to the CCF, and taking its mean.
-Variation in line shape between different spectra, which indicate the presence of signals induced by stellar activity, is measured by analysing the different moments of the CCF.
+Variations in line shape between different spectra, which indicate the presence of signals induced by stellar activity, is measured by analysing the different moments of the CCF.
 Generally, the width of the CCF is estimated using the FWHM of the fitted Normal distribution, and its asymmetry using the the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
@@
 The hyperparameters of the Gaussian process are generally trained on the different activity indicators \citep[e.g.][]{Haywood-2014,Rajpaul-2015}.
-It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated to the RVs but also for which we can obtain the best precision.
+It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated to the RV's but also for which we can obtain the best precision.
 
@@
 Several works have derived indicators that are more sensitive to line asymmetry than the BIS SPAN.
-In \citet{Boisse-2011}, the authors develop $V_{span}$ a new indicator to derive the CCF asymmetry, that is more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR).
+In \citet{Boisse-2011}, the authors develop $V_{span}$, a new indicator to derive the CCF asymmetry that is more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR).
 \citet{Figueira-2013} studied the use of two new indicators, bi-Gauss and $V_{asy}$.
-The authors were able to show that when using bi-Gauss, the amplitude in asymmetry is 30\% larger, therefore allowing the detection of smaller-amplitude correlations with radial-velocity variations.
+The authors were able to show that when using bi-Gauss, the amplitude in asymmetry is 30\% larger, therefore allowing the detection of smaller-amplitude correlations with RV's variations.
 They also demonstrated that $V_{asy}$ seems to be the best indicator of line asymmetry at high SNR, as its correlation with RV is more significant than any other asymmetry indictors.
@@
 %\subsection{Why using a SN distribution?}
-In all the method described above, the RV and the FWHM is derived using a Normal distribution fitted to the CCF, and the asymmetry is estimated using another approach.
+In all the method described above, the RV and the FWHM are derived using a Normal distribution fitted to the CCF, and the asymmetry is estimated using another approach.
+
 In this paper we propose to use a Skew Normal (SN) distribution to derive at the same time the RV, the FWHM and the asymmetry of the CCF, as this function includes a skewness parameter \citep[][]{Azzalini1985}.
@@
 The paper is organized as follow.
-In Sec.~\ref{sec:2} and in Sec.~\ref{sec:3} we introduce the SN distribution and describe its applicability for modeling the CCF,  showing that the SN distribution is a better representation of observed CCF than a Normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
-In Sec.~\ref{sec:3.1} we present a simple model to correct from stellar activity.
-In Sec.~\ref{sec:soap} we study the SN fit to the CCF using simulation coming from SOAP 2.0.
+In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  showing that the SN distribution is a better representation of observed CCF than a Normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
+In Sec.~\ref{sec:31} we present a simple model to correct from stellar activity which extends the ones proposed by \citet[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
+In Sec.~\ref{sec:soap} we study the SN fit to the CCF using simulations coming from SOAP 2.0.
 In Sec.~\ref{sec:4}, we compare on real observations the sensitivity of the SN parameters to stellar activity with respect to other existing indicators.
-In Sec.~\ref{sec:5} we derive error bars for the different CCF parameters, and finally we discuss our results and conclude in Sec.~\ref{sec:discu} and Sec.~\ref{sec:conclu}.
+In Sec.~\ref{sec:5} we derive error bars for the different CCF moments and finally we discuss our results and conclude in Sec.~\ref{sec:discu} and Sec.~\ref{sec:conclu}.
 
@@
 %
-For reasons related to the interpretation of the parameters in Equation~\eqref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used, which is referred to as the \emph{centered parametrization} (CP).
+For reasons related to the interpretation of the parameters in Eq.~\eqref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used, which is referred to as the \emph{centered parametrization} (CP).
 We will be using the CP in this work, which includes a mean parameter $\mu$, a variance parameter $\sigma^2$ and a skewness parameter $\gamma$.
@@
 By using Eq.~\eqref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution.
-For the $\alpha$ values used in Fig.~\ref{fig:SN.plot}, the corresponding values of $\mu$, $\sigma^2$, $\gamma$ are displayed in Table~\ref{tab:cp_values}.
+For the $\alpha$ values used in Fig.~\ref{fig:SN.plot}, the corresponding values of ($\mu$, $\sigma^2$, $\gamma$) are displayed in Table~\ref{tab:cp_values}.
 In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution (rather than simply a location and scale parameter) and $\gamma$ becomes an index for evaluating the skewness of the SN.
@@
 Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution should in principle better catch this aspect, together with other changes in asymmetry, respect the Normal fit.
-To initially check this assumption, we compared the CCF residuals after fitting a Normal and a SN distribution for 2 stars.
-The first star is Alpha Centauri b, whose CCFs have high signal-to-noise ratio (SNR).
-The second star is Corot-7, whose CCFs have low SNR.
+To initially check this intuition, we compared the CCF residuals after fitting a Normal and a SN distribution for 2 stars.
+The first star is Alpha Centauri b, whose CCF's have high signal-to-noise ratio (SNR).
+The second star is Corot-7, whose CCF's have low SNR.
 Fig.~\ref{fig:Residual.comparison} shows that the SN seems to be a slightly better model to explain the shape of the CCF, in particular as the SNR decreases.
@@
 \includegraphics[height = 2.5in]{[1]LRa01_E2Residuals.pdf} 
-   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCFs from the star Alpha Centauri b (left) and Corot-7 (right).
+   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCF's from the star Alpha Centauri b (left) and Corot-7 (right).
 When looking at the residuals corresponding to the tails of the CCF, the results derived by the two fits are comparable.
@@
 In the following of the paper, we define RV as the mean of the Normal distribution.
-Concerning the fit of the CCF using the SN, we present at first $2$ indicators that define the RV of the star: the mean of the SN, defined as RV mean SN and the median of the SN, defined as RV median SN (i.e.
-realling Eq.\eqref{eq:snmed}, $m$ = RV median SN).
-We will discuss advantages and limits for both these choices in Section \ref{sec:4} and Section \ref{sec:5}.
+Concerning the fit of the CCF using the SN, we present at first $2$ indicators that define the RV of the star: the mean of the SN, defined as SN mean RV and the median of the SN, defined as SN median RV (i.e.
+realling Eq.\eqref{eq:snmed}, $m$ = SN median RV).
+We will discuss advantages and limits for both these choices in Sec.
+\ref{sec:4} and Sec.
+\ref{sec:5}.
 For the width of the CCF, we use the FWHM of the Normal, which is $2\sqrt(2\ln2)\sigma$.
@@
 The BIS SPAN will be compared to the asymmetric parameter $\gamma$ of the SN, named SN GAMMA.
-To test the strength of the correlation between the RVs and the different indicators for stellar activity, we calculated the Pearson correlation coefficient, $R$.
-A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ (i.e., no correlation) is provided, along with a $95\,\%$ confidence interval for $R$.
+To test the strength of the correlation between the estimated RV's and the different indicators used to evaluate stellar activity, we calculated the Pearson correlation coefficient, which in its general form is defined as:
+%
+\begin{equation}
+R (x,y)= \frac{cov(x,y)}{\sigma(x),\sigma(y)},
+\label{eq:Pearson:corr}
+\end{equation}
+%
+where $x$ and $y$ are two quantitative variables, $cov(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represent their standard deviations. 
+A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided, along with a $95\,\%$ confidence interval for $R$.
 
@@
 
-To test the strength of the correlation between the estimated RV's and the different indicators used to evaluate stellar activity, we calculated the Pearson correlation coefficient, which in its general form is defined as:
-%
-\begin{equation}
-R (x,y)= \frac{cov(x,y)}{\sigma(x),\sigma(y)},
-\label{eq:Pearson:corr}
-\end{equation}
-where $x$ and $y$ are two quantitative variables, $cov(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represent their standard deviations. 
-A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided, along with a $95\,\%$ confidence interval for $R$.
-%
 Because of the spurious variations in RV's caused by active regions, a crucial step of the entire analysis is to correct the initially estimated RV's in order to retrieve a set of RV's containing ideally only the possibly pure doppler shift coming from the exoplanets.
-In order to reach this goal, we propose to consider a linear combination of the RV's having as covariates the amplitude parameter A, the BIS SPAN, the FWHM and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM and the interaction between $\gamma$ and SN FWHM in the SN case), as shown in Eq.~\eqref{eq:RV:correction}.
+In order to reach this goal, we propose to consider a linear combination of the RV's having as covariates the amplitude parameter A (also known as contrast), the BIS SPAN (or $\gamma$), the FWHM (or SN FWHM) and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM and the interaction between $\gamma$ and SN FWHM in the SN case).
+The parameters in parenthesis will be used when the SN fit is used.
+We propose the following function to correct the RV's from stellar activity:
 %
@@
 
-While the parameters $\gamma$ (or BIS SPAN) and SN FWHM (or FWHM) have already been introduced, in Eq.~\eqref{eq:RV:correction} we propose also two include the amplitude parameter $A$ and a variable that quantifies the interaction between $\gamma$ (or BIS SPAN) and SN FWHM (or FWHM).
-The inclusion of the amplitude parameter A is justified by the expected behavior of the CCF in presence of active regions.
-Fig.~\ref{fig:spotA} show that the presence for instance of a spot produces also changes on the amplitude of the CCF and not only on its asymmetry or width.
+While the parameters BIS SPAN (or $\gamma$) and FWHM (or SN FWHM) have already been introduced and used in \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}, by using Eq.~\eqref{eq:RV:correction} we propose also to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN WHM).
+The inclusion of the contrast parameter $A$ is justified by the expected behavior of the CCF in presence of active regions.
+Fig.~\ref{fig:spotA} shows that the presence for instance of a spot produces also changes on the amplitude of the CCF and not only on its asymmetry or width.
 %
@@
 \includegraphics[height = 4in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
-   \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF and not only on its asymmetry or width.}
+   \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF (also known as contrast) and not only on its asymmetry or width.
+This very same plot has been originally presented by \citep{Dumusque-2014b} when introducing the Spot Oscillation And Planet (SOAP) 2.0 simulator.}
     \label{fig:spotA}
@@
 %
-The reasons for including in Eq.~\eqref{eq:RV:correction} a variable that quantifies the interaction between $\gamma$ (or BIS SPAN) and SN FWHM (or FWHM) will be clarified in the next Section and are related to a first attempt to disentangle spots from faculae.
+The reasons for including in Eq.~\eqref{eq:RV:correction} a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM) will be better justified through the results of the examples presented in Sec.\ref{sec:soap}.
+We point out however that while the association between in this case BIS SPAN  (or $\gamma$) and FWHM (or SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant.
+In particular the effect differs at different values of the other values.
+As a consequence of this, if two variables are interacting the may or may not be associated.
+In all the analyses presented in Sec.
+\ref{sec:soap} and Sec.
+\ref{sec:4} we found weak correlations between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM) but the inclusion of the interaction term in Eq.~\eqref{eq:RV:correction} has shown nevertheless some utility in explaining spurious variations in RV's.
 
@@
 
+As final remark we recall that, when working with a linear regression, there are several ways to select the variables to include in the model.
+While usually the stepwise technique takes place \citep{efroymson1960multiple,hocking1976biometrics}, the proposed function defined in Eq.~\eqref{eq:RV:correction} that corrects from stellar activity is the result of statistical and astronomical considerations.
+In particular we checked that the correlations between the proposed parameters were not approaching one: if it were the case, the matrix needed to calculate the estimates would have been singular, hence non invertible.
+This problem is known in statistic with the term multicollinearity and leads to unreasonable results and estimation of the standard errors associated to the parameters of interest.
+A detailed discussion of the topic can be found in the book by \citep{belsley1991conditioning}.
+In the literature there are examples of stars presenting a high correlation between the contrast parameter $A$ and the FWHM \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
+In the analyses of the presented work, we did not find any correlation between the contrast parameter $A$ and the FWHM (or between the contrast parameter $A$ and the SN FWHM) exceeding $0.66$ for all the analyzed stars and therefore the problem of multicollinearity is avoided.
+For the interpretation of the coefficients, we centered on the mean all the variables considered in the linear regression defined in Eq.~\eqref{eq:RV:correction}.
+Last, when proposing interactions between covariates, we found that only the one between the width and the asymmetry of the CCF is statistically helpful to explain spurious variations in RV's caused by stellar activity.
+Consequently, in the present work, the other interactions variables are not displayed.
+
 %-----------------------------------------------------------------------------------------------------------------------------------------------
 \section{Simulation Study} \label{sec:soap}
-In order to evaluate the performance of the proposed SN approach for modeling the CCF, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.
+In order to evaluate the performance of the proposed SN approach for modeling the CCF and the goodness of the proposed correction from stellar activity by using Eq.~\eqref{eq:RV:correction}, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.
 
@@
 \umberto{Specify characteristic of the star.}
+\xavier{}
 
@@
 
-\umberto{Specify characteristic of the faculae.}
+\umberto{Specify characteristic of the faculae.}\xavier{}
 
 Fig.~\ref{fig:faculae} shows the results obtained when a faculae is present on the photosphere of the star.
-It is possible to note that, although there is not a planet, the presence of the faculae leads to spurious variations in RVs for all the proposed indicators.
+It is possible to note that, although there is not a planet, the presence of the faculae leads to spurious variations in RV's for all the proposed indicators.
 SN mean RV seems to have the smallest spurious variations caused by the faculae.
-%Anyway, the evaluation of the standard errors retrieved by using a bootstrap analysis that will be detailed discussed in Section \ref{sec:5}, shows that RV mean SN has the largest related uncertainties.
-The standard errors associates with RV median SN and RV are comparable, although the standard errors retrieved when the RV is defined as the median of the SN are $10 \%$ smaller than the standard errors derived for RV.
-
-Since in this case we know that the variations in RV are only caused by the faculae, the evaluation of the correlations between the set of RVs and the asymmetry parameters can provide relevant information to understand the cause of the variations observed in RVs.
-Fig.~\ref{fig:faculae.corr} shows the correlations obtained using as RV respectively RV mean SN, RV median SN and RV.
-The $\gamma$ parameter shows a correlation with RV median SN equal to $-0.944$, which is stronger than the correlations between the other asymmetry indicators and their estimated RVs.
-The correlation between the width of the CCF and RV mean SN is the strongest one ($R^{2}=0.655$).
+
+Since in this case we know that the variations in RV are only caused by the faculae, the evaluation of the correlations between the set of RV's and the asymmetry parameters can provide relevant information to understand the cause of the variations observed in RV's.
+Fig.~\ref{fig:faculae.corr} shows the correlations obtained using as RV respectively SN mean RV, SN median RV and RV.
+The $\gamma$ parameter shows a correlation with SN median RV equal to $-0.944$, which is stronger than the correlations between the other asymmetry indicators and their estimated RV's.
+When focusing on the width of the CCF, The correlation between SN FWHM and SN mean RV is the strongest one ($R^{2}=0.655$).
 
@@
 (right) Evaluation of the standard errors corresponding to the defined RVs.
-The standard errors retrieved for RV median SN are $10 \%$ smaller than the standard errors derived for RV.
-RV mean SN has the largest related uncertainties.}
+The standard errors retrieved for SN median RV are $10 \%$ smaller than the standard errors derived for RV.
+SN mean RV has the largest related uncertainties.}
     \label{fig:faculae}
@@
 
-Since all the variations in RV's displayed in Fig.~\ref{fig:faculae} are caused by the presence of a faculae on the photosphere of the star, we corrected the originally estimated set of RV's by using Eq.~\eqref{eq:RV:correction}).
-The results of the correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the parameters involved in Eq.~\eqref{eq:RV:correction}) are summarized in Table \ref{table:faculae.test}.
+Since all the variations in RV's displayed in Fig.~\ref{fig:faculae} are caused by the presence of a faculae on the photosphere of the star, we corrected the originally estimated set of RV's by using Eq.~\eqref{eq:RV:correction}.
+The results of the correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the parameters involved in Eq.~\eqref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
 It is straightforward noticing that the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the faculae.
@@
    \caption{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.~\eqref{eq:RV:correction}).}
+The correction is done using Eq.~\eqref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
+Once corrected for stellar activity the residuals do not show a systematic component.}
     \label{fig:faculae.correction}
@@
 \hline
-$\beta_{0}$            &    $1.93e-09$    & $0.03563$ & $0.03600$ \\
-\hline
-$\beta_{1}$            &    $3.75e-05$    & $0.00681$ & $0.00684$ \\
-\hline
-$\beta_{2}$            &     $0.423$   &  $ 0.24128 $ & $ 0.24112$\\
-\hline
-$\beta_{3}$            &     $0.281$   &  $ 0.00168 $ & $  0.00169 $\\
-\hline
-$\beta_{4}$            &     $0.526 $   &  $ 0.22108 $ & $ 0.21188 $\\
+$\beta_{0}$            &    $0.0016$    & $0.26$ & $0.60$ \\
+\hline
+$\beta_{1}$            &    $3.75e-05$    & $0.0068$ & $0.0069$ \\
+\hline
+$\beta_{2}$            &     $7.79e-16$   &  $1.97e-05$ & $3.69e-08$\\
+\hline
+$\beta_{3}$            &     $0.25$   &  $0.0011$ & $0.0011$\\
+\hline
+$\beta_{4}$            &     $0.53$   &  $0.21$ & $0.21$\\
 \hline
@@
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a faculae, according to Eq.~\eqref{eq:RV:correction}).}
+\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a faculae, according to Eq.~\eqref{eq:RV:correction}.
+Beyond the contrast parameter A and the asymmetry parameter of the CCF which are useful for both the analyses, the width of the CCF is statistically useful to explain spurious variations in RV's caused by a faculae only for the SN analyses.
+The term of interaction between the asymmetry and the width of the CCF is not helpful to explain part of the variability in the set of RV's.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}
 \label{table:faculae.test}
@@
 
-\umberto{Specify characteristic of the spot.}
+\umberto{Specify characteristic of the spot.}\xavier{}
 
 Fig.~\ref{fig:spot} shows the results obtained when a spot is present on the photosphere of the star.
-Similarly to the previous case, the presence of the spot leads to spurious variations in RVs for all the proposed indicators, but N mean RV seems to have the smallest ones.
-We note however that in this case all the three indicators are similarly effected by the spurious changes in RVs caused by the spot.
-%The evaluation of the standard errors, as before, shows that RV mean SN has the largest variability, while the standard errors associated with RV median SN are $10 \%$ smaller than the standard errors associated with RV.
-
-Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and respectively RV mean SN, RV median SN and RV.
-The correlation between $\gamma$ and RV median SN is equal to $-0.89$ while the correlation between $\gamma$ and RV median SN is equal to $-0.82$.
+Similarly to the previous case, the presence of the spot leads to spurious variations in RV's for all the proposed indicators, but SN mean RV seems to have the smallest ones.
+We note however that in this case all the three indicators are similarly effected by the spurious changes in RV's caused by the spot.
+
+Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and respectively SN mean RV, SN median RV and RV.
+The correlation between $\gamma$ and SN median RV is equal to $-0.89$ while the correlation between $\gamma$ and SN median RV is equal to $-0.82$.
 Both these correlations are stronger than the correlation between the BIS SPAN and RV ($R^2=-0.77$).
-The correlations between the width of the CCF and the corresponding RVs are slightly stronger when fitting a SN rather than a Normal distribution, as shown in the left series of plots in Fig.~\ref{fig:spot.corr}.
-The results shows anyway a correlation close to $0$, suggesting that the presence of a spot on the photosphere of star changes the shape of the CCF rather than its width.
+The correlations between the width of the CCF and the corresponding RV's are slightly stronger when fitting a SN rather than a Normal distribution, as shown in the left series of plots in Fig.~\ref{fig:spot.corr}.
+The results show anyway a correlation close to $0$ when focusing on the width of the CCF, suggesting that the presence of a spot on the photosphere of star leads to changes in the shape of the CCF rather than its width.
 
@@
 (right) Evaluation of the standard errors corresponding to the defined RVs.
-The standard errors retrieved for RV median SN are $10 \%$ smaller than the standard errors derived for RV.
-RV mean SN has the largest related uncertainties.}
+The standard errors retrieved for SN median RV are $10 \%$ smaller than the standard errors derived for RV.
+SN mean RV has the largest related uncertainties.}
     \label{fig:spot}
@@
 
-As before, we corrected the originally estimated set of RV's by using Eq.~\eqref{eq:RV:correction}).
-The results of the correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the parameters involved in Eq.~\eqref{eq:RV:correction}) are summarized in Table \ref{table:spot.test}.
+As before, we corrected the originally estimated set of RV's by using Eq.~\eqref{eq:RV:correction}.
+The results of the correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the parameters involved in Eq.~\eqref{eq:RV:correction} are summarized in Table \ref{table:spot.test}.
 Also in this case the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the spot.
 The $R^{2}$ is extremely high regardless the fit that has been use (Normal or SN).
-The main difference respect to the previous case is that the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) is statistically significant to explain spurious variations caused by a spot.
+The main differences respect to the previous case are that the parameter $\beta_{3}$, associated with $\gamma$, and the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM), are statistically significant to explain spurious variations caused by a spot.
 This information could be useful in the future for disentangle spots from facuale.
@@
    \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.~\eqref{eq:RV:correction}).}
+The correction is done using Eq.~\eqref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
+Once corrected for stellar activity the residuals do not show a systematic component.}
     \label{fig:spot.correction}
@@
 \hline
-$\beta_{0}$            &    $8.62e-10 $    & $7.24e-09$ & $7.19e-09$ \\
-\hline
-$\beta_{1}$            &    $0.000354$    & $0.0639$ & $0.0638 $ \\
-\hline
-$\beta_{2}$            &     $1.04e-07$   &  $ 2.67e-08 $ & $ 2.66e-08$\\
-\hline
-$\beta_{3}$            &     $ 2.26e-06$   &  $ 1.72e-07 $ & $  1.72e-07 $\\
-\hline
-$\beta_{4}$            &     $1.11e-07 $   &  $ 2.85e-08 $ & $ 2.87e-08 $\\
+$\beta_{0}$            &    $0.47$    & $0.84$ & $0.81$ \\
+\hline
+$\beta_{1}$            &    $0.00035$    & $0.064$ & $0.064$ \\
+\hline
+$\beta_{2}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
+\hline
+$\beta_{3}$            &     $0.53$   &  $0.61$ & $0.61$\\
+\hline
+$\beta_{4}$            &     $1.11e-07 $   &  $2.85e-08 $ & $ 2.87e-08 $\\
 \hline
@@
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\eqref{eq:RV:correction}).}
+\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\eqref{eq:RV:correction}.
+All the covariates are statistically useful to explain the variability in RV's causued by a spot except the intercept and the width of the CCF.
+Concerning the SN analysis, the contrast parameter A is not statistically significant at level $5\%$.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}
 \label{table:spot.test}
@@
 
-The last presented simulation example consists in having not only spurious variations caused by the presence of a spot on the photosphere of the star but also artificially injecting a planet.
-The purpose of this example is to check if we are able to disentangle the two difference sources of variations in the set of RV's.
+The last presented simulation example consists in having not only spurious variations in RV's caused by the presence of a spot on the photosphere of the star but also a pure doppler shift because of an artificially injected planet.
+The purpose of this example is to check if we are able to disentangle the two different sources of variations in the set of RV's.
 
@@
 In this case N mean RV seems to have the largest variations caused by the combined action of spot and planet.
-%The evaluation of the standard errors leads to the same conclusions reported for the two previous cases: RV mean SN has the largest related uncertainties and the standard errors associates with RV median SN are $10 \%$ smaller than the standard errors derived for RV.
-
-Fig.~\ref{fig:spot.plus.planet.corr} shows the correlations between $\gamma$ and respectively RV mean SN and RV median SN and the correlation between BIS SPAN and RV.
+%The evaluation of the standard errors leads to the same conclusions reported for the two previous cases: SN mean RV has the largest related uncertainties and the standard errors associates with SN median RV are $10 \%$ smaller than the standard errors derived for RV.
+
+Fig.~\ref{fig:spot.plus.planet.corr} shows the correlations between $\gamma$ and respectively SN mean RV and SN median RV and the correlation between BIS SPAN and RV.
 In this case the correlations are weaker than the ones derived when only a spot is present on the photosphere of the star.
 Anyway the $\gamma$ parameter shows a correlation with the median SN of $-0.433$, which is stronger than what the correlation between the other asymmetry indicators and their corresponding RVs.
-The correlations between the width of the CCF and the corresponding RVs are comparable and, similarly to the previous case, close to $0$.
+The correlations between the width of the CCF and the corresponding RV's are comparable and, similarly to the previous case, close to $0$.
 
@@
 (right) Evaluation of the standard errors corresponding to the defined RVs.
-The standard errors retrieved for RV median SN are $10 \%$ smaller than the standard errors derived for RV.
-RV mean SN has the largest related uncertainties.}
+The standard errors retrieved for SN median RV are $10 \%$ smaller than the standard errors derived for RV.
+SN mean RV has the largest related uncertainties.}
     \label{fig:spot.plus.planet}
@@
 
-In order to correct the estimated set of RV's from spurious variations caused by the spot, we need to generalize Eq.~\eqref{eq:RV:correction}), in order to consider also the possibly presence of an exoplanet.
-Hence, rather than just using Eq.~\eqref{eq:RV:correction}) we add the following function, which represents the pure doppler shift of the exoplanet under the assumption of circular orbit:
+In order to correct the estimated set of RV's from spurious variations caused by the spot, we need to generalize Eq.~\eqref{eq:RV:correction}, in order to consider also the possibly presence of an exoplanet.
+Hence, rather than just using Eq.~\eqref{eq:RV:correction} we add the following keplerian function, which represents the pure doppler shift of the exoplanet under the assumption of circular orbit:
 %
@@
 
-We note that the p-value associated with the amplitude parameter $K$ is particularly relevant for rejecting or not rejecting the assumption about the presence of an orbiting companion.
-Finally we note also that Eq.~\eqref{eq:RV:correction.planet}) is non linear, meaning that the estimation of all the parameters involved in Equation  (\ref{eq:RV:correction.overall}) has to be done numerically.
-We used non linear least squares and the results are displayed in Fig..~\ref{fig:spotplanet.correction}.
+We note that the p--value associated with the amplitude parameter $K$ is particularly relevant for rejecting or not rejecting the assumption about the presence of an orbiting companion.
+Moreover we note also that Eq.~\eqref{eq:RV:correction.planet} is highly non linear, meaning that the estimation of all the parameters involved in Eq.~\eqref{eq:RV:correction.overall} has to be done numerically.
+%We used non linear least squares and the results are displayed in Fig.~\ref{fig:spotplanet.correction}.
 We can see how in this case we are able to disentangle the spurious variations in RV's caused by stellar activity from the pure doppler shift due to the planet.
 The statistical tests conducted on the parameters, whose results are summarized in Table \ref{table:spotplanet.test}, are significant.
-We note in particular that the p-value associate to the amplitude parameter $K$ is $2e-16$.
+We note in particular that the p--value associate to the amplitude parameter $K$ is $2e-16$.
 This result can be justify by the fact that the planet artificially injected has amplitude $K=10 \ms$.
 
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 4in]{SPOT_PLANET_NEW_CORRECTION.pdf} 
-   \caption{Set of  variations in RV's estimated using a Normal and a SN fit before and once corrected from stellar activity.
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 4in]{SPOT_PLANET_NEW_CORRECTION.pdf} 
+%   \caption{Set of  variations in RV's estimated using a Normal and a SN fit before and once corrected from stellar activity.
 In this case there are spurious variations caused by the spot and pure doppler shift due to the planet.
-The correction is done using Eq.~\eqref{eq:RV:correction.overall}).}
-    \label{fig:spotplanet.correction}
-\end{figure*}
+The correction is done using Eq.~\eqref{eq:RV:correction.overall} and the estimated parameters are presented in Table \ref{table:spotplanet.test}.
+In this case, by solving Eq.~\eqref{eq:RV:correction.overall}, we are able to completely disentangle the spurious variations in RV's caused by the presence of the spot from the pure dopplershift caused by the exoplanet.}
+%    \label{fig:spotplanet.correction}
+%\end{figure*}
 
@@
 \hline
-$\beta_{0}$            &    $2.89e-09$    & $2.02e-07 $  & $2.00e-07$ \\
-\hline
-$\beta_{1}$            &    $0.00105$    & $0.005216 $  & $0.005211$ \\
-\hline
-$\beta_{2}$            &     $6.31e-07$   & $7.33e-06$ & $ 7.32e-06$\\
-\hline
-$\beta_{3}$            &     $ 2.34e-05$   &  $ 0.000315$  & $ 0.000315 $\\
-\hline
-$\beta_{4}$            &     $6.73e-07$   &  $7.78e-06$ & $ 7.82e-06 $\\
+$\beta_{0}$            &    $7.09e-09$    & $ 3.44e-07$  & $4.96e-09$ \\
+\hline
+$\beta_{1}$            &    $0.00105$    & $0.0052$  & $0.0052$ \\
+\hline
+$\beta_{2}$            &     $2e-16$   & $2.43e-16$ & $2e-16$\\
+\hline
+$\beta_{3}$            &     $0.79$   &  $0.22$  & $0.22$\\
+\hline
+$\beta_{4}$            &     $6.73e-07$   &  $7.78e-06$ & $7.82e-06$\\
 \hline
@@
 \hline
+$\text{Residuals}$      &     $0.61 \ms$    &  $ 0.60 \ms$ & $0.60 \ms$  \\
+\hline
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\eqref{eq:RV:correction.overall}).
-All the parameters are statistically significants, in particular the amplitude parameter $K$ that provides relevance about the possibly presence of the exoplanet.
-Note that since non linear least squares are required, the $R^2$ is not displayed.}
+\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\eqref{eq:RV:correction.overall}.
+All the parameters are statistically helpful to address spurious variations in RV's except the FWHM.
+Concerning the keplerian parameters, the amplitude $K$ that provides relevance about the possibly presence of the exoplanet.
+Note that since non linear least squares are required, the residual standard error rather than the $R^2$ is displayed for each case.}
 \label{table:spotplanet.test}
@@
 
-In this Section we presented a first implementation of the SN fit to CCF, using the simulation environment SOAP.
-Before moving to the next Section, where the analyses on five real stars are presented, we need to provide further considerations.
-First of all, looking ad the analyses conducted with SOAP, it seems that the largest correlation between an asymmetry parameter and a set of RVs happens to be when respectively $\gamma$ and RV median SN are used.
-This is a bit surprising, since as the shape of the CCF changes, we expect RV median SN to be more robust than RV mean SN.
+In this Sec.\ref{sec:soap} we presented a first implementation of the SN fit to CCF, using the simulation environment SOAP.
+Before moving to real cases, where the analyses on five stars are presented, we need to provide further considerations.
+First of all, looking ad the analyses conducted with SOAP, it seems that the largest correlation between an asymmetry parameter and a set of RV's happens to be when respectively $\gamma$ and SN median RV are used.
+This is a bit surprising, since as the shape of the CCF changes, we expect SN median RV to be more robust than SN mean RV.
 \umberto{A possible justification of this ...}.
-As second, when searching for stellar activity by deriving the correlation between the set of RVs and either an asymmetry parameter or the width of the CCF, the latter leads to weaker and hence less conclusive results if the active region is a spot.
+As second, when searching for stellar activity by deriving the correlation between the set of RV's and either an asymmetry parameter or the width of the CCF, the latter leads to weaker and hence less conclusive results if the active region is a spot.
 When stellar activity is dominated by faculae, both the shape and the width of the CCF changes as the faculae evolves on the photosphere of the star.
+Related to these last two considerations, we note that the interaction between the asymmetry and the width of the CCF is useful to explain part of the variability in the RV's if the active region is a spot but not when it is a faculae.
 The proposed function to correct for stellar activity addressed high level of spurious variations in RV's caused by active regions.
 In particular, respect to other common linear interpolation, we proposed to use as covariates also the amplitude parameter of the CCF and the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM).
+As a consequence of using the interaction between the asymmetry and the width of the CCF, we note that the FWHM (or SN FWHM) becomes statistically not significant, while this is not the case if the interaction term is not involved in the linear regression.
 Finally, the correlations involving the common indicators (i.e.
@@
 
-We remand the reader to Section \ref{sec:5} for the evaluation of the standard errors associated with the parameters estimated for all the three presented cases.
-This step will point out how RV median SN minimizes the uncertainties respect using both RV mean SN and RV, therefore suggesting its use in order to properly define the set of RVs of the star.
+%In Sec.
+\ref{sec:5} we will present the evaluation of the standard errors associated with the parameters estimated for all the three presented cases.
+This step will point out how SN median RV minimizes the uncertainties respect using both SN mean RV and RV, therefore suggesting its use in order to properly define the set of RVs of the star.
 
@@
 
-In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN distribution defined in Section \ref{sec:3} with the approach based on the Normal distribution.
+In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN distribution defined in Sec.
+\ref{sec:3} with the approach based on the Normal distribution.
 Other four stars have been analyzed with the proposed method and details can be found in the Appendix \ref{appendix}.
-For all the stars that have been considered in the present work, we selected those CCFs having SNR larger than 10.
-
- A comparison with the results obtained by the classic approach is done, where the RVs of the star are estimated by retrieving the mean of the Normal distribution used to fit the CCF, along with the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}.
-The latter parameters are calculated separately from the Normal fit that leads to the set of RVs of the star.
+For all the stars that have been considered in the present work, we selected those CCF's having SNR larger than 10.
+
+ A comparison with the results obtained by the classic approach is done, where the RV's of the star are estimated by retrieving the mean of the Normal distribution used to fit the CCF, along with the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}.
+The latter parameters are calculated separately from the Normal fit that leads to the set of RV's of the star.
 
@@
 
-A total of $1808$ CCFs measured in $2010$ have been analysed from the star Alpha Centauri B.
+A total of $1808$ CCF's measured in $2010$ have been analysed from the star Alpha Centauri B.
 Several measurement in 2010 are contaminated by light from Alpha Centauri A.
-To remove contaminated spectra and thus CCFs, we performed the same selection as presented in \citet{Dumusque-2012}.
+To remove contaminated spectra and thus CCF's, we performed the same selection as presented in \citet{Dumusque-2012}.
 Moreover, as noted in \citet{Dumusque-2012} and \citet{Thompson-2017}, this dataset presents a strong stellar activity signal.
@@
 
-Fig.~\ref{fig:alphacent:diff:RV} shows the comparison between the RVs retrieved using the SN shape and the ones obtained with the Normal shape.
+Fig.~\ref{fig:alphacent:diff:RV} shows the comparison between the RV's retrieved using the SN shape and the ones obtained with the Normal shape.
 It is possible to appreciate the presence of a strong stellar activity signal, as expected \citep{Dumusque-2012,Thompson-2017}.
-When using RV mean SN, it is possible to observe more variations than the ones measured by the Normal fitting.
+When using SN mean RV, it is possible to observe more variations than the ones measured by the Normal fitting.
 This happens because the mean of the SN is more sensitive to stellar activity.
-In fact, because the SN includes an asymmetry parameter, RV mean SN gets more shifted in the direction of the asymmetry induced by stellar activity.
-On the other hand, when using RV median SN, smaller variations in RV are caused by changes in the asymmetry of the CCF, because this second location parameter is a more robust indicator than the mean.
+In fact, because the SN includes an asymmetry parameter, SN mean RV gets more shifted in the direction of the asymmetry induced by stellar activity.
+On the other hand, when using SN median RV, smaller variations in RV are caused by changes in the asymmetry of the CCF, because this second location parameter is a more robust indicator than the mean.
 The bottom plot of Fig.~\ref{fig:alphacent:diff:RV} captures this aspect.
@@
    \caption{(top) RVs as function of Julian Day for Alpha Centauri b.
-The RVs are retrieved using the mean of the Normal (red triangles), RV mean SN (black circles), RV median SN (cyan crosses).
-(bottom) RV differences between Normal RV and RV mean SN (black circles) and between Normal RV and a RV median SN (cyan crosses).}
+The RV's are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses).
+(bottom) RV differences between Normal RV and SN mean RV (black circles) and between Normal RV and a SN median RV (cyan crosses).}
    \label{fig:alphacent:diff:RV}
@@
 
-Similar to \citet{Figueira-2013}, we compare the correlation between the different activity indicators and the RVs of the star in Fig.~\ref{fig:alphacent:corrPlot}.
-The correlation between $\gamma$ and RV mean SN and the correlation between $\gamma$ and RV median SN are much stronger than the correlations calculated between the other asymmetry parameters and their corresponding RVs.
-In particular the correlation between $\gamma$ and RV mean SN is almost twice the correlation between the other asymmetry parameters and their corresponding RVs.
-
-Because the median is a more rubust index than the mean, the correlation between $\gamma$ and RV median SN is not as large as the correlation between $\gamma$ and RV mean SN, but it is nonetheless $1.5$ times larger than the correlation between the other common asymmetry parameters and their corresponding RVs.
-In other words, changes in the asymmetry of the CCF are better captured when using the RV mean SN.
-The correlation between FWHM and the RVs, either by using RV mean SN or RV median SN, is as well stronger when fitting a SN distribution rather than a Normal.
+Similar to \citet{Figueira-2013}, we compare the correlation between the different activity indicators and the RV's of the star in Fig.~\ref{fig:alphacent:corrPlot}.
+The correlation between $\gamma$ and SN mean RV and the correlation between $\gamma$ and SN median RV are much stronger than the correlations calculated between the other asymmetry parameters and their corresponding RV's.
+In particular the correlation between $\gamma$ and SN mean RV is almost twice the correlation between the other asymmetry parameters and their corresponding RV's.
+
+Because the median is a more robust index than the mean, the correlation between $\gamma$ and SN median RV is not as large as the correlation between $\gamma$ and SN mean RV, but it is nonetheless $1.5$ times larger than the correlation between the other common asymmetry parameters and their corresponding RV's.
+In other words, changes in the asymmetry of the CCF are better captured when using the SN mean RV.
+The correlation between FWHM and the RV's, either by using SN mean RV or SN median RV, is as well stronger when fitting a SN distribution rather than a Normal.
 All the correlations are statistically different from $0$.
-Recalling the analyses presented in Section \ref{sec:soap}, we could infer that Alpha Centauri b is dominated by faculae, because the correlations between the RVs and the width of the CCF are strong (in particular the correlation between RV mean SN and SN FWHM is $0.817$).
+Recalling the analyses presented in Sec.
+\ref{sec:soap}, we could infer that Alpha Centauri b is dominated by faculae, because the correlations between the RV's and the width of the CCF are strong (in particular the correlation between SN mean RV and SN FWHM is $0.817$).
 %
@@
    \caption{Correlation between the asymmetry parameters and the RVs for Alpha Centauri B.
-The last three plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN (RV mean SN and RV median SN) and the Normal fits.
+The last three plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN (SN mean RV and SN median RV) and the Normal fits.
 The correlations are always stronger when using parameters derived from the SN fit than the Normal one.}
@@
 
-Using Equation (\ref{eq:RV:correction}), we provide a new set of RV's corrected from stellar activity.
+Using Eq.
+\eqref{eq:RV:correction}, we provide a new set of RV's corrected from stellar activity.
 The results are shown in Figure ~\ref{fig:alphacent:correctionRV}.
@@
 spurious variations in RV's).
+We note also that the BIS SPAN is not helpful to address part of the spurious variability caused by stellar activity, while the opposite conclusion has reached when evaluating the p-value related to $\gamma$.
 
@@
    \caption{Set of RV's for Alpha Centauri B using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Equation (\ref{eq:RV:correction}).
+The correction is done using Eq.
+\eqref{eq:RV:correction}.
 Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
@@
 \hline
-$\beta_{0}$            &    $2.22e-16$    & $2.22e-16 $  & $2.22e-16$ \\
+$\beta_{0}$            &    $0.49$    & $0.90 $  & $0.027$ \\
 \hline
@@
 \hline
-$\beta_{2}$            &     $2.22e-16$   & $2.22e-16 $ & $2.22e-16$\\
+$\beta_{2}$            &     $0.33$   & $2.22e-16 $ & $1.23e-11$\\
 \hline
@@
 \hline
-$R^{2}$      &     $0.57$    &  $0.78$ & $0.67$  \\
+$R^{2}$      &     $0.57$    &  $0.78$ & $0.66$  \\
 \hline
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\eqref{eq:RV:correction}).
-All the parameters are useful in explaining variations in RV's of the star that can be caused by stellar activity.
+\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\eqref{eq:RV:correction}.
+Concerning the Normal fit, all the parameters but the intercept and the BIS SPAN are useful in explaining variations in RV's of the star that can be caused by stellar activity.
+For the SN fit we note that the parameter related to $\gamma$ is highly significant to address part of the spurious variations in RV's caused by stellar activity.
 The evaluation of the $R^2$ shows that the proposed linear combination better explains variations in RV's due to stellar activity coming from the SN analysis that uses SN mean RV.}
@@
 
-Both the proposed indicators coming from the SN distribution have desirable and undesirable behaviors: RV mean SN better catches changes in the asymmetry of the CCF but the resulting set of RVs ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Section \ref{intro}.
-When using RV median SN, the final set of radial velocity is less affected by those spurious shifts caused by stellar activity, but at the same time this indicator is not able to catch as well as RV mean SN changes in the shape and in the width of the CCF.
-Anyway, both RV mean SN and RV median SN are useful to catch different aspects of the CCF and our suggestion is to use RV mean SN when interested in retrieving information about changes in the shape and/or the width of the CCF.
-In order to provide a set of RVs containing the smallest amount of spurious contamination imputable to stellar activity, our suggestion is to use instead RV median SN.
+Both the proposed indicators coming from the SN distribution have advantages and limits: SN mean RV better catches changes in the asymmetry of the CCF but the resulting set of RV's ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Sec.
+\ref{intro}.
+When using SN median RV, the final set of RV's is less affected by those spurious shifts caused by stellar activity, but at the same time this indicator is not able to catch as well as SN mean RV changes in the shape and in the width of the CCF.
+Once corrected from stellar activity using Eq.~\eqref{eq:RV:correction}, the results are comparable.
+Anyway, both SN mean RV and SN median RV are useful to catch different aspects of the CCF and our suggestion is to use SN mean RV when interested in retrieving information about changes in the shape and/or the width of the CCF.
+In order to provide a set of RV's containing the smallest amount of spurious contamination imputable to stellar activity (i.e.
+before to run Eq.~\eqref{eq:RV:correction}), our suggestion is to use instead SN median RV.
 
@@
 
-In the next Section we further motivate the reasons to define the RVs derived by the CCF by calculating RV median SN.
-In order to do that, we retrieve the standard errors associated with RV mean SN, RV median SN and RV.
+In the next Section we further motivate the reasons to define the RV's derived by the CCF by calculating SN median RV.
+In order to do that, we retrieve the standard errors associated with SN mean RV, SN median RV and RV.
 
@@
 
-In this section, we perform a bootstrap analysis to measure the standard errors associated to RV mean SN, RV median SN, RV, FWHM, SN FWHM, BIS SPAN and $\gamma$.
+In this Section, we perform a bootstrap analysis to measure the standard errors associated to SN mean RV, SN median RV, RV, FWHM, SN FWHM, BIS SPAN and $\gamma$.
 Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
@@
 To bypass this problem, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF.
-We then fit a Normal or a SN to each of these CCFs and then calculate the standard deviations of the distribution for the location parameters (RV, RV mean SN or RV median SN), the width parameters (FWHM or SN FWHM) and the parameters of asymmetry (BIS SPAN or $\gamma$).
+We then fit a Normal or a SN to each of these CCFs and then calculate the standard deviations of the distribution for the location parameters (RV, SN mean RV or SN median RV), the width parameters (FWHM or SN FWHM) and the parameters of asymmetry (BIS SPAN or $\gamma$).
 \comment{It is not clear what you are doing here.
@@
 
-We start by calculating the standard errors of the parameters retrieved in Section \ref{sec:soap}, where with SOAP we produced CCFs contaminated by a faculae or a spot.
+We start by calculating the standard errors of the parameters retrieved in Sec.
+\ref{sec:soap}, where with SOAP we produced CCFs contaminated by a faculae or a spot.
 In the third and final case we considered, beyond the spot, a planetary signal that produces pure doppler shifts i the CCFs.
@@
 Fig.~\ref{fig:se.soap.faculae} shows the results of the bootstrap analysis performed when a faculae is present on the photosphere of the star.
-The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} show the different errors for the RVs, defined as RV (red triangles), RV mean SN (black circles) or RV median SN (cyan crosses), the width and the asymmetry of the CCFs.
+The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} show the different errors for the RVs, defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width and the asymmetry of the CCFs.
 In the three plots in the bottomof Fig.~\ref{fig:se.soap.faculae} we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameters derived from the bootstrap analysis fitting the Normal distribution.
-Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.5$ when using RV mean SN and $0.9$ when using RV median SN.
-By using RV median SN we get standard errors $10\%$ smaller than using the Normal fit and its corresponding mean.
+Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.5$ when using SN mean RV and $0.9$ when using SN median RV.
+By using SN median RV we get standard errors $10\%$ smaller than using the Normal fit and its corresponding mean.
 Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable.
@@
 Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
-When using RV mean SN (black circles), the standard errors are in average $50\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using RV median SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+When using SN mean RV (black circles), the standard errors are in average $50\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
 To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN.
@@
 The series of plots follows the specifications outlined for the previous case.
-Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$ when using RV mean SN and $0.9$ when using RV median SN.
+Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$ when using SN mean RV and $0.9$ when using SN median RV.
 Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable.
@@
 Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
-When using RV mean SN (black circles), the standard errors are in average $40\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using RV median SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+When using SN mean RV (black circles), the standard errors are in average $40\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
 To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN.
@@
 The conclusions are comparable to the case in which only a spot is present on the photosphere of the star.
-The ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$ when using RV mean SN and $0.9$ when using RV median SN.
+The ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$ when using SN mean RV and $0.9$ when using SN median RV.
 The errors in width of the CCF are comparable and the errors in evaluating the asymmetry of the CCF are $20\%$ smaller when using the asymmetry parameter $\gamma$ of the SN.
@@
 \subsection{Estimation of standard errors for the CCF parameters for real stars} \label{sec:bootstrap_real_star}
-In the top plots of Fig.~\ref{fig:se} we show the different errors for the RVs, either defined as RV (red triangles), RV mean SN (black circles) or RV median SN (cyan crosses), the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels.
+In the top plots of Fig.~\ref{fig:se} we show the different errors for the RVs, either defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels.
 The parameter SN50 corresponds to the SNR in order 50, which defines a wavelength of 550\,nm.
@@
 
-Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.6$ when using RV mean SN and $0.9$ when using RV median SN.
-In other words, by using RV median SN as parameter that defines the radial velocity of the star given a CCF, we get standard errors $10\%$ smaller than using the Normal fit and its corresponding mean.
-This result is consistent with what we observed with the simulation from SOAP presented in Section \ref{sec:soap}.
+Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.6$ when using SN mean RV and $0.9$ when using SN median RV.
+In other words, by using SN median RV as parameter that defines the radial velocity of the star given a CCF, we get standard errors $10\%$ smaller than using the Normal fit and its corresponding mean.
+This result is consistent with what we observed with the simulation from SOAP presented in Sec.
+\ref{sec:soap}.
 
@@
    \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
-When using RV mean SN (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using RV median SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
 To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
@@
 Therefore, the SN parameters are more sensitive to activity.
-In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of $0.322$ between $\gamma$ and RV mean SN, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.$225$.
+In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of $0.322$ between $\gamma$ and SN mean RV, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.$225$.
 
@@
 For evaluating changes in the asymmetry of the CCF, we suggest to use the mean of the SN.
-The correlations between RV mean SN and SN FWHM, and RV mean SN and $\gamma$ (the asymmetry parameter of the SN) are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
+The correlations between SN mean RV and SN FWHM, and SN mean RV and $\gamma$ (the asymmetry parameter of the SN) are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
 The precision on the asymmetry measured by $\gamma$ is greater than the one on BIS SPAN by $\sim$15\%.
@@
 The results are all consistent with the conclusions derived by the analyses on Alpha Centauri b.
-The correlation between $\gamma$ and RV mean SN is stronger than the correlation between the BIS SPAN and RV for all the considered stars.
-The correlation between SN FWHM and RV mean SN is stronger than the correlation between FWHM and RV for three of the four stars.
+The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and RV for all the considered stars.
+The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV for three of the four stars.
 The analyses of the correlations for the four stars are are presented Fig.
@@
 \hline
-\textbf{Star}          &\textbf{ \# CCFs}  &   \textbf{$\text{R}(\text{SN }\gamma, \text{Bis-Span})$} & \textbf{$\text{slope}(\text{SN }\gamma, \text{Bis-Span})$} &   \textbf{$\text{R}(\text{SN }\gamma, \text{RV mean SN})$} & \textbf{$\text{R}(\text{Bis-Span}, \text{RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{RV mean SN})$}  & \textbf{$\text{R}(\text{FWHM}, \text{RV})$} \\
+\textbf{Star}          &\textbf{ \# CCFs}  &   \textbf{$\text{R}(\text{SN }\gamma, \text{Bis-Span})$} & \textbf{$\text{slope}(\text{SN }\gamma, \text{Bis-Span})$} &   \textbf{$\text{R}(\text{SN }\gamma, \text{SN mean RV})$} & \textbf{$\text{R}(\text{Bis-Span}, \text{RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{SN mean RV})$}  & \textbf{$\text{R}(\text{FWHM}, \text{RV})$} \\
 \hline

### 2018-05-21 manuscript.tex
Add files via upload

@@
 
-In this Section, we perform a bootstrap analysis to measure the standard errors associated to SN mean RV, SN median RV, RV, FWHM, SN FWHM, BIS SPAN and $\gamma$.
+In this Section, we perform a bootstrap analysis \citep{davison1997bootstrap, efron1994introduction} in order to retrieve the standard errors associated to SN mean RV, SN median RV, RV, FWHM, SN FWHM, BIS SPAN and $\gamma$.
 Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
 Therefore, we cannot do a bootstrap analysis on perturbing independently each CCF point with a Gaussian distribution scaled to the error of each given point.
-To bypass this problem, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF.
+A detailed discussions of the methods nowadays available to resampling in situations with dependent data structures is available in \citep{lahiri2013resampling}.
+All the bootstrap methods that deal with dependant data structures rely on the so called Block Bootstrap methods, originally introduced by \citep{wilks1997resampling}.
+In our particular case, since each point in a CCF is correlated with each other, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF.
 We then fit a Normal or a SN to each of these CCFs and then calculate the standard deviations of the distribution for the location parameters (RV, SN mean RV or SN median RV), the width parameters (FWHM or SN FWHM) and the parameters of asymmetry (BIS SPAN or $\gamma$).
-\comment{It is not clear what you are doing here.
-I can understand bootstrapping a time series: you shuffle all the values keeping the time stamps fixed.
-How do you bootstrap a stellar spectrum?
-Do you shuffle the intensity values keeping the wavelengths fixed?
-That would produce a mess.
-Do you just add different levels of random noise?
-But the spectra already have noise in them, they are real observations.
-You need to state more clearly here what you did.}
 

### 2018-05-24 manuscript.tex
Add files via upload

@@
 Stellar activity can be probed by measuring variations in the shape of the cross-correlation function (CCF) as a function of time.
-Those variations are measured using the different moments of the CCF, therefore measuring with the best precision those moments is crucial to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
-
-We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, naturally provides an extra parameter to model the natural asymmetry of the CCF induced by convective blueshift.
-
-We analyze 5 stars with different activity levels and different signal-to-noise ratio (SNR) levels.
+Those variations are measured using the different moments of the CCF.
+Therefore measuring with the best precision those moments is crucial to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
+
+We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, automatically includes an extra parameter to model the natural asymmetry of the CCF induced by convective blueshift.
+
+We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (SNR) levels.
 In each case, we compare the results obtained by fitting to the CCF respectively a Normal and a SN.
@@
 
-The correlation between the RV's and the CCF asymmetry or the correlation between the RV's and the CCF width are always stronger when using the parameters derived from the SN in the case of real observations.
+The correlation between the RV's and the asymmetry of the CCF and the correlation between the RV's and the width of the CCF are always stronger when using the parameters derived from the SN in the case of real observations.
 Therefore the CCF asymmetry and the CCF width derived using a SN are more sensitive to stellar activity, which allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals.
 The precision on the estimated set of RV's, derived using the median of the fitted SN distributions are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
-In addition, the asymmetry parameter derived from the SN is on average $15\%$ better than the one calculated on the common Bisector Inverse Slope Span (BIS SPAN).
+In addition, the uncertainties related to the asymmetry parameter derived from the SN are on average $15\%$ smaller than the ones calculated on the common Bisector Inverse Slope Span (BIS SPAN).
 We strongly encourage the use of the SN distribution rather than the Normal distribution, because this allows us to retrieve in one single fit the different moments of the CCF, because the derived moments better catch stellar activity signals and finally because the standard errors on the RV's and the the asymmetry parameter are smaller than the one estimated with the Normal fit.
@@
 When working with radial velocities (RV's), the main limitation to the detection of small-mass exoplanets is not anymore the precision of the instruments used, but the different noises induced by the stars we are observing \citep[][]{Dumusque:2017aa}.
-Indeed, stellar oscillations, granulation phenomena and stellar activity all induce RV signals \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are beyond the meter-per-second precision reached by the best high-resolution spectrographs.
+Indeed, stellar oscillations, granulation phenomena and stellar activity all induce RV signals \citep{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are beyond the meter-per-second precision reached by the best high-resolution spectrographs.
 It is therefore mandatory to understand better stellar signals and to find ways to correct for them, if in the near future we want to detect or confirm an Earth-twin planet using the RV technique.
-This is even more true now that instrument like ESPRESSO \citep{Pepe-2014} and EXPRESS \citep{Fischer:2017aa} should have the stability to detect such signals.
+This is even more true now that instrument like ESPRESSO \citep{Pepe-2014} and EXPRESS \citep{fischer2016state} should have the stability to detect such signals.
 However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging.
@@
 Among the different stellar signals we are aware of, the one that is the most difficult to characterize and to correct for is the signal induced by stellar activity.
-Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, inducing spurious RV's variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b}.
-In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, that will shift the entire stellar spectrum, and stellar activity that modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}.
+Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, inducing spurious RV's variations \citep{Meunier-2010a, Dumusque-2014b}.
+In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, that will shift the entire stellar spectrum and stellar activity, that modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}.
 However, on quiet GKM dwarfs, the main target for precise RV's measurements, stellar activity induce signals of a few \ms.
@@
 
-To be able to measure such tiny variations, we average the information of all the line in the spectrum by cross correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}.
+To be able to measure such tiny variations, we average the information of all the lines in the spectrum by cross correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}.
 The result of this operation gives us the cross-correlation function (CCF).
-To measure the Doppler-shift between different spectra, and therefore get the RV's of a star as a function of time, we calculate the variations of the CCF barycenter.
-The barycenter is generally estimated by fitting a Normal distribution to the CCF, and taking its mean.
+To measure the Doppler-shift between different spectra and therefore to retrieve the RV's of a star as a function of time, we calculate the variations of the CCF barycenter.
+The barycenter is generally estimated by fitting a Normal distribution to the CCF and taking its mean.
 Variations in line shape between different spectra, which indicate the presence of signals induced by stellar activity, is measured by analysing the different moments of the CCF.
-Generally, the width of the CCF is estimated using the FWHM of the fitted Normal distribution, and its asymmetry using the the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
+Usually, the width of the CCF is estimated using the FWHM of the fitted Normal distribution, and its asymmetry using the the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
 
@@
 
-If a RV signal is induced by activity, generally a strong correlation will be observed between the RV and chromospheric activity indicators like \logrhk\,or H-$\alpha$ \citep[e.g.][]{Boisse-2009,Dumusque-2012,Robertson-2014}, but also between the RV and the FWHM of the CCF or its BIS SPAN \citep[][]{Queloz-2001,Boisse-2009,Queloz-2009,Dumusque-2016a}.
-It is therefore common now, that when fitting for a planetray signal, in addition to a Keplerian, the model includes in addition linear dependancies with the \logrhk, the FWHM and the BIS SPAN \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
+If a RV signal is induced by activity, generally a strong correlation will be observed between the RV and chromospheric activity indicators like \logrhk\,or H-$\alpha$ \citep{Boisse-2009,Dumusque-2012,Robertson-2014}, but also between the RV and the FWHM of the CCF or its BIS SPAN \citep[][]{Queloz-2001,Boisse-2009,Queloz-2009,Dumusque-2016a}.
+It is therefore common now, that when fitting for a planetray signal, in addition to a Keplerian, the model includes in addition linear dependancies with the \logrhk, the FWHM and the BIS SPAN \citep{Dumusque:2017aa,Feng:2017aa}.
 It is also common to add a Gaussian process to the model to account for the correlated noise induced by stellar activity.
-The hyperparameters of the Gaussian process are generally trained on the different activity indicators \citep[e.g.][]{Haywood-2014,Rajpaul-2015}.
+The hyperparameters of the Gaussian process are generally trained on the different activity indicators \citep{Haywood-2014,Rajpaul-2015}.
 It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated to the RV's but also for which we can obtain the best precision.
@@
 %\subsection{Why using a SN distribution?}
-In all the method described above, the RV and the FWHM are derived using a Normal distribution fitted to the CCF, and the asymmetry is estimated using another approach.
+In all the methods described above, the RV and the FWHM are derived using a Normal distribution fitted to the CCF, and the asymmetry is estimated using another approach.
 
 In this paper we propose to use a Skew Normal (SN) distribution to derive at the same time the RV, the FWHM and the asymmetry of the CCF, as this function includes a skewness parameter \citep[][]{Azzalini1985}.
-In addition, we know that for solar-type stars and cooler dwarfs, the bisector of the CCF as a "C"-shape due to convective blueshift \citep[e.g.][]{Dravins-1981, Gray-2009}.
-Therefore, fitting the CCF using a model that naturally includes an asymmetry, like the SN distribution, should give more precise results.
+In addition, we know that for solar-type stars and cooler dwarfs, the bisector of the CCF as a "C"-shape due to convective blueshift \citep{Dravins-1981, Gray-2009}.
+Therefore, fitting the CCF using a model that naturally includes an asymmetry, like the SN distribution, should give in principle more precise results.
 
@@
 In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  showing that the SN distribution is a better representation of observed CCF than a Normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
-In Sec.~\ref{sec:31} we present a simple model to correct from stellar activity which extends the ones proposed by \citet[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
+In Sec.~\ref{sec:31} we present a simple model to correct from stellar activity which extends the ones previously proposed \citep{Dumusque:2017aa,Feng:2017aa}.
 In Sec.~\ref{sec:soap} we study the SN fit to the CCF using simulations coming from SOAP 2.0.
@@
 %
-where C is an unknown offset fitting the continuum of the CCF, A is an unknown amplitude parameter and $y_1, \ldots, y_n$ are the set of RV's considered for the CCF.
+where C is an unknown offset fitting the continuum of the CCF, A is an unknown amplitude parameter known with the term ``contrast'' and $y_1, \ldots, y_n$ are the set of RV's considered for the CCF.
 Note that the CCF is expressed in flux as a function of the lag of the cross-correlation template, expressed in RV.
@@
 Being a Normal distribution symmetric, there is not such a parameter that evaluates the asymmetry of the distribution, so the BIS SPAN is used.
-The BIS SPAN will be compared to the asymmetric parameter $\gamma$ of the SN, named SN GAMMA.
+The BIS SPAN will be compared to the asymmetric parameter $\gamma$ of the SN, known also as SN GAMMA.
 To test the strength of the correlation between the estimated RV's and the different indicators used to evaluate stellar activity, we calculated the Pearson correlation coefficient, which in its general form is defined as:
@@
 where $x$ and $y$ are two quantitative variables, $cov(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represent their standard deviations.
-A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided, along with a $95\,\%$ confidence interval for $R$.
+A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided, along with a $95\%$ confidence interval for $R$ when needed.
 
@@
 
-Exoplanets will only produce a variation in RV's induced by a pure doppler shift of stellar spectra.
+Exoplanets will only produce a variation in RV's induced by a pure Doppler-shift of stellar spectra.
 Stellar activity and in particular the presence of active regions on the photosphere of the star, on the contrary, does not produce a blueshift or redshift of the spectra, but creates spurious RV's signal by modifying the shape of the spectral lines.
@@
 
-Because of the spurious variations in RV's caused by active regions, a crucial step of the entire analysis is to correct the initially estimated RV's in order to retrieve a set of RV's containing ideally only the possibly pure doppler shift coming from the exoplanets.
-In order to reach this goal, we propose to consider a linear combination of the RV's having as covariates the amplitude parameter A (also known as contrast), the BIS SPAN (or $\gamma$), the FWHM (or SN FWHM) and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM and the interaction between $\gamma$ and SN FWHM in the SN case).
-The parameters in parenthesis will be used when the SN fit is used.
+Because of the spurious variations in RV's caused by active regions, a crucial step of the entire analysis is to correct the initially estimated RV's in order to retrieve a set of RV's containing ideally only the possibly pure Doppler-shift coming from the exoplanets.
+In order to reach this goal, we propose to consider a linear combination of the RV's having as covariates the amplitude parameter A, the BIS SPAN (or $\gamma$), the FWHM (or SN FWHM) and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM and the interaction between $\gamma$ and SN FWHM in the SN case).
 We propose the following function to correct the RV's from stellar activity:
@@
 
-While the parameters BIS SPAN (or $\gamma$) and FWHM (or SN FWHM) have already been introduced and used in \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}, by using Eq.~\eqref{eq:RV:correction} we propose also to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN WHM).
+While the parameters BIS SPAN and FWHM have already been introduced and used in \citep{Dumusque:2017aa,Feng:2017aa}, by using Eq.~\eqref{eq:RV:correction} we propose also to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN WHM).
 The inclusion of the contrast parameter $A$ is justified by the expected behavior of the CCF in presence of active regions.
-Fig.~\ref{fig:spotA} shows that the presence for instance of a spot produces also changes on the amplitude of the CCF and not only on its asymmetry or width.
+Fig.~\ref{fig:spotA} shows that the presence for instance of a spot produces also changes in the amplitude of the CCF and not only on its asymmetry or width.
 %
@@
 %
+
 The reasons for including in Eq.~\eqref{eq:RV:correction} a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM) will be better justified through the results of the examples presented in Sec.\ref{sec:soap}.
@@
 In particular the effect differs at different values of the other values.
-As a consequence of this, if two variables are interacting the may or may not be associated.
-In all the analyses presented in Sec.
-\ref{sec:soap} and Sec.
-\ref{sec:4} we found weak correlations between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM) but the inclusion of the interaction term in Eq.~\eqref{eq:RV:correction} has shown nevertheless some utility in explaining spurious variations in RV's.
+%As a consequence of this, if two variables are interacting the may or may not be associated.
 
@@
 In particular we checked that the correlations between the proposed parameters were not approaching one: if it were the case, the matrix needed to calculate the estimates would have been singular, hence non invertible.
-This problem is known in statistic with the term multicollinearity and leads to unreasonable results and estimation of the standard errors associated to the parameters of interest.
-A detailed discussion of the topic can be found in the book by \citep{belsley1991conditioning}.
-In the literature there are examples of stars presenting a high correlation between the contrast parameter $A$ and the FWHM \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
+This problem is known in statistic with the term multicollinearity.
+A detailed discussion of the topic can be found in the book by \citep{belsley1991}.
+In the literature there are examples of stars presenting a high correlation between the contrast parameter $A$ and the FWHM \citep{Dumusque:2017aa,Feng:2017aa}.
 In the analyses of the presented work, we did not find any correlation between the contrast parameter $A$ and the FWHM (or between the contrast parameter $A$ and the SN FWHM) exceeding $0.66$ for all the analyzed stars and therefore the problem of multicollinearity is avoided.
@@
 Last, when proposing interactions between covariates, we found that only the one between the width and the asymmetry of the CCF is statistically helpful to explain spurious variations in RV's caused by stellar activity.
-Consequently, in the present work, the other interactions variables are not displayed.
+Consequently, in the present work, the interaction between other variables are not used as covariates.
 
@@
 \includegraphics[height = 4in]{SOAP_SPOT_Comparison_para_SN.pdf} 
-   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a spot is present on the photosphere of the star.
-In this case only the shape of the CCF changes as the spot moves, producing statistically significative correlations only between the RVs and the asymmetry parameter.}
+   \caption{Evaluation of the correlation between the RV's and the asymmetry parameters when a spot is present on the photosphere of the star.
+In this case only the shape of the CCF changes as the spot moves, producing statistically significative correlations only between the RV's and the asymmetry parameter.}
     \label{fig:spot.corr}
@@
 
-The last presented simulation example consists in having not only spurious variations in RV's caused by the presence of a spot on the photosphere of the star but also a pure doppler shift because of an artificially injected planet.
+The last presented simulation example consists in having not only spurious variations in RV's caused by the presence of a spot on the photosphere of the star but also a pure Doppler-shift because of an artificially injected planet.
 The purpose of this example is to check if we are able to disentangle the two different sources of variations in the set of RV's.
@@
 Fig.~\ref{fig:spot.plus.planet} shows the results obtained when a spot is present on the photosphere of the star and a planet is injected.
-The planet, having an amplitude of 10 \ms, produces a pure doppler shift on the CCF, without further changing its shape.
+The planet, having an amplitude of 10 \ms, produces a pure Doppler-shift on the CCF, without further changing its shape.
 In this case N mean RV seems to have the largest variations caused by the combined action of spot and planet.
@@
    \centering
-\includegraphics[height = 4in]{RV_comparison_PLANET_SPOT.pdf} 
+\includegraphics[height = 4in]{RV_comparison_SPOT_PLANET.pdf} 
 %\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
@@
 \includegraphics[height = 4in]{SOAP_SPOT_PLANET_Comparison_para_SN.pdf} 
-   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a spot is present on the photosphere of the star and a planet is injected.
+   \caption{Evaluation of the correlation between the RV's and the asymmetry parameters when a spot is present on the photosphere of the star and a planet is injected.
 In this case only the shape of the CCF changes as the spot moves, producing statistically significative correlations only between the RVs and the asymmetry parameter.
@@
 In order to correct the estimated set of RV's from spurious variations caused by the spot, we need to generalize Eq.~\eqref{eq:RV:correction}, in order to consider also the possibly presence of an exoplanet.
-Hence, rather than just using Eq.~\eqref{eq:RV:correction} we add the following keplerian function, which represents the pure doppler shift of the exoplanet under the assumption of circular orbit:
+Hence, rather than just using Eq.~\eqref{eq:RV:correction} we add the following keplerian function, which represents the pure Doppler-shift of the exoplanet under the assumption of circular orbit:
 %
@@
 %We used non linear least squares and the results are displayed in Fig.~\ref{fig:spotplanet.correction}.
-We can see how in this case we are able to disentangle the spurious variations in RV's caused by stellar activity from the pure doppler shift due to the planet.
+We can see how in this case we are able to disentangle the spurious variations in RV's caused by stellar activity from the pure Doppler-shift due to the planet.
 The statistical tests conducted on the parameters, whose results are summarized in Table \ref{table:spotplanet.test}, are significant.
@@
 %   \caption{Set of  variations in RV's estimated using a Normal and a SN fit before and once corrected from stellar activity.
-In this case there are spurious variations caused by the spot and pure doppler shift due to the planet.
+In this case there are spurious variations caused by the spot and pure Doppler-shift due to the planet.
 The correction is done using Eq.~\eqref{eq:RV:correction.overall} and the estimated parameters are presented in Table \ref{table:spotplanet.test}.
@@
 \end{table}
+
+\subsection{Conclusions on the simulation study} \label{sec:soap.conclusions}
 
@@
 \includegraphics[height = 4in]{HD12862_[2]RadialVelocityDifferences.pdf} 
-   \caption{(top) RVs as function of Julian Day for Alpha Centauri b.
+   \caption{(top) RV's as function of Julian Day for Alpha Centauri b.
 The RV's are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses).
@@
    \centering
-\includegraphics[height = 4in]{HD12862_[4]Comparison_para.pdf}  
+\includegraphics[height = 6in]{HD12862_[4]Comparison_para.pdf}  
    \caption{Correlation between the asymmetry parameters and the RVs for Alpha Centauri B.
 The last three plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN (SN mean RV and SN median RV) and the Normal fits.
-The correlations are always stronger when using parameters derived from the SN fit than the Normal one.}
+The correlations are always stronger when using parameters derived from the SN fit than the Normal one.
+The p--values associated with each $R$ is statistically different from $0$.}
    \label{fig:alphacent:corrPlot}
@@
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Doppler shift added to Alpha Centauri B} \label{sec:soap_real}
-
-We also consider a real-data example using HARPS spectra from the star Alpha Centauri B with an imputed Doppler shift added...
-
-\umberto{to be done}
-\umberto{add here correction for stellar activity: table + plot to check if we get the planet}
+\subsection{Doppler-shift added to Alpha Centauri B} \label{sec:soap_real}
+
+We also consider a real-data example using HARPS spectra from the star Alpha Centauri B with an imputed Doppler-shift added...
+
+\umberto{to be done}\xavier{to plot K vs P for Normal, SN mean, SN median}
 
@@
 \ref{sec:soap}, where with SOAP we produced CCFs contaminated by a faculae or a spot.
-In the third and final case we considered, beyond the spot, a planetary signal that produces pure doppler shifts i the CCFs.
+In the third and final case we considered, beyond the spot, a planetary signal that produces pure Doppler-shifts i the CCFs.
 
@@
 
-\umberto{Add further information about the stars here presented.}
+\umberto{Add further information about the stars here presented.}\xavier{}
 
@@
 The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV for three of the four stars.
-The analyses of the correlations for the four stars are are presented Fig.
-\ref{fig:Gliese785:corrPlot}, \ref{fig:Tau:corrPlot}, \ref{fig:HD215152:corrPlot} and \ref{fig:Corot7:corrPlot}.
+Also for all these stars we corrected the originally estimated RV's from spurious variations in RV's caused by stellar activity, using Eq.
+\eqref{eq:RV:correction}.
+Fig.
+\ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RV's.
+While the Normal and SN residuals, once corrected for stellar activity, are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$, the results of the analyses on the star $\text{HD}215152$ (whose CCF's have lower SNR respect to the previous two analyzed stars) suggest that the residuals for the Normal are $0.054 \ms$ higher than the residuals retrieved with the SN analysis.
+Finally, the results of the analysis on $\text{Corot }7$, whose CCF's have lowest SNR, show that once corrected from stellar activity the residuals from the Normal fit are $0.336 \ms$ higher than the residuals retrieved with the SN analysis.
 
@@
 }
-\caption{Subset of notable correlations between the asymmetry parameter (and the FWHM) and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.}
+\caption{Subset of notable correlations between the asymmetry parameter (and the FWHM) and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.
+The complete results of the analyses of the correlations for the four stars are presented in Fig.
+\ref{fig:Gliese785:corrPlot}--\ref{fig:Corot7:corrPlot}.}
 \label{table:summaryStars}
@@
 
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 4in]{HD19231_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RVs for HD 192310.
-The last three plots show the correlation between the FWHM and the RVs for HD 192310 using respectively the SN and the Normal fits.
-\umberto{faculae???}}
+%HD192310
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
+   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}192310$.
+The last three plots show the correlation between the FWHM and the RV's for $\text{HD}192310$ using respectively the SN and the Normal fits.
+The p--values associated with each $R$ is statistically different from $0$.}
    \label{fig:Gliese785:corrPlot}
@@
 
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 4in]{HD10700_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RVs for Tau Ceti.
-The last three plots show the correlation between the FWHM and the RVs for Tau Ceti using respectively the SN and the Normal fits.\umberto{faculae???}}
+\begin{figure} 
+   \centering
+\includegraphics[height = 6in]{NEW_CORRECTIONHD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of RV's for $\text{HD}192310$  using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.
+\eqref{eq:RV:correction}.
+Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
+   \label{fig:HD192310:correctionRV}
+\end{figure}
+
+%HD10700
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
+   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}10700$.
+The last three plots show the correlation between the FWHM and the RV's for $\text{HD}10700$ using respectively the SN and the Normal fits.
+The p--values associated with each $R$ is statistically different from $0$.}
    \label{fig:Tau:corrPlot}
@@
 
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 4in]{HD21515_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RVs for HD 215152.
-The last three plots show the correlation between the FWHM and the RVs for HD 215152 using respectively the SN and the Normal fits.\umberto{spot???}}
+\begin{figure} 
+   \centering
+\includegraphics[height = 6in]{NEW_CORRECTIONHD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of RV's for $\text{HD}10700$  using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.
+\eqref{eq:RV:correction}.
+Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
+   \label{fig:HD10700:correctionRV}
+\end{figure}
+
+%HD215152
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
+   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}215152$.
+The last three plots show the correlation between the FWHM and the RV's for $\text{HD}215152$ using respectively the SN and the Normal fits.
+Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
    \label{fig:HD215152:corrPlot}
@@
 
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 4in]{LRa01_E_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RVs for Corot-7.
-The last three plots show the correlation between the FWHM and the RVs for Corot-7 using respectively the SN and the Normal fits.\umberto{faculae???}}
+\begin{figure} 
+   \centering
+\includegraphics[height = 6in]{NEW_CORRECTIONHD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of RV's for $\text{HD}215152$ using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.
+\eqref{eq:RV:correction}.
+Once corrected for stellar activity, the residuals for the Normal are $0.054$ \ms higher than the residuals retrieved with the SN analysis.}
+   \label{fig:HD215152:correctionRV}
+\end{figure}
+
+%Corot-7
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
+   \caption{Correlation between the asymmetry parameters and the RV's for  $\text{Corot }7$.
+The last three plots show the correlation between the FWHM and the RV's for  $\text{Corot }7$ using respectively the SN and the Normal fits.
+Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
    \label{fig:Corot7:corrPlot}
 \end{figure*}
+
+\begin{figure} 
+   \centering
+\includegraphics[height = 6in]{NEW_CORRECTIONLRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of RV's for  $\text{Corot }7$ using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.
+\eqref{eq:RV:correction}.
+Once corrected for stellar activity, the residuals for the Normal are $0.336$ \ms higher than the residuals retrieved with the SN analysis.}
+   \label{fig:Corot-7:correctionRV}
+\end{figure}
 

### 2018-05-24 manuscript.tex
Add files via upload

@@
 \section{Simulation Study} \label{sec:soap}
-In order to evaluate the performance of the proposed SN approach for modeling the CCF and the goodness of the proposed correction from stellar activity by using Eq.~\eqref{eq:RV:correction}, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.
+In order to evaluate the performance of the proposed SN approach for modelling the CCF and the goodness of the proposed correction from stellar activity by using Eq.~\eqref{eq:RV:correction}, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.
 
@@
 \includegraphics[height = 4in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
-   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a faculae is present on the photosphere of the star.
-In this case both the shape and the width of the CCF changes as the faculae moves, producing statistically significative correlations between the RVs and respectively the asymmetry parameter and the width parameter.}
+   \caption{Evaluation of the correlation between the RV's and the asymmetry parameters when a faculae is present on the photosphere of the star.
+In this case both the shape and the width of the CCF changes as the faculae moves, producing statistically significative correlations between the RV's and respectively the asymmetry parameter and the width parameter.}
     \label{fig:faculae.corr}
@@
    \centering
-\includegraphics[height = 4in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+\includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
    \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity.
@@
    \centering
-\includegraphics[height = 4in]{RV_comparison_SPOT_PLANET.pdf} 
+\includegraphics[height = 6in]{RV_comparison_SPOT_PLANET.pdf} 
 %\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
@@
    \centering
-\includegraphics[height = 4in]{SOAP_SPOT_PLANET_Comparison_para_SN.pdf} 
+\includegraphics[height = 6in]{SOAP_SPOT_PLANET_Comparison_para_SN.pdf} 
    \caption{Evaluation of the correlation between the RV's and the asymmetry parameters when a spot is present on the photosphere of the star and a planet is injected.
@@
 
-In this Section, we perform a bootstrap analysis \citep{davison1997bootstrap, efron1994introduction} in order to retrieve the standard errors associated to SN mean RV, SN median RV, RV, FWHM, SN FWHM, BIS SPAN and $\gamma$.
+In this Section, we perform a bootstrap analysis \citep{davison1997bootstrap, efron1994introduction} in order to retrieve the standard errors associated to SN mean RV, SN median RV, RV, SN FWHM, FWHM, $\gamma$ and BIS SPAN.
 Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
 Therefore, we cannot do a bootstrap analysis on perturbing independently each CCF point with a Gaussian distribution scaled to the error of each given point.
-A detailed discussions of the methods nowadays available to resampling in situations with dependent data structures is available in \citep{lahiri2013resampling}.
-All the bootstrap methods that deal with dependant data structures rely on the so called Block Bootstrap methods, originally introduced by \citep{wilks1997resampling}.
+A detailed discussions of the methods nowadays available to resampling in situations with dependent data structures is available in \citet{lahiri2013resampling}.
+All the bootstrap methods that deal with dependant data structures rely on the so called Block Bootstrap methods, originally introduced by \citet{wilks1997resampling}.
 In our particular case, since each point in a CCF is correlated with each other, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF.
-We then fit a Normal or a SN to each of these CCFs and then calculate the standard deviations of the distribution for the location parameters (RV, SN mean RV or SN median RV), the width parameters (FWHM or SN FWHM) and the parameters of asymmetry (BIS SPAN or $\gamma$).
+We then fit a Normal or a SN distribution to each of these CCF's and then calculate the standard deviations of the distribution for the location parameters (RV, SN mean RV or SN median RV), the width parameters (SN FWHM or FWHM ) and the asymmetry parameters ($\gamma$ or BIS SPAN).
 
@@
 We start by calculating the standard errors of the parameters retrieved in Sec.
-\ref{sec:soap}, where with SOAP we produced CCFs contaminated by a faculae or a spot.
-In the third and final case we considered, beyond the spot, a planetary signal that produces pure Doppler-shifts i the CCFs.
+\ref{sec:soap}, where with SOAP we produced CCF's presenting spurious variations in RV's caused by a faculae or by a spot.
+In the third and final case we considered, beyond the spot, a planetary signal that produces pure Doppler-shifts in the CCF's.
 
 Fig.~\ref{fig:se.soap.faculae} shows the results of the bootstrap analysis performed when a faculae is present on the photosphere of the star.
-The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} show the different errors for the RVs, defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width and the asymmetry of the CCFs.
-In the three plots in the bottomof Fig.~\ref{fig:se.soap.faculae} we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameters derived from the bootstrap analysis fitting the Normal distribution.
-Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.5$ when using SN mean RV and $0.9$ when using SN median RV.
-By using SN median RV we get standard errors $10\%$ smaller than using the Normal fit and its corresponding mean.
+The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} shows the different errors for the RV's, defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width of the CCF, defined as FWHM (red triangles) or SN FWHM (black circles) and the asymmetry of the CCF, defined as SN GAMMA (black circles) or BIS SPAN (red triangles).
+In the series of three plots in the bottom of Fig.~\ref{fig:se.soap.faculae} we show the ratio between errors associated to the parameters derived from the bootstrap analysis fitting the SN and the errors associated to the parameters derived from the bootstrap analysis fitting the Normal distribution.
+We used the same notation also for the other two cases, where respectively a spot is present on the photosphere of the star (Fig.~\ref{fig:se.soap.spot}) and a spot and a planet are introducing both spurious and pure variations in the RV's (Fig.~\ref{fig:se.soap.spot.planet}).
+Concerning the standard errors related to the RV's if a faculae is creating spurious signals, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$, when using SN mean RV and $0.8$ when using SN median RV.
+By using SN median RV we get standard errors $20\%$ smaller than using the Normal fit and its corresponding mean.
 Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable.
@@
    \caption{Faculae Case.
-Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
-When using SN mean RV (black circles), the standard errors are in average $50\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+Comparison between the standard errors using the bootstrap analysis for the RV's, the FWHM and the asymmetry parameter.
+When using SN mean RV (black circles), the standard errors are in average $40\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using SN median RV (cyan crosses), the standard errors are in average $20\%$ smaller than the standard errors coming from the Normal fit.
 To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN.
@@
 The series of plots follows the specifications outlined for the previous case.
-Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$ when using SN mean RV and $0.9$ when using SN median RV.
+Concerning the standard errors related to the RV's, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.3$ when using SN mean RV and $0.8$ when using SN median RV.
 Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable.
@@
    \caption{Spot case.
-Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
-When using SN mean RV (black circles), the standard errors are in average $40\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+Comparison between the standard errors using the bootstrap analysis for the RV's, the FWHM and the asymmetry parameter.
+When using SN mean RV (black circles), the standard errors are in average $30\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using SN median RV (cyan crosses), the standard errors are in average $20\%$ smaller than the standard errors coming from the Normal fit.
 To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN.
@@
 The conclusions are comparable to the case in which only a spot is present on the photosphere of the star.
-The ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$ when using SN mean RV and $0.9$ when using SN median RV.
-The errors in width of the CCF are comparable and the errors in evaluating the asymmetry of the CCF are $20\%$ smaller when using the asymmetry parameter $\gamma$ of the SN.
+The ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.3$ when using SN mean RV and $0.8$ when using SN median RV.
+The errors in width of the CCF are comparable and the errors in evaluating the asymmetry of the CCF are $15\%$ smaller when using the asymmetry parameter $\gamma$ of the SN.
 
@@
 Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
-When using SN mean RV (black circles), the standard errors are in average $50\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
-To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN.
+When using SN mean RV (black circles), the standard errors are in average $30\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using SN median RV (cyan crosses), the standard errors are in average $20\%$ smaller than the standard errors coming from the Normal fit.
+To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
 Note that for the asymmetry, the error in BIS SPAN is in \kms.
@@
 An analysis of the CCF residuals after fitting a Normal or SN distribution shows that the SN is a slightly better model to explain the shape of the CCF.
-This comes from the fact that CCFs present a natural asymmetry due the convective blueshift.
-
-We tested at first our assumptions by using simulated CCFs retrieved using the software SOAP 2.0.
-We then compared for five real stars the difference between the RVs (defined as mean of a Normal, mean of the SN or median of the SN), FWHM and asymmetry (BIS SPAN in the Normal case and $\gamma$ in the SN case).
+This comes from the fact that CCF's present a natural asymmetry due the convective blueshift.
+
+We tested at first our assumptions by using simulated CCF's retrieved using the software SOAP 2.0.
+We then compared for five real stars the difference between the RV's (defined as mean of a Normal, mean of the SN or median of the SN), FWHM and asymmetry (BIS SPAN in the Normal case and $\gamma$ in the SN case).
 The $\gamma$ parameter is linearly dependent on the BIS SPAN, with always a strong correlation coefficient.
@@
 However, once the RV is defined as the median of the SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
-When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma$ in the SN case) with respect to the RVs (RVs in the Normal case or SN RVs in the SN case), we observe that the correlations are always stronger for the parameters of the SN.
+When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma$ in the SN case) with respect to the RV's (RV's in the Normal case or SN RV's in the SN case), we observe that the correlations are always stronger for the parameters of the SN.
 Therefore, the SN parameters are more sensitive to activity.
@@
 
-In this paper we introduced a novel approach based on the Skew Normal (SN) distribution for deriving RVs and shape variations in the CCF of stars.
-When searching for small-mass exoplanets using the RV technique, it is essential to understand the shape variation of the CCF, which is a proxy for stellar activity effects.
-The standard approach consist at first to adjust a Normal distribution to the CCF to get the RV and FWHM, defined as the mean and the FWHM of the Normal distribution, and then to measure the asymmetry by calculating BIS SPAN.
+In this paper we introduced a novel approach based on the Skew Normal (SN) distribution to retrieve RV's and shape variations in the CCF of stars.
+When searching for small-mass exoplanets using the RV technique, it is essential to understand variation of the shape of the CCF, which is a proxy for stellar activity effects.
+The standard approach consist at first to fit a Normal distribution to the CCF to get the RV and FWHM, defined as the mean and the FWHM of the Normal distribution, and then to measure the asymmetry of the CCF by calculating the BIS SPAN.
 FWHM and BIS SPAN give us information on the line shape that are used to probe stellar activity signals.
@@
 In this paper we propose to conduct the analysis fitting a SN distribution to the CCF.
-Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution can better catch these aspects respect the Normal fit.
-On top of that, by using the SN distribution to fit CCFs, we can measure simultaneously the RV of the star, the width and the asymmetry of the CCF.
-
-Starting from the simulation environment SOAP and then moving to real stars, we showed that using the SN distribution to fit CCFs brings a significant improvement in probing stellar activity.
+Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution can in principle better catch these aspects respect the Normal fit.
+On top of that, by using the SN distribution to fit CCF's, we can measure simultaneously the RV of the star, the width and the asymmetry of the CCF.
+
+Starting from the simulation environment SOAP and then moving to real stars, we showed that using the SN distribution to fit CCF's leads to a significant improvement to probing stellar activity.
 While for the Normal distribution mean and median are equivalent, using the SN fit different location parameters can be tested.
-While the median of the SN is more robust respect variations in the shape of the CCF, the mean of the SN is more sensible to changes in the asymmetry of the CCF.
-We suggest to use as parameter that defines the RV of the star the median of the SN, since the standard errors related to this parameter are $10\%$ smaller than the standard errors retrieved using the Normal distribution.
-For evaluating changes in the asymmetry of the CCF, we suggest to use the mean of the SN.
-The correlations between SN mean RV and SN FWHM, and SN mean RV and $\gamma$ (the asymmetry parameter of the SN) are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
+While the median of the SN is a more robust statistic respect variations in the shape of the CCF, the mean of the SN is more sensible to changes in the asymmetry of the CCF.
+We suggest to use as parameter that defines the RV of the star the median of the SN, since the standard errors related to this parameter working with CCF's from real stars are on average $10\%$ smaller than the standard errors retrieved using the Normal distribution.
+To evaluate changes in the asymmetry of the CCF, we suggest to use the mean of the SN.
+The correlation between SN mean RV and SN FWHM and the correlation between SN mean RV and $\gamma$ (the asymmetry parameter of the SN) are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
 The precision on the asymmetry measured by $\gamma$ is greater than the one on BIS SPAN by $\sim$15\%.
@@
 
+Because of stellar activity the estimated RV's are contaminated by spurious variations.
+We propose to use a function that corrects from stellar activity that beyond the width and the asymmetry parameters of the CCF includes also the contrast parameter A and the fourth parameter defined as the interaction between width and the asymmetry parameters of the CCF.
+We found these new two parameter helpful to explain part of the spurious variations in RV's caused by stellar activity.
+
 Finally, we also encourage the use of bootstrapping to estimate more realistic errors on the different parameters of the Normal or SN fitted to the CCF, mainly in the low SNR regime where a gain of 50\% can be reached.
-This takes significantly more time, but note that 100 realization are enough to get a good estimation of errors.
+This takes significantly more time, but note that 100 bootstrapped dataset are enough to get a good estimation of errors.
 

### 2018-05-24 manuscript.tex
Add files via upload

@@
    \centering
-\includegraphics[height = 4in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
+\includegraphics[height = 2.5in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
    \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF (also known as contrast) and not only on its asymmetry or width.
@@
    \centering
-\includegraphics[height = 4in]{RV_comparison_FACULAE.pdf} 
+\includegraphics[height = 2.5in]{RV_comparison_FACULAE.pdf} 
 %\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
@@
    \centering
-\includegraphics[height = 4in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
+\includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
    \caption{Evaluation of the correlation between the RV's and the asymmetry parameters when a faculae is present on the photosphere of the star.
@@
    \centering
-\includegraphics[height = 4in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
    \caption{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity.
@@
    \centering
-\includegraphics[height = 4in]{RV_comparison_SPOT.pdf} 
+\includegraphics[height = 2.5in]{RV_comparison_SPOT.pdf} 
 %\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
@@
    \centering
-\includegraphics[height = 4in]{SOAP_SPOT_Comparison_para_SN.pdf} 
+\includegraphics[height = 6in]{SOAP_SPOT_Comparison_para_SN.pdf} 
    \caption{Evaluation of the correlation between the RV's and the asymmetry parameters when a spot is present on the photosphere of the star.
@@
    \centering
-\includegraphics[height = 6in]{RV_comparison_SPOT_PLANET.pdf} 
+\includegraphics[height = 2.5in]{RV_comparison_SPOT_PLANET.pdf} 
 %\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
@@
    \centering
-\includegraphics[height = 4in]{HD12862_[2]gamma_vs_bisspan.pdf} 
+\includegraphics[height = 6in]{HD12862_[2]gamma_vs_bisspan.pdf} 
    \caption{Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
@@
    \centering
-\includegraphics[height = 4in]{HD12862_[2]RadialVelocityDifferences.pdf} 
+\includegraphics[height = 6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
    \caption{(top) RV's as function of Julian Day for Alpha Centauri b.
@@
    \centering
-\includegraphics[height = 4in]{RV_comparison_FACULAE_standard_errors.pdf} 
+\includegraphics[height = 6in]{RV_comparison_FACULAE_standard_errors.pdf} 
    \caption{Faculae Case.
@@
    \centering
-\includegraphics[height = 4in]{RV_comparison_SPOT_standard_errors.pdf} 
+\includegraphics[height = 6in]{RV_comparison_SPOT_standard_errors.pdf} 
    \caption{Spot case.
@@
    \centering
-\includegraphics[height = 4in]{RV_comparison_SPOT_PLANET_standard_errors.pdf} 
+\includegraphics[height = 6in]{RV_comparison_SPOT_PLANET_standard_errors.pdf} 
    \caption{Spot and Planet case.
@@
    \centering
-\includegraphics[height = 4in]{[5]Errors_vs_SNR_all_stars.pdf} 
+\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
    \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.

### 2018-05-24 manuscript.tex
Modif Sect 2 and 3
Rephrasing of Section 2 and 3

--- 2018-05-24 manuscript.tex
@@
 The Skew Normal (SN) distribution is a class of probability distributions which includes the Normal distribution as a special case \citep{Azzalini1985}.
-The SN distribution has, in addition to a location and a scale parameter analogous to the Normal distribution's mean and standard deviation, a third parameter which describes the asymmetry, or the skewness, of the distribution.
-Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $Y = y$ can be written as
+The SN distribution has, in addition to a location and a scale parameter analogous to the Normal distribution's mean and standard deviation, a third parameter which describes the skewness of the distribution.
+Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $y\in Y$ can be written as
 \begin{equation} \label{def:snd_gen}
@@
 \end{equation}
-where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a \emph{standard} Normal distribution\footnote{A standard Normal distribution is a Normal distribution with a mean of 0 and a standard deviation of 1.}
- and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN.
-We then write $Y \sim SN(\xi, \omega^{2}, \alpha)$ to mean that the random variable $Y$ follows the noted SN distribution.
+where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution\footnote{A standard Normal distribution is a Normal distribution with a mean of 0 and a standard deviation of 1.}.
+The skewness parameter $\alpha$ quantifies the asymmetry of the SN. 
 Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Fig.~\ref{fig:SN.plot}.
-A usual Normal distribution is the special case of the SN distribution when the skewness parameter, $\alpha$, is equal to 0.\footnote{This can be seen from Eq.~\eqref{def:snd_gen}.
-If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0)$; this is the the probability a standard Normal random variable is less than or equal to 0, which is $0.5$.
-The $0.5$ cancels with the $2$ in the denominator and what remains is the usual Normal density, $\frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$}
+A usual Normal distribution is the special case of the SN distribution when the skewness parameter $\alpha$ is equal to zero\footnote{This can be seen from Eq.~\ref{def:snd_gen}.
+If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0) = 0.5$ and therefore $SN(y;\xi, \omega, 0) = \frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$ which is the density or a Normal distribution.
+Note that $\Phi(0) = 0.5$ because $\Phi(0)$ is the the probability that a standard Normal random variable is less than or equal than 0.}.
 %
@@
 \includegraphics[height = 3in]{Skew_Normal_densities_jjck.pdf} 
-   \caption{Density function of a random variable $Y \sim SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
+   \caption{Density function of a random variable Y following the SN distribution $SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
 Note that the solid black line has an $\alpha = 0$, making it a Normal distribution.}
@@
 %
-For reasons related to the interpretation of the parameters in Eq.~\eqref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used, which is referred to as the \emph{centered parametrization} (CP).
-We will be using the CP in this work, which includes a mean parameter $\mu$, a variance parameter $\sigma^2$ and a skewness parameter $\gamma$.
-In order to define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of the one used in the Equation~\eqref{def:snd_gen} with $(\xi, \omega^2, \alpha)$ by
+For reasons related to the interpretation of the parameters in Eq.~\ref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used in this work, which is referred to as the \emph{centered parametrization} (CP).
+This CP is much closer to the parametrization of a Normal distribution, as it uses a mean parameter $\mu$, a variance parameter $\sigma^2$ and a skewness parameter $\gamma$.
+In order to define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of $(\xi, \omega^2, \alpha)$.
+This can be done using the following relations:
 %
@@
 %
-where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$.
-
-By using Eq.~\eqref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution.
+where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$ \citep[e.g.][]{Arellano-2010}.
+
+By using Eq.~\ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution.
 For the $\alpha$ values used in Fig.~\ref{fig:SN.plot}, the corresponding values of ($\mu$, $\sigma^2$, $\gamma$) are displayed in Table~\ref{tab:cp_values}.
-In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution (rather than simply a location and scale parameter) and $\gamma$ becomes an index for evaluating the skewness of the SN.
+In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution, rather than simply a location and scale parameter, and $\gamma$ becomes an variable that evaluate the skewness of the SN.
 
 Beyond the mean of the SN, we introduce a second location parameter that will be largely used in the analyses: the median.
-The median of the SN, and in general the median of an absolute continuous random variable, is defined as that value $m$ such that
+The median of the SN, and in general the median of an absolute continuous random variable, is defined as the value $m$ such that\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}:
 %
 \begin{equation} \label{eq:snmed}
-\int_{-\infty}^{m} SN(y;\xi, \omega, \alpha) = \frac{1}{2},
+\int_{-\infty}^{m} SN(y;\xi, \omega, \alpha) = \frac{1}{2}.
 \end{equation}
 %
-where $SN(y;\xi, \omega, \alpha)$ follows Eq.~\eqref{def:snd_gen}.\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}
 
@@
    \end{tabular}
-   \caption{CP values, $(\mu, \sigma^2, \gamma)$, corresponding to the $\alpha$ values from Fig.~\ref{fig:SN.plot} (with location parameter $\xi = 0$ and scale parameter $\omega = 1$) using Eq.~\eqref{eq:snd_cp}.
+   \caption{CP values $(\mu, \sigma^2, \gamma)$ corresponding to the $\alpha$ values shown in Fig.~\ref{fig:SN.plot}, with location parameter $\xi = 0$ and scale parameter $\omega = 1$.
 Values are rounded to three decimal places.}
@@
 %
-Further details about the parametrization from Eq.~\eqref{def:snd_gen} (called \emph{Direct Parametrization} or DP), the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
+Further details about the parametrization from Eq.~\ref{def:snd_gen}, called \emph{Direct Parametrization} or DP, the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
 
@@
 %The CCF represents the average shape of spectral lines and is expressed in flux as a function of radial-velocity.
-The SN density shape is used to model the CCF.  In particular, using least-squares algorithm, we fit the following function:
+To fit the CCF using a SN distribution, we use a least-squares algorithm and the following model:
 %
@@
 %
-where C is an unknown offset fitting the continuum of the CCF, A is an unknown amplitude parameter known with the term ``contrast'' and $y_1, \ldots, y_n$ are the set of RV's considered for the CCF.
-Note that the CCF is expressed in flux as a function of the lag of the cross-correlation template, expressed in RV.
-
-Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution should in principle better catch this aspect, together with other changes in asymmetry, respect the Normal fit.
+where C is an unknown offset fitting for the continuum of the CCF, A is the unknown contrast of the CCF and $\mu$, $\sigma^2$ and $\gamma$ are the mean, variance and skewness of the SN as defined is Sect.
+\ref{sec:2}.
+The values $y_1, \ldots, y_n$ are the different values of the abscisse of the CCF, generally with the dimension of a velocity.
+
+Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution should in principle better catch this aspect, together with other changes in asymmetry, with respect to fitting a Normal distribution.
 To initially check this intuition, we compared the CCF residuals after fitting a Normal and a SN distribution for 2 stars.
@@
 The second star is Corot-7, whose CCF's have low SNR.
-Fig.~\ref{fig:Residual.comparison} shows that the SN seems to be a slightly better model to explain the shape of the CCF, in particular as the SNR decreases.
+Fig.~\ref{fig:Residual.comparison} shows that the SN seems to be a slightly better model to explain the shape of the CCF.%, in particular as the SNR decreases.
 %
@@
    \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCF's from the star Alpha Centauri b (left) and Corot-7 (right).
-When looking at the residuals corresponding to the tails of the CCF, the results derived by the two fits are comparable.
-However, when focusing on the center of the CCF, the SN fit leads to slightly better results for both the stars.
-Moreover, as the SNR decreases, the SN distribution shows smaller residuals respect the Normal ones.}
+When looking at the residuals corresponding to the center of the CCF, the SN fit leads to slightly better results for both stars.} %Moreover, as the SNR decreases, the SN distribution shows smaller residuals respect the Normal ones.}
     \label{fig:Residual.comparison}
@@
 
-In the following of the paper, we define RV as the mean of the Normal distribution.
-Concerning the fit of the CCF using the SN, we present at first $2$ indicators that define the RV of the star: the mean of the SN, defined as SN mean RV and the median of the SN, defined as SN median RV (i.e.
-realling Eq.\eqref{eq:snmed}, $m$ = SN median RV).
-We will discuss advantages and limits for both these choices in Sec.
+When fitting a Normal distribution to the CCF, the mean of the fitted distribution is defined as the measured RV, the FWHM of the Normal distribution ($=2\sqrt(2\ln2)\sigma$) represents the width of the CCF and because the Normal distribution is symmetric, a  skewness parameter cannot be obtained directly from this fit.
+Such a parameter is generally obtain in a second step by calculating the BIS SPAN of the CCF \citep[see Sect.
+\ref{intro}, and e.g.][]{Queloz-2001}.
+When fitting a SN distribution, we define two indicators for the RV: the mean of the SN, defined as SN mean RV and the median of the SN, defined as SN median RV.
+We will discuss advantages and limits for both of these choices in Sec.
 \ref{sec:4} and Sec.
 \ref{sec:5}.
-For the width of the CCF, we use the FWHM of the Normal, which is $2\sqrt(2\ln2)\sigma$.
-The width of the SN, SN FWHM, is defined in the same way\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}.
-Being a Normal distribution symmetric, there is not such a parameter that evaluates the asymmetry of the distribution, so the BIS SPAN is used.
-The BIS SPAN will be compared to the asymmetric parameter $\gamma$ of the SN, known also as SN GAMMA.
+We define the width of the SN, SN FWHM, in the same way as for the Normal distribution\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}, and finally the skewness of the CCF, SN GAMMA, is derived using the $\gamma$ parameter.
+
 To test the strength of the correlation between the estimated RV's and the different indicators used to evaluate stellar activity, we calculated the Pearson correlation coefficient, which in its general form is defined as:
@@
 
-While the parameters BIS SPAN and FWHM have already been introduced and used in \citep{Dumusque:2017aa,Feng:2017aa}, by using Eq.~\eqref{eq:RV:correction} we propose also to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN WHM).
+While the parameters BIS SPAN and FWHM have already been introduced and used in \citep{Dumusque:2017aa,Feng:2017aa}, by using Eq.~\ref{eq:RV:correction} we propose also to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN WHM).
 The inclusion of the contrast parameter $A$ is justified by the expected behavior of the CCF in presence of active regions.
@@
 
-The reasons for including in Eq.~\eqref{eq:RV:correction} a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM) will be better justified through the results of the examples presented in Sec.\ref{sec:soap}.
+The reasons for including in Eq.~\ref{eq:RV:correction} a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM) will be better justified through the results of the examples presented in Sec.\ref{sec:soap}.
 We point out however that while the association between in this case BIS SPAN  (or $\gamma$) and FWHM (or SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant.
@@
 As final remark we recall that, when working with a linear regression, there are several ways to select the variables to include in the model.
-While usually the stepwise technique takes place \citep{efroymson1960multiple,hocking1976biometrics}, the proposed function defined in Eq.~\eqref{eq:RV:correction} that corrects from stellar activity is the result of statistical and astronomical considerations.
+While usually the stepwise technique takes place \citep{efroymson1960multiple,hocking1976biometrics}, the proposed function defined in Eq.~\ref{eq:RV:correction} that corrects from stellar activity is the result of statistical and astronomical considerations.
 In particular we checked that the correlations between the proposed parameters were not approaching one: if it were the case, the matrix needed to calculate the estimates would have been singular, hence non invertible.
@@
 In the analyses of the presented work, we did not find any correlation between the contrast parameter $A$ and the FWHM (or between the contrast parameter $A$ and the SN FWHM) exceeding $0.66$ for all the analyzed stars and therefore the problem of multicollinearity is avoided.
-For the interpretation of the coefficients, we centered on the mean all the variables considered in the linear regression defined in Eq.~\eqref{eq:RV:correction}.
+For the interpretation of the coefficients, we centered on the mean all the variables considered in the linear regression defined in Eq.~\ref{eq:RV:correction}.
 Last, when proposing interactions between covariates, we found that only the one between the width and the asymmetry of the CCF is statistically helpful to explain spurious variations in RV's caused by stellar activity.
@@
 \section{Simulation Study} \label{sec:soap}
-In order to evaluate the performance of the proposed SN approach for modeling the CCF and the goodness of the proposed correction from stellar activity by using Eq.~\eqref{eq:RV:correction}, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.
+In order to evaluate the performance of the proposed SN approach for modeling the CCF and the goodness of the proposed correction from stellar activity by using Eq.~\ref{eq:RV:correction}, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.
 
@@
 
-Since all the variations in RV's displayed in Fig.~\ref{fig:faculae} are caused by the presence of a faculae on the photosphere of the star, we corrected the originally estimated set of RV's by using Eq.~\eqref{eq:RV:correction}.
-The results of the correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the parameters involved in Eq.~\eqref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
+Since all the variations in RV's displayed in Fig.~\ref{fig:faculae} are caused by the presence of a faculae on the photosphere of the star, we corrected the originally estimated set of RV's by using Eq.~\ref{eq:RV:correction}.
+The results of the correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the parameters involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
 It is straightforward noticing that the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the faculae.
@@
    \caption{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.~\eqref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
+The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
 Once corrected for stellar activity the residuals do not show a systematic component.}
@@
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a faculae, according to Eq.~\eqref{eq:RV:correction}.
+\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a faculae, according to Eq.~\ref{eq:RV:correction}.
 Beyond the contrast parameter A and the asymmetry parameter of the CCF which are useful for both the analyses, the width of the CCF is statistically useful to explain spurious variations in RV's caused by a faculae only for the SN analyses.
@@
 
-As before, we corrected the originally estimated set of RV's by using Eq.~\eqref{eq:RV:correction}.
-The results of the correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the parameters involved in Eq.~\eqref{eq:RV:correction} are summarized in Table \ref{table:spot.test}.
+As before, we corrected the originally estimated set of RV's by using Eq.~\ref{eq:RV:correction}.
+The results of the correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the parameters involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:spot.test}.
 Also in this case the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the spot.
@@
    \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.~\eqref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
+The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
 Once corrected for stellar activity the residuals do not show a systematic component.}
@@
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\eqref{eq:RV:correction}.
+\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\ref{eq:RV:correction}.
 All the covariates are statistically useful to explain the variability in RV's causued by a spot except the intercept and the width of the CCF.
@@
 
-In order to correct the estimated set of RV's from spurious variations caused by the spot, we need to generalize Eq.~\eqref{eq:RV:correction}, in order to consider also the possibly presence of an exoplanet.
-Hence, rather than just using Eq.~\eqref{eq:RV:correction} we add the following keplerian function, which represents the pure Doppler-shift of the exoplanet under the assumption of circular orbit:
+In order to correct the estimated set of RV's from spurious variations caused by the spot, we need to generalize Eq.~\ref{eq:RV:correction}, in order to consider also the possibly presence of an exoplanet.
+Hence, rather than just using Eq.~\ref{eq:RV:correction} we add the following keplerian function, which represents the pure Doppler-shift of the exoplanet under the assumption of circular orbit:
 %
@@
 We note that the p--value associated with the amplitude parameter $K$ is particularly relevant for rejecting or not rejecting the assumption about the presence of an orbiting companion.
-Moreover we note also that Eq.~\eqref{eq:RV:correction.planet} is highly non linear, meaning that the estimation of all the parameters involved in Eq.~\eqref{eq:RV:correction.overall} has to be done numerically.
+Moreover we note also that Eq.~\ref{eq:RV:correction.planet} is highly non linear, meaning that the estimation of all the parameters involved in Eq.~\ref{eq:RV:correction.overall} has to be done numerically.
 %We used non linear least squares and the results are displayed in Fig.~\ref{fig:spotplanet.correction}.
@@
 In this case there are spurious variations caused by the spot and pure Doppler-shift due to the planet.
-The correction is done using Eq.~\eqref{eq:RV:correction.overall} and the estimated parameters are presented in Table \ref{table:spotplanet.test}.
-In this case, by solving Eq.~\eqref{eq:RV:correction.overall}, we are able to completely disentangle the spurious variations in RV's caused by the presence of the spot from the pure dopplershift caused by the exoplanet.}
+The correction is done using Eq.~\ref{eq:RV:correction.overall} and the estimated parameters are presented in Table \ref{table:spotplanet.test}.
+In this case, by solving Eq.~\ref{eq:RV:correction.overall}, we are able to completely disentangle the spurious variations in RV's caused by the presence of the spot from the pure dopplershift caused by the exoplanet.}
 %    \label{fig:spotplanet.correction}
@@
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\eqref{eq:RV:correction.overall}.
+\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\ref{eq:RV:correction.overall}.
 All the parameters are statistically helpful to address spurious variations in RV's except the FWHM.
@@
 Using Eq.
-\eqref{eq:RV:correction}, we provide a new set of RV's corrected from stellar activity.
+\ref{eq:RV:correction}, we provide a new set of RV's corrected from stellar activity.
 The results are shown in Figure ~\ref{fig:alphacent:correctionRV}.
@@
 The correction is done using Eq.
-\eqref{eq:RV:correction}.
+\ref{eq:RV:correction}.
 Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
@@
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\eqref{eq:RV:correction}.
+\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\ref{eq:RV:correction}.
 Concerning the Normal fit, all the parameters but the intercept and the BIS SPAN are useful in explaining variations in RV's of the star that can be caused by stellar activity.
@@
 When using SN median RV, the final set of RV's is less affected by those spurious shifts caused by stellar activity, but at the same time this indicator is not able to catch as well as SN mean RV changes in the shape and in the width of the CCF.
-Once corrected from stellar activity using Eq.~\eqref{eq:RV:correction}, the results are comparable.
+Once corrected from stellar activity using Eq.~\ref{eq:RV:correction}, the results are comparable.
 Anyway, both SN mean RV and SN median RV are useful to catch different aspects of the CCF and our suggestion is to use SN mean RV when interested in retrieving information about changes in the shape and/or the width of the CCF.
 In order to provide a set of RV's containing the smallest amount of spurious contamination imputable to stellar activity (i.e.
-before to run Eq.~\eqref{eq:RV:correction}), our suggestion is to use instead SN median RV.
+before to run Eq.~\ref{eq:RV:correction}), our suggestion is to use instead SN median RV.
 
@@
 Also for all these stars we corrected the originally estimated RV's from spurious variations in RV's caused by stellar activity, using Eq.
-\eqref{eq:RV:correction}.
+\ref{eq:RV:correction}.
 Fig.
@@
 The correction is done using Eq.
-\eqref{eq:RV:correction}.
+\ref{eq:RV:correction}.
 Once corrected for stellar activity, the residuals for the Normal are $0.054$ \ms higher than the residuals retrieved with the SN analysis.}
@@
 The correction is done using Eq.
-\eqref{eq:RV:correction}.
+\ref{eq:RV:correction}.
 Once corrected for stellar activity, the residuals for the Normal are $0.336$ \ms higher than the residuals retrieved with the SN analysis.}

### 2018-05-24 manuscript.tex
resolved conflicts

@@
 \section{Simulation Study} \label{sec:soap}
-In order to evaluate the performance of the proposed SN approach for modeling the CCF and the goodness of the proposed correction from stellar activity by using Eq.~\ref{eq:RV:correction}, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.
+In order to evaluate the performance of the proposed SN approach for modelling the CCF and the goodness of the proposed correction from stellar activity by using Eq.~\eqref{eq:RV:correction}, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.
 
@@
    \centering
-\includegraphics[height = 4in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
-   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a faculae is present on the photosphere of the star.
-In this case both the shape and the width of the CCF changes as the faculae moves, producing statistically significative correlations between the RVs and respectively the asymmetry parameter and the width parameter.}
+\includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
+   \caption{Evaluation of the correlation between the RV's and the asymmetry parameters when a faculae is present on the photosphere of the star.
+In this case both the shape and the width of the CCF changes as the faculae moves, producing statistically significative correlations between the RV's and respectively the asymmetry parameter and the width parameter.}
     \label{fig:faculae.corr}
@@
    \centering
-\includegraphics[height = 4in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
    \caption{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
+The correction is done using Eq.~\eqref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
 Once corrected for stellar activity the residuals do not show a systematic component.}
@@
    \centering
-\includegraphics[height = 4in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+\includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
    \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
+The correction is done using Eq.~\eqref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
 Once corrected for stellar activity the residuals do not show a systematic component.}
@@
    \centering
-\includegraphics[height = 4in]{RV_comparison_SPOT_PLANET.pdf} 
+\includegraphics[height = 2.5in]{RV_comparison_SPOT_PLANET.pdf} 
 %\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
@@
    \centering
-\includegraphics[height = 4in]{RV_comparison_FACULAE_standard_errors.pdf} 
+\includegraphics[height = 6in]{RV_comparison_FACULAE_standard_errors.pdf} 
    \caption{Faculae Case.
-Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
-When using SN mean RV (black circles), the standard errors are in average $50\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+Comparison between the standard errors using the bootstrap analysis for the RV's, the FWHM and the asymmetry parameter.
+When using SN mean RV (black circles), the standard errors are in average $40\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using SN median RV (cyan crosses), the standard errors are in average $20\%$ smaller than the standard errors coming from the Normal fit.
 To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN.
@@
    \centering
-\includegraphics[height = 4in]{RV_comparison_SPOT_standard_errors.pdf} 
+\includegraphics[height = 6in]{RV_comparison_SPOT_standard_errors.pdf} 
    \caption{Spot case.
-Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
-When using SN mean RV (black circles), the standard errors are in average $40\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+Comparison between the standard errors using the bootstrap analysis for the RV's, the FWHM and the asymmetry parameter.
+When using SN mean RV (black circles), the standard errors are in average $30\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using SN median RV (cyan crosses), the standard errors are in average $20\%$ smaller than the standard errors coming from the Normal fit.
 To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN.
@@
 The conclusions are comparable to the case in which only a spot is present on the photosphere of the star.
-The ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$ when using SN mean RV and $0.9$ when using SN median RV.
-The errors in width of the CCF are comparable and the errors in evaluating the asymmetry of the CCF are $20\%$ smaller when using the asymmetry parameter $\gamma$ of the SN.
-
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 4in]{RV_comparison_SPOT_PLANET_standard_errors.pdf} 
+The ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.3$ when using SN mean RV and $0.8$ when using SN median RV.
+The errors in width of the CCF are comparable and the errors in evaluating the asymmetry of the CCF are $15\%$ smaller when using the asymmetry parameter $\gamma$ of the SN.
+
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 6in]{RV_comparison_SPOT_PLANET_standard_errors.pdf} 
    \caption{Spot and Planet case.
 Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
-When using SN mean RV (black circles), the standard errors are in average $50\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
-To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN.
+When using SN mean RV (black circles), the standard errors are in average $30\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using SN median RV (cyan crosses), the standard errors are in average $20\%$ smaller than the standard errors coming from the Normal fit.
+To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
 Note that for the asymmetry, the error in BIS SPAN is in \kms.

### 2018-05-24 manuscript.tex
small text modif

@@
 While the parameters BIS SPAN and FWHM have already been introduced and used in \citep{Dumusque:2017aa,Feng:2017aa}, by using Eq.~\ref{eq:RV:correction} we propose also to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN WHM).
-The inclusion of the contrast parameter $A$ is justified by the expected behavior of the CCF in presence of active regions.
-Fig.~\ref{fig:spotA} shows that the presence for instance of a spot produces also changes in the amplitude of the CCF and not only on its asymmetry or width.
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 2.5in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
-   \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF (also known as contrast) and not only on its asymmetry or width.
+The inclusion of the contrast parameter $A$ is justified by the fact that the presence for instance of a spot produces also changes in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g.
+Fig.
+2 in ][]{Dumusque-2014b}.
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 2.5in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
+%   \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF (also known as contrast) and not only on its asymmetry or width.
 This very same plot has been originally presented by \citep{Dumusque-2014b} when introducing the Spot Oscillation And Planet (SOAP) 2.0 simulator.}
-    \label{fig:spotA}
-\end{figure*}
-%
+%    \label{fig:spotA}
+%\end{figure*}
+%%
 
@@
 The level for not rejecting the null hypothesis is fixed equal to $0.05$.
-The coefficient of multiple correlation $R^2$ is introduced in order to explain how well this linear combination addresses the variability of the RV's of the star as caused by stellar activity.
+The coefficient of multiple correlation $R^2$ is introduced in order to explain how well this linear combination addresses the variability of the RV variation induced by stellar activity.
 
@@
 \section{Simulation Study} \label{sec:soap}
-In order to evaluate the performance of the proposed SN approach for modelling the CCF and the goodness of the proposed correction from stellar activity by using Eq.~\eqref{eq:RV:correction}, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.
+In order to evaluate the performance of the proposed SN approach for modelling the CCF and the benefit of using the proposed correction for stellar activity (See Eq.~\ref{eq:RV:correction}), we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.
 

### 2018-05-25 manuscript.tex
updated abstract

@@
 % Context, Aims, Methods, Results, Conclu (not mandatory)
-Stellar activity is the main limitation to the detection of small-mass exoplanets using the radial-velocity (RV) technique.
-Stellar activity can be probed by measuring variations in the shape of the cross-correlation function (CCF) as a function of time.
-Those variations are measured using the different moments of the CCF.
-Therefore measuring with the best precision those moments is crucial to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
-
-We propose here to measure those moments using a Skew Normal (SN) distribution, which compared to the Normal distribution generally used, automatically includes an extra parameter to model the natural asymmetry of the CCF induced by convective blueshift.
-
-We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (SNR) levels.
+Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
+Stellar activity can be probed by measuring variations in the shape of the cross-correlation function (CCF) as a function of time often using different moments of a modeled CCF.
+Therefore estimating the moments of the CCF with high precision is essential to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
+%
+We propose to estimate the moments of the CCF by first fitting a model using a Skew Normal (SN) density shape, which unlike the commonly employed Normal density,  includes an asymmetry parameter to capture the natural asymmetry of the CCF induced by convective blueshift.
+\jessi{is convective blueshift the only asymmetry-inducing variable of the CCF?}
+%
+The performance of the proposed method is compared to the Normal density using both simulated and real observations with varying levels of activity and signal-to-noise ratio (SNR) levels.
+%We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (SNR) levels.
 In each case, we compare the results obtained by fitting to the CCF respectively a Normal and a SN.
 We also estimate rigorous errors for the different moments of the CCF using a bootstrap analysis.
-
-The correlation between the RV's and the asymmetry of the CCF and the correlation between the RV's and the width of the CCF are always stronger when using the parameters derived from the SN in the case of real observations.
+%
+When considering the real observations, the correlation between the RV's and the asymmetry of the CCF and the correlation between the RV's and the width of the CCF are stronger when using the parameters derived from the SN than the Normal approach.
+This suggests that the CCF asymmetry and the CCF width derived using a SN may be more sensitive to stellar activity, which can be helpful with estimating stellar rotational periods and generally characterizing the stellar activity signals.
+%
+The estimated uncertainties in the estimated RV's using the proposed SN approach are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal, and the estimated uncertainties on the SN asymmetry parameter are on average $15\%$ smaller than the commonly used Bisector Inverse Slope Span (BIS SPAN) approach for estimating the asymmetry of the CCF.
+%
+The derived benefits of using the proposed SN approach includes an asymmetry parameter along with several options for estimating the RV, while the Normal model only includes an RV estimate and requires a separate procedure for estimating the asymmetry.
+Furthermore, the estimated uncertainties on the RV's and the asymmetry parameter are smaller in the SN setting.
+%The correlation between the RV's and the asymmetry of the CCF and the correlation between the RV's and the width of the CCF are always stronger when using the parameters derived from the SN in the case of real observations.
 Therefore the CCF asymmetry and the CCF width derived using a SN are more sensitive to stellar activity, which allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals.

### 2018-05-25 manuscript.tex
updated section 1

@@
 
-When working with radial velocities (RV's), the main limitation to the detection of small-mass exoplanets is not anymore the precision of the instruments used, but the different noises induced by the stars we are observing \citep[][]{Dumusque:2017aa}.
-Indeed, stellar oscillations, granulation phenomena and stellar activity all induce RV signals \citep{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are beyond the meter-per-second precision reached by the best high-resolution spectrographs.
-It is therefore mandatory to understand better stellar signals and to find ways to correct for them, if in the near future we want to detect or confirm an Earth-twin planet using the RV technique.
-This is even more true now that instrument like ESPRESSO \citep{Pepe-2014} and EXPRESS \citep{fischer2016state} should have the stability to detect such signals.
-However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging.
+When working with radial velocities (RV's), one of the main limitations to the detection of small-mass exoplanets is no longer the precision of the instruments used, but the different sources of variability induced by the stars \citep[][]{Dumusque:2017aa} \jessi{We should add more citations here to new spectrographs...maybe EXPRES?}.
+Stellar oscillations, granulation phenomena, and stellar activity can all induce apparent RV signals \citep{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are beyond \jessi{what is meant by the word ``beyond'' here?
+Do you mean below the limit or above?
+I think you mean above since they can induce singles that are greater than 1m/s, but we need to unambiguous here since this is a crucial point.
+Beyond could also mean it is below the limit so hasn't been a concern.} the meter-per-second precision reached by the best high-resolution spectrographs \citep{fischer2016state}.
+\jessi{It seems the 1m/s spectrographs should be cited here...HARPS?}
+%
+It is therefore mandatory to better understand stellar signals and to develop methods to correct for them, if in the near future we want to detect or confirm an Earth-twin planet using the RV technique.
+This is even more true now that instrument like the Echelle SPectrograph for Rocky Exoplanet and Stable Spectroscopic Observations (ESPRESSO) \citep{Pepe-2014} and EXtreme PREcision Spectrometer (EXPRES) \citep{fischer2016state} should have the stability to detect such signals.
+However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging and false detections could plague the field.
 
@@
 
-Among the different stellar signals we are aware of, the one that is the most difficult to characterize and to correct for is the signal induced by stellar activity.
-Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, inducing spurious RV's variations \citep{Meunier-2010a, Dumusque-2014b}.
-In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, that will shift the entire stellar spectrum and stellar activity, that modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}.
-However, on quiet GKM dwarfs, the main target for precise RV's measurements, stellar activity induce signals of a few \ms.
+One of the most challenging stellar signal to characterize and to correct for is the signal induced by stellar activity. 
+Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, which can induce spurious RV's variations \citep{Meunier-2010a, Dumusque-2014b}.
+In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}.
+However, on quiet GKM dwarfs, the main target for precise RV's measurements, stellar activity can induce signals of a few \ms.
 This corresponds physically to variations smaller than 1/100th of a pixel on the detector.
-
-To be able to measure such tiny variations, we average the information of all the lines in the spectrum by cross correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}.
+\jessi{it seems the previous sentence is missing further justification for how it relates to the sentence that proceeds it.
+Do we want to add something like, ``...smaller than 1/100th of a pixel on the detector making the changing shape of the spectral lines challenging to detect.''?}
+
+In order to measure such tiny variations, a common approach is to average the information of all the lines in the spectrum by cross correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}.
 The result of this operation gives us the cross-correlation function (CCF).
-To measure the Doppler-shift between different spectra and therefore to retrieve the RV's of a star as a function of time, we calculate the variations of the CCF barycenter.
-The barycenter is generally estimated by fitting a Normal distribution to the CCF and taking its mean.
-Variations in line shape between different spectra, which indicate the presence of signals induced by stellar activity, is measured by analysing the different moments of the CCF.
-Usually, the width of the CCF is estimated using the FWHM of the fitted Normal distribution, and its asymmetry using the the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
+The CCF gives the spectrum's cross-correlation with the template as the template is shifted according to different RVs.
+%
+To measure the Doppler-shift between different spectra and therefore to retrieve the RV's of a star as a function of time, the variations of the CCF barycenter are calculated. 
+The barycenter is generally estimated by fitting a Normal density to the CCF and retaining its mean.
+Variations in line shape between different spectra, which indicate the presence of signals induced by stellar activity, are measured by analyzing the different moments of the CCF.
+Usually, the width of the CCF is estimated using the full-width half-maximum (FWHM) of the fitted Normal density, and its asymmetry using the the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
 

### 2018-05-25 manuscript.tex
updated section 1

@@
 
-If a RV signal is induced by activity, generally a strong correlation will be observed between the RV and chromospheric activity indicators like \logrhk\,or H-$\alpha$ \citep{Boisse-2009,Dumusque-2012,Robertson-2014}, but also between the RV and the FWHM of the CCF or its BIS SPAN \citep[][]{Queloz-2001,Boisse-2009,Queloz-2009,Dumusque-2016a}.
-It is therefore common now, that when fitting for a planetray signal, in addition to a Keplerian, the model includes in addition linear dependancies with the \logrhk, the FWHM and the BIS SPAN \citep{Dumusque:2017aa,Feng:2017aa}.
+If an apparent RV signal is induced by activity, generally a strong correlation will be observed between the RV and chromospheric activity indicators like \logrhk\,or H-$\alpha$ \citep{Boisse-2009,Dumusque-2012,Robertson-2014}, but also between the RV and the FWHM of the CCF or its BIS SPAN \citep[][]{Queloz-2001,Boisse-2009,Queloz-2009,Dumusque-2016a}.
+%
+It is therefore common now, that when fitting a set of RV's for a planetary signal, in addition to a Keplerian, the model includes in addition linear dependancy with the \logrhk, the FWHM and the BIS SPAN \citep{Dumusque:2017aa,Feng:2017aa}.
+\jessi{What is meant by ``a Keplerian''?
+Is that a Keplerian signal?
+Is this different from a planetary signal?}
+%
 It is also common to add a Gaussian process to the model to account for the correlated noise induced by stellar activity.
-The hyperparameters of the Gaussian process are generally trained on the different activity indicators \citep{Haywood-2014,Rajpaul-2015}.
-It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated to the RV's but also for which we can obtain the best precision.
+The hyperparameters of the Gaussian process can be trained on different activity indicators \citep{Haywood-2014,Rajpaul-2015}.
+It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated with the RV's but also for which we can obtain the best precision.
 
@@
 %\subsection{Figueira indicators of stellar activity + other}
-Several works have derived indicators that are more sensitive to line asymmetry than the BIS SPAN.
-In \citet{Boisse-2011}, the authors develop $V_{span}$, a new indicator to derive the CCF asymmetry that is more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR).
+Several indicators have been developed that are more sensitive to line asymmetry than the BIS SPAN.
+In \citet{Boisse-2011}, the authors develop $V_{span}$, an indicator of CCF asymmetry that is more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR) \jessi{Can a few words be added to explain what this indicator is measuring?}.
+%
 \citet{Figueira-2013} studied the use of two new indicators, bi-Gauss and $V_{asy}$.
-The authors were able to show that when using bi-Gauss, the amplitude in asymmetry is 30\% larger, therefore allowing the detection of smaller-amplitude correlations with RV's variations.
-They also demonstrated that $V_{asy}$ seems to be the best indicator of line asymmetry at high SNR, as its correlation with RV is more significant than any other asymmetry indictors.
+The authors were able to show that when using bi-Gauss, the amplitude in asymmetry is 30\% larger \jessi{larger than what?
+BIS SPAN?}, therefore allowing the detection of smaller-amplitude correlations with RV's variations.
+\jessi{The previous sentence is a bit unclear.
+I'm assuming the amplitude in asymmetry is just the amplitude of the asymmetry parameter vs.
+RV.
+The second part of the sentence is what is unclear.
+I think what is meant is ``allowing the detection of lower levels of activity'' since the correlation between the indicator and RV would be higher with the new indicator.}
+They also demonstrated that $V_{asy}$ seems to be a better indicator of line asymmetry at high SNR, as its correlation with RV is more significant than any of the previously proposed asymmetry indictors.
 
@@
 In all the methods described above, the RV and the FWHM are derived using a Normal distribution fitted to the CCF, and the asymmetry is estimated using another approach. 
-
-In this paper we propose to use a Skew Normal (SN) distribution to derive at the same time the RV, the FWHM and the asymmetry of the CCF, as this function includes a skewness parameter \citep[][]{Azzalini1985}.
-In addition, we know that for solar-type stars and cooler dwarfs, the bisector of the CCF as a "C"-shape due to convective blueshift \citep{Dravins-1981, Gray-2009}.
-Therefore, fitting the CCF using a model that naturally includes an asymmetry, like the SN distribution, should give in principle more precise results.
+%
+In this paper we propose to use a Skew Normal (SN) density to estimate with a single model fitting the RV, the FWHM and the asymmetry of the CCF, as this function includes a skewness parameter \citep[][]{Azzalini1985}.
+
+%In addition, we know that for solar-type stars and cooler dwarfs, the bisector of the CCF has a "C"-shape due to convective blueshift \citep{Dravins-1981, Gray-2009}. 
+%Therefore, fitting the CCF using a model that naturally includes an asymmetry, like the SN distribution, should give in principle more precise results.
 
@@
 The paper is organized as follow.
-In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  showing that the SN distribution is a better representation of observed CCF than a Normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
-In Sec.~\ref{sec:31} we present a simple model to correct from stellar activity which extends the ones previously proposed \citep{Dumusque:2017aa,Feng:2017aa}.
-In Sec.~\ref{sec:soap} we study the SN fit to the CCF using simulations coming from SOAP 2.0.
-In Sec.~\ref{sec:4}, we compare on real observations the sensitivity of the SN parameters to stellar activity with respect to other existing indicators.
-In Sec.~\ref{sec:5} we derive error bars for the different CCF moments and finally we discuss our results and conclude in Sec.~\ref{sec:discu} and Sec.~\ref{sec:conclu}.
+In Sec.~\ref{sec:2} we introduce the SN distribution, describe its applicability for modeling the CCF, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
+%
+In Sec.~\ref{sec:31} we propose an expanded linear model used to correct the estimated RV's from the inferred stellar activity, which extends the linear models previously proposed for this purpose \citep{Dumusque:2017aa,Feng:2017aa}.
+%
+In Sec.~\ref{sec:soap} the performance of the SN fit to the CCF is investigated using simulations coming from the Spot Oscillation And Planet (SOAP) 2.0 \citep{Dumusque-2014b}, followed by an analysis of real observations in Sec.~\ref{sec:4}.
+%
+Sec.~\ref{sec:5} considers derived error bars for the different estimated CCF parameters, and finally a discussion of the results and conclusions are included in Sec.~\ref{sec:discu} and Sec.~\ref{sec:conclu}, respectively.
 

### 2018-05-25 manuscript.tex
added median to table 1

@@
 The Skew Normal (SN) distribution is a class of probability distributions which includes the Normal distribution as a special case \citep{Azzalini1985}.
-The SN distribution has, in addition to a location and a scale parameter analogous to the Normal distribution's mean and standard deviation, a third parameter which describes the skewness of the distribution.
+The SN distribution has, in addition to a location and a scale parameter analogous to the Normal distribution's mean and standard deviation, a third parameter which describes the skewness (i.e.
+the asymmetry) of the distribution.
 Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $y\in Y$ can be written as
@@
 A usual Normal distribution is the special case of the SN distribution when the skewness parameter $\alpha$ is equal to zero\footnote{This can be seen from Eq.~\ref{def:snd_gen}.
-If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0) = 0.5$ and therefore $SN(y;\xi, \omega, 0) = \frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$ which is the density or a Normal distribution.
+If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0) = 0.5$ and therefore $SN(y;\xi, \omega, 0) = \frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$ which is the density of a Normal distribution.
 Note that $\Phi(0) = 0.5$ because $\Phi(0)$ is the the probability that a standard Normal random variable is less than or equal than 0.}.
@@
 
-By using Eq.~\ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution.
+By using Eq.~\ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a clearer interpretation of the behavior of the SN distribution.
 For the $\alpha$ values used in Fig.~\ref{fig:SN.plot}, the corresponding values of ($\mu$, $\sigma^2$, $\gamma$) are displayed in Table~\ref{tab:cp_values}.
-In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution, rather than simply a location and scale parameter, and $\gamma$ becomes an variable that evaluate the skewness of the SN.
-
-Beyond the mean of the SN, we introduce a second location parameter that will be largely used in the analyses: the median.
-The median of the SN, and in general the median of an absolute continuous random variable, is defined as the value $m$ such that\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}:
-%
-\begin{equation} \label{eq:snmed}
-\int_{-\infty}^{m} SN(y;\xi, \omega, \alpha) = \frac{1}{2}.
-\end{equation}
+In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution, rather than simply a location and scale parameter, and $\gamma$ provides an measure of the skewness of the SN.
+Along with the mean of the SN, we consider the median of the distribution as a measure of center, which is used in the proposed method. 
+%The median of the SN, and in general the median of an absolute continuous random variable, is defined as the value $m$ such that\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}:
+%%
+%\begin{equation} \label{eq:snmed}
+%\int_{-\infty}^{m} SN(y;\xi, \omega, \alpha) = \frac{1}{2}.
+%\end{equation}
 %
@@
    %\topcaption{Table captions are better up top} % requires the topcapt package
-   \begin{tabular}{|cccc|} % Column formatting, @{} suppresses leading/trailing space
-\hline
-$\alpha$ & $\mu$ & $\sigma^2$ & $\gamma$ \\
-\hline
- -3 	&	 -0.757	&	 0.427	&	 -0.667 \\
-0	&	 0.000 	&	1.000	&	 0.000 \\
-2	&	 0.714	&	 0.491	&	 0.454\\
-6	&	 0.787	&	 0.381	&	 0.891\\
-10	&	 0.794	&	 0.370	&	 0.956\\
+   \begin{tabular}{|ccccc|} % Column formatting, @{} suppresses leading/trailing space
+\hline
+$\alpha$ & $\mu$ & $\sigma^2$ & $\gamma$  & Median \\
+\hline
+ -3 	&	 -0.757	&	 0.427	&	 -0.667  	& 	-0.672\\
+0	&	 0.000 	&	1.000	&	 0.000 	& 	0.000\\
+2	&	 0.714	&	 0.491	&	 0.454 	& 	0.655\\
+6	&	 0.787	&	 0.381	&	 0.891 	& 	0.674\\
+10	&	 0.794	&	 0.370	&	 0.956 	& 	0.674\\
 \hline

### 2018-05-25 manuscript.tex
edits to section 2

@@
 Along with the mean of the SN, we consider the median of the distribution as a measure of center, which is used in the proposed method.
+See Table~\ref{tab:cp_values} for the medians of the SN densities displayed in Fig.~\ref{fig:SN.plot}.
 %The median of the SN, and in general the median of an absolute continuous random variable, is defined as the value $m$ such that\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}:
@@
    \end{tabular}
-   \caption{CP values $(\mu, \sigma^2, \gamma)$ corresponding to the $\alpha$ values shown in Fig.~\ref{fig:SN.plot}, with location parameter $\xi = 0$ and scale parameter $\omega = 1$.
+   \caption{CP values $(\mu, \sigma^2, \gamma)$ along with the median corresponding to the $\alpha$ values shown in Fig.~\ref{fig:SN.plot}, with location parameter $\xi = 0$ and scale parameter $\omega = 1$.
 Values are rounded to three decimal places.}
@@
 %
-Further details about the parametrization from Eq.~\ref{def:snd_gen}, called \emph{Direct Parametrization} or DP, the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
+Further details about the parametrization from Eq.~\ref{def:snd_gen}, called the \emph{Direct Parametrization} or DP, the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
 
@@
 %The CCF represents the average shape of spectral lines and is expressed in flux as a function of radial-velocity.
-To fit the CCF using a SN distribution, we use a least-squares algorithm and the following model:
+To fit the CCF using a SN density shape, we use a least-squares algorithm and the following model:
 %
@@
 %
-where C is an unknown offset fitting for the continuum of the CCF, A is the unknown contrast of the CCF and $\mu$, $\sigma^2$ and $\gamma$ are the mean, variance and skewness of the SN as defined is Sect.
-\ref{sec:2}.
-The values $y_1, \ldots, y_n$ are the different values of the abscisse of the CCF, generally with the dimension of a velocity.
-
-Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution should in principle better catch this aspect, together with other changes in asymmetry, with respect to fitting a Normal distribution.
-To initially check this intuition, we compared the CCF residuals after fitting a Normal and a SN distribution for 2 stars.
+where C is an unknown offset for the continuum of the CCF, A is the unknown contrast of the CCF \jessi{what is meant by the ``contrast''?} and $\mu$, $\sigma^2$ and $\gamma$ are the mean, variance and skewness of the SN as defined above.
+The values $y_1, \ldots, y_n$ are the different values of the abscisse \jessi{what is this previous word?} of the CCF, generally with the dimension of a velocity.
+\jessi{what is meant by ``with the dimension of a velocity''?
+Do you mean units?}
+
+%%%Since the CCF has an asymmetry due the convective blueshift, the SN density should in principle better catch this aspect, together with other changes in asymmetry, with respect to fitting a Normal distribution.
+%%%To initially check this intuition, we compared the CCF residuals after fitting a Normal and a SN distribution for 2 stars.
 The first star is Alpha Centauri b, whose CCF's have high signal-to-noise ratio (SNR).
@@
 Fig.~\ref{fig:Residual.comparison} shows that the SN seems to be a slightly better model to explain the shape of the CCF.%, in particular as the SNR decreases.
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 2.5in]{[1]HD128621Residuals.pdf} 
-\includegraphics[height = 2.5in]{[1]LRa01_E2Residuals.pdf} 
-   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCF's from the star Alpha Centauri b (left) and Corot-7 (right).
+%%%%
+%%%\begin{figure*}[htbp]
+%%%   \centering
+%%%\includegraphics[height = 2.5in]{[1]HD128621Residuals.pdf} 
+%%%\includegraphics[height = 2.5in]{[1]LRa01_E2Residuals.pdf} 
+%%%   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCF's from the star Alpha Centauri b (left) and Corot-7 (right).
 When looking at the residuals corresponding to the center of the CCF, the SN fit leads to slightly better results for both stars.} %Moreover, as the SNR decreases, the SN distribution shows smaller residuals respect the Normal ones.}
-    \label{fig:Residual.comparison}
-\end{figure*}
-%
-
-When fitting a Normal distribution to the CCF, the mean of the fitted distribution is defined as the measured RV, the FWHM of the Normal distribution ($=2\sqrt(2\ln2)\sigma$) represents the width of the CCF and because the Normal distribution is symmetric, a  skewness parameter cannot be obtained directly from this fit.
-Such a parameter is generally obtain in a second step by calculating the BIS SPAN of the CCF \citep[see Sect.
-\ref{intro}, and e.g.][]{Queloz-2001}.
-When fitting a SN distribution, we define two indicators for the RV: the mean of the SN, defined as SN mean RV and the median of the SN, defined as SN median RV.
-We will discuss advantages and limits for both of these choices in Sec.
+%%%    \label{fig:Residual.comparison}
+%%%\end{figure*}
+%%%%
+
+When fitting a Normal distribution to the CCF, the estimated mean of the model is used as the estimated RV, the FWHM of the Normal density ($2\sqrt(2\ln2)\sigma$ with standard deviation $\sigma$) represents the width of the CCF.
+Because the Normal density is symmetric, the skewness is always equal to 0 so a separate approach is needed to estimate the skewness of the CCF.
+An estimated skewness parameter is generally obtained by calculating the BIS SPAN of the CCF \citep[see Sect. \ref{intro}, and e.g.][]{Queloz-2001}. 
+%
+
+With the proposed SN approach, we propose two estimators of the RV: the mean and median of the SN model fit (referred to as \emph{SN mean RV} and \emph{SN median RV}, respecitvely) , and present advantages and limitations for both of these choices in Sec.
 \ref{sec:4} and Sec.
 \ref{sec:5}.
-We define the width of the SN, SN FWHM, in the same way as for the Normal distribution\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}, and finally the skewness of the CCF, SN GAMMA, is derived using the $\gamma$ parameter.
-
-To test the strength of the correlation between the estimated RV's and the different indicators used to evaluate stellar activity, we calculated the Pearson correlation coefficient, which in its general form is defined as:
+The width of the SN, \emph{SN FWHM}, is defined in the same way as for the Normal distribution\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}, and finally the skewness of the CCF, \emph{SN GAMMA}, is estimated by the $\gamma$ parameter.
+
+To evaluate the strength of the correlation between the estimated RV's and the different stellar activity indicators, we calculated the Pearson correlation coefficient, which in its general form is defined as:
 %

### 2018-05-28 manuscript.tex

@@
 
-With the proposed SN approach, we propose two estimators of the RV: the mean and median of the SN model fit (referred to as \emph{SN mean RV} and \emph{SN median RV}, respecitvely) , and present advantages and limitations for both of these choices in Sec.
+With the proposed SN approach, we propose two estimators of the RV: the mean and median of the SN model fit (referred to as \emph{SN mean RV} and \emph{SN median RV}, respectively) , and present advantages and limitations for both of these choices in Sec.
 \ref{sec:4} and Sec.

### 2018-05-28 manuscript.tex
Answered to Jessi's comments

@@
 
-\title{Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal distribution}
+\title{Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density}
 %\thanks{Based on observations collected at the La Silla Parana Observatory,
@@
 Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
-Stellar activity can be probed by measuring variations in the shape of the cross-correlation function (CCF) as a function of time often using different moments of a modeled CCF.
+Stellar activity can be probed by measuring time dependant variations in the shape of the cross-correlation function (CCF), often estimated using the different moments of the modelled CCF.
 Therefore estimating the moments of the CCF with high precision is essential to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
 %
-We propose to estimate the moments of the CCF by first fitting a model using a Skew Normal (SN) density shape, which unlike the commonly employed Normal density,  includes an asymmetry parameter to capture the natural asymmetry of the CCF induced by convective blueshift.
-\jessi{is convective blueshift the only asymmetry-inducing variable of the CCF?}
+We propose to estimate the moments of the CCF by fitting a model using a Skew Normal (SN) density shape, which unlike the commonly employed Normal density, \xavier{includes an skewness parameter to capture the asymmetry of the CCF induced by stellar activity, but also the natural asymmetry induced by convective blueshift.}
 %
@@
 Therefore the CCF asymmetry and the CCF width derived using a SN are more sensitive to stellar activity, which allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals.
-The precision on the estimated set of RV's, derived using the median of the fitted SN distributions are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
+The precision on the estimated set of RV's, derived using the median of the fitted SN densities are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
 In addition, the uncertainties related to the asymmetry parameter derived from the SN are on average $15\%$ smaller than the ones calculated on the common Bisector Inverse Slope Span (BIS SPAN).
-We strongly encourage the use of the SN distribution rather than the Normal distribution, because this allows us to retrieve in one single fit the different moments of the CCF, because the derived moments better catch stellar activity signals and finally because the standard errors on the RV's and the the asymmetry parameter are smaller than the one estimated with the Normal fit.
+We strongly encourage the use of the SN density rather than the Normal density, because this allows us to retrieve in one single fit the different moments of the CCF, because the derived moments better catch stellar activity signals and finally because the standard errors on the RV's and the the asymmetry parameter are smaller than the one estimated with the Normal fit.
 
@@
 
-When working with radial velocities (RV's), one of the main limitations to the detection of small-mass exoplanets is no longer the precision of the instruments used, but the different sources of variability induced by the stars \citep[][]{Dumusque:2017aa} \jessi{We should add more citations here to new spectrographs...maybe EXPRES?}.
-Stellar oscillations, granulation phenomena, and stellar activity can all induce apparent RV signals \citep{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are beyond \jessi{what is meant by the word ``beyond'' here?
-Do you mean below the limit or above?
-I think you mean above since they can induce singles that are greater than 1m/s, but we need to unambiguous here since this is a crucial point.
-Beyond could also mean it is below the limit so hasn't been a concern.} the meter-per-second precision reached by the best high-resolution spectrographs \citep{fischer2016state}.
-\jessi{It seems the 1m/s spectrographs should be cited here...HARPS?}
+When working with radial velocities (RV's), one of the main limitations to the detection of small-mass exoplanets is no longer the precision of the instruments used, but the different sources of variability induced by the stars \citep[e.g.][]{Feng:2017aa, Dumusque:2017aa, Rajpaul-2015, Robertson-2014}.
+Stellar oscillations, granulation phenomena, and stellar activity can all induce apparent RV signals \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are above the meter-per-second precision reached by the best high-resolution spectrographs \citep[HARPS, HARPS-N,][]{Mayor-2003,Cosentino-2012}.
 %
@@
 However, on quiet GKM dwarfs, the main target for precise RV's measurements, stellar activity can induce signals of a few \ms.
-This corresponds physically to variations smaller than 1/100th of a pixel on the detector.
-\jessi{it seems the previous sentence is missing further justification for how it relates to the sentence that proceeds it.
-Do we want to add something like, ``...smaller than 1/100th of a pixel on the detector making the changing shape of the spectral lines challenging to detect.''?}
+This corresponds physically to variations smaller than 1/100th of a pixel on the detector making the changing shape of the spectral lines challenging to detect.
 
@@
 %
-It is therefore common now, that when fitting a set of RV's for a planetary signal, in addition to a Keplerian, the model includes in addition linear dependancy with the \logrhk, the FWHM and the BIS SPAN \citep{Dumusque:2017aa,Feng:2017aa}.
-\jessi{What is meant by ``a Keplerian''?
-Is that a Keplerian signal?
-Is this different from a planetary signal?}
+It is therefore common now, that when fitting a Keplerian signal to a set of RVs to look for a planet, the model includes in addition linear dependancies with the \logrhk, the FWHM and the BIS SPAN \citep{Dumusque:2017aa,Feng:2017aa}.
 %
@@
 Several indicators have been developed that are more sensitive to line asymmetry than the BIS SPAN.
-In \citet{Boisse-2011}, the authors develop $V_{span}$, an indicator of CCF asymmetry that is more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR) \jessi{Can a few words be added to explain what this indicator is measuring?}.
+In \citet{Boisse-2011}, the authors develop $V_{span}$, which is the difference between the RV measured respectively by fitting a Normal density to the upper and the bottom part of the CCF.
+This CCF asymmetry parameter is shown to be more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR).
 %
 \citet{Figueira-2013} studied the use of two new indicators, bi-Gauss and $V_{asy}$.
-The authors were able to show that when using bi-Gauss, the amplitude in asymmetry is 30\% larger \jessi{larger than what?
-BIS SPAN?}, therefore allowing the detection of smaller-amplitude correlations with RV's variations.
-\jessi{The previous sentence is a bit unclear.
-I'm assuming the amplitude in asymmetry is just the amplitude of the asymmetry parameter vs.
-RV.
-The second part of the sentence is what is unclear.
-I think what is meant is ``allowing the detection of lower levels of activity'' since the correlation between the indicator and RV would be higher with the new indicator.}
+The authors were able to show that when using bi-Gauss, the amplitude in asymmetry is 30\% larger than when using BIS SPAN, therefore allowing the detection of lower levels of activity.
 They also demonstrated that $V_{asy}$ seems to be a better indicator of line asymmetry at high SNR, as its correlation with RV is more significant than any of the previously proposed asymmetry indictors.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Why using a SN distribution?}
-In all the methods described above, the RV and the FWHM are derived using a Normal distribution fitted to the CCF, and the asymmetry is estimated using another approach. 
-%
-In this paper we propose to use a Skew Normal (SN) density to estimate with a single model fitting the RV, the FWHM and the asymmetry of the CCF, as this function includes a skewness parameter \citep[][]{Azzalini1985}.
+%\subsection{Why using a SN density?}
+In all the methods described above, except bi-Gauss, the RV and the FWHM are derived using a Normal density fitted to the CCF, and the asymmetry is estimated using another approach. 
+%
+In this paper we propose to use a Skew Normal (SN) density to estimate with a single fit of the CCF, the RV, the FWHM and the asymmetry of the CCF, as this function includes a skewness parameter \citep[][]{Azzalini1985}.
 
 %In addition, we know that for solar-type stars and cooler dwarfs, the bisector of the CCF has a "C"-shape due to convective blueshift \citep{Dravins-1981, Gray-2009}. 
-%Therefore, fitting the CCF using a model that naturally includes an asymmetry, like the SN distribution, should give in principle more precise results.
+%Therefore, fitting the CCF using a model that naturally includes an asymmetry, like the SN density, should give in principle more precise results.
 
@@
 The paper is organized as follow.
-In Sec.~\ref{sec:2} we introduce the SN distribution, describe its applicability for modeling the CCF, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
+In Sec.~\ref{sec:2} we introduce the SN density, describe its applicability for modeling the CCF, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
 %
@@
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Fitting the Skew Normal distribution to the CCF} \label{sec:3}
+\subsection{Fitting the Skew Normal density to the CCF} \label{sec:3}
 
@@
 \begin{eqnarray} \label{eq:3}
-f_{CCF}(y_i) = \mathrm{C} - \mathrm{A} \times SN(y_i;\mu, \sigma^2, \gamma), \quad i = 1, \ldots, n
+f_{CCF}(x_i) = \mathrm{C} - \mathrm{A} \times SN(x_i;\mu, \sigma^2, \gamma), \quad i = 1, \ldots, n
 \end{eqnarray}
 %
-where C is an unknown offset for the continuum of the CCF, A is the unknown contrast of the CCF \jessi{what is meant by the ``contrast''?} and $\mu$, $\sigma^2$ and $\gamma$ are the mean, variance and skewness of the SN as defined above.
-The values $y_1, \ldots, y_n$ are the different values of the abscisse \jessi{what is this previous word?} of the CCF, generally with the dimension of a velocity.
-\jessi{what is meant by ``with the dimension of a velocity''?
-Do you mean units?}
-
-%%%Since the CCF has an asymmetry due the convective blueshift, the SN density should in principle better catch this aspect, together with other changes in asymmetry, with respect to fitting a Normal distribution.
-%%%To initially check this intuition, we compared the CCF residuals after fitting a Normal and a SN distribution for 2 stars.
+where C is an unknown offset for the continuum of the CCF, A is the unknown amplitude of the CCF, commonly referred to as the contrast, and $\mu$, $\sigma^2$ and $\gamma$ are the mean, variance and skewness of the SN as defined above.
+The values $x_1, \ldots, x_n$ are the different values of the x-axis of the CCF, generally in the unit of a velocity.
+
+%%%Since the CCF has an asymmetry due the convective blueshift, the SN density should in principle better catch this aspect, together with other changes in asymmetry, with respect to fitting a Normal density.
+%%%To initially check this intuition, we compared the CCF residuals after fitting a Normal and a SN density for 2 stars.
 The first star is Alpha Centauri b, whose CCF's have high signal-to-noise ratio (SNR).
@@
 %%%   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCF's from the star Alpha Centauri b (left) and Corot-7 (right).
-When looking at the residuals corresponding to the center of the CCF, the SN fit leads to slightly better results for both stars.} %Moreover, as the SNR decreases, the SN distribution shows smaller residuals respect the Normal ones.}
+When looking at the residuals corresponding to the center of the CCF, the SN fit leads to slightly better results for both stars.} %Moreover, as the SNR decreases, the SN density shows smaller residuals respect the Normal ones.}
 %%%    \label{fig:Residual.comparison}
@@
 
-When fitting a Normal distribution to the CCF, the estimated mean of the model is used as the estimated RV, the FWHM of the Normal density ($2\sqrt(2\ln2)\sigma$ with standard deviation $\sigma$) represents the width of the CCF.
+When fitting a Normal density to the CCF, the estimated mean of the model is used as the estimated RV, the FWHM of the Normal density\footnote{FWHM$=2\sqrt{2\ln2}\,\sigma$ with standard deviation $\sigma$} represents the width of the CCF.
 Because the Normal density is symmetric, the skewness is always equal to 0 so a separate approach is needed to estimate the skewness of the CCF.
@@
 \ref{sec:5}.
-The width of the SN, \emph{SN FWHM}, is defined in the same way as for the Normal distribution\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}, and finally the skewness of the CCF, \emph{SN GAMMA}, is estimated by the $\gamma$ parameter.
+The width of the SN, \emph{SN FWHM}, is defined in the same way as for the Normal density\footnote{Note that SN FWHM does not correspond to the width of the SN density at half maximum like in the Normal case.}, and finally the skewness of the CCF, \emph{SN GAMMA}, is estimated by the $\gamma$ parameter.
 
@@
 Both these correlations are stronger than the correlation between the BIS SPAN and RV ($R^2=-0.77$).
-The correlations between the width of the CCF and the corresponding RV's are slightly stronger when fitting a SN rather than a Normal distribution, as shown in the left series of plots in Fig.~\ref{fig:spot.corr}.
+The correlations between the width of the CCF and the corresponding RV's are slightly stronger when fitting a SN rather than a Normal density, as shown in the left series of plots in Fig.~\ref{fig:spot.corr}.
 The results show anyway a correlation close to $0$ when focusing on the width of the CCF, suggesting that the presence of a spot on the photosphere of star leads to changes in the shape of the CCF rather than its width.
@@
 Finally, the correlations involving the common indicators (i.e.
-RV, FWHM and BIS SPAN) are systematically weaker than the correlations obtained by fitting the SN to the CCF, suggesting that this distribution could be helpful when searching for active regions.
+RV, FWHM and BIS SPAN) are systematically weaker than the correlations obtained by fitting the SN to the CCF, suggesting that this density could be helpful when searching for active regions.
 We recall moreover that all the quantities needed for conducting the analyses of the CCF are directly available by just fitting the SN.
@@
 
-In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN distribution defined in Sec.
-\ref{sec:3} with the approach based on the Normal distribution.
+In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN density defined in Sec.
+\ref{sec:3} with the approach based on the Normal density.
 Other four stars have been analyzed with the proposed method and details can be found in the Appendix \ref{appendix}.
@@
 
- A comparison with the results obtained by the classic approach is done, where the RV's of the star are estimated by retrieving the mean of the Normal distribution used to fit the CCF, along with the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}.
+ A comparison with the results obtained by the classic approach is done, where the RV's of the star are estimated by retrieving the mean of the Normal density used to fit the CCF, along with the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}.
 The latter parameters are calculated separately from the Normal fit that leads to the set of RV's of the star.
@@
 In other words, changes in the asymmetry of the CCF are better captured when using the SN mean RV.
-The correlation between FWHM and the RV's, either by using SN mean RV or SN median RV, is as well stronger when fitting a SN distribution rather than a Normal.
+The correlation between FWHM and the RV's, either by using SN mean RV or SN median RV, is as well stronger when fitting a SN density rather than a Normal.
 All the correlations are statistically different from $0$.
@@
 
-Both the proposed indicators coming from the SN distribution have advantages and limits: SN mean RV better catches changes in the asymmetry of the CCF but the resulting set of RV's ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Sec.
+Both the proposed indicators coming from the SN density have advantages and limits: SN mean RV better catches changes in the asymmetry of the CCF but the resulting set of RV's ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Sec.
 \ref{intro}.
@@
 Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
-Therefore, we cannot do a bootstrap analysis on perturbing independently each CCF point with a Gaussian distribution scaled to the error of each given point.
+Therefore, we cannot do a bootstrap analysis on perturbing independently each CCF point with a Normal density scaled to the error of each given point.
 A detailed discussions of the methods nowadays available to resampling in situations with dependent data structures is available in \citet{lahiri2013resampling}.
@@
 In our particular case, since each point in a CCF is correlated with each other, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF.
-We then fit a Normal or a SN distribution to each of these CCF's and then calculate the standard deviations of the distribution for the location parameters (RV, SN mean RV or SN median RV), the width parameters (SN FWHM or FWHM ) and the asymmetry parameters ($\gamma$ or BIS SPAN).
+We then fit a Normal or a SN density to each of these CCF's and then calculate the standard deviations of the density for the location parameters (RV, SN mean RV or SN median RV), the width parameters (SN FWHM or FWHM ) and the asymmetry parameters ($\gamma$ or BIS SPAN).
 
@@
 The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} shows the different errors for the RV's, defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width of the CCF, defined as FWHM (red triangles) or SN FWHM (black circles) and the asymmetry of the CCF, defined as SN GAMMA (black circles) or BIS SPAN (red triangles).
-In the series of three plots in the bottom of Fig.~\ref{fig:se.soap.faculae} we show the ratio between errors associated to the parameters derived from the bootstrap analysis fitting the SN and the errors associated to the parameters derived from the bootstrap analysis fitting the Normal distribution.
+In the series of three plots in the bottom of Fig.~\ref{fig:se.soap.faculae} we show the ratio between errors associated to the parameters derived from the bootstrap analysis fitting the SN and the errors associated to the parameters derived from the bootstrap analysis fitting the Normal density.
 We used the same notation also for the other two cases, where respectively a spot is present on the photosphere of the star (Fig.~\ref{fig:se.soap.spot}) and a spot and a planet are introducing both spurious and pure variations in the RV's (Fig.~\ref{fig:se.soap.spot.planet}).
@@
 The parameter SN50 corresponds to the SNR in order 50, which defines a wavelength of 550\,nm.
-In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameters derived from the bootstrap analysis fitting the Normal distribution.
+In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameters derived from the bootstrap analysis fitting the Normal density.
 We first see that the errors on the CCF parameters only depends on the SNR and do not depend on the spectral type.
@@
 
-An analysis of the CCF residuals after fitting a Normal or SN distribution shows that the SN is a slightly better model to explain the shape of the CCF.
+An analysis of the CCF residuals after fitting a Normal or SN density shows that the SN is a slightly better model to explain the shape of the CCF.
 This comes from the fact that CCF's present a natural asymmetry due the convective blueshift.
@@
 
-In this paper we introduced a novel approach based on the Skew Normal (SN) distribution to retrieve RV's and shape variations in the CCF of stars.
+In this paper we introduced a novel approach based on the Skew Normal (SN) density to retrieve RV's and shape variations in the CCF of stars.
 When searching for small-mass exoplanets using the RV technique, it is essential to understand variation of the shape of the CCF, which is a proxy for stellar activity effects.
-The standard approach consist at first to fit a Normal distribution to the CCF to get the RV and FWHM, defined as the mean and the FWHM of the Normal distribution, and then to measure the asymmetry of the CCF by calculating the BIS SPAN.
+The standard approach consist at first to fit a Normal density to the CCF to get the RV and FWHM, defined as the mean and the FWHM of the Normal density, and then to measure the asymmetry of the CCF by calculating the BIS SPAN.
 FWHM and BIS SPAN give us information on the line shape that are used to probe stellar activity signals.
 
-In this paper we propose to conduct the analysis fitting a SN distribution to the CCF.
-Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution can in principle better catch these aspects respect the Normal fit.
-On top of that, by using the SN distribution to fit CCF's, we can measure simultaneously the RV of the star, the width and the asymmetry of the CCF.
-
-Starting from the simulation environment SOAP and then moving to real stars, we showed that using the SN distribution to fit CCF's leads to a significant improvement to probing stellar activity.
-While for the Normal distribution mean and median are equivalent, using the SN fit different location parameters can be tested.
+In this paper we propose to conduct the analysis fitting a SN density to the CCF.
+Since the CCF presents a natural asymmetry due the convective blueshift, the SN density can in principle better catch these aspects respect the Normal fit.
+On top of that, by using the SN density to fit CCF's, we can measure simultaneously the RV of the star, the width and the asymmetry of the CCF.
+
+Starting from the simulation environment SOAP and then moving to real stars, we showed that using the SN density to fit CCF's leads to a significant improvement to probing stellar activity.
+While for the Normal density mean and median are equivalent, using the SN fit different location parameters can be tested.
 While the median of the SN is a more robust statistic respect variations in the shape of the CCF, the mean of the SN is more sensible to changes in the asymmetry of the CCF.
-We suggest to use as parameter that defines the RV of the star the median of the SN, since the standard errors related to this parameter working with CCF's from real stars are on average $10\%$ smaller than the standard errors retrieved using the Normal distribution.
+We suggest to use as parameter that defines the RV of the star the median of the SN, since the standard errors related to this parameter working with CCF's from real stars are on average $10\%$ smaller than the standard errors retrieved using the Normal density.
 To evaluate changes in the asymmetry of the CCF, we suggest to use the mean of the SN.
@@
 Then, by getting from the original profile line $100$ simulated profiles, we run the SN fitting analyses, allowing us retrieving for all the parameter of interests an estimation for their standard errors.
-Concerning the standard error associated to the means of the distributions, the SN fit leads to slightly larger standard errors respect when running the Normal fit.
+Concerning the standard error associated to the means of the densitys, the SN fit leads to slightly larger standard errors respect when running the Normal fit.
 This fact can be explained by noticing that as a simulated CCF is created according to the procedure described above, we expect slightly differences on the asymmetry of the CCF as well.
-The natural correlation between the RVs of the star and $\gamma$, where the mean of the SN is shifted in the direction of the asymmetry of the distribution, leads to larger uncertainties related to the RVs of the star.
+The natural correlation between the RVs of the star and $\gamma$, where the mean of the SN is shifted in the direction of the asymmetry of the density, leads to larger uncertainties related to the RVs of the star.
 The latter consideration provides a further justification for correcting the RVs of the star from stellar activity and explains why this correction is more helpful when running the proposed analysis rather than the classic Normal fit.

### 2018-05-28 manuscript.tex
Working on sect 3

@@
 
-With the proposed SN approach, we propose two estimators of the RV: the mean and median of the SN model fit (referred to as \emph{SN mean RV} and \emph{SN median RV}, respectively) , and present advantages and limitations for both of these choices in Sec.
+With the proposed SN approach, we propose two estimators of the RV: the mean and median of the SN model fit (referred to as SN mean RV and SN median RV, respectively), and present advantages and limitations for both of these choices in Sec.
 \ref{sec:4} and Sec.
 \ref{sec:5}.
-The width of the SN, \emph{SN FWHM}, is defined in the same way as for the Normal density\footnote{Note that SN FWHM does not correspond to the width of the SN density at half maximum like in the Normal case.}, and finally the skewness of the CCF, \emph{SN GAMMA}, is estimated by the $\gamma$ parameter.
+The width of the SN, SN FWHM, is defined in the same way as for the Normal density\footnote{Note that SN FWHM does not correspond to the width of the SN density at half maximum like in the Normal case.}, and finally the skewness of the CCF is estimated by the $\gamma$ parameter.
 
@@
 
-Exoplanets will only produce a variation in RV's induced by a pure Doppler-shift of stellar spectra.
-Stellar activity and in particular the presence of active regions on the photosphere of the star, on the contrary, does not produce a blueshift or redshift of the spectra, but creates spurious RV's signal by modifying the shape of the spectral lines.
-To track these changes in the shape of the line profile, the general approach consists in using the FWHM, the BIS SPAN or the indicators introduced by \citep{Figueira-2013}, which provide an information on the average width and asymmetry of the CCF.
-A strong correlation between the estimated set of RV's and one or more of these parameters provides an indication that the RV's are affected by stellar activity signals.
+\xavier{Exoplanets only produce a pure RV signal.
+Stellar activity on the contrary, and in particular the presence of active regions on the stellar photosphere, does not produce a blueshift or redshift of the entire stellar spectra, but creates a spurious RV signal by modifying the shape of spectral lines.
+To track these variations in the shape of the spectral lines}, the general approach consists in using the FWHM, the BIS SPAN or the indicators introduced in \citet{Boisse-2011} or \citet{Figueira-2013}, which provide information on the width and asymmetry of the CCF.
+A strong correlation between the estimated RVs and one or more of these parameters provides an indication that stellar activity signals are affecting our measurements.
 
@@
 
-While the parameters BIS SPAN and FWHM have already been introduced and used in \citep{Dumusque:2017aa,Feng:2017aa}, by using Eq.~\ref{eq:RV:correction} we propose also to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN WHM).
+While the parameters BIS SPAN and FWHM have already been introduced and used in several analysis \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}, we propose in addition to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM).
 The inclusion of the contrast parameter $A$ is justified by the fact that the presence for instance of a spot produces also changes in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g.
@@
 Fig.~\ref{fig:se.soap.faculae} shows the results of the bootstrap analysis performed when a faculae is present on the photosphere of the star.
-The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} shows the different errors for the RV's, defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width of the CCF, defined as FWHM (red triangles) or SN FWHM (black circles) and the asymmetry of the CCF, defined as SN GAMMA (black circles) or BIS SPAN (red triangles).
+The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} shows the different errors for the RV's, defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width of the CCF, defined as FWHM (red triangles) or SN FWHM (black circles) and the asymmetry of the CCF, defined as $\gamma$ (black circles) or BIS SPAN (red triangles).
 In the series of three plots in the bottom of Fig.~\ref{fig:se.soap.faculae} we show the ratio between errors associated to the parameters derived from the bootstrap analysis fitting the SN and the errors associated to the parameters derived from the bootstrap analysis fitting the Normal density.

### 2018-05-29 manuscript.tex
Section 3 reviewed

@@
 
-Because of the spurious variations in RV's caused by active regions, a crucial step of the entire analysis is to correct the initially estimated RV's in order to retrieve a set of RV's containing ideally only the possibly pure Doppler-shift coming from the exoplanets.
-In order to reach this goal, we propose to consider a linear combination of the RV's having as covariates the amplitude parameter A, the BIS SPAN (or $\gamma$), the FWHM (or SN FWHM) and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM and the interaction between $\gamma$ and SN FWHM in the SN case).
-We propose the following function to correct the RV's from stellar activity:
+\xavier{When fitting for planetary signals in RV data, it is common to include in the fitted model, linear dependencies with the BIS SPAN and the FWHM, to take into account the signal induced by stellar activity \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
+%Some people also include the \logrhk, however, \citet{Feng-2018} show that this is probably not a good choice as \logrhk and RV are not well correlated.
+In this paper, we propose to add additional parameters in the model to correct for stellar activity: first the amplitude parameter A of the CCF, generally referred to as the CCF contrast, and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case).
+The stellar activity correction we propose can therefore be written as:}
 %
@@
 where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix). 
-
-While the parameters BIS SPAN and FWHM have already been introduced and used in several analysis \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}, we propose in addition to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM).
-The inclusion of the contrast parameter $A$ is justified by the fact that the presence for instance of a spot produces also changes in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g.
+The inclusion of the contrast parameter $A$ is justified by the fact that the presence of a spot on the stellar surface produces a changes in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g.
 Fig.
 2 in ][]{Dumusque-2014b}.
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 2.5in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
-%   \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF (also known as contrast) and not only on its asymmetry or width.
-This very same plot has been originally presented by \citep{Dumusque-2014b} when introducing the Spot Oscillation And Planet (SOAP) 2.0 simulator.}
-%    \label{fig:spotA}
-%\end{figure*}
-%%
-
-The reasons for including in Eq.~\ref{eq:RV:correction} a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM) will be better justified through the results of the examples presented in Sec.\ref{sec:soap}.
-We point out however that while the association between in this case BIS SPAN  (or $\gamma$) and FWHM (or SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant.
+The reasons for including in Eq.~\ref{eq:RV:correction} a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better justified through the results of the examples presented in Sec.\ref{sec:soap}.
+\xavier{This interaction term allows to take into account cases when for different values of SN FWHM (or FWHM), the linear coefficient $\beta_{2}$ for $\gamma$ (or BIS SPAN) varies}.
+\xavier{Umberto, Jessi, is this correct ?}
+%while the association between in this case BIS SPAN and FWHM (or $\gamma$ and SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant.
 In particular the effect differs at different values of the other values.
@@
 In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$, $\beta_{2}$, $\beta_{3}$ and $\beta_{4}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,\dots,4$.
-The level for not rejecting the null hypothesis is fixed equal to $0.05$.
+The level for not rejecting the null hypothesis is fixed to $0.05$.
 The coefficient of multiple correlation $R^2$ is introduced in order to explain how well this linear combination addresses the variability of the RV variation induced by stellar activity.
 
-As final remark we recall that, when working with a linear regression, there are several ways to select the variables to include in the model.
-While usually the stepwise technique takes place \citep{efroymson1960multiple,hocking1976biometrics}, the proposed function defined in Eq.~\ref{eq:RV:correction} that corrects from stellar activity is the result of statistical and astronomical considerations.
-In particular we checked that the correlations between the proposed parameters were not approaching one: if it were the case, the matrix needed to calculate the estimates would have been singular, hence non invertible.
-This problem is known in statistic with the term multicollinearity.
-A detailed discussion of the topic can be found in the book by \citep{belsley1991}.
-In the literature there are examples of stars presenting a high correlation between the contrast parameter $A$ and the FWHM \citep{Dumusque:2017aa,Feng:2017aa}.
-In the analyses of the presented work, we did not find any correlation between the contrast parameter $A$ and the FWHM (or between the contrast parameter $A$ and the SN FWHM) exceeding $0.66$ for all the analyzed stars and therefore the problem of multicollinearity is avoided.
-For the interpretation of the coefficients, we centered on the mean all the variables considered in the linear regression defined in Eq.~\ref{eq:RV:correction}.
-Last, when proposing interactions between covariates, we found that only the one between the width and the asymmetry of the CCF is statistically helpful to explain spurious variations in RV's caused by stellar activity.
-Consequently, in the present work, the interaction between other variables are not used as covariates.
+When working with a linear regression, there are several ways to select the variables to include in the model.
+While usually the stepwise technique is used \citep{efroymson1960multiple,hocking1976biometrics}, the proposed function defined in Eq.~\ref{eq:RV:correction}, that accounts for stellar activity, is the result of statistical and astronomical considerations.
+In particular we checked that the correlations between the proposed parameters were not approaching one: if it was the case, the matrix needed to calculate the estimates would be singular, hence non invertible.
+This problem is known in statistics with the term multicollinearity.
+A detailed discussion of the topic can be found in the book by \citet{belsley1991}.
+\xavier{It is common to see some correlation between the amplitude parameter $A$ and the FWHM (or SN FWHM) of the CCF.
+However, in the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ and therefore, the problem of multicollinearity is avoided.
+Finally, we investigate as well the statistical significant of the interaction term between $A$ and the width, and $A$ and the asymmetry of the CC, however, those interaction were relevant for accounting for stellar signal.}
 

### 2018-05-29 manuscript.tex
reviewing sect 4 in process

@@
 \section{Simulation Study} \label{sec:soap}
-In order to evaluate the performance of the proposed SN approach for modelling the CCF and the benefit of using the proposed correction for stellar activity (See Eq.~\ref{eq:RV:correction}), we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.
-
-\umberto{Add more information on SOAP, the way we retrieve the CCFs with SOAP, the characteristics of the CCF (i.e. how many points, ...) and the reasons why we need CCFs simulated with SOAP.}
-\umberto{Specify characteristic of the star.}
-\xavier{}
+In order to evaluate the performance of the proposed SN approach for modelling the CCF and the benefit of using the proposed correction for stellar activity (See Eq.~\ref{eq:RV:correction}), we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet 2.0 code \citep[SOAP 2.0,][]{Dumusque-2014b}.
+
+\xavier{For a given configuration of spots and faculae on the stellar surface, SOAP 2.0 gives as output the simulated CCF as a function of rotational phase.
+The code returns as well the RV and the FWHM by fitting a Normal density to the CCF, and the BIS SPAN by calculating the bisector of the CCF.
+SOAP 2.0 gives us therefore noiseless CCFs affected by stellar activity, which will be used to compare the benefits of fitting a SN density to the CCF compared to a Normal density fit.}
+
+\xavier{For the simulations shown below, we modelled a star similar to the Sun.
+The stellar rotational period is set to 25.0 days, the radius to a solar radius and the star is seen equator on.
+The stellar effective temperature is set to 5778 K (NASA Planetary Fact Sheets), and we use a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
+In addition, to be able to compare the result of those simulations with real data obtained with the HARPS spectrograph in Sect.~\ref{sec:4}, we asked SOAP 2.0 to generate CCFs of width 40 \kms and of resolution 115'000, so that those CCFs would have the same properties as the one returned by the HARPS data reduction.}
 
@@
 
-\umberto{Specify characteristic of the faculae.}\xavier{}
-
-Fig.~\ref{fig:faculae} shows the results obtained when a faculae is present on the photosphere of the star.
-It is possible to note that, although there is not a planet, the presence of the faculae leads to spurious variations in RV's for all the proposed indicators.
-SN mean RV seems to have the smallest spurious variations caused by the faculae.
+\xavier{Fig.~\ref{fig:faculae} shows the barycentric variation of the CCF induced by a simulated equatorial faculae of size 3\% relative to the visible stellar hemisphere.
+We compare the barycentric variation as measured when fitting a Normal density and taking its mean (RV), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV).
+Although the different estimates for the RV present similar variation as a function of rotational phase, we note that SN mean RV present a smaller amplitude than the two others.}
 

### 2018-05-29 manuscript.tex
finished 4.1

@@
 
-Since in this case we know that the variations in RV are only caused by the faculae, the evaluation of the correlations between the set of RV's and the asymmetry parameters can provide relevant information to understand the cause of the variations observed in RV's.
-Fig.~\ref{fig:faculae.corr} shows the correlations obtained using as RV respectively SN mean RV, SN median RV and RV.
-The $\gamma$ parameter shows a correlation with SN median RV equal to $-0.944$, which is stronger than the correlations between the other asymmetry indicators and their estimated RV's.
-When focusing on the width of the CCF, The correlation between SN FWHM and SN mean RV is the strongest one ($R^{2}=0.655$).
-
 \begin{figure*}[htbp]
@@
 
+\xavier{In Fig.~\ref{fig:faculae.corr}, we compare the correlation between the different RV estimates and the different asymmetry or width estimates.
+As we can see, the strength of the correlation between $\gamma$ and SN mean RV is extremely similar to the correlation between BIS SPAN and the RV, with a Pearson correlation coefficient} \xavier{$R=-0.75$}.
+\xavier{Moreover, the correlation between $\gamma$ and SN median RV is much stronger, reaching} \xavier{$R=-0.95$}.
+\xavier{When comparing the correlation between the width and the different RV estimates, we observe that the data draw a circle, which implies a phase shift between those two parameters.
+In this case we find no correlation between those parameters, however, the different estimates gives very similar results.}
+
 \begin{figure*}[htbp]
@@
 
-Since all the variations in RV's displayed in Fig.~\ref{fig:faculae} are caused by the presence of a faculae on the photosphere of the star, we corrected the originally estimated set of RV's by using Eq.~\ref{eq:RV:correction}.
-The results of the correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the parameters involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
+Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a faculae, \xavier{we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its efficient in in th ecase of a faculae.} The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
+\xavier{To modify with respect to the new results.
 It is straightforward noticing that the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the faculae.
 In particular the $R^{2}$ is extremely high regardless the fit that has been use (Normal or SN).
-We note also that the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) is not statistically significant to explain spurious variations caused by a faculae.
+We note also that the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) is not statistically significant to explain spurious variations caused by a faculae.}
 

### 2018-05-30 manuscript.tex
finished sect 4

@@
 
-\xavier{Fig.~\ref{fig:faculae} shows the barycentric variation of the CCF induced by a simulated equatorial faculae of size 3\% relative to the visible stellar hemisphere.
-We compare the barycentric variation as measured when fitting a Normal density and taking its mean (RV), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV).
-Although the different estimates for the RV present similar variation as a function of rotational phase, we note that SN mean RV present a smaller amplitude than the two others.}
+\xavier{To see the impact of a faculae on the different parameters of the CCF, we simulated the effect of an equatorial faculae of size 3\% relative to the visible stellar hemisphere.
+The faculae is face on when the phase equals to 0.
+Note that a 3\% faculae is relatively big for the Sun.
+At maximum activity, big faculae have generally a size of 1\%.
+In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and taking its mean (RV), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV).
+We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is slightly different with respect to the two others, with a maximum amplitude happening at a different phase.}
 
@@
 \xavier{In Fig.~\ref{fig:faculae.corr}, we compare the correlation between the different RV estimates and the different asymmetry or width estimates.
-As we can see, the strength of the correlation between $\gamma$ and SN mean RV is extremely similar to the correlation between BIS SPAN and the RV, with a Pearson correlation coefficient} \xavier{$R=-0.75$}.
-\xavier{Moreover, the correlation between $\gamma$ and SN median RV is much stronger, reaching} \xavier{$R=-0.95$}.
-\xavier{When comparing the correlation between the width and the different RV estimates, we observe that the data draw a circle, which implies a phase shift between those two parameters.
-In this case we find no correlation between those parameters, however, the different estimates gives very similar results.}
+As we can see, the strength of the correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are much stronger than the correlations between BIS SPAN and RV, with Pearson correlation coefficient $R$ values of 0.46, -0.67 and -0.09, respectively.
+Regarding the width barycenter correlations, we also find a stronger correlation between SN FWHM and SN mean RV compared to the one between FWHM and RV, $R=0.98$ and 0.84, respectively.
+In this case however, the correlation between SN FWHM and SN median RV is smaller with $R=0.50$.
+This first analysis shows that in the case of a faculae, using some parameters from the SN can lead to much stronger correlation than the usual Normal parameters and therefore, the SN parameters seems to be better
+
+probe better stellar activity.
+We will of course confirm this in the next sections presenting the case of a spot and of a spot plus a planet, but also in Sec~\ref{sec:4} when we will apply the SN fitting to real data sets.}
 
@@
 
-Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a faculae, \xavier{we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its efficient in in th ecase of a faculae.} The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
-\xavier{To modify with respect to the new results.
-It is straightforward noticing that the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the faculae.
-In particular the $R^{2}$ is extremely high regardless the fit that has been use (Normal or SN).
-We note also that the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) is not statistically significant to explain spurious variations caused by a faculae.}
+Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a faculae, \xavier{we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its efficiency in the case of a faculae.} The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
+It is straightforward to see that the proposed correction for \xavier{stellar activity is able to account for the majority of the activity signal created by a faculae, with a $R^2$ of our model larger than 0.95.
+In addition, the rms of the different estimates of the RV reduces from about 3 \ms before correction to values below 0.15 \ms after correction.
+We see a slightly smaller rms after correction for the SN parameters, however the different is not significant.
+When comparing the correction proposed in Eq.~\ref{eq:RV:correction} with what is generally used, i.e.
+a linear combination of the asymmetry and width parameter, we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2.
+Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that the intercept $\beta_0$ is only significant at a level of 1\% in the case of the Normal parameters, the coefficient $\beta_3$ that corresponds to the CCF width is only significant when using the SN parameters, and the coefficient $\beta_4$ that account for the interaction between the width and the asymmetry parameters is never significant.}
 
@@
 
-\umberto{Specify characteristic of the spot.}\xavier{}
-
-Fig.~\ref{fig:spot} shows the results obtained when a spot is present on the photosphere of the star.
-Similarly to the previous case, the presence of the spot leads to spurious variations in RV's for all the proposed indicators, but SN mean RV seems to have the smallest ones.
-We note however that in this case all the three indicators are similarly effected by the spurious changes in RV's caused by the spot.
-
-Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and respectively SN mean RV, SN median RV and RV.
-The correlation between $\gamma$ and SN median RV is equal to $-0.89$ while the correlation between $\gamma$ and SN median RV is equal to $-0.82$.
-Both these correlations are stronger than the correlation between the BIS SPAN and RV ($R^2=-0.77$).
-The correlations between the width of the CCF and the corresponding RV's are slightly stronger when fitting a SN rather than a Normal density, as shown in the left series of plots in Fig.~\ref{fig:spot.corr}.
-The results show anyway a correlation close to $0$ when focusing on the width of the CCF, suggesting that the presence of a spot on the photosphere of star leads to changes in the shape of the CCF rather than its width.
+\xavier{In this section, we simulate the effect on the CCF parameters of an equatorial spot of size 1\% relative to the visible stellar hemisphere.
+The spot is face on when the phase equals to 0.
+Note that this is an extremely big spot for the Sun, as in general big spots are more in the regime of 0.1\%.
+In Fig.~\ref{fig:spot}, we shows the barycentric variation of the CCF induced by this simulated spot.
+Contrary to the case of the faculae seen before, for the spots, all the different estimates of the CCF barycenter have exactly the same shape in variation.
+The amplitude for SN mean RV is however slightly smaller.}
+
+Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and the different estimates for the CCF barycenter: SN mean RV, SN median RV and RV.
+\xavier{The correlation between $\gamma$ and SN median RV is the strongest with a $R=0.94$, followed then by the correlation BIS SPAN -RV and $\gamma$-SN mean RV, with $R=0.86$.
+Regarding the correlation between the width and the CCF barycenter, we note that the variation is seen as a circle in this parameter space and therefore no correlation is observed.
+Once again, like in the case of the faculae, we see that some parameters of the SN gives stronger correlation than when using the Normal parameters.}
 
@@
 
-As before, we corrected the originally estimated set of RV's by using Eq.~\ref{eq:RV:correction}.
-The results of the correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the parameters involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:spot.test}.
-Also in this case the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the spot.
-The $R^{2}$ is extremely high regardless the fit that has been use (Normal or SN).
-The main differences respect to the previous case are that the parameter $\beta_{3}$, associated with $\gamma$, and the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM), are statistically significant to explain spurious variations caused by a spot.
-This information could be useful in the future for disentangle spots from facuale.
+As before, we corrected the originally RVs by using Eq.~\ref{eq:RV:correction}.
+The results of the correction are displayed in Fig.~\ref{fig:spot.correction}.
+Also in this case the proposed correction almost completely addresses the issue when considering the SN or Normal parameters, with values of $R^2$ larger than 0.98.
+\xavier{Looking at Fig.~\ref{fig:spot.correction}, we see that the activity correction proposed here is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms.
+In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however,} \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant.
+When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.
+
+In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summmurized in Table \ref{table:spot.test}, we observe that the intercept and $\beta_3$, corresponding to the width of the CCF, are useless to understand the variation seen in RVs.
+This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
+We see also that the ampltitude parameter, with coefficient $\beta_1$ is only useful to explain the RV variation of the spot in the case of the Normal distribution.}
 
@@
 
-The last presented simulation example consists in having not only spurious variations in RV's caused by the presence of a spot on the photosphere of the star but also a pure Doppler-shift because of an artificially injected planet.
-The purpose of this example is to check if we are able to disentangle the two different sources of variations in the set of RV's.
-
-Fig.~\ref{fig:spot.plus.planet} shows the results obtained when a spot is present on the photosphere of the star and a planet is injected.
-The planet, having an amplitude of 10 \ms, produces a pure Doppler-shift on the CCF, without further changing its shape.
-In this case N mean RV seems to have the largest variations caused by the combined action of spot and planet.
-%The evaluation of the standard errors leads to the same conclusions reported for the two previous cases: SN mean RV has the largest related uncertainties and the standard errors associates with SN median RV are $10 \%$ smaller than the standard errors derived for RV.
-
-Fig.~\ref{fig:spot.plus.planet.corr} shows the correlations between $\gamma$ and respectively SN mean RV and SN median RV and the correlation between BIS SPAN and RV.
-In this case the correlations are weaker than the ones derived when only a spot is present on the photosphere of the star.
-Anyway the $\gamma$ parameter shows a correlation with the median SN of $-0.433$, which is stronger than what the correlation between the other asymmetry indicators and their corresponding RVs.
-The correlations between the width of the CCF and the corresponding RV's are comparable and, similarly to the previous case, close to $0$.
+The last simulation presented consists in having a planetary signal influencing the CCF, in addition to the 1\% spot modeled before (see Sec.~\ref{sec:soap.spot}).
+\xavier{The purpose of this example is to check if we are able to disentangle as efficiently the two different sources of variations when using the parameters derived using a Normal, or a SN fit the the CCF.
+In this case, we inject a planet with an semi-amplitude of 10 \ms, with no eccentricity, and with a period corresponding to 1/3rd of the stellar rotational phase.}
+
+Fig.~\ref{fig:spot.plus.planet} shows the variation observed in the CCF barycenter parameters.
+Like in the case of the spot, all barycenter indicators show very similar variations, with SN mean RV showing a slightly smaller amplitude.
+
+In Fig.~\ref{fig:spot.plus.planet.corr}, we show the correlation between the different CCF parameters.
+\xavier{Except of seing smaller correlation than in the case of the spot, due to the fact that the planet induces changes in the CCF barycenter without any change in any of the width or asymmetry parameters, the correlation strengths between the asymmetry parameters and the CCF barycenter are in exactly the same order than in the case of the spot: $\gamma$--SN median RV $R=-0.84$, BIS SPAN-RV $R=-0.78$ and $\gamma$--SN mean RV $R=-0.76$.
+The variation seen in the width-CCF barycenter space draw a circle like in the case of a spot, therefore, no correlation is observed between those parameters.}
 
@@
 
-In order to correct the estimated set of RV's from spurious variations caused by the spot, we need to generalize Eq.~\ref{eq:RV:correction}, in order to consider also the possibly presence of an exoplanet.
-Hence, rather than just using Eq.~\ref{eq:RV:correction} we add the following keplerian function, which represents the pure Doppler-shift of the exoplanet under the assumption of circular orbit:
+In order to correct the RVs from the spurious variation caused by the spot, \xavier{we need to add to our model of activity correction, a signal to take into account the RV variation caused by the injected planet.
+The observed RV can therefore be modeled by a combination of the activity and the planet signal:}
+%
+\begin{equation}
+RV= RV_{\text{stellar activity}} + RV_{\text{planet}},
+\label{eq:RV:correction.overall}
+\end{equation}
+%
+\xavier{where $RV_{\text{stellar activity}}$ can be found in Eq.~\ref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case of no eccentricity, can be modelled by the following sinusoidal function:}
 %
@@
 %
-where the amplitude $K$, the orbital period $P$ and the epoch at the periapsis $t_{0}$ are three unknown parameters that define the presence of the exoplanet.
-Overall, the variations in RV's of the star can be defined as
-%
-\begin{equation}
-RV= RV_{\text{stellar activity}} + RV_{\text{exoplanet}}.
-\label{eq:RV:correction.overall}
-\end{equation}
-%
-
-We note that the p--value associated with the amplitude parameter $K$ is particularly relevant for rejecting or not rejecting the assumption about the presence of an orbiting companion.
+where the amplitude $K$, the orbital period $P$ and the epoch at the periapsis $t_{0}$ are three unknown parameters that define the planetary orbit.
+
+%We note that the p--value associated with the amplitude parameter $K$ is particularly relevant for rejecting or not rejecting the assumption about the presence of an orbiting companion.
 Moreover we note also that Eq.~\ref{eq:RV:correction.planet} is highly non linear, meaning that the estimation of all the parameters involved in Eq.~\ref{eq:RV:correction.overall} has to be done numerically.
@@
 We can see how in this case we are able to disentangle the spurious variations in RV's caused by stellar activity from the pure Doppler-shift due to the planet.
-The statistical tests conducted on the parameters, whose results are summarized in Table \ref{table:spotplanet.test}, are significant.
-We note in particular that the p--value associate to the amplitude parameter $K$ is $2e-16$.
-This result can be justify by the fact that the planet artificially injected has amplitude $K=10 \ms$.
-
+The statistical tests conducted on the parameters, whose results are summarized in Table \ref{table:spotplanet.test}, \xavier{shows that except for the width parameters with coefficient $\beta_3$, all the other are significantly useful to explain the RV variation induce by a spot plus a planet.}
 %\begin{figure*}[htbp]
@@
 
-In this Sec.\ref{sec:soap} we presented a first implementation of the SN fit to CCF, using the simulation environment SOAP.
+In this Sec.\ref{sec:soap}, we presented a first implementation of the SN fit to the CCF, using SOAP 2.0 to simulate noiseless CCF affected by stellar activity variation.
+
+\xavier{is all this discussion really usefull ?
 Before moving to real cases, where the analyses on five stars are presented, we need to provide further considerations.
-First of all, looking ad the analyses conducted with SOAP, it seems that the largest correlation between an asymmetry parameter and a set of RV's happens to be when respectively $\gamma$ and SN median RV are used.
+First of all, looking ad the analyses conducted with SOAP 2.0, it seems that the largest correlation between an asymmetry parameter and a set of RV's happens to be when respectively $\gamma$ and SN median RV are used.
 This is a bit surprising, since as the shape of the CCF changes, we expect SN median RV to be more robust than SN mean RV.
@@
 RV, FWHM and BIS SPAN) are systematically weaker than the correlations obtained by fitting the SN to the CCF, suggesting that this density could be helpful when searching for active regions.
-We recall moreover that all the quantities needed for conducting the analyses of the CCF are directly available by just fitting the SN.
+We recall moreover that all the quantities needed for conducting the analyses of the CCF are directly available by just fitting the SN.}
 
@@
 In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN density defined in Sec.
-\ref{sec:3} with the approach based on the Normal density.
-Other four stars have been analyzed with the proposed method and details can be found in the Appendix \ref{appendix}.
-For all the stars that have been considered in the present work, we selected those CCF's having SNR larger than 10.
-
- A comparison with the results obtained by the classic approach is done, where the RV's of the star are estimated by retrieving the mean of the Normal density used to fit the CCF, along with the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}.
+\ref{sec:3} with the approach based on fitting a Normal density to retrieve the RV and width of the CCF and calculating the bisector to derive the asymmetry parameter BIS SPAN.
+Four other stars have been analyzed with the proposed method and details can be found in the Appendix \ref{appendix}.
+For all the stars that have been considered in the present work, \xavier{we selected CCFs  that were derived from spectra that had a SNR at 550 nm larger than 10.}
+
+% A comparison with the results obtained by the classic approach is done, where the RV is estimated by retrieving the mean of the Normal density used to fit the CCF, along with the FWHM of the Normal density and the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}.
 The latter parameters are calculated separately from the Normal fit that leads to the set of RV's of the star.
@@
 
-A total of $1808$ CCF's measured in $2010$ have been analysed from the star Alpha Centauri B.
-Several measurement in 2010 are contaminated by light from Alpha Centauri A.
-To remove contaminated spectra and thus CCF's, we performed the same selection as presented in \citet{Dumusque-2012}.
-Moreover, as noted in \citet{Dumusque-2012} and \citet{Thompson-2017}, this dataset presents a strong stellar activity signal.
+We analysed the $1808$ RV observations of Alpha Centauri B taken in 2010 by the HARPS spectrograph.
+Note that more observation have been done during this year, however we selected here only the data that are not significantly affected by contamination from Alpha Cen A \citep[see][]{Dumusque-2012}.
+\xavier{We choose these observations as their represent probably the best sampled and most precise RV data set showing a strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.}
 
 We begin the analyses by evaluating the correlation between $\gamma$ and the BIS SPAN.
-In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.72$ and a strong Pearson correlation coefficient of $0.954$.
-This comparison is useful because $\gamma$ is an adimensional parameter taking information about the asymmetry of the SN while the BIS SPAN, beyond this, has got unit of measure of \kms.
-In other words, by using Fig.~\ref{fig:alphacent:corr.gamma}, it is possible to provide a physical meaning to $\gamma$.
+\xavier{As $\gamma$ has no units, this will allow us to compare the amplitude of the activity signals seen in $\gamma$ and in BIS SPAN, by using the slope of this correlation as a scaling factor}.
+In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.72$ and a strong Pearson correlation coefficient of $R=0.95$.
 %
@@
 
-Fig.~\ref{fig:alphacent:diff:RV} shows the comparison between the RV's retrieved using the SN shape and the ones obtained with the Normal shape.
+Fig.~\ref{fig:alphacent:diff:RV} shows the comparison between the RVs retrieved using the SN density and the ones obtained with the Normal density.
 It is possible to appreciate the presence of a strong stellar activity signal, as expected \citep{Dumusque-2012,Thompson-2017}.

### 2018-05-30 manuscript.tex
curated section 5 (not finished) and formated the paper in A&A style

@@
-\documentclass[11pt, oneside]{article}   
-\usepackage{geometry}                		
-\geometry{letterpaper}                   		
-\usepackage{graphicx}
-
-\usepackage{amssymb}
-\usepackage{amsmath}
+\documentclass{aa}
+%\documentclass[referee]{aa}
 \usepackage{natbib}
-\bibliographystyle{abbrvnat}
-\usepackage{aas_macros} % AAS journal abbreviations
-
-\usepackage{lscape}
-%\usepackage{pdflscape} % or {lscape}
+%\usepackage{lscape}
+\usepackage{pdflscape} % or {lscape}
 \usepackage{wasysym}
@@
 \usepackage{longtable}
+
 \usepackage{afterpage}
+
 \usepackage[usenames,dvipsnames]{color}
@@
 \newcommand{\umberto}[1]{{\color{green}[[\textbf{Umberto: }#1]]}}
-\newcommand{\comment}[1]{{\color{red}[[\textbf{Referee: }#1]]}}
+%\newcommand{\comment}[1]{{\color{red}[[\textbf{Referee: }#1]]}}
 \newcommand{\todo}[1]{{\color{cyan}[[\textbf{TODO: }#1]]}}
 
-\title{Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density}
-%\thanks{Based on observations collected at the La Silla Parana Observatory,
-%ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}}
-
-%\subtitle{II. First results of the analysis of the data set}
-
-\author{U. Simola
-	    \and X. Dumusque
-	    \and Jessi Cisewski-Kehe
+\begin{document}
+
+\title{Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density
+\thanks{Based on observations collected at the La Silla Parana Observatory,
+ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}}
+
+\author{U. Simola \inst{1,2}
+	    \thanks{\email{umberto.simola@yale.edu}}
+	    \and X. Dumusque\inst{3}
+	    \thanks{Branco Weiss Fellow--Society in Science (url: \url{http://www.society-in-science.org})}    
+	    \and Jessi Cisewski\inst{2}
 	    }
 
-%\author{U. Simola \inst{1,2}
-%	    \thanks{\email{umberto.simola@yale.edu}}
-%	    \and X. Dumusque\inst{3}
-%	    \thanks{Society in Science -- Branco Weiss Fellow (url: \url{http://www.society-in-science.org})}    
-%	    \and Jessi Cisewski\inst{2}
-%	    }
-%
-%\institute{Department of Mathematic and Statistics, University of Helsinki, Helsinki, Finland
-%	      \and Department of Statistics and Data Science, Yale University, New Haven, CT, USA
-%	      \and Observatoire de Gen\`eve, Universit\'e de Gen\`eve, 51 ch. des Maillettes, CH-1290 Versoix, Switzerland 
-%	      }
-
-\begin{document}
-\maketitle
-
-%\abstract
-{\bf Abstract}\\
+\institute{Department of Statistical Sciences, University of Padua, Padua, Italy
+	      \and Department of Statistics and Data Science, Yale University, New Haven, CT, USA
+	      \and Observatoire de Gen\`eve, Universit\'e de Gen\`eve, 51 ch. des Maillettes, CH-1290 Versoix, Switzerland 
+	      }
+
+\date{Received XXX; accepted XXX}
+
+\abstract
 % Context, Aims, Methods, Results, Conclu (not mandatory)
-Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
+{Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
 Stellar activity can be probed by measuring time dependant variations in the shape of the cross-correlation function (CCF), often estimated using the different moments of the modelled CCF.
-Therefore estimating the moments of the CCF with high precision is essential to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.
-%
-We propose to estimate the moments of the CCF by fitting a model using a Skew Normal (SN) density shape, which unlike the commonly employed Normal density, \xavier{includes an skewness parameter to capture the asymmetry of the CCF induced by stellar activity, but also the natural asymmetry induced by convective blueshift.}
-%
-The performance of the proposed method is compared to the Normal density using both simulated and real observations with varying levels of activity and signal-to-noise ratio (SNR) levels.
+Therefore estimating the moments of the CCF with high precision is essential to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.}
+%
+{We propose to estimate the moments of the CCF by fitting a model using a Skew Normal (SN) density shape, which unlike the commonly employed Normal density, \xavier{includes an skewness parameter to capture the asymmetry of the CCF induced by stellar activity, but also the natural asymmetry induced by convective blueshift.}}
+%
+{The performance of the proposed method is compared to the Normal density using both simulated and real observations with varying levels of activity and signal-to-noise ratio (SNR) levels.}
 %We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (SNR) levels.
@@
 %
-When considering the real observations, the correlation between the RV's and the asymmetry of the CCF and the correlation between the RV's and the width of the CCF are stronger when using the parameters derived from the SN than the Normal approach.
+{When considering the real observations, the correlation between the RV's and the asymmetry of the CCF and the correlation between the RV's and the width of the CCF are stronger when using the parameters derived from the SN than the Normal approach.
 This suggests that the CCF asymmetry and the CCF width derived using a SN may be more sensitive to stellar activity, which can be helpful with estimating stellar rotational periods and generally characterizing the stellar activity signals.
-%
 The estimated uncertainties in the estimated RV's using the proposed SN approach are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal, and the estimated uncertainties on the SN asymmetry parameter are on average $15\%$ smaller than the commonly used Bisector Inverse Slope Span (BIS SPAN) approach for estimating the asymmetry of the CCF.
-%
-The derived benefits of using the proposed SN approach includes an asymmetry parameter along with several options for estimating the RV, while the Normal model only includes an RV estimate and requires a separate procedure for estimating the asymmetry.
-Furthermore, the estimated uncertainties on the RV's and the asymmetry parameter are smaller in the SN setting.
+}
+%
+%{The derived benefits of using the proposed SN approach includes an asymmetry parameter along with several options for estimating the RV, while the Normal model only includes an RV estimate and requires a separate procedure for estimating the asymmetry.
+Furthermore, the estimated uncertainties on the RV's and the asymmetry parameter are smaller in the SN setting.}
 %The correlation between the RV's and the asymmetry of the CCF and the correlation between the RV's and the width of the CCF are always stronger when using the parameters derived from the SN in the case of real observations.
@@
 
-%\keywords{techniques: radial velocities -- planetary systems -- stars: activity -- methods: data analysis}
-
+\keywords{techniques: radial velocities -- planetary systems -- stars: activity -- methods: data analysis}
+
+\titlerunning{Fitting a SN distribution to CCF}
+\authorrunning{U. Simola, X. Dumusque and J. Cisewski}
+\maketitle
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
 \section{Introduction} \label{intro}
@@
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-\section{Radial Velocity correction function for stellar activity} \label{sec:31}
+\section{Radial Velocity correction for stellar activity} \label{sec:31}
 
@@
 
-\subsection{Alpha Centauri B} \label{sec:alphacentb}
-
-We analysed the $1808$ RV observations of Alpha Centauri B taken in 2010 by the HARPS spectrograph.
-Note that more observation have been done during this year, however we selected here only the data that are not significantly affected by contamination from Alpha Cen A \citep[see][]{Dumusque-2012}.
+\subsection{Comparison between the different CCF parameters derived with the Normal and the Skew Normal density} \label{sec:alphacentb}
+
+We analysed the $1808$ CCFs derived from spectra of Alpha Centauri B taken in 2010 by the HARPS spectrograph.
+Note that more observations have been done during this year, however we selected here only the data that are not significantly affected by contamination from Alpha Cen A \citep[see][]{Dumusque-2012}.
 \xavier{We choose these observations as their represent probably the best sampled and most precise RV data set showing a strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.}
@@
 We begin the analyses by evaluating the correlation between $\gamma$ and the BIS SPAN. 
-\xavier{As $\gamma$ has no units, this will allow us to compare the amplitude of the activity signals seen in $\gamma$ and in BIS SPAN, by using the slope of this correlation as a scaling factor}.
-In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.72$ and a strong Pearson correlation coefficient of $R=0.95$.
-%
-\begin{figure}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD12862_[2]gamma_vs_bisspan.pdf} 
-   \caption{Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
-Because $\gamma$ is adimensional, retrieving the slope between $\gamma$ and the BIS SPAN, which is expressed in \kms, allows us to provide physical meaning to $\gamma$.}
+In the left panel of Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.72$ and a strong Pearson correlation coefficient of $R=0.95$.
+This strong correlation shows that $\gamma$ and BIS SPAN are measuring in a very similar way the CCF asymmetry.
+\xavier{This strong correlation allows as well to convert the dimensionless $\gamma$ parameters in \ms to compare it with BIS SPAN using the slope of the correlation, in this case 720 \ms.}
+%\xavier{As $\gamma$ has no units, this will allow us to compare the amplitude of the activity signal seen in $\gamma$ and in BIS SPAN, by using the slope of this correlation as a scaling factor}.
+
+%
+\begin{figure*}[htbp]
+   \centering
+\includegraphics[height = 3.55in]{HD12862_[2]gamma_vs_bisspan.pdf} 
+\includegraphics[height = 3.65in]{HD12862_[2]RadialVelocityDifferences.pdf} 
+   \caption{\emph{Left: }Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
+As we can see with the strong correlation, those two parameters measure the CCF asymmetry in the same way.
+\emph{Top right:} RVs as function of Julian Day for Alpha Centauri b in 2010.
+The RVs are retrieved using the mean of a Normal fitted to the CCF (red triangles), or the mean (black circles) or median (cyan crosses) of a SN density fitted to the CCF.
+\emph{Bottom right:} RV differences between the RV derived when using the SN density and the RV derived when using the Normal density.}
    \label{fig:alphacent:corr.gamma}
-\end{figure}
-%
-
-Fig.~\ref{fig:alphacent:diff:RV} shows the comparison between the RVs retrieved using the SN density and the ones obtained with the Normal density.
-It is possible to appreciate the presence of a strong stellar activity signal, as expected \citep{Dumusque-2012,Thompson-2017}.
-When using SN mean RV, it is possible to observe more variations than the ones measured by the Normal fitting.
+\end{figure*}
+%
+
+In the right of Fig.~\ref{fig:alphacent:corr.gamma}, we show the comparison between the RVs retrieved using the SN density and the ones obtained with the Normal density.
+\xavier{We clearly see that the amplitude of the activity signal is stronger when using SN mean RV, and the signal measured using N mean RV or SN median RV are very similar.
+We observe the same behavior in the case of a faculae (see Sec.~\ref{sec:soap.faculae}) and therefore it seems that the activity signal seen in those data are more likely affected by faculae.
+This is an observation that was already made in \citet{Dumusque-2014c}.}
+%When using SN mean RV, it is possible to observe more variations than the ones measured by the Normal fitting.
 This happens because the mean of the SN is more sensitive to stellar activity.
@@
 Both indicators can be used to capture and summarise the different information available in the CCF, as will be shown in the remainder of this work.
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
-   \caption{(top) RV's as function of Julian Day for Alpha Centauri b.
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{HD12862_[2]RadialVelocityDifferences.pdf} 
+%   \caption{(top) RV's as function of Julian Day for Alpha Centauri b.
 The RV's are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses).
 (bottom) RV differences between Normal RV and SN mean RV (black circles) and between Normal RV and a SN median RV (cyan crosses).}
-   \label{fig:alphacent:diff:RV}
-\end{figure*}
-%
-
-Similar to \citet{Figueira-2013}, we compare the correlation between the different activity indicators and the RV's of the star in Fig.~\ref{fig:alphacent:corrPlot}.
-The correlation between $\gamma$ and SN mean RV and the correlation between $\gamma$ and SN median RV are much stronger than the correlations calculated between the other asymmetry parameters and their corresponding RV's.
-In particular the correlation between $\gamma$ and SN mean RV is almost twice the correlation between the other asymmetry parameters and their corresponding RV's.
-
-Because the median is a more robust index than the mean, the correlation between $\gamma$ and SN median RV is not as large as the correlation between $\gamma$ and SN mean RV, but it is nonetheless $1.5$ times larger than the correlation between the other common asymmetry parameters and their corresponding RV's.
+%   \label{fig:alphacent:diff:RV}
+%\end{figure*}
+%
+
+\xavier{Similar to what is done in Sec.~\ref{sec:soap}, we compare the correlation between the asymmetry or the width parameters of the CCF and the RV, i.e.
+the CCF barycenter, in Fig.~\ref{fig:alphacent:corrPlot}.
+In addition to what is done in Sec.~\ref{sec:soap}, we add the asymmetry parameters derived in \citet{Boisse-2011}, $V_{span}$ and in \citet{Figueira-2013}, BIS-, BIS+, Bi Gauss and $V_{asy}$, as these authors found those asymmetry parameters more correlated to the RVs than BIS SPAN.
+It is clear in the case of Alpha Cen B, but also in the four other stars presented in Appendix \ref{appendix}, that the correlation found between $\gamma$ and SN mean RV is always the strongest.
+On alpha Cen B, the Pearson correlation coefficient reaches a value of $R=0.74$, while it reaches at best $R=-0.42$ for all the other asymmetry-RV correlations not derived using the SN density fit.
+When looking at the width-RV correlation, once again, the correlation between SN FWHM and SN mean RV is the strongest for all the stars, except for the quietest star of all five, HD10700, for which the Pearson correlation coefficient 0.53 for the Normal parameters and 0.42 for the SN parameters.
+This analysis shows that the parameters derived when using a SN density are more sensitive the stellar activity, and therefore using those parameters can lead to the detection of stellar activity, when the Normal parameters do not detect anything (see the Appendix \ref{appendix} the case of the the asymmetry-RV correlation for HD10700, HD215152, Corot-7, and the width-RV correlation for HD215152)}
+
+%The correlations between $\gamma$ and SN mean RV, and also SN FWHM and SN mean RV
+
+%Because the median is a more robust index than the mean, the correlation between $\gamma$ and SN median RV is not as large as the correlation between $\gamma$ and SN mean RV, but it is nonetheless $1.5$ times larger than the correlation between the other common asymmetry parameters and their corresponding RV's.
 In other words, changes in the asymmetry of the CCF are better captured when using the SN mean RV.
@@
 \ref{sec:soap}, we could infer that Alpha Centauri b is dominated by faculae, because the correlations between the RV's and the width of the CCF are strong (in particular the correlation between SN mean RV and SN FWHM is $0.817$).
-%
+%%
 \begin{figure*}[htbp]
@@
 
-Using Eq.
-\ref{eq:RV:correction}, we provide a new set of RV's corrected from stellar activity.
-The results are shown in Figure ~\ref{fig:alphacent:correctionRV}.
-We see that, once corrected for stellar activity, the residuals in the Normal and SN analysis are comparable.
+\xavier{In Fig \ref{fig:alphacent:correctionRV}, we study the efficiency of the stellar activity correction proposed in Sec.~\ref{sec:31}.
+The first observation is that the RV measured with SN mean RV presents a rms 35\% larger than the RV measured when fitting a Normal density.
+In the case of SN median RV, we see as well a larger RV rms, however this one is only 9\% larger.
+Even though we see those differences in RV, once we correct for the stellar activity using Eq.~\ref{eq:RV:correction}, we find the same RV residuals rms.
+In the best case, for SN mean RV, we reduce the stellar activity signal by a factor of 2, while in the worst case, N mean RV, only a factor 1.5.
+Therefore, although it seems that the parameters derived using the SN density are more sensitive to stellar activity, we are not able to correct better for stellar activity signal using a linear combination of the different CCF parameters.}
+
+\xavier{ To rediscuss with the new values.
 However, we note that when using SN mean RV, the correction is more important.
@@
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Doppler-shift added to Alpha Centauri B} \label{sec:soap_real}
+\subsection{Detection limits when using the RV derived with the Normal or the Skew Normal density} \label{sec:soap_real}
 
@@
 We are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
-XD is grateful to the Society in Science--The Branco Weiss Fellowship for its financial support.
+XD is grateful to The Branco Weiss Fellowship--Society in Science for its financial support.
 

### 2018-05-30 manuscript.tex
Section 5 finished

@@
 
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 2.5in]{RV_comparison_FACULAE.pdf} 
+\begin{figure}[htbp]
+   \centering
+\includegraphics[width=3.6in]{RV_comparison_FACULAE.pdf} 
 %\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
@@
     \label{fig:faculae}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 2.5in]{RV_comparison_SPOT.pdf} 
+\begin{figure}[htbp]
+   \centering
+\includegraphics[width=3.6in]{RV_comparison_SPOT.pdf} 
 %\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
@@
     \label{fig:spot}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 2.5in]{RV_comparison_SPOT_PLANET.pdf} 
+\begin{figure}[htbp]
+   \centering
+\includegraphics[width = 3.6in]{RV_comparison_SPOT_PLANET.pdf} 
 %\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
@@
     \label{fig:spot.plus.planet}
-\end{figure*}
+\end{figure}
 
@@
 
-\xavier{ To rediscuss with the new values.
-However, we note that when using SN mean RV, the correction is more important.
-In fact, the comparison of $R^2$ shows that the SN fit accounts for a higher percentage of variability caused by stellar activity (i.e.
-spurious variations in RV's).
-We note also that the BIS SPAN is not helpful to address part of the spurious variability caused by stellar activity, while the opposite conclusion has reached when evaluating the p-value related to $\gamma$.
-
-\begin{figure} 
+\xavier{When looking at the significance of the different parameters in the activity correction in Table~\ref{table:alphacent.test}, we see that the intercept is not significant for any of the correction, and BIS SPAN, with coefficient $\beta_2$, is not useful to explain stellar activity when using the parameters derived from the Normal density fit.
+However all the other parameters in the Normal and SN case are useful.
+By analyzing the value for $R^2$, we see that the correction is more efficient at explaining stellar activity when considering for the CCF barycenter SN mean RV.
+This is expected from the results above since for the three different cases, we arrive to the same RV residual rms after correction, but before correction SN mean RV shows the largest RV rms.}
+
+\begin{figure*} 
    \centering
@@
    \label{fig:alphacent:correctionRV}
-\end{figure}
+\end{figure*}
 
@@
 
-Both the proposed indicators coming from the SN density have advantages and limits: SN mean RV better catches changes in the asymmetry of the CCF but the resulting set of RV's ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Sec.
+%Both the proposed indicators coming from the SN density have advantages and limits: SN mean RV better catches changes in the asymmetry of the CCF but the resulting set of RV's ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Sec.
 \ref{intro}.
@@
 
-We also consider a real-data example using HARPS spectra from the star Alpha Centauri B with an imputed Doppler-shift added...
-
-\umberto{to be done}\xavier{to plot K vs P for Normal, SN mean, SN median}
-
-In the next Section we further motivate the reasons to define the RV's derived by the CCF by calculating SN median RV.
-In order to do that, we retrieve the standard errors associated with SN mean RV, SN median RV and RV.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\xavier{In the preceding section, we saw that the RV measured when considering a SN or a Normal density present different amplitudes, mainly in the case of SN mean RV.
+However, when correcting for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, it seems that we are able to reach the same RV precision.
+In this section, we want to investigate if for some of the three different RV definitions presented in this paper, it is easier or more difficult to detect planetary signals when considering stellar activity.
+To do so, we estimated what would be the minimum amplitude of a planetray signal we could detect at different orbital periods.
+
+To get CCF affected by realistic stellar activity signals, we took the ones from Alpha Cen B used in the preceding section.
+To simulate a planetary signal, when then blue- or red-shifted those CCF with the wanted amplitude, period and phase.
+
+We first simulated several RV data sets, with always the same stellar signal, but injecting planets with parameters corresponding to the following grid:
+\begin{itemize}
+\item period of 3, 5, 7, 9, 11, 15, 20 , 25 and 30 days,
+\item amplitude from 0.5 to 3 \ms\, by steps of 0.05\,\ms,
+\item 10 different phases, evenly sampled between 0 and 2$\pi$.
+\end{itemize}
+
+For each simulation, 4500 in total, we applied the activity correction presented in Eq.~\ref{eq:RV:correction} and look for signals in the residuals using a Generalized Lomb-Scargle periodogram \citep[GLS][]{Zechmeister-2009}.
+If a signal with a p--value\footnote{estimated by bootstrap} smaller than 1\% had a period compatible with the injected planetary period considering an error of 20\%, we were estimating this signal as significant, and therefore the corresponding planet as detected.
+
+Finally, for each period, we searched for the minimum amplitude for which at least 50\% of the planets with different phases were detected.
+The results are shown in Fig.~\ref{fig:detection_limits.pdf}.
+As we can see, all the different RV estimates gives extremely similar detection limits.
+Therefore, we can use any of these estimates when searching for planetary signal in RV data contaminated by stellar activity.
+
+Although the detection limits stay constant for nearly all the periods, we see that for 30 days, we have a huge increase for all the RV estimates.
+This is because the planet period is close to the rotation period of the star \citep[36.7 days,][]{Dumusque-2012}, and therefore close to the semi-periodicity of the stellar activity signal.
+In such a case, the activity correction absorbs part of the planetary signal.
+We thus need to inject a much stronger planetary signal at this period if we want to detect it.}
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
 \section{Estimation of standard errors for the CCF parameters} \label{sec:5}
 
-In this Section, we perform a bootstrap analysis \citep{davison1997bootstrap, efron1994introduction} in order to retrieve the standard errors associated to SN mean RV, SN median RV, RV, SN FWHM, FWHM, $\gamma$ and BIS SPAN.
+\xavier{In this section, Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
+Therefore, we cannot simply shuffle each point in the CCF with their respective error bar and then recalculate the best SN or Normal density fit, to see how the noise of the CCF influence the noise on the parameters derived from the CCF.
+We therefore decided to start with the spectrum, for which we know that each points are totally independent of the others.
+The standard error on each point is given by the photon noise, which follows a Poisson law and is therefore the square root of the measured flux.}
+
+In this Section, we perform a bootstrap analysis \citep[e.g.][]{davison1997bootstrap, efron1994introduction} in order to retrieve the standard errors associated to SN mean RV, SN median RV, RV, SN FWHM, FWHM, $\gamma$ and BIS SPAN.
 Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.

### 2018-05-31 manuscript.tex
umberto: comment Section 4
added right table with new SOAP2.0 data

@@
 \author{U. Simola \inst{1,2}
-	    \thanks{\email{umberto.simola@yale.edu}}
+	    \thanks{\email{umberto.simola@helsinki.fi}}
 	    \and X. Dumusque\inst{3}
@@
    \centering
-\includegraphics[height = 3in]{Skew_Normal_densities_jjck.pdf} 
+\includegraphics[height = 2.3in]{Skew_Normal_densities_jjck.pdf} 
    \caption{Density function of a random variable Y following the SN distribution $SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
@@
 a linear combination of the asymmetry and width parameter, we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2.
-Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that the intercept $\beta_0$ is only significant at a level of 1\% in the case of the Normal parameters, the coefficient $\beta_3$ that corresponds to the CCF width is only significant when using the SN parameters, and the coefficient $\beta_4$ that account for the interaction between the width and the asymmetry parameters is never significant.}
+Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that the \umberto{parameter related to the} intercept, $\beta_0$, is only significant at a level of 1\% in the case of the Normal parameters \umberto{or when SN median RV is used}.}
 
@@
 \includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
-Once corrected for stellar activity the residuals do not show a systematic component.}
+   \caption{\umberto{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity.
+The new correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
+Once corrected for stellar activity using the proposed linear function (black dots), the residuals present a smaller systematic component if compared with the residuals obtained with the usual correction (blue triangles).}}
     \label{fig:faculae.correction}
@@
 \hline
-Parameter          & RV         &   SN mean RV &   SN median RV \\
-\hline
-$\beta_{0}$            &    $0.0016$    & $0.26$ & $0.60$ \\
-\hline
-$\beta_{1}$            &    $3.75e-05$    & $0.0068$ & $0.0069$ \\
-\hline
-$\beta_{2}$            &     $7.79e-16$   &  $1.97e-05$ & $3.69e-08$\\
-\hline
-$\beta_{3}$            &     $0.25$   &  $0.0011$ & $0.0011$\\
-\hline
-$\beta_{4}$            &     $0.53$   &  $0.21$ & $0.21$\\
-\hline
-$R^{2}$      &     $0.9967$    &  $0.9571$ & $0.977$  \\
+Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
+\hline
+$\beta_{0}$            &    $0.033$    & $0.00020$ & $0.61$ \\
+\hline
+$\beta_{1}$            &    $2.22e-16 $    & $2.22e-16 $ & $2.22e-16 $ \\
+\hline
+$\beta_{2}$            &     $0.0034$   &  $2.22e-16 $ & $2.22e-16 $\\
+\hline
+$\beta_{3}$            &     $0.00016$   &  $1.091e-6$ & $9.75e-7$\\
+\hline
+$\beta_{4}$            &     $2.22e-16$   &  $2.22e-16$ & $2.22e-16$\\
+\hline
+$R^{2}$      &     $0.9978$    &  $0.9985$ & $0.9981$  \\
 \hline
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a faculae, according to Eq.~\ref{eq:RV:correction}.
-Beyond the contrast parameter A and the asymmetry parameter of the CCF which are useful for both the analyses, the width of the CCF is statistically useful to explain spurious variations in RV's caused by a faculae only for the SN analyses.
-The term of interaction between the asymmetry and the width of the CCF is not helpful to explain part of the variability in the set of RV's.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}
+\caption{\umberto{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a \textbf{faculae}, according to Eq.~\ref{eq:RV:correction}.
+All the variables, except the intercept when the independent variable is SN median RV, are statistically useful to explain spurious variations in RV's caused by a faculae only for the SN analyses.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}}
 \label{table:faculae.test}
@@
 
-As before, we corrected the originally RVs by using Eq.~\ref{eq:RV:correction}.
+As before, we corrected the originally RV's by using Eq.~\ref{eq:RV:correction}.
 The results of the correction are displayed in Fig.~\ref{fig:spot.correction}.
-Also in this case the proposed correction almost completely addresses the issue when considering the SN or Normal parameters, with values of $R^2$ larger than 0.98.
+Also in this case the proposed correction almost completely addresses the issue when considering the SN or Normal parameters, with values of $R^2$ larger than 0.99.
 \xavier{Looking at Fig.~\ref{fig:spot.correction}, we see that the activity correction proposed here is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms.
@@
 
-In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summmurized in Table \ref{table:spot.test}, we observe that the intercept and $\beta_3$, corresponding to the width of the CCF, are useless to understand the variation seen in RVs.
+In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summmurized in Table \ref{table:spot.test}, \umberto{we observe that the $\beta_0$, and $\beta_3$, corresponding respectively to the intercept and to the width of the CCF}, are \umberto{not helpful} to understand the variation measured in RV's.
 This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
@@
 \includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
-Once corrected for stellar activity the residuals do not show a systematic component.}
+   \caption{\umberto{Set of  spurious variations in RV's caused by a \textbf{spot} using a Normal and a SN fit before and once corrected from stellar activity.
+The new correction has done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
+Once corrected for stellar activity using the proposed linear function (black dots), the residuals present a smaller systematic component if compared with the residuals obtained with the usual correction (blue triangles).}}
     \label{fig:spot.correction}
@@
 \hline
-Parameter          & RV         &   SN mean RV &   SN median RV \\
-\hline
-$\beta_{0}$            &    $0.47$    & $0.84$ & $0.81$ \\
-\hline
-$\beta_{1}$            &    $0.00035$    & $0.064$ & $0.064$ \\
+Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
+\hline
+$\beta_{0}$            &    $0.4975$    & $0.21$ & $0.21$ \\
+\hline
+$\beta_{1}$            &    $2e-16$    & $2e-16$ & $2e-16$ \\
 \hline
@@
 \hline
-$\beta_{3}$            &     $0.53$   &  $0.61$ & $0.61$\\
-\hline
-$\beta_{4}$            &     $1.11e-07 $   &  $2.85e-08 $ & $ 2.87e-08 $\\
-\hline
-$R^{2}$      &     $0.9897$    &  $0.9914$ & $0.9929$  \\
+$\beta_{3}$            &     $0.017$   &  $0.13$ & $0.11$\\
+\hline
+$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
+\hline
+$R^{2}$      &     $0.9959$    &  $0.9936$ & $0.9952$  \\
 \hline
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\ref{eq:RV:correction}.
-All the covariates are statistically useful to explain the variability in RV's causued by a spot except the intercept and the width of the CCF.
-Concerning the SN analysis, the contrast parameter A is not statistically significant at level $5\%$.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}
+\caption{\umberto{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\ref{eq:RV:correction}.
+All the covariates are statistically useful to explain the variability in RV's caused by a spot, except the intercept and the width of the CCF.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}}
 \label{table:spot.test}
@@
 
-In order to correct the RVs from the spurious variation caused by the spot, \xavier{we need to add to our model of activity correction, a signal to take into account the RV variation caused by the injected planet.
+In order to correct the RV's from the spurious variation caused by the spot, \xavier{we need to add to our model of activity correction, a signal to take into account the RV variation caused by the injected planet.
 The observed RV can therefore be modeled by a combination of the activity and the planet signal:}
@@
 \hline
-Parameter          & RV         &   SN mean RV &   SN median RV \\
-\hline
-$\beta_{0}$            &    $7.09e-09$    & $ 3.44e-07$  & $4.96e-09$ \\
-\hline
-$\beta_{1}$            &    $0.00105$    & $0.0052$  & $0.0052$ \\
-\hline
-$\beta_{2}$            &     $2e-16$   & $2.43e-16$ & $2e-16$\\
-\hline
-$\beta_{3}$            &     $0.79$   &  $0.22$  & $0.22$\\
-\hline
-$\beta_{4}$            &     $6.73e-07$   &  $7.78e-06$ & $7.82e-06$\\
-\hline
-K            &     $2e-16$   &  $2e-16$   & $ 2e-16 $\\
-\hline
-P            &     $2e-16$   &  $2e-16$ & $2e-16 $\\
-\hline
-$t_{0}$            &     $2e-16$   &  $2e-16$ & $2e-16 $\\
-\hline
-$\text{Residuals}$      &     $0.61 \ms$    &  $ 0.60 \ms$ & $0.60 \ms$  \\
+Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
+\hline
+$\beta_{0}$            &    $0.00063$    & $2e-16$  & $1.42e-09$ \\
+\hline
+$\beta_{1}$            &    $2e-16$    & $2e-16$  & $2e-16$ \\
+\hline
+$\beta_{2}$            &     $2e-16$   & $2e-16$ & $2e-16$\\
+\hline
+$\beta_{3}$            &     $0.067$   &  $0.40$  & $0.38$\\
+\hline
+$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
+\hline
+K            &     $2e-16$   &  $2e-16$   & $2e-16$ \\
+\hline
+P            &     $2e-16$   &  $2e-16$ & $2e-16$ \\
+\hline
+$t_{0}$            &     $2e-16$   &  $2e-16$ & $2e-16$ \\
+\hline
+$\text{Residuals}$      &     $0.71 \ms$    &  $ 0.66 \ms$ & $0.70 \ms$  \\
 \hline
@@
 In this Sec.\ref{sec:soap}, we presented a first implementation of the SN fit to the CCF, using SOAP 2.0 to simulate noiseless CCF affected by stellar activity variation.
+
+\umberto{Do we need to point out the following: \\ If we look at the $R^2$, the proposed function that corrects from stellar activity addresses (almost) all the spurious variations caused in RV's by active regions.
+Anyway, if we look the residuals, a systematic component is still present, although smaller respect the residual obtained with the usual correction.
+The residuals are supposed to be homoscedastic with 0 mean under the assumption that the model is correct.
+Therefore, since our $R^2$ is always close to $1$, we can argue, as we discussed already many times, that the CCF does not follow a normal fit, neither a SN one, otherwise, given our extremely high $R^2$ we should have gotten homoscedastic 0 mean residuals.}
 

### 2018-05-31 manuscript.tex
Modifying Section 6

--- 2018-05-30 manuscript.tex
@@
 \begin{figure}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 3in]{Skew_Normal_densities_jjck.pdf} 
@@
    \label{fig:SN.plot}
+\end{center}
 \end{figure}
@@
 \begin{table}[htbp]
-   \centering
+\begin{center}
    %\topcaption{Table captions are better up top} % requires the topcapt package
@@
    \label{tab:cp_values}
+\end{center}
 \end{table}
@@
 \begin{figure}[htbp]
-   \centering
+\begin{center}
 \includegraphics[width=3.6in]{RV_comparison_FACULAE.pdf} 
@@
     \label{fig:faculae}
+\end{center}
 \end{figure}
@@
 \begin{figure*}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
@@
     \label{fig:faculae.corr}
+\end{center}
 \end{figure*}
@@
 \begin{figure*}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
@@
     \label{fig:faculae.correction}
+\end{center}
 \end{figure*}
@@
 \begin{figure}[htbp]
-   \centering
+\begin{center}
 \includegraphics[width=3.6in]{RV_comparison_SPOT.pdf} 
@@
     \label{fig:spot}
+\end{center}
 \end{figure}
@@
 \begin{figure*}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{SOAP_SPOT_Comparison_para_SN.pdf} 
@@
     \label{fig:spot.corr}
+\end{center}
 \end{figure*}
@@
 \begin{figure}[htbp]
-   \centering
+\begin{center}
 \includegraphics[width = 3.6in]{RV_comparison_SPOT_PLANET.pdf} 
@@
     \label{fig:spot.plus.planet}
+\end{center}
 \end{figure}
@@
 \begin{figure*}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{SOAP_SPOT_PLANET_Comparison_para_SN.pdf} 
@@
     \label{fig:spot.plus.planet.corr}
+\end{center}
 \end{figure*}
@@
 \begin{figure*}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 3.55in]{HD12862_[2]gamma_vs_bisspan.pdf} 
@@
    \label{fig:alphacent:corr.gamma}
+\end{center}
 \end{figure*}
@@
 \begin{figure*}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{HD12862_[4]Comparison_para.pdf}  
@@
    \label{fig:alphacent:corrPlot}
+\end{center}
 \end{figure*}
@@
 \begin{figure*} 
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{NEW_CORRECTIONHD12862_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
@@
    \label{fig:alphacent:correctionRV}
+\end{center}
 \end{figure*}
@@
 Finally, for each period, we searched for the minimum amplitude for which at least 50\% of the planets with different phases were detected.
-The results are shown in Fig.~\ref{fig:detection_limits.pdf}.
+The results are shown in Fig.~\ref{fig:detection_limits}.
 As we can see, all the different RV estimates gives extremely similar detection limits.
@@
 
-Although the detection limits stay constant for nearly all the periods, we see that for 30 days, we have a huge increase for all the RV estimates.
-This is because the planet period is close to the rotation period of the star \citep[36.7 days,][]{Dumusque-2012}, and therefore close to the semi-periodicity of the stellar activity signal.
-In such a case, the activity correction absorbs part of the planetary signal.
-We thus need to inject a much stronger planetary signal at this period if we want to detect it.}
+\begin{figure}[!h]
+\begin{center}
+\includegraphics[height = 2.6in]{detection_limits.pdf} 
+   \caption{Detection limits of planetary signals once we have removed from the raw RVs the linear combination of CCF parameters proposed in Eq.~\ref{eq:RV:correction} to correct for stellar activity.
+As we can see, when considering the different parametrization for the RV: N mean RV, SN mean RV and SN median RV, we arrive to very similar detection limits.}
+   \label{fig:detection_limits}
+\end{center}
+\end{figure}
+
+Although the detection limits stay constant for all the periods below 15 days, we see that for 20 and 30 days, we have a huge increase in detection limits for all the RV estimates. 
+This is because period of the simulated planet, 20 days and 30 days, are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012}
+and therefore close to the semi-periodicity of the stellar activity signal. In such a case, the activity 
+correction absorbs part of the planetary signal. We thus need to inject a much stronger planetary signal at these periods to detect them.}
 
@@
 
-\xavier{In this section, Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
-Therefore, we cannot simply shuffle each point in the CCF with their respective error bar and then recalculate the best SN or Normal density fit, to see how the noise of the CCF influence the noise on the parameters derived from the CCF.
-We therefore decided to start with the spectrum, for which we know that each points are totally independent of the others.
-The standard error on each point is given by the photon noise, which follows a Poisson law and is therefore the square root of the measured flux.}
-
-In this Section, we perform a bootstrap analysis \citep[e.g.][]{davison1997bootstrap, efron1994introduction} in order to retrieve the standard errors associated to SN mean RV, SN median RV, RV, SN FWHM, FWHM, $\gamma$ and BIS SPAN.
+\xavier{In this section, we investigate how the noise of the CCF influence the CCF parameters derived either by a Normal density or a SN density fit.
+Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
+Therefore, we cannot simply vary each point in the CCF with their respective error bar and then recalculate the best SN or Normal density fit, to see how the CCF noise influences N mean RV, SN mean RV, SN median RV, FWHM, SN FWHM, BIS SPAN and $\gamma$.
+We therefore started from the spectrum, for which we know that each point is totally independent of the others.
+The standard error on each point of the spectrum is given by the photon noise, which follows a Poisson law and is therefore obtained by taking the square root of the measured flux.}
+
+\xavier{We applied the following method to estimate the error bars on the different parameters derived from the CCF.
+We first modify the values of all the points in the spectrum given their respective error bars.
+To do so we added to each point the value randomly drawn from a Gaussian distribution centered on the value of the point and with standard deviation the square root of the flux.
+We then calculated the CCF from this spectrum using the method presented in \citet{Pepe-2002a}, fitted either a Normal or SN density to this CCF and recorded the different parameters.
+We redo this process a hundred times, which gives us at the end, a distribution for each CFF parameter.
+The standard deviations of the obtained distributions is then associated to the noise of each CCF parameters.}
+
+\xavier{We measured the standard deviation of each CCF parameters for all the CCF of HD215152, HD192310 and Corot-7.
+This gives us an information of how the noise on each CCF parameter varies as a function of SNR.
+In this case, the SNR, measured at 550 nm on the original spectra, varies between 10 and 500.
+The results can be seen in Fig.~\ref{fig:se}.
+}
+
+%In this Section, we perform a bootstrap analysis \citep[e.g.][]{davison1997bootstrap, efron1994introduction} in order to retrieve the standard errors associated to SN mean RV, SN median RV, RV, SN FWHM, FWHM, $\gamma$ and BIS SPAN.
 Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
@@
 
-\subsection{Estimation of standard errors for the CCF parameters for the simulation study} \label{sec:bootstrap_soap}
-
-We start by calculating the standard errors of the parameters retrieved in Sec.
+%\subsection{Estimation of standard errors for the CCF parameters for the simulation study} \label{sec:bootstrap_soap}
+%
+%We start by calculating the standard errors of the parameters retrieved in Sec.
 \ref{sec:soap}, where with SOAP we produced CCF's presenting spurious variations in RV's caused by a faculae or by a spot.
 In the third and final case we considered, beyond the spot, a planetary signal that produces pure Doppler-shifts in the CCF's.
-
-Fig.~\ref{fig:se.soap.faculae} shows the results of the bootstrap analysis performed when a faculae is present on the photosphere of the star.
+%
+%Fig.~\ref{fig:se.soap.faculae} shows the results of the bootstrap analysis performed when a faculae is present on the photosphere of the star.
 The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} shows the different errors for the RV's, defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width of the CCF, defined as FWHM (red triangles) or SN FWHM (black circles) and the asymmetry of the CCF, defined as $\gamma$ (black circles) or BIS SPAN (red triangles).
@@
 Therefore, the SN fit gives a better precision in CCF asymmetry than what can be reached using BIS SPAN.
-
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{RV_comparison_FACULAE_standard_errors.pdf} 
-   \caption{Faculae Case.
+%
+%\begin{figure*}[htbp]
+%\begin{center}
+%\includegraphics[height = 6in]{RV_comparison_FACULAE_standard_errors.pdf} 
+%   \caption{Faculae Case.
 Comparison between the standard errors using the bootstrap analysis for the RV's, the FWHM and the asymmetry parameter.
@@
 To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
-   \label{fig:se.soap.faculae}
-\end{figure*}
-
-Fig.~\ref{fig:se.soap.spot} shows the results of the bootstrap analysis performed when a spot is present on the photosphere of the star.
+%   \label{fig:se.soap.faculae}
+%\end{center}
+%\end{figure*}
+%
+%Fig.~\ref{fig:se.soap.spot} shows the results of the bootstrap analysis performed when a spot is present on the photosphere of the star.
 The series of plots follows the specifications outlined for the previous case.
@@
 Finally, for the errors in evaluating the asymmetry of the CCF, we see that, when fitting the SN to the CCF, the asymmetry errors are $20\%$ smaller.
-
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{RV_comparison_SPOT_standard_errors.pdf} 
-   \caption{Spot case.
+%
+%\begin{figure*}[htbp]
+%\begin{center}
+%\includegraphics[height = 6in]{RV_comparison_SPOT_standard_errors.pdf} 
+%   \caption{Spot case.
 Comparison between the standard errors using the bootstrap analysis for the RV's, the FWHM and the asymmetry parameter.
@@
 To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
-   \label{fig:se.soap.spot}
-\end{figure*}
-
-Fig.~\ref{fig:se.soap.spot.planet} shows the results of the bootstrap analysis performed when a spot is present on the photosphere of the star.
+%   \label{fig:se.soap.spot}
+%\end{center}
+%\end{figure*}
+%
+%Fig.~\ref{fig:se.soap.spot.planet} shows the results of the bootstrap analysis performed when a spot is present on the photosphere of the star.
 The series of plots follows the specifications outlined for the previous two cases.
@@
 The errors in width of the CCF are comparable and the errors in evaluating the asymmetry of the CCF are $15\%$ smaller when using the asymmetry parameter $\gamma$ of the SN.
-
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{RV_comparison_SPOT_PLANET_standard_errors.pdf} 
-   \caption{Spot and Planet case.
+%
+%\begin{figure*}[htbp]
+%\begin{center}
+%\includegraphics[height = 6in]{RV_comparison_SPOT_PLANET_standard_errors.pdf} 
+%   \caption{Spot and Planet case.
 Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
@@
 To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
-   \label{fig:se.soap.spot.planet}
-\end{figure*}
+%   \label{fig:se.soap.spot.planet}
+%\end{center}
+%\end{figure*}
 
@@
 \begin{figure*}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
@@
    \label{fig:se}
+\end{center}
 \end{figure*}
@@
 
-\begin{figure} 
+\begin{figure*} 
    \centering
@@
    \label{fig:HD192310:correctionRV}
-\end{figure}
+\end{figure*}
 
@@
    \label{fig:HD10700:correctionRV}
-\end{figure}
+\end{figure*}
 
@@
    \label{fig:HD215152:correctionRV}
-\end{figure}
+\end{figure*}
 
@@
    \label{fig:Corot-7:correctionRV}
-\end{figure}
-
-%%%%%%
-\iffalse
-%\subsection{HD192310}  \label{sec:Gl785}
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 3in]{[0]HD19231_HistogramsDiff.pdf} 
-   \caption{RVs comparison for HD192310 considering a Normal and a SN fitting (using both the mean and the median).}
-   \label{fig:HD192310:RV}
-\end{figure*}
-%
-\begin{figure}[htbp]
-   \centering
-\includegraphics[height = 3in]{HD19231_[2]gamma_vs_bisspan.pdf} 
-   \caption{Correlation between $\gamma$ and the BIS SPAN for HD192310.}
-   \label{fig:Gliese785:corr.gamma}
-\end{figure}
-%
-
-%\subsection{Tau Ceti}  \label{sec:Taucet}
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 3in]{[0]TauCeti_HistogramsDiff.pdf} 
-   \caption{RVs comparison for Tau Ceti considering a Normal and a SN fitting (using both the mean and the median).}
-   \label{fig:Tau Ceti:RV}
-\end{figure*}
-%
-\begin{figure}[htbp]
-   \centering
-\includegraphics[height = 3in]{HD10700_[2]gamma_vs_bisspan.pdf} 
-   \caption{Correlation between $\gamma$ and the BIS SPAN for Tau Ceti.}
-   \label{fig:Tau:corr.gamma}
-\end{figure}
-%
-
-%\subsection{HD215152}  \label{sec:HD215152}
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 3in]{[0]HD21515_HistogramsDiff.pdf} 
-   \caption{RVs comparison for HD215152 considering a Normal and a SN fitting (using both the mean and the median).}
-   \label{fig:HD215152:RV}
-\end{figure*}
-%
-\begin{figure}[htbp]
-   \centering
-\includegraphics[height = 3in]{HD21515_[2]gamma_vs_bisspan.pdf} 
-   \caption{Correlation between $\gamma$ and the BIS SPAN for HD 215152.}
-   \label{fig:HD215152:corr.gamma}
-\end{figure}
-%
-
-%\subsection{Corot-7}  \label{sec:Corot7}
-%
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 3in]{[0]LRa01_E_HistogramsDiff.pdf} 
-   \caption{RVs comparison for Corot-7 considering a Normal and a SN fitting (using both the mean and the median).}
-   \label{fig:corot7:RV}
-\end{figure*}
-%
-\begin{figure}[htbp]
-   \centering
-\includegraphics[height = 3in]{LRa01_E_[2]gamma_vs_bisspan.pdf} 
-   \caption{Correlation between $\gamma$ and the BIS SPAN for Corot-7.}
-   \label{fig:Corot7:corr.gamma}
-\end{figure}
-%
-\fi
-%
+\end{figure*}
+
+%%%%%%%
+%\iffalse
+%%\subsection{HD192310}  \label{sec:Gl785}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{[0]HD19231_HistogramsDiff.pdf} 
+%   \caption{RVs comparison for HD192310 considering a Normal and a SN fitting (using both the mean and the median).}
+%   \label{fig:HD192310:RV}
+%\end{figure*}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{HD19231_[2]gamma_vs_bisspan.pdf} 
+%   \caption{Correlation between $\gamma$ and the BIS SPAN for HD192310.}
+%   \label{fig:Gliese785:corr.gamma}
+%\end{figure*}
+%%
+%
+%
+%%\subsection{Tau Ceti}  \label{sec:Taucet}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{[0]TauCeti_HistogramsDiff.pdf} 
+%   \caption{RVs comparison for Tau Ceti considering a Normal and a SN fitting (using both the mean and the median).}
+%   \label{fig:Tau Ceti:RV}
+%\end{figure*}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{HD10700_[2]gamma_vs_bisspan.pdf} 
+%   \caption{Correlation between $\gamma$ and the BIS SPAN for Tau Ceti.}
+%   \label{fig:Tau:corr.gamma}
+%\end{figure*}
+%%
+%
+%
+%%\subsection{HD215152}  \label{sec:HD215152}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{[0]HD21515_HistogramsDiff.pdf} 
+%   \caption{RVs comparison for HD215152 considering a Normal and a SN fitting (using both the mean and the median).}
+%   \label{fig:HD215152:RV}
+%\end{figure*}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{HD21515_[2]gamma_vs_bisspan.pdf} 
+%   \caption{Correlation between $\gamma$ and the BIS SPAN for HD 215152.}
+%   \label{fig:HD215152:corr.gamma}
+%\end{figure*}
+%%
+%
+%
+%%\subsection{Corot-7}  \label{sec:Corot7}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{[0]LRa01_E_HistogramsDiff.pdf} 
+%   \caption{RVs comparison for Corot-7 considering a Normal and a SN fitting (using both the mean and the median).}
+%   \label{fig:corot7:RV}
+%\end{figure*}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{LRa01_E_[2]gamma_vs_bisspan.pdf} 
+%   \caption{Correlation between $\gamma$ and the BIS SPAN for Corot-7.}
+%   \label{fig:Corot7:corr.gamma}
+%\end{figure*}
+%%
+%\fi
+%%
 

### 2018-05-31 manuscript_Windows.tex
Modifying Section 6

--- 2018-05-30 manuscript.tex
@@
 Finally, for each period, we searched for the minimum amplitude for which at least 50\% of the planets with different phases were detected.
-The results are shown in Fig.~\ref{fig:detection_limits.pdf}.
+The results are shown in Fig.~\ref{fig:detection_limits}.
 As we can see, all the different RV estimates gives extremely similar detection limits.
-Therefore, we can use any of these estimates when searching for planetary signal in RV data contaminated by stellar activity.
-
-Although the detection limits stay constant for nearly all the periods, we see that for 30 days, we have a huge increase for all the RV estimates.
-This is because the planet period is close to the rotation period of the star \citep[36.7 days,][]{Dumusque-2012}, and therefore close to the semi-periodicity of the stellar activity signal.
+Therefore, we can use any of these estimates when searching for planetary signal in RV data contaminated by stellar activity.}
+
+\begin{figure}[!h]
+   \centering
+\includegraphics[height = 2.6in]{detection_limits.pdf} 
+   \caption{Detection limits of planetary signals once we have removed from the raw RVs the linear combination of CCF parameters proposed in Eq.~\ref{eq:RV:correction} to correct for stellar activity.
+As we can see, when considering the different parametrization for the RV: N mean RV, SN mean RV and SN median RV, we arrive to very similar detection limits.}
+   \label{fig:detection_limits}
+\end{figure}
+%
+%Although the detection limits stay constant for all the periods below 15 days, we see that for 20 and 30 days, we have a huge increase in detection limits for all the RV estimates.
+This is because period of the simulated planet, 20 days and 30 days, are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012}, and therefore close to the semi-periodicity of the stellar activity signal.
 In such a case, the activity correction absorbs part of the planetary signal.
-We thus need to inject a much stronger planetary signal at this period if we want to detect it.}
+We thus need to inject a much stronger planetary signal at these periods to detect them.}
+%
 
@@
 
-\xavier{In this section, Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
-Therefore, we cannot simply shuffle each point in the CCF with their respective error bar and then recalculate the best SN or Normal density fit, to see how the noise of the CCF influence the noise on the parameters derived from the CCF.
-We therefore decided to start with the spectrum, for which we know that each points are totally independent of the others.
-The standard error on each point is given by the photon noise, which follows a Poisson law and is therefore the square root of the measured flux.}
+\xavier{In this section, we investigate how the noise of the CCF influence the CCF parameters derived either by a Normal density or a SN density fit to the CCF.
+Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
+Therefore, we cannot simply shuffle each point in the CCF with their respective error bar and then recalculate the best SN or Normal density fit, to see how the CCF noise influences N mean RV, SN mean RV, SN median RV, FWHM, SN FWHM, BIS SPAN and $\gamma$.
+We therefore started from the spectrum, for which we know that each points are totally independent of the others.
+The standard error on each point of the spectrum is given by the photon noise, which follows a Poisson law and is therefore obtained by taking the square root of the measured flux.}
+
+\xavier{We applied to following method to estimate the errors bar on the different parameters derived from the CCF. We first shuffle }
 

### 2018-05-31 manuscript.tex
Modify Sect 6

@@
 \begin{center}
-\includegraphics[height = 3in]{Skew_Normal_densities_jjck.pdf} 
+\includegraphics[height = 2.3in]{Skew_Normal_densities_jjck.pdf} 
    \caption{Density function of a random variable Y following the SN distribution $SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
@@
 \begin{figure*}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
-Once corrected for stellar activity the residuals do not show a systematic component.}
+   \caption{\umberto{Set of  spurious variations in RV's caused by a \textbf{spot} using a Normal and a SN fit before and once corrected from stellar activity.
+The new correction has done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
+Once corrected for stellar activity using the proposed linear function (black dots), the residuals present a smaller systematic component if compared with the residuals obtained with the usual correction (blue triangles).}}
     \label{fig:spot.correction}
+\end{center}
 \end{figure*}
@@
 \begin{figure*}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
@@
    \label{fig:Gliese785:corrPlot}
+\end{center}
 \end{figure*}
@@
 \begin{figure*} 
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{NEW_CORRECTIONHD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
@@
    \label{fig:HD192310:correctionRV}
+\end{center}
 \end{figure*}
@@
 \begin{figure*}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
@@
    \label{fig:Tau:corrPlot}
+\end{center}
 \end{figure*}
@@
 \begin{figure*} 
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{NEW_CORRECTIONHD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
@@
    \label{fig:HD10700:correctionRV}
+\end{center}
 \end{figure*}
@@
 \begin{figure*}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
@@
    \label{fig:HD215152:corrPlot}
+\end{center}
 \end{figure*}
@@
 \begin{figure*} 
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{NEW_CORRECTIONHD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
@@
    \label{fig:HD215152:correctionRV}
+\end{center}
 \end{figure*}
@@
 \begin{figure*}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
@@
    \label{fig:Corot7:corrPlot}
+\end{center}
 \end{figure*}
@@
 \begin{figure*} 
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{NEW_CORRECTIONLRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
@@
    \label{fig:Corot-7:correctionRV}
+\end{center}
 \end{figure*}

### 2018-05-31 manuscript.tex
sec 3 update

--- 2018-05-31 manuscript.tex
@@
 where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix). 
-The inclusion of the contrast parameter $A$ is justified by the fact that the presence of a spot on the stellar surface produces a changes in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g.
+The contrast parameter $A$ accounts for the presence of a spot on the stellar surface, which produces a change in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g.
 Fig.
 2 in ][]{Dumusque-2014b}.
-The reasons for including in Eq.~\ref{eq:RV:correction} a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better justified through the results of the examples presented in Sec.\ref{sec:soap}.
-\xavier{This interaction term allows to take into account cases when for different values of SN FWHM (or FWHM), the linear coefficient $\beta_{2}$ for $\gamma$ (or BIS SPAN) varies}.
-\xavier{Umberto, Jessi, is this correct ?}
+The reasons for including in Eq.~\ref{eq:RV:correction} a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better understood through the results of the examples presented in Sec.\ref{sec:soap}.
+\xavier{This interaction term can accounts for possible interactions between SN FWHM (or FWHM) and $\gamma$ (or BIS SPAN), meaning that the two variables' association with the response, $RV_{\text{stellar activity}}$, depends also on the other variable.
+}. \xavier{Umberto, Jessi, is this correct ?} \jessi{I modified the statement - is the modification clear?}
 %while the association between in this case BIS SPAN and FWHM (or $\gamma$ and SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant.

### 2018-05-31 manuscript.tex
minor updates
abstract

@@
 %\documentclass[referee]{aa}
+%
+\usepackage{pdflscape} % or {lscape}
 \usepackage{natbib}
 %\usepackage{lscape}
-\usepackage{pdflscape} % or {lscape}
 \usepackage{wasysym}
@@
 	    \thanks{Branco Weiss Fellow--Society in Science (url: \url{http://www.society-in-science.org})}    
-	    \and Jessi Cisewski\inst{2}
+	    \and Jessi Cisewski-Kehe\inst{2}
 	    }
@@
 {Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
-Stellar activity can be probed by measuring time dependant variations in the shape of the cross-correlation function (CCF), often estimated using the different moments of the modelled CCF.
+Stellar activity can be probed by measuring time dependent variations in the shape of the cross-correlation function (CCF), often estimated using the different moments of the modeled CCF.
 Therefore estimating the moments of the CCF with high precision is essential to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.}
 %
-{We propose to estimate the moments of the CCF by fitting a model using a Skew Normal (SN) density shape, which unlike the commonly employed Normal density, \xavier{includes an skewness parameter to capture the asymmetry of the CCF induced by stellar activity, but also the natural asymmetry induced by convective blueshift.}}
+{We propose to estimate the moments of the CCF by fitting a model using a Skew Normal (SN) density shape, which unlike the commonly employed Normal density, includes an skewness parameter to capture the asymmetry of the CCF induced by stellar activity, but also the natural asymmetry induced by convective blueshift.}
 %
@@
 }
+{XXX \jessi{It looks like we still need to add conclusions here}}
 %

### 2018-05-31 manuscript.tex
sec 2 updates

@@
 where C is an unknown offset for the continuum of the CCF, A is the unknown amplitude of the CCF, commonly referred to as the contrast, and $\mu$, $\sigma^2$ and $\gamma$ are the mean, variance and skewness of the SN as defined above.
-The values $x_1, \ldots, x_n$ are the different values of the x-axis of the CCF, generally in the unit of a velocity.
+The values $x_1, \ldots, x_n$ are the different values of the x-axis of the CCF, generally in velocity units (e.g. \ms).
 
@@
 
-To evaluate the strength of the correlation between the estimated RV's and the different stellar activity indicators, we calculated the Pearson correlation coefficient, which in its general form is defined as:
+To evaluate the strength of the correlation between the estimated RV's and the different stellar activity indicators, we calculated the Pearson correlation coefficient, $R$, which in its general form is defined as:
 %
 \begin{equation}
-R (x,y)= \frac{cov(x,y)}{\sigma(x),\sigma(y)},
+R (x,y)= \frac{cov(x,y)}{\sigma(x)\sigma(y)},
 \label{eq:Pearson:corr}

### 2018-05-31 manuscript.tex
section 3 updates

@@
 
-\xavier{Exoplanets only produce a pure RV signal.
-Stellar activity on the contrary, and in particular the presence of active regions on the stellar photosphere, does not produce a blueshift or redshift of the entire stellar spectra, but creates a spurious RV signal by modifying the shape of spectral lines.
-To track these variations in the shape of the spectral lines}, the general approach consists in using the FWHM, the BIS SPAN or the indicators introduced in \citet{Boisse-2011} or \citet{Figueira-2013}, which provide information on the width and asymmetry of the CCF.
-A strong correlation between the estimated RVs and one or more of these parameters provides an indication that stellar activity signals are affecting our measurements.
+Exoplanets only produce a pure RV signal.
+On the contrary, stellar activity, in particular the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.
+To track these variations in the shape of the spectral lines, the general approach consists in using the FWHM, the BIS SPAN or other indicators such as those introduced in \citet{Boisse-2011} or \citet{Figueira-2013}, which provide information on the width and asymmetry of the CCF.
+A strong correlation between the estimated RVs and one or more of these parameters provides an indication that stellar activity signals may be affecting the measurements.
 

### 2018-05-31 manuscript.tex
sec 3 updates

@@
 \documentclass{aa}
+
 %\documentclass[referee]{aa}
@@
 
-\xavier{When fitting for planetary signals in RV data, it is common to include in the fitted model, linear dependencies with the BIS SPAN and the FWHM, to take into account the signal induced by stellar activity \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
+When fitting for planetary signals in RV data, it is common to include linear dependencies with the BIS SPAN and the FWHM and to take into account the signal induced by stellar activity \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
 %Some people also include the \logrhk, however, \citet{Feng-2018} show that this is probably not a good choice as \logrhk and RV are not well correlated.
-In this paper, we propose to add additional parameters in the model to correct for stellar activity: first the amplitude parameter A of the CCF, generally referred to as the CCF contrast, and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case).
-The stellar activity correction we propose can therefore be written as:}
+We propose to add additional parameters in the model to correct for stellar activity: first the amplitude parameter A of the CCF, generally referred to as the CCF contrast, and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case).
+The stellar activity correction we propose can therefore be written as:
 %
 \begin{equation}
-RV_{\text{stellar activity}}= \beta_{0} + \beta_{1} A + \beta_{2} \gamma + \beta_{3} \text{SN FWHM} + \beta_{4} (\gamma  \text{SN FWHM})+\epsilon,
+RV_{\text{activity}}= \beta_{0} + \beta_{1} A + \beta_{2} \gamma + \beta_{3} \text{SN FWHM} + \beta_{4} (\gamma  \text{SN FWHM})+\epsilon,
 \label{eq:RV:correction}
@@
 The reasons for including in Eq.~\ref{eq:RV:correction} a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better understood through the results of the examples presented in Sec.\ref{sec:soap}.
-\xavier{This interaction term can accounts for possible interactions between SN FWHM (or FWHM) and $\gamma$ (or BIS SPAN), meaning that the two variables' association with the response, $RV_{\text{stellar activity}}$, depends also on the other variable.
+\xavier{This interaction term can accounts for possible interactions between SN FWHM (or FWHM) and $\gamma$ (or BIS SPAN), meaning that the two variables' association with the response, $RV_{\text{activity}}$, depends also on the other variable.
 }. \xavier{Umberto, Jessi, is this correct ?} \jessi{I modified the statement - is the modification clear?}
@@
 \begin{equation}
-RV= RV_{\text{stellar activity}} + RV_{\text{planet}},
+RV= RV_{\text{activity}} + RV_{\text{planet}},
 \label{eq:RV:correction.overall}
@@
 %
-\xavier{where $RV_{\text{stellar activity}}$ can be found in Eq.~\ref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case of no eccentricity, can be modelled by the following sinusoidal function:}
+\xavier{where $RV_{\text{activity}}$ can be found in Eq.~\ref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case of no eccentricity, can be modelled by the following sinusoidal function:}
 %

### 2018-05-31 manuscript.tex
sec 3 updates

@@
 %
-where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix). 
+where $\beta_{0}$ is the intercept and $\epsilon$ is the error with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix). 
 The contrast parameter $A$ accounts for the presence of a spot on the stellar surface, which produces a change in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g.
@@
 2 in ][]{Dumusque-2014b}.
-The reasons for including in Eq.~\ref{eq:RV:correction} a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better understood through the results of the examples presented in Sec.\ref{sec:soap}.
-\xavier{This interaction term can accounts for possible interactions between SN FWHM (or FWHM) and $\gamma$ (or BIS SPAN), meaning that the two variables' association with the response, $RV_{\text{activity}}$, depends also on the other variable.
-}. \xavier{Umberto, Jessi, is this correct ?} \jessi{I modified the statement - is the modification clear?}
+The benefits of including a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better understood through the results of the examples presented in Sec.\ref{sec:soap}.
+This interaction term can account for possible interactions between SN FWHM (or FWHM) and $\gamma$ (or BIS SPAN), meaning that each  variables' association with the response, $RV_{\text{activity}}$, depends also on the other variable.
 %while the association between in this case BIS SPAN and FWHM (or $\gamma$ and SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant.

### 2018-05-31 manuscript.tex
sec 3 updates

@@
 
-In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$, $\beta_{2}$, $\beta_{3}$ and $\beta_{4}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,\dots,4$.
-The level for not rejecting the null hypothesis is fixed to $0.05$.
-The coefficient of multiple correlation $R^2$ is introduced in order to explain how well this linear combination addresses the variability of the RV variation induced by stellar activity.
+The proposed model is analyzed using statistical tests on the parameters $\beta_{0}$, $\beta_{1}$, $\beta_{2}$, $\beta_{3}$ and $\beta_{4}$ where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,\dots,4$.
+The significance level for the tests are set at $0.05$.
+The coefficient of determination, $R^2$, is used to assess how well the proposed linear combination of variables accounts for the variability of $RV_{\text{activity}}$.
 

### 2018-05-31 manuscript.tex
sec 3 updates

@@
 
+\jessi{Is the following paragraph needed?
+Is any model selection actually carried out here?
+It seems the model of Eq.~\ref{eq:RV:correction} is fit, and then the significance of the variables are discussed, but no attempts are really made to remove/add/step through the various model options.
+The point about multicollinearity is probably good to keep though.}
 When working with a linear regression, there are several ways to select the variables to include in the model.
@@
 A detailed discussion of the topic can be found in the book by \citet{belsley1991}.
-\xavier{It is common to see some correlation between the amplitude parameter $A$ and the FWHM (or SN FWHM) of the CCF.
+It is common to see some correlation between the amplitude parameter $A$ and the FWHM (or SN FWHM) of the CCF.
 However, in the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ and therefore, the problem of multicollinearity is avoided.
-Finally, we investigate as well the statistical significant of the interaction term between $A$ and the width, and $A$ and the asymmetry of the CC, however, those interaction were relevant for accounting for stellar signal.}
+Finally, we investigate as well the statistical significant of the interaction term between $A$ and the width, and $A$ and the asymmetry of the CC, however, those interaction were relevant for accounting for stellar signal.
 

### 2018-05-31 manuscript.tex
sec 4 updates

@@
 
-\xavier{For a given configuration of spots and faculae on the stellar surface, SOAP 2.0 gives as output the simulated CCF as a function of rotational phase.
-The code returns as well the RV and the FWHM by fitting a Normal density to the CCF, and the BIS SPAN by calculating the bisector of the CCF.
-SOAP 2.0 gives us therefore noiseless CCFs affected by stellar activity, which will be used to compare the benefits of fitting a SN density to the CCF compared to a Normal density fit.}
+For a given configuration of spots and faculae on the stellar surface, SOAP 2.0 gives as output the simulated CCF as a function of rotational phase.
+The code also returns the RV and the FWHM by fitting a Normal density to the CCF, and the BIS SPAN by calculating the bisector of the CCF.
+SOAP 2.0 gives noiseless CCFs affected by stellar activity, which are used to compare the benefits of a SN density fit to the CCF compared to a Normal density fit.
 

### 2018-05-31 manuscript.tex
sec 4 updates

@@
 
-\xavier{For the simulations shown below, we modelled a star similar to the Sun.
+For the simulations discussed below, a star similar to the Sun was modeled.
 The stellar rotational period is set to 25.0 days, the radius to a solar radius and the star is seen equator on.
-The stellar effective temperature is set to 5778 K (NASA Planetary Fact Sheets), and we use a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
-In addition, to be able to compare the result of those simulations with real data obtained with the HARPS spectrograph in Sect.~\ref{sec:4}, we asked SOAP 2.0 to generate CCFs of width 40 \kms and of resolution 115'000, so that those CCFs would have the same properties as the one returned by the HARPS data reduction.}
+\jessi{The previous sentence seems incomplete and I'm not sure how to update it.}
+The stellar effective temperature is set to 5778 K (NASA Planetary Fact Sheets)\jessi{Is there a full citation available for this NASA fact sheet?
+Also, why is it referenced?
+Is the effective temperature supposed to be similar to the Sun?}, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011} are used.
+In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generate with a width of 40 \kms and a resolution of 115'000.
+\jessi{Is a resolution of ``115'000'' standard notation?
+I'm not sure what it means.}
+%, so that those CCFs would have the same properties as the one returned by the HARPS data reduction.
 

### 2018-05-31 manuscript.tex
sec 4 updates

@@
 
-\xavier{To see the impact of a faculae on the different parameters of the CCF, we simulated the effect of an equatorial faculae of size 3\% relative to the visible stellar hemisphere.
+To see the impact of a facula on the different parameters of the CCF, we simulated the effect of an equatorial faculae \jessi{Should a footnote be added here to explain that the SOAP 2.0 faculae are not simulated from actual faculae templates?} of size 3\% relative to the visible stellar hemisphere.
 The faculae is face on when the phase equals to 0.
-Note that a 3\% faculae is relatively big for the Sun.
-At maximum activity, big faculae have generally a size of 1\%.
-In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and taking its mean (RV), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV).
-We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is slightly different with respect to the two others, with a maximum amplitude happening at a different phase.}
+Note that a 3\% faculae is relatively large for the Sun; at maximum activity, big faculae have generally a size of 1\%.
+\jessi{Is there a reference for this that could be added?}
+In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and using its mean (RV \jessi{I believe this was going to be updated to ``N mean RV''?}), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV).
+We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is different from the two others with a maximum amplitude happening at a different phase.
 
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
-\caption{RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
-SN mean RV seems to have the smallest spurious variations caused by the faculae.}
+\caption{Using CCFs from SOAP 2.0 with a single facula, the estimated RV changes as function of the orbital phase.
+SN mean RV seems to have the smallest spurious variations caused by the faculae.\jessi{The previous sentence does not seem correct.}  \jessi{The cyan line is hard to see in the legend, and may be impossible in a black-and-white version - could the legend background be white?}
+}
    %\caption{(left) RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.

### 2018-05-31 manuscript.tex
sec 4 updates

@@
 
-\xavier{In Fig.~\ref{fig:faculae.corr}, we compare the correlation between the different RV estimates and the different asymmetry or width estimates.
-As we can see, the strength of the correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are much stronger than the correlations between BIS SPAN and RV, with Pearson correlation coefficient $R$ values of 0.46, -0.67 and -0.09, respectively.
-Regarding the width barycenter correlations, we also find a stronger correlation between SN FWHM and SN mean RV compared to the one between FWHM and RV, $R=0.98$ and 0.84, respectively.
+Correlations between the different RV estimates and the different CCF asymmetry or width estimates are displayed in Fig.~\ref{fig:faculae.corr}.
+The strength of the correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are stronger than the correlations between BIS SPAN and RV, with Pearson correlation coefficient $R$ values of 0.46, -0.67 and -0.09, respectively.
+For the width barycenter correlations, there is a stronger correlation between SN FWHM and SN mean RV compared to the one between FWHM and RV \jessi{updated to N mean RV?}, $R=0.98$ and 0.84, respectively.
 In this case however, the correlation between SN FWHM and SN median RV is smaller with $R=0.50$.
-This first analysis shows that in the case of a faculae, using some parameters from the SN can lead to much stronger correlation than the usual Normal parameters and therefore, the SN parameters seems to be better
-
-probe better stellar activity.
-We will of course confirm this in the next sections presenting the case of a spot and of a spot plus a planet, but also in Sec~\ref{sec:4} when we will apply the SN fitting to real data sets.}
+This first analysis shows that in the case of a facula, using some parameters from the SN can lead to much stronger correlation than the usual Normal parameters and therefore, the SN parameters may better probe stellar activity.
+We investigate this feature further in the next sections where we consider simulated data with a single spot and a spot plus a planet, and in Sec~\ref{sec:4} with real observations.
 

### 2018-05-31 manuscript.tex
sec 4 updates

@@
 \includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
-   \caption{Evaluation of the correlation between the RV's and the asymmetry parameters when a faculae is present on the photosphere of the star.
-In this case both the shape and the width of the CCF changes as the faculae moves, producing statistically significative correlations between the RV's and respectively the asymmetry parameter and the width parameter.}
+   \caption{Using CCFs from SOAP 2.0 with a single facula, the correlation between the estimated RV's and the asymmetry parameters are displayed.
+In this case both the shape and the width of the CCF changes as the facula moves, producing statistically significant correlations between the estimated RV's and, respectively, the asymmetry parameter or the width parameter.}
     \label{fig:faculae.corr}

### 2018-05-31 manuscript.tex
sec 4 updates

@@
 
-Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a faculae, \xavier{we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its efficiency in the case of a faculae.} The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
-It is straightforward to see that the proposed correction for \xavier{stellar activity is able to account for the majority of the activity signal created by a faculae, with a $R^2$ of our model larger than 0.95.
+Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a facula, we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its performance in this setting.
+The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
+The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a $R^2$ of our model larger than 0.95.
 In addition, the rms of the different estimates of the RV reduces from about 3 \ms before correction to values below 0.15 \ms after correction.
 We see a slightly smaller rms after correction for the SN parameters, however the different is not significant.
-When comparing the correction proposed in Eq.~\ref{eq:RV:correction} with what is generally used, i.e.
-a linear combination of the asymmetry and width parameter, we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2.
-Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that the \umberto{parameter related to the} intercept, $\beta_0$, is only significant at a level of 1\% in the case of the Normal parameters \umberto{or when SN median RV is used}.}
+\jessi{In the previous sentence, is this a comparison between SN and N?
+If so, it should be clarified.}
+When comparing the correction proposed in Eq.~\ref{eq:RV:correction} with what is generally used (i.e.
+a linear combination of only the asymmetry and width parameter), we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2.
+Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that the parameter related to the intercept, $\beta_0$, is only significant at a level of 1\% in the case of the Normal parameters or when SN median RV is used.
+\jessi{Is the point about $\beta_0$ relevant?}
 

### 2018-05-31 manuscript.tex
sec 4 updates

@@
 \end{tabular}
-\caption{\umberto{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a \textbf{faculae}, according to Eq.~\ref{eq:RV:correction}.
-All the variables, except the intercept when the independent variable is SN median RV, are statistically useful to explain spurious variations in RV's caused by a faculae only for the SN analyses.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}}
+\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction} to correct the estimated  RVs from spurious variations caused by a facula.
+All the variables, except the intercept when the response variable is SN median RV, are statistically significant to explain spurious variations in RV's caused by a facula.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability in the estimated RVs.}
 \label{table:faculae.test}

### 2018-05-31 manuscript.tex
sec 4 updates

@@
 \includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{\umberto{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity.
-The new correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
-Once corrected for stellar activity using the proposed linear function (black dots), the residuals present a smaller systematic component if compared with the residuals obtained with the usual correction (blue triangles).}}
+   \caption{(top) The spurious RVs caused by a facula in the simulated data using a Normal and a SN fit.
+before and once corrected from stellar activity.
+\jessi{What is the correction done here?
+I think what you mean is this:  ``The black circles are the estimated RVs and the red plus signs are the estimated RVs from the fit model of  Eq.~\ref{eq:RV:correction}.''  If my assumption is correct, the legend should say ``RV estimates'' and ``RV model'' or something like that.
+Otherwise this is rather confusing because in the bottom plot you are actually comparing residuals from two models, while the top has a different interpretation.}
+   %
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (new correction) and the usual correction \jessi{it might be helpful to actually have an equation for the usual/old model}.
+The residuals have a smaller systematic component when using the proposed model of
+  Eq.~\ref{eq:RV:correction} (blue circles) compared to the usual model (blue triangles).
+The estimated parameters are presented in Table \ref{table:faculae.test} \jessi{This table only has p-values and $R^2$}. }
     \label{fig:faculae.correction}

### 2018-05-31 manuscript.tex
sec 4 updates

@@
 
-\xavier{In this section, we simulate the effect on the CCF parameters of an equatorial spot of size 1\% relative to the visible stellar hemisphere.
+In this section, we consider the effects on the CCF parameters of an equatorial spot of size 1\% relative to the visible stellar hemisphere.
 The spot is face on when the phase equals to 0.
-Note that this is an extremely big spot for the Sun, as in general big spots are more in the regime of 0.1\%.
+Note that this is a large spot for the Sun, as in general large spots are more in the regime of 0.1\%.\jessi{Can we add a reference for the previous statement?}
 In Fig.~\ref{fig:spot}, we shows the barycentric variation of the CCF induced by this simulated spot.
-Contrary to the case of the faculae seen before, for the spots, all the different estimates of the CCF barycenter have exactly the same shape in variation.
-The amplitude for SN mean RV is however slightly smaller.}
-
-Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and the different estimates for the CCF barycenter: SN mean RV, SN median RV and RV.
-\xavier{The correlation between $\gamma$ and SN median RV is the strongest with a $R=0.94$, followed then by the correlation BIS SPAN -RV and $\gamma$-SN mean RV, with $R=0.86$.
-Regarding the correlation between the width and the CCF barycenter, we note that the variation is seen as a circle in this parameter space and therefore no correlation is observed.
-Once again, like in the case of the faculae, we see that some parameters of the SN gives stronger correlation than when using the Normal parameters.}
+In contrast to the case of the facula, all the different estimates of the CCF barycenter for the spot have the same shape in variation.
+The amplitude for SN mean RV is however slightly smaller.
+
+Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and the different estimates for the CCF barycenter (i.e.
+the SN mean RV, SN median RV and RV).
+The correlation between $\gamma$ and SN median RV is the strongest with a $R=0.94$, followed by the correlation BIS SPAN - RV and $\gamma$ - SN mean RV, with $R=0.86$.
+\jessi{Do the previous numbers need updating?}  Regarding the correlation between the width and the CCF barycenter, we note that the variation is seen as a circle in this parameter space and therefore no correlation is observed.
+Once again, like in the case of the facula, we see that some parameters of the SN gives stronger correlations than when using the Normal parameters.
 

### 2018-05-31 manuscript.tex
table  updates

@@
 \end{tabular}
-\caption{\umberto{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\ref{eq:RV:correction}.
-All the covariates are statistically useful to explain the variability in RV's caused by a spot, except the intercept and the width of the CCF.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}}
+\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction} to correct the estimated RVs from spurious variations caused by a spot. 
+All the covariates are statistically significant to explain the variability in RV's caused by a spot, except the intercept and the width of the CCF.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability in the estimated RVs.
+\jessi{Isn't the width of the CCF parameter sig for N mean RV at 0.017?
+Previously it was noted that a 5\% significance level was going to be used.}}
 \label{table:spot.test}
@@
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\ref{eq:RV:correction.overall}.
-All the parameters are statistically helpful to address spurious variations in RV's except the FWHM.
-Concerning the keplerian parameters, the amplitude $K$ that provides relevance about the possibly presence of the exoplanet.
-Note that since non linear least squares are required, the residual standard error rather than the $R^2$ is displayed for each case.}
+\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction.overall} to correct the estimated RVs from spurious variations caused by a spot while also accounting for a true planet RV.
+All the covariates are statistically significant to explain the variability in RV's caused by a spot, except the FWHM.
+Concerning the Keplerian parameters, the amplitude $K$ that provides relevance about the possibly presence of the exoplanet.
+Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.
+}
 \label{table:spotplanet.test}

### 2018-05-31 manuscript.tex
captian  updates

@@
 \caption{Using CCFs from SOAP 2.0 with a single facula, the estimated RV changes as function of the orbital phase.
-SN mean RV seems to have the smallest spurious variations caused by the faculae.\jessi{The previous sentence does not seem correct.}  \jessi{The cyan line is hard to see in the legend, and may be impossible in a black-and-white version - could the legend background be white?}
+SN mean RV seems to have the smallest spurious variations caused by the facula.\jessi{The previous sentence does not seem correct.}  \jessi{The cyan line is hard to see in the legend, and may be impossible in a black-and-white version - could the legend background be white?}
 }
@@
    \caption{(top) The spurious RVs caused by a facula in the simulated data using a Normal and a SN fit.
-before and once corrected from stellar activity.
+Before and once corrected from stellar activity.
 \jessi{What is the correction done here?
@@
 \includegraphics[height = 6in]{SOAP_SPOT_Comparison_para_SN.pdf} 
-   \caption{Evaluation of the correlation between the RV's and the asymmetry parameters when a spot is present on the photosphere of the star.
-In this case only the shape of the CCF changes as the spot moves, producing statistically significative correlations only between the RV's and the asymmetry parameter.}
+   \caption{Using CCFs from SOAP 2.0 with a single spot, the correlation between the estimated RVs and the asymmetry or width parameters are displayed.
+In this case the shape changes with phase, producing statistically significant correlations between the estimated RVs and the asymmetry parameters (but not for the estimated RVs and the width parameters).}
     \label{fig:spot.corr}

### 2018-06-01 manuscript.tex

@@
 
-As before, we corrected the originally RV's by using Eq.~\ref{eq:RV:correction}.
-The results of the correction are displayed in Fig.~\ref{fig:spot.correction}.
-Also in this case the proposed correction almost completely addresses the issue when considering the SN or Normal parameters, with values of $R^2$ larger than 0.99.
-\xavier{Looking at Fig.~\ref{fig:spot.correction}, we see that the activity correction proposed here is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms.
-In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however,} \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant.
+As before, the originally RVs were corrected by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction}. 
+In this setting, the proposed correction almost completely addresses the issue \jessi{what issue?} when considering the SN or Normal parameters, with values of $R^2$ larger than 0.99. 
+Considering Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms.
+\jessi{Doesn't the facula setting do better getting down to $\sim$0.13 \ms?}
+In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however, \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant.
 When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.
 
-In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summmurized in Table \ref{table:spot.test}, \umberto{we observe that the $\beta_0$, and $\beta_3$, corresponding respectively to the intercept and to the width of the CCF}, are \umberto{not helpful} to understand the variation measured in RV's.
+In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summarized in Table \ref{table:spot.test}, \umberto{we observe that the $\beta_0$, and $\beta_3$, corresponding respectively to the intercept and to the width of the CCF}, are \umberto{not helpful} to understand the variation measured in RV's.
 This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.

### 2018-06-02 manuscript.tex
Discussion and Conclusion finished

@@
 \begin{center}
-\includegraphics[height = 3.55in]{HD12862_[2]gamma_vs_bisspan.pdf} 
-\includegraphics[height = 3.65in]{HD12862_[2]RadialVelocityDifferences.pdf} 
+\includegraphics[height = 3.6in]{HD12862_gamma_vs_bisspan.pdf} 
+\includegraphics[height = 3.6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
    \caption{\emph{Left: }Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
@@
 The results can be seen in Fig.~\ref{fig:se}.
+In the top plots of this figure, we show the standard errors for the different RV, width and asymmetry estimates.
+Note that because BIS SPAN and $\gamma$ does not have the same units, we used the slope of the correlation between those two parameters to transform $\gamma$ in \ms (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star).
+In the bottom plots, we show the ratio between the standard errors measured when using the SN parameters and the Normal parameters.
+Values smaller or larger than one will imply that standard errors fro the SN parameters are more or less precise, respectively.}
+
+\xavier{Looking at the estimates for the RV, we see that they all follow a similar exponential decay.
+Although we plot the data for three different stars, we do not see any offsets in this decay, which implies that the SNR at 550 nm is the main contributor to the precision measured in RV.
+This is not surprising as the 3 stars studies are all main sequence K-dwarfs.
+When comparing the three different estimates for the RV, we see that SN mean RV presents standard errors that are 60\% larger than what N mean RV gives.
+On the opposite, SN median RV gives errors 10\% more precise than N mean RV.
+Regarding the parameters describing the width of the CCF, FWHM and SN FWHM have the same standard errors.
+Finally, for the asymmetry parameters, we see that $\gamma$, derived from the SN, is 15\% more precise than BIS SPAN.
+In conclusion, when fitting a SN density to the CCF and using as RV estimates SN mean RV, we are able to improve by 10\% the precision on the RV, 15\% the precision on the asymmetry, and this without degrading the precision on the width estimate.
+SN mean RV should not be use to derive RVs, except perhaps for stars for which the photon noise is not the dominant source of noise, as the precision on this parameter if 60\% worse than the precision on the RV derived from a Normal density fit.}
+%
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
+   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
+When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
+Note that for the asymmetry, the error in BIS SPAN is in \kms.
+To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
+   \label{fig:se}
+\end{center}
+\end{figure*}
+
+%, using the spectrum derivative
+%, the pure photon-noise error on RV measured 
+%Together with the pointwise estimates, retrieving the standard errors for the RVs of the star, $\gamma$ and the FWHM provides information about the uncertainties associated to each parameter.
+Since the procedure for retrieving the RVs of the star consists in fitting with a density function a CCF, getting the standard errors for all the parameter of interests cannot be done by using the common asymptotic theory.
+The implementation of a standard bootstrap analysis cannot as well be done, because the points of the CCF are highly correlated.
+In the analysis of the present work, in order to get the standard errors for the parameters of interest for a particular CCF, we moved each point of this CCF according to its measurement errors, producing $100$ simulated CCFs from the original one.
+Then we run both the Normal and the SN analyses on these simulated CCFs, letting us to retrieve an evaluation of the standard errors.
+This operation has been repeated for all the CCFs available for the analyzed stars.
+The comparison between the standard errors retrieved in this way with the classic noise parameter, {\color{red} obtained by using the Gray's equation cit.
+Gray (1983)} are presented in Fig.~ \ref{fig:se}.
+{\color{red} Xavier: Is it correct how the noise parameter is obtained?
+Or it is simply $\sqrt(photons)$?}
+
+%Given the strong correlation between the $\gamma$ parameter of the SN and its mean, the standard errors are larger respect the Normal fitting analysis.
+This fact confirms how correcting the RVs for stellar activity using Eq.
+\ref{eq:RV:correction} is more helpful when using the SN fitting.
+The standard errors for the FWHM are comparable for both the SN and the Normal analyses, whereas an improvement is clearly measurable for the standard errors associated to the asymmetry indicators.
+The last plot in Fig.~\ref{fig:se} shows that the standard errors for $\gamma$ are $10 \%$ smaller than the ones retrieved for the BIS SPAN.
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
+\section{Discussion} \label{sec:discu}
+
+\xavier{When fitting a SN density to the CCF, it is possible at once to retrieve parameters that describe the RV, i.e.
+the CCF barycenter, the amplitude, also called the contrast, the width, and the asymmetry of the CCF.
+For the RV, we investigated the use of the mean and the median of the SN density.
+Then the width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry, by using $\gamma$, the skewness parameter of the SN density.
+
+When we tested the SN density fit to the CCF provided by the SOAP 2.0 code, that simulate the activity signal induced by a spot or a faculae on a solar-like star, we arrived to the conclusion that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual method.
+By more sensitive, we mean here that the correlation between the skewness and either the mean or median of the SN density is stronger than between BIS SPAN and the mean of a Normal density.
+Moreover, the correlation between the FWHM and the CCF barycenter is also stronger when using the parameters from the SN compared to the parameters from the Normal.
+We also confirmed the behavior that the SN parameters are more correlated than the Normal parameters in the case where a planetary signal is added the to stellar activity modeled by SOAP 2.0.
+
+We also present in this paper a new function to correct for stellar activity signals.
+Generally, when fitting for planetary signals, people use a model composed of one or several Keplerians to account for the planets, in addition to a linear combination with the FWHM and BIS SPAN of the CCF to account for stellar activity signals.
+The new function propose to add a linear dependency with the amplitude of the CCF retrieved either by the SN or Normal density fit, and a interaction term between the asymmetry and the width parameters.
+On the simulated data from SOAP 2.0, this new model allows to mitigate stellar activity signals by a factor of 2 and 3.5 compared to the model generally used, for the faculae and spot, respectively.
+
+When moving to real data, we arrived to the same conclusions regarding the strength of the correlation between the asymmetry and the CCF barycenter, as well as between the width and the CCF barycenter.
+We note however that although in the case of the simulated data, the stronger asymmetry-RV correlation was found between $\gamma$ and the median of the SN, in the case of real data, it was between $\gamma$ and the mean of the SN.
+This can be due to the fact that in SOAP 2.0, the faculae is not modelled properly, as it uses as emerging spectrum the one from a spot.
+We know that the temperature between a spot and a faculae is significantly different, therefore their spectra should be different.
+In addition, there is always several active regions on a star, at different locations in longitude and latitude.
+This could also be responsible for the fact that we do not observe the same behavior for the mean and the median of the SN when we compare the SOAP 2.0 simulation and real data.
+Nevertheless, in both the simulated case and the real cases, the parameters derived from the SN are more sensitive to activity than the parameters derived from a Normal fit.
+In addition, the correlation between the asymmetry and the mean of the SN is always stronger than any other parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
+
+When comparing the different RV estimates obtained from the mean of the Normal density, the mean or the median of the SN density, we see that in the case of real data, the amplitude of stellar activity is larger for the mean of the SN, followed by the median of the SN and the mean of the Normal.
+Although there is a huge gap between the first and the second estimate, the difference between the second and the third is much smaller.
+The mean of the SN density is therefore more sensitive to variation in the CCF shape than the median of the SN or the mean of the Normal, which is not surprising as the SN density is able to model the asymmetry of the CCF, what the Normal density does not.
+
+Having an estimate of the RV that is more sensitive to stellar activity, like the mean of the SN, can help us to probe better stellar rotational periods, or understand better the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}.
+We saw in the preceding section that the RV estimated by the mean of the SN is 60\% noisier than the RV derived by the mean of the Normal.
+This is not necessarily a negative aspect.
+Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized by increasing its induced RV amplitude even if the white noise is 60\% larger.
+
+Even if the different RV estimates have different amplitudes, once we apply our new correction for stellar activity, we arrive exactly to the same RV rms in the residuals, meaning that for activity correction, the SN parameters does not help.
+We note that when comparing the activity correction presented in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, we only see a slight improvement brought by our proposed correction.
+
+We checked if some RV estimates were better at finding planets in RV data affected by observed stellar signals.
+When using the new correction proposed in this paper to mitigate the effect from stellar activity, and when assesing planetary detection based on periodogram analysis, we find very similar detection limits for the three RV estimates presented in this paper.
+Therefore it seems that any of the RV estimate can be used to search for planetary signals.
+
+Finally, we investigated the precision of each of the SN and Normal parameters including the BIS SPAN.
+It turns out that the mean of the SN should not be used to get precise RVs as the standard errors on this parameter is 60\% greater than when taking the mean of the Normal distribution.
+However, the median of the SN should be used, as it is 10\% more precise than the mean of the Normal.
+Regarding the asymmetry estimates, we observe that $\gamma$ has a precision15\% better than the BIS SPAN.
+It is therefore clear in this case that the SN parameters are more precise to measure the barycenter and the asymmetry of the CCF.}
+
+%Finally, we also encourage the use of bootstrapping to estimate more realistic errors on the different parameters of the Normal or SN fitted to the CCF, mainly in the low SNR regime where a gain of 50\% can be reached.
+This takes significantly more time, but note that 100 bootstrapped dataset are enough to get a good estimation of errors.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion} \label{sec:conclu}
+
+\xavier{When searching for small-mass exoplanets using the RV technique, it is crucial to get the best precision possible on the determination of the RV, but also to measure precisely the shape variations of the CCF, as such variations are induced by stellar activity, and not by planets.
+The correlations between the width of the CCF and the RV, and the asymmetry of the CCF and the RV are used as a way to assess if the measurements are affect by stellar activity signals, therefore, the stronger the correlation, the better we can probe small level of stellar activity.
+
+In this paper we introduced a novel approach based on the Skew Normal (SN) density to retrieve the RV and shape variation of the CCF.
+This new method is compared to the usual one, where a Normal density is fitted to the CCF to retrieve the information on the RV and the width of the CCF, and a bisector analysis allows to retrieve the asymmetry of the CCF using the BIS SPAN.
+In addition, we also compare this novel approach to other parameterisations of the CCF asymmetry that have been shown to be more sensitive to activity signals \citep[][]{Boisse-2011,Figueira-2013}.
+
+In all the different tests we could conduct in this paper, the SN parameters were doing as well as the parameters derived when fitting a Normal distribution and calculating the BIS SPAN.
+Moreover, in some cases, we were getting better results when using the SN parameters.
+This is the case when looking at the correlations between the CCF asymmetry and the RV or the CCF width and the RV.
+The SN parameters $\gamma$, SN FWHM and the mean of the SN density always show stronger correlation that any of the parameters derived by the Normal density fit and the BIS SPAN, or the different asymmetry parametrization presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
+Those SN parameters can therefore probe better stellar activity signals.
+In addition, the precision measured on the median of the SN density and the asymmetry of the SN density are 10 and 15\% more precise than the mean of the Normal and BIS SPAN, respectively.
+
+Because of these advantages of using the SN parameters compared to the Normal parameters, BIS SPAN, and all the asymmetry parameters described in \citet{Boisse-2011} and \citet{Figueira-2013}.
+we strongly encourage the community of using this new parametrization of the CCF.
+Correlations between the asymmetry and the mean of the SN, and between the width and the mean of the SN should be used to probe better stellar signals in RV data, and the median of the SN should be used as the new definition for RV.
 }
+
+%the RVs of the star can be calculated as the mean of the SN, whereas its asymmetry parameter $\gamma$ can be naturally used for retrieving information about the asymmetry of the CCF.
+Because of the natural correlation between the RVs and the asymmetry parameter, a linear combination of both $\gamma$ and the FWHM has been implemented for correcting the RVs from stellar activity, allowing us to retrieve a more precise RVs.
+
+%In order to get the standard errors for the estimated parameters, rather than using the common $noise$ statistic, we created a simulated procedure based on perturbing each point of the CCF according to its measurement error.
+Then, by getting from the original profile line $100$ simulated profiles, we run the SN fitting analyses, allowing us retrieving for all the parameter of interests an estimation for their standard errors.
+Concerning the standard error associated to the means of the densitys, the SN fit leads to slightly larger standard errors respect when running the Normal fit.
+This fact can be explained by noticing that as a simulated CCF is created according to the procedure described above, we expect slightly differences on the asymmetry of the CCF as well.
+The natural correlation between the RVs of the star and $\gamma$, where the mean of the SN is shifted in the direction of the asymmetry of the density, leads to larger uncertainties related to the RVs of the star.
+The latter consideration provides a further justification for correcting the RVs of the star from stellar activity and explains why this correction is more helpful when running the proposed analysis rather than the classic Normal fit.
+Concerning the standard errors related to the asymmetry parameters, when using the SN fit the uncertainties are $10 \%$ smaller than using the classic BIS SPAN.
+In conclusion, we showed how using the SN fit provides in an unique step a better understanding of the stellar activity through using the asymmetry parameter $\gamma$ rather than using the common statistics such as the BIS SPAN or other indicators.
+On top of that, when focusing on low signal-to-noise cases, the SN procedure showed how statistically significant results are retrieved with the proposed approach in terms of correlation between the asymmetry of the profile line and the RVs, whereas for the previous analyses this correlation does not result statistically significant.
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
+\section{Acknowledgements}
+
+We are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
+XD is grateful to The Branco Weiss Fellowship--Society in Science for its financial support.
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
+%\section{Appendix}
+\appendix
+\section{Appendix} \label{appendix}
+
+In this Appendix we present the analyses conducted on other 4 stars: HD192310, HD10700, HD215152 and finally Corot-7.
+
+\umberto{Add further information about the stars here presented.}\xavier{}
+
+Table \ref{table:summaryStars} summarizes the results obtained by the SN fit and the some of the results based on the Normal fit.
+The results are all consistent with the conclusions derived by the analyses on Alpha Centauri b.
+The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and RV for all the considered stars.
+The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV for three of the four stars.
+Also for all these stars we corrected the originally estimated RV's from spurious variations in RV's caused by stellar activity, using Eq.
+\ref{eq:RV:correction}.
+Fig.
+\ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RV's.
+While the Normal and SN residuals, once corrected for stellar activity, are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$, the results of the analyses on the star $\text{HD}215152$ (whose CCF's have lower SNR respect to the previous two analyzed stars) suggest that the residuals for the Normal are $0.054 \ms$ higher than the residuals retrieved with the SN analysis.
+Finally, the results of the analysis on $\text{Corot }7$, whose CCF's have lowest SNR, show that once corrected from stellar activity the residuals from the Normal fit are $0.336 \ms$ higher than the residuals retrieved with the SN analysis.
+
+\small{
+\begin{table*}[!t]
+\caption{Subset of notable correlations between the asymmetry parameter (and the FWHM) and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.
+The complete results of the analyses of the correlations for the four stars are presented in Fig.
+\ref{fig:Gliese785:corrPlot}--\ref{fig:Corot7:corrPlot}.}
+\begin{tabular}{ccccccccc}
+\textbf{Star}          &\textbf{ \# CCFs}  &   \textbf{$\text{R}(\text{SN }\gamma, \text{Bis-Span})$} & \textbf{$\text{slope}(\text{SN }\gamma, \text{Bis-Span})$} &   \textbf{$\text{R}(\text{SN }\gamma, \text{SN mean RV})$}\\
+\hline
+\hline
+ $\text{HD}192310  $          &    $1577$    & $0.888$ & $0.786$ & $0.669 (0.64; 0.695)$\\
+\hline
+ $\text{HD}10700 $            &    $7928$    & $0.78$ & $0.604$ & $0.322 (0.302; 0.342)$\\
+\hline
+ $\text{HD}215152 $          &     $273$   &  $ 0.763$ & $0.794$ & $0.571 (0.485; 0.646)$ \\
+\hline
+ $\text{Corot }7$     &     $173$    &  $0.814$  & $0.607$ & $0.561 (0.450; 0.656)$  \\
+\hline
+\rule{0pt}{2ex}    & & & &\\
+\textbf{Star}          &\textbf{$\text{R}(\text{Bis-Span}, \text{RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{SN mean RV})$}  & \textbf{$\text{R}(\text{FWHM}, \text{RV})$} \\
+\hline
+\hline
+ $\text{HD}192310  $& $0.329 (0.285; 0.373)$  & $-0.333 (-0.376; -0.289)$ & $0.666 (0.637; 0.692)$ & $0.476 (0.4367; 0.514)$\\
+\hline
+ $\text{HD}10700 $ & $-0.073 (-0.095; -0.0051)$ & $0.127 (0.105; 0.148)$ & $0.421 (0.403; 0.439)$ & $0.529 (0.513; 0.545)$ \\
+\hline
+ $\text{HD}215152 $& $-0.067 (-0.184; 0.052)$  & $0.269 (0.155; 0.376)$ & $0.210 (0.094; 0.321)$ & $-0.138 (-0.253; -0.020)$ \\
+\hline
+ $\text{Corot }7$ & $0.092 (-0.058; 0.238)$ & $-0.335 (-0.228; -0.082)$ & $-0.709 (0.626;0.776)$ & $0.595 (0.489; 0.683)$ \\
+\hline
+\rule{0pt}{2ex}    & & & &\\
+\end{tabular}
+\label{table:summaryStars}
+\end{table*}
+}
+
+%HD192310
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
+   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}192310$.
+The last three plots show the correlation between the FWHM and the RV's for $\text{HD}192310$ using respectively the SN and the Normal fits.
+The p--values associated with each $R$ is statistically different from $0$.}
+   \label{fig:Gliese785:corrPlot}
+\end{center}
+\end{figure*}
+
+\begin{figure*} 
+\begin{center}
+\includegraphics[height = 6in]{NEW_CORRECTIONHD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of RV's for $\text{HD}192310$  using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.
+\ref{eq:RV:correction}.
+Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
+   \label{fig:HD192310:correctionRV}
+\end{center}
+\end{figure*}
+
+%HD10700
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
+   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}10700$.
+The last three plots show the correlation between the FWHM and the RV's for $\text{HD}10700$ using respectively the SN and the Normal fits.
+The p--values associated with each $R$ is statistically different from $0$.}
+   \label{fig:Tau:corrPlot}
+\end{center}
+\end{figure*}
+
+\begin{figure*} 
+\begin{center}
+\includegraphics[height = 6in]{NEW_CORRECTIONHD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of RV's for $\text{HD}10700$  using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.
+\ref{eq:RV:correction}.
+Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
+   \label{fig:HD10700:correctionRV}
+\end{center}
+\end{figure*}
+
+%HD215152
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
+   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}215152$.
+The last three plots show the correlation between the FWHM and the RV's for $\text{HD}215152$ using respectively the SN and the Normal fits.
+Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
+   \label{fig:HD215152:corrPlot}
+\end{center}
+\end{figure*}
+
+\begin{figure*} 
+\begin{center}
+\includegraphics[height = 6in]{NEW_CORRECTIONHD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of RV's for $\text{HD}215152$ using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.
+\ref{eq:RV:correction}.
+Once corrected for stellar activity, the residuals for the Normal are $0.054$ \ms higher than the residuals retrieved with the SN analysis.}
+   \label{fig:HD215152:correctionRV}
+\end{center}
+\end{figure*}
+
+%Corot-7
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
+   \caption{Correlation between the asymmetry parameters and the RV's for  $\text{Corot }7$.
+The last three plots show the correlation between the FWHM and the RV's for  $\text{Corot }7$ using respectively the SN and the Normal fits.
+Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
+   \label{fig:Corot7:corrPlot}
+\end{center}
+\end{figure*}
+
+\begin{figure*} 
+\begin{center}
+\includegraphics[height = 6in]{NEW_CORRECTIONLRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of RV's for  $\text{Corot }7$ using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.
+\ref{eq:RV:correction}.
+Once corrected for stellar activity, the residuals for the Normal are $0.336$ \ms higher than the residuals retrieved with the SN analysis.}
+   \label{fig:Corot-7:correctionRV}
+\end{center}
+\end{figure*}
+
+%%%%%%%
+%\iffalse
+%%\subsection{HD192310}  \label{sec:Gl785}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{[0]HD19231_HistogramsDiff.pdf} 
+%   \caption{RVs comparison for HD192310 considering a Normal and a SN fitting (using both the mean and the median).}
+%   \label{fig:HD192310:RV}
+%\end{figure*}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{HD19231_[2]gamma_vs_bisspan.pdf} 
+%   \caption{Correlation between $\gamma$ and the BIS SPAN for HD192310.}
+%   \label{fig:Gliese785:corr.gamma}
+%\end{figure*}
+%%
+%
+%
+%%\subsection{Tau Ceti}  \label{sec:Taucet}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{[0]TauCeti_HistogramsDiff.pdf} 
+%   \caption{RVs comparison for Tau Ceti considering a Normal and a SN fitting (using both the mean and the median).}
+%   \label{fig:Tau Ceti:RV}
+%\end{figure*}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{HD10700_[2]gamma_vs_bisspan.pdf} 
+%   \caption{Correlation between $\gamma$ and the BIS SPAN for Tau Ceti.}
+%   \label{fig:Tau:corr.gamma}
+%\end{figure*}
+%%
+%
+%
+%%\subsection{HD215152}  \label{sec:HD215152}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{[0]HD21515_HistogramsDiff.pdf} 
+%   \caption{RVs comparison for HD215152 considering a Normal and a SN fitting (using both the mean and the median).}
+%   \label{fig:HD215152:RV}
+%\end{figure*}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{HD21515_[2]gamma_vs_bisspan.pdf} 
+%   \caption{Correlation between $\gamma$ and the BIS SPAN for HD 215152.}
+%   \label{fig:HD215152:corr.gamma}
+%\end{figure*}
+%%
+%
+%
+%%\subsection{Corot-7}  \label{sec:Corot7}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{[0]LRa01_E_HistogramsDiff.pdf} 
+%   \caption{RVs comparison for Corot-7 considering a Normal and a SN fitting (using both the mean and the median).}
+%   \label{fig:corot7:RV}
+%\end{figure*}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{LRa01_E_[2]gamma_vs_bisspan.pdf} 
+%   \caption{Correlation between $\gamma$ and the BIS SPAN for Corot-7.}
+%   \label{fig:Corot7:corr.gamma}
+%\end{figure*}
+%%
+%\fi
+%%
 
@@
 
-\subsection{Estimation of standard errors for the CCF parameters for real stars} \label{sec:bootstrap_real_star}
-In the top plots of Fig.~\ref{fig:se} we show the different errors for the RVs, either defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels.
-The parameter SN50 corresponds to the SNR in order 50, which defines a wavelength of 550\,nm.
-In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameters derived from the bootstrap analysis fitting the Normal density.
-We first see that the errors on the CCF parameters only depends on the SNR and do not depend on the spectral type.
-This is true if the spectral type are not too different though, like here where we show the results for G and K dwarfs.
-
-Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.6$ when using SN mean RV and $0.9$ when using SN median RV.
-In other words, by using SN median RV as parameter that defines the radial velocity of the star given a CCF, we get standard errors $10\%$ smaller than using the Normal fit and its corresponding mean.
-This result is consistent with what we observed with the simulation from SOAP presented in Sec.
-\ref{sec:soap}.
-
-Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable.
-Therefore, the precision in the width of the CCF is the comparable if we fit a Normal or a SN to the CCF.
-
-Finally, for the errors in evaluating the asymmetry of the CCF, we see that, when fitting the SN to the CCF, the asymmetry errors are $15\%$ smaller.
-Therefore, the SN fit gives a better precision in CCF asymmetry than what can be reached using BIS SPAN.
-We recall moreover that, using the SN, all parameters are automatically retrieved in 1 single step, while in the common approach the RV and the BIS SPAN are calculated separately.
-
-%
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
-   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
-When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
-To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
-Note that for the asymmetry, the error in BIS SPAN is in \kms.
-To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
-   \label{fig:se}
-\end{center}
-\end{figure*}
-
-%, using the spectrum derivative
-%, the pure photon-noise error on RV measured 
-%Together with the pointwise estimates, retrieving the standard errors for the RVs of the star, $\gamma$ and the FWHM provides information about the uncertainties associated to each parameter.
-Since the procedure for retrieving the RVs of the star consists in fitting with a density function a CCF, getting the standard errors for all the parameter of interests cannot be done by using the common asymptotic theory.
-The implementation of a standard bootstrap analysis cannot as well be done, because the points of the CCF are highly correlated.
-In the analysis of the present work, in order to get the standard errors for the parameters of interest for a particular CCF, we moved each point of this CCF according to its measurement errors, producing $100$ simulated CCFs from the original one.
-Then we run both the Normal and the SN analyses on these simulated CCFs, letting us to retrieve an evaluation of the standard errors.
-This operation has been repeated for all the CCFs available for the analyzed stars.
-The comparison between the standard errors retrieved in this way with the classic noise parameter, {\color{red} obtained by using the Gray's equation cit.
-Gray (1983)} are presented in Fig.~ \ref{fig:se}.
-{\color{red} Xavier: Is it correct how the noise parameter is obtained?
-Or it is simply $\sqrt(photons)$?}
-
-%Given the strong correlation between the $\gamma$ parameter of the SN and its mean, the standard errors are larger respect the Normal fitting analysis.
-This fact confirms how correcting the RVs for stellar activity using Eq.
-\ref{eq:RV:correction} is more helpful when using the SN fitting.
-The standard errors for the FWHM are comparable for both the SN and the Normal analyses, whereas an improvement is clearly measurable for the standard errors associated to the asymmetry indicators.
-The last plot in Fig.~\ref{fig:se} shows that the standard errors for $\gamma$ are $10 \%$ smaller than the ones retrieved for the BIS SPAN.
-
-%-----------------------------------------------------------------------------------------------------------------------------------------------
-\section{Discussion} \label{sec:discu}
-
-An analysis of the CCF residuals after fitting a Normal or SN density shows that the SN is a slightly better model to explain the shape of the CCF.
-This comes from the fact that CCF's present a natural asymmetry due the convective blueshift.
-
-We tested at first our assumptions by using simulated CCF's retrieved using the software SOAP 2.0.
-We then compared for five real stars the difference between the RV's (defined as mean of a Normal, mean of the SN or median of the SN), FWHM and asymmetry (BIS SPAN in the Normal case and $\gamma$ in the SN case).
-The $\gamma$ parameter is linearly dependent on the BIS SPAN, with always a strong correlation coefficient.
-%To compare $\gamma$, that do not have any units, with BIS SPAN expressed in \kms, one has simply to multiply $\gamma$ by the slope of the linear dependence between $\gamma$ and BIS SPAN. 
-The slope of this linear correlation changes depending on the studied star. This is probably because the spectral type is different, therefore the effects from stellar activity are different.
-
-When using as parameter for the RV the mean of the SN, the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal.
-However, once the RV is defined as the median of the SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
-When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma$ in the SN case) with respect to the RV's (RV's in the Normal case or SN RV's in the SN case), we observe that the correlations are always stronger for the parameters of the SN.
-Therefore, the SN parameters are more sensitive to activity.
-In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of $0.322$ between $\gamma$ and SN mean RV, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.$225$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion} \label{sec:conclu}
-
-In this paper we introduced a novel approach based on the Skew Normal (SN) density to retrieve RV's and shape variations in the CCF of stars.
-When searching for small-mass exoplanets using the RV technique, it is essential to understand variation of the shape of the CCF, which is a proxy for stellar activity effects.
-The standard approach consist at first to fit a Normal density to the CCF to get the RV and FWHM, defined as the mean and the FWHM of the Normal density, and then to measure the asymmetry of the CCF by calculating the BIS SPAN.
-FWHM and BIS SPAN give us information on the line shape that are used to probe stellar activity signals.
-
-In this paper we propose to conduct the analysis fitting a SN density to the CCF.
-Since the CCF presents a natural asymmetry due the convective blueshift, the SN density can in principle better catch these aspects respect the Normal fit.
-On top of that, by using the SN density to fit CCF's, we can measure simultaneously the RV of the star, the width and the asymmetry of the CCF.
-
-Starting from the simulation environment SOAP and then moving to real stars, we showed that using the SN density to fit CCF's leads to a significant improvement to probing stellar activity.
-While for the Normal density mean and median are equivalent, using the SN fit different location parameters can be tested.
-While the median of the SN is a more robust statistic respect variations in the shape of the CCF, the mean of the SN is more sensible to changes in the asymmetry of the CCF.
-We suggest to use as parameter that defines the RV of the star the median of the SN, since the standard errors related to this parameter working with CCF's from real stars are on average $10\%$ smaller than the standard errors retrieved using the Normal density.
-To evaluate changes in the asymmetry of the CCF, we suggest to use the mean of the SN.
-The correlation between SN mean RV and SN FWHM and the correlation between SN mean RV and $\gamma$ (the asymmetry parameter of the SN) are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
-The precision on the asymmetry measured by $\gamma$ is greater than the one on BIS SPAN by $\sim$15\%.
-Therefore when searching for rotational periods in the data, or applying Gaussian Processes to account for stellar activity signals, the SN parameters should be used.
-
-Because of stellar activity the estimated RV's are contaminated by spurious variations.
-We propose to use a function that corrects from stellar activity that beyond the width and the asymmetry parameters of the CCF includes also the contrast parameter A and the fourth parameter defined as the interaction between width and the asymmetry parameters of the CCF.
-We found these new two parameter helpful to explain part of the spurious variations in RV's caused by stellar activity.
-
-Finally, we also encourage the use of bootstrapping to estimate more realistic errors on the different parameters of the Normal or SN fitted to the CCF, mainly in the low SNR regime where a gain of 50\% can be reached.
-This takes significantly more time, but note that 100 bootstrapped dataset are enough to get a good estimation of errors.
-
-%the RVs of the star can be calculated as the mean of the SN, whereas its asymmetry parameter $\gamma$ can be naturally used for retrieving information about the asymmetry of the CCF.
-Because of the natural correlation between the RVs and the asymmetry parameter, a linear combination of both $\gamma$ and the FWHM has been implemented for correcting the RVs from stellar activity, allowing us to retrieve a more precise RVs.
-
-%In order to get the standard errors for the estimated parameters, rather than using the common $noise$ statistic, we created a simulated procedure based on perturbing each point of the CCF according to its measurement error.
-Then, by getting from the original profile line $100$ simulated profiles, we run the SN fitting analyses, allowing us retrieving for all the parameter of interests an estimation for their standard errors.
-Concerning the standard error associated to the means of the densitys, the SN fit leads to slightly larger standard errors respect when running the Normal fit.
-This fact can be explained by noticing that as a simulated CCF is created according to the procedure described above, we expect slightly differences on the asymmetry of the CCF as well.
-The natural correlation between the RVs of the star and $\gamma$, where the mean of the SN is shifted in the direction of the asymmetry of the density, leads to larger uncertainties related to the RVs of the star.
-The latter consideration provides a further justification for correcting the RVs of the star from stellar activity and explains why this correction is more helpful when running the proposed analysis rather than the classic Normal fit.
-Concerning the standard errors related to the asymmetry parameters, when using the SN fit the uncertainties are $10 \%$ smaller than using the classic BIS SPAN.
-In conclusion, we showed how using the SN fit provides in an unique step a better understanding of the stellar activity through using the asymmetry parameter $\gamma$ rather than using the common statistics such as the BIS SPAN or other indicators.
-On top of that, when focusing on low signal-to-noise cases, the SN procedure showed how statistically significant results are retrieved with the proposed approach in terms of correlation between the asymmetry of the profile line and the RVs, whereas for the previous analyses this correlation does not result statistically significant.
-
-%-----------------------------------------------------------------------------------------------------------------------------------------------
-\section{Acknowledgements}
-
-We are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
-XD is grateful to The Branco Weiss Fellowship--Society in Science for its financial support.
-
-%-----------------------------------------------------------------------------------------------------------------------------------------------
-%\section{Appendix}
-\appendix
-\section{Appendix} \label{appendix}
-
-In this Appendix we present the analyses conducted on other 4 stars: HD192310, HD10700, HD215152 and finally Corot-7.
-
-\umberto{Add further information about the stars here presented.}\xavier{}
-
-Table \ref{table:summaryStars} summarizes the results obtained by the SN fit and the some of the results based on the Normal fit.
-The results are all consistent with the conclusions derived by the analyses on Alpha Centauri b.
-The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and RV for all the considered stars.
-The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV for three of the four stars.
-Also for all these stars we corrected the originally estimated RV's from spurious variations in RV's caused by stellar activity, using Eq.
-\ref{eq:RV:correction}.
-Fig.
-\ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RV's.
-While the Normal and SN residuals, once corrected for stellar activity, are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$, the results of the analyses on the star $\text{HD}215152$ (whose CCF's have lower SNR respect to the previous two analyzed stars) suggest that the residuals for the Normal are $0.054 \ms$ higher than the residuals retrieved with the SN analysis.
-Finally, the results of the analysis on $\text{Corot }7$, whose CCF's have lowest SNR, show that once corrected from stellar activity the residuals from the Normal fit are $0.336 \ms$ higher than the residuals retrieved with the SN analysis.
-
-\small{
-\begin{table}[!t]
-\scalebox{0.45}{
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
-\hline
-\textbf{Star}          &\textbf{ \# CCFs}  &   \textbf{$\text{R}(\text{SN }\gamma, \text{Bis-Span})$} & \textbf{$\text{slope}(\text{SN }\gamma, \text{Bis-Span})$} &   \textbf{$\text{R}(\text{SN }\gamma, \text{SN mean RV})$} & \textbf{$\text{R}(\text{Bis-Span}, \text{RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{SN mean RV})$}  & \textbf{$\text{R}(\text{FWHM}, \text{RV})$} \\
-\hline
- $\text{HD}192310  $          &    $1577$    & $0.888$ & $0.786$ & $0.669 (0.64; 0.695)$ & $0.329 (0.285; 0.373)$  & $-0.333 (-0.376; -0.289)$ & $0.666 (0.637; 0.692)$ & $0.476 (0.4367 0.514)$\\
-\hline
- $\text{HD}10700 $            &    $7928$    & $0.78$ & $0.604$ & $0.322 (0.302; 0.342)$ & $-0.073 (-0.095; -0.0051)$ & $0.127 (0.105; 0.148)$ & $0.421 (0.403; 0.439)$ & $0.529 (0.513; 0.545)$ \\
-\hline
- $\text{HD}215152 $          &     $273$   &  $ 0.763$ & $0.794$ & $0.571 (0.485; 0.646)$ & $-0.067 (-0.184; 0.052)$  & $0.269 (0.155; 0.376)$ & $0.210 (0.094; 0.321)$ & $-0.138 (-0.253; -0.020)$ \\
-\hline
- $\text{Corot }7$     &     $173$    &  $0.814$  & $0.607$ & $0.561 (0.450; 0.656)$ & $0.092 (-0.058; 0.238)$ & $-0.335 (-0.228; -0.082)$ & $-0.709 (0.626;0.776)$ & $0.595 (0.489; 0.683)$ \\
-\hline
-\end{tabular}
-}
-\caption{Subset of notable correlations between the asymmetry parameter (and the FWHM) and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.
-The complete results of the analyses of the correlations for the four stars are presented in Fig.
-\ref{fig:Gliese785:corrPlot}--\ref{fig:Corot7:corrPlot}.}
-\label{table:summaryStars}
-\end{table}
-}
-
-%HD192310
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}192310$.
-The last three plots show the correlation between the FWHM and the RV's for $\text{HD}192310$ using respectively the SN and the Normal fits.
-The p--values associated with each $R$ is statistically different from $0$.}
-   \label{fig:Gliese785:corrPlot}
-\end{center}
-\end{figure*}
-
-\begin{figure*} 
-\begin{center}
-\includegraphics[height = 6in]{NEW_CORRECTIONHD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RV's for $\text{HD}192310$  using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.
-\ref{eq:RV:correction}.
-Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
-   \label{fig:HD192310:correctionRV}
-\end{center}
-\end{figure*}
-
-%HD10700
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}10700$.
-The last three plots show the correlation between the FWHM and the RV's for $\text{HD}10700$ using respectively the SN and the Normal fits.
-The p--values associated with each $R$ is statistically different from $0$.}
-   \label{fig:Tau:corrPlot}
-\end{center}
-\end{figure*}
-
-\begin{figure*} 
-\begin{center}
-\includegraphics[height = 6in]{NEW_CORRECTIONHD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RV's for $\text{HD}10700$  using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.
-\ref{eq:RV:correction}.
-Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
-   \label{fig:HD10700:correctionRV}
-\end{center}
-\end{figure*}
-
-%HD215152
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}215152$.
-The last three plots show the correlation between the FWHM and the RV's for $\text{HD}215152$ using respectively the SN and the Normal fits.
-Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
-   \label{fig:HD215152:corrPlot}
-\end{center}
-\end{figure*}
-
-\begin{figure*} 
-\begin{center}
-\includegraphics[height = 6in]{NEW_CORRECTIONHD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RV's for $\text{HD}215152$ using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.
-\ref{eq:RV:correction}.
-Once corrected for stellar activity, the residuals for the Normal are $0.054$ \ms higher than the residuals retrieved with the SN analysis.}
-   \label{fig:HD215152:correctionRV}
-\end{center}
-\end{figure*}
-
-%Corot-7
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RV's for  $\text{Corot }7$.
-The last three plots show the correlation between the FWHM and the RV's for  $\text{Corot }7$ using respectively the SN and the Normal fits.
-Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
-   \label{fig:Corot7:corrPlot}
-\end{center}
-\end{figure*}
-
-\begin{figure*} 
-\begin{center}
-\includegraphics[height = 6in]{NEW_CORRECTIONLRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RV's for  $\text{Corot }7$ using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.
-\ref{eq:RV:correction}.
-Once corrected for stellar activity, the residuals for the Normal are $0.336$ \ms higher than the residuals retrieved with the SN analysis.}
-   \label{fig:Corot-7:correctionRV}
-\end{center}
-\end{figure*}
-
-%%%%%%%
-%\iffalse
-%%\subsection{HD192310}  \label{sec:Gl785}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{[0]HD19231_HistogramsDiff.pdf} 
-%   \caption{RVs comparison for HD192310 considering a Normal and a SN fitting (using both the mean and the median).}
-%   \label{fig:HD192310:RV}
-%\end{figure*}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{HD19231_[2]gamma_vs_bisspan.pdf} 
-%   \caption{Correlation between $\gamma$ and the BIS SPAN for HD192310.}
-%   \label{fig:Gliese785:corr.gamma}
-%\end{figure*}
-%%
-%
-%
-%%\subsection{Tau Ceti}  \label{sec:Taucet}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{[0]TauCeti_HistogramsDiff.pdf} 
-%   \caption{RVs comparison for Tau Ceti considering a Normal and a SN fitting (using both the mean and the median).}
-%   \label{fig:Tau Ceti:RV}
-%\end{figure*}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{HD10700_[2]gamma_vs_bisspan.pdf} 
-%   \caption{Correlation between $\gamma$ and the BIS SPAN for Tau Ceti.}
-%   \label{fig:Tau:corr.gamma}
-%\end{figure*}
-%%
-%
-%
-%%\subsection{HD215152}  \label{sec:HD215152}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{[0]HD21515_HistogramsDiff.pdf} 
-%   \caption{RVs comparison for HD215152 considering a Normal and a SN fitting (using both the mean and the median).}
-%   \label{fig:HD215152:RV}
-%\end{figure*}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{HD21515_[2]gamma_vs_bisspan.pdf} 
-%   \caption{Correlation between $\gamma$ and the BIS SPAN for HD 215152.}
-%   \label{fig:HD215152:corr.gamma}
-%\end{figure*}
-%%
-%
-%
-%%\subsection{Corot-7}  \label{sec:Corot7}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{[0]LRa01_E_HistogramsDiff.pdf} 
-%   \caption{RVs comparison for Corot-7 considering a Normal and a SN fitting (using both the mean and the median).}
-%   \label{fig:corot7:RV}
-%\end{figure*}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{LRa01_E_[2]gamma_vs_bisspan.pdf} 
-%   \caption{Correlation between $\gamma$ and the BIS SPAN for Corot-7.}
-%   \label{fig:Corot7:corr.gamma}
-%\end{figure*}
-%%
-%\fi
-%%
-
 %%-----------------------------------------------------------------------------------------------------------------------------------------------

### 2018-06-02 manuscript.tex
Went through Sect 1, 2, 3 and did some small modif, updated the text according to Jessi's comments

@@
 \usepackage{hyperref}
+%\usepackage[draft]{hyperref}
 \bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
@@
 %
-{When considering the real observations, the correlation between the RV's and the asymmetry of the CCF and the correlation between the RV's and the width of the CCF are stronger when using the parameters derived from the SN than the Normal approach.
+{When considering the real observations, the correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are stronger when using the parameters derived from the SN than the Normal approach.
 This suggests that the CCF asymmetry and the CCF width derived using a SN may be more sensitive to stellar activity, which can be helpful with estimating stellar rotational periods and generally characterizing the stellar activity signals.
-The estimated uncertainties in the estimated RV's using the proposed SN approach are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal, and the estimated uncertainties on the SN asymmetry parameter are on average $15\%$ smaller than the commonly used Bisector Inverse Slope Span (BIS SPAN) approach for estimating the asymmetry of the CCF.
+The estimated uncertainties in the estimated RVs using the proposed SN approach are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal, and the estimated uncertainties on the SN asymmetry parameter are on average $15\%$ smaller than the commonly used Bisector Inverse Slope Span (BIS SPAN) approach for estimating the asymmetry of the CCF.
 }
@@
 %{The derived benefits of using the proposed SN approach includes an asymmetry parameter along with several options for estimating the RV, while the Normal model only includes an RV estimate and requires a separate procedure for estimating the asymmetry.
-Furthermore, the estimated uncertainties on the RV's and the asymmetry parameter are smaller in the SN setting.}
-%The correlation between the RV's and the asymmetry of the CCF and the correlation between the RV's and the width of the CCF are always stronger when using the parameters derived from the SN in the case of real observations.
+Furthermore, the estimated uncertainties on the RVs and the asymmetry parameter are smaller in the SN setting.}
+%The correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are always stronger when using the parameters derived from the SN in the case of real observations.
 Therefore the CCF asymmetry and the CCF width derived using a SN are more sensitive to stellar activity, which allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals.
-The precision on the estimated set of RV's, derived using the median of the fitted SN densities are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
+The precision on the estimated set of RVs, derived using the median of the fitted SN densities are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
 In addition, the uncertainties related to the asymmetry parameter derived from the SN are on average $15\%$ smaller than the ones calculated on the common Bisector Inverse Slope Span (BIS SPAN).
-We strongly encourage the use of the SN density rather than the Normal density, because this allows us to retrieve in one single fit the different moments of the CCF, because the derived moments better catch stellar activity signals and finally because the standard errors on the RV's and the the asymmetry parameter are smaller than the one estimated with the Normal fit.
+We strongly encourage the use of the SN density rather than the Normal density, because this allows us to retrieve in one single fit the different moments of the CCF, because the derived moments better catch stellar activity signals and finally because the standard errors on the RVs and the the asymmetry parameter are smaller than the one estimated with the Normal fit.
 
@@
 
-When working with radial velocities (RV's), one of the main limitations to the detection of small-mass exoplanets is no longer the precision of the instruments used, but the different sources of variability induced by the stars \citep[e.g.][]{Feng:2017aa, Dumusque:2017aa, Rajpaul-2015, Robertson-2014}.
-Stellar oscillations, granulation phenomena, and stellar activity can all induce apparent RV signals \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} that are above the meter-per-second precision reached by the best high-resolution spectrographs \citep[HARPS, HARPS-N,][]{Mayor-2003,Cosentino-2012}.
+When working with radial-velocities data (RVs), one of the main limitations to the detection of small-mass exoplanets is no longer the precision of the instruments used, but the different sources of variability induced by the stars \citep[e.g.][]{Feng:2017aa, Dumusque:2017aa, Rajpaul-2015, Robertson-2014}.
+Stellar oscillations, granulation phenomena, and stellar activity can all induce apparent RV signals that are above the meter-per-second precision \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} reached by the best high-resolution spectrographs \citep[HARPS, HARPS-N,][]{Mayor-2003,Cosentino-2012}.
 %
 It is therefore mandatory to better understand stellar signals and to develop methods to correct for them, if in the near future we want to detect or confirm an Earth-twin planet using the RV technique.
-This is even more true now that instrument like the Echelle SPectrograph for Rocky Exoplanet and Stable Spectroscopic Observations (ESPRESSO) \citep{Pepe-2014} and EXtreme PREcision Spectrometer (EXPRES) \citep{fischer2016state} should have the stability to detect such signals.
+This is even more true now that instruments like the Echelle SPectrograph for Rocky Exoplanet and Stable Spectroscopic Observations (ESPRESSO) \citep{Pepe-2014} and the EXtreme PREcision Spectrometer (EXPRES) \citep{fischer2016state} should reach the stability to detect such signals.
 However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging and false detections could plague the field.
@@
 One of the most challenging stellar signal to characterize and to correct for is the signal induced by stellar activity. 
-Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, which can induce spurious RV's variations \citep{Meunier-2010a, Dumusque-2014b}.
+Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, which can induce spurious RVs variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b, Borgniet-2015}.
 In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}.
-However, on quiet GKM dwarfs, the main target for precise RV's measurements, stellar activity can induce signals of a few \ms.
+However, on quiet GKM dwarfs, the main target for precise RVs measurements, stellar activity can induce signals of a few \ms.
 This corresponds physically to variations smaller than 1/100th of a pixel on the detector making the changing shape of the spectral lines challenging to detect.
-
-In order to measure such tiny variations, a common approach is to average the information of all the lines in the spectrum by cross correlating the stellar spectrum with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}.
+In order to measure such tiny variations, a common approach is to average the information of all the lines in the spectrum by cross correlating the stellar spectrum with a synthetic or an observed stellar template \citep[][]{Baranne-1996,Pepe-2002a, Anglada-Escude-2012}.
 The result of this operation gives us the cross-correlation function (CCF).
-The CCF gives the spectrum's cross-correlation with the template as the template is shifted according to different RVs.
-%
-To measure the Doppler-shift between different spectra and therefore to retrieve the RV's of a star as a function of time, the variations of the CCF barycenter are calculated. 
+%The CCF gives the spectrum's cross-correlation with the template as the template is shifted according to different RVs.
+%
+To measure the Doppler-shift between different spectra and therefore to retrieve the RVs of a star as a function of time, the variations of the CCF barycenter are calculated. 
 The barycenter is generally estimated by fitting a Normal density to the CCF and retaining its mean.
 Variations in line shape between different spectra, which indicate the presence of signals induced by stellar activity, are measured by analyzing the different moments of the CCF.
-Usually, the width of the CCF is estimated using the full-width half-maximum (FWHM) of the fitted Normal density, and its asymmetry using the the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
+Usually, the width of the CCF is estimated using the full-width half-maximum (FWHM) of the fitted Normal density, and its asymmetry by calculating the CCF bisector and measuring the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
 
@@
 It is also common to add a Gaussian process to the model to account for the correlated noise induced by stellar activity.
-The hyperparameters of the Gaussian process can be trained on different activity indicators \citep{Haywood-2014,Rajpaul-2015}.
-It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated with the RV's but also for which we can obtain the best precision.
+The hyperparameters of the Gaussian process can be trained on different activity indicators \citep{Haywood-2014,Rajpaul-2015} or directly on the RVs \citep{Faria-2016a}.
+It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated with the RVs but also for which we can obtain the best precision.
 
@@
 %
-\citet{Figueira-2013} studied the use of two new indicators, bi-Gauss and $V_{asy}$.
+\citet{Figueira-2013} studied the use of new indicators, BIS-, BIS+, bi-Gauss and $V_{asy}$.
 The authors were able to show that when using bi-Gauss, the amplitude in asymmetry is 30\% larger than when using BIS SPAN, therefore allowing the detection of lower levels of activity.
@@
 %
-In Sec.~\ref{sec:31} we propose an expanded linear model used to correct the estimated RV's from the inferred stellar activity, which extends the linear models previously proposed for this purpose \citep{Dumusque:2017aa,Feng:2017aa}.
-%
-In Sec.~\ref{sec:soap} the performance of the SN fit to the CCF is investigated using simulations coming from the Spot Oscillation And Planet (SOAP) 2.0 \citep{Dumusque-2014b}, followed by an analysis of real observations in Sec.~\ref{sec:4}.
-%
-Sec.~\ref{sec:5} considers derived error bars for the different estimated CCF parameters, and finally a discussion of the results and conclusions are included in Sec.~\ref{sec:discu} and Sec.~\ref{sec:conclu}, respectively.
+In Sec.~\ref{sec:31} we propose an expanded linear model to correct for stellar activity signals in RVs, which extends the linear models previously proposed for this purpose \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
+%
+In Sec.~\ref{sec:soap} the performance of the SN fit to the CCF is investigated using simulations coming from the Spot Oscillation And Planet 2.0 code \citep[SOAP 2.0,][]{Dumusque-2014b}, followed by an analysis of real observations in Sec.~\ref{sec:4}.
+%
+Sec.~\ref{sec:5} considers derived error bars for the different estimated CCF parameters, and finally a discussion of the results and conclusions are included in Secs.~\ref{sec:discu} and ~\ref{sec:conclu}, respectively.
 
@@
 In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution, rather than simply a location and scale parameter, and $\gamma$ provides an measure of the skewness of the SN.
-Along with the mean of the SN, we consider the median of the distribution as a measure of center, which is used in the proposed method.
+Along with the mean of the SN, we consider the median of the distribution as a measure of its barycenter.
 See Table~\ref{tab:cp_values} for the medians of the SN densities displayed in Fig.~\ref{fig:SN.plot}.
+
 %The median of the SN, and in general the median of an absolute continuous random variable, is defined as the value $m$ such that\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}:
@@
 \begin{center}
-   %\topcaption{Table captions are better up top} % requires the topcapt package
+   \caption{CP values $(\mu, \sigma^2, \gamma)$ along with the median corresponding to the $\alpha$ values shown in Fig.~\ref{fig:SN.plot}, with location parameter $\xi = 0$ and scale parameter $\omega = 1$.
+Values are rounded to three decimal places.}
+   \label{tab:cp_values}
    \begin{tabular}{|ccccc|} % Column formatting, @{} suppresses leading/trailing space
@@
    \end{tabular}
-   \caption{CP values $(\mu, \sigma^2, \gamma)$ along with the median corresponding to the $\alpha$ values shown in Fig.~\ref{fig:SN.plot}, with location parameter $\xi = 0$ and scale parameter $\omega = 1$.
-Values are rounded to three decimal places.}
-   \label{tab:cp_values}
+
 \end{center}
@@
 %
-where C is an unknown offset for the continuum of the CCF, A is the unknown amplitude of the CCF, commonly referred to as the contrast, and $\mu$, $\sigma^2$ and $\gamma$ are the mean, variance and skewness of the SN as defined above.
+where C is an unknown offset for the continuum of the CCF, A is the unknown amplitude of the CCF, some times referred to as the CCF contrast, and $\mu$, $\sigma^2$ and $\gamma$ are the mean, variance and skewness of the SN as defined above.
 The values $x_1, \ldots, x_n$ are the different values of the x-axis of the CCF, generally in velocity units (e.g. \ms).
@@
 
-To evaluate the strength of the correlation between the estimated RV's and the different stellar activity indicators, we calculated the Pearson correlation coefficient, $R$, which in its general form is defined as:
+To evaluate the strength of the correlation between the estimated RVs and the different stellar activity indicators, we calculated the Pearson correlation coefficient, $R$, which in its general form is defined as:
 %
@@
 
-When fitting for planetary signals in RV data, it is common to include linear dependencies with the BIS SPAN and the FWHM and to take into account the signal induced by stellar activity \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
+When fitting for planetary signals in RV data, it is common to include linear dependencies with the BIS SPAN and the FWHM to take into account the signal induced by stellar activity \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
 %Some people also include the \logrhk, however, \citet{Feng-2018} show that this is probably not a good choice as \logrhk and RV are not well correlated.
@@
 This interaction term can account for possible interactions between SN FWHM (or FWHM) and $\gamma$ (or BIS SPAN), meaning that each  variables' association with the response, $RV_{\text{activity}}$, depends also on the other variable.
-%while the association between in this case BIS SPAN and FWHM (or $\gamma$ and SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant.
+%while the association between in this case BIS SPAN and FWHM (or $\gamma$ and SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RVs is not constant.
 In particular the effect differs at different values of the other values.
@@
 
-\jessi{Is the following paragraph needed?
-Is any model selection actually carried out here?
-It seems the model of Eq.~\ref{eq:RV:correction} is fit, and then the significance of the variables are discussed, but no attempts are really made to remove/add/step through the various model options.
-The point about multicollinearity is probably good to keep though.}
-When working with a linear regression, there are several ways to select the variables to include in the model.
-While usually the stepwise technique is used \citep{efroymson1960multiple,hocking1976biometrics}, the proposed function defined in Eq.~\ref{eq:RV:correction}, that accounts for stellar activity, is the result of statistical and astronomical considerations.
+The proposed function defined in Eq.~\ref{eq:RV:correction} is the result of statistical and astronomical considerations.
 In particular we checked that the correlations between the proposed parameters were not approaching one: if it was the case, the matrix needed to calculate the estimates would be singular, hence non invertible.
@@
 A detailed discussion of the topic can be found in the book by \citet{belsley1991}.
-It is common to see some correlation between the amplitude parameter $A$ and the FWHM (or SN FWHM) of the CCF.
-However, in the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ and therefore, the problem of multicollinearity is avoided.
-Finally, we investigate as well the statistical significant of the interaction term between $A$ and the width, and $A$ and the asymmetry of the CC, however, those interaction were relevant for accounting for stellar signal.
+In the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ between the asymmetry and width parameters and therefore, the problem of multicollinearity is avoided.
+Note that we investigated the statistical significant of the interaction term between $A$ and the width, and $A$ and the asymmetry of the CCF, however, those interaction were not relevant for accounting for stellar signal.
 
@@
 
-For the simulations discussed below, a star similar to the Sun was modeled.
-The stellar rotational period is set to 25.0 days, the radius to a solar radius and the star is seen equator on.
-\jessi{The previous sentence seems incomplete and I'm not sure how to update it.}
-The stellar effective temperature is set to 5778 K (NASA Planetary Fact Sheets)\jessi{Is there a full citation available for this NASA fact sheet?
-Also, why is it referenced?
-Is the effective temperature supposed to be similar to the Sun?}, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011} are used.
-In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generate with a width of 40 \kms and a resolution of 115'000.
-\jessi{Is a resolution of ``115'000'' standard notation?
-I'm not sure what it means.}
+For the simulations discussed below, a star similar to the Sun was modeled, with a solar disc of one solar radius seen equator-on, and with a stellar rotational period set to 25.0 days.
+The stellar effective temperature is set to 5778 K
+%(NASA Planetary Fact Sheets)\jessi{Is there a full citation available for this NASA fact sheet?  Also, why is it referenced?  Is the effective temperature supposed to be similar to the Sun?}
+, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34 are used, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
+In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generate with a width of 40 \kms\,and considering initial spectra with a spectral resolution of R=115'000.
+%\jessi{Is a resolution of ``115'000'' standard notation?  I'm not sure what it means.}
 %, so that those CCFs would have the same properties as the one returned by the HARPS data reduction.
@@
 
-To see the impact of a facula on the different parameters of the CCF, we simulated the effect of an equatorial faculae \jessi{Should a footnote be added here to explain that the SOAP 2.0 faculae are not simulated from actual faculae templates?} of size 3\% relative to the visible stellar hemisphere.
-The faculae is face on when the phase equals to 0.
+To see the impact of a facula on the different parameters of the CCF, we simulated the effect of an equatorial faculae
+%\jessi{Should a footnote be added here to explain that the SOAP 2.0 faculae are not simulated from actual faculae templates?} 
+of size 3\% relative to the visible stellar hemisphere.
+The faculae is face-on when the phase equals to 0.
 Note that a 3\% faculae is relatively large for the Sun; at maximum activity, big faculae have generally a size of 1\%.
@@
 }
-   %\caption{(left) RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
+   %\caption{(left) RVs changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
 SN mean RV seems to have the smallest spurious variations caused by the faculae.
@@
 \includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
-   \caption{Using CCFs from SOAP 2.0 with a single facula, the correlation between the estimated RV's and the asymmetry parameters are displayed.
-In this case both the shape and the width of the CCF changes as the facula moves, producing statistically significant correlations between the estimated RV's and, respectively, the asymmetry parameter or the width parameter.}
+   \caption{Using CCFs from SOAP 2.0 with a single facula, the correlation between the estimated RVs and the asymmetry parameters are displayed.
+In this case both the shape and the width of the CCF changes as the facula moves, producing statistically significant correlations between the estimated RVs and, respectively, the asymmetry parameter or the width parameter.}
     \label{fig:faculae.corr}
@@
 \begin{table}
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
-\hline
-$\beta_{0}$            &    $0.033$    & $0.00020$ & $0.61$ \\
-\hline
-$\beta_{1}$            &    $2.22e-16 $    & $2.22e-16 $ & $2.22e-16 $ \\
-\hline
-$\beta_{2}$            &     $0.0034$   &  $2.22e-16 $ & $2.22e-16 $\\
-\hline
-$\beta_{3}$            &     $0.00016$   &  $1.091e-6$ & $9.75e-7$\\
-\hline
-$\beta_{4}$            &     $2.22e-16$   &  $2.22e-16$ & $2.22e-16$\\
-\hline
-$R^{2}$      &     $0.9978$    &  $0.9985$ & $0.9981$  \\
-\hline
-\end{tabular}
+\begin{center}
 \caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction} to correct the estimated  RVs from spurious variations caused by a facula.
-All the variables, except the intercept when the response variable is SN median RV, are statistically significant to explain spurious variations in RV's caused by a facula.
+All the variables, except the intercept when the response variable is SN median RV, are statistically significant to explain spurious variations in RVs caused by a facula.
 The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability in the estimated RVs.}
 \label{table:faculae.test}
+\begin{tabular}{|c|c|c|c|}
+\hline
+Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
+\hline
+$\beta_{0}$            &    $0.033$    & $0.00020$ & $0.61$ \\
+\hline
+$\beta_{1}$            &    $2.22e-16 $    & $2.22e-16 $ & $2.22e-16 $ \\
+\hline
+$\beta_{2}$            &     $0.0034$   &  $2.22e-16 $ & $2.22e-16 $\\
+\hline
+$\beta_{3}$            &     $0.00016$   &  $1.091e-6$ & $9.75e-7$\\
+\hline
+$\beta_{4}$            &     $2.22e-16$   &  $2.22e-16$ & $2.22e-16$\\
+\hline
+$R^{2}$      &     $0.9978$    &  $0.9985$ & $0.9981$  \\
+\hline
+\end{tabular}
+\end{center}
 \end{table}
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
-\caption{RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
+\caption{RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
 SN mean RV seems to have the smallest spurious variations caused by the faculae.}
-   %\caption{(left) RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
+   %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
 SN mean RV seems to have the smallest spurious variations caused by the faculae.
@@
 
-In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summarized in Table \ref{table:spot.test}, \umberto{we observe that the $\beta_0$, and $\beta_3$, corresponding respectively to the intercept and to the width of the CCF}, are \umberto{not helpful} to understand the variation measured in RV's.
+In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summarized in Table \ref{table:spot.test}, \umberto{we observe that the $\beta_0$, and $\beta_3$, corresponding respectively to the intercept and to the width of the CCF}, are \umberto{not helpful} to understand the variation measured in RVs.
 This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
@@
 \includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{\umberto{Set of  spurious variations in RV's caused by a \textbf{spot} using a Normal and a SN fit before and once corrected from stellar activity.
+   \caption{\umberto{Set of  spurious variations in RVs caused by a \textbf{spot} using a Normal and a SN fit before and once corrected from stellar activity.
 The new correction has done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
@@
 \begin{table}
-\centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
-\hline
-$\beta_{0}$            &    $0.4975$    & $0.21$ & $0.21$ \\
-\hline
-$\beta_{1}$            &    $2e-16$    & $2e-16$ & $2e-16$ \\
-\hline
-$\beta_{2}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
-\hline
-$\beta_{3}$            &     $0.017$   &  $0.13$ & $0.11$\\
-\hline
-$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
-\hline
-$R^{2}$      &     $0.9959$    &  $0.9936$ & $0.9952$  \\
-\hline
-\end{tabular}
+\begin{center}
 \caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction} to correct the estimated RVs from spurious variations caused by a spot. 
-All the covariates are statistically significant to explain the variability in RV's caused by a spot, except the intercept and the width of the CCF.
+All the covariates are statistically significant to explain the variability in RVs caused by a spot, except the intercept and the width of the CCF.
 The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability in the estimated RVs.
@@
 \label{table:spot.test}
+\begin{tabular}{|c|c|c|c|}
+\hline
+Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
+\hline
+$\beta_{0}$            &    $0.4975$    & $0.21$ & $0.21$ \\
+\hline
+$\beta_{1}$            &    $2e-16$    & $2e-16$ & $2e-16$ \\
+\hline
+$\beta_{2}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
+\hline
+$\beta_{3}$            &     $0.017$   &  $0.13$ & $0.11$\\
+\hline
+$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
+\hline
+$R^{2}$      &     $0.9959$    &  $0.9936$ & $0.9952$  \\
+\hline
+\end{tabular}
+\end{center}
 \end{table}
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
- \caption{RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
+ \caption{RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
 N mean RV seems to have the largest variations caused by the combined action of spot and planet.}
-   %\caption{(left) RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
+   %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
 N mean RV seems to have the largest variations caused by the combined action of spot and planet.
@@
 \includegraphics[height = 6in]{SOAP_SPOT_PLANET_Comparison_para_SN.pdf} 
-   \caption{Evaluation of the correlation between the RV's and the asymmetry parameters when a spot is present on the photosphere of the star and a planet is injected.
+   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a spot is present on the photosphere of the star and a planet is injected.
 In this case only the shape of the CCF changes as the spot moves, producing statistically significative correlations only between the RVs and the asymmetry parameter.
@@
 
-In order to correct the RV's from the spurious variation caused by the spot, \xavier{we need to add to our model of activity correction, a signal to take into account the RV variation caused by the injected planet.
+In order to correct the RVs from the spurious variation caused by the spot, \xavier{we need to add to our model of activity correction, a signal to take into account the RV variation caused by the injected planet.
 The observed RV can therefore be modeled by a combination of the activity and the planet signal:}
@@
 %We used non linear least squares and the results are displayed in Fig.~\ref{fig:spotplanet.correction}.
-We can see how in this case we are able to disentangle the spurious variations in RV's caused by stellar activity from the pure Doppler-shift due to the planet.
+We can see how in this case we are able to disentangle the spurious variations in RVs caused by stellar activity from the pure Doppler-shift due to the planet.
 The statistical tests conducted on the parameters, whose results are summarized in Table \ref{table:spotplanet.test}, \xavier{shows that except for the width parameters with coefficient $\beta_3$, all the other are significantly useful to explain the RV variation induce by a spot plus a planet.}
@@
 %\includegraphics[height = 4in]{SPOT_PLANET_NEW_CORRECTION.pdf} 
-%   \caption{Set of  variations in RV's estimated using a Normal and a SN fit before and once corrected from stellar activity.
+%   \caption{Set of  variations in RVs estimated using a Normal and a SN fit before and once corrected from stellar activity.
 In this case there are spurious variations caused by the spot and pure Doppler-shift due to the planet.
 The correction is done using Eq.~\ref{eq:RV:correction.overall} and the estimated parameters are presented in Table \ref{table:spotplanet.test}.
-In this case, by solving Eq.~\ref{eq:RV:correction.overall}, we are able to completely disentangle the spurious variations in RV's caused by the presence of the spot from the pure dopplershift caused by the exoplanet.}
+In this case, by solving Eq.~\ref{eq:RV:correction.overall}, we are able to completely disentangle the spurious variations in RVs caused by the presence of the spot from the pure dopplershift caused by the exoplanet.}
 %    \label{fig:spotplanet.correction}
@@
 \begin{table}
-\centering
+\begin{center}
+\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction.overall} to correct the estimated RVs from spurious variations caused by a spot while also accounting for a true planet RV.
+All the covariates are statistically significant to explain the variability in RVs caused by a spot, except the FWHM.
+Concerning the Keplerian parameters, the amplitude $K$ that provides relevance about the possibly presence of the exoplanet.
+Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.}
+\label{table:spotplanet.test}
 \begin{tabular}{|c|c|c|c|}
@@
 \end{tabular}
-\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction.overall} to correct the estimated RVs from spurious variations caused by a spot while also accounting for a true planet RV.
-All the covariates are statistically significant to explain the variability in RV's caused by a spot, except the FWHM.
-Concerning the Keplerian parameters, the amplitude $K$ that provides relevance about the possibly presence of the exoplanet.
-Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.
-}
-\label{table:spotplanet.test}
+\end{center}
 \end{table}
@@
 
-\umberto{Do we need to point out the following: \\ If we look at the $R^2$, the proposed function that corrects from stellar activity addresses (almost) all the spurious variations caused in RV's by active regions.
+\umberto{Do we need to point out the following: \\ If we look at the $R^2$, the proposed function that corrects from stellar activity addresses (almost) all the spurious variations caused in RVs by active regions.
 Anyway, if we look the residuals, a systematic component is still present, although smaller respect the residual obtained with the usual correction.
@@
 Before moving to real cases, where the analyses on five stars are presented, we need to provide further considerations.
-First of all, looking ad the analyses conducted with SOAP 2.0, it seems that the largest correlation between an asymmetry parameter and a set of RV's happens to be when respectively $\gamma$ and SN median RV are used.
+First of all, looking ad the analyses conducted with SOAP 2.0, it seems that the largest correlation between an asymmetry parameter and a set of RVs happens to be when respectively $\gamma$ and SN median RV are used.
 This is a bit surprising, since as the shape of the CCF changes, we expect SN median RV to be more robust than SN mean RV.
 \umberto{A possible justification of this ...}.
-As second, when searching for stellar activity by deriving the correlation between the set of RV's and either an asymmetry parameter or the width of the CCF, the latter leads to weaker and hence less conclusive results if the active region is a spot.
+As second, when searching for stellar activity by deriving the correlation between the set of RVs and either an asymmetry parameter or the width of the CCF, the latter leads to weaker and hence less conclusive results if the active region is a spot.
 When stellar activity is dominated by faculae, both the shape and the width of the CCF changes as the faculae evolves on the photosphere of the star.
-Related to these last two considerations, we note that the interaction between the asymmetry and the width of the CCF is useful to explain part of the variability in the RV's if the active region is a spot but not when it is a faculae.
-The proposed function to correct for stellar activity addressed high level of spurious variations in RV's caused by active regions.
+Related to these last two considerations, we note that the interaction between the asymmetry and the width of the CCF is useful to explain part of the variability in the RVs if the active region is a spot but not when it is a faculae.
+The proposed function to correct for stellar activity addressed high level of spurious variations in RVs caused by active regions.
 In particular, respect to other common linear interpolation, we proposed to use as covariates also the amplitude parameter of the CCF and the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM).
@@
 % A comparison with the results obtained by the classic approach is done, where the RV is estimated by retrieving the mean of the Normal density used to fit the CCF, along with the FWHM of the Normal density and the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}.
-The latter parameters are calculated separately from the Normal fit that leads to the set of RV's of the star.
+The latter parameters are calculated separately from the Normal fit that leads to the set of RVs of the star.
 
@@
 %\includegraphics[height = 3in]{HD12862_[2]RadialVelocityDifferences.pdf} 
-%   \caption{(top) RV's as function of Julian Day for Alpha Centauri b.
-The RV's are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses).
+%   \caption{(top) RVs as function of Julian Day for Alpha Centauri b.
+The RVs are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses).
 (bottom) RV differences between Normal RV and SN mean RV (black circles) and between Normal RV and a SN median RV (cyan crosses).}
@@
 
-%Because the median is a more robust index than the mean, the correlation between $\gamma$ and SN median RV is not as large as the correlation between $\gamma$ and SN mean RV, but it is nonetheless $1.5$ times larger than the correlation between the other common asymmetry parameters and their corresponding RV's.
+%Because the median is a more robust index than the mean, the correlation between $\gamma$ and SN median RV is not as large as the correlation between $\gamma$ and SN mean RV, but it is nonetheless $1.5$ times larger than the correlation between the other common asymmetry parameters and their corresponding RVs.
 In other words, changes in the asymmetry of the CCF are better captured when using the SN mean RV.
-The correlation between FWHM and the RV's, either by using SN mean RV or SN median RV, is as well stronger when fitting a SN density rather than a Normal.
+The correlation between FWHM and the RVs, either by using SN mean RV or SN median RV, is as well stronger when fitting a SN density rather than a Normal.
 All the correlations are statistically different from $0$.
 Recalling the analyses presented in Sec.
-\ref{sec:soap}, we could infer that Alpha Centauri b is dominated by faculae, because the correlations between the RV's and the width of the CCF are strong (in particular the correlation between SN mean RV and SN FWHM is $0.817$).
+\ref{sec:soap}, we could infer that Alpha Centauri b is dominated by faculae, because the correlations between the RVs and the width of the CCF are strong (in particular the correlation between SN mean RV and SN FWHM is $0.817$).
 %%
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONHD12862_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RV's for Alpha Centauri B using a Normal and a SN fit before and once corrected from stellar activity.
+   \caption{Set of RVs for Alpha Centauri B using a Normal and a SN fit before and once corrected from stellar activity.
 The correction is done using Eq.
@@
 \begin{table}
-\centering
+\begin{center}
+\caption{Evaluation of the linear combination used for correcting the RVs, according to Eq.~\ref{eq:RV:correction}.
+Concerning the Normal fit, all the parameters but the intercept and the BIS SPAN are useful in explaining variations in RVs of the star that can be caused by stellar activity.
+For the SN fit we note that the parameter related to $\gamma$ is highly significant to address part of the spurious variations in RVs caused by stellar activity.
+The evaluation of the $R^2$ shows that the proposed linear combination better explains variations in RVs due to stellar activity coming from the SN analysis that uses SN mean RV.}
+\label{table:alphacent.test}
 \begin{tabular}{|c|c|c|c|}
@@
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\ref{eq:RV:correction}.
-Concerning the Normal fit, all the parameters but the intercept and the BIS SPAN are useful in explaining variations in RV's of the star that can be caused by stellar activity.
-For the SN fit we note that the parameter related to $\gamma$ is highly significant to address part of the spurious variations in RV's caused by stellar activity.
-The evaluation of the $R^2$ shows that the proposed linear combination better explains variations in RV's due to stellar activity coming from the SN analysis that uses SN mean RV.}
-\label{table:alphacent.test}
+\end{center}
 \end{table}
 
-%Both the proposed indicators coming from the SN density have advantages and limits: SN mean RV better catches changes in the asymmetry of the CCF but the resulting set of RV's ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Sec.
+%Both the proposed indicators coming from the SN density have advantages and limits: SN mean RV better catches changes in the asymmetry of the CCF but the resulting set of RVs ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Sec.
 \ref{intro}.
-When using SN median RV, the final set of RV's is less affected by those spurious shifts caused by stellar activity, but at the same time this indicator is not able to catch as well as SN mean RV changes in the shape and in the width of the CCF.
+When using SN median RV, the final set of RVs is less affected by those spurious shifts caused by stellar activity, but at the same time this indicator is not able to catch as well as SN mean RV changes in the shape and in the width of the CCF.
 Once corrected from stellar activity using Eq.~\ref{eq:RV:correction}, the results are comparable.
 Anyway, both SN mean RV and SN median RV are useful to catch different aspects of the CCF and our suggestion is to use SN mean RV when interested in retrieving information about changes in the shape and/or the width of the CCF.
-In order to provide a set of RV's containing the smallest amount of spurious contamination imputable to stellar activity (i.e.
+In order to provide a set of RVs containing the smallest amount of spurious contamination imputable to stellar activity (i.e.
 before to run Eq.~\ref{eq:RV:correction}), our suggestion is to use instead SN median RV.
@@
 The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV for three of the four stars.
-Also for all these stars we corrected the originally estimated RV's from spurious variations in RV's caused by stellar activity, using Eq.
+Also for all these stars we corrected the originally estimated RVs from spurious variations in RVs caused by stellar activity, using Eq.
 \ref{eq:RV:correction}.
 Fig.
-\ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RV's.
+\ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RVs.
 While the Normal and SN residuals, once corrected for stellar activity, are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$, the results of the analyses on the star $\text{HD}215152$ (whose CCF's have lower SNR respect to the previous two analyzed stars) suggest that the residuals for the Normal are $0.054 \ms$ higher than the residuals retrieved with the SN analysis.
@@
 \ref{fig:Gliese785:corrPlot}--\ref{fig:Corot7:corrPlot}.}
+\label{table:summaryStars}
+\begin{center}
 \begin{tabular}{ccccccccc}
@@
 \end{tabular}
-\label{table:summaryStars}
+\end{center}
 \end{table*}
@@
 \includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}192310$.
-The last three plots show the correlation between the FWHM and the RV's for $\text{HD}192310$ using respectively the SN and the Normal fits.
+   \caption{Correlation between the asymmetry parameters and the RVs for $\text{HD}192310$.
+The last three plots show the correlation between the FWHM and the RVs for $\text{HD}192310$ using respectively the SN and the Normal fits.
 The p--values associated with each $R$ is statistically different from $0$.}
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONHD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RV's for $\text{HD}192310$  using a Normal and a SN fit before and once corrected from stellar activity.
+   \caption{Set of RVs for $\text{HD}192310$  using a Normal and a SN fit before and once corrected from stellar activity.
 The correction is done using Eq.
@@
 \includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}10700$.
-The last three plots show the correlation between the FWHM and the RV's for $\text{HD}10700$ using respectively the SN and the Normal fits.
+   \caption{Correlation between the asymmetry parameters and the RVs for $\text{HD}10700$.
+The last three plots show the correlation between the FWHM and the RVs for $\text{HD}10700$ using respectively the SN and the Normal fits.
 The p--values associated with each $R$ is statistically different from $0$.}
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONHD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RV's for $\text{HD}10700$  using a Normal and a SN fit before and once corrected from stellar activity.
+   \caption{Set of RVs for $\text{HD}10700$  using a Normal and a SN fit before and once corrected from stellar activity.
 The correction is done using Eq.
@@
 \includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}215152$.
-The last three plots show the correlation between the FWHM and the RV's for $\text{HD}215152$ using respectively the SN and the Normal fits.
+   \caption{Correlation between the asymmetry parameters and the RVs for $\text{HD}215152$.
+The last three plots show the correlation between the FWHM and the RVs for $\text{HD}215152$ using respectively the SN and the Normal fits.
 Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONHD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RV's for $\text{HD}215152$ using a Normal and a SN fit before and once corrected from stellar activity.
+   \caption{Set of RVs for $\text{HD}215152$ using a Normal and a SN fit before and once corrected from stellar activity.
 The correction is done using Eq.
@@
 \includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RV's for  $\text{Corot }7$.
-The last three plots show the correlation between the FWHM and the RV's for  $\text{Corot }7$ using respectively the SN and the Normal fits.
+   \caption{Correlation between the asymmetry parameters and the RVs for  $\text{Corot }7$.
+The last three plots show the correlation between the FWHM and the RVs for  $\text{Corot }7$ using respectively the SN and the Normal fits.
 Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONLRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RV's for  $\text{Corot }7$ using a Normal and a SN fit before and once corrected from stellar activity.
+   \caption{Set of RVs for  $\text{Corot }7$ using a Normal and a SN fit before and once corrected from stellar activity.
 The correction is done using Eq.
@@
 %We start by calculating the standard errors of the parameters retrieved in Sec.
-\ref{sec:soap}, where with SOAP we produced CCF's presenting spurious variations in RV's caused by a faculae or by a spot.
+\ref{sec:soap}, where with SOAP we produced CCF's presenting spurious variations in RVs caused by a faculae or by a spot.
 In the third and final case we considered, beyond the spot, a planetary signal that produces pure Doppler-shifts in the CCF's.
@@
 %Fig.~\ref{fig:se.soap.faculae} shows the results of the bootstrap analysis performed when a faculae is present on the photosphere of the star.
-The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} shows the different errors for the RV's, defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width of the CCF, defined as FWHM (red triangles) or SN FWHM (black circles) and the asymmetry of the CCF, defined as $\gamma$ (black circles) or BIS SPAN (red triangles).
+The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} shows the different errors for the RVs, defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width of the CCF, defined as FWHM (red triangles) or SN FWHM (black circles) and the asymmetry of the CCF, defined as $\gamma$ (black circles) or BIS SPAN (red triangles).
 In the series of three plots in the bottom of Fig.~\ref{fig:se.soap.faculae} we show the ratio between errors associated to the parameters derived from the bootstrap analysis fitting the SN and the errors associated to the parameters derived from the bootstrap analysis fitting the Normal density.
-We used the same notation also for the other two cases, where respectively a spot is present on the photosphere of the star (Fig.~\ref{fig:se.soap.spot}) and a spot and a planet are introducing both spurious and pure variations in the RV's (Fig.~\ref{fig:se.soap.spot.planet}).
-Concerning the standard errors related to the RV's if a faculae is creating spurious signals, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$, when using SN mean RV and $0.8$ when using SN median RV.
+We used the same notation also for the other two cases, where respectively a spot is present on the photosphere of the star (Fig.~\ref{fig:se.soap.spot}) and a spot and a planet are introducing both spurious and pure variations in the RVs (Fig.~\ref{fig:se.soap.spot.planet}).
+Concerning the standard errors related to the RVs if a faculae is creating spurious signals, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$, when using SN mean RV and $0.8$ when using SN median RV.
 By using SN median RV we get standard errors $20\%$ smaller than using the Normal fit and its corresponding mean.
@@
 %   \caption{Faculae Case.
-Comparison between the standard errors using the bootstrap analysis for the RV's, the FWHM and the asymmetry parameter.
+Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
 When using SN mean RV (black circles), the standard errors are in average $40\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
@@
 The series of plots follows the specifications outlined for the previous case.
-Concerning the standard errors related to the RV's, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.3$ when using SN mean RV and $0.8$ when using SN median RV.
+Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.3$ when using SN mean RV and $0.8$ when using SN median RV.
 Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable.
@@
 %   \caption{Spot case.
-Comparison between the standard errors using the bootstrap analysis for the RV's, the FWHM and the asymmetry parameter.
+Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
 When using SN mean RV (black circles), the standard errors are in average $30\%$ larger than the standard errors retrieved fitting a Normal (red triangles).

### 2018-06-02 manuscript_Windows.tex
Went through Sect 1, 2, 3 and did some small modif, updated the text according to Jessi's comments

--- 2018-05-31 manuscript.tex
@@
 \documentclass{aa}
+
 %\documentclass[referee]{aa}
+%
+\usepackage{pdflscape} % or {lscape}
 \usepackage{natbib}
 %\usepackage{lscape}
-\usepackage{pdflscape} % or {lscape}
 \usepackage{wasysym}
@@
 \author{U. Simola \inst{1,2}
-	    \thanks{\email{umberto.simola@yale.edu}}
+	    \thanks{\email{umberto.simola@helsinki.fi}}
 	    \and X. Dumusque\inst{3}
 	    \thanks{Branco Weiss Fellow--Society in Science (url: \url{http://www.society-in-science.org})}    
-	    \and Jessi Cisewski\inst{2}
+	    \and Jessi Cisewski-Kehe\inst{2}
 	    }
@@
 %
-{When considering the real observations, the correlation between the RV's and the asymmetry of the CCF and the correlation between the RV's and the width of the CCF are stronger when using the parameters derived from the SN than the Normal approach.
+{When considering the real observations, the correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are stronger when using the parameters derived from the SN than the Normal approach.
 This suggests that the CCF asymmetry and the CCF width derived using a SN may be more sensitive to stellar activity, which can be helpful with estimating stellar rotational periods and generally characterizing the stellar activity signals.
-The estimated uncertainties in the estimated RV's using the proposed SN approach are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal, and the estimated uncertainties on the SN asymmetry parameter are on average $15\%$ smaller than the commonly used Bisector Inverse Slope Span (BIS SPAN) approach for estimating the asymmetry of the CCF.
+The estimated uncertainties in the estimated RVs using the proposed SN approach are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal, and the estimated uncertainties on the SN asymmetry parameter are on average $15\%$ smaller than the commonly used Bisector Inverse Slope Span (BIS SPAN) approach for estimating the asymmetry of the CCF.
 }
+{XXX \jessi{It looks like we still need to add conclusions here}}
 %
 %{The derived benefits of using the proposed SN approach includes an asymmetry parameter along with several options for estimating the RV, while the Normal model only includes an RV estimate and requires a separate procedure for estimating the asymmetry.
-Furthermore, the estimated uncertainties on the RV's and the asymmetry parameter are smaller in the SN setting.}
-%The correlation between the RV's and the asymmetry of the CCF and the correlation between the RV's and the width of the CCF are always stronger when using the parameters derived from the SN in the case of real observations.
+Furthermore, the estimated uncertainties on the RVs and the asymmetry parameter are smaller in the SN setting.}
+%The correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are always stronger when using the parameters derived from the SN in the case of real observations.
 Therefore the CCF asymmetry and the CCF width derived using a SN are more sensitive to stellar activity, which allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals.
-The precision on the estimated set of RV's, derived using the median of the fitted SN densities are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
+The precision on the estimated set of RVs, derived using the median of the fitted SN densities are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
 In addition, the uncertainties related to the asymmetry parameter derived from the SN are on average $15\%$ smaller than the ones calculated on the common Bisector Inverse Slope Span (BIS SPAN).
-We strongly encourage the use of the SN density rather than the Normal density, because this allows us to retrieve in one single fit the different moments of the CCF, because the derived moments better catch stellar activity signals and finally because the standard errors on the RV's and the the asymmetry parameter are smaller than the one estimated with the Normal fit.
+We strongly encourage the use of the SN density rather than the Normal density, because this allows us to retrieve in one single fit the different moments of the CCF, because the derived moments better catch stellar activity signals and finally because the standard errors on the RVs and the the asymmetry parameter are smaller than the one estimated with the Normal fit.
 
@@
 One of the most challenging stellar signal to characterize and to correct for is the signal induced by stellar activity. 
-Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, which can induce spurious RV's variations \citep{Meunier-2010a, Dumusque-2014b}.
+Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, which can induce spurious RVs variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b, Borgniet-2015}.
 In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}.
-However, on quiet GKM dwarfs, the main target for precise RV's measurements, stellar activity can induce signals of a few \ms.
+However, on quiet GKM dwarfs, the main target for precise RVs measurements, stellar activity can induce signals of a few \ms.
 This corresponds physically to variations smaller than 1/100th of a pixel on the detector making the changing shape of the spectral lines challenging to detect.
@@
 %
-To measure the Doppler-shift between different spectra and therefore to retrieve the RV's of a star as a function of time, the variations of the CCF barycenter are calculated. 
+To measure the Doppler-shift between different spectra and therefore to retrieve the RVs of a star as a function of time, the variations of the CCF barycenter are calculated. 
 The barycenter is generally estimated by fitting a Normal density to the CCF and retaining its mean.
@@
 The hyperparameters of the Gaussian process can be trained on different activity indicators \citep{Haywood-2014,Rajpaul-2015}.
-It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated with the RV's but also for which we can obtain the best precision.
+It is therefore essential for mitigating stellar activity to obtain activity indicators that are the most correlated with the RVs but also for which we can obtain the best precision.
 
@@
 %
-In Sec.~\ref{sec:31} we propose an expanded linear model used to correct the estimated RV's from the inferred stellar activity, which extends the linear models previously proposed for this purpose \citep{Dumusque:2017aa,Feng:2017aa}.
+In Sec.~\ref{sec:31} we propose an expanded linear model used to correct the estimated RVs from the inferred stellar activity, which extends the linear models previously proposed for this purpose \citep{Dumusque:2017aa,Feng:2017aa}.
 %
@@
 This can be done using the following relations:
-%
-\begin{equation} \label{eq:snd_cp}
-\mu = \xi + \omega \beta, \quad \sigma^{2} = \omega^{2}(1-\beta^2), \quad \gamma = \frac{1}{2}(4-\pi) \beta^{3}\left(1-\beta^2\right)^{-3/2},
-\end{equation}
-%
-where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$ \citep[e.g.][]{Arellano-2010}.
-
-By using Eq.~\ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a clearer interpretation of the behavior of the SN distribution.
+%%
+%\begin{equation} \label{eq:snd_cp}
+%\mu = \xi + \omega \beta, \quad \sigma^{2} = \omega^{2}(1-\beta^2), \quad \gamma = \frac{1}{2}(4-\pi) \beta^{3}\left(1-\beta^2\right)^{-3/2},
+%\end{equation}
+%%
+%where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$ \citep[e.g.][]{Arellano-2010}.
+
+%By using Eq.~\ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a clearer interpretation of the behavior of the SN distribution.
 For the $\alpha$ values used in Fig.~\ref{fig:SN.plot}, the corresponding values of ($\mu$, $\sigma^2$, $\gamma$) are displayed in Table~\ref{tab:cp_values}.
 In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution, rather than simply a location and scale parameter, and $\gamma$ provides an measure of the skewness of the SN.
-Along with the mean of the SN, we consider the median of the distribution as a measure of center, which is used in the proposed method.
+%Along with the mean of the SN, we consider the median of the distribution as a measure of center, which is used in the proposed method.
 See Table~\ref{tab:cp_values} for the medians of the SN densities displayed in Fig.~\ref{fig:SN.plot}.
+
 %The median of the SN, and in general the median of an absolute continuous random variable, is defined as the value $m$ such that\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}:
@@
 
-To evaluate the strength of the correlation between the estimated RV's and the different stellar activity indicators, we calculated the Pearson correlation coefficient, which in its general form is defined as:
+To evaluate the strength of the correlation between the estimated RVs and the different stellar activity indicators, we calculated the Pearson correlation coefficient, $R$, which in its general form is defined as:
 %
 \begin{equation}
-R (x,y)= \frac{cov(x,y)}{\sigma(x),\sigma(y)},
+R (x,y)= \frac{cov(x,y)}{\sigma(x)\sigma(y)},
 \label{eq:Pearson:corr}
@@
 
-\xavier{Exoplanets only produce a pure RV signal.
-Stellar activity on the contrary, and in particular the presence of active regions on the stellar photosphere, does not produce a blueshift or redshift of the entire stellar spectra, but creates a spurious RV signal by modifying the shape of spectral lines.
-To track these variations in the shape of the spectral lines}, the general approach consists in using the FWHM, the BIS SPAN or the indicators introduced in \citet{Boisse-2011} or \citet{Figueira-2013}, which provide information on the width and asymmetry of the CCF.
-A strong correlation between the estimated RVs and one or more of these parameters provides an indication that stellar activity signals are affecting our measurements.
-
-\xavier{When fitting for planetary signals in RV data, it is common to include in the fitted model, linear dependencies with the BIS SPAN and the FWHM, to take into account the signal induced by stellar activity \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
+Exoplanets only produce a pure RV signal.
+On the contrary, stellar activity, in particular the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.
+To track these variations in the shape of the spectral lines, the general approach consists in using the FWHM, the BIS SPAN or other indicators such as those introduced in \citet{Boisse-2011} or \citet{Figueira-2013}, which provide information on the width and asymmetry of the CCF.
+A strong correlation between the estimated RVs and one or more of these parameters provides an indication that stellar activity signals may be affecting the measurements.
+
+When fitting for planetary signals in RV data, it is common to include linear dependencies with the BIS SPAN and the FWHM and to take into account the signal induced by stellar activity \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
 %Some people also include the \logrhk, however, \citet{Feng-2018} show that this is probably not a good choice as \logrhk and RV are not well correlated.
-In this paper, we propose to add additional parameters in the model to correct for stellar activity: first the amplitude parameter A of the CCF, generally referred to as the CCF contrast, and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case).
-The stellar activity correction we propose can therefore be written as:}
+We propose to add additional parameters in the model to correct for stellar activity: first the amplitude parameter A of the CCF, generally referred to as the CCF contrast, and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case).
+The stellar activity correction we propose can therefore be written as:
 %
 \begin{equation}
-RV_{\text{stellar activity}}= \beta_{0} + \beta_{1} A + \beta_{2} \gamma + \beta_{3} \text{SN FWHM} + \beta_{4} (\gamma  \text{SN FWHM})+\epsilon,
+RV_{\text{activity}}= \beta_{0} + \beta_{1} A + \beta_{2} \gamma + \beta_{3} \text{SN FWHM} + \beta_{4} (\gamma  \text{SN FWHM})+\epsilon,
 \label{eq:RV:correction}
@@
 %
-where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix). 
-The inclusion of the contrast parameter $A$ is justified by the fact that the presence of a spot on the stellar surface produces a changes in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g.
+where $\beta_{0}$ is the intercept and $\epsilon$ is the error with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix). 
+The contrast parameter $A$ accounts for the presence of a spot on the stellar surface, which produces a change in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g.
 Fig.
 2 in ][]{Dumusque-2014b}.
-The reasons for including in Eq.~\ref{eq:RV:correction} a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better justified through the results of the examples presented in Sec.\ref{sec:soap}.
-\xavier{This interaction term allows to take into account cases when for different values of SN FWHM (or FWHM), the linear coefficient $\beta_{2}$ for $\gamma$ (or BIS SPAN) varies}.
-\xavier{Umberto, Jessi, is this correct ?}
-%while the association between in this case BIS SPAN and FWHM (or $\gamma$ and SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant.
+The benefits of including a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better understood through the results of the examples presented in Sec.\ref{sec:soap}.
+This interaction term can account for possible interactions between SN FWHM (or FWHM) and $\gamma$ (or BIS SPAN), meaning that each  variables' association with the response, $RV_{\text{activity}}$, depends also on the other variable.
+%while the association between in this case BIS SPAN and FWHM (or $\gamma$ and SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RVs is not constant.
 In particular the effect differs at different values of the other values.
@@
 
-In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$, $\beta_{2}$, $\beta_{3}$ and $\beta_{4}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,\dots,4$.
-The level for not rejecting the null hypothesis is fixed to $0.05$.
-The coefficient of multiple correlation $R^2$ is introduced in order to explain how well this linear combination addresses the variability of the RV variation induced by stellar activity.
-
+The proposed model is analyzed using statistical tests on the parameters $\beta_{0}$, $\beta_{1}$, $\beta_{2}$, $\beta_{3}$ and $\beta_{4}$ where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,\dots,4$.
+The significance level for the tests are set at $0.05$.
+The coefficient of determination, $R^2$, is used to assess how well the proposed linear combination of variables accounts for the variability of $RV_{\text{activity}}$.
+
+\jessi{Is the following paragraph needed?
+Is any model selection actually carried out here?
+It seems the model of Eq.~\ref{eq:RV:correction} is fit, and then the significance of the variables are discussed, but no attempts are really made to remove/add/step through the various model options.
+The point about multicollinearity is probably good to keep though.}
 When working with a linear regression, there are several ways to select the variables to include in the model.
@@
 
-\xavier{For a given configuration of spots and faculae on the stellar surface, SOAP 2.0 gives as output the simulated CCF as a function of rotational phase.
-The code returns as well the RV and the FWHM by fitting a Normal density to the CCF, and the BIS SPAN by calculating the bisector of the CCF.
-SOAP 2.0 gives us therefore noiseless CCFs affected by stellar activity, which will be used to compare the benefits of fitting a SN density to the CCF compared to a Normal density fit.}
-
-\xavier{For the simulations shown below, we modelled a star similar to the Sun.
+For a given configuration of spots and faculae on the stellar surface, SOAP 2.0 gives as output the simulated CCF as a function of rotational phase.
+The code also returns the RV and the FWHM by fitting a Normal density to the CCF, and the BIS SPAN by calculating the bisector of the CCF.
+SOAP 2.0 gives noiseless CCFs affected by stellar activity, which are used to compare the benefits of a SN density fit to the CCF compared to a Normal density fit.
+
+For the simulations discussed below, a star similar to the Sun was modeled.
 The stellar rotational period is set to 25.0 days, the radius to a solar radius and the star is seen equator on.
-The stellar effective temperature is set to 5778 K (NASA Planetary Fact Sheets), and we use a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
-In addition, to be able to compare the result of those simulations with real data obtained with the HARPS spectrograph in Sect.~\ref{sec:4}, we asked SOAP 2.0 to generate CCFs of width 40 \kms and of resolution 115'000, so that those CCFs would have the same properties as the one returned by the HARPS data reduction.}
+\jessi{The previous sentence seems incomplete and I'm not sure how to update it.}
+The stellar effective temperature is set to 5778 K (NASA Planetary Fact Sheets)\jessi{Is there a full citation available for this NASA fact sheet?
+Also, why is it referenced?
+Is the effective temperature supposed to be similar to the Sun?}, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011} are used.
+In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generate with a width of 40 \kms and a resolution of 115'000.
+\jessi{Is a resolution of ``115'000'' standard notation?
+I'm not sure what it means.}
+%, so that those CCFs would have the same properties as the one returned by the HARPS data reduction.
 
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
-\caption{RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
-SN mean RV seems to have the smallest spurious variations caused by the faculae.}
-   %\caption{(left) RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
+\caption{Using CCFs from SOAP 2.0 with a single facula, the estimated RV changes as function of the orbital phase.
+SN mean RV seems to have the smallest spurious variations caused by the facula.\jessi{The previous sentence does not seem correct.}  \jessi{The cyan line is hard to see in the legend, and may be impossible in a black-and-white version - could the legend background be white?}
+}
+   %\caption{(left) RVs changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star.
 SN mean RV seems to have the smallest spurious variations caused by the faculae.
@@
 \includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
-   \caption{Evaluation of the correlation between the RV's and the asymmetry parameters when a faculae is present on the photosphere of the star.
-In this case both the shape and the width of the CCF changes as the faculae moves, producing statistically significative correlations between the RV's and respectively the asymmetry parameter and the width parameter.}
+   \caption{Using CCFs from SOAP 2.0 with a single facula, the correlation between the estimated RVs and the asymmetry parameters are displayed.
+In this case both the shape and the width of the CCF changes as the facula moves, producing statistically significant correlations between the estimated RVs and, respectively, the asymmetry parameter or the width parameter.}
     \label{fig:faculae.corr}
@@
 
-Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a faculae, \xavier{we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its efficiency in the case of a faculae.} The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
-It is straightforward to see that the proposed correction for \xavier{stellar activity is able to account for the majority of the activity signal created by a faculae, with a $R^2$ of our model larger than 0.95.
+Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a facula, we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its performance in this setting.
+The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
+The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a $R^2$ of our model larger than 0.95.
 In addition, the rms of the different estimates of the RV reduces from about 3 \ms before correction to values below 0.15 \ms after correction.
 We see a slightly smaller rms after correction for the SN parameters, however the different is not significant.
-When comparing the correction proposed in Eq.~\ref{eq:RV:correction} with what is generally used, i.e.
-a linear combination of the asymmetry and width parameter, we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2.
-Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that the intercept $\beta_0$ is only significant at a level of 1\% in the case of the Normal parameters, the coefficient $\beta_3$ that corresponds to the CCF width is only significant when using the SN parameters, and the coefficient $\beta_4$ that account for the interaction between the width and the asymmetry parameters is never significant.}
+\jessi{In the previous sentence, is this a comparison between SN and N?
+If so, it should be clarified.}
+When comparing the correction proposed in Eq.~\ref{eq:RV:correction} with what is generally used (i.e.
+a linear combination of only the asymmetry and width parameter), we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2.
+Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that the parameter related to the intercept, $\beta_0$, is only significant at a level of 1\% in the case of the Normal parameters or when SN median RV is used.
+\jessi{Is the point about $\beta_0$ relevant?}
 
@@
 \includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
-Once corrected for stellar activity the residuals do not show a systematic component.}
+   \caption{(top) The spurious RVs caused by a facula in the simulated data using a Normal and a SN fit.
+Before and once corrected from stellar activity.
+\jessi{What is the correction done here?
+I think what you mean is this:  ``The black circles are the estimated RVs and the red plus signs are the estimated RVs from the fit model of  Eq.~\ref{eq:RV:correction}.''  If my assumption is correct, the legend should say ``RV estimates'' and ``RV model'' or something like that.
+Otherwise this is rather confusing because in the bottom plot you are actually comparing residuals from two models, while the top has a different interpretation.}
+   %
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (new correction) and the usual correction \jessi{it might be helpful to actually have an equation for the usual/old model}.
+The residuals have a smaller systematic component when using the proposed model of
+  Eq.~\ref{eq:RV:correction} (blue circles) compared to the usual model (blue triangles).
+The estimated parameters are presented in Table \ref{table:faculae.test} \jessi{This table only has p-values and $R^2$}. }
     \label{fig:faculae.correction}
@@
 \begin{table}
-\centering
+\begin{center}
+\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction} to correct the estimated  RVs from spurious variations caused by a facula.
+All the variables, except the intercept when the response variable is SN median RV, are statistically significant to explain spurious variations in RVs caused by a facula.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability in the estimated RVs.}
+\label{table:faculae.test}
 \begin{tabular}{|c|c|c|c|}
 \hline
-Parameter          & RV         &   SN mean RV &   SN median RV \\
-\hline
-$\beta_{0}$            &    $0.0016$    & $0.26$ & $0.60$ \\
-\hline
-$\beta_{1}$            &    $3.75e-05$    & $0.0068$ & $0.0069$ \\
-\hline
-$\beta_{2}$            &     $7.79e-16$   &  $1.97e-05$ & $3.69e-08$\\
-\hline
-$\beta_{3}$            &     $0.25$   &  $0.0011$ & $0.0011$\\
-\hline
-$\beta_{4}$            &     $0.53$   &  $0.21$ & $0.21$\\
-\hline
-$R^{2}$      &     $0.9967$    &  $0.9571$ & $0.977$  \\
+Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
+\hline
+$\beta_{0}$            &    $0.033$    & $0.00020$ & $0.61$ \\
+\hline
+$\beta_{1}$            &    $2.22e-16 $    & $2.22e-16 $ & $2.22e-16 $ \\
+\hline
+$\beta_{2}$            &     $0.0034$   &  $2.22e-16 $ & $2.22e-16 $\\
+\hline
+$\beta_{3}$            &     $0.00016$   &  $1.091e-6$ & $9.75e-7$\\
+\hline
+$\beta_{4}$            &     $2.22e-16$   &  $2.22e-16$ & $2.22e-16$\\
+\hline
+$R^{2}$      &     $0.9978$    &  $0.9985$ & $0.9981$  \\
 \hline
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a faculae, according to Eq.~\ref{eq:RV:correction}.
-Beyond the contrast parameter A and the asymmetry parameter of the CCF which are useful for both the analyses, the width of the CCF is statistically useful to explain spurious variations in RV's caused by a faculae only for the SN analyses.
-The term of interaction between the asymmetry and the width of the CCF is not helpful to explain part of the variability in the set of RV's.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}
-\label{table:faculae.test}
+\end{center}
 \end{table}
@@
 
-As before, we corrected the originally RVs by using Eq.~\ref{eq:RV:correction}.
-The results of the correction are displayed in Fig.~\ref{fig:spot.correction}.
-Also in this case the proposed correction almost completely addresses the issue when considering the SN or Normal parameters, with values of $R^2$ larger than 0.98.
-\xavier{Looking at Fig.~\ref{fig:spot.correction}, we see that the activity correction proposed here is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms.
-In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however,} \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant.
+As before, the originally RVs were corrected by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction}. 
+In this setting, the proposed correction almost completely addresses the issue \jessi{what issue?} when considering the SN or Normal parameters, with values of $R^2$ larger than 0.99. 
+Considering Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms.
+\jessi{Doesn't the facula setting do better getting down to $\sim$0.13 \ms?}
+In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however, \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant.
 When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.
 
-In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summmurized in Table \ref{table:spot.test}, we observe that the intercept and $\beta_3$, corresponding to the width of the CCF, are useless to understand the variation seen in RVs.
+In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summarized in Table \ref{table:spot.test}, \umberto{we observe that the $\beta_0$, and $\beta_3$, corresponding respectively to the intercept and to the width of the CCF}, are \umberto{not helpful} to understand the variation measured in RVs.
 This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
@@
 \begin{figure*}[htbp]
-   \centering
+\begin{center}
 \includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
-Once corrected for stellar activity the residuals do not show a systematic component.}
+   \caption{\umberto{Set of  spurious variations in RVs caused by a \textbf{spot} using a Normal and a SN fit before and once corrected from stellar activity.
+The new correction has done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
+Once corrected for stellar activity using the proposed linear function (black dots), the residuals present a smaller systematic component if compared with the residuals obtained with the usual correction (blue triangles).}}
     \label{fig:spot.correction}
+\end{center}
 \end{figure*}
@@
 \begin{table}
-\centering
+\begin{center}
+\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction} to correct the estimated RVs from spurious variations caused by a spot. 
+All the covariates are statistically significant to explain the variability in RVs caused by a spot, except the intercept and the width of the CCF.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability in the estimated RVs.
+\jessi{Isn't the width of the CCF parameter sig for N mean RV at 0.017?
+Previously it was noted that a 5\% significance level was going to be used.}}
+\label{table:spot.test}
 \begin{tabular}{|c|c|c|c|}
 \hline
-Parameter          & RV         &   SN mean RV &   SN median RV \\
-\hline
-$\beta_{0}$            &    $0.47$    & $0.84$ & $0.81$ \\
-\hline
-$\beta_{1}$            &    $0.00035$    & $0.064$ & $0.064$ \\
+Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
+\hline
+$\beta_{0}$            &    $0.4975$    & $0.21$ & $0.21$ \\
+\hline
+$\beta_{1}$            &    $2e-16$    & $2e-16$ & $2e-16$ \\
 \hline
@@
 \hline
-$\beta_{3}$            &     $0.53$   &  $0.61$ & $0.61$\\
-\hline
-$\beta_{4}$            &     $1.11e-07 $   &  $2.85e-08 $ & $ 2.87e-08 $\\
-\hline
-$R^{2}$      &     $0.9897$    &  $0.9914$ & $0.9929$  \\
+$\beta_{3}$            &     $0.017$   &  $0.13$ & $0.11$\\
+\hline
+$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
+\hline
+$R^{2}$      &     $0.9959$    &  $0.9936$ & $0.9952$  \\
 \hline
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\ref{eq:RV:correction}.
-All the covariates are statistically useful to explain the variability in RV's causued by a spot except the intercept and the width of the CCF.
-Concerning the SN analysis, the contrast parameter A is not statistically significant at level $5\%$.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}
-\label{table:spot.test}
+\end{center}
 \end{table}
@@
 \begin{table}
-\centering
+\begin{center}
+\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction.overall} to correct the estimated RVs from spurious variations caused by a spot while also accounting for a true planet RV.
+All the covariates are statistically significant to explain the variability in RVs caused by a spot, except the FWHM.
+Concerning the Keplerian parameters, the amplitude $K$ that provides relevance about the possibly presence of the exoplanet.
+Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.}
+\label{table:spotplanet.test}
 \begin{tabular}{|c|c|c|c|}
 \hline
-Parameter          & RV         &   SN mean RV &   SN median RV \\
-\hline
-$\beta_{0}$            &    $7.09e-09$    & $ 3.44e-07$  & $4.96e-09$ \\
-\hline
-$\beta_{1}$            &    $0.00105$    & $0.0052$  & $0.0052$ \\
-\hline
-$\beta_{2}$            &     $2e-16$   & $2.43e-16$ & $2e-16$\\
-\hline
-$\beta_{3}$            &     $0.79$   &  $0.22$  & $0.22$\\
-\hline
-$\beta_{4}$            &     $6.73e-07$   &  $7.78e-06$ & $7.82e-06$\\
-\hline
-K            &     $2e-16$   &  $2e-16$   & $ 2e-16 $\\
-\hline
-P            &     $2e-16$   &  $2e-16$ & $2e-16 $\\
-\hline
-$t_{0}$            &     $2e-16$   &  $2e-16$ & $2e-16 $\\
-\hline
-$\text{Residuals}$      &     $0.61 \ms$    &  $ 0.60 \ms$ & $0.60 \ms$  \\
+Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
+\hline
+$\beta_{0}$            &    $0.00063$    & $2e-16$  & $1.42e-09$ \\
+\hline
+$\beta_{1}$            &    $2e-16$    & $2e-16$  & $2e-16$ \\
+\hline
+$\beta_{2}$            &     $2e-16$   & $2e-16$ & $2e-16$\\
+\hline
+$\beta_{3}$            &     $0.067$   &  $0.40$  & $0.38$\\
+\hline
+$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
+\hline
+K            &     $2e-16$   &  $2e-16$   & $2e-16$ \\
+\hline
+P            &     $2e-16$   &  $2e-16$ & $2e-16$ \\
+\hline
+$t_{0}$            &     $2e-16$   &  $2e-16$ & $2e-16$ \\
+\hline
+$\text{Residuals}$      &     $0.71 \ms$    &  $ 0.66 \ms$ & $0.70 \ms$  \\
 \hline
 \end{tabular}
-\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\ref{eq:RV:correction.overall}.
-All the parameters are statistically helpful to address spurious variations in RV's except the FWHM.
-Concerning the keplerian parameters, the amplitude $K$ that provides relevance about the possibly presence of the exoplanet.
-Note that since non linear least squares are required, the residual standard error rather than the $R^2$ is displayed for each case.}
-\label{table:spotplanet.test}
+\end{center}
 \end{table}
@@
 In this Sec.\ref{sec:soap}, we presented a first implementation of the SN fit to the CCF, using SOAP 2.0 to simulate noiseless CCF affected by stellar activity variation.
+
+\umberto{Do we need to point out the following: \\ If we look at the $R^2$, the proposed function that corrects from stellar activity addresses (almost) all the spurious variations caused in RVs by active regions.
+Anyway, if we look the residuals, a systematic component is still present, although smaller respect the residual obtained with the usual correction.
+The residuals are supposed to be homoscedastic with 0 mean under the assumption that the model is correct.
+Therefore, since our $R^2$ is always close to $1$, we can argue, as we discussed already many times, that the CCF does not follow a normal fit, neither a SN one, otherwise, given our extremely high $R^2$ we should have gotten homoscedastic 0 mean residuals.}
 
@@
 The results can be seen in Fig.~\ref{fig:se}.
+In the top plots of this figure, we show the standard errors for the different RV, width and asymmetry estimates.
+Note that because BIS SPAN and $\gamma$ does not have the same units, we used the slope of the correlation between those two parameters to transform $\gamma$ in \ms (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star).
+In the bottom plots, we show the ratio between the standard errors measured when using the SN parameters and the Normal parameters.
+Values smaller or larger than one will imply that standard errors fro the SN parameters are more or less precise, respectively.}
+
+\xavier{Looking at the estimates for the RV, we see that they all follow a similar exponential decay.
+Although we plot the data for three different stars, we do not see any offsets in this decay, which implies that the SNR at 550 nm is the main contributor to the precision measured in RV.
+This is not surprising as the 3 stars studies are all main sequence K-dwarfs.
+When comparing the three different estimates for the RV, we see that SN mean RV presents standard errors that are 60\% larger than what N mean RV gives.
+On the opposite, SN median RV gives errors 10\% more precise than N mean RV.
+Regarding the parameters describing the width of the CCF, FWHM and SN FWHM have the same standard errors.
+Finally, for the asymmetry parameters, we see that $\gamma$, derived from the SN, is 15\% more precise than BIS SPAN.
+In conclusion, when fitting a SN density to the CCF and using as RV estimates SN mean RV, we are able to improve by 10\% the precision on the RV, 15\% the precision on the asymmetry, and this without degrading the precision on the width estimate.
+SN mean RV should not be use to derive RVs, except perhaps for stars for which the photon noise is not the dominant source of noise, as the precision on this parameter if 60\% worse than the precision on the RV derived from a Normal density fit.}
+%
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
+   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
+When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
+Note that for the asymmetry, the error in BIS SPAN is in \kms.
+To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
+   \label{fig:se}
+\end{center}
+\end{figure*}
+
+%, using the spectrum derivative
+%, the pure photon-noise error on RV measured 
+%Together with the pointwise estimates, retrieving the standard errors for the RVs of the star, $\gamma$ and the FWHM provides information about the uncertainties associated to each parameter.
+Since the procedure for retrieving the RVs of the star consists in fitting with a density function a CCF, getting the standard errors for all the parameter of interests cannot be done by using the common asymptotic theory.
+The implementation of a standard bootstrap analysis cannot as well be done, because the points of the CCF are highly correlated.
+In the analysis of the present work, in order to get the standard errors for the parameters of interest for a particular CCF, we moved each point of this CCF according to its measurement errors, producing $100$ simulated CCFs from the original one.
+Then we run both the Normal and the SN analyses on these simulated CCFs, letting us to retrieve an evaluation of the standard errors.
+This operation has been repeated for all the CCFs available for the analyzed stars.
+The comparison between the standard errors retrieved in this way with the classic noise parameter, {\color{red} obtained by using the Gray's equation cit.
+Gray (1983)} are presented in Fig.~ \ref{fig:se}.
+{\color{red} Xavier: Is it correct how the noise parameter is obtained?
+Or it is simply $\sqrt(photons)$?}
+
+%Given the strong correlation between the $\gamma$ parameter of the SN and its mean, the standard errors are larger respect the Normal fitting analysis.
+This fact confirms how correcting the RVs for stellar activity using Eq.
+\ref{eq:RV:correction} is more helpful when using the SN fitting.
+The standard errors for the FWHM are comparable for both the SN and the Normal analyses, whereas an improvement is clearly measurable for the standard errors associated to the asymmetry indicators.
+The last plot in Fig.~\ref{fig:se} shows that the standard errors for $\gamma$ are $10 \%$ smaller than the ones retrieved for the BIS SPAN.
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
+\section{Discussion} \label{sec:discu}
+
+\xavier{When fitting a SN density to the CCF, it is possible at once to retrieve parameters that describe the RV, i.e.
+the CCF barycenter, the amplitude, also called the contrast, the width, and the asymmetry of the CCF.
+For the RV, we investigated the use of the mean and the median of the SN density.
+Then the width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry, by using $\gamma$, the skewness parameter of the SN density.
+
+When we tested the SN density fit to the CCF provided by the SOAP 2.0 code, that simulate the activity signal induced by a spot or a faculae on a solar-like star, we arrived to the conclusion that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual method.
+By more sensitive, we mean here that the correlation between the skewness and either the mean or median of the SN density is stronger than between BIS SPAN and the mean of a Normal density.
+Moreover, the correlation between the FWHM and the CCF barycenter is also stronger when using the parameters from the SN compared to the parameters from the Normal.
+We also confirmed the behavior that the SN parameters are more correlated than the Normal parameters in the case where a planetary signal is added the to stellar activity modeled by SOAP 2.0.
+
+We also present in this paper a new function to correct for stellar activity signals.
+Generally, when fitting for planetary signals, people use a model composed of one or several Keplerians to account for the planets, in addition to a linear combination with the FWHM and BIS SPAN of the CCF to account for stellar activity signals.
+The new function propose to add a linear dependency with the amplitude of the CCF retrieved either by the SN or Normal density fit, and a interaction term between the asymmetry and the width parameters.
+On the simulated data from SOAP 2.0, this new model allows to mitigate stellar activity signals by a factor of 2 and 3.5 compared to the model generally used, for the faculae and spot, respectively.
+
+When moving to real data, we arrived to the same conclusions regarding the strength of the correlation between the asymmetry and the CCF barycenter, as well as between the width and the CCF barycenter.
+We note however that although in the case of the simulated data, the stronger asymmetry-RV correlation was found between $\gamma$ and the median of the SN, in the case of real data, it was between $\gamma$ and the mean of the SN.
+This can be due to the fact that in SOAP 2.0, the faculae is not modelled properly, as it uses as emerging spectrum the one from a spot.
+We know that the temperature between a spot and a faculae is significantly different, therefore their spectra should be different.
+In addition, there is always several active regions on a star, at different locations in longitude and latitude.
+This could also be responsible for the fact that we do not observe the same behavior for the mean and the median of the SN when we compare the SOAP 2.0 simulation and real data.
+Nevertheless, in both the simulated case and the real cases, the parameters derived from the SN are more sensitive to activity than the parameters derived from a Normal fit.
+In addition, the correlation between the asymmetry and the mean of the SN is always stronger than any other parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
+
+When comparing the different RV estimates obtained from the mean of the Normal density, the mean or the median of the SN density, we see that in the case of real data, the amplitude of stellar activity is larger for the mean of the SN, followed by the median of the SN and the mean of the Normal.
+Although there is a huge gap between the first and the second estimate, the difference between the second and the third is much smaller.
+The mean of the SN density is therefore more sensitive to variation in the CCF shape than the median of the SN or the mean of the Normal, which is not surprising as the SN density is able to model the asymmetry of the CCF, what the Normal density does not.
+
+Having an estimate of the RV that is more sensitive to stellar activity, like the mean of the SN, can help us to probe better stellar rotational periods, or understand better the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}.
+We saw in the preceding section that the RV estimated by the mean of the SN is 60\% noisier than the RV derived by the mean of the Normal.
+This is not necessarily a negative aspect.
+Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized by increasing its induced RV amplitude even if the white noise is 60\% larger.
+
+Even if the different RV estimates have different amplitudes, once we apply our new correction for stellar activity, we arrive exactly to the same RV rms in the residuals, meaning that for activity correction, the SN parameters does not help.
+We note that when comparing the activity correction presented in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, we only see a slight improvement brought by our proposed correction.
+
+We checked if some RV estimates were better at finding planets in RV data affected by observed stellar signals.
+When using the new correction proposed in this paper to mitigate the effect from stellar activity, and when assesing planetary detection based on periodogram analysis, we find very similar detection limits for the three RV estimates presented in this paper.
+Therefore it seems that any of the RV estimate can be used to search for planetary signals.
+
+Finally, we investigated the precision of each of the SN and Normal parameters including the BIS SPAN.
+It turns out that the mean of the SN should not be used to get precise RVs as the standard errors on this parameter is 60\% greater than when taking the mean of the Normal distribution.
+However, the median of the SN should be used, as it is 10\% more precise than the mean of the Normal.
+Regarding the asymmetry estimates, we observe that $\gamma$ has a precision15\% better than the BIS SPAN.
+It is therefore clear in this case that the SN parameters are more precise to measure the barycenter and the asymmetry of the CCF.}
+
+%Finally, we also encourage the use of bootstrapping to estimate more realistic errors on the different parameters of the Normal or SN fitted to the CCF, mainly in the low SNR regime where a gain of 50\% can be reached.
+This takes significantly more time, but note that 100 bootstrapped dataset are enough to get a good estimation of errors.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion} \label{sec:conclu}
+
+\xavier{When searching for small-mass exoplanets using the RV technique, it is crucial to get the best precision possible on the determination of the RV, but also to measure precisely the shape variations of the CCF, as such variations are induced by stellar activity, and not by planets.
+The correlations between the width of the CCF and the RV, and the asymmetry of the CCF and the RV are used as a way to assess if the measurements are affect by stellar activity signals, therefore, the stronger the correlation, the better we can probe small level of stellar activity.
+
+In this paper we introduced a novel approach based on the Skew Normal (SN) density to retrieve the RV and shape variation of the CCF.
+This new method is compared to the usual one, where a Normal density is fitted to the CCF to retrieve the information on the RV and the width of the CCF, and a bisector analysis allows to retrieve the asymmetry of the CCF using the BIS SPAN.
+In addition, we also compare this novel approach to other parameterisations of the CCF asymmetry that have been shown to be more sensitive to activity signals \citep[][]{Boisse-2011,Figueira-2013}.
+
+In all the different tests we could conduct in this paper, the SN parameters were doing as well as the parameters derived when fitting a Normal distribution and calculating the BIS SPAN.
+Moreover, in some cases, we were getting better results when using the SN parameters.
+This is the case when looking at the correlations between the CCF asymmetry and the RV or the CCF width and the RV.
+The SN parameters $\gamma$, SN FWHM and the mean of the SN density always show stronger correlation that any of the parameters derived by the Normal density fit and the BIS SPAN, or the different asymmetry parametrization presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
+Those SN parameters can therefore probe better stellar activity signals.
+In addition, the precision measured on the median of the SN density and the asymmetry of the SN density are 10 and 15\% more precise than the mean of the Normal and BIS SPAN, respectively.
+
+Because of these advantages of using the SN parameters compared to the Normal parameters, BIS SPAN, and all the asymmetry parameters described in \citet{Boisse-2011} and \citet{Figueira-2013}.
+we strongly encourage the community of using this new parametrization of the CCF.
+Correlations between the asymmetry and the mean of the SN, and between the width and the mean of the SN should be used to probe better stellar signals in RV data, and the median of the SN should be used as the new definition for RV.
 }
+
+%the RVs of the star can be calculated as the mean of the SN, whereas its asymmetry parameter $\gamma$ can be naturally used for retrieving information about the asymmetry of the CCF.
+Because of the natural correlation between the RVs and the asymmetry parameter, a linear combination of both $\gamma$ and the FWHM has been implemented for correcting the RVs from stellar activity, allowing us to retrieve a more precise RVs.
+
+%In order to get the standard errors for the estimated parameters, rather than using the common $noise$ statistic, we created a simulated procedure based on perturbing each point of the CCF according to its measurement error.
+Then, by getting from the original profile line $100$ simulated profiles, we run the SN fitting analyses, allowing us retrieving for all the parameter of interests an estimation for their standard errors.
+Concerning the standard error associated to the means of the densitys, the SN fit leads to slightly larger standard errors respect when running the Normal fit.
+This fact can be explained by noticing that as a simulated CCF is created according to the procedure described above, we expect slightly differences on the asymmetry of the CCF as well.
+The natural correlation between the RVs of the star and $\gamma$, where the mean of the SN is shifted in the direction of the asymmetry of the density, leads to larger uncertainties related to the RVs of the star.
+The latter consideration provides a further justification for correcting the RVs of the star from stellar activity and explains why this correction is more helpful when running the proposed analysis rather than the classic Normal fit.
+Concerning the standard errors related to the asymmetry parameters, when using the SN fit the uncertainties are $10 \%$ smaller than using the classic BIS SPAN.
+In conclusion, we showed how using the SN fit provides in an unique step a better understanding of the stellar activity through using the asymmetry parameter $\gamma$ rather than using the common statistics such as the BIS SPAN or other indicators.
+On top of that, when focusing on low signal-to-noise cases, the SN procedure showed how statistically significant results are retrieved with the proposed approach in terms of correlation between the asymmetry of the profile line and the RVs, whereas for the previous analyses this correlation does not result statistically significant.
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
+\section{Acknowledgements}
+
+We are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
+XD is grateful to The Branco Weiss Fellowship--Society in Science for its financial support.
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
+%\section{Appendix}
+\appendix
+\section{Appendix} \label{appendix}
+
+In this Appendix we present the analyses conducted on other 4 stars: HD192310, HD10700, HD215152 and finally Corot-7.
+
+\umberto{Add further information about the stars here presented.}\xavier{}
+
+Table \ref{table:summaryStars} summarizes the results obtained by the SN fit and the some of the results based on the Normal fit.
+The results are all consistent with the conclusions derived by the analyses on Alpha Centauri b.
+The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and RV for all the considered stars.
+The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV for three of the four stars.
+Also for all these stars we corrected the originally estimated RVs from spurious variations in RVs caused by stellar activity, using Eq.
+\ref{eq:RV:correction}.
+Fig.
+\ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RVs.
+While the Normal and SN residuals, once corrected for stellar activity, are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$, the results of the analyses on the star $\text{HD}215152$ (whose CCF's have lower SNR respect to the previous two analyzed stars) suggest that the residuals for the Normal are $0.054 \ms$ higher than the residuals retrieved with the SN analysis.
+Finally, the results of the analysis on $\text{Corot }7$, whose CCF's have lowest SNR, show that once corrected from stellar activity the residuals from the Normal fit are $0.336 \ms$ higher than the residuals retrieved with the SN analysis.
+
+\small{
+\begin{table*}[!t]
+\caption{Subset of notable correlations between the asymmetry parameter (and the FWHM) and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.
+The complete results of the analyses of the correlations for the four stars are presented in Fig.
+\ref{fig:Gliese785:corrPlot}--\ref{fig:Corot7:corrPlot}.}
+\label{table:summaryStars}
+\begin{center}
+\begin{tabular}{ccccccccc}
+\textbf{Star}          &\textbf{ \# CCFs}  &   \textbf{$\text{R}(\text{SN }\gamma, \text{Bis-Span})$} & \textbf{$\text{slope}(\text{SN }\gamma, \text{Bis-Span})$} &   \textbf{$\text{R}(\text{SN }\gamma, \text{SN mean RV})$}\\
+\hline
+\hline
+ $\text{HD}192310  $          &    $1577$    & $0.888$ & $0.786$ & $0.669 (0.64; 0.695)$\\
+\hline
+ $\text{HD}10700 $            &    $7928$    & $0.78$ & $0.604$ & $0.322 (0.302; 0.342)$\\
+\hline
+ $\text{HD}215152 $          &     $273$   &  $ 0.763$ & $0.794$ & $0.571 (0.485; 0.646)$ \\
+\hline
+ $\text{Corot }7$     &     $173$    &  $0.814$  & $0.607$ & $0.561 (0.450; 0.656)$  \\
+\hline
+\rule{0pt}{2ex}    & & & &\\
+\textbf{Star}          &\textbf{$\text{R}(\text{Bis-Span}, \text{RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{SN mean RV})$}  & \textbf{$\text{R}(\text{FWHM}, \text{RV})$} \\
+\hline
+\hline
+ $\text{HD}192310  $& $0.329 (0.285; 0.373)$  & $-0.333 (-0.376; -0.289)$ & $0.666 (0.637; 0.692)$ & $0.476 (0.4367; 0.514)$\\
+\hline
+ $\text{HD}10700 $ & $-0.073 (-0.095; -0.0051)$ & $0.127 (0.105; 0.148)$ & $0.421 (0.403; 0.439)$ & $0.529 (0.513; 0.545)$ \\
+\hline
+ $\text{HD}215152 $& $-0.067 (-0.184; 0.052)$  & $0.269 (0.155; 0.376)$ & $0.210 (0.094; 0.321)$ & $-0.138 (-0.253; -0.020)$ \\
+\hline
+ $\text{Corot }7$ & $0.092 (-0.058; 0.238)$ & $-0.335 (-0.228; -0.082)$ & $-0.709 (0.626;0.776)$ & $0.595 (0.489; 0.683)$ \\
+\hline
+\rule{0pt}{2ex}    & & & &\\
+\end{tabular}
+\end{center}
+\end{table*}
+}
+
+%HD192310
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
+   \caption{Correlation between the asymmetry parameters and the RVs for $\text{HD}192310$.
+The last three plots show the correlation between the FWHM and the RVs for $\text{HD}192310$ using respectively the SN and the Normal fits.
+The p--values associated with each $R$ is statistically different from $0$.}
+   \label{fig:Gliese785:corrPlot}
+\end{center}
+\end{figure*}
+
+\begin{figure*} 
+\begin{center}
+\includegraphics[height = 6in]{NEW_CORRECTIONHD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of RVs for $\text{HD}192310$  using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.
+\ref{eq:RV:correction}.
+Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
+   \label{fig:HD192310:correctionRV}
+\end{center}
+\end{figure*}
+
+%HD10700
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
+   \caption{Correlation between the asymmetry parameters and the RVs for $\text{HD}10700$.
+The last three plots show the correlation between the FWHM and the RVs for $\text{HD}10700$ using respectively the SN and the Normal fits.
+The p--values associated with each $R$ is statistically different from $0$.}
+   \label{fig:Tau:corrPlot}
+\end{center}
+\end{figure*}
+
+\begin{figure*} 
+\begin{center}
+\includegraphics[height = 6in]{NEW_CORRECTIONHD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of RVs for $\text{HD}10700$  using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.
+\ref{eq:RV:correction}.
+Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
+   \label{fig:HD10700:correctionRV}
+\end{center}
+\end{figure*}
+
+%HD215152
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
+   \caption{Correlation between the asymmetry parameters and the RVs for $\text{HD}215152$.
+The last three plots show the correlation between the FWHM and the RVs for $\text{HD}215152$ using respectively the SN and the Normal fits.
+Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
+   \label{fig:HD215152:corrPlot}
+\end{center}
+\end{figure*}
+
+\begin{figure*} 
+\begin{center}
+\includegraphics[height = 6in]{NEW_CORRECTIONHD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of RVs for $\text{HD}215152$ using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.
+\ref{eq:RV:correction}.
+Once corrected for stellar activity, the residuals for the Normal are $0.054$ \ms higher than the residuals retrieved with the SN analysis.}
+   \label{fig:HD215152:correctionRV}
+\end{center}
+\end{figure*}
+
+%Corot-7
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
+   \caption{Correlation between the asymmetry parameters and the RVs for  $\text{Corot }7$.
+The last three plots show the correlation between the FWHM and the RVs for  $\text{Corot }7$ using respectively the SN and the Normal fits.
+Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
+   \label{fig:Corot7:corrPlot}
+\end{center}
+\end{figure*}
+
+\begin{figure*} 
+\begin{center}
+\includegraphics[height = 6in]{NEW_CORRECTIONLRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+   \caption{Set of RVs for  $\text{Corot }7$ using a Normal and a SN fit before and once corrected from stellar activity.
+The correction is done using Eq.
+\ref{eq:RV:correction}.
+Once corrected for stellar activity, the residuals for the Normal are $0.336$ \ms higher than the residuals retrieved with the SN analysis.}
+   \label{fig:Corot-7:correctionRV}
+\end{center}
+\end{figure*}
+
+%%%%%%%
+%\iffalse
+%%\subsection{HD192310}  \label{sec:Gl785}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{[0]HD19231_HistogramsDiff.pdf} 
+%   \caption{RVs comparison for HD192310 considering a Normal and a SN fitting (using both the mean and the median).}
+%   \label{fig:HD192310:RV}
+%\end{figure*}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{HD19231_[2]gamma_vs_bisspan.pdf} 
+%   \caption{Correlation between $\gamma$ and the BIS SPAN for HD192310.}
+%   \label{fig:Gliese785:corr.gamma}
+%\end{figure*}
+%%
+%
+%
+%%\subsection{Tau Ceti}  \label{sec:Taucet}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{[0]TauCeti_HistogramsDiff.pdf} 
+%   \caption{RVs comparison for Tau Ceti considering a Normal and a SN fitting (using both the mean and the median).}
+%   \label{fig:Tau Ceti:RV}
+%\end{figure*}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{HD10700_[2]gamma_vs_bisspan.pdf} 
+%   \caption{Correlation between $\gamma$ and the BIS SPAN for Tau Ceti.}
+%   \label{fig:Tau:corr.gamma}
+%\end{figure*}
+%%
+%
+%
+%%\subsection{HD215152}  \label{sec:HD215152}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{[0]HD21515_HistogramsDiff.pdf} 
+%   \caption{RVs comparison for HD215152 considering a Normal and a SN fitting (using both the mean and the median).}
+%   \label{fig:HD215152:RV}
+%\end{figure*}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{HD21515_[2]gamma_vs_bisspan.pdf} 
+%   \caption{Correlation between $\gamma$ and the BIS SPAN for HD 215152.}
+%   \label{fig:HD215152:corr.gamma}
+%\end{figure*}
+%%
+%
+%
+%%\subsection{Corot-7}  \label{sec:Corot7}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{[0]LRa01_E_HistogramsDiff.pdf} 
+%   \caption{RVs comparison for Corot-7 considering a Normal and a SN fitting (using both the mean and the median).}
+%   \label{fig:corot7:RV}
+%\end{figure*}
+%%
+%\begin{figure*}[htbp]
+%   \centering
+%\includegraphics[height = 3in]{LRa01_E_[2]gamma_vs_bisspan.pdf} 
+%   \caption{Correlation between $\gamma$ and the BIS SPAN for Corot-7.}
+%   \label{fig:Corot7:corr.gamma}
+%\end{figure*}
+%%
+%\fi
+%%
 
@@
 
-\subsection{Estimation of standard errors for the CCF parameters for real stars} \label{sec:bootstrap_real_star}
-In the top plots of Fig.~\ref{fig:se} we show the different errors for the RVs, either defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels.
-The parameter SN50 corresponds to the SNR in order 50, which defines a wavelength of 550\,nm.
-In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameters derived from the bootstrap analysis fitting the Normal density.
-We first see that the errors on the CCF parameters only depends on the SNR and do not depend on the spectral type.
-This is true if the spectral type are not too different though, like here where we show the results for G and K dwarfs.
-
-Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.6$ when using SN mean RV and $0.9$ when using SN median RV.
-In other words, by using SN median RV as parameter that defines the radial velocity of the star given a CCF, we get standard errors $10\%$ smaller than using the Normal fit and its corresponding mean.
-This result is consistent with what we observed with the simulation from SOAP presented in Sec.
-\ref{sec:soap}.
-
-Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable.
-Therefore, the precision in the width of the CCF is the comparable if we fit a Normal or a SN to the CCF.
-
-Finally, for the errors in evaluating the asymmetry of the CCF, we see that, when fitting the SN to the CCF, the asymmetry errors are $15\%$ smaller.
-Therefore, the SN fit gives a better precision in CCF asymmetry than what can be reached using BIS SPAN.
-We recall moreover that, using the SN, all parameters are automatically retrieved in 1 single step, while in the common approach the RV and the BIS SPAN are calculated separately.
-
-%
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
-   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
-When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
-To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
-Note that for the asymmetry, the error in BIS SPAN is in \kms.
-To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
-   \label{fig:se}
-\end{center}
-\end{figure*}
-
-%, using the spectrum derivative
-%, the pure photon-noise error on RV measured 
-%Together with the pointwise estimates, retrieving the standard errors for the RVs of the star, $\gamma$ and the FWHM provides information about the uncertainties associated to each parameter.
-Since the procedure for retrieving the RVs of the star consists in fitting with a density function a CCF, getting the standard errors for all the parameter of interests cannot be done by using the common asymptotic theory.
-The implementation of a standard bootstrap analysis cannot as well be done, because the points of the CCF are highly correlated.
-In the analysis of the present work, in order to get the standard errors for the parameters of interest for a particular CCF, we moved each point of this CCF according to its measurement errors, producing $100$ simulated CCFs from the original one.
-Then we run both the Normal and the SN analyses on these simulated CCFs, letting us to retrieve an evaluation of the standard errors.
-This operation has been repeated for all the CCFs available for the analyzed stars.
-The comparison between the standard errors retrieved in this way with the classic noise parameter, {\color{red} obtained by using the Gray's equation cit.
-Gray (1983)} are presented in Fig.~ \ref{fig:se}.
-{\color{red} Xavier: Is it correct how the noise parameter is obtained?
-Or it is simply $\sqrt(photons)$?}
-
-%Given the strong correlation between the $\gamma$ parameter of the SN and its mean, the standard errors are larger respect the Normal fitting analysis.
-This fact confirms how correcting the RVs for stellar activity using Eq.
-\ref{eq:RV:correction} is more helpful when using the SN fitting.
-The standard errors for the FWHM are comparable for both the SN and the Normal analyses, whereas an improvement is clearly measurable for the standard errors associated to the asymmetry indicators.
-The last plot in Fig.~\ref{fig:se} shows that the standard errors for $\gamma$ are $10 \%$ smaller than the ones retrieved for the BIS SPAN.
-
-%-----------------------------------------------------------------------------------------------------------------------------------------------
-\section{Discussion} \label{sec:discu}
-
-An analysis of the CCF residuals after fitting a Normal or SN density shows that the SN is a slightly better model to explain the shape of the CCF.
-This comes from the fact that CCF's present a natural asymmetry due the convective blueshift.
-
-We tested at first our assumptions by using simulated CCF's retrieved using the software SOAP 2.0.
-We then compared for five real stars the difference between the RV's (defined as mean of a Normal, mean of the SN or median of the SN), FWHM and asymmetry (BIS SPAN in the Normal case and $\gamma$ in the SN case).
-The $\gamma$ parameter is linearly dependent on the BIS SPAN, with always a strong correlation coefficient.
-%To compare $\gamma$, that do not have any units, with BIS SPAN expressed in \kms, one has simply to multiply $\gamma$ by the slope of the linear dependence between $\gamma$ and BIS SPAN. 
-The slope of this linear correlation changes depending on the studied star. This is probably because the spectral type is different, therefore the effects from stellar activity are different.
-
-When using as parameter for the RV the mean of the SN, the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal.
-However, once the RV is defined as the median of the SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
-When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma$ in the SN case) with respect to the RV's (RV's in the Normal case or SN RV's in the SN case), we observe that the correlations are always stronger for the parameters of the SN.
-Therefore, the SN parameters are more sensitive to activity.
-In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of $0.322$ between $\gamma$ and SN mean RV, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.$225$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion} \label{sec:conclu}
-
-In this paper we introduced a novel approach based on the Skew Normal (SN) density to retrieve RV's and shape variations in the CCF of stars.
-When searching for small-mass exoplanets using the RV technique, it is essential to understand variation of the shape of the CCF, which is a proxy for stellar activity effects.
-The standard approach consist at first to fit a Normal density to the CCF to get the RV and FWHM, defined as the mean and the FWHM of the Normal density, and then to measure the asymmetry of the CCF by calculating the BIS SPAN.
-FWHM and BIS SPAN give us information on the line shape that are used to probe stellar activity signals.
-
-In this paper we propose to conduct the analysis fitting a SN density to the CCF.
-Since the CCF presents a natural asymmetry due the convective blueshift, the SN density can in principle better catch these aspects respect the Normal fit.
-On top of that, by using the SN density to fit CCF's, we can measure simultaneously the RV of the star, the width and the asymmetry of the CCF.
-
-Starting from the simulation environment SOAP and then moving to real stars, we showed that using the SN density to fit CCF's leads to a significant improvement to probing stellar activity.
-While for the Normal density mean and median are equivalent, using the SN fit different location parameters can be tested.
-While the median of the SN is a more robust statistic respect variations in the shape of the CCF, the mean of the SN is more sensible to changes in the asymmetry of the CCF.
-We suggest to use as parameter that defines the RV of the star the median of the SN, since the standard errors related to this parameter working with CCF's from real stars are on average $10\%$ smaller than the standard errors retrieved using the Normal density.
-To evaluate changes in the asymmetry of the CCF, we suggest to use the mean of the SN.
-The correlation between SN mean RV and SN FWHM and the correlation between SN mean RV and $\gamma$ (the asymmetry parameter of the SN) are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}).
-The precision on the asymmetry measured by $\gamma$ is greater than the one on BIS SPAN by $\sim$15\%.
-Therefore when searching for rotational periods in the data, or applying Gaussian Processes to account for stellar activity signals, the SN parameters should be used.
-
-Because of stellar activity the estimated RV's are contaminated by spurious variations.
-We propose to use a function that corrects from stellar activity that beyond the width and the asymmetry parameters of the CCF includes also the contrast parameter A and the fourth parameter defined as the interaction between width and the asymmetry parameters of the CCF.
-We found these new two parameter helpful to explain part of the spurious variations in RV's caused by stellar activity.
-
-Finally, we also encourage the use of bootstrapping to estimate more realistic errors on the different parameters of the Normal or SN fitted to the CCF, mainly in the low SNR regime where a gain of 50\% can be reached.
-This takes significantly more time, but note that 100 bootstrapped dataset are enough to get a good estimation of errors.
-
-%the RVs of the star can be calculated as the mean of the SN, whereas its asymmetry parameter $\gamma$ can be naturally used for retrieving information about the asymmetry of the CCF.
-Because of the natural correlation between the RVs and the asymmetry parameter, a linear combination of both $\gamma$ and the FWHM has been implemented for correcting the RVs from stellar activity, allowing us to retrieve a more precise RVs.
-
-%In order to get the standard errors for the estimated parameters, rather than using the common $noise$ statistic, we created a simulated procedure based on perturbing each point of the CCF according to its measurement error.
-Then, by getting from the original profile line $100$ simulated profiles, we run the SN fitting analyses, allowing us retrieving for all the parameter of interests an estimation for their standard errors.
-Concerning the standard error associated to the means of the densitys, the SN fit leads to slightly larger standard errors respect when running the Normal fit.
-This fact can be explained by noticing that as a simulated CCF is created according to the procedure described above, we expect slightly differences on the asymmetry of the CCF as well.
-The natural correlation between the RVs of the star and $\gamma$, where the mean of the SN is shifted in the direction of the asymmetry of the density, leads to larger uncertainties related to the RVs of the star.
-The latter consideration provides a further justification for correcting the RVs of the star from stellar activity and explains why this correction is more helpful when running the proposed analysis rather than the classic Normal fit.
-Concerning the standard errors related to the asymmetry parameters, when using the SN fit the uncertainties are $10 \%$ smaller than using the classic BIS SPAN.
-In conclusion, we showed how using the SN fit provides in an unique step a better understanding of the stellar activity through using the asymmetry parameter $\gamma$ rather than using the common statistics such as the BIS SPAN or other indicators.
-On top of that, when focusing on low signal-to-noise cases, the SN procedure showed how statistically significant results are retrieved with the proposed approach in terms of correlation between the asymmetry of the profile line and the RVs, whereas for the previous analyses this correlation does not result statistically significant.
-
-%-----------------------------------------------------------------------------------------------------------------------------------------------
-\section{Acknowledgements}
-
-We are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
-XD is grateful to The Branco Weiss Fellowship--Society in Science for its financial support.
-
-%-----------------------------------------------------------------------------------------------------------------------------------------------
-%\section{Appendix}
-\appendix
-\section{Appendix} \label{appendix}
-
-In this Appendix we present the analyses conducted on other 4 stars: HD192310, HD10700, HD215152 and finally Corot-7.
-
-\umberto{Add further information about the stars here presented.}\xavier{}
-
-Table \ref{table:summaryStars} summarizes the results obtained by the SN fit and the some of the results based on the Normal fit.
-The results are all consistent with the conclusions derived by the analyses on Alpha Centauri b.
-The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and RV for all the considered stars.
-The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV for three of the four stars.
-Also for all these stars we corrected the originally estimated RV's from spurious variations in RV's caused by stellar activity, using Eq.
-\ref{eq:RV:correction}.
-Fig.
-\ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RV's.
-While the Normal and SN residuals, once corrected for stellar activity, are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$, the results of the analyses on the star $\text{HD}215152$ (whose CCF's have lower SNR respect to the previous two analyzed stars) suggest that the residuals for the Normal are $0.054 \ms$ higher than the residuals retrieved with the SN analysis.
-Finally, the results of the analysis on $\text{Corot }7$, whose CCF's have lowest SNR, show that once corrected from stellar activity the residuals from the Normal fit are $0.336 \ms$ higher than the residuals retrieved with the SN analysis.
-
-\small{
-\begin{table}[!t]
-\scalebox{0.45}{
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
-\hline
-\textbf{Star}          &\textbf{ \# CCFs}  &   \textbf{$\text{R}(\text{SN }\gamma, \text{Bis-Span})$} & \textbf{$\text{slope}(\text{SN }\gamma, \text{Bis-Span})$} &   \textbf{$\text{R}(\text{SN }\gamma, \text{SN mean RV})$} & \textbf{$\text{R}(\text{Bis-Span}, \text{RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{SN mean RV})$}  & \textbf{$\text{R}(\text{FWHM}, \text{RV})$} \\
-\hline
- $\text{HD}192310  $          &    $1577$    & $0.888$ & $0.786$ & $0.669 (0.64; 0.695)$ & $0.329 (0.285; 0.373)$  & $-0.333 (-0.376; -0.289)$ & $0.666 (0.637; 0.692)$ & $0.476 (0.4367 0.514)$\\
-\hline
- $\text{HD}10700 $            &    $7928$    & $0.78$ & $0.604$ & $0.322 (0.302; 0.342)$ & $-0.073 (-0.095; -0.0051)$ & $0.127 (0.105; 0.148)$ & $0.421 (0.403; 0.439)$ & $0.529 (0.513; 0.545)$ \\
-\hline
- $\text{HD}215152 $          &     $273$   &  $ 0.763$ & $0.794$ & $0.571 (0.485; 0.646)$ & $-0.067 (-0.184; 0.052)$  & $0.269 (0.155; 0.376)$ & $0.210 (0.094; 0.321)$ & $-0.138 (-0.253; -0.020)$ \\
-\hline
- $\text{Corot }7$     &     $173$    &  $0.814$  & $0.607$ & $0.561 (0.450; 0.656)$ & $0.092 (-0.058; 0.238)$ & $-0.335 (-0.228; -0.082)$ & $-0.709 (0.626;0.776)$ & $0.595 (0.489; 0.683)$ \\
-\hline
-\end{tabular}
-}
-\caption{Subset of notable correlations between the asymmetry parameter (and the FWHM) and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.
-The complete results of the analyses of the correlations for the four stars are presented in Fig.
-\ref{fig:Gliese785:corrPlot}--\ref{fig:Corot7:corrPlot}.}
-\label{table:summaryStars}
-\end{table}
-}
-
-%HD192310
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}192310$.
-The last three plots show the correlation between the FWHM and the RV's for $\text{HD}192310$ using respectively the SN and the Normal fits.
-The p--values associated with each $R$ is statistically different from $0$.}
-   \label{fig:Gliese785:corrPlot}
-\end{figure*}
-
-\begin{figure*} 
-   \centering
-\includegraphics[height = 6in]{NEW_CORRECTIONHD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RV's for $\text{HD}192310$  using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.
-\ref{eq:RV:correction}.
-Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
-   \label{fig:HD192310:correctionRV}
-\end{figure*}
-
-%HD10700
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}10700$.
-The last three plots show the correlation between the FWHM and the RV's for $\text{HD}10700$ using respectively the SN and the Normal fits.
-The p--values associated with each $R$ is statistically different from $0$.}
-   \label{fig:Tau:corrPlot}
-\end{figure*}
-
-\begin{figure*} 
-   \centering
-\includegraphics[height = 6in]{NEW_CORRECTIONHD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RV's for $\text{HD}10700$  using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.
-\ref{eq:RV:correction}.
-Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
-   \label{fig:HD10700:correctionRV}
-\end{figure*}
-
-%HD215152
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RV's for $\text{HD}215152$.
-The last three plots show the correlation between the FWHM and the RV's for $\text{HD}215152$ using respectively the SN and the Normal fits.
-Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
-   \label{fig:HD215152:corrPlot}
-\end{figure*}
-
-\begin{figure*} 
-   \centering
-\includegraphics[height = 6in]{NEW_CORRECTIONHD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RV's for $\text{HD}215152$ using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.
-\ref{eq:RV:correction}.
-Once corrected for stellar activity, the residuals for the Normal are $0.054$ \ms higher than the residuals retrieved with the SN analysis.}
-   \label{fig:HD215152:correctionRV}
-\end{figure*}
-
-%Corot-7
-\begin{figure*}[htbp]
-   \centering
-\includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RV's for  $\text{Corot }7$.
-The last three plots show the correlation between the FWHM and the RV's for  $\text{Corot }7$ using respectively the SN and the Normal fits.
-Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
-   \label{fig:Corot7:corrPlot}
-\end{figure*}
-
-\begin{figure*} 
-   \centering
-\includegraphics[height = 6in]{NEW_CORRECTIONLRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RV's for  $\text{Corot }7$ using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.
-\ref{eq:RV:correction}.
-Once corrected for stellar activity, the residuals for the Normal are $0.336$ \ms higher than the residuals retrieved with the SN analysis.}
-   \label{fig:Corot-7:correctionRV}
-\end{figure*}
-
-%%%%%%%
-%\iffalse
-%%\subsection{HD192310}  \label{sec:Gl785}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{[0]HD19231_HistogramsDiff.pdf} 
-%   \caption{RVs comparison for HD192310 considering a Normal and a SN fitting (using both the mean and the median).}
-%   \label{fig:HD192310:RV}
-%\end{figure*}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{HD19231_[2]gamma_vs_bisspan.pdf} 
-%   \caption{Correlation between $\gamma$ and the BIS SPAN for HD192310.}
-%   \label{fig:Gliese785:corr.gamma}
-%\end{figure*}
-%%
-%
-%
-%%\subsection{Tau Ceti}  \label{sec:Taucet}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{[0]TauCeti_HistogramsDiff.pdf} 
-%   \caption{RVs comparison for Tau Ceti considering a Normal and a SN fitting (using both the mean and the median).}
-%   \label{fig:Tau Ceti:RV}
-%\end{figure*}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{HD10700_[2]gamma_vs_bisspan.pdf} 
-%   \caption{Correlation between $\gamma$ and the BIS SPAN for Tau Ceti.}
-%   \label{fig:Tau:corr.gamma}
-%\end{figure*}
-%%
-%
-%
-%%\subsection{HD215152}  \label{sec:HD215152}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{[0]HD21515_HistogramsDiff.pdf} 
-%   \caption{RVs comparison for HD215152 considering a Normal and a SN fitting (using both the mean and the median).}
-%   \label{fig:HD215152:RV}
-%\end{figure*}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{HD21515_[2]gamma_vs_bisspan.pdf} 
-%   \caption{Correlation between $\gamma$ and the BIS SPAN for HD 215152.}
-%   \label{fig:HD215152:corr.gamma}
-%\end{figure*}
-%%
-%
-%
-%%\subsection{Corot-7}  \label{sec:Corot7}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{[0]LRa01_E_HistogramsDiff.pdf} 
-%   \caption{RVs comparison for Corot-7 considering a Normal and a SN fitting (using both the mean and the median).}
-%   \label{fig:corot7:RV}
-%\end{figure*}
-%%
-%\begin{figure*}[htbp]
-%   \centering
-%\includegraphics[height = 3in]{LRa01_E_[2]gamma_vs_bisspan.pdf} 
-%   \caption{Correlation between $\gamma$ and the BIS SPAN for Corot-7.}
-%   \label{fig:Corot7:corr.gamma}
-%\end{figure*}
-%%
-%\fi
-%%
-
 %%-----------------------------------------------------------------------------------------------------------------------------------------------

### 2018-06-02 manuscript.tex
Add files via upload
Went through Sect 1, 2, 3, 4 (no conclusions Sec.4), did changes, according to Jessi's comments, updated plots

@@
 
-\institute{Department of Statistical Sciences, University of Padua, Padua, Italy
+\institute{Department of Mathematics and Statistics, University of Helsinki, Helsinki, Finland
 	      \and Department of Statistics and Data Science, Yale University, New Haven, CT, USA
@@
 \jessi{Is there a reference for this that could be added?}
-In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and using its mean (RV \jessi{I believe this was going to be updated to ``N mean RV''?}), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV).
+In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and using its mean (N mean RV), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV).
 We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is different from the two others with a maximum amplitude happening at a different phase.
@@
 \caption{Using CCFs from SOAP 2.0 with a single facula, the estimated RV changes as function of the orbital phase.
-SN mean RV seems to have the smallest spurious variations caused by the facula.\jessi{The previous sentence does not seem correct.}  \jessi{The cyan line is hard to see in the legend, and may be impossible in a black-and-white version - could the legend background be white?}
+SN mean RV seems to have the smallest spurious variations caused by the facula.\jessi{The previous sentence does not seem correct.}
 }
@@
 The strength of the correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are stronger than the correlations between BIS SPAN and RV, with Pearson correlation coefficient $R$ values of 0.46, -0.67 and -0.09, respectively.
-For the width barycenter correlations, there is a stronger correlation between SN FWHM and SN mean RV compared to the one between FWHM and RV \jessi{updated to N mean RV?}, $R=0.98$ and 0.84, respectively.
+For the width barycenter correlations, there is a stronger correlation between SN FWHM and SN mean RV compared to the one between FWHM and N mean RV, $R=0.98$ and 0.84, respectively.
 In this case however, the correlation between SN FWHM and SN median RV is smaller with $R=0.50$.
@@
    \caption{(top) The spurious RVs caused by a facula in the simulated data using a Normal and a SN fit.
-Before and once corrected from stellar activity.
-\jessi{What is the correction done here?
-I think what you mean is this:  ``The black circles are the estimated RVs and the red plus signs are the estimated RVs from the fit model of  Eq.~\ref{eq:RV:correction}.''  If my assumption is correct, the legend should say ``RV estimates'' and ``RV model'' or something like that.
-Otherwise this is rather confusing because in the bottom plot you are actually comparing residuals from two models, while the top has a different interpretation.}
-   %
- (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (new correction) and the usual correction \jessi{it might be helpful to actually have an equation for the usual/old model}.
+The black circles are the estimated RVs and the red plus signs are the estimated RVs from the fit model of  Eq.~\ref{eq:RV:correction}.
+   %
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
+std) and the residuals from the usual correction (Usual corr.
+std), obtained fitting the function $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$.
 The residuals have a smaller systematic component when using the proposed model of
-  Eq.~\ref{eq:RV:correction} (blue circles) compared to the usual model (blue triangles).
-The estimated parameters are presented in Table \ref{table:faculae.test} \jessi{This table only has p-values and $R^2$}. }
+  Eq.~\ref{eq:RV:correction} (black circles) compared to the usual model (blue triangles).
+The tests of statistical significance on the parameters are presented in Table \ref{table:faculae.test}.}
     \label{fig:faculae.correction}
@@
 The correlation between $\gamma$ and SN median RV is the strongest with a $R=0.94$, followed by the correlation BIS SPAN - RV and $\gamma$ - SN mean RV, with $R=0.86$.
-\jessi{Do the previous numbers need updating?}  Regarding the correlation between the width and the CCF barycenter, we note that the variation is seen as a circle in this parameter space and therefore no correlation is observed.
+Regarding the correlation between the width and the CCF barycenter, we note that the variation is seen as a circle in this parameter space and therefore no correlation is observed.
 Once again, like in the case of the facula, we see that some parameters of the SN gives stronger correlations than when using the Normal parameters.
@@
 As before, the originally RVs were corrected by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction}. 
-In this setting, the proposed correction almost completely addresses the issue \jessi{what issue?} when considering the SN or Normal parameters, with values of $R^2$ larger than 0.99. 
-Considering Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms.
-\jessi{Doesn't the facula setting do better getting down to $\sim$0.13 \ms?}
+In this setting, the proposed correction almost completely explains the spurious variations in RV's when considering the SN or Normal parameters, with values of $R^2$ larger than 0.99. 
+Considering Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than 3\ms down to a rms of 13 \ms.
 In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however, \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant.
-When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.
-
-In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summarized in Table \ref{table:spot.test}, \umberto{we observe that the $\beta_0$, and $\beta_3$, corresponding respectively to the intercept and to the width of the CCF}, are \umberto{not helpful} to understand the variation measured in RVs.
+When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.}
+
+In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summarized in Table \ref{table:spot.test}, we observe that the $\beta_0$, and $\beta_3$, corresponding respectively to the intercept and to the width of the CCF, are not helpful to understand the variation measured in RVs when the SN fit is used.
+When the Normal fit has used, only the parameter  $\beta_0$ associated to the intercept is not statistically helpful to address part of the spurious variations in RVs.
 This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
-We see also that the ampltitude parameter, with coefficient $\beta_1$ is only useful to explain the RV variation of the spot in the case of the Normal distribution.}
+We see also that the ampltitude parameter, with coefficient $\beta_1$ is only useful to explain the RV variation of the spot in the case of the Normal distribution.
 
@@
 \begin{center}
-\includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{\umberto{Set of  spurious variations in RVs caused by a \textbf{spot} using a Normal and a SN fit before and once corrected from stellar activity.
-The new correction has done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
-Once corrected for stellar activity using the proposed linear function (black dots), the residuals present a smaller systematic component if compared with the residuals obtained with the usual correction (blue triangles).}}
+\includegraphics[height = 6in]{SPOT_COMPARISON_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+ \caption{(top) The spurious RVs caused by a spot in the simulated data using a Normal and a SN fit.
+The black circles are the estimated RVs and the red plus signs are the estimated RVs from the fit model of  Eq.~\ref{eq:RV:correction}.
+   %
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
+std) and the residuals from the usual correction (Usual corr.
+std), obtained fitting the function $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$.
+The residuals have a smaller systematic component when using the proposed model of
+  Eq.~\ref{eq:RV:correction} (black circles) compared to the usual model (blue triangles).
+The tests of statistical significance on the parameters are presented in Table \ref{table:spot.test}.}
     \label{fig:spot.correction}
@@
 \caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction} to correct the estimated RVs from spurious variations caused by a spot. 
-All the covariates are statistically significant to explain the variability in RVs caused by a spot, except the intercept and the width of the CCF.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability in the estimated RVs.
-\jessi{Isn't the width of the CCF parameter sig for N mean RV at 0.017?
-Previously it was noted that a 5\% significance level was going to be used.}}
+Concerning the SN fit, all the covariates are statistically significant to explain the variability in RVs caused by a spot, except the intercept and the width of the CCF.
+Concerning the Normal fit, only the intercept is not statistically significant to explain the variability in RVs caused by a spot.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability in the estimated RVs. }
 \label{table:spot.test}
@@
 The last simulation presented consists in having a planetary signal influencing the CCF, in addition to the 1\% spot modeled before (see Sec.~\ref{sec:soap.spot}).
-\xavier{The purpose of this example is to check if we are able to disentangle as efficiently the two different sources of variations when using the parameters derived using a Normal, or a SN fit the the CCF.
-In this case, we inject a planet with an semi-amplitude of 10 \ms, with no eccentricity, and with a period corresponding to 1/3rd of the stellar rotational phase.}
+The purpose of this example is to check if we are able to disentangle as efficiently the two different sources of variations when using the parameters derived using a Normal, or a SN fit the the CCF.
+In this case, we inject a planet with an semi-amplitude of 10 \ms, with no eccentricity, and with a period corresponding to 1/3rd of the stellar rotational phase.
 
@@
 
-\umberto{Do we need to point out the following: \\ If we look at the $R^2$, the proposed function that corrects from stellar activity addresses (almost) all the spurious variations caused in RVs by active regions.
-Anyway, if we look the residuals, a systematic component is still present, although smaller respect the residual obtained with the usual correction.
-The residuals are supposed to be homoscedastic with 0 mean under the assumption that the model is correct.
-Therefore, since our $R^2$ is always close to $1$, we can argue, as we discussed already many times, that the CCF does not follow a normal fit, neither a SN one, otherwise, given our extremely high $R^2$ we should have gotten homoscedastic 0 mean residuals.}
-
 \xavier{is all this discussion really usefull ?

### 2018-06-03 manuscript.tex
Finished Sect 4 and 5

--- 2018-06-02 manuscript.tex
@@
 %
-\begin{figure}[htbp]
+\begin{figure}[t]
 \begin{center}
@@
 %%%To initially check this intuition, we compared the CCF residuals after fitting a Normal and a SN density for 2 stars.
-The first star is Alpha Centauri b, whose CCF's have high signal-to-noise ratio (SNR).
+The first star is Alpha Centauri B, whose CCF's have high signal-to-noise ratio (SNR).
 The second star is Corot-7, whose CCF's have low SNR.
@@
 %%%\includegraphics[height = 2.5in]{[1]LRa01_E2Residuals.pdf} 
-%%%   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCF's from the star Alpha Centauri b (left) and Corot-7 (right).
+%%%   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCF's from the star Alpha Centauri B (left) and Corot-7 (right).
 When looking at the residuals corresponding to the center of the CCF, the SN fit leads to slightly better results for both stars.} %Moreover, as the SNR decreases, the SN density shows smaller residuals respect the Normal ones.}
@@
 The faculae is face-on when the phase equals to 0.
-Note that a 3\% faculae is relatively large for the Sun; at maximum activity, big faculae have generally a size of 1\%.
-\jessi{Is there a reference for this that could be added?}
-In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and using its mean (RV \jessi{I believe this was going to be updated to ``N mean RV''?}), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV).
+Note that a 3\% faculae is relatively large for the Sun; at maximum activity, big faculae have generally a size of 1\% \citep[e.g.][]{Borgniet-2015}.
+In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and using its mean (N mean RV), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV).
 We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is different from the two others with a maximum amplitude happening at a different phase.
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
-\caption{Using CCFs from SOAP 2.0 with a single facula, the estimated RV changes as function of the orbital phase.
-SN mean RV seems to have the smallest spurious variations caused by the facula.\jessi{The previous sentence does not seem correct.}  \jessi{The cyan line is hard to see in the legend, and may be impossible in a black-and-white version - could the legend background be white?}
+\caption{\xavier{RV estimated either by the mean of a Normal density fit to the CCF (N mean RV) or by the mean (SN mean RV) or median (SN median RV) of a SN density fit to the CCF.
+In this case, the CCFs have been generated using SOAP 2.0, considering an equatorial 3\% faculae on the simulated Sun.
+The star do one full rotation between phase -0.5 and 0.5, with the faculae being seen face-on for phase 0.
+The variation seen in SN mean RV is quite different from the variations seen in SN median RV and N mean RV.}  \jessi{The cyan line is hard to see in the legend, and may be impossible in a black-and-white version - could the legend background be white?}
 }
@@
 Correlations between the different RV estimates and the different CCF asymmetry or width estimates are displayed in Fig.~\ref{fig:faculae.corr}.
-The strength of the correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are stronger than the correlations between BIS SPAN and RV, with Pearson correlation coefficient $R$ values of 0.46, -0.67 and -0.09, respectively.
-For the width barycenter correlations, there is a stronger correlation between SN FWHM and SN mean RV compared to the one between FWHM and RV \jessi{updated to N mean RV?}, $R=0.98$ and 0.84, respectively.
+The strength of the correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are stronger than the correlations between BIS SPAN and RV, with Pearson correlation coefficient values of $R$=0.46, -0.67 and -0.09, respectively.
+For the width barycenter correlations, there is a stronger correlation between SN FWHM and SN mean RV compared to the one between FWHM and N mean RV, $R=0.98$ and 0.84, respectively.
 In this case however, the correlation between SN FWHM and SN median RV is smaller with $R=0.50$.
-This first analysis shows that in the case of a facula, using some parameters from the SN can lead to much stronger correlation than the usual Normal parameters and therefore, the SN parameters may better probe stellar activity.
+This first analysis shows that in the case of a facula, using some parameters from the SN can lead to stronger correlation than the usual Normal parameters and therefore, the SN parameters may better probe stellar activity.
 We investigate this feature further in the next sections where we consider simulated data with a single spot and a spot plus a planet, and in Sec~\ref{sec:4} with real observations.
@@
 \includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
-   \caption{Using CCFs from SOAP 2.0 with a single facula, the correlation between the estimated RVs and the asymmetry parameters are displayed.
-In this case both the shape and the width of the CCF changes as the facula moves, producing statistically significant correlations between the estimated RVs and, respectively, the asymmetry parameter or the width parameter.}
+   \caption{\xavier{\emph{Left:} Correlation between the different asymmetry parameters and the different RV estimates in the case of an equatorial 3\% faculae on the simulated Sun.
+\emph{Right:} Correlation between the different width parameters and the different RV estimates for the same faculae.
+   In the presence of a faculae, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations.}}
     \label{fig:faculae.corr}
@@
 In addition, the rms of the different estimates of the RV reduces from about 3 \ms before correction to values below 0.15 \ms after correction.
-We see a slightly smaller rms after correction for the SN parameters, however the different is not significant.
-\jessi{In the previous sentence, is this a comparison between SN and N?
-If so, it should be clarified.}
+We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters, however the different is probably not significant.
 When comparing the correction proposed in Eq.~\ref{eq:RV:correction} with what is generally used (i.e.
 a linear combination of only the asymmetry and width parameter), we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2.
-Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that the parameter related to the intercept, $\beta_0$, is only significant at a level of 1\% in the case of the Normal parameters or when SN median RV is used.
-\jessi{Is the point about $\beta_0$ relevant?}
+Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that all the Sn or Normal parameters are relevant for the correction.
 
@@
 \includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{(top) The spurious RVs caused by a facula in the simulated data using a Normal and a SN fit.
+   \caption{\xavier{I agree with Jessi here, you should show on the top plot the estimated RVs, and the new and old model.
+Then leave the bottom plot the same.
+I would put estimated RVs in black, new model in red and old model in green, then keep the same colors for the bottoms plots.
+Also for the caption, I would use like you put already SN mean RV estimate, SN median estimate, N mean estimate, and for the model "new activity model", "usual activity model"}(top) The spurious RVs caused by a facula in the simulated data using a Normal and a SN fit.
 Before and once corrected from stellar activity.
@@
 \begin{center}
-\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction} to correct the estimated  RVs from spurious variations caused by a facula.
-All the variables, except the intercept when the response variable is SN median RV, are statistically significant to explain spurious variations in RVs caused by a facula.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability in the estimated RVs.}
+\caption{\xavier{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 3\% faculae on the simulated Sun.
+All the variables corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by a facula.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability seen in the different RV estimates.}}
 \label{table:faculae.test}
@@
 The spot is face on when the phase equals to 0.
-Note that this is a large spot for the Sun, as in general large spots are more in the regime of 0.1\%.\jessi{Can we add a reference for the previous statement?}
+Note that this is a large spot for the Sun, as in general large spots are more in the regime of 0.1\% \citep[e.g.][]{Borgniet-2015}.
 In Fig.~\ref{fig:spot}, we shows the barycentric variation of the CCF induced by this simulated spot.
@@
 Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and the different estimates for the CCF barycenter (i.e.
-the SN mean RV, SN median RV and RV).
-The correlation between $\gamma$ and SN median RV is the strongest with a $R=0.94$, followed by the correlation BIS SPAN - RV and $\gamma$ - SN mean RV, with $R=0.86$.
-\jessi{Do the previous numbers need updating?}  Regarding the correlation between the width and the CCF barycenter, we note that the variation is seen as a circle in this parameter space and therefore no correlation is observed.
-Once again, like in the case of the facula, we see that some parameters of the SN gives stronger correlations than when using the Normal parameters.
+SN mean RV, SN median RV and N mean RV).
+The correlation between $\gamma$ and SN median RV is the strongest with a $R=0.94$, followed by the correlation BIS SPAN - N mean RV and $\gamma$ - SN mean RV, with $R=0.86$.
+Regarding the correlation between the width and the CCF barycenter, we note that the variation is seen as a circle in this parameter space and therefore no correlation is observed.
+Once again, like in the case of the facula, we see that some parameters of the SN gives stronger correlations than the Normal parameters.
 
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
-\caption{RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
-SN mean RV seems to have the smallest spurious variations caused by the faculae.}
+\caption{\xavier{RV estimated either by the mean of a Normal density fit to the CCF (N mean RV) or by the mean (SN mean RV) or median (SN median RV) of a SN density fit to the CCF.
+In this case, the CCFs have been generated using SOAP 2.0, considering an equatorial 1\% spot on the simulated Sun.
+The star do one full rotation between phase -0.5 and 0.5, with the spot being seen face-on for phase 0.} SN mean RV seems to have the smallest spurious variations caused by the spot.}
    %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
@@
 \includegraphics[height = 6in]{SOAP_SPOT_Comparison_para_SN.pdf} 
-   \caption{Using CCFs from SOAP 2.0 with a single spot, the correlation between the estimated RVs and the asymmetry or width parameters are displayed.
-In this case the shape changes with phase, producing statistically significant correlations between the estimated RVs and the asymmetry parameters (but not for the estimated RVs and the width parameters).}
+   \caption{\xavier{\emph{Left:} Correlation between the different asymmetry parameters and the different RV estimates in the case of an equatorial 1\% spot on the simulated Sun.
+\emph{Right:} Correlation between the different width parameters and the different RV estimates for the same spot.
+In the presence of a spot, both the shape and the width of the CCF change as the star rotates.
+However, only the asymmetry produces a statistically significant correlation with the different RV estimates.
+In the case of the correlation between the width and the different RV estimates the data produces a circle, meaning that those two quantities are not varying in phase.}}
     \label{fig:spot.corr}
@@
 
-As before, the originally RVs were corrected by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction}. 
-In this setting, the proposed correction almost completely addresses the issue \jessi{what issue?} when considering the SN or Normal parameters, with values of $R^2$ larger than 0.99. 
-Considering Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms.
-\jessi{Doesn't the facula setting do better getting down to $\sim$0.13 \ms?}
-In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however, \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant.
+As before, the originally RVs were corrected by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction} and in Table \ref{table:spot.test}. 
+Like for the faculae, the proposed correction is able, in the case of the spot, to almost model entirely the stellar activity signal when considering the SN or Normal parameters, with $R^2$ values for the linear combination larger than 0.99.
+Looking at Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms, for any of the different RV estimates.
 When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.
 
-In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summarized in Table \ref{table:spot.test}, \umberto{we observe that the $\beta_0$, and $\beta_3$, corresponding respectively to the intercept and to the width of the CCF}, are \umberto{not helpful} to understand the variation measured in RVs.
+Looking at Table \ref{table:spot.test}, we see that the Normal or SN parameters appearing in Eq.~\ref{eq:RV:correction} are all statistically significant to explain the activity signal, except the width of the CCF when the RVs are derived with the mean or median of the SN density.
 This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
-We see also that the ampltitude parameter, with coefficient $\beta_1$ is only useful to explain the RV variation of the spot in the case of the Normal distribution.}
 
@@
 \includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{\umberto{Set of  spurious variations in RVs caused by a \textbf{spot} using a Normal and a SN fit before and once corrected from stellar activity.
+   \caption{\xavier{same comments as for Fig.
+4}\umberto{Set of  spurious variations in RVs caused by a \textbf{spot} using a Normal and a SN fit before and once corrected from stellar activity.
 The new correction has done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
@@
 \begin{center}
-\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction} to correct the estimated RVs from spurious variations caused by a spot. 
-All the covariates are statistically significant to explain the variability in RVs caused by a spot, except the intercept and the width of the CCF.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability in the estimated RVs.
-\jessi{Isn't the width of the CCF parameter sig for N mean RV at 0.017?
-Previously it was noted that a 5\% significance level was going to be used.}}
+\caption{\xavier{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun.
+All the variables corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by this spot, except for the width of the CCF when using SN mean RV or SN median RV as RV estimates.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability seen in the different RV estimates.}}
 \label{table:spot.test}
@@
 The last simulation presented consists in having a planetary signal influencing the CCF, in addition to the 1\% spot modeled before (see Sec.~\ref{sec:soap.spot}).
-\xavier{The purpose of this example is to check if we are able to disentangle as efficiently the two different sources of variations when using the parameters derived using a Normal, or a SN fit the the CCF.
-In this case, we inject a planet with an semi-amplitude of 10 \ms, with no eccentricity, and with a period corresponding to 1/3rd of the stellar rotational phase.}
+The purpose of this example is to check if we are able to disentangle as efficiently the two different sources of variations when using the parameters derived using a Normal, or a SN fit to the CCF.
+In this case, we inject a planet with a semi-amplitude of 10 \ms, with no eccentricity, and with a period corresponding to one third of the stellar rotational period.
 
 Fig.~\ref{fig:spot.plus.planet} shows the variation observed in the CCF barycenter parameters.
-Like in the case of the spot, all barycenter indicators show very similar variations, with SN mean RV showing a slightly smaller amplitude.
+Like in the case of the spot, all RV estimates show very similar variations, with SN mean RV showing a slightly smaller amplitude.
 
 In Fig.~\ref{fig:spot.plus.planet.corr}, we show the correlation between the different CCF parameters.
-\xavier{Except of seing smaller correlation than in the case of the spot, due to the fact that the planet induces changes in the CCF barycenter without any change in any of the width or asymmetry parameters, the correlation strengths between the asymmetry parameters and the CCF barycenter are in exactly the same order than in the case of the spot: $\gamma$--SN median RV $R=-0.84$, BIS SPAN-RV $R=-0.78$ and $\gamma$--SN mean RV $R=-0.76$.
-The variation seen in the width-CCF barycenter space draw a circle like in the case of a spot, therefore, no correlation is observed between those parameters.}
+Although observing weaker correlations than in the case of the spot, due to the fact that the planet induces changes in RV without inducing any change in width or asymmetry of the CCF, the correlation strengths between the CCF asymmetry and RV are in exactly the same order than in the case of the spot: $\gamma$--SN median RV, BIS SPAN--N mean RV and $\gamma$--SN mean RV, with $R$ values of $-0.84$, $-0.78$ and $-0.76$, respectively.
+The variation seen in the width-RV phase space draw a circle like in the case of a spot, therefore, no correlation is observed between those two parameters.
 
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
- \caption{RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
-N mean RV seems to have the largest variations caused by the combined action of spot and planet.}
+ \caption{\xavier{RV estimated either by the mean of a Normal density fit to the CCF (N mean RV) or by the mean (SN mean RV) or median (SN median RV) of a SN density fit to the CCF.
+In this case, the CCFs have been generated using SOAP 2.0, considering an equatorial 1\% spot on the simulated Sun in addition to a planet with a period of one third of the rotational period of the star and with an amplitude of 10\,\ms.
+The star do one full rotation between phase -0.5 and 0.5, with the spot being seen face-on for phase 0.}}
    %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
@@
 
-In order to correct the RVs from the spurious variation caused by the spot, \xavier{we need to add to our model of activity correction, a signal to take into account the RV variation caused by the injected planet.
-The observed RV can therefore be modeled by a combination of the activity and the planet signal:}
+In order to correct the RVs from the spurious variation caused by the spot, we need to add to our model of activity correction, a signal to take into account the RV variation caused by the injected planet.
+The observed RV can therefore be modeled as a combination of the activity and planetary signal:
 %
@@
 %
-\xavier{where $RV_{\text{activity}}$ can be found in Eq.~\ref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case of no eccentricity, can be modelled by the following sinusoidal function:}
+where $RV_{\text{activity}}$ can be found in Eq.~\ref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case of no eccentricity, can be modelled by the following sinusoidal function:
 %
@@
 We can see how in this case we are able to disentangle the spurious variations in RVs caused by stellar activity from the pure Doppler-shift due to the planet.
-The statistical tests conducted on the parameters, whose results are summarized in Table \ref{table:spotplanet.test}, \xavier{shows that except for the width parameters with coefficient $\beta_3$, all the other are significantly useful to explain the RV variation induce by a spot plus a planet.}
+The statistical tests conducted on the parameters, whose results are summarized in Table \ref{table:spotplanet.test}, shows that except for the width parameters with coefficient $\beta_3$, all the other Normal or SN parameters are significantly useful to explain the RV variation induce by a spot plus a planet.
+\xavier{When looking in the same Table at the RV rms of the residuals after correcting for stellar activity plus de planet, we see that all the RV estimates gives very similar results, with SN mean RV giving the smallest value.}
+
 %\begin{figure*}[htbp]
@@
 \begin{center}
-\caption{The p-values and coefficient of determination for the models fit using Eq.~\ref{eq:RV:correction.overall} to correct the estimated RVs from spurious variations caused by a spot while also accounting for a true planet RV.
-All the covariates are statistically significant to explain the variability in RVs caused by a spot, except the FWHM.
-Concerning the Keplerian parameters, the amplitude $K$ that provides relevance about the possibly presence of the exoplanet.
-Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.}
+\caption{\xavier{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun and a planet with period one third of the rotational period and semi-amplitude 10\,\ms.
+All the variables corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by this spot plus planet, except for the width of the CCF.
+Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.}}
 \label{table:spotplanet.test}
@@
 
-\subsection{Conclusions on the simulation study} \label{sec:soap.conclusions}
-
-In this Sec.\ref{sec:soap}, we presented a first implementation of the SN fit to the CCF, using SOAP 2.0 to simulate noiseless CCF affected by stellar activity variation.
-
-\umberto{Do we need to point out the following: \\ If we look at the $R^2$, the proposed function that corrects from stellar activity addresses (almost) all the spurious variations caused in RVs by active regions.
+%\subsection{Conclusions on the simulation study} \label{sec:soap.conclusions}
+%
+%In this Sec.\ref{sec:soap}, we presented a first implementation of the SN fit to the CCF, using SOAP 2.0 to simulate noiseless CCF affected by stellar activity variation. 
+%
+%\umberto{Do we need to point out the following: \\ If we look at the $R^2$, the proposed function that corrects from stellar activity addresses (almost) all the spurious variations caused in RVs by active regions.
 Anyway, if we look the residuals, a systematic component is still present, although smaller respect the residual obtained with the usual correction.
@@
 Therefore, since our $R^2$ is always close to $1$, we can argue, as we discussed already many times, that the CCF does not follow a normal fit, neither a SN one, otherwise, given our extremely high $R^2$ we should have gotten homoscedastic 0 mean residuals.}
-
-\xavier{is all this discussion really usefull ?
+%
+%\xavier{is all this discussion really usefull ?
 Before moving to real cases, where the analyses on five stars are presented, we need to provide further considerations.
@@
 
-In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN density defined in Sec.
-\ref{sec:3} with the approach based on fitting a Normal density to retrieve the RV and width of the CCF and calculating the bisector to derive the asymmetry parameter BIS SPAN.
+In this Section we present the analysis conducted on Alpha Centauri B, comparing the result of fitting a CCF using the SN density defined in Sec.
+\ref{sec:3} with the usual approach based on fitting a Normal density to retrieve the RV and width of the CCF and calculating the bisector to derive the asymmetry parameter BIS SPAN.
 Four other stars have been analyzed with the proposed method and details can be found in the Appendix \ref{appendix}.
-For all the stars that have been considered in the present work, \xavier{we selected CCFs  that were derived from spectra that had a SNR at 550 nm larger than 10.}
+For all the stars that we considered in the present work, \xavier{we selected only the CCFs that were derived from spectra that had at least a SNR at 550 nm of 10.}
 
@@
 
-We analysed the $1808$ CCFs derived from spectra of Alpha Centauri B taken in 2010 by the HARPS spectrograph.
+We analyzed $1808$ CCFs derived from spectra of Alpha Centauri B taken in 2010 by the HARPS spectrograph.
 Note that more observations have been done during this year, however we selected here only the data that are not significantly affected by contamination from Alpha Cen A \citep[see][]{Dumusque-2012}.
-\xavier{We choose these observations as their represent probably the best sampled and most precise RV data set showing a strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.}
-
-We begin the analyses by evaluating the correlation between $\gamma$ and the BIS SPAN. 
-In the left panel of Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.72$ and a strong Pearson correlation coefficient of $R=0.95$.
+\xavier{We choose these observations as they represent probably the best sampled and most precise RV data set showing a strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.}
+
+We begin the analysis by evaluating the correlation between $\gamma$ and BIS SPAN. 
+In the left panel of Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $720$ and a strong Pearson correlation coefficient of $R=0.95$.
 This strong correlation shows that $\gamma$ and BIS SPAN are measuring in a very similar way the CCF asymmetry.
-\xavier{This strong correlation allows as well to convert the dimensionless $\gamma$ parameters in \ms to compare it with BIS SPAN using the slope of the correlation, in this case 720 \ms.}
+This strong correlation allows as well to convert the dimensionless $\gamma$ parameters into \ms\,using the slope of the correlation, in this case 720 \ms.
 %\xavier{As $\gamma$ has no units, this will allow us to compare the amplitude of the activity signal seen in $\gamma$ and in BIS SPAN, by using the slope of this correlation as a scaling factor}.
@@
 As we can see with the strong correlation, those two parameters measure the CCF asymmetry in the same way.
-\emph{Top right:} RVs as function of Julian Day for Alpha Centauri b in 2010.
+\emph{Top right:} RVs as function of Julian Day for Alpha Centauri B in 2010.
 The RVs are retrieved using the mean of a Normal fitted to the CCF (red triangles), or the mean (black circles) or median (cyan crosses) of a SN density fitted to the CCF.
-\emph{Bottom right:} RV differences between the RV derived when using the SN density and the RV derived when using the Normal density.}
+\emph{Bottom right:} RV differences between the RVs derived when using the SN density and the RV derived when using the Normal density.}
    \label{fig:alphacent:corr.gamma}
@@
 In the right of Fig.~\ref{fig:alphacent:corr.gamma}, we show the comparison between the RVs retrieved using the SN density and the ones obtained with the Normal density.
-\xavier{We clearly see that the amplitude of the activity signal is stronger when using SN mean RV, and the signal measured using N mean RV or SN median RV are very similar.
-We observe the same behavior in the case of a faculae (see Sec.~\ref{sec:soap.faculae}) and therefore it seems that the activity signal seen in those data are more likely affected by faculae.
-This is an observation that was already made in \citet{Dumusque-2014c}.}
+We clearly see that the amplitude of the activity signal is stronger when using SN mean RV, and the signal measured using N mean RV or SN median RV are very similar.
+We observe the same behavior in the case of a faculae (see Sec.~\ref{sec:soap.faculae}) and therefore, it seems that the activity signal seen in those data os most likely induced by faculae.
+This is an observation that was already made in \citet{Dumusque-2014c}.
 %When using SN mean RV, it is possible to observe more variations than the ones measured by the Normal fitting.
@@
 %\includegraphics[height = 3in]{HD12862_[2]RadialVelocityDifferences.pdf} 
-%   \caption{(top) RVs as function of Julian Day for Alpha Centauri b.
+%   \caption{(top) RVs as function of Julian Day for Alpha Centauri B.
 The RVs are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses).
@@
 
-\xavier{Similar to what is done in Sec.~\ref{sec:soap}, we compare the correlation between the asymmetry or the width parameters of the CCF and the RV, i.e.
-the CCF barycenter, in Fig.~\ref{fig:alphacent:corrPlot}.
+Similar to what is done in Sec.~\ref{sec:soap}, we compare the correlation between the asymmetry or the width parameters of the CCF and the RV in Fig.~\ref{fig:alphacent:corrPlot}.
 In addition to what is done in Sec.~\ref{sec:soap}, we add the asymmetry parameters derived in \citet{Boisse-2011}, $V_{span}$ and in \citet{Figueira-2013}, BIS-, BIS+, Bi Gauss and $V_{asy}$, as these authors found those asymmetry parameters more correlated to the RVs than BIS SPAN.
 It is clear in the case of Alpha Cen B, but also in the four other stars presented in Appendix \ref{appendix}, that the correlation found between $\gamma$ and SN mean RV is always the strongest.
-On alpha Cen B, the Pearson correlation coefficient reaches a value of $R=0.74$, while it reaches at best $R=-0.42$ for all the other asymmetry-RV correlations not derived using the SN density fit.
-When looking at the width-RV correlation, once again, the correlation between SN FWHM and SN mean RV is the strongest for all the stars, except for the quietest star of all five, HD10700, for which the Pearson correlation coefficient 0.53 for the Normal parameters and 0.42 for the SN parameters.
-This analysis shows that the parameters derived when using a SN density are more sensitive the stellar activity, and therefore using those parameters can lead to the detection of stellar activity, when the Normal parameters do not detect anything (see the Appendix \ref{appendix} the case of the the asymmetry-RV correlation for HD10700, HD215152, Corot-7, and the width-RV correlation for HD215152)}
+On alpha Cen B, the Pearson correlation coefficient reaches a value of $R=0.74$, while it reaches at best $R=-0.42$ for all the other asymmetry--RV correlations not derived using the SN density fit.
+When looking at the width-RV correlation, once again, the correlation between SN FWHM and SN mean RV is the strongest for all the stars, except for the quietest star of all five, HD10700, for which the Pearson correlation coefficient is 0.53 for the Normal parameters and 0.42 for the SN parameters.
+This analysis shows that the parameters derived when using a SN density are more sensitive the stellar activity, and therefore using those parameters can lead to the detection of stellar activity, when the Normal parameters do not detect anything.
+This is the case for the asymmetry-RV correlation of HD10700, HD215152, Corot-7, and the width-RV correlation for HD215152 (see Appendix \ref{appendix}).
 
@@
 Recalling the analyses presented in Sec.
-\ref{sec:soap}, we could infer that Alpha Centauri b is dominated by faculae, because the correlations between the RVs and the width of the CCF are strong (in particular the correlation between SN mean RV and SN FWHM is $0.817$).
+\ref{sec:soap}, we could infer that Alpha Centauri B is dominated by faculae, because the correlations between the RVs and the width of the CCF are strong (in particular the correlation between SN mean RV and SN FWHM is $0.817$).
 %%
@@
 
-\xavier{In Fig \ref{fig:alphacent:correctionRV}, we study the efficiency of the stellar activity correction proposed in Sec.~\ref{sec:31}.
-The first observation is that the RV measured with SN mean RV presents a rms 35\% larger than the RV measured when fitting a Normal density.
-In the case of SN median RV, we see as well a larger RV rms, however this one is only 9\% larger.
+In Fig \ref{fig:alphacent:correctionRV}, we study the efficiency of the stellar activity correction proposed in Sec.~\ref{sec:31}.
+The first observation we can make is that the RV measured with SN mean RV presents a rms 35\% larger than the RV measured when fitting a Normal density.
+In the case of SN median RV, we see as well a larger RV rms, however only 9\% larger.
 Even though we see those differences in RV, once we correct for the stellar activity using Eq.~\ref{eq:RV:correction}, we find the same RV residuals rms.
-In the best case, for SN mean RV, we reduce the stellar activity signal by a factor of 2, while in the worst case, N mean RV, only a factor 1.5.
-Therefore, although it seems that the parameters derived using the SN density are more sensitive to stellar activity, we are not able to correct better for stellar activity signal using a linear combination of the different CCF parameters.}
-
-\xavier{When looking at the significance of the different parameters in the activity correction in Table~\ref{table:alphacent.test}, we see that the intercept is not significant for any of the correction, and BIS SPAN, with coefficient $\beta_2$, is not useful to explain stellar activity when using the parameters derived from the Normal density fit.
-However all the other parameters in the Normal and SN case are useful.
-By analyzing the value for $R^2$, we see that the correction is more efficient at explaining stellar activity when considering for the CCF barycenter SN mean RV.
-This is expected from the results above since for the three different cases, we arrive to the same RV residual rms after correction, but before correction SN mean RV shows the largest RV rms.}
+%In the best case, for SN mean RV, we reduce the stellar activity signal by a factor of 2, while in the worst case, N mean RV, only by a factor 1.5. 
+Therefore, although it seems that the parameters derived using the SN density are more sensitive to stellar activity, we are not able to correct better for stellar activity signal using a linear combination of the different CCF parameters.
+
+When looking at the significance of the different parameters in the activity correction in Table~\ref{table:alphacent.test}, we see that the intercept is not significant for any of the correction, and BIS SPAN, with coefficient $\beta_2$, is not useful to explain stellar activity when using the parameters derived from the Normal density fit.
+However all the other parameters in the Normal and SN cases are useful to model stellar activity.
+By analyzing the values of $R^2$, we see that the correction is more efficient at explaining stellar activity when considering SN mean RV as the RV estimate.
+This is expected from the results above since for the three different RV estimates, we arrive to the same RV residual rms after correction for activity, but before correction, SN mean RV shows the largest RV rms.
 
@@
 \begin{center}
-\caption{Evaluation of the linear combination used for correcting the RVs, according to Eq.~\ref{eq:RV:correction}.
-Concerning the Normal fit, all the parameters but the intercept and the BIS SPAN are useful in explaining variations in RVs of the star that can be caused by stellar activity.
-For the SN fit we note that the parameter related to $\gamma$ is highly significant to address part of the spurious variations in RVs caused by stellar activity.
-The evaluation of the $R^2$ shows that the proposed linear combination better explains variations in RVs due to stellar activity coming from the SN analysis that uses SN mean RV.}
+\caption{\xavier{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity in Alpha Cen B data.
+All the variables corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by stellar activity, except for the asymmetry of the CCF when using the Normal parameters (BIS SPAN).}
+The evaluation of the $R^2$ shows that the proposed linear combination better explains variations in RVs due to the stellar activity, when the RVs are derived using SN mean RV.}
 \label{table:alphacent.test}
@@
 
-\xavier{In the preceding section, we saw that the RV measured when considering a SN or a Normal density present different amplitudes, mainly in the case of SN mean RV.
+In the preceding section, we saw that the RV measured when considering a SN or a Normal density present different amplitudes, mainly in the case of SN mean RV.
 However, when correcting for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, it seems that we are able to reach the same RV precision.
 In this section, we want to investigate if for some of the three different RV definitions presented in this paper, it is easier or more difficult to detect planetary signals when considering stellar activity.
-To do so, we estimated what would be the minimum amplitude of a planetray signal we could detect at different orbital periods.
-
-To get CCF affected by realistic stellar activity signals, we took the ones from Alpha Cen B used in the preceding section.
-To simulate a planetary signal, when then blue- or red-shifted those CCF with the wanted amplitude, period and phase.
-
+To do so, we estimated what would be the minimum amplitude of a planetray signal we could detect at different orbital periods when considering data affected by stellar activity.
+
+To get CCFs affected by realistic stellar activity signals, we took the ones from Alpha Cen B used in the preceding section.
+To simulate a planetary signal, we then blue- or red-shifted those CCFs with the wanted amplitude, period and phase.
 We first simulated several RV data sets, with always the same stellar signal, but injecting planets with parameters corresponding to the following grid:
@@
 
-For each simulation, 4500 in total, we applied the activity correction presented in Eq.~\ref{eq:RV:correction} and look for signals in the residuals using a Generalized Lomb-Scargle periodogram \citep[GLS][]{Zechmeister-2009}.
+For each simulation, 4500 in total, we applied the activity correction presented in Eq.~\ref{eq:RV:correction} and look for signals in the residuals using a Generalized Lomb-Scargle periodogram \citep[][]{Zechmeister-2009,Scargle-1982,Lomb-1976a}.
 If a signal with a p--value\footnote{estimated by bootstrap} smaller than 1\% had a period compatible with the injected planetary period considering an error of 20\%, we were estimating this signal as significant, and therefore the corresponding planet as detected.
-
 Finally, for each period, we searched for the minimum amplitude for which at least 50\% of the planets with different phases were detected.
@@
 Although the detection limits stay constant for all the periods below 15 days, we see that for 20 and 30 days, we have a huge increase in detection limits for all the RV estimates. 
-This is because period of the simulated planet, 20 days and 30 days, are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012}
+This is because the periods of the simulated planets, 20 days and 30 days, are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012}
 and therefore close to the semi-periodicity of the stellar activity signal. In such a case, the activity 
-correction absorbs part of the planetary signal. We thus need to inject a much stronger planetary signal at these periods to detect them.}
+correction absorbs part of the planetary signal. We thus need to inject a much stronger planetary signal at these periods to detect them.
 
@@
 Table \ref{table:summaryStars} summarizes the results obtained by the SN fit and the some of the results based on the Normal fit.
-The results are all consistent with the conclusions derived by the analyses on Alpha Centauri b.
+The results are all consistent with the conclusions derived by the analyses on Alpha Centauri B.
 The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and RV for all the considered stars.

### 2018-06-03 manuscript.tex
Resolved conflits

@@
    %
- (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (new correction) and the usual correction \jessi{it might be helpful to actually have an equation for the usual/old model}.
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
+std) and the residuals from the usual correction (Usual corr.
+std), obtained fitting the function $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$.
 The residuals have a smaller systematic component when using the proposed model of
-  Eq.~\ref{eq:RV:correction} (blue circles) compared to the usual model (blue triangles).
-The estimated parameters are presented in Table \ref{table:faculae.test} \jessi{This table only has p-values and $R^2$}. }
+  Eq.~\ref{eq:RV:correction} (black circles) compared to the usual model (blue triangles).
+The tests of statistical significance on the parameters are presented in Table \ref{table:faculae.test}.}
     \label{fig:faculae.correction}

### 2018-06-03 manuscript.tex
Finished reviewing paper

@@
 % Context, Aims, Methods, Results, Conclu (not mandatory)
-{Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
+{\xavier{@Umberto, Update the abstract please.} Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
 Stellar activity can be probed by measuring time dependent variations in the shape of the cross-correlation function (CCF), often estimated using the different moments of the modeled CCF.
@@
 \includegraphics[height = 3.6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
-   \caption{\emph{Left: }Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
+   \caption{\xavier{Slope should be 720, Legend for subplot bottom right should be N mean RV and bot N mean RV RV}.
+\emph{Left: }Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
 As we can see with the strong correlation, those two parameters measure the CCF asymmetry in the same way.
@@
 
-\xavier{In this section, we investigate how the noise of the CCF influence the CCF parameters derived either by a Normal density or a SN density fit.
+In this section, we investigate how the noise of the CCF influences the CCF parameters derived either by a Normal density or a SN density fit.
 Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
@@
 We therefore started from the spectrum, for which we know that each point is totally independent of the others.
-The standard error on each point of the spectrum is given by the photon noise, which follows a Poisson law and is therefore obtained by taking the square root of the measured flux.}
-
-\xavier{We applied the following method to estimate the error bars on the different parameters derived from the CCF.
+The standard error on each point of the spectrum is given by the photon noise, which follows a Poisson law and is therefore obtained by taking the square root of the measured flux.
+
+We applied the following method to estimate the error bars on the different parameters derived from the CCF.
 We first modify the values of all the points in the spectrum given their respective error bars.
@@
 We redo this process a hundred times, which gives us at the end, a distribution for each CFF parameter.
-The standard deviations of the obtained distributions is then associated to the noise of each CCF parameters.}
-
-\xavier{We measured the standard deviation of each CCF parameters for all the CCF of HD215152, HD192310 and Corot-7.
+The standard deviations of the obtained distributions is then associated to the standard errors of each CCF parameters.
+
+We measured the standard errors of each CCF parameters for all the CCFs of HD215152, HD192310 and Corot-7.
 This gives us an information of how the noise on each CCF parameter varies as a function of SNR.
@@
 In the bottom plots, we show the ratio between the standard errors measured when using the SN parameters and the Normal parameters.
-Values smaller or larger than one will imply that standard errors fro the SN parameters are more or less precise, respectively.}
-
-\xavier{Looking at the estimates for the RV, we see that they all follow a similar exponential decay.
+Values smaller or larger than one will imply that standard errors from the SN parameters are more or less precise, respectively.
+
+Looking at the estimates for the RV, we see that they all follow a similar exponential decay.
 Although we plot the data for three different stars, we do not see any offsets in this decay, which implies that the SNR at 550 nm is the main contributor to the precision measured in RV.
-This is not surprising as the 3 stars studies are all main sequence K-dwarfs.
+This is not surprising as the three stars studied here are all main sequence K-dwarfs.
+
 When comparing the three different estimates for the RV, we see that SN mean RV presents standard errors that are 60\% larger than what N mean RV gives.
@@
 In conclusion, when fitting a SN density to the CCF and using as RV estimates SN mean RV, we are able to improve by 10\% the precision on the RV, 15\% the precision on the asymmetry, and this without degrading the precision on the width estimate.
-SN mean RV should not be use to derive RVs, except perhaps for stars for which the photon noise is not the dominant source of noise, as the precision on this parameter if 60\% worse than the precision on the RV derived from a Normal density fit.}
+SN mean RV should not be use to derive precise RVs, except perhaps in specific conditions described below, as the precision on this parameter is 60\% worse than the precision on the RVs derived when using the mean of a Normal density fit to the CCF.
 %
@@
 \includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
-   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter.
-When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
+   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameters.
+When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved when fitting a Normal density (red triangles).
 However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
-To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
-Note that for the asymmetry, the error in BIS SPAN is in \kms.
+The use of the asymmetry SN parameter $\gamma$ leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
+Note that for the asymmetry, the error in BIS SPAN is in \ms.
 To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
@@
 
-\xavier{When fitting a SN density to the CCF, it is possible at once to retrieve parameters that describe the RV, i.e.
-the CCF barycenter, the amplitude, also called the contrast, the width, and the asymmetry of the CCF.
-For the RV, we investigated the use of the mean and the median of the SN density.
-Then the width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry, by using $\gamma$, the skewness parameter of the SN density.
-
-When we tested the SN density fit to the CCF provided by the SOAP 2.0 code, that simulate the activity signal induced by a spot or a faculae on a solar-like star, we arrived to the conclusion that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual method.
+When fitting a SN density to the CCF, it is possible at once to retrieve parameters that describe the RV, i.e.
+the CCF barycenter, the amplitude, sometimes called the CCF contrast, the width, and the asymmetry of the CCF.
+To estimate the RV, we investigated the use of the mean and the median of the SN density.
+Then the width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry by using $\gamma$, the skewness parameter of the SN density.
+
+When we tested the SN density fit to the CCFs provided by the SOAP 2.0 code, that simulate the activity signal induced by a spot or a faculae on a solar-like star, we arrived to the conclusion that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual method.
 By more sensitive, we mean here that the correlation between the skewness and either the mean or median of the SN density is stronger than between BIS SPAN and the mean of a Normal density.
@@
 Generally, when fitting for planetary signals, people use a model composed of one or several Keplerians to account for the planets, in addition to a linear combination with the FWHM and BIS SPAN of the CCF to account for stellar activity signals.
-The new function propose to add a linear dependency with the amplitude of the CCF retrieved either by the SN or Normal density fit, and a interaction term between the asymmetry and the width parameters.
-On the simulated data from SOAP 2.0, this new model allows to mitigate stellar activity signals by a factor of 2 and 3.5 compared to the model generally used, for the faculae and spot, respectively.
-
-When moving to real data, we arrived to the same conclusions regarding the strength of the correlation between the asymmetry and the CCF barycenter, as well as between the width and the CCF barycenter.
-We note however that although in the case of the simulated data, the stronger asymmetry-RV correlation was found between $\gamma$ and the median of the SN, in the case of real data, it was between $\gamma$ and the mean of the SN.
+The new function proposes to add a linear dependency with the amplitude of the CCF retrieved either by the SN or Normal density fit, and an interaction term between the asymmetry and the width parameters.
+On the simulated data from SOAP 2.0, this new model allows to mitigate stellar activity signals by a factor of 2 and 3.5 better compared to the model generally used, for the faculae and spot, respectively.
+
+When moving to real data, we arrived to the same conclusions than the results of the SOAP 2.0 simulations regarding the strength of the correlation between the CCF asymmetry and the RV, as well as between the CCF width and the RV.
+We note however that although in the case of the simulated data, the stronger asymmetry-RV correlation was found between $\gamma$ and the median of the SN, in the case of real data, it was found between $\gamma$ and the mean of the SN.
 This can be due to the fact that in SOAP 2.0, the faculae is not modelled properly, as it uses as emerging spectrum the one from a spot.
 We know that the temperature between a spot and a faculae is significantly different, therefore their spectra should be different.
-In addition, there is always several active regions on a star, at different locations in longitude and latitude.
+In addition, there is always several active regions on a star, at different locations in longitude and latitude, which is not the case in our SOAP 2.0 simulations were only one active region was modelled at a time.
 This could also be responsible for the fact that we do not observe the same behavior for the mean and the median of the SN when we compare the SOAP 2.0 simulation and real data.
-Nevertheless, in both the simulated case and the real cases, the parameters derived from the SN are more sensitive to activity than the parameters derived from a Normal fit.
+Nevertheless, in both the simulated and the real cases, the parameters derived from the SN are more sensitive to activity than the parameters derived from a Normal fit.
 In addition, the correlation between the asymmetry and the mean of the SN is always stronger than any other parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
@@
 Having an estimate of the RV that is more sensitive to stellar activity, like the mean of the SN, can help us to probe better stellar rotational periods, or understand better the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}.
-We saw in the preceding section that the RV estimated by the mean of the SN is 60\% noisier than the RV derived by the mean of the Normal.
+We saw in the preceding section that the RV estimated derived by the mean of the SN is 60\% noisier than the RV derived by the mean of the Normal.
 This is not necessarily a negative aspect.
-Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized by increasing its induced RV amplitude even if the white noise is 60\% larger.
-
-Even if the different RV estimates have different amplitudes, once we apply our new correction for stellar activity, we arrive exactly to the same RV rms in the residuals, meaning that for activity correction, the SN parameters does not help.
+Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring SN mean RV, even if the white noise in the data is increased by 60\%.
+
+Even if the different RV estimates have different amplitudes, once we apply our new correction for stellar activity, we arrive exactly to the same RV rms in the residuals, meaning that for an activity correction based on a linear combination of CCF parameters, the SN density fit does not help.
 We note that when comparing the activity correction presented in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, we only see a slight improvement brought by our proposed correction.
@@
 We checked if some RV estimates were better at finding planets in RV data affected by observed stellar signals.
-When using the new correction proposed in this paper to mitigate the effect from stellar activity, and when assesing planetary detection based on periodogram analysis, we find very similar detection limits for the three RV estimates presented in this paper.
+When using the new correction proposed in this paper to mitigate the effect from stellar activity, and when assesing planetary detection based on aperiodogram analysis, we find very similar detection limits for the three RV estimates presented in this paper.
 Therefore it seems that any of the RV estimate can be used to search for planetary signals.
@@
 Regarding the asymmetry estimates, we observe that $\gamma$ has a precision15\% better than the BIS SPAN.
-It is therefore clear in this case that the SN parameters are more precise to measure the barycenter and the asymmetry of the CCF.}
+It is therefore clear in this case that the SN parameters are more precise to measure the RV and the asymmetry of the CCF.
 
@@
 
-\xavier{When searching for small-mass exoplanets using the RV technique, it is crucial to get the best precision possible on the determination of the RV, but also to measure precisely the shape variations of the CCF, as such variations are induced by stellar activity, and not by planets.
-The correlations between the width of the CCF and the RV, and the asymmetry of the CCF and the RV are used as a way to assess if the measurements are affect by stellar activity signals, therefore, the stronger the correlation, the better we can probe small level of stellar activity.
-
-In this paper we introduced a novel approach based on the Skew Normal (SN) density to retrieve the RV and shape variation of the CCF.
+When searching for small-mass exoplanets using the RV technique, it is crucial to get the best precision possible on the determination of the RV, but also to measure precisely the shape variations of the CCF, as such variations are induced by stellar activity, and not by planets.
+The correlations between the width of the CCF and the RV, and the asymmetry of the CCF and the RV are used as a way to assess if the measurements are affect by stellar activity signals, therefore, the stronger those correlations are, the better we can probe low level of stellar activity.
+
+In this paper, we introduced a novel approach based on the Skew Normal (SN) density to retrieve the RV and shape variation of the CCF.
 This new method is compared to the usual one, where a Normal density is fitted to the CCF to retrieve the information on the RV and the width of the CCF, and a bisector analysis allows to retrieve the asymmetry of the CCF using the BIS SPAN.
@@
 we strongly encourage the community of using this new parametrization of the CCF.
-Correlations between the asymmetry and the mean of the SN, and between the width and the mean of the SN should be used to probe better stellar signals in RV data, and the median of the SN should be used as the new definition for RV.
-}
+Correlations between the asymmetry and the mean of the SN, and between the width and the mean of the SN should be used to probe better stellar activity signals in RV data, and the median of the SN should be used as the new definition for RV.
 
@@
 
-In this Appendix we present the analyses conducted on other 4 stars: HD192310, HD10700, HD215152 and finally Corot-7.
-
-\umberto{Add further information about the stars here presented.}\xavier{}
-
-Table \ref{table:summaryStars} summarizes the results obtained by the SN fit and the some of the results based on the Normal fit.
+In this Appendix we present the same analysis as presented in Sec.~\ref{sec:4} for those four main-sequence stars: HD192310 (K2V), HD10700 (G8V), HD215152 (K3V) and finally Corot-7 (K0V).
+
+Table \ref{table:summaryStars} summarizes the results obtained by the SN fit and some of the results based on the Normal fit.
 The results are all consistent with the conclusions derived by the analyses on Alpha Centauri B.
-The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and RV for all the considered stars.
+The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and RV or between the asymmetry parameters derived in \citet{Boisse-2009} and \citet{Figueira-2013} and RV for all the considered stars.
 The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV for three of the four stars.
@@
 \ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RVs.
-While the Normal and SN residuals, once corrected for stellar activity, are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$, the results of the analyses on the star $\text{HD}215152$ (whose CCF's have lower SNR respect to the previous two analyzed stars) suggest that the residuals for the Normal are $0.054 \ms$ higher than the residuals retrieved with the SN analysis.
-Finally, the results of the analysis on $\text{Corot }7$, whose CCF's have lowest SNR, show that once corrected from stellar activity the residuals from the Normal fit are $0.336 \ms$ higher than the residuals retrieved with the SN analysis.
+While the Normal and SN residuals, once corrected for stellar activity, are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$, the results of the analyses on $\text{HD}215152$ and Corot-7, whose measurements have lower SNR with respect to the previous two analyzed stars, suggest that the residuals for the Normal are 0.05 and 0.34\,\ms\,higher than the residuals retrieved with the SN analysis, respectively.
 
@@
 \begin{table*}[!t]
-\caption{Subset of notable correlations between the asymmetry parameter (and the FWHM) and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.
+\caption{Subset of notable correlations between the asymmetry or the FWHM parameters and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.
 The complete results of the analyses of the correlations for the four stars are presented in Fig.
@@
 \hline
- $\text{HD}192310  $          &    $1577$    & $0.888$ & $0.786$ & $0.669 (0.64; 0.695)$\\
-\hline
- $\text{HD}10700 $            &    $7928$    & $0.78$ & $0.604$ & $0.322 (0.302; 0.342)$\\
-\hline
- $\text{HD}215152 $          &     $273$   &  $ 0.763$ & $0.794$ & $0.571 (0.485; 0.646)$ \\
-\hline
- $\text{Corot }7$     &     $173$    &  $0.814$  & $0.607$ & $0.561 (0.450; 0.656)$  \\
+ $\text{HD}192310  $          &    $1577$    & $0.888$ & $786$ & $0.669 (0.64; 0.695)$\\
+\hline
+ $\text{HD}10700 $            &    $7928$    & $0.78$ & $604$ & $0.322 (0.302; 0.342)$\\
+\hline
+ $\text{HD}215152 $          &     $273$   &  $ 0.763$ & $794$ & $0.571 (0.485; 0.646)$ \\
+\hline
+ $\text{Corot }7$     &     $173$    &  $0.814$  & $607$ & $0.561 (0.450; 0.656)$  \\
 \hline
 \rule{0pt}{2ex}    & & & &\\
-\textbf{Star}          &\textbf{$\text{R}(\text{Bis-Span}, \text{RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{SN mean RV})$}  & \textbf{$\text{R}(\text{FWHM}, \text{RV})$} \\
+\textbf{Star}          &\textbf{$\text{R}(\text{Bis-Span}, \text{N mean RV})$} & \textbf{$\text{R}(\text{FIG BiGaussian}, \text{N mean RV})$} & \textbf{$\text{R}(\text{SN FWHM}, \text{SN mean RV})$}  & \textbf{$\text{R}(\text{FWHM}, \text{N mean RV})$} \\
 \hline
@@
 \includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RVs for $\text{HD}192310$.
+   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
+Correlation between the asymmetry parameters and the RVs for $\text{HD}192310$.
 The last three plots show the correlation between the FWHM and the RVs for $\text{HD}192310$ using respectively the SN and the Normal fits.
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONHD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RVs for $\text{HD}192310$  using a Normal and a SN fit before and once corrected from stellar activity.
+   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
+Set of RVs for $\text{HD}192310$  using a Normal and a SN fit before and once corrected from stellar activity.
 The correction is done using Eq.
@@
 \includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RVs for $\text{HD}10700$.
+   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
+Correlation between the asymmetry parameters and the RVs for $\text{HD}10700$.
 The last three plots show the correlation between the FWHM and the RVs for $\text{HD}10700$ using respectively the SN and the Normal fits.
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONHD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RVs for $\text{HD}10700$  using a Normal and a SN fit before and once corrected from stellar activity.
+   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
+Set of RVs for $\text{HD}10700$  using a Normal and a SN fit before and once corrected from stellar activity.
 The correction is done using Eq.
@@
 \includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RVs for $\text{HD}215152$.
+   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
+Correlation between the asymmetry parameters and the RVs for $\text{HD}215152$.
 The last three plots show the correlation between the FWHM and the RVs for $\text{HD}215152$ using respectively the SN and the Normal fits.
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONHD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RVs for $\text{HD}215152$ using a Normal and a SN fit before and once corrected from stellar activity.
+   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
+Set of RVs for $\text{HD}215152$ using a Normal and a SN fit before and once corrected from stellar activity.
 The correction is done using Eq.
@@
 \includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
-   \caption{Correlation between the asymmetry parameters and the RVs for  $\text{Corot }7$.
+   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
+Correlation between the asymmetry parameters and the RVs for  $\text{Corot }7$.
 The last three plots show the correlation between the FWHM and the RVs for  $\text{Corot }7$ using respectively the SN and the Normal fits.
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONLRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RVs for  $\text{Corot }7$ using a Normal and a SN fit before and once corrected from stellar activity.
+   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
+Set of RVs for  $\text{Corot }7$ using a Normal and a SN fit before and once corrected from stellar activity.
 The correction is done using Eq.

### 2018-06-03 manuscript.tex
Add files via upload
comments edited, plots updated

@@
 
-\author{U. Simola \inst{1,2}
+\author{U. Simola \inst{1}
 	    \thanks{\email{umberto.simola@helsinki.fi}}
@@
 % Context, Aims, Methods, Results, Conclu (not mandatory)
-{\xavier{@Umberto, Update the abstract please.} Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
-Stellar activity can be probed by measuring time dependent variations in the shape of the cross-correlation function (CCF), often estimated using the different moments of the modeled CCF.
-Therefore estimating the moments of the CCF with high precision is essential to de-correlate exoplanet signals from spurious RV signals originating from stellar activity.}
-%
-{We propose to estimate the moments of the CCF by fitting a model using a Skew Normal (SN) density shape, which unlike the commonly employed Normal density, includes an skewness parameter to capture the asymmetry of the CCF induced by stellar activity, but also the natural asymmetry induced by convective blueshift.}
-%
-{The performance of the proposed method is compared to the Normal density using both simulated and real observations with varying levels of activity and signal-to-noise ratio (SNR) levels.}
+{Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
+Stellar activity can be probed by measuring time dependent variations in the shape of the cross-correlation function (CCF), often estimated using different parameters of the modeled CCF.
+Therefore estimating the moments of the CCF with high precision is essential to de-correlate the signal of an exoplanet from spurious RV signals originating from stellar activity.}
+%
+{We propose to estimate the parameters of the CCF by fitting a Skew Normal (SN) density shape which.
+Unlike the commonly employed Normal density, the SN density includes a skewness parameter to capture the asymmetry of the CCF induced by stellar activity and also the natural asymmetry induced by convective blueshift.
+Moreover, the SN distribution allows for different location parameters beyond the mean, such as the median of the CCF.}
+%
+{The performances of the proposed method are compared to the commonly employed Normal density, using both simulations and real observations, with different levels of activity and signal-to-noise ratio (SNR) levels.}
 %We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (SNR) levels.
@@
 %
-{When considering the real observations, the correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are stronger when using the parameters derived from the SN than the Normal approach.
-This suggests that the CCF asymmetry and the CCF width derived using a SN may be more sensitive to stellar activity, which can be helpful with estimating stellar rotational periods and generally characterizing the stellar activity signals.
-The estimated uncertainties in the estimated RVs using the proposed SN approach are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal, and the estimated uncertainties on the SN asymmetry parameter are on average $15\%$ smaller than the commonly used Bisector Inverse Slope Span (BIS SPAN) approach for estimating the asymmetry of the CCF.
+{When considering real observations, the correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are stronger when using the parameters estimated with the SN rather than the ones obtained with the commonly employed Normal density.
+In particular the strongest correlations have been obtained when using as location parameter the  mean of the SN.
+This suggests that the asymmetry of the CCF and the width of the CCF estimated using a SN may be more sensitive to stellar activity, which can be helpful when estimating stellar rotational periods and generally for characterizing stellar activity signals.
+The estimated uncertainties in the measured RVs using the proposed SN approach and as location parameter the median of the SN are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
+The estimated uncertainties on the asymmetry parameter of the SN are on average $15\%$ smaller than the uncertainties measured on the Bisector Inverse Slope Span (BIS SPAN), which is the commonly parameter used to evaluate the asymmetry of the CCF.
 }
-{XXX \jessi{It looks like we still need to add conclusions here}}
+{We strongly encourage the use of the SN distribution to retrieve the different parameters of the CCF.
+The correlation between the mean of the SN and the asymmetry parameter of the CCF and the correlation between the mean of the SN and the width parameter of the CCF probe better stellar activity signals than when using the parameters retrieved with the Normal distribution.
+Using the SN distribution leads to smaller uncertainties for both the median of the SN and the asymmetry of the CCF than using the commonly employed Normal density.
+Finally, all the parameters are available in one single fit to the CCF.
+}
 %
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
-\caption{\xavier{RV estimated either by the mean of a Normal density fit to the CCF (N mean RV) or by the mean (SN mean RV) or median (SN median RV) of a SN density fit to the CCF.
+\caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line) or SN median RV (cyan dots-dashed line).
 In this case, the CCFs have been generated using SOAP 2.0, considering an equatorial 3\% faculae on the simulated Sun.
-The star do one full rotation between phase -0.5 and 0.5, with the faculae being seen face-on for phase 0.
-The variation seen in SN mean RV is quite different from the variations seen in SN median RV and N mean RV.}  \jessi{The cyan line is hard to see in the legend, and may be impossible in a black-and-white version - could the legend background be white?}
+The star does one full rotation between phase -0.5 and 0.5, with the facula being seen face-on for phase $0$.
+The variations observed in SN mean RV are quite different from the variations measured in SN median RV and N mean RV.
+\jessi{The cyan line is hard to see in the legend, and may be impossible in a black-and-white version - could the legend background be white?}
 }
@@
 \includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
-   \caption{\xavier{\emph{Left:} Correlation between the different asymmetry parameters and the different RV estimates in the case of an equatorial 3\% faculae on the simulated Sun.
-\emph{Right:} Correlation between the different width parameters and the different RV estimates for the same faculae.
-   In the presence of a faculae, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations.}}
+   \caption{\emph{Left:} Correlations between the different asymmetry parameters and their corresponding RVs estimates in the case of an equatorial 3\% faculae on the simulated Sun.
+\emph{Right:} Correlations between the different width parameters and their corresponding RVs estimates for the same facula.
+   In the presence of a facula, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations.}
     \label{fig:faculae.corr}
@@
 \includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{\xavier{I agree with Jessi here, you should show on the top plot the estimated RVs, and the new and old model.
-Then leave the bottom plot the same.
-I would put estimated RVs in black, new model in red and old model in green, then keep the same colors for the bottoms plots.
-Also for the caption, I would use like you put already SN mean RV estimate, SN median estimate, N mean estimate, and for the model "new activity model", "usual activity model"}(top) The spurious RVs caused by a facula in the simulated data using a Normal and a SN fit.
-Before and once corrected from stellar activity.
-\jessi{What is the correction done here?
-I think what you mean is this:  ``The black circles are the estimated RVs and the red plus signs are the estimated RVs from the fit model of  Eq.~\ref{eq:RV:correction}.''  If my assumption is correct, the legend should say ``RV estimates'' and ``RV model'' or something like that.
-Otherwise this is rather confusing because in the bottom plot you are actually comparing residuals from two models, while the top has a different interpretation.}
+   \caption{(top) The spurious RVs (black dots) caused by a facula in the simulated data using a Normal and a SN fit, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
    %
  (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
-std) and the residuals from the usual correction (Usual corr.
-std), obtained fitting the function $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$.
+std--red crosses) and the residuals from the usual correction (Usual corr.
+std--green triangles).
 The residuals have a smaller systematic component when using the proposed model of
-  Eq.~\ref{eq:RV:correction} (black circles) compared to the usual model (blue triangles).
+  Eq.~\ref{eq:RV:correction} (red crosses) compared to the usual model (green triangles).
 The tests of statistical significance on the parameters are presented in Table \ref{table:faculae.test}.}
@@
 \begin{center}
-\caption{\xavier{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 3\% faculae on the simulated Sun.
-All the variables corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by a facula.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability seen in the different RV estimates.}}
+\caption{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction from stellar activity induced by an equatorial 3\% facula on the simulated Sun.
+All the parameters corresponding to the Normal or SN variables are statistically significant to explain the spurious RV variations caused by a facula.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability seen in the different RV estimates.}
 \label{table:faculae.test}
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
-\caption{\xavier{RV estimated either by the mean of a Normal density fit to the CCF (N mean RV) or by the mean (SN mean RV) or median (SN median RV) of a SN density fit to the CCF.
+\caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line) or SN median RV (cyan dots-dashed line).
 In this case, the CCFs have been generated using SOAP 2.0, considering an equatorial 1\% spot on the simulated Sun.
-The star do one full rotation between phase -0.5 and 0.5, with the spot being seen face-on for phase 0.} SN mean RV seems to have the smallest spurious variations caused by the spot.}
+The star do one full rotation between phase -0.5 and 0.5, with the spot being seen face-on for phase 0.
+SN mean RV seems to have the smallest spurious variations caused by the spot.}
    %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
@@
 \includegraphics[height = 6in]{SOAP_SPOT_Comparison_para_SN.pdf} 
-   \caption{\xavier{\emph{Left:} Correlation between the different asymmetry parameters and the different RV estimates in the case of an equatorial 1\% spot on the simulated Sun.
-\emph{Right:} Correlation between the different width parameters and the different RV estimates for the same spot.
+   \caption{\emph{Left:} Correlations between the different asymmetry parameters and their corresponding RV estimates in the case of an equatorial 1\% spot on the simulated Sun.
+\emph{Right:} Correlations between the different width parameters and their corresponding RV estimates for the same spot.
 In the presence of a spot, both the shape and the width of the CCF change as the star rotates.
 However, only the asymmetry produces a statistically significant correlation with the different RV estimates.
-In the case of the correlation between the width and the different RV estimates the data produces a circle, meaning that those two quantities are not varying in phase.}}
+In the case of the correlation between the width parameters and their corresponding RV estimates the data produces a circle, meaning that those two quantities are not varying in phase.}
     \label{fig:spot.corr}
@@
 \includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{\xavier{same comments as for Fig.
-4}\umberto{Set of  spurious variations in RVs caused by a \textbf{spot} using a Normal and a SN fit before and once corrected from stellar activity.
-The new correction has done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}.
-Once corrected for stellar activity using the proposed linear function (black dots), the residuals present a smaller systematic component if compared with the residuals obtained with the usual correction (blue triangles).}}
+   \caption{(top) The spurious RVs (black dots) caused by a spot in the simulated data using a Normal and a SN fit, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+   %
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
+std--red crosses) and the residuals from the usual correction (Usual corr.
+std--green triangles).The residuals have a smaller systematic component when using the proposed model of
+  Eq.~\ref{eq:RV:correction} (red crosses) compared to the usual model (green triangles).
+The tests of statistical significance on the parameters are presented in Table \ref{table:spot.test}.}
     \label{fig:spot.correction}
@@
 
+(top) The spurious RVs (black dots) caused by a spot in the simulated data using a Normal and a SN fit, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$.
+   %
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
+std) and the residuals from the usual correction (Usual corr.
+std), obtained fitting the function $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$.
+The residuals have a smaller systematic component when using the proposed model of
+  Eq.~\ref{eq:RV:correction} (red crosses) compared to the usual model (green triangles).
+The tests of statistical significance on the parameters are presented in Table \ref{table:spot.test}.
+
 \begin{table}
 \begin{center}
-\caption{\xavier{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun.
-All the variables corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by this spot, except for the width of the CCF when using SN mean RV or SN median RV as RV estimates.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability seen in the different RV estimates.}}
+\caption{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun.
+All the parameters corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by this spot, except for the width of the CCF when using SN mean RV or SN median RV as RV estimates.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability seen in the different RV estimates.}
 \label{table:spot.test}
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
- \caption{\xavier{RV estimated either by the mean of a Normal density fit to the CCF (N mean RV) or by the mean (SN mean RV) or median (SN median RV) of a SN density fit to the CCF.
+ \caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line) or SN median RV (cyan dots-dashed line).
 In this case, the CCFs have been generated using SOAP 2.0, considering an equatorial 1\% spot on the simulated Sun in addition to a planet with a period of one third of the rotational period of the star and with an amplitude of 10\,\ms.
-The star do one full rotation between phase -0.5 and 0.5, with the spot being seen face-on for phase 0.}}
+The star do one full rotation between phase -0.5 and 0.5, with the spot being seen face-on for phase 0.}
    %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
@@
 The statistical tests conducted on the parameters, whose results are summarized in Table \ref{table:spotplanet.test}, shows that except for the width parameters with coefficient $\beta_3$, all the other Normal or SN parameters are significantly useful to explain the RV variation induce by a spot plus a planet.
-\xavier{When looking in the same Table at the RV rms of the residuals after correcting for stellar activity plus de planet, we see that all the RV estimates gives very similar results, with SN mean RV giving the smallest value.}
+Always looking at Table \ref{table:spotplanet.test}, we see that the residuals, once corrected for stellar activity an the presence of the planet, lead to similar results, with SN mean RV giving the smallest value.
 
@@
 \begin{center}
-\caption{\xavier{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun and a planet with period one third of the rotational period and semi-amplitude 10\,\ms.
-All the variables corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by this spot plus planet, except for the width of the CCF.
-Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.}}
+\caption{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun and a planet with period one third of the rotational period and semi-amplitude 10\,\ms.
+All the parameters corresponding to the Normal or SN variables are statistically significant to explain the spurious RV variations caused by this spot plus planet, except for the width of the CCF.
+Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.}
 \label{table:spotplanet.test}
@@
 Four other stars have been analyzed with the proposed method and details can be found in the Appendix \ref{appendix}.
-For all the stars that we considered in the present work, \xavier{we selected only the CCFs that were derived from spectra that had at least a SNR at 550 nm of 10.}
+For all the stars that we considered in the present work, we selected only the CCFs that were derived from spectra that had at least a SNR at 550 nm of 10.
 
@@
 Note that more observations have been done during this year, however we selected here only the data that are not significantly affected by contamination from Alpha Cen A \citep[see][]{Dumusque-2012}.
-\xavier{We choose these observations as they represent probably the best sampled and most precise RV data set showing a strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.}
+We chosen those observations as they represent probably the best sampled and most precise RV data set showing a strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.
 
@@
 \includegraphics[height = 3.6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
-   \caption{\xavier{Slope should be 720, Legend for subplot bottom right should be N mean RV and bot N mean RV RV}.
-\emph{Left: }Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
+   \caption{\emph{Left: }Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
 As we can see with the strong correlation, those two parameters measure the CCF asymmetry in the same way.
@@
 \includegraphics[height = 6in]{HD12862_[4]Comparison_para.pdf}  
-   \caption{Correlation between the asymmetry parameters and the RVs for Alpha Centauri B.
+   \caption{Correlations between the asymmetry parameters and their corresponding RVs for Alpha Centauri B.
 The last three plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN (SN mean RV and SN median RV) and the Normal fits.
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONHD12862_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{Set of RVs for Alpha Centauri B using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.
-\ref{eq:RV:correction}.
-Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
+   \caption{(top) The RVs (black dots) for Alpha Centauri B estimated using a SN and a Normal fit.
+   %
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
+std--black dots) and the residuals from the usual correction (Usual corr.
+std--blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+The residuals have a smaller systematic component when using the proposed model of
+  Eq.~\ref{eq:RV:correction} (black dots) compared to the usual model (blue triangles).}
    \label{fig:alphacent:correctionRV}
@@
 \begin{center}
-\caption{\xavier{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity in Alpha Cen B data.
-All the variables corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by stellar activity, except for the asymmetry of the CCF when using the Normal parameters (BIS SPAN).}
-The evaluation of the $R^2$ shows that the proposed linear combination better explains variations in RVs due to the stellar activity, when the RVs are derived using SN mean RV.}
+\caption{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction from stellar activity in Alpha Cen B data.
+All the variables corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by stellar activity, except for the asymmetry of the CCF when using the Normal parameters (BIS SPAN).
+The evaluation of the $R^2$ shows that the proposed linear combination better explains variations in RVs due to the stellar activity when the RVs are derived using SN mean RV.}
 \label{table:alphacent.test}
@@
 \includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
-   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
-Correlation between the asymmetry parameters and the RVs for $\text{HD}192310$.
-The last three plots show the correlation between the FWHM and the RVs for $\text{HD}192310$ using respectively the SN and the Normal fits.
-The p--values associated with each $R$ is statistically different from $0$.}
+   \caption{Correlations between the asymmetry parameters and their corresponding RVs for $\text{HD}192310$.
+The last three plots show the correlation between the FWHM and the RVs for $\text{HD}192310$ using respectively the SN (SN mean RV and SN median RV) and the Normal fits.
+The correlations are always stronger when using parameters derived from the SN fit than the Normal one.
+The p--values associated with each $R$ are statistically different from $0$.}
    \label{fig:Gliese785:corrPlot}
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONHD19231_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
-Set of RVs for $\text{HD}192310$  using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.
-\ref{eq:RV:correction}.
-Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
+   \caption{(top) The RVs (black dots) for $\text{HD}192310$ estimated using a SN and a Normal fit.
+   %
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
+std--black dots) and the residuals from the usual correction (Usual corr.
+std--blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+The residuals for both the proposed correction from stellar activity are comparable.}
    \label{fig:HD192310:correctionRV}
@@
 \includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
-   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
-Correlation between the asymmetry parameters and the RVs for $\text{HD}10700$.
-The last three plots show the correlation between the FWHM and the RVs for $\text{HD}10700$ using respectively the SN and the Normal fits.
-The p--values associated with each $R$ is statistically different from $0$.}
+   \caption{Correlations between the asymmetry parameters and their corresponding RVs for $\text{HD}10700$.
+The last three plots show the correlation between the FWHM and the RVs for $\text{HD}10700$ using respectively the SN (SN mean RV and SN median RV) and the Normal fits.
+The correlations between the asymmetry parameters and their corresponding RVs are stronger when using the parameter SN mean RV obtained from the SN fit than the Normal one.
+The correlation between the FWHM and the RVs is stronger when using the parameter retrieved with the Normal distribution.
+The p--values associated with each $R$ are statistically different from $0$, except for the correlation between FIG BIS- and RV (p--values=0.36).}
    \label{fig:Tau:corrPlot}
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONHD10700_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
-Set of RVs for $\text{HD}10700$  using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.
-\ref{eq:RV:correction}.
-Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
+   \caption{(top) The RVs (black dots) for $\text{HD}10700$ estimated using a SN and a Normal fit.
+   %
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
+std--black dots) and the residuals from the usual correction (Usual corr.
+std--blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+The residuals for both the proposed correction from stellar activity are comparable.}
    \label{fig:HD10700:correctionRV}
@@
 \includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
-   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
-Correlation between the asymmetry parameters and the RVs for $\text{HD}215152$.
-The last three plots show the correlation between the FWHM and the RVs for $\text{HD}215152$ using respectively the SN and the Normal fits.
-Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
+   \caption{Correlations between the asymmetry parameters and their corresponding RVs for $\text{HD}215152$.The last three plots show the correlation between the FWHM and the RVs for $\text{HD}215152$ using respectively the SN (SN mean RV and SN median RV) and the Normal fits.
+The correlations between the asymmetry parameters and their corresponding RVs are stronger when using the parameter SN mean RV obtained from the SN fit than the Normal one.
+The p--values associated with each $R$ are, from the top to the bottom, from the left to the right: $2.2e-16,0.02,0.27, 0.05 ,7e-4,1e-5,1e-5,0.0007,0.0004,0.5,0.2$.}
    \label{fig:HD215152:corrPlot}
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONHD21515_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
-Set of RVs for $\text{HD}215152$ using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.
-\ref{eq:RV:correction}.
-Once corrected for stellar activity, the residuals for the Normal are $0.054$ \ms higher than the residuals retrieved with the SN analysis.}
+   \caption{(top) The RVs (black dots) for $\text{HD}215152$ estimated using a SN and a Normal fit.
+   %
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
+std--black dots) and the residuals from the usual correction (Usual corr.
+std--blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+The residuals for both the proposed correction from stellar activity are comparable.}
    \label{fig:HD215152:correctionRV}
@@
 \includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
-   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
-Correlation between the asymmetry parameters and the RVs for  $\text{Corot }7$.
-The last three plots show the correlation between the FWHM and the RVs for  $\text{Corot }7$ using respectively the SN and the Normal fits.
-Concerning the asymmetry of the CCF, note that the p--values associated with $R$ are strongly different fro $0$ for those parameters retrieved by using the SN.}
+   \caption{Correlations between the asymmetry parameters and their corresponding RVs for $\text{Corot }7$.
+The last three plots show the correlation between the FWHM and the RVs for $\text{Corot }7$ using respectively the SN (SN mean RV and SN median RV) and the Normal fits.
+The correlations between the asymmetry parameters and their corresponding RVs are stronger when using the parameter SN mean RV obtained from the SN fit than the Normal one.
+The p--values associated with each $R$ are, from the top to the bottom, from the left to the right: $2.2e-16,2e-5,0.23,0.11,0.0055,0.0025,0.012,0.002,2.2e-16,2.2e-16,2.2e-16$.
+}
    \label{fig:Corot7:corrPlot}
@@
 \includegraphics[height = 6in]{NEW_CORRECTIONLRa01_E_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{\xavier{Update correposnding to similar figures in Sec 5}.
-Set of RVs for  $\text{Corot }7$ using a Normal and a SN fit before and once corrected from stellar activity.
-The correction is done using Eq.
-\ref{eq:RV:correction}.
-Once corrected for stellar activity, the residuals for the Normal are $0.336$ \ms higher than the residuals retrieved with the SN analysis.}
+   \caption{(top) The RVs (black dots) for $\text{Corot }7$ estimated using a SN and a Normal fit.
+   %
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
+std--black dots) and the residuals from the usual correction (Usual corr.
+std--blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+The residuals have a smaller systematic component when using the proposed model of Eq.~\ref{eq:RV:correction} (black dots) compared to the usual model (blue triangles) Moreover, once corrected from stellar activity using Eq.
+\ref{eq:RV:correction}, the systematic component using the SN is $0.334$ \ms smaller than the one retrieved with the Normal analysis.}
    \label{fig:Corot-7:correctionRV}

### 2018-06-04 manuscript.tex
4.3 updates

@@
 The variations observed in SN mean RV are quite different from the variations measured in SN median RV and N mean RV.
-\jessi{The cyan line is hard to see in the legend, and may be impossible in a black-and-white version - could the legend background be white?}
 }
@@
 
-The last simulation presented consists in having a planetary signal influencing the CCF, in addition to the 1\% spot modeled before (see Sec.~\ref{sec:soap.spot}).
-The purpose of this example is to check if we are able to disentangle as efficiently the two different sources of variations when using the parameters derived using a Normal, or a SN fit to the CCF.
-In this case, we inject a planet with a semi-amplitude of 10 \ms, with no eccentricity, and with a period corresponding to one third of the stellar rotational period.
+The final simulation presented here includes a planetary signal influencing the CCF along with the 1\% spot modeled previously (see Sec.~\ref{sec:soap.spot}). 
+The purpose of this example is to check if we are able to disentangle these two different sources of variations when using the parameters derived using a Normal versus a SN fit to the CCF.
+In this scenario the planet is injected with a semi-amplitude of 10 \ms with no eccentricity and with a period corresponding to one third of the stellar rotational period \jessi{(i.e.
+one-third of 25 days)} \jessi{The previous i.e.
+I added is highlighted just so you can verify that indeed the rotation period is 25 days as noted at the beginning of this section}.
 
 Fig.~\ref{fig:spot.plus.planet} shows the variation observed in the CCF barycenter parameters.
-Like in the case of the spot, all RV estimates show very similar variations, with SN mean RV showing a slightly smaller amplitude.
-
-In Fig.~\ref{fig:spot.plus.planet.corr}, we show the correlation between the different CCF parameters.
-Although observing weaker correlations than in the case of the spot, due to the fact that the planet induces changes in RV without inducing any change in width or asymmetry of the CCF, the correlation strengths between the CCF asymmetry and RV are in exactly the same order than in the case of the spot: $\gamma$--SN median RV, BIS SPAN--N mean RV and $\gamma$--SN mean RV, with $R$ values of $-0.84$, $-0.78$ and $-0.76$, respectively.
+As in the case of the spot, all RV estimates show similar variations, with SN mean RV showing a slightly smaller amplitude.
+
+The correlation between the different CCF parameters are displayed in Fig.~\ref{fig:spot.plus.planet.corr}. 
+The correlations are weaker than in the case of the spot due to the planet inducing changes in RV without affecting the width or asymmetry of the CCF.
+However, the strength of the correlations between the CCF asymmetry and RV are in the same order as with the spot-only model: $\gamma$--SN median RV, BIS SPAN--N mean RV and $\gamma$--SN mean RV, with $R$ values of $-0.84$, $-0.78$ and $-0.76$, respectively.
 The variation seen in the width-RV phase space draw a circle like in the case of a spot, therefore, no correlation is observed between those two parameters.

### 2018-06-04 manuscript.tex
4.3 updates

@@
   Eq.~\ref{eq:RV:correction} (red crosses) compared to the usual model (green triangles).
-The tests of statistical significance on the parameters are presented in Table \ref{table:spot.test}.}
+The tests of statistical significance on the parameters are presented in Table \ref{table:spot.test}.
+\jessi{The SN Mean and Median bottom plots still show the two outliers - in the updated plots emailed out by Umberto it had looked like the outliers were at least somewhat resolved}
+}
     \label{fig:spot.correction}
@@
 The correlations are weaker than in the case of the spot due to the planet inducing changes in RV without affecting the width or asymmetry of the CCF.
-However, the strength of the correlations between the CCF asymmetry and RV are in the same order as with the spot-only model: $\gamma$--SN median RV, BIS SPAN--N mean RV and $\gamma$--SN mean RV, with $R$ values of $-0.84$, $-0.78$ and $-0.76$, respectively.
-The variation seen in the width-RV phase space draw a circle like in the case of a spot, therefore, no correlation is observed between those two parameters.
+However, the strength of the correlations between the CCF asymmetry and RV are in the same order as with the spot-only model: $\gamma$--SN median RV has the highest correlation followed by BIS SPAN--N mean RV and then $\gamma$--SN mean RV, with $R$ values of $-0.84$, $-0.78$ and $-0.76$, respectively.
+The patterns seen in the width-RV phase space in Fig.~\ref{fig:spot.plus.planet.corr} follow a circle similar to the spot-only model, and no correlation is observed between those two parameters.
 
@@
    \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a spot is present on the photosphere of the star and a planet is injected.
-In this case only the shape of the CCF changes as the spot moves, producing statistically significative correlations only between the RVs and the asymmetry parameter.
+The shape of the CCF changes as the spot moves, producing statistically significative correlations only between the RVs and the asymmetry parameter.
 The correlations between the RVs and the width parameter of the CCF is weaker than the previous case that considers only the presence of a spot on the photosphere of the star.}
@@
 
-In order to correct the RVs from the spurious variation caused by the spot, we need to add to our model of activity correction, a signal to take into account the RV variation caused by the injected planet.
-The observed RV can therefore be modeled as a combination of the activity and planetary signal:
+In order to correct the estimated RVs from the spurious variation caused by the spot, the proposed model for correcting the activity is added to a signal that takes into account the RV variation caused by a injected planet.
+The observed RV can therefore be modeled as a combination of the activity and planetary signals:
 %
@@
 %
-where $RV_{\text{activity}}$ can be found in Eq.~\ref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case of no eccentricity, can be modelled by the following sinusoidal function:
+where $RV_{\text{activity}}$ can be found in Eq.~\ref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case with no eccentricity, can be modeled by the following sinusoidal function:
 %
@@
 %
-where the amplitude $K$, the orbital period $P$ and the epoch at the periapsis $t_{0}$ are three unknown parameters that define the planetary orbit.
+with amplitude $K$, orbital period $P$, and an epoch at the periapsis $t_{0}$.  The previous three unknown parameters define the planetary orbit.
 
@@
 We can see how in this case we are able to disentangle the spurious variations in RVs caused by stellar activity from the pure Doppler-shift due to the planet.
-The statistical tests conducted on the parameters, whose results are summarized in Table \ref{table:spotplanet.test}, shows that except for the width parameters with coefficient $\beta_3$, all the other Normal or SN parameters are significantly useful to explain the RV variation induce by a spot plus a planet.
-Always looking at Table \ref{table:spotplanet.test}, we see that the residuals, once corrected for stellar activity an the presence of the planet, lead to similar results, with SN mean RV giving the smallest value.
+The proposed model from Eqn~\eqref{eq:RV:correction.overall} was fit and the results of the estimated model are summarized summarized in Table \ref{table:spotplanet.test}.
+Except for the width parameters with coefficient $\beta_3$, all the other Normal or SN parameters are significantly useful to explain the RV variation induce by a spot plus a planet.
+It is also apparent that the residuals, once corrected for stellar activity and the presence of the planet, lead to similar results with SN mean RV giving the smallest value.
+\jessi{I'm not sure what the point of the previous sentence is - the SN mean RV residuals is similar to what?}
 

### 2018-06-04 manuscript.tex
5 updates

@@
 
-In this Section we present the analysis conducted on Alpha Centauri B, comparing the result of fitting a CCF using the SN density defined in Sec.
-\ref{sec:3} with the usual approach based on fitting a Normal density to retrieve the RV and width of the CCF and calculating the bisector to derive the asymmetry parameter BIS SPAN.
-Four other stars have been analyzed with the proposed method and details can be found in the Appendix \ref{appendix}.
-For all the stars that we considered in the present work, we selected only the CCFs that were derived from spectra that had at least a SNR at 550 nm of 10.
+In this Section we present the analysis conducted on the star Alpha Centauri B, comparing the result of fitting a CCF using the SN density defined in Sec.
+\ref{sec:3} with the usual approach based on fitting a Normal density for estimating the RV and asymmetry of the CCF.
+%to retrieve the RV and width of the CCF and calculating the bisector to derive the asymmetry parameter BIS SPAN. 
+Four other stars have been analyzed with the proposed method and details can be found in Appendix \ref{appendix}. 
+For all the stars considered in the presented work, only CCFs that were derived from spectra that had at least a SNR at 550 nm of 10 were selected.
 
@@
 
-\subsection{Comparison between the different CCF parameters derived with the Normal and the Skew Normal density} \label{sec:alphacentb}
-
-We analyzed $1808$ CCFs derived from spectra of Alpha Centauri B taken in 2010 by the HARPS spectrograph.
-Note that more observations have been done during this year, however we selected here only the data that are not significantly affected by contamination from Alpha Cen A \citep[see][]{Dumusque-2012}.
-We chosen those observations as they represent probably the best sampled and most precise RV data set showing a strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.
-
-We begin the analysis by evaluating the correlation between $\gamma$ and BIS SPAN. 
+\subsection{Comparison between the different CCF parameters derived with the Normal and the Skew Normal} \label{sec:alphacentb}
+
+There were $1808$ CCFs analyzed that were derived from the spectra of Alpha Centauri B taken in 2010 by the HARPS spectrograph.
+Note that more observations were carried out this year, however only the data that were not significantly affected by contamination from Alpha Centauri A were used \citep[see][]{Dumusque-2012}.
+The selected observations should represent the best sampled and most precise RV data set available for Alpha Centauri B \jessi{I added ``Alpha Centauri B'' - if the previous statement was to be more general, please remove} showing strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.
+
+First, the correlation between $\gamma$ and BIS SPAN is evaluated.
 In the left panel of Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $720$ and a strong Pearson correlation coefficient of $R=0.95$.
-This strong correlation shows that $\gamma$ and BIS SPAN are measuring in a very similar way the CCF asymmetry.
+This strong correlation suggests that the $\gamma$ and BIS SPAN are measuring a similar asymmetry for the CCF.
 This strong correlation allows as well to convert the dimensionless $\gamma$ parameters into \ms\,using the slope of the correlation, in this case 720 \ms.

### 2018-06-04 manuscript.tex
5 updates

@@
   Eq.~\ref{eq:RV:correction} (red crosses) compared to the usual model (green triangles).
-The tests of statistical significance on the parameters are presented in Table \ref{table:faculae.test}.}
+The tests of statistical significance on the parameters are presented in Table \ref{table:faculae.test}.
+}
     \label{fig:faculae.correction}
@@
 
-In the right of Fig.~\ref{fig:alphacent:corr.gamma}, we show the comparison between the RVs retrieved using the SN density and the ones obtained with the Normal density.
-We clearly see that the amplitude of the activity signal is stronger when using SN mean RV, and the signal measured using N mean RV or SN median RV are very similar.
-We observe the same behavior in the case of a faculae (see Sec.~\ref{sec:soap.faculae}) and therefore, it seems that the activity signal seen in those data os most likely induced by faculae.
-This is an observation that was already made in \citet{Dumusque-2014c}.
+The right plot of Fig.~\ref{fig:alphacent:corr.gamma} displays the comparison between the RVs derived estimated using the SN density and the Normal density. 
+The amplitude of the activity signal is slightly stronger for the SN mean RV (in the top-right plot the black circles of the SN mean RV tend to be more extreme), while the signal measured using N mean RV or SN median RV tend to be similar.
+This behavior is similar to the faculae (see Sec.~\ref{sec:soap.faculae}) suggesting that the activity signal could be due to faculae present on Alpha Centauri B; \jessi{the previous statement seems like rather weak evidence - is there more that could be said to strengthen this point?}
+\citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
 %When using SN mean RV, it is possible to observe more variations than the ones measured by the Normal fitting.

### 2018-06-04 manuscript.tex
5 updates

@@
 The tests of statistical significance on the parameters are presented in Table \ref{table:faculae.test}.
-}
-    \label{fig:faculae.correction}
+}\label{fig:faculae.correction}
 \end{center}
@@
 The tests of statistical significance on the parameters are presented in Table \ref{table:spot.test}.
-\jessi{The SN Mean and Median bottom plots still show the two outliers - in the updated plots emailed out by Umberto it had looked like the outliers were at least somewhat resolved}
+\jessi{The SN Mean and Median bottom plots still show the two outliers - in the updated plots emailed out by Umberto it had looked like the outliers were at least somewhat resolved.
+Also, it would be good to clarify what the std is in the top plots (e.g.
+Estimated RV std) since there are three sets of points.}
 }
@@
 The amplitude of the activity signal is slightly stronger for the SN mean RV (in the top-right plot the black circles of the SN mean RV tend to be more extreme), while the signal measured using N mean RV or SN median RV tend to be similar.
-This behavior is similar to the faculae (see Sec.~\ref{sec:soap.faculae}) suggesting that the activity signal could be due to faculae present on Alpha Centauri B; \jessi{the previous statement seems like rather weak evidence - is there more that could be said to strengthen this point?}
+This behavior is similar to the faculae (see Sec.~\ref{sec:soap.faculae}) suggesting that the activity signal could be due to faculae present on Alpha Centauri B; \jessi{the previous statement seems like rather weak evidence - is there more that could be said to strengthen this point?
+Or are there plots that could be referenced/compared?}
 \citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
@@
 
-Similar to what is done in Sec.~\ref{sec:soap}, we compare the correlation between the asymmetry or the width parameters of the CCF and the RV in Fig.~\ref{fig:alphacent:corrPlot}.
-In addition to what is done in Sec.~\ref{sec:soap}, we add the asymmetry parameters derived in \citet{Boisse-2011}, $V_{span}$ and in \citet{Figueira-2013}, BIS-, BIS+, Bi Gauss and $V_{asy}$, as these authors found those asymmetry parameters more correlated to the RVs than BIS SPAN.
-It is clear in the case of Alpha Cen B, but also in the four other stars presented in Appendix \ref{appendix}, that the correlation found between $\gamma$ and SN mean RV is always the strongest.
-On alpha Cen B, the Pearson correlation coefficient reaches a value of $R=0.74$, while it reaches at best $R=-0.42$ for all the other asymmetry--RV correlations not derived using the SN density fit.
-When looking at the width-RV correlation, once again, the correlation between SN FWHM and SN mean RV is the strongest for all the stars, except for the quietest star of all five, HD10700, for which the Pearson correlation coefficient is 0.53 for the Normal parameters and 0.42 for the SN parameters.
+Similar to the anayses in Sec.~\ref{sec:soap}, we compare the correlation between the asymmetry or the width parameters of the CCF and the RV in Fig.~\ref{fig:alphacent:corrPlot}. 
+For this analysis, we also include the asymmetry parameters derived in \citet{Boisse-2011}, $V_{span}$ and in \citet{Figueira-2013}, BIS-, BIS+, Bi Gauss and $V_{asy}$, as these authors found those asymmetry parameters more correlated to the RVs than BIS SPAN.
+It is clear in the case of Alpha Cen B, but also in the four other stars presented in Appendix \ref{appendix}, that the correlation found between $\gamma$ and SN mean RV is consistently the strongest.
+In particular, for Alpha Cen B, the Pearson correlation coefficient is $R=0.74$, while it is at best $R=-0.42$ for all the other asymmetry--RV correlations not derived using the SN density fit.
+
+\jessi{The next paragraph is somewhat confusing because the other stars are now wrapped into the discussion without proper introduction.}
+The correlation between SN FWHM and SN mean RV is the strongest for all the stars, except for the quietest star of all five, HD10700, for which the Pearson correlation coefficient is 0.53 for the Normal parameters and 0.42 for the SN parameters.
 This analysis shows that the parameters derived when using a SN density are more sensitive the stellar activity, and therefore using those parameters can lead to the detection of stellar activity, when the Normal parameters do not detect anything.

### 2018-06-04 manuscript.tex
5 updates

@@
 
-\jessi{The next paragraph is somewhat confusing because the other stars are now wrapped into the discussion without proper introduction.}
+\jessi{This next paragraph is somewhat confusing because the other stars are now wrapped into the discussion without proper introduction.}
 The correlation between SN FWHM and SN mean RV is the strongest for all the stars, except for the quietest star of all five, HD10700, for which the Pearson correlation coefficient is 0.53 for the Normal parameters and 0.42 for the SN parameters.
@@
 
-In Fig \ref{fig:alphacent:correctionRV}, we study the efficiency of the stellar activity correction proposed in Sec.~\ref{sec:31}.
-The first observation we can make is that the RV measured with SN mean RV presents a rms 35\% larger than the RV measured when fitting a Normal density.
-In the case of SN median RV, we see as well a larger RV rms, however only 9\% larger.
-Even though we see those differences in RV, once we correct for the stellar activity using Eq.~\ref{eq:RV:correction}, we find the same RV residuals rms.
+\jessi{I changed some things in the following paragraph that I'm not completely sure are accurate - please review}
+\jessi{The performance of the stellar activity correction proposed in Sec.~\ref{sec:31} is displayed in Fig~\ref{fig:alphacent:correctionRV}. 
+The RV estimated with SN mean RV has a std that is 35\% larger than the std of the RV estimated with the N mean RV, and the std of SN median RV is 9\% larger than that of the N mean RV.
+Even though we see these differences in the estimated RV, once we correct for the stellar activity using Eq.~\ref{eq:RV:correction}, 
+the remaining std of the residuals are essentially the same for all three approaches.
 %In the best case, for SN mean RV, we reduce the stellar activity signal by a factor of 2, while in the worst case, N mean RV, only by a factor 1.5. 
-Therefore, although it seems that the parameters derived using the SN density are more sensitive to stellar activity, we are not able to correct better for stellar activity signal using a linear combination of the different CCF parameters.
+Although it seems that the parameters derived using the SN density are more sensitive to stellar activity than with the N density, after correction using the proposed model, the methods appear to be similarly successful at addressing the stellar activity signal.
+%we are not able to correct better for stellar activity signal using a linear combination of the different CCF parameters.
+}
 

### 2018-06-04 manuscript.tex
5.1 updates

@@
 
-When looking at the significance of the different parameters in the activity correction in Table~\ref{table:alphacent.test}, we see that the intercept is not significant for any of the correction, and BIS SPAN, with coefficient $\beta_2$, is not useful to explain stellar activity when using the parameters derived from the Normal density fit.
-However all the other parameters in the Normal and SN cases are useful to model stellar activity.
-By analyzing the values of $R^2$, we see that the correction is more efficient at explaining stellar activity when considering SN mean RV as the RV estimate.
-This is expected from the results above since for the three different RV estimates, we arrive to the same RV residual rms after correction for activity, but before correction, SN mean RV shows the largest RV rms.
+When looking at the statistical significance of the different parameters used for correcting activity in Table~\ref{table:alphacent.test}, we see that the intercept is not significant for any of the models, and BIS SPAN (coefficient $\beta_2$) does not statistically significantly help in explaining stellar activity when using the parameters derived from the Normal density fit.
+However all the other parameters in the Normal and SN cases are statistically significant for modeling stellar activity. 
+By analyzing the values of the coefficient of determination, $R^2$, we see that the model for the SN mean RV is able to capture the highest percentage of variability in the estimated RV. 
+This is not a surprising result since for the three different RV estimates, we arrive to the same RV residual rms after correction for activity, but before correction, SN mean RV shows the largest RV rms (see Fig~\ref{fig:alphacent:correctionRV}).
 

### 2018-06-04 manuscript.tex
5.1 updates
Add files via upload
Fig.4,7 updated. Fig.7 without outliers. Resized Table in Appendix.

@@
 The tests of statistical significance on the parameters are presented in Table \ref{table:spot.test}.
-\jessi{The SN Mean and Median bottom plots still show the two outliers - in the updated plots emailed out by Umberto it had looked like the outliers were at least somewhat resolved.
-Also, it would be good to clarify what the std is in the top plots (e.g.
-Estimated RV std) since there are three sets of points.}
 }
@@
 Except for the width parameters with coefficient $\beta_3$, all the other Normal or SN parameters are significantly useful to explain the RV variation induce by a spot plus a planet.
-It is also apparent that the residuals, once corrected for stellar activity and the presence of the planet, lead to similar results with SN mean RV giving the smallest value.
-\jessi{I'm not sure what the point of the previous sentence is - the SN mean RV residuals is similar to what?}
+\umberto{check if I understood correctly the meaning ...
+We also observe that the residuals, once corrected for stellar activity and the presence of the planet, are comparable for all the three analyses, with SN mean RV giving the smallest values.} \jessi{I'm not sure what the point of the previous sentence is - the SN mean RV residuals is similar to what?}
 
@@
 
-\jessi{This next paragraph is somewhat confusing because the other stars are now wrapped into the discussion without proper introduction.}
+\umberto{maybe we can just remove this sentence and note in the caption of the correlation plot for TauCeti that this is the only case in which the correlation using the common fit is higher.} \jessi{This next paragraph is somewhat confusing because the other stars are now wrapped into the discussion without proper introduction.}
 The correlation between SN FWHM and SN mean RV is the strongest for all the stars, except for the quietest star of all five, HD10700, for which the Pearson correlation coefficient is 0.53 for the Normal parameters and 0.42 for the SN parameters.
@@
 \hline
-Parameter          & RV         &   SN mean RV &   SN median RV \\
+Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
 \hline
@@
 \begin{center}
+\scalebox{0.9}{
 \begin{tabular}{ccccccccc}
@@
 \rule{0pt}{2ex}    & & & &\\
-\end{tabular}
+\end{tabular}}
 \end{center}
@@
 The correlations between the asymmetry parameters and their corresponding RVs are stronger when using the parameter SN mean RV obtained from the SN fit than the Normal one.
-The correlation between the FWHM and the RVs is stronger when using the parameter retrieved with the Normal distribution.
+\umberto{The correlation between the FWHM and the RVs is, only for this quiet star, stronger when using the parameter retrieved with the Normal distribution}.
 The p--values associated with each $R$ are statistically different from $0$, except for the correlation between FIG BIS- and RV (p--values=0.36).}

### 2018-06-05 manuscript.tex
answering to comments

@@
 The stellar effective temperature is set to 5778 K
-%(NASA Planetary Fact Sheets)\jessi{Is there a full citation available for this NASA fact sheet?  Also, why is it referenced?  Is the effective temperature supposed to be similar to the Sun?}
 , and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34 are used, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
@@
 The purpose of this example is to check if we are able to disentangle these two different sources of variations when using the parameters derived using a Normal versus a SN fit to the CCF.
-In this scenario the planet is injected with a semi-amplitude of 10 \ms with no eccentricity and with a period corresponding to one third of the stellar rotational period \jessi{(i.e.
-one-third of 25 days)} \jessi{The previous i.e.
-I added is highlighted just so you can verify that indeed the rotation period is 25 days as noted at the beginning of this section}.
+In this scenario the planet is injected with a semi-amplitude of 10 \ms with no eccentricity and with a period corresponding to one third of the stellar rotational period, i.e.
+one-third of 25 days.
 
@@
 We can see how in this case we are able to disentangle the spurious variations in RVs caused by stellar activity from the pure Doppler-shift due to the planet.
-The proposed model from Eqn~\eqref{eq:RV:correction.overall} was fit and the results of the estimated model are summarized summarized in Table \ref{table:spotplanet.test}.
-Except for the width parameters with coefficient $\beta_3$, all the other Normal or SN parameters are significantly useful to explain the RV variation induce by a spot plus a planet.
-\umberto{check if I understood correctly the meaning ...
-We also observe that the residuals, once corrected for stellar activity and the presence of the planet, are comparable for all the three analyses, with SN mean RV giving the smallest values.} \jessi{I'm not sure what the point of the previous sentence is - the SN mean RV residuals is similar to what?}
-
+The proposed model from Eq.~\ref{eq:RV:correction.overall} was fitted to the RV data and the results of the estimated model are summarized in Table \ref{table:spotplanet.test}.
+Except for the width parameters with coefficient $\beta_3$, all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet.
+\xavier{We also observe that the RV residuals, once corrected for stellar activity and the presence of the planet, are comparable in terms of rms for all the three different RV estimates, with SN mean RV giving a slightly smaller value.}
 %\begin{figure*}[htbp]
@@
 Note that more observations were carried out this year, however only the data that were not significantly affected by contamination from Alpha Centauri A were used \citep[see][]{Dumusque-2012}.
-The selected observations should represent the best sampled and most precise RV data set available for Alpha Centauri B \jessi{I added ``Alpha Centauri B'' - if the previous statement was to be more general, please remove} showing strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.
+The selected observations represent probably, among all RV data existing, the best sampled and most precise RV data set showing strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.
 
@@
 The amplitude of the activity signal is slightly stronger for the SN mean RV (in the top-right plot the black circles of the SN mean RV tend to be more extreme), while the signal measured using N mean RV or SN median RV tend to be similar.
-This behavior is similar to the faculae (see Sec.~\ref{sec:soap.faculae}) suggesting that the activity signal could be due to faculae present on Alpha Centauri B; \jessi{the previous statement seems like rather weak evidence - is there more that could be said to strengthen this point?
-Or are there plots that could be referenced/compared?}
+This behavior is similar to the faculae simulated with SOAP 2.0 in see Sec.~\ref{sec:soap.faculae}, suggesting that the activity signal could be due to faculae present on Alpha Centauri B.
+\xavier{Another argument in favour of the faculae, is the presence of the positive correlation between $\gamma$ and SN mean RV and SN FWHM and SN mean RV seen in Fig.~\ref{fig:alphacent:corrPlot}.
+In Sec.~\ref{sec:soap.spot}, we saw that a spot induces a negative correlation between $\gamma$ and SN mean RV and no correlation between SN FWHM and SN mean RV}.
 \citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
@@
 
-Similar to the anayses in Sec.~\ref{sec:soap}, we compare the correlation between the asymmetry or the width parameters of the CCF and the RV in Fig.~\ref{fig:alphacent:corrPlot}. 
+Similar to the analyses in Sec.~\ref{sec:soap}, we compare the correlation between the asymmetry or the width parameters of the CCF and the RV in Fig.~\ref{fig:alphacent:corrPlot}. 
 For this analysis, we also include the asymmetry parameters derived in \citet{Boisse-2011}, $V_{span}$ and in \citet{Figueira-2013}, BIS-, BIS+, Bi Gauss and $V_{asy}$, as these authors found those asymmetry parameters more correlated to the RVs than BIS SPAN.

### 2018-06-05 manuscript.tex
finished corrections

@@
 \usepackage{graphicx}
-\usepackage{hyperref}
-%\usepackage[draft]{hyperref}
+%\usepackage{hyperref}
+\usepackage[draft]{hyperref}
 \bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
@@
 %
-{We propose to estimate the parameters of the CCF by fitting a Skew Normal (SN) density shape which.
-Unlike the commonly employed Normal density, the SN density includes a skewness parameter to capture the asymmetry of the CCF induced by stellar activity and also the natural asymmetry induced by convective blueshift.
-Moreover, the SN distribution allows for different location parameters beyond the mean, such as the median of the CCF.}
+{We propose to estimate the parameters of the CCF by fitting a Skew Normal (SN) density which, unlike the commonly employed Normal density, includes a skewness parameter to capture the asymmetry of the CCF induced by stellar activity and also the natural asymmetry induced by convective blueshift.}
+%Moreover, the SN distribution allows for different location parameters beyond the mean, such as the median of the CCF.}
 %
@@
 {When considering real observations, the correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are stronger when using the parameters estimated with the SN rather than the ones obtained with the commonly employed Normal density.
-In particular the strongest correlations have been obtained when using as location parameter the  mean of the SN.
-This suggests that the asymmetry of the CCF and the width of the CCF estimated using a SN may be more sensitive to stellar activity, which can be helpful when estimating stellar rotational periods and generally for characterizing stellar activity signals.
-The estimated uncertainties in the measured RVs using the proposed SN approach and as location parameter the median of the SN are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
+In particular the strongest correlations have been obtained when using as RV estimate the  mean of the SN.
+This suggests that the asymmetry of the CCF and the width of the CCF estimated using a SN density may be more sensitive to stellar activity, which can be helpful when estimating stellar rotational periods and generally for characterizing stellar activity signals.
+The estimated uncertainties in the measured RVs using the proposed SN approach and as RV estimate the median of the SN are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
 The estimated uncertainties on the asymmetry parameter of the SN are on average $15\%$ smaller than the uncertainties measured on the Bisector Inverse Slope Span (BIS SPAN), which is the commonly parameter used to evaluate the asymmetry of the CCF.
 }
-{We strongly encourage the use of the SN distribution to retrieve the different parameters of the CCF.
+{We strongly encourage the use of the SN distribution to retrieve the different parameters of the CCF as the correlations used to probe stellar activity are stronger and the measure of the RV and the CCF asymmetry are more precise.
+}
+%{We strongly encourage the use of the SN distribution to retrieve the different parameters of the CCF.
 The correlation between the mean of the SN and the asymmetry parameter of the CCF and the correlation between the mean of the SN and the width parameter of the CCF probe better stellar activity signals than when using the parameters retrieved with the Normal distribution.
@@
 Finally, all the parameters are available in one single fit to the CCF.
-}
+%}
 %
@@
 
-\subsection{Comparison between the different CCF parameters derived with the Normal and the Skew Normal} \label{sec:alphacentb}
+\subsection{Comparison for Alpha Cen B of the different CCF parameters derived with the Normal and the Skew Normal} \label{sec:alphacentb}
 
@@
 For this analysis, we also include the asymmetry parameters derived in \citet{Boisse-2011}, $V_{span}$ and in \citet{Figueira-2013}, BIS-, BIS+, Bi Gauss and $V_{asy}$, as these authors found those asymmetry parameters more correlated to the RVs than BIS SPAN.
-It is clear in the case of Alpha Cen B, but also in the four other stars presented in Appendix \ref{appendix}, that the correlation found between $\gamma$ and SN mean RV is consistently the strongest.
-In particular, for Alpha Cen B, the Pearson correlation coefficient is $R=0.74$, while it is at best $R=-0.42$ for all the other asymmetry--RV correlations not derived using the SN density fit.
-
-\umberto{maybe we can just remove this sentence and note in the caption of the correlation plot for TauCeti that this is the only case in which the correlation using the common fit is higher.} \jessi{This next paragraph is somewhat confusing because the other stars are now wrapped into the discussion without proper introduction.}
-The correlation between SN FWHM and SN mean RV is the strongest for all the stars, except for the quietest star of all five, HD10700, for which the Pearson correlation coefficient is 0.53 for the Normal parameters and 0.42 for the SN parameters.
-This analysis shows that the parameters derived when using a SN density are more sensitive the stellar activity, and therefore using those parameters can lead to the detection of stellar activity, when the Normal parameters do not detect anything.
-This is the case for the asymmetry-RV correlation of HD10700, HD215152, Corot-7, and the width-RV correlation for HD215152 (see Appendix \ref{appendix}).
-
+\jessi{This next paragraph is somewhat confusing because the other stars are now wrapped into the discussion without proper introduction.}
+\xavier{I create a new subsection after this one to discuss rapidly th eother stars}
+\xavier{It is clear in the case of Alpha Cen B, that the correlation found between $\gamma$ and SN mean RV is the strongest. 
+The Pearson correlation coefficient is $R=0.74$, while it is at best $R=0.42$ for all the other asymmetry--RV correlations not derived using the SN density fit.
+When looking at the correlation between the width and the RV estimate for Alpha Cen B, once again the correlation is the strongest for the SN parameters, with $R=0.82$ for SN FWHM-SN mean RV, while it is equals to $R=0.7$ for the correlation between FWHM and N mean RV.}
+%
 %The correlations between $\gamma$ and SN mean RV, and also SN FWHM and SN mean RV
-
+%
 %Because the median is a more robust index than the mean, the correlation between $\gamma$ and SN median RV is not as large as the correlation between $\gamma$ and SN mean RV, but it is nonetheless $1.5$ times larger than the correlation between the other common asymmetry parameters and their corresponding RVs.
@@
 
-\jessi{I changed some things in the following paragraph that I'm not completely sure are accurate - please review}
-\jessi{The performance of the stellar activity correction proposed in Sec.~\ref{sec:31} is displayed in Fig~\ref{fig:alphacent:correctionRV}. 
-The RV estimated with SN mean RV has a std that is 35\% larger than the std of the RV estimated with the N mean RV, and the std of SN median RV is 9\% larger than that of the N mean RV.
+The performance of the stellar activity correction proposed in Sec.~\ref{sec:31} is displayed in Fig~\ref{fig:alphacent:correctionRV}. 
+For Alpha Cen B, the RV estimated with SN mean RV has a std that is 35\% larger than the std of the RV estimated with the N mean RV, and the std of SN median RV is 9\% larger than that of the N mean RV.
 Even though we see these differences in the estimated RV, once we correct for the stellar activity using Eq.~\ref{eq:RV:correction}, 
-the remaining std of the residuals are essentially the same for all three approaches.
+the remaining RV rms of the residuals are essentially the same for all three approaches.
 %In the best case, for SN mean RV, we reduce the stellar activity signal by a factor of 2, while in the worst case, N mean RV, only by a factor 1.5. 
-Although it seems that the parameters derived using the SN density are more sensitive to stellar activity than with the N density, after correction using the proposed model, the methods appear to be similarly successful at addressing the stellar activity signal.
+\xavier{Although, when studying the correlations between the different parameters, we see that the parameters derived using the SN density are more sensitive to stellar activity than with the Normal density,
+the proposed linear model for correcting stellar activity is not able to perform better in the SN case than in the Normal case.}
+\xavier{@Jessi: I deleted "after correction using the proposed model, the methods appear to be similarly successful at addressing the stellar activity signal" as it was giving the wrong impression that the SN parameters are useless}
+\xavier{Comparing the new correction proposed in Sec.~\ref{sec:31} to correct for activity and the usual correction only using a linear combination of the width and the asymmetry of the CCF, we see very similar efficiency.
+The new correction is however able to get RV rms that are 6\,\cms\,smaller than the usual correction.}
+%it seems that the parameters derived using the SN density are more sensitive to stellar activity than with the Normal density, after correction using the proposed model, the methods appear to be similarly successful at addressing the stellar activity signal.
 %we are not able to correct better for stellar activity signal using a linear combination of the different CCF parameters.
-}
 
@@
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Detection limits when using the RV derived with the Normal or the Skew Normal density} \label{sec:soap_real}
+\subsection{Comparison for HD192310, HD10700, HD215152 and Corot-7 of the different CCF parameters derived with the Normal and the Skew Normal} \label{sec:real_data_other_stars}
+
+\xavier{The preceding section was analysing the improvement brought by the SN parameters compared to the Nomral parameters and the BIS SPAN.
+Here we do a similar analysis for four other main sequence stars: HD192310, HD10700, HD215152 and Corot-7.
+The same correlation plots, and activity-correction plots that was found in the preceding section can be found found for those new stars in Appendix \ref{appendix}.
+
+When looking to the correlation between the parameters, we arrive to the same conclusions than for Alpha Cen B.
+The correlation between $\gamma$ and SN mean RV is always the strongest among all the other asymmetry-RV corrleations not derived with SN parameters.
+For the correlation between the width and the RV, the strongest correlation is also found for all the stars between SN FWHM and SN mean RV.
+There is one exception however, in the case of HD10700, the Pearson correlation coefficient between FWHM and N mean RV is equal to $R=0.53$, while it is only $R=0.42$ for the correlation between SN FWHM and SN mean RV.
+
+Except for the special case discussed above for HD10700, the analysis of those four stars, in addition to Alpha Cen B shows that the parameters derived when using a SN density are more sensitive to activity, and therefore using those parameters can lead to the detection of stellar activity, when the Normal parameters do not detect anything.
+This is the case for the asymmetry-RV correlation of HD10700, HD215152, Corot-7, and the width-RV correlation for HD215152 (see Appendix \ref{appendix}).
+
+In terms of activity correction, we see like in the case of Alpha Cen B, that although the RV rms is larger when measuring the RVs using SN mean RV compared to the RVs derived using N mean RV, after correcting for activity using the new model proposed in Sec.~\ref{sec:31}, both RV estimates gives similar residuals.
+We also see nearly no significant differences between the new correction proposed and the usual correction only using a linear combination of the width and the asymmetry of the CCF.
+There is only in the case of Corot-7 where the new correction is able to get a RV residual rms 30\,\cms smaller than the usual correction.}
+
+%-----------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Detection limits when using the RV derived with the Normal or the Skew Normal density} \label{sec:detect_limits}
 
@@
 We note that when comparing the activity correction presented in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, we only see a slight improvement brought by our proposed correction.
+\xavier{We however encourage the community to use this new model if the goal is to reduce activity without considering the computationally expensive use of Gaussian Process.
+A further analysis of the p--value of each coefficient can be performed to see the ones that are not relevant and that can therefore be removed.}
 

### 2018-06-06 manuscript.tex
Add files via upload
went through the paper, slightly updated Xavier's comments.

@@
 Except for the width parameters with coefficient $\beta_3$, all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet.
-\xavier{We also observe that the RV residuals, once corrected for stellar activity and the presence of the planet, are comparable in terms of rms for all the three different RV estimates, with SN mean RV giving a slightly smaller value.}
+We also observe that the RV residuals, once corrected for stellar activity and the presence of the planet, are comparable in terms of rms for all the three different RV estimates, with SN mean RV giving a slightly smaller value.
 %\begin{figure*}[htbp]
@@
 This behavior is similar to the faculae simulated with SOAP 2.0 in see Sec.~\ref{sec:soap.faculae}, suggesting that the activity signal could be due to faculae present on Alpha Centauri B.
-\xavier{Another argument in favour of the faculae, is the presence of the positive correlation between $\gamma$ and SN mean RV and SN FWHM and SN mean RV seen in Fig.~\ref{fig:alphacent:corrPlot}.
-In Sec.~\ref{sec:soap.spot}, we saw that a spot induces a negative correlation between $\gamma$ and SN mean RV and no correlation between SN FWHM and SN mean RV}.
+\umberto{Another argument that suggests the presence of faculae, is the strong positive measured correlation between $\gamma$ and SN mean RV and SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot}.
+In Sec.~\ref{sec:soap.spot}, we saw that a spot induces a negative correlation between $\gamma$ and SN mean RV, while weak correlations are measured between SN FWHM and SN mean RV}.
 \citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
@@
 \xavier{I create a new subsection after this one to discuss rapidly th eother stars}
-\xavier{It is clear in the case of Alpha Cen B, that the correlation found between $\gamma$ and SN mean RV is the strongest. 
+\umberto{It is clear in the case of Alpha Cen B, that the correlation found between $\gamma$ and SN mean RV is the strongest. 
 The Pearson correlation coefficient is $R=0.74$, while it is at best $R=0.42$ for all the other asymmetry--RV correlations not derived using the SN density fit.
-When looking at the correlation between the width and the RV estimate for Alpha Cen B, once again the correlation is the strongest for the SN parameters, with $R=0.82$ for SN FWHM-SN mean RV, while it is equals to $R=0.7$ for the correlation between FWHM and N mean RV.}
+When looking at the correlations between the width and the RV estimates for Alpha Cen B, once again the correlation is strongest for the parameters retrieved form the SN density, with $R=0.82$ for SN FWHM-SN mean RV, while it is equals to $R=0.7$ for the correlation between FWHM and N mean RV.}
 %
@@
 %In the best case, for SN mean RV, we reduce the stellar activity signal by a factor of 2, while in the worst case, N mean RV, only by a factor 1.5. 
-\xavier{Although, when studying the correlations between the different parameters, we see that the parameters derived using the SN density are more sensitive to stellar activity than with the Normal density,
-the proposed linear model for correcting stellar activity is not able to perform better in the SN case than in the Normal case.}
+\umberto{Although when studying the correlations between the different parameters we see that the parameters retrieved by using the SN density are more sensitive to stellar activity than the ones obtained with a Normal density fit,
+the proposed linear model for correcting from stellar activity is not able to perform better in the SN case than in the Normal case.}
 \xavier{@Jessi: I deleted "after correction using the proposed model, the methods appear to be similarly successful at addressing the stellar activity signal" as it was giving the wrong impression that the SN parameters are useless}
-\xavier{Comparing the new correction proposed in Sec.~\ref{sec:31} to correct for activity and the usual correction only using a linear combination of the width and the asymmetry of the CCF, we see very similar efficiency.
+\umberto{When comparing the new correction for stellar activity proposed in Sec.~\ref{sec:31} with the usual correction, that uses only a linear combination of the width and the asymmetry of the CCF, we end up with very similar results.
 The new correction is however able to get RV rms that are 6\,\cms\,smaller than the usual correction.}
@@
 
-\xavier{The preceding section was analysing the improvement brought by the SN parameters compared to the Nomral parameters and the BIS SPAN.
-Here we do a similar analysis for four other main sequence stars: HD192310, HD10700, HD215152 and Corot-7.
-The same correlation plots, and activity-correction plots that was found in the preceding section can be found found for those new stars in Appendix \ref{appendix}.
-
-When looking to the correlation between the parameters, we arrive to the same conclusions than for Alpha Cen B.
-The correlation between $\gamma$ and SN mean RV is always the strongest among all the other asymmetry-RV corrleations not derived with SN parameters.
+\umberto{In the previous section we evaluated the improvement obtained by the SN parameters respect to the Normal parameters and the BIS SPAN.
+We execute similar analyses for four other main sequence stars: HD192310, HD10700, HD215152 and Corot-7.
+The same correlations plots and activity--after--correction plots displayed in the previous section for Alpha Cen B can be found found for those new four stars in Appendix \ref{appendix}.
+
+When looking to the correlation between the parameters, we arrive to the same conclusions obtained for Alpha Cen B.
+The correlation between $\gamma$ and SN mean RV is always the strongest among all the asymmetry-RV correlations not retrieved by the SN parameters.
 For the correlation between the width and the RV, the strongest correlation is also found for all the stars between SN FWHM and SN mean RV.
-There is one exception however, in the case of HD10700, the Pearson correlation coefficient between FWHM and N mean RV is equal to $R=0.53$, while it is only $R=0.42$ for the correlation between SN FWHM and SN mean RV.
+There is one exception however, in the case of HD10700: the Pearson correlation coefficient between FWHM and N mean RV is equal to $R=0.53$, while it is only $R=0.42$ for the correlation between SN FWHM and SN mean RV.
 
 Except for the special case discussed above for HD10700, the analysis of those four stars, in addition to Alpha Cen B shows that the parameters derived when using a SN density are more sensitive to activity, and therefore using those parameters can lead to the detection of stellar activity, when the Normal parameters do not detect anything.
-This is the case for the asymmetry-RV correlation of HD10700, HD215152, Corot-7, and the width-RV correlation for HD215152 (see Appendix \ref{appendix}).
-
-In terms of activity correction, we see like in the case of Alpha Cen B, that although the RV rms is larger when measuring the RVs using SN mean RV compared to the RVs derived using N mean RV, after correcting for activity using the new model proposed in Sec.~\ref{sec:31}, both RV estimates gives similar residuals.
-We also see nearly no significant differences between the new correction proposed and the usual correction only using a linear combination of the width and the asymmetry of the CCF.
-There is only in the case of Corot-7 where the new correction is able to get a RV residual rms 30\,\cms smaller than the usual correction.}
+This is the case for the evaluation of the asymmetry-RV correlations for HD10700, HD215152, Corot-7, and the width-RV correlation for HD215152 (see Appendix \ref{appendix}).
+
+In terms of correction for stellar activity, in the case of Alpha Cen B we see that although the RV rms is larger when measuring the RVs using SN mean RV (respect to the RVs obtained using N mean RV), once corrected for activity using the new model proposed in Sec.~\ref{sec:31}, both RVs estimates provides similar residuals.
+We also observe slight differences in the rms between the new proposed correction and the usual correction, that uses only a linear combination of the width and the asymmetry of the CCF.
+Only in the case of Corot-7 the new correction is able to provide RV residual rms 30\,\cms smaller than the one obtained with the usual correction.}
 
@@
 The correlations between the asymmetry parameters and their corresponding RVs are stronger when using the parameter SN mean RV obtained from the SN fit than the Normal one.
-\umberto{The correlation between the FWHM and the RVs is, only for this quiet star, stronger when using the parameter retrieved with the Normal distribution}.
+The correlation between the FWHM and the RVs is, only for this quiet star, stronger when using the parameter retrieved with the Normal distribution.
 The p--values associated with each $R$ are statistically different from $0$, except for the correlation between FIG BIS- and RV (p--values=0.36).}

### 2018-06-06 manuscript.tex
minor updates

@@
 
-\title{Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density
-\thanks{Based on observations collected at the La Silla Parana Observatory,
+\title{Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory,
 ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}}
@@
 Four other stars have been analyzed with the proposed method and details can be found in Appendix \ref{appendix}. 
-For all the stars considered in the presented work, only CCFs that were derived from spectra that had at least a SNR at 550 nm of 10 were selected.
+For all the stars considered in the presented work, only CCFs that were derived from spectra that had at least a SNR of 10 at 550 nm were selected.
 

### 2018-06-06 manuscript.tex
5.2 updates

@@
 The Pearson correlation coefficient is $R=0.74$, while it is at best $R=0.42$ for all the other asymmetry--RV correlations not derived using the SN density fit.
-When looking at the correlations between the width and the RV estimates for Alpha Cen B, once again the correlation is strongest for the parameters retrieved form the SN density, with $R=0.82$ for SN FWHM-SN mean RV, while it is equals to $R=0.7$ for the correlation between FWHM and N mean RV.}
+When looking at the correlations between the width and the RV estimates for Alpha Cen B, again the correlation is strongest for the SN parameters with $R=0.82$ for SN FWHM-SN mean RV, while it is $R=0.70$ for FWHM and N mean RV.}
 %
@@
 
-The performance of the stellar activity correction proposed in Sec.~\ref{sec:31} is displayed in Fig~\ref{fig:alphacent:correctionRV}. 
+Results illustrating the performance of the stellar activity correction proposed in Sec.~\ref{sec:31} is displayed in Fig~\ref{fig:alphacent:correctionRV}. 
 For Alpha Cen B, the RV estimated with SN mean RV has a std that is 35\% larger than the std of the RV estimated with the N mean RV, and the std of SN median RV is 9\% larger than that of the N mean RV.
 Even though we see these differences in the estimated RV, once we correct for the stellar activity using Eq.~\ref{eq:RV:correction}, 
-the remaining RV rms of the residuals are essentially the same for all three approaches.
+the rms of the residuals are essentially the same for all three approaches.
 %In the best case, for SN mean RV, we reduce the stellar activity signal by a factor of 2, while in the worst case, N mean RV, only by a factor 1.5. 
@@
 
-\umberto{In the previous section we evaluated the improvement obtained by the SN parameters respect to the Normal parameters and the BIS SPAN.
-We execute similar analyses for four other main sequence stars: HD192310, HD10700, HD215152 and Corot-7.
+\umberto{In the previous section we evaluated the improvement obtained by the SN parameters compared to the Normal parameters and the BIS SPAN.
+We carryout similar analyses for four other main sequence stars: HD192310, HD10700, HD215152 and Corot-7.
 The same correlations plots and activity--after--correction plots displayed in the previous section for Alpha Cen B can be found found for those new four stars in Appendix \ref{appendix}.
 
-When looking to the correlation between the parameters, we arrive to the same conclusions obtained for Alpha Cen B.
-The correlation between $\gamma$ and SN mean RV is always the strongest among all the asymmetry-RV correlations not retrieved by the SN parameters.
-For the correlation between the width and the RV, the strongest correlation is also found for all the stars between SN FWHM and SN mean RV.
-There is one exception however, in the case of HD10700: the Pearson correlation coefficient between FWHM and N mean RV is equal to $R=0.53$, while it is only $R=0.42$ for the correlation between SN FWHM and SN mean RV.
-
-Except for the special case discussed above for HD10700, the analysis of those four stars, in addition to Alpha Cen B shows that the parameters derived when using a SN density are more sensitive to activity, and therefore using those parameters can lead to the detection of stellar activity, when the Normal parameters do not detect anything.
+The correlations between the parameters of these additional stars are similar to those obtained for Alpha Cen B.
+The correlation between $\gamma$ and SN mean RV is the strongest among all the asymmetry-RV correlations.
+For the correlation between the width and the estimated RV, the strongest correlation is consistently between SN FWHM and SN mean RV.
+However, there is one exception in the case of HD10700 where the Pearson correlation coefficient between FWHM and N mean RV is equal to $R=0.53$, while it is $R=0.42$ between SN FWHM and SN mean RV.
+
+Except for the special case discussed above for HD10700, the analysis of those four stars, in addition to Alpha Cen B shows that the parameters derived when using a SN density are more sensitive to activity.
+Therefore using the SN parameters can lead to the better detection of stellar activity over the Normal parameters.
 This is the case for the evaluation of the asymmetry-RV correlations for HD10700, HD215152, Corot-7, and the width-RV correlation for HD215152 (see Appendix \ref{appendix}).
-
-In terms of correction for stellar activity, in the case of Alpha Cen B we see that although the RV rms is larger when measuring the RVs using SN mean RV (respect to the RVs obtained using N mean RV), once corrected for activity using the new model proposed in Sec.~\ref{sec:31}, both RVs estimates provides similar residuals.
-We also observe slight differences in the rms between the new proposed correction and the usual correction, that uses only a linear combination of the width and the asymmetry of the CCF.
-Only in the case of Corot-7 the new correction is able to provide RV residual rms 30\,\cms smaller than the one obtained with the usual correction.}
+\jessi{The final sentence in this paragraph does not make sense given the preceding two sentences - it reads like the SN has higher correlations than the N, but then only says this is true for only 3 of the 4 stars}
+
+In terms of correction for stellar activity, in the case of Alpha Cen B we see that although the RV rms is larger when measuring the RVs using SN mean RV (compared to the RVs obtained using N mean RV), once corrected for activity using the new model proposed in Sec.~\ref{sec:31}, both RVs estimates provides similar residuals.
+We also observe slight differences in the rms between the new proposed correction and the usual correction, which uses only a linear combination of the width and the asymmetry of the CCF.
+For Corot-7 the new correction is able to provide RV residual rms 30\,\cms smaller than the one obtained with the usual correction.}
 

### 2018-06-06 manuscript.tex
5.3 updates

@@
 %-----------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Detection limits when using the RV derived with the Normal or the Skew Normal density} \label{sec:detect_limits}
-
-In the preceding section, we saw that the RV measured when considering a SN or a Normal density present different amplitudes, mainly in the case of SN mean RV.
-However, when correcting for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, it seems that we are able to reach the same RV precision.
-In this section, we want to investigate if for some of the three different RV definitions presented in this paper, it is easier or more difficult to detect planetary signals when considering stellar activity.
-To do so, we estimated what would be the minimum amplitude of a planetray signal we could detect at different orbital periods when considering data affected by stellar activity.
+\subsection{Detection limits when using the estimated RVs from the Normal or the Skew Normal models} \label{sec:detect_limits}
+
+In the preceding section, we saw that the estimated RV measured when considering a SN or a Normal model resulted in different amplitudes, especially when using the SN mean RV.
+However, when correcting for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, it seems same RV precision is achieved.
+\jessi{It would be good to be a little more precise in the previous sentence:  by ``same precision'' do you mean the same std of the residuals?
+Given the first sentence the reader may be confused because it says they have different amplitudes estimated.}
+In this section, we investigate the ability of the three different RV estimators' (N mean RV, SN mean RV, and SN median RV) ability to detect planetary signals among stellar activity.
+To carryout this test, the minimum detected amplitude of a planetary signal is estimated at different orbital periods when considering data affected by stellar activity.
 

### 2018-06-06 manuscript.tex
5.3 updates

@@
 
-To get CCFs affected by realistic stellar activity signals, we took the ones from Alpha Cen B used in the preceding section.
-To simulate a planetary signal, we then blue- or red-shifted those CCFs with the wanted amplitude, period and phase.
-We first simulated several RV data sets, with always the same stellar signal, but injecting planets with parameters corresponding to the following grid:
+In order to obtain CCFs affected by realistic stellar activity signals, the CCFs from Alpha Cen B used previously were considered. 
+To simulate a planetary signal, the CCFs were blue- or red-shifted with the desired amplitude, period, and phase.
+Several RV data sets with the same stellar signal, but different planetary signals were injected using parameters corresponding to the following grid:
 \begin{itemize}
-\item period of 3, 5, 7, 9, 11, 15, 20 , 25 and 30 days,
+\item period of 3, 5, 7, 9, 11, 15, 20, 25, and 30 days,
 \item amplitude from 0.5 to 3 \ms\, by steps of 0.05\,\ms,
@@
 
-For each simulation, 4500 in total, we applied the activity correction presented in Eq.~\ref{eq:RV:correction} and look for signals in the residuals using a Generalized Lomb-Scargle periodogram \citep[][]{Zechmeister-2009,Scargle-1982,Lomb-1976a}.
-If a signal with a p--value\footnote{estimated by bootstrap} smaller than 1\% had a period compatible with the injected planetary period considering an error of 20\%, we were estimating this signal as significant, and therefore the corresponding planet as detected.
-Finally, for each period, we searched for the minimum amplitude for which at least 50\% of the planets with different phases were detected.
+For each of the 4500 simulations considered, the activity correction presented in Eq.~\ref{eq:RV:correction} was applied, and signals in the residuals were investigated using a Generalized Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982, Zechmeister-2009}.
+If a signal with a p--value\footnote{The p--values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected.
+Finally, for each period considered, the minimum amplitude at which at least 50\% of the planets with different phases were detected was found.
 The results are shown in Fig.~\ref{fig:detection_limits}.
-As we can see, all the different RV estimates gives extremely similar detection limits.
-Therefore, we can use any of these estimates when searching for planetary signal in RV data contaminated by stellar activity.
+All three of the different RV estimators give similar detection limits.
+Though more investigations should be considered, these results suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity.
 

### 2018-06-06 manuscript.tex
5.3 updates

@@
 
-Although the detection limits stay constant for all the periods below 15 days, we see that for 20 and 30 days, we have a huge increase in detection limits for all the RV estimates. 
-This is because the periods of the simulated planets, 20 days and 30 days, are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012}
+Although the detection limits remain relatively constant for the periods  $\leq$15 days, there is a notable increase in the detection limit at 20 and 30 days. 
+This is likely due to the periods of the simulated planets, 20 days and 30 days, are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012}
 and therefore close to the semi-periodicity of the stellar activity signal. In such a case, the activity 
-correction absorbs part of the planetary signal. We thus need to inject a much stronger planetary signal at these periods to detect them.
+correction absorbs part of the planetary signal and a stronger planetary signal is needed at these periods in order for them to be detectable.
 

### 2018-06-06 manuscript.tex
6 updates

@@
 In this section, we investigate how the noise of the CCF influences the CCF parameters derived either by a Normal density or a SN density fit. 
-Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other.
-Therefore, we cannot simply vary each point in the CCF with their respective error bar and then recalculate the best SN or Normal density fit, to see how the CCF noise influences N mean RV, SN mean RV, SN median RV, FWHM, SN FWHM, BIS SPAN and $\gamma$.
-We therefore started from the spectrum, for which we know that each point is totally independent of the others.
-The standard error on each point of the spectrum is given by the photon noise, which follows a Poisson law and is therefore obtained by taking the square root of the measured flux.
-
-We applied the following method to estimate the error bars on the different parameters derived from the CCF.
+\jessi{Should we note that the CCF noise is from the photon-noise of the spectra?  Is there more to ``noise'' in the previous sentence?}
+Because a CCF is obtained from a cross-correlation, each point of a CCF is correlated with the other points.
+Therefore, we cannot simply vary each point in the CCF by their respective error bars and then recalculate the best SN or Normal density fit to see how the CCF noise influences the estimation of the parameters of interest (i.e., N mean RV, SN mean RV, SN median RV, FWHM, SN FWHM, BIS SPAN and $\gamma$).
+Instead, we go to the individual spectra where the individual measurements can be considered independent fo the other points.
+The standard error on each point of a spectrum is given by the photon noise, which follows a Poisson distribution and is therefore estimated by taking the squareroot of the measured flux.
+
+The following method was carried out in order to estimate the error bars on the different parameters derived from the CCF. 
 We first modify the values of all the points in the spectrum given their respective error bars.

### 2018-06-07 manuscript.tex
Add files via upload
updates on Jessi's comments. just check last 2 comments (pag10, pag12)

@@
 This behavior is similar to the faculae simulated with SOAP 2.0 in see Sec.~\ref{sec:soap.faculae}, suggesting that the activity signal could be due to faculae present on Alpha Centauri B.
-\umberto{Another argument that suggests the presence of faculae, is the strong positive measured correlation between $\gamma$ and SN mean RV and SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot}.
-In Sec.~\ref{sec:soap.spot}, we saw that a spot induces a negative correlation between $\gamma$ and SN mean RV, while weak correlations are measured between SN FWHM and SN mean RV}.
+Another argument that suggests the presence of faculae, is the strong positive measured correlation between $\gamma$ and SN mean RV and SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot}.
+In Sec.~\ref{sec:soap.spot}, we saw that a spot induces a negative correlation between $\gamma$ and SN mean RV, while weak correlations are measured between SN FWHM and SN mean RV.
 \citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
@@
 For this analysis, we also include the asymmetry parameters derived in \citet{Boisse-2011}, $V_{span}$ and in \citet{Figueira-2013}, BIS-, BIS+, Bi Gauss and $V_{asy}$, as these authors found those asymmetry parameters more correlated to the RVs than BIS SPAN.
-\jessi{This next paragraph is somewhat confusing because the other stars are now wrapped into the discussion without proper introduction.}
-\xavier{I create a new subsection after this one to discuss rapidly th eother stars}
-\umberto{It is clear in the case of Alpha Cen B, that the correlation found between $\gamma$ and SN mean RV is the strongest. 
+It is clear in the case of Alpha Cen B, that the correlation found between $\gamma$ and SN mean RV is the strongest.
 The Pearson correlation coefficient is $R=0.74$, while it is at best $R=0.42$ for all the other asymmetry--RV correlations not derived using the SN density fit.
-When looking at the correlations between the width and the RV estimates for Alpha Cen B, again the correlation is strongest for the SN parameters with $R=0.82$ for SN FWHM-SN mean RV, while it is $R=0.70$ for FWHM and N mean RV.}
+When looking at the correlations between the width and the RV estimates for Alpha Cen B, again the correlation is strongest for the SN parameters with $R=0.82$ for SN FWHM-SN mean RV, while it is $R=0.70$ for FWHM and N mean RV.
 %
@@
 %In the best case, for SN mean RV, we reduce the stellar activity signal by a factor of 2, while in the worst case, N mean RV, only by a factor 1.5. 
-\umberto{Although when studying the correlations between the different parameters we see that the parameters retrieved by using the SN density are more sensitive to stellar activity than the ones obtained with a Normal density fit,
-the proposed linear model for correcting from stellar activity is not able to perform better in the SN case than in the Normal case.}
-\xavier{@Jessi: I deleted "after correction using the proposed model, the methods appear to be similarly successful at addressing the stellar activity signal" as it was giving the wrong impression that the SN parameters are useless}
-\umberto{When comparing the new correction for stellar activity proposed in Sec.~\ref{sec:31} with the usual correction, that uses only a linear combination of the width and the asymmetry of the CCF, we end up with very similar results.
-The new correction is however able to get RV rms that are 6\,\cms\,smaller than the usual correction.}
+Although when studying the correlations between the different parameters we see that the parameters retrieved by using the SN density are more sensitive to stellar activity than the ones obtained with a Normal density fit,
+the proposed linear model for correcting from stellar activity is not able to perform better in the SN case than in the Normal case.
+When comparing the new correction for stellar activity proposed in Sec.~\ref{sec:31} with the usual correction, that uses only a linear combination of the width and the asymmetry of the CCF, we end up with very similar results.
+The new correction is however able to get RV rms that are 6\,\cms\,smaller than the usual correction.
 %it seems that the parameters derived using the SN density are more sensitive to stellar activity than with the Normal density, after correction using the proposed model, the methods appear to be similarly successful at addressing the stellar activity signal.
@@
 
-\umberto{In the previous section we evaluated the improvement obtained by the SN parameters compared to the Normal parameters and the BIS SPAN.
+In the previous section we evaluated the improvement obtained by the SN parameters compared to the Normal parameters and the BIS SPAN.
 We carryout similar analyses for four other main sequence stars: HD192310, HD10700, HD215152 and Corot-7.
@@
 
-Except for the special case discussed above for HD10700, the analysis of those four stars, in addition to Alpha Cen B shows that the parameters derived when using a SN density are more sensitive to activity.
-Therefore using the SN parameters can lead to the better detection of stellar activity over the Normal parameters.
-This is the case for the evaluation of the asymmetry-RV correlations for HD10700, HD215152, Corot-7, and the width-RV correlation for HD215152 (see Appendix \ref{appendix}).
-\jessi{The final sentence in this paragraph does not make sense given the preceding two sentences - it reads like the SN has higher correlations than the N, but then only says this is true for only 3 of the 4 stars}
+Except for the special case discussed above for HD10700, the analyses of those four stars, in addition to the analyses on Alpha Cen B, shows that the parameters derived when using a SN density are more sensitive to activity.
+Therefore using the SN parameters, and in particular defining RV as SN mean RV, can lead to better detection of stellar activity over the Normal parameters.
+This is the case for the evaluation of the asymmetry-RV correlations for  Alpha Cen B, HD10700, HD215152, HD192310 and Corot-7, and the width-RV correlation for Alpha Cen B, HD215152, HD192310 and Corot-7 (see Appendix \ref{appendix}).
 
@@
 We also observe slight differences in the rms between the new proposed correction and the usual correction, which uses only a linear combination of the width and the asymmetry of the CCF.
-For Corot-7 the new correction is able to provide RV residual rms 30\,\cms smaller than the one obtained with the usual correction.}
+For Corot-7 the new correction is able to provide RV residual rms 30\,\cms smaller than the one obtained with the usual correction.
 
@@
 
-In the preceding section, we saw that the estimated RV measured when considering a SN or a Normal model resulted in different amplitudes, especially when using the SN mean RV.
-However, when correcting for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, it seems same RV precision is achieved.
-\jessi{It would be good to be a little more precise in the previous sentence:  by ``same precision'' do you mean the same std of the residuals?
+\umberto{In the previous section, we saw that the estimated RV measured when considering a SN or a Normal model resulted in different amplitudes, especially when using the SN mean RV.
+However, once corrected for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, as shown in the bottom plots of Fig~\ref{fig:alphacent:correctionRV} the rms of the residuals are essentially the same for all three approaches.} \jessi{It would be good to be a little more precise in the previous sentence:  by ``same precision'' do you mean the same std of the residuals?
 Given the first sentence the reader may be confused because it says they have different amplitudes estimated.}
@@
 We note that when comparing the activity correction presented in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, we only see a slight improvement brought by our proposed correction.
-\xavier{We however encourage the community to use this new model if the goal is to reduce activity without considering the computationally expensive use of Gaussian Process.
-A further analysis of the p--value of each coefficient can be performed to see the ones that are not relevant and that can therefore be removed.}
+We however encourage the community to use this new simple linear model if the goal is to reduce activity without considering the computationally expensive use of Gaussian Process.
+A further analysis of the p--value for each coefficient can be performed to see the ones that are not relevant and that can therefore be removed.
 

### 2018-06-07 manuscript.tex
6 updates

@@
 Instead, we go to the individual spectra where the individual measurements can be considered independent fo the other points.
-The standard error on each point of a spectrum is given by the photon noise, which follows a Poisson distribution and is therefore estimated by taking the squareroot of the measured flux.
+The standard error on each point of a spectrum is given by the photon noise, which follows a Poisson distribution and is therefore estimated by taking the square-root of the measured flux.
 
@@
 We first modify the values of all the points in the spectrum given their respective error bars. 
-To do so we added to each point the value randomly drawn from a Gaussian distribution centered on the value of the point and with standard deviation the square root of the flux.
-We then calculated the CCF from this spectrum using the method presented in \citet{Pepe-2002a}, fitted either a Normal or SN density to this CCF and recorded the different parameters.
-We redo this process a hundred times, which gives us at the end, a distribution for each CFF parameter.
-The standard deviations of the obtained distributions is then associated to the standard errors of each CCF parameters.
+To do so random Gaussian noise centered on the value of the point and with standard deviation the square-root of the flux was added across each spectrum. 
+The CCF was calculated using this spectrum according to the method presented in \citet{Pepe-2002a}, then fitted either a Normal or SN density to this CCF and recorded the different parameters. 
+This process was repeated a hundred times in order to obtain a distribution for each CCF parameter. 
+The standard deviations of the resulting distributions provide standard errors for each CCF parameters.
 

### 2018-06-07 manuscript.tex
6 updates

@@
 
-We measured the standard errors of each CCF parameters for all the CCFs of HD215152, HD192310 and Corot-7.
-This gives us an information of how the noise on each CCF parameter varies as a function of SNR.
-In this case, the SNR, measured at 550 nm on the original spectra, varies between 10 and 500.
-The results can be seen in Fig.~\ref{fig:se}.
-In the top plots of this figure, we show the standard errors for the different RV, width and asymmetry estimates.
-Note that because BIS SPAN and $\gamma$ does not have the same units, we used the slope of the correlation between those two parameters to transform $\gamma$ in \ms (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star).
-In the bottom plots, we show the ratio between the standard errors measured when using the SN parameters and the Normal parameters.
-Values smaller or larger than one will imply that standard errors from the SN parameters are more or less precise, respectively.
+The standard errors were also computed for each CCF parameter for all the CCFs of HD215152, HD192310 and Corot-7. 
+This provides information on how the noise of each CCF parameter varies as a function of SNR, where the SNR measured at 550 nm on the original spectra varies between 10 and 500. 
+The combined results for all the stars considered are displayed in Fig.~\ref{fig:se}. 
+The top plots show the standard errors of the three different estimated RV's, the width, and the asymmetry estimates. 
+Note that because BIS SPAN and $\gamma$ do not have the same units, the estimated slopes of the correlation between those two parameters to transform $\gamma$ in \ms were used (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star).
+In the bottom plots show the ratio between the standard errors measured when using the SN parameters and the Normal parameters.
+Values smaller or larger than one will imply that standard errors from the SN parameters are more or less precise than the Normal parameters, respectively.
 

### 2018-06-07 manuscript.tex
6 updates

@@
 
-The standard errors were also computed for each CCF parameter for all the CCFs of HD215152, HD192310 and Corot-7. 
+The standard errors were also computed for each CCF parameter for all the CCFs of HD215152, HD192310 and Corot-7. \jessi{Why weren't the others stars included?}
 This provides information on how the noise of each CCF parameter varies as a function of SNR, where the SNR measured at 550 nm on the original spectra varies between 10 and 500. 
@@
 
-Looking at the estimates for the RV, we see that they all follow a similar exponential decay.
-Although we plot the data for three different stars, we do not see any offsets in this decay, which implies that the SNR at 550 nm is the main contributor to the precision measured in RV.
+The estimates for the RV all appear to follow a similar exponential decay.
+Although the results for three different stars are included in the plot, there do not appear to be any offsets in this decay, which implies that the SNR at 550 nm is the main contributor to the precision measured in RV.
+\jessi{The previous sentence does not make sense to me.
+Why would no offsets imply it is the main contributor in the precision?}
 This is not surprising as the three stars studied here are all main sequence K-dwarfs.
 
-When comparing the three different estimates for the RV, we see that SN mean RV presents standard errors that are 60\% larger than what N mean RV gives.
-On the opposite, SN median RV gives errors 10\% more precise than N mean RV.
+When comparing the three different estimates for the RV, the SN mean RV presents standard errors that are 60\% larger than the N mean RV.
+However, the SN median RV gives errors 10\% more precise than N mean RV.
 Regarding the parameters describing the width of the CCF, FWHM and SN FWHM have the same standard errors.

### 2018-06-07 manuscript.tex
6 updates

@@
 However, the SN median RV gives errors 10\% more precise than N mean RV.
-Regarding the parameters describing the width of the CCF, FWHM and SN FWHM have the same standard errors.
-Finally, for the asymmetry parameters, we see that $\gamma$, derived from the SN, is 15\% more precise than BIS SPAN.
-In conclusion, when fitting a SN density to the CCF and using as RV estimates SN mean RV, we are able to improve by 10\% the precision on the RV, 15\% the precision on the asymmetry, and this without degrading the precision on the width estimate.
-SN mean RV should not be use to derive precise RVs, except perhaps in specific conditions described below, as the precision on this parameter is 60\% worse than the precision on the RVs derived when using the mean of a Normal density fit to the CCF.
+The parameters describing the width of the CCF, FWHM and SN FWHM, have comparable standard errors. 
+Finally, for the asymmetry parameters, $\gamma$ has standard errors that are 15\% more precise than BIS SPAN. 
+In conclusion, when fitting a SN density to the CCF and using as RV estimates SN mean RV \jessi{I'm assuming you mean the median here?}, we are able to improve by 10\% the precision on the estimated RV, 15\% the precision on the estimated asymmetry, both without degrading the precision on the estimated width.
+SN mean RV should not be use to derive precise estimated RVs, except perhaps in specific conditions described below, as the precision on this parameter is 60\% worse than the precision on the RVs derived from N mean RV.
 %

### 2018-06-07 manuscript.tex
6 updates

@@
 \includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
-   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameters.
+   \caption{\jessi{The stars used should be noted here}  Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM, and the asymmetry parameters.
 When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved when fitting a Normal density (red triangles).
-However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit.
+However, the standard errors for SN median RV (cyan crosses) are on average $10\%$ smaller than the standard errors coming from the N mean RV.
 The use of the asymmetry SN parameter $\gamma$ leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
 Note that for the asymmetry, the error in BIS SPAN is in \ms.
-To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
+To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.
+\jessi{it would be good to have a "(top)" and "(bottom)" noted here.}}
    \label{fig:se}

### 2018-06-07 manuscript.tex
7 updates

@@
 
-When fitting a SN density to the CCF, it is possible at once to retrieve parameters that describe the RV, i.e.
-the CCF barycenter, the amplitude, sometimes called the CCF contrast, the width, and the asymmetry of the CCF.
-To estimate the RV, we investigated the use of the mean and the median of the SN density.
+When fitting a SN density to the CCF, parameters that describe the RV (i.e.
+the CCF barycenter), the amplitude (sometimes called the CCF contrast), the width, and the asymmetry of the CCF can all be estimated in a single model framework.
+For the RV estimator, we investigated the use of the mean and the median of the SN density. 
 Then the width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry by using $\gamma$, the skewness parameter of the SN density.

### 2018-06-07 manuscript.tex
7 updates

@@
 
-When we tested the SN density fit to the CCFs provided by the SOAP 2.0 code, that simulate the activity signal induced by a spot or a faculae on a solar-like star, we arrived to the conclusion that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual method.
-By more sensitive, we mean here that the correlation between the skewness and either the mean or median of the SN density is stronger than between BIS SPAN and the mean of a Normal density.
-Moreover, the correlation between the FWHM and the CCF barycenter is also stronger when using the parameters from the SN compared to the parameters from the Normal.
-We also confirmed the behavior that the SN parameters are more correlated than the Normal parameters in the case where a planetary signal is added the to stellar activity modeled by SOAP 2.0.
+To analyze the performance the proposed SN framework, tests on both simulated and real data were carried out and compared to the usual approach of fitting a Normal density shape (for estimating the RV and FWHM) and the BIS SPAN (for estimating the asymmetry).
+The simulated CCFs were generated using the SOAP 2.0 code, which can simulate activity signals induced by a spot or a facula on a solar-like star.
+The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method.
+In this case, sensitivity was measured using the correlation between the asymmetry and the estimated RV's, and it turned out either SN mean RV or SN median RV had a stronger correlation with gamma than the correlation between N mean RV and BIS SPAN.
+Moreover, the correlation between the FWHM and the estimated RV's is also stronger when using the parameters from the SN compared to the parameters from the Normal. 
+The SN parameters continued to have stronger correlations than the Normal in the setting where a planetary signal was added the SOAP 2.0 with a single spot.
 

### 2018-06-07 manuscript.tex
7 updates

@@
 
-We also present in this paper a new function to correct for stellar activity signals.
-Generally, when fitting for planetary signals, people use a model composed of one or several Keplerians to account for the planets, in addition to a linear combination with the FWHM and BIS SPAN of the CCF to account for stellar activity signals.
-The new function proposes to add a linear dependency with the amplitude of the CCF retrieved either by the SN or Normal density fit, and an interaction term between the asymmetry and the width parameters.
-On the simulated data from SOAP 2.0, this new model allows to mitigate stellar activity signals by a factor of 2 and 3.5 better compared to the model generally used, for the faculae and spot, respectively.
+We also propose a new model to correct estimated RV data for stellar activity signals. 
+Generally, when fitting for planetary signals, it is common to use a model composed of one or several Keplerian signals to account for the planets, in addition to a linear combination of the FWHM and BIS SPAN to account for stellar activity signals.
+The proposed model adds an additional term to account for the amplitude of the CCF, and an interaction term between the estimated asymmetry and the width parameters. 
+Using the simulated data from SOAP 2.0, this new model reduces the effect of the stellar activity signal by a factor of 2 and 3.5 over the usual model, for the facula and spot, respectively.
 

### 2018-06-08 manuscript.tex
7 updates

@@
 	    \thanks{\email{umberto.simola@helsinki.fi}}
-	    \and X. Dumusque\inst{3}
+	    \and X. Dumusque\inst{2}
 	    \thanks{Branco Weiss Fellow--Society in Science (url: \url{http://www.society-in-science.org})}    
-	    \and Jessi Cisewski-Kehe\inst{2}
+	    \and Jessi Cisewski-Kehe\inst{3}
 	    }
@@
 \institute{Department of Mathematics and Statistics, University of Helsinki, Helsinki, Finland
+	      \and Observatoire de Gen\`eve, Universit\'e de Gen\`eve, 51 ch. des Maillettes, CH-1290 Versoix, Switzerland 
 	      \and Department of Statistics and Data Science, Yale University, New Haven, CT, USA
-	      \and Observatoire de Gen\`eve, Universit\'e de Gen\`eve, 51 ch. des Maillettes, CH-1290 Versoix, Switzerland 
 	      }
@@
 
-(top) The spurious RVs (black dots) caused by a spot in the simulated data using a Normal and a SN fit, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$.
+\jessi{What is going on with the following paragraph?
+why is "(top)" and "(bottom)" appearing?
+Was this intended for a caption?
+These should not appear in the body of the text - only captions} (top) The spurious RVs (black dots) caused by a spot in the simulated data using a Normal and a SN fit, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$.
    %
@@
 
-When moving to real data, we arrived to the same conclusions than the results of the SOAP 2.0 simulations regarding the strength of the correlation between the CCF asymmetry and the RV, as well as between the CCF width and the RV.
-We note however that although in the case of the simulated data, the stronger asymmetry-RV correlation was found between $\gamma$ and the median of the SN, in the case of real data, it was found between $\gamma$ and the mean of the SN.
-This can be due to the fact that in SOAP 2.0, the faculae is not modelled properly, as it uses as emerging spectrum the one from a spot.
-We know that the temperature between a spot and a faculae is significantly different, therefore their spectra should be different.
-In addition, there is always several active regions on a star, at different locations in longitude and latitude, which is not the case in our SOAP 2.0 simulations were only one active region was modelled at a time.
-This could also be responsible for the fact that we do not observe the same behavior for the mean and the median of the SN when we compare the SOAP 2.0 simulation and real data.
-Nevertheless, in both the simulated and the real cases, the parameters derived from the SN are more sensitive to activity than the parameters derived from a Normal fit.
-In addition, the correlation between the asymmetry and the mean of the SN is always stronger than any other parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
+Similar conclusions were reached with the real data as with the results of the SOAP 2.0 simulations regarding the strength of the correlation between the CCF asymmetry and the RV, as well as between the CCF width and the RV.
+However, the simulated data stronger asymmetry-RV correlation between $\gamma$ and SN median RV while the real data had stronger correlations between $\gamma$ and SN mean RV. 
+There could be several reasons for this difference.
+\jessi{First, it may be due to the fact that in SOAP 2.0 uses a variation of a spot template spectrum as the model rather than a facula template spectrum so the SOAP spectra with a facula is not accurately modeling this type of activity}.
+Because the temperature between a spot and a faculae is significantly different, their spectra should be different. 
+Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region.
+These reasons could also be responsible for the general differences observed in the behavior of the mean and the median of the SN between the SOAP 2.0 data and real data.
+\jessi{regarding the previous statement, would you say that there are also difference in the N mean RV generally between the SOAP and real data?
+I wonder if that could somehow be tied in?
+}
+Nevertheless, in both the simulated and the real cases, the parameters derived from the SN are generally more sensitive to activity than the parameters derived from the Normal.
+Also, the correlation between the asymmetry and the SN mean RV is always stronger than the parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
+\jessi{it may be helpful here to emphasize why it is better fr the parameters to be more sensitive to activity}
 

### 2018-06-08 manuscript.tex
7 updates

@@
 
-When comparing the different RV estimates obtained from the mean of the Normal density, the mean or the median of the SN density, we see that in the case of real data, the amplitude of stellar activity is larger for the mean of the SN, followed by the median of the SN and the mean of the Normal.
-Although there is a huge gap between the first and the second estimate, the difference between the second and the third is much smaller.
-The mean of the SN density is therefore more sensitive to variation in the CCF shape than the median of the SN or the mean of the Normal, which is not surprising as the SN density is able to model the asymmetry of the CCF, what the Normal density does not.
+Considering the different RV estimates of the real data, the amplitude of stellar activity tends to be largest for the SN mean RV, followed by the SN median RV, and then N mean RV. 
+Although there appears to be a larger difference between the SN mean RV and the SN median RV, the SN median RV is similar to the N mean RV. 
+Hence, the mean of the SN density appears to be more sensitive to variation in the CCF shape than the median of the SN or the mean of the Normal.
+This is not surprising as the SN density is able to model the asymmetry of the CCF, what the Normal density does not.
+\jessi{The previous sentence does not follow from the points made in the paragraph.}
 

### 2018-06-08 manuscript.tex
7 updates

@@
 
-Having an estimate of the RV that is more sensitive to stellar activity, like the mean of the SN, can help us to probe better stellar rotational periods, or understand better the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}.
-We saw in the preceding section that the RV estimated derived by the mean of the SN is 60\% noisier than the RV derived by the mean of the Normal.
+Having an estimator of RV that is more sensitive to stellar activity, such as the SN mean RV, can help with better probing stellar rotational periods or better understanding the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}.
+We saw in the preceding section that the SN mean RV estimator is 60\% noisier than the N mean RV estimator. 
 This is not necessarily a negative aspect. 
-Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring SN mean RV, even if the white noise in the data is increased by 60\%.
-
-Even if the different RV estimates have different amplitudes, once we apply our new correction for stellar activity, we arrive exactly to the same RV rms in the residuals, meaning that for an activity correction based on a linear combination of CCF parameters, the SN density fit does not help.
-We note that when comparing the activity correction presented in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, we only see a slight improvement brought by our proposed correction.
+Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring the SN mean RV, even if the white noise in the data is increased by 60\%.
+\jessi{white noise of the estimator?
+The previous two sentences are not very convincing to me.}
+
+Even if the different RV estimators generally have different amplitudes, once the new correction for stellar activity is applied, the residuals of the model have similar rms.
+This suggests that for an activity correction based on a linear combination of CCF parameters, the SN density fit does not help.
+\jessi{The previous sentence does not seem to be a good sentence...I'm not sure what the intent of it is so I'm not sure how to fix it.}
+When comparing the activity correction proposed in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, there appears to be only a slight improvement.
+\jessi{In the previous sentence, are you referring to the real data only?
+The SOAP data did show improvement - right?}
 We however encourage the community to use this new simple linear model if the goal is to reduce activity without considering the computationally expensive use of Gaussian Process.
+\jessi{The previous sentence makes no sense given the discussion in this paragraph.
+You are saying the proposed correction doesn't help, and then you say to use it...}
 A further analysis of the p--value for each coefficient can be performed to see the ones that are not relevant and that can therefore be removed.
 
-We checked if some RV estimates were better at finding planets in RV data affected by observed stellar signals.
-When using the new correction proposed in this paper to mitigate the effect from stellar activity, and when assesing planetary detection based on aperiodogram analysis, we find very similar detection limits for the three RV estimates presented in this paper.
+A test was carried out to see if some RV estimates were better at finding planets in RV data affected by observed stellar signals. 
+When using the new correction proposed in this paper to mitigate the effect from stellar activity and when assessing planetary detection based on a periodogram analysis, we find very similar detection limits for the three RV estimators presented in this paper.
+\jessi{Maybe to try another test to see if the proposed correction is helpful, the detection-limit test could be carried out with the usual correction and we can see if it does not performa s well.}
 Therefore it seems that any of the RV estimate can be used to search for planetary signals.
@@
 Finally, we investigated the precision of each of the SN and Normal parameters including the BIS SPAN.
-It turns out that the mean of the SN should not be used to get precise RVs as the standard errors on this parameter is 60\% greater than when taking the mean of the Normal distribution.
-However, the median of the SN should be used, as it is 10\% more precise than the mean of the Normal.
-Regarding the asymmetry estimates, we observe that $\gamma$ has a precision15\% better than the BIS SPAN.
-It is therefore clear in this case that the SN parameters are more precise to measure the RV and the asymmetry of the CCF.
+It turns out that the SN mean RV should not be used to get precise RVs as the standard errors on this parameter is 60\% greater than the N mean RV.
+However, the SN median RV is 10\% more precise than the N mean RV. 
+Regarding the asymmetry estimates, we observe that $\gamma$ has a precision 15\% better than the BIS SPAN.
 

### 2018-06-08 manuscript.tex
8 updates

@@
 
-When searching for small-mass exoplanets using the RV technique, it is crucial to get the best precision possible on the determination of the RV, but also to measure precisely the shape variations of the CCF, as such variations are induced by stellar activity, and not by planets.
-The correlations between the width of the CCF and the RV, and the asymmetry of the CCF and the RV are used as a way to assess if the measurements are affect by stellar activity signals, therefore, the stronger those correlations are, the better we can probe low level of stellar activity.
+When searching for low-mass exoplanets using the RV technique, it is necessary to get precise estimates of the RV and also to account for variations induced by stellar activity in order to avoid false detections.
+Stellar activity such as spots and faculae can lead to shape variations in the spectra features, which then results in shape variations of the CCF.
+The correlations between the width or asymmetry of the CCF and the estimated RV are commonly used as way to detect if the RVs are affected by stellar activity signals.
+Because the presence of real planets would result in only a shift in the CCF (not a shape change), strong correlations between the shape features of the CCF and the estimated RVs suggest that stellar activity may be present.
 

### 2018-06-08 manuscript.tex
8 updates

@@
 
-In this paper, we introduced a novel approach based on the Skew Normal (SN) density to retrieve the RV and shape variation of the CCF.
-This new method is compared to the usual one, where a Normal density is fitted to the CCF to retrieve the information on the RV and the width of the CCF, and a bisector analysis allows to retrieve the asymmetry of the CCF using the BIS SPAN.
-In addition, we also compare this novel approach to other parameterisations of the CCF asymmetry that have been shown to be more sensitive to activity signals \citep[][]{Boisse-2011,Figueira-2013}.
+In this paper, a new approach for measuring shape changes in the CCF is proposed using the SN density to estimate the RV and shape of the CCF. 
+This new method is compared to a commonly used method based on a Normal density fit to the CCF.
+The mean of the Normal density is used as the estimated RV and the FWHM estimates the width of the CCF.
+Because the Normal density does not have any skewness, another method is need to estimate the asymmetry of the CCF, and the BIS SPAN is often employed.
+In addition, the proposed SN approach is compared to other parameterizations of the CCF asymmetry that have been shown to be sensitive to activity signals \citep[][]{Boisse-2011,Figueira-2013}.
 

### 2018-06-08 manuscript.tex
8 updates

@@
 
-\umberto{In the previous section, we saw that the estimated RV measured when considering a SN or a Normal model resulted in different amplitudes, especially when using the SN mean RV.
-However, once corrected for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, as shown in the bottom plots of Fig~\ref{fig:alphacent:correctionRV} the rms of the residuals are essentially the same for all three approaches.} \jessi{It would be good to be a little more precise in the previous sentence:  by ``same precision'' do you mean the same std of the residuals?
-Given the first sentence the reader may be confused because it says they have different amplitudes estimated.}
+In the previous section, we saw that the estimated RV measured when considering a SN or a Normal model resulted in different amplitudes, especially when using the SN mean RV.
+However, once corrected for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, as shown in the bottom plots of Fig~\ref{fig:alphacent:correctionRV}, the rms of the residuals are essentially the same for all three approaches.
 In this section, we investigate the ability of the three different RV estimators' (N mean RV, SN mean RV, and SN median RV) ability to detect planetary signals among stellar activity.
@@
 
-In all the different tests we could conduct in this paper, the SN parameters were doing as well as the parameters derived when fitting a Normal distribution and calculating the BIS SPAN.
-Moreover, in some cases, we were getting better results when using the SN parameters.
-This is the case when looking at the correlations between the CCF asymmetry and the RV or the CCF width and the RV.
-The SN parameters $\gamma$, SN FWHM and the mean of the SN density always show stronger correlation that any of the parameters derived by the Normal density fit and the BIS SPAN, or the different asymmetry parametrization presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
-Those SN parameters can therefore probe better stellar activity signals.
-In addition, the precision measured on the median of the SN density and the asymmetry of the SN density are 10 and 15\% more precise than the mean of the Normal and BIS SPAN, respectively.
-
-Because of these advantages of using the SN parameters compared to the Normal parameters, BIS SPAN, and all the asymmetry parameters described in \citet{Boisse-2011} and \citet{Figueira-2013}.
-we strongly encourage the community of using this new parametrization of the CCF.
-Correlations between the asymmetry and the mean of the SN, and between the width and the mean of the SN should be used to probe better stellar activity signals in RV data, and the median of the SN should be used as the new definition for RV.
+In the different tests carried out for this work, the SN parameters tended to perform at least as well (and sometimes better) as the parameters from the Normal approach with the BIS SPAN.
+The SN parameters $\gamma$, SN FWHM and SN mean RV always show stronger correlation than the correlations between any of the parameters derived by the Normal and the BIS SPAN, or the different asymmetry parametrization presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
+This suggests the SN parameters may be better at probing stellar activity signals than the other methods. 
+In addition, the precision measured on the SN median RV and the $\gamma$ are 10 and 15\% more precise than the N mean RV and the BIS SPAN, respectively.
+
+Because of the advantages of using the proposed SN approach compared to the Normal approach, BIS SPAN, and all the asymmetry parameters described in \citet{Boisse-2011} and \citet{Figueira-2013}, this new parametrization of the CCF may be more useful for detecting stellar activity than the previously proposed parametrizations.
+Correlations between $\gamma$ and the SN mean RV, and between the width and the SN mean RV can be used to probe stellar activity signals in RV data, and the SN median RV can be used to estimate RV.
 

### 2018-06-08 manuscript.tex
Appendix updates

@@
 
-In this Appendix we present the same analysis as presented in Sec.~\ref{sec:4} for those four main-sequence stars: HD192310 (K2V), HD10700 (G8V), HD215152 (K3V) and finally Corot-7 (K0V).
-
-Table \ref{table:summaryStars} summarizes the results obtained by the SN fit and some of the results based on the Normal fit.
-The results are all consistent with the conclusions derived by the analyses on Alpha Centauri B.
-The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and RV or between the asymmetry parameters derived in \citet{Boisse-2009} and \citet{Figueira-2013} and RV for all the considered stars.
-The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV for three of the four stars.
-Also for all these stars we corrected the originally estimated RVs from spurious variations in RVs caused by stellar activity, using Eq.
+In this Appendix, a similar analysis as presented in Sec.~\ref{sec:4} is discussed for four main-sequence stars: HD192310 (K2V), HD10700 (G8V), HD215152 (K3V) and finally Corot-7 (K0V).
+\jessi{Are there papers that can/should be cited here for the datasets used?}
+
+Table~\ref{table:summaryStars} summarizes the results obtained by the SN and Normal models. 
+These results are consistent with those from the analysis of Alpha Centauri B. 
+The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and Normal mean RV or between the asymmetry parameters derived in \citet{Boisse-2009} and \citet{Figueira-2013} and RV \jessi{was the RV for these other asymmetry papers the Normal mean RV?} for all the considered stars.
+The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV \jessi{N mean RV?} for three of the four stars.
+Also for all these stars the originally estimated RVs were corrected from spurious variations in RVs caused by stellar activity using Eq.
 \ref{eq:RV:correction}.
-Fig.
-\ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RVs.
-While the Normal and SN residuals, once corrected for stellar activity, are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$, the results of the analyses on $\text{HD}215152$ and Corot-7, whose measurements have lower SNR with respect to the previous two analyzed stars, suggest that the residuals for the Normal are 0.05 and 0.34\,\ms\,higher than the residuals retrieved with the SN analysis, respectively.
+Fig. \ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RVs. 
+The stellar activity-corrected Normal and SN residuals are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$.
+However, the rms of the residuals for $\text{HD}215152$ are 0.05\,\ms lower for the SN model than the Normal model, and the rms of the residuals for Corot-7 are 0.34\,\ms lower.
+$\text{HD}215152$ and Corot-7 have  lower SNR than the other two analyzed stars.
+\jessi{was the SNR of the four stars stated anywhere?
+If not, if we want to keep the last point, we should note what the SNR of the stars are.}
 

### 2018-06-08 manuscript.tex
figure caption  updates

@@
    \caption{Density function of a random variable Y following the SN distribution $SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
-Note that the solid black line has an $\alpha = 0$, making it a Normal distribution.}
+Note that the solid black line has an $\alpha = 0$ making it a Normal distribution.}
    \label{fig:SN.plot}
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
-\caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line) or SN median RV (cyan dots-dashed line).
-In this case, the CCFs have been generated using SOAP 2.0, considering an equatorial 3\% faculae on the simulated Sun.
+\caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line), and SN median RV (cyan dots-dashed line).
+In this case, the CCFs were generated using SOAP 2.0 with an equatorial 3\% facula on the simulated Sun.
 The star does one full rotation between phase -0.5 and 0.5, with the facula being seen face-on for phase $0$.
-The variations observed in SN mean RV are quite different from the variations measured in SN median RV and N mean RV.
+The variations observed in SN mean RV are notably different from the variations measured in SN median RV and N mean RV.
 }
@@
 \includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
-   \caption{\emph{Left:} Correlations between the different asymmetry parameters and their corresponding RVs estimates in the case of an equatorial 3\% faculae on the simulated Sun.
-\emph{Right:} Correlations between the different width parameters and their corresponding RVs estimates for the same facula.
+   \caption{(left) Correlations between the different asymmetry parameters and their corresponding RV estimates in the case of an equatorial 3\% facula on the simulated Sun.
+(right) Correlations between the different width parameters and their corresponding RV estimates for the same facula.
    In the presence of a facula, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations.}
@@
 \includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{(top) The spurious RVs (black dots) caused by a facula in the simulated data using a Normal and a SN fit, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+   \caption{(top) The spurious estimated RVs (black dots) caused by a facula in the simulated data using a Normal and a SN fit, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses), and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
    %
  (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
-std--red crosses) and the residuals from the usual correction (Usual corr.
-std--green triangles).
+std, red crosses) and the residuals from the usual correction (Usual corr.
+std, green triangles).
 The residuals have a smaller systematic component when using the proposed model of
@@
 \begin{center}
-\caption{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction from stellar activity induced by an equatorial 3\% facula on the simulated Sun.
-All the parameters corresponding to the Normal or SN variables are statistically significant to explain the spurious RV variations caused by a facula.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability seen in the different RV estimates.}
+\caption{P--values for the estimated coefficients from the model in Eq.~\ref{eq:RV:correction} for correcting stellar activity induced by an equatorial 3\% facula on the simulated Sun.
+All the parameters corresponding to the Normal or SN variables are statistically significant to explain the spurious RV variations caused by the facula.
+The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability present in the different RV estimates.}
 \label{table:faculae.test}
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
-\caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line) or SN median RV (cyan dots-dashed line).
-In this case, the CCFs have been generated using SOAP 2.0, considering an equatorial 1\% spot on the simulated Sun.
-The star do one full rotation between phase -0.5 and 0.5, with the spot being seen face-on for phase 0.
+\caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line) or SN median RV (cyan dots-dashed line) using CCFs generated from SOAP 2.0 with an equatorial 1\% spot on the simulated Sun.
+The star does one full rotation between phase -0.5 and 0.5, with the spot being seen face-on for phase 0.
 SN mean RV seems to have the smallest spurious variations caused by the spot.}
@@
 \includegraphics[height = 6in]{SOAP_SPOT_Comparison_para_SN.pdf} 
-   \caption{\emph{Left:} Correlations between the different asymmetry parameters and their corresponding RV estimates in the case of an equatorial 1\% spot on the simulated Sun.
-\emph{Right:} Correlations between the different width parameters and their corresponding RV estimates for the same spot.
+   \caption{(left) Correlations between the different asymmetry parameters and their corresponding RV estimates in the case of an equatorial 1\% spot on the simulated Sun.
+(right) Correlations between the different width parameters and their corresponding RV estimates for the same spot.
 In the presence of a spot, both the shape and the width of the CCF change as the star rotates.
 However, only the asymmetry produces a statistically significant correlation with the different RV estimates.
-In the case of the correlation between the width parameters and their corresponding RV estimates the data produces a circle, meaning that those two quantities are not varying in phase.}
+In the case of the correlation between the width parameters and their corresponding RV estimates the data produces a circle, meaning that those two quantities are not varying in phase.
+\jessi{why would you say the two quantities are not varying in phase?
+they clearly are changing with phase...(?)}}
     \label{fig:spot.corr}
@@
 \includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{(top) The spurious RVs (black dots) caused by a spot in the simulated data using a Normal and a SN fit, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+   \caption{(top) The spurious estimated RVs (black dots) caused by a spot in the simulated data, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
    %
  (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
-std--red crosses) and the residuals from the usual correction (Usual corr.
-std--green triangles).The residuals have a smaller systematic component when using the proposed model of
+std, red crosses) and the residuals from the usual correction (Usual corr.
+std, green triangles).
+The residuals have a smaller systematic component when using the proposed model of
   Eq.~\ref{eq:RV:correction} (red crosses) compared to the usual model (green triangles).
@@
 \begin{center}
-\caption{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun and a planet with period one third of the rotational period and semi-amplitude 10\,\ms.
+\caption{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun, and a planet with period one third of the rotational period and a semi-amplitude 10\,\ms.
 All the parameters corresponding to the Normal or SN variables are statistically significant to explain the spurious RV variations caused by this spot plus planet, except for the width of the CCF.
-Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.}
+Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.
+\jessi{is there a reason the actual model,  \eqref{eq:RV:correction.overall}, with the Doppler shift was not references?}}
 \label{table:spotplanet.test}
@@
 \includegraphics[height = 3.6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
-   \caption{\emph{Left: }Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
+   \caption{(left) Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
 As we can see with the strong correlation, those two parameters measure the CCF asymmetry in the same way.
-\emph{Top right:} RVs as function of Julian Day for Alpha Centauri B in 2010.
+(top right) RVs as function of Julian Day for Alpha Centauri B in 2010.
 The RVs are retrieved using the mean of a Normal fitted to the CCF (red triangles), or the mean (black circles) or median (cyan crosses) of a SN density fitted to the CCF.
-\emph{Bottom right:} RV differences between the RVs derived when using the SN density and the RV derived when using the Normal density.}
+(bottom right) RV differences between the RVs derived when using the SN density and the RV derived when using the Normal density.}
    \label{fig:alphacent:corr.gamma}

### 2018-06-08 manuscript.tex
figure caption  updates

@@
 \includegraphics[height = 6in]{SOAP_SPOT_PLANET_Comparison_para_SN.pdf} 
-   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a spot is present on the photosphere of the star and a planet is injected.
-The shape of the CCF changes as the spot moves, producing statistically significative correlations only between the RVs and the asymmetry parameter.
-The correlations between the RVs and the width parameter of the CCF is weaker than the previous case that considers only the presence of a spot on the photosphere of the star.}
+   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters of the simulated data with a 1\% spot and an injected planetary signal.
+The shape of the CCF changes as the spot moves, producing statistically significant correlations only between the estimated RVs and the asymmetry parameter.
+The correlations between the estimated RVs and the width parameter of the CCF is weaker than the case with only a spot.}
     \label{fig:spot.plus.planet.corr}
@@
 
-In this Section we present the analysis conducted on the star Alpha Centauri B, comparing the result of fitting a CCF using the SN density defined in Sec.
+In this Section we present the analysis conducted on the star Alpha Centauri B (Alpha Cen B), comparing the result of fitting a CCF using the SN density defined in Sec.
 \ref{sec:3} with the usual approach based on fitting a Normal density for estimating the RV and asymmetry of the CCF.
@@
 \includegraphics[height = 3.6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
-   \caption{(left) Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
-As we can see with the strong correlation, those two parameters measure the CCF asymmetry in the same way.
+   \caption{(left) Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B. The strong correlation suggests these two parameters are similarly measuring the asymmetry.
 (top right) RVs as function of Julian Day for Alpha Centauri B in 2010.
-The RVs are retrieved using the mean of a Normal fitted to the CCF (red triangles), or the mean (black circles) or median (cyan crosses) of a SN density fitted to the CCF.
-(bottom right) RV differences between the RVs derived when using the SN density and the RV derived when using the Normal density.}
+The RVs are estimated using the mean of a Normal fitted to the CCF (red triangles), or the mean (black circles) or median (cyan crosses) of a SN density fitted to the CCF.
+(bottom right) Differences between the RVs estimated with the SN density and those from the Normal density.}
    \label{fig:alphacent:corr.gamma}
@@
 \includegraphics[height = 6in]{HD12862_[4]Comparison_para.pdf}  
-   \caption{Correlations between the asymmetry parameters and their corresponding RVs for Alpha Centauri B.
-The last three plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN (SN mean RV and SN median RV) and the Normal fits.
-The correlations are always stronger when using parameters derived from the SN fit than the Normal one.
-The p--values associated with each $R$ is statistically different from $0$.}
+   \caption{(top three rows) Correlations between the asymmetry parameters and their corresponding estimated RVs for Alpha Centauri B. 
+(bottom row) The correlation between the FWHM and the estimated RVs for Alpha Centauri B.
+The correlations are stronger when using parameters derived from the SN fit than the Normal one.
+The estimated $R$'s are all statistically significant.}
    \label{fig:alphacent:corrPlot}
@@
  (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
-std--black dots) and the residuals from the usual correction (Usual corr.
-std--blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+std, black dots) and the residuals from the usual correction (Usual corr.
+std, blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
 The residuals have a smaller systematic component when using the proposed model of
-  Eq.~\ref{eq:RV:correction} (black dots) compared to the usual model (blue triangles).}
+  Eq.~\ref{eq:RV:correction} (black dots) compared to the usual model (blue triangles). \jessi{The bottom plot has black triangles rather than black dots...}}
    \label{fig:alphacent:correctionRV}
@@
 \caption{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction from stellar activity in Alpha Cen B data.
-All the variables corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by stellar activity, except for the asymmetry of the CCF when using the Normal parameters (BIS SPAN).
+All the variables corresponding to the Normal or SN parameters are statistically significant, except for the asymmetry of the CCF when using the BIS SPAN with the N mean RV.
 The evaluation of the $R^2$ shows that the proposed linear combination better explains variations in RVs due to the stellar activity when the RVs are derived using SN mean RV.}

### 2018-06-08 manuscript.tex
appendix figure caption  updates

@@
 \includegraphics[height = 6in]{HD12862_[4]Comparison_para.pdf}  
-   \caption{(top three rows) Correlations between the asymmetry parameters and their corresponding estimated RVs for Alpha Centauri B. 
+   \caption{(top three rows) Correlations between the asymmetry parameters and their corresponding estimated RVs for Alpha Cen B. 
 (bottom row) The correlation between the FWHM and the estimated RVs for Alpha Centauri B.
@@
 \includegraphics[height = 2.6in]{detection_limits.pdf} 
-   \caption{Detection limits of planetary signals once we have removed from the raw RVs the linear combination of CCF parameters proposed in Eq.~\ref{eq:RV:correction} to correct for stellar activity.
-As we can see, when considering the different parametrization for the RV: N mean RV, SN mean RV and SN median RV, we arrive to very similar detection limits.}
+   \caption{Detection limits of planetary signals once the stellar activity signal is removed from the raw RVs using the model proposed in  Eq.~\ref{eq:RV:correction}.
+\jessi{For the black-and-white versions, it would be helpful to have different line types plotted}
+The different RV estimators have similar detection limits.}
    \label{fig:detection_limits}
@@
 \includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
-   \caption{\jessi{The stars used should be noted here}  Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM, and the asymmetry parameters.
-When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved when fitting a Normal density (red triangles).
+   \caption{\jessi{The stars used should be noted here}  Comparison between the standard errors from the bootstrap analysis of the estimated RVs, FWHM, and asymmetry parameters.
+When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors of N mean RV (red triangles).
 However, the standard errors for SN median RV (cyan crosses) are on average $10\%$ smaller than the standard errors coming from the N mean RV.
@@
 \begin{table*}[!t]
-\caption{Subset of notable correlations between the asymmetry or the FWHM parameters and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.
+\caption{Notable correlations between the asymmetry or the FWHM parameters and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.
 The complete results of the analyses of the correlations for the four stars are presented in Fig.
@@
 \includegraphics[height = 6in]{HD19231_[4]Comparison_para.pdf} 
-   \caption{Correlations between the asymmetry parameters and their corresponding RVs for $\text{HD}192310$.
-The last three plots show the correlation between the FWHM and the RVs for $\text{HD}192310$ using respectively the SN (SN mean RV and SN median RV) and the Normal fits.
-The correlations are always stronger when using parameters derived from the SN fit than the Normal one.
-The p--values associated with each $R$ are statistically different from $0$.}
+   \caption{(top three rows) Correlations between the asymmetry parameters and their corresponding RVs for $\text{HD}192310$.  
+   (bottom row) Correlations between the FWHM and the estimated RVs. 
+   The correlations are consistently stronger when using parameters derived from the SN than the Normal. The estimated $R$ are all statistically significant.}   
    \label{fig:Gliese785:corrPlot}
@@
 \includegraphics[height = 6in]{HD10700_[4]Comparison_para.pdf}  
-   \caption{Correlations between the asymmetry parameters and their corresponding RVs for $\text{HD}10700$.
-The last three plots show the correlation between the FWHM and the RVs for $\text{HD}10700$ using respectively the SN (SN mean RV and SN median RV) and the Normal fits.
-The correlations between the asymmetry parameters and their corresponding RVs are stronger when using the parameter SN mean RV obtained from the SN fit than the Normal one.
-The correlation between the FWHM and the RVs is, only for this quiet star, stronger when using the parameter retrieved with the Normal distribution.
-The p--values associated with each $R$ are statistically different from $0$, except for the correlation between FIG BIS- and RV (p--values=0.36).}
+   \caption{(top three rows) Correlations between the asymmetry parameters and their corresponding RVs for $\text{HD}10700$. 
+(bottom row) Correlations between the FWHM and the RVs for $\text{HD}10700$. 
+The correlations between the asymmetry parameters and their corresponding RVs are stronger when using the SN mean RV compared to N mean RV. 
+The correlation between the FWHM and the N mean RV, only for this quiet star, is stronger the the analogous correlations with the estimated SN RVs.
+The estimated $R$ are statistically significant, except for the correlation between FIG BIS and RV (p--values=0.36).}
    \label{fig:Tau:corrPlot}
@@
 \includegraphics[height = 6in]{HD21515_[4]Comparison_para.pdf}  
-   \caption{Correlations between the asymmetry parameters and their corresponding RVs for $\text{HD}215152$.The last three plots show the correlation between the FWHM and the RVs for $\text{HD}215152$ using respectively the SN (SN mean RV and SN median RV) and the Normal fits.
-The correlations between the asymmetry parameters and their corresponding RVs are stronger when using the parameter SN mean RV obtained from the SN fit than the Normal one.
-The p--values associated with each $R$ are, from the top to the bottom, from the left to the right: $2.2e-16,0.02,0.27, 0.05 ,7e-4,1e-5,1e-5,0.0007,0.0004,0.5,0.2$.}
+   \caption{(top three rows) Correlations between the asymmetry parameters and their corresponding RVs for $\text{HD}215152$. 
+(bottom row) Correlations between the FWHM and the RVs for $\text{HD}215152$. 
+The correlations are consistently stronger when using SN mean RV compared to N mean RV.
+The p--values associated with each $R$ are, from the top to the bottom, from the left to the right: $2.2e-16,0.02,0.27, 0.05 ,7e-4,1e-5,1e-5,0.0007,0.0004,0.5,0.2$.
+\jessi{It is probably best to just note the ones that do not have statistically significant p-values...}}
    \label{fig:HD215152:corrPlot}
@@
 \includegraphics[height = 6in]{LRa01_E_[4]Comparison_para.pdf} 
-   \caption{Correlations between the asymmetry parameters and their corresponding RVs for $\text{Corot }7$.
-The last three plots show the correlation between the FWHM and the RVs for $\text{Corot }7$ using respectively the SN (SN mean RV and SN median RV) and the Normal fits.
-The correlations between the asymmetry parameters and their corresponding RVs are stronger when using the parameter SN mean RV obtained from the SN fit than the Normal one.
+   \caption{(top three rows) Correlations between the asymmetry parameters and their corresponding RVs for $\text{Corot }7$. 
+(bottom row) Correlations between the FWHM and the RVs for $\text{Corot }7$.
+The correlations are consistently stronger when using SN mean RV compared to N mean RV.
 The p--values associated with each $R$ are, from the top to the bottom, from the left to the right: $2.2e-16,2e-5,0.23,0.11,0.0055,0.0025,0.012,0.002,2.2e-16,2.2e-16,2.2e-16$.
-}
+\jessi{maybe just note the ones that are not statistically significant.}}
    \label{fig:Corot7:corrPlot}

### 2018-06-08 manuscript.tex
appendix figure caption  updates

@@
 (bottom row) Correlations between the FWHM and the RVs for $\text{HD}10700$. 
-The correlations between the asymmetry parameters and their corresponding RVs are stronger when using the SN mean RV compared to N mean RV. 
-The correlation between the FWHM and the N mean RV, only for this quiet star, is stronger the the analogous correlations with the estimated SN RVs.
+The correlations are consistently stronger when using SN mean RV compared to N mean RV for the asymmetry parameters; however, the correlation between the FWHM and the N mean RV, only for this quiet star, is stronger the the analogous correlations with the estimated SN RVs.
 The estimated $R$ are statistically significant, except for the correlation between FIG BIS and RV (p--values=0.36).}
@@
 (bottom row) Correlations between the FWHM and the RVs for $\text{Corot }7$.
-The correlations are consistently stronger when using SN mean RV compared to N mean RV.
+The correlations are consistently stronger when using parameters derived from the SN than the Normal.
 The p--values associated with each $R$ are, from the top to the bottom, from the left to the right: $2.2e-16,2e-5,0.23,0.11,0.0055,0.0025,0.012,0.002,2.2e-16,2.2e-16,2.2e-16$.

### 2018-06-08 manuscript.tex
appendix figure caption  updates

@@
 std--blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
-The residuals for both the proposed correction from stellar activity are comparable.}
+The residuals for both the proposed correction from stellar activity are comparable.
+ \jessi{black triangles on bottom row need to be updated to circles throughout the appendix}
+ }
    \label{fig:HD192310:correctionRV}
@@
 std--blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
-The residuals have a smaller systematic component when using the proposed model of Eq.~\ref{eq:RV:correction} (black dots) compared to the usual model (blue triangles) Moreover, once corrected from stellar activity using Eq.
-\ref{eq:RV:correction}, the systematic component using the SN is $0.334$ \ms smaller than the one retrieved with the Normal analysis.}
+The residuals have a smaller systematic component when using the proposed model of Eq.~\ref{eq:RV:correction} (black dots) compared to the usual model (blue triangles).
+Moreover, once corrected for stellar activity using Eq.
+\ref{eq:RV:correction}, the remaining std from the SN models are $0.334$ \ms smaller than the remaining std of the Normal model.}
    \label{fig:Corot-7:correctionRV}

### 2018-06-08 manuscript.tex
Add files via upload
updated part of Jessi's comments. to be finished

@@
 
-\jessi{What is going on with the following paragraph?
-why is "(top)" and "(bottom)" appearing?
-Was this intended for a caption?
-These should not appear in the body of the text - only captions} (top) The spurious RVs (black dots) caused by a spot in the simulated data using a Normal and a SN fit, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$.
-   %
- (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
-std) and the residuals from the usual correction (Usual corr.
-std), obtained fitting the function $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$.
-The residuals have a smaller systematic component when using the proposed model of
-  Eq.~\ref{eq:RV:correction} (red crosses) compared to the usual model (green triangles).
-The tests of statistical significance on the parameters are presented in Table \ref{table:spot.test}.
-
 \begin{table}
@@
 The residuals have a smaller systematic component when using the proposed model of
-  Eq.~\ref{eq:RV:correction} (black dots) compared to the usual model (blue triangles). \jessi{The bottom plot has black triangles rather than black dots...}}
+  Eq.~\ref{eq:RV:correction} (black dots) compared to the usual model (blue triangles).}
    \label{fig:alphacent:correctionRV}
@@
 
-The standard errors were also computed for each CCF parameter for all the CCFs of HD215152, HD192310 and Corot-7. \jessi{Why weren't the others stars included?}
+The standard errors were also computed for each CCF parameter for all the CCFs of HD215152, HD192310 and Corot-7.
+\jessi{Why weren't the others stars included?} \umberto{because the computational time for Tau Ceti and Alpha Cent was much longer (there are much more CCF's).}
 This provides information on how the noise of each CCF parameter varies as a function of SNR, where the SNR measured at 550 nm on the original spectra varies between 10 and 500. 
@@
 Finally, for the asymmetry parameters, $\gamma$ has standard errors that are 15\% more precise than BIS SPAN. 
-In conclusion, when fitting a SN density to the CCF and using as RV estimates SN mean RV \jessi{I'm assuming you mean the median here?}, we are able to improve by 10\% the precision on the estimated RV, 15\% the precision on the estimated asymmetry, both without degrading the precision on the estimated width.
+In conclusion, when fitting a SN density to the CCF and using as RV estimates SN median RV, we are able to improve by 10\% the precision on the estimated RV, 15\% the precision on the estimated asymmetry, both without degrading the precision on the estimated width.
 SN mean RV should not be use to derive precise estimated RVs, except perhaps in specific conditions described below, as the precision on this parameter is 60\% worse than the precision on the RVs derived from N mean RV.
@@
 \includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
-   \caption{\jessi{The stars used should be noted here}  Comparison between the standard errors from the bootstrap analysis of the estimated RVs, FWHM, and asymmetry parameters.
+   \caption{\textit{Bootstrap analyses on the stars HD215152, HD192310 and Corot-7}.
+Comparison between the standard errors from the bootstrap analysis of the estimated RVs, FWHM, and asymmetry parameters.
 When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors of N mean RV (red triangles).
@@
 Also, the correlation between the asymmetry and the SN mean RV is always stronger than the parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
-\jessi{it may be helpful here to emphasize why it is better fr the parameters to be more sensitive to activity}
+\jessi{it may be helpful here to emphasize why it is better for the parameters to be more sensitive to activity}
 
@@
 These results are consistent with those from the analysis of Alpha Centauri B. 
-The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and Normal mean RV or between the asymmetry parameters derived in \citet{Boisse-2009} and \citet{Figueira-2013} and RV \jessi{was the RV for these other asymmetry papers the Normal mean RV?} for all the considered stars.
-The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and RV \jessi{N mean RV?} for three of the four stars.
+The correlation between $\gamma$ and SN mean RV is stronger than the correlation between the BIS SPAN and N mean RV or between the asymmetry parameters derived in \citet{Boisse-2009} and \citet{Figueira-2013} and N mean RV for all the considered stars.
+The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and N mean RV for three of the four stars.
 Also for all these stars the originally estimated RVs were corrected from spurious variations in RVs caused by stellar activity using Eq.
@@
 The residuals for both the proposed correction from stellar activity are comparable.
- \jessi{black triangles on bottom row need to be updated to circles throughout the appendix}
  }

### 2018-06-09 manuscript.tex
Add files via upload
updates majority of Jessi's comments. some of them left

@@
 However, only the asymmetry produces a statistically significant correlation with the different RV estimates.
-In the case of the correlation between the width parameters and their corresponding RV estimates the data produces a circle, meaning that those two quantities are not varying in phase.
-\jessi{why would you say the two quantities are not varying in phase?
-they clearly are changing with phase...(?)}}
+The width parameters and their corresponding RV estimates present weak correlations and in general much weaker correlations respect to the results obtained when an equatorial 3\% facula is present on the simulated Sun.}
     \label{fig:spot.corr}
@@
 The standard errors were also computed for each CCF parameter for all the CCFs of HD215152, HD192310 and Corot-7.
-\jessi{Why weren't the others stars included?} \umberto{because the computational time for Tau Ceti and Alpha Cent was much longer (there are much more CCF's).}
+\jessi{Why weren't the others stars included?} \umberto{because the computational time for Tau Ceti and Alpha Cent was much longer (there are much more CCF's).
+can we add the the SNR 'levels' are covered with the stars we used?}
 This provides information on how the noise of each CCF parameter varies as a function of SNR, where the SNR measured at 550 nm on the original spectra varies between 10 and 500. 
@@
    \caption{\textit{Bootstrap analyses on the stars HD215152, HD192310 and Corot-7}.
-Comparison between the standard errors from the bootstrap analysis of the estimated RVs, FWHM, and asymmetry parameters.
+(top) Comparison between the standard errors from the bootstrap analysis of the estimated RVs, FWHM, and asymmetry parameters using the SN fit and the common strategy (Normal fit and BIS SPAN).
+(bottom) Ratio between the standard errors retrieved on the parameters derived from the common strategy and the corresponding standard errors retrieved on the parameters derived from the SN fit.
 When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors of N mean RV (red triangles).
@@
 Note that for the asymmetry, the error in BIS SPAN is in \ms.
-To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.
-\jessi{it would be good to have a "(top)" and "(bottom)" noted here.}}
+To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
    \label{fig:se}
@@
 There could be several reasons for this difference.
-\jessi{First, it may be due to the fact that in SOAP 2.0 uses a variation of a spot template spectrum as the model rather than a facula template spectrum so the SOAP spectra with a facula is not accurately modeling this type of activity}.
+First, it may be due to the fact that in SOAP 2.0 uses a variation of a spot template spectrum as the model rather than a facula template spectrum so the SOAP spectra with a facula is not accurately modeling this type of activity.
 Because the temperature between a spot and a faculae is significantly different, their spectra should be different.
@@
 Also, the correlation between the asymmetry and the SN mean RV is always stronger than the parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
-\jessi{it may be helpful here to emphasize why it is better for the parameters to be more sensitive to activity}
+Since if an apparent RV signal is induced by activity generally a strong correlation will be observed between the RV and the FWHM of the CCF or its BIS SPAN, to use the SN density to fit the CCF leads to a better understanding of the spurious variations in RV caused by stellar activity.
 
@@
 Hence, the mean of the SN density appears to be more sensitive to variation in the CCF shape than the median of the SN or the mean of the Normal.
-This is not surprising as the SN density is able to model the asymmetry of the CCF, what the Normal density does not.
+%This is not surprising as the SN density is able to model the asymmetry of the CCF, what the Normal density does not.
 \jessi{The previous sentence does not follow from the points made in the paragraph.}
@@
 This is not necessarily a negative aspect. 
-Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring the SN mean RV, even if the white noise in the data is increased by 60\%.
-\jessi{white noise of the estimator?
-The previous two sentences are not very convincing to me.}
+Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring the SN mean RV, even if the uncertainties related to this parameter are increased by 60\%.
 
 Even if the different RV estimators generally have different amplitudes, once the new correction for stellar activity is applied, the residuals of the model have similar rms.
-This suggests that for an activity correction based on a linear combination of CCF parameters, the SN density fit does not help.
-\jessi{The previous sentence does not seem to be a good sentence...I'm not sure what the intent of it is so I'm not sure how to fix it.}
-When comparing the activity correction proposed in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, there appears to be only a slight improvement.
-\jessi{In the previous sentence, are you referring to the real data only?
-The SOAP data did show improvement - right?}
-We however encourage the community to use this new simple linear model if the goal is to reduce activity without considering the computationally expensive use of Gaussian Process.
-\jessi{The previous sentence makes no sense given the discussion in this paragraph.
-You are saying the proposed correction doesn't help, and then you say to use it...}
+When comparing the activity correction proposed in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, for the simulations based on the presence of a facula or a spot the new proposed correction almost entirely explains the spurious variations in RV.
+However, when moving to real data, there is just a slight improvement by using the proposed correction function for stellar activity.
+Anyway, we encourage the community to use this new simple linear model if the goal is to reduce activity without considering the computationally expensive use of Gaussian Process.
 A further analysis of the p--value for each coefficient can be performed to see the ones that are not relevant and that can therefore be removed.
@@
 The correlations are consistently stronger when using SN mean RV compared to N mean RV.
-The p--values associated with each $R$ are, from the top to the bottom, from the left to the right: $2.2e-16,0.02,0.27, 0.05 ,7e-4,1e-5,1e-5,0.0007,0.0004,0.5,0.2$.
-\jessi{It is probably best to just note the ones that do not have statistically significant p-values...}}
+The p--values associated with each $R$ are not statistically significant for the correlation between N mean RV and BIS SPAN (p--values=0.27), the correlation between N mean RV and FIG BIS- (p--values=0.05),  the correlation between SN median RV and SN FWHM (p--values=0.5) and the correlation between N mean RV and FWHM (p--values=0.2).
+}
    \label{fig:HD215152:corrPlot}
@@
 The correlations are consistently stronger when using parameters derived from the SN than the Normal.
-The p--values associated with each $R$ are, from the top to the bottom, from the left to the right: $2.2e-16,2e-5,0.23,0.11,0.0055,0.0025,0.012,0.002,2.2e-16,2.2e-16,2.2e-16$.
-\jessi{maybe just note the ones that are not statistically significant.}}
+The p--values associated with each $R$ are not statistically significant for the correlation between N mean RV and BIS SPAN (p--values=0.23) and the correlation between N mean RV and FIG BIS- (p--values=0.11).}
    \label{fig:Corot7:corrPlot}

### 2018-06-11 manuscript.tex
responded to/revised some comments

@@
 can we add the the SNR 'levels' are covered with the stars we used?}
+\jessi{How much longer would it take to include these?  Can we run them on an HPC?  At the very least we should note why they are not included}
 This provides information on how the noise of each CCF parameter varies as a function of SNR, where the SNR measured at 550 nm on the original spectra varies between 10 and 500. 
@@
 These reasons could also be responsible for the general differences observed in the behavior of the mean and the median of the SN between the SOAP 2.0 data and real data.
-\jessi{regarding the previous statement, would you say that there are also difference in the N mean RV generally between the SOAP and real data?
+\jessi{regarding the previous statement, would you say that there are also differences in the N mean RV generally between the SOAP and real data?
 I wonder if that could somehow be tied in?

### 2018-06-12 manuscript.tex
Answered to comments

--- 2018-06-09 manuscript.tex
@@
 All the parameters corresponding to the Normal or SN variables are statistically significant to explain the spurious RV variations caused by this spot plus planet, except for the width of the CCF.
-Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.
-\jessi{is there a reason the actual model,  \eqref{eq:RV:correction.overall}, with the Doppler shift was not references?}}
+Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.}
 \label{table:spotplanet.test}
@@
 
-In this section, we investigate how the noise of the CCF influences the CCF parameters derived either by a Normal density or a SN density fit. 
-\jessi{Should we note that the CCF noise is from the photon-noise of the spectra?  Is there more to ``noise'' in the previous sentence?}
+In this section, we investigate how the photon noise influences the CCF parameters derived either by a Normal density or a SN density fit. 
 Because a CCF is obtained from a cross-correlation, each point of a CCF is correlated with the other points.
@@
 
-The standard errors were also computed for each CCF parameter for all the CCFs of HD215152, HD192310 and Corot-7.
-\jessi{Why weren't the others stars included?} \umberto{because the computational time for Tau Ceti and Alpha Cent was much longer (there are much more CCF's).
-can we add the the SNR 'levels' are covered with the stars we used?}
-This provides information on how the noise of each CCF parameter varies as a function of SNR, where the SNR measured at 550 nm on the original spectra varies between 10 and 500. 
-The combined results for all the stars considered are displayed in Fig.~\ref{fig:se}. 
+The standard errors were computed for each CCF parameter for all the HARPS measurements of HD215152, HD192310 and Corot-7.
+\xavier{This analysis was not performed on HD10700 and Alpha Cen B due to the huge number of measurements, which would require several weeks of computation on a standard computer, but also because for the three stars analysed, the measurements cover all the range of SNR measured at 550 nm (SNR550) from 10 to 500, which represent a very low SNR and the saturation limit of the HARPS detector, respectively.}
+The variation of the noise for each CCF parameter as a function of SNR550 is displayed in Fig.~\ref{fig:se}.
 The top plots show the standard errors of the three different estimated RV's, the width, and the asymmetry estimates. 
@@
 
-The estimates for the RV all appear to follow a similar exponential decay.
-Although the results for three different stars are included in the plot, there do not appear to be any offsets in this decay, which implies that the SNR at 550 nm is the main contributor to the precision measured in RV.
-\jessi{The previous sentence does not make sense to me.
-Why would no offsets imply it is the main contributor in the precision?}
-This is not surprising as the three stars studied here are all main sequence K-dwarfs.
+The different RV estimates all appear to follow a similar exponential decay.
+\xavier{If we analyse each RV estimate individually, we see that all the measurements, even though from three different stars, follow the same curve.
+This implies that for the stars considered, the precision in each RV estimate is driven by the SNR of the analysed spectra.} This is not surprising as the three stars studied have very similar spectral types.
+They are all main sequence K-dwarfs.
 
@@
 
-Similar conclusions were reached with the real data as with the results of the SOAP 2.0 simulations regarding the strength of the correlation between the CCF asymmetry and the RV, as well as between the CCF width and the RV.
-However, the simulated data stronger asymmetry-RV correlation between $\gamma$ and SN median RV while the real data had stronger correlations between $\gamma$ and SN mean RV. 
-There could be several reasons for this difference.
-First, it may be due to the fact that in SOAP 2.0 uses a variation of a spot template spectrum as the model rather than a facula template spectrum so the SOAP spectra with a facula is not accurately modeling this type of activity.
+\xavier{The same conclusion found for the SOAP 2.0 simulations, i.e.
+that the correlation between the CCF asymmetry and the RV, as well as between the CCF width and the RV is stronger for the SN than the Normal parameters, still hold when analyzing real data.}
+However, the stronger asymmetry-RV correlation for the simulated data is between $\gamma$ and SN median RV, while it is between $\gamma$ and SN mean RV for the real data.
+There could be several reasons for this difference. It may be due to the fact that SOAP 2.0 uses the spectrum of a spot as input to model the stellar activity induced by a faculae.
 Because the temperature between a spot and a faculae is significantly different, their spectra should be different. 
 Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region.
-These reasons could also be responsible for the general differences observed in the behavior of the mean and the median of the SN between the SOAP 2.0 data and real data.
-\jessi{regarding the previous statement, would you say that there are also difference in the N mean RV generally between the SOAP and real data?
-I wonder if that could somehow be tied in?
-}
+\xavier{The fact that we also find significant differences between the simulated and real data for the correlations between BIS SPAN and N mean RV and between FWHM and N mean RV shows that the SOAP 2.0 simulation studied here are too simple to explain the complexity of stellar activity in real RV observations.}
 Nevertheless, in both the simulated and the real cases, the parameters derived from the SN are generally more sensitive to activity than the parameters derived from the Normal.
@@
 When using the new correction proposed in this paper to mitigate the effect from stellar activity and when assessing planetary detection based on a periodogram analysis, we find very similar detection limits for the three RV estimators presented in this paper.
-\jessi{Maybe to try another test to see if the proposed correction is helpful, the detection-limit test could be carried out with the usual correction and we can see if it does not performa s well.}
+\jessi{Maybe to try another test to see if the proposed correction is helpful, the detection-limit test could be carried out with the usual correction and we can see if it does not performa s well.}\xavier{Umberto, could you give me the residuals for new and usual correction ??
+or do you have to re generate everything ?}
 Therefore it seems that any of the RV estimate can be used to search for planetary signals.
@@
 In this Appendix, a similar analysis as presented in Sec.~\ref{sec:4} is discussed for four main-sequence stars: HD192310 (K2V), HD10700 (G8V), HD215152 (K3V) and finally Corot-7 (K0V).
-\jessi{Are there papers that can/should be cited here for the datasets used?}
+\xavier{All those data are public and were found on the ESO archive.
+We have an acknowledgement for that} \jessi{Are there papers that can/should be cited here for the datasets used?}
 
@@
 However, the rms of the residuals for $\text{HD}215152$ are 0.05\,\ms lower for the SN model than the Normal model, and the rms of the residuals for Corot-7 are 0.34\,\ms lower.
-$\text{HD}215152$ and Corot-7 have  lower SNR than the other two analyzed stars.
-\jessi{was the SNR of the four stars stated anywhere?
-If not, if we want to keep the last point, we should note what the SNR of the stars are.}
+\xavier{$\text{HD}215152$ and Corot-7 have in average a lower SNR at 550 nm than HD10700 and HD192310, 273, 207, 141 and 44, respectively.}
 

### 2018-06-12 manuscript.tex
section 6 revision

@@
 \xavier{This analysis was not performed on HD10700 and Alpha Cen B due to the huge number of measurements, which would require several weeks of computation on a standard computer, but also because for the three stars analysed, the measurements cover all the range of SNR measured at 550 nm (SNR550) from 10 to 500, which represent a very low SNR and the saturation limit of the HARPS detector, respectively.}
+\jessi{[My suggested revision] These three stars include measurements that cover the range of SNR measured at 550 nm (SNR550) from 10 to 500, which represent a very low SNR and the saturation limit of the HARPS detector, respectively.
+HD10700 and Alpha Cen B were not included because they have a large number of measurements, which would require a substantial computational effort.}
 The variation of the noise for each CCF parameter as a function of SNR550 is displayed in Fig.~\ref{fig:se}.

### 2018-06-12 manuscript.tex
section 6 revision

@@
 The different RV estimates all appear to follow a similar exponential decay.
-\xavier{If we analyse each RV estimate individually, we see that all the measurements, even though from three different stars, follow the same curve.
-This implies that for the stars considered, the precision in each RV estimate is driven by the SNR of the analysed spectra.} This is not surprising as the three stars studied have very similar spectral types.
+\xavier{Considering each RV estimate individually, it appears that all the measurements follow the same curve even though the measurements are from three different stars.
+This suggests that for the stars considered, the precision in each RV estimate may be driven by the SNR of the analyzed spectra.} This is not surprising as the three stars studied have very similar spectral types.
 They are all main sequence K-dwarfs.

### 2018-06-12 manuscript.tex
section 7 revision

@@
 
-\xavier{The same conclusion found for the SOAP 2.0 simulations, i.e.
-that the correlation between the CCF asymmetry and the RV, as well as between the CCF width and the RV is stronger for the SN than the Normal parameters, still hold when analyzing real data.}
+\xavier{The conclusion found for the SOAP 2.0 simulations that the correlation between the CCF asymmetry and the estimated RV, as well as between the CCF width and the estimated RV, is stronger for the SN than the Normal parameters also holds when analyzing real data.
+} \jessi{I mildly revised Xavier's statement}
+%
 However, the stronger asymmetry-RV correlation for the simulated data is between $\gamma$ and SN median RV, while it is between $\gamma$ and SN mean RV for the real data.
-There could be several reasons for this difference. It may be due to the fact that SOAP 2.0 uses the spectrum of a spot as input to model the stellar activity induced by a faculae.
+There could be several reasons for this difference. It may be due to the fact that SOAP 2.0 uses the spectrum of a spot as input to model the stellar activity induced by a facula.
 Because the temperature between a spot and a faculae is significantly different, their spectra should be different. 
@@
 \xavier{The fact that we also find significant differences between the simulated and real data for the correlations between BIS SPAN and N mean RV and between FWHM and N mean RV shows that the SOAP 2.0 simulation studied here are too simple to explain the complexity of stellar activity in real RV observations.}
+\jessi{What are these differences for Normal case?
+The specific difference for the SN is the strength of the correlations with the SN mean RV compared to the SN median RV.
+When I look at the SOAP vs.
+real data for the Normal, I do not notice anything specifically different other than different patterns, but that is not surprising.}
 Nevertheless, in both the simulated and the real cases, the parameters derived from the SN are generally more sensitive to activity than the parameters derived from the Normal.

### 2018-06-12 manuscript.tex
Add files via upload
Slightly edited abstract. Small changes on last comment in the Appendix

@@
 {Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
-Stellar activity can be probed by measuring time dependent variations in the shape of the cross-correlation function (CCF), often estimated using different parameters of the modeled CCF.
-Therefore estimating the moments of the CCF with high precision is essential to de-correlate the signal of an exoplanet from spurious RV signals originating from stellar activity.}
+Stellar activity can be probed by measuring time dependent variations in the shape of the cross-correlation function (CCF), often estimated using different parameters of the modelled CCF.
+Therefore to estimate the parameters of the CCF with high precision is essential to de-correlate the signal of an exoplanet from spurious RV signals caused by stellar activity.}
 %
@@
 %
-{When considering real observations, the correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are stronger when using the parameters estimated with the SN rather than the ones obtained with the commonly employed Normal density.
-In particular the strongest correlations have been obtained when using as RV estimate the  mean of the SN.
-This suggests that the asymmetry of the CCF and the width of the CCF estimated using a SN density may be more sensitive to stellar activity, which can be helpful when estimating stellar rotational periods and generally for characterizing stellar activity signals.
-The estimated uncertainties in the measured RVs using the proposed SN approach and as RV estimate the median of the SN are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
-The estimated uncertainties on the asymmetry parameter of the SN are on average $15\%$ smaller than the uncertainties measured on the Bisector Inverse Slope Span (BIS SPAN), which is the commonly parameter used to evaluate the asymmetry of the CCF.
+{When considering real observations, the correlation between the RV and the asymmetry of the CCF and the correlation between the RV and the width of the CCF are stronger when using the parameters estimated with the SN rather than the ones obtained with the commonly employed Normal density.
+In particular the strongest correlations have been obtained when using as estimate for the RV the mean of the SN.
+This suggests that the asymmetry of the CCF and the width of the CCF estimated using a SN density may be more sensitive to stellar activity, which can be helpful when estimating stellar rotational periods and in general when characterizing stellar activity signals.
+Using the proposed SN approach, the uncertainties estimated on the RV defined as the median of the SN are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
+The uncertainties estimated on the asymmetry parameter of the SN are on average $15\%$ smaller than the uncertainties measured on the Bisector Inverse Slope Span (BIS SPAN), which is the commonly parameter used to evaluate the asymmetry of the CCF.
 }
-{We strongly encourage the use of the SN distribution to retrieve the different parameters of the CCF as the correlations used to probe stellar activity are stronger and the measure of the RV and the CCF asymmetry are more precise.
+{We strongly encourage the use of the SN densitty to retrieve the different parameters of the CCF since the correlations used to probe stellar activity are stronger than the ones retrieved by the common approach and because the estimation of RV and CCF asymmetry parameters are more precise.
 }
@@
 The standard errors were computed for each CCF parameter for all the HARPS measurements of HD215152, HD192310 and Corot-7.
-\xavier{This analysis was not performed on HD10700 and Alpha Cen B due to the huge number of measurements, which would require several weeks of computation on a standard computer, but also because for the three stars analysed, the measurements cover all the range of SNR measured at 550 nm (SNR550) from 10 to 500, which represent a very low SNR and the saturation limit of the HARPS detector, respectively.}
-\jessi{[My suggested revision] These three stars include measurements that cover the range of SNR measured at 550 nm (SNR550) from 10 to 500, which represent a very low SNR and the saturation limit of the HARPS detector, respectively.
-HD10700 and Alpha Cen B were not included because they have a large number of measurements, which would require a substantial computational effort.}
+These three stars include measurements that cover the range of SNR measured at 550 nm (SNR550) from 10 to 500, which represent a very low SNR and the saturation limit of the HARPS detector, respectively.
+HD10700 and Alpha Cen B were not included because they have a large number of measurements, which would require a substantial computational effort.
 The variation of the noise for each CCF parameter as a function of SNR550 is displayed in Fig.~\ref{fig:se}.
@@
 The different RV estimates all appear to follow a similar exponential decay.
-\xavier{Considering each RV estimate individually, it appears that all the measurements follow the same curve even though the measurements are from three different stars.
-This suggests that for the stars considered, the precision in each RV estimate may be driven by the SNR of the analyzed spectra.} This is not surprising as the three stars studied have very similar spectral types.
+Considering each RV estimate individually, it appears that all the measurements follow the same curve even though the measurements are from three different stars.
+This suggests that for the stars considered, the precision in each RV estimate may be driven by the SNR of the analyzed spectra.
+This is not surprising as the three stars studied have very similar spectral types.
 They are all main sequence K-dwarfs.
@@
 
-\xavier{The conclusion found for the SOAP 2.0 simulations that the correlation between the CCF asymmetry and the estimated RV, as well as between the CCF width and the estimated RV, is stronger for the SN than the Normal parameters also holds when analyzing real data.
-} \jessi{I mildly revised Xavier's statement}
+The conclusion found for the SOAP 2.0 simulations that the correlation between the CCF asymmetry and the estimated RV, as well as between the CCF width and the estimated RV, is stronger for the SN than the Normal parameters also holds when analyzing real data.
 %
@@
 real data for the Normal, I do not notice anything specifically different other than different patterns, but that is not surprising.}
+\umberto{I suggest to comment only about the differences for the SN case, since for the Normal I do not see differences between the analyses with SOAP2.0 and real stars.}
 Nevertheless, in both the simulated and the real cases, the parameters derived from the SN are generally more sensitive to activity than the parameters derived from the Normal.
@@
 When using the new correction proposed in this paper to mitigate the effect from stellar activity and when assessing planetary detection based on a periodogram analysis, we find very similar detection limits for the three RV estimators presented in this paper.
-\jessi{Maybe to try another test to see if the proposed correction is helpful, the detection-limit test could be carried out with the usual correction and we can see if it does not performa s well.}\xavier{Umberto, could you give me the residuals for new and usual correction ??
-or do you have to re generate everything ?}
+\jessi{Maybe to try another test to see if the proposed correction is helpful, the detection-limit test could be carried out with the usual correction and we can see if it does not performa s well.}
 Therefore it seems that any of the RV estimate can be used to search for planetary signals.
@@
 Fig. \ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RVs. 
-The stellar activity-corrected Normal and SN residuals are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$.
+Once corrected from stellar activity, the Normal and SN residuals are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$.
 However, the rms of the residuals for $\text{HD}215152$ are 0.05\,\ms lower for the SN model than the Normal model, and the rms of the residuals for Corot-7 are 0.34\,\ms lower.
 \xavier{$\text{HD}215152$ and Corot-7 have in average a lower SNR at 550 nm than HD10700 and HD192310, 273, 207, 141 and 44, respectively.}
+ \umberto{$\text{HD}215152$ and Corot-7 have in average a lower SNR at 550 nm than HD10700 and HD192310.
+The average SNR at 550 nm for the stars \text{HD}10700, \text{HD}192310, $\text{HD}215152$ and Corot-7 are respectively 273, 207, 141 and 44.} \umberto{I slightly modified this sentences.
+Can you please check Xavier it is correct?}
 

### 2018-06-13 manuscript.tex
Add files via upload
reviewed Secs 1,2,3

@@
 %
-{The performances of the proposed method are compared to the commonly employed Normal density, using both simulations and real observations, with different levels of activity and signal-to-noise ratio (SNR) levels.}
+{The performances of the proposed method are compared to the commonly employed Normal density using both simulations and real observations, with different levels of activity and signal-to-noise ratio (SNR) levels.}
 %We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (SNR) levels.
@@
 Using the proposed SN approach, the uncertainties estimated on the RV defined as the median of the SN are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
-The uncertainties estimated on the asymmetry parameter of the SN are on average $15\%$ smaller than the uncertainties measured on the Bisector Inverse Slope Span (BIS SPAN), which is the commonly parameter used to evaluate the asymmetry of the CCF.
+The uncertainties estimated on the asymmetry parameter of the SN are on average $15\%$ smaller than the uncertainties measured on the Bisector Inverse Slope Span (BIS SPAN), which is the commonly used parameter to evaluate the asymmetry of the CCF.
 }
-{We strongly encourage the use of the SN densitty to retrieve the different parameters of the CCF since the correlations used to probe stellar activity are stronger than the ones retrieved by the common approach and because the estimation of RV and CCF asymmetry parameters are more precise.
+{We strongly encourage the use of the SN density to retrieve the different parameters of the CCF since the correlations used to probe stellar activity are stronger than the ones retrieved by the common approach and because the uncertainties associated to the RV and the asymmetry of the CCF are both smaller than the ones retrieved by the commonly employed strategies.
 }
@@
 When working with radial-velocities data (RVs), one of the main limitations to the detection of small-mass exoplanets is no longer the precision of the instruments used, but the different sources of variability induced by the stars \citep[e.g.][]{Feng:2017aa, Dumusque:2017aa, Rajpaul-2015, Robertson-2014}.
-Stellar oscillations, granulation phenomena, and stellar activity can all induce apparent RV signals that are above the meter-per-second precision \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} reached by the best high-resolution spectrographs \citep[HARPS, HARPS-N,][]{Mayor-2003,Cosentino-2012}.
+Stellar oscillations, granulation phenomena, and stellar activity can all induce apparent RV signals that are above the meter-per-second (\ms) precision \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} reached by the best high-resolution spectrographs \citep[HARPS, HARPS-N,][]{Mayor-2003,Cosentino-2012}.
 %
@@
 
-One of the most challenging stellar signal to characterize and to correct for is the signal induced by stellar activity. 
+One of the most challenging stellar signals to characterize and to correct for are the signals induced by stellar activity. 
 Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, which can induce spurious RVs variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b, Borgniet-2015}.
-In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so create a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}.
+In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so creates a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}.
 However, on quiet GKM dwarfs, the main target for precise RVs measurements, stellar activity can induce signals of a few \ms.
-This corresponds physically to variations smaller than 1/100th of a pixel on the detector making the changing shape of the spectral lines challenging to detect.
+This corresponds physically to variations smaller than 1/100th of a pixel on the detector, making changing in the shape of the spectral lines challenging to detect.
 In order to measure such tiny variations, a common approach is to average the information of all the lines in the spectrum by cross correlating the stellar spectrum with a synthetic or an observed stellar template \citep[][]{Baranne-1996,Pepe-2002a, Anglada-Escude-2012}.
@@
 The barycenter is generally estimated by fitting a Normal density to the CCF and retaining its mean.
-Variations in line shape between different spectra, which indicate the presence of signals induced by stellar activity, are measured by analyzing the different moments of the CCF.
-Usually, the width of the CCF is estimated using the full-width half-maximum (FWHM) of the fitted Normal density, and its asymmetry by calculating the CCF bisector and measuring the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
+Variations in line shape between different spectra, which indicate the presence of signals induced by stellar activity, are measured by analyzing the different parameters of the CCF.
+Usually the width of the CCF is estimated using the full-width half-maximum (FWHM) of the fitted Normal density and its asymmetry by calculating the CCF bisector and measuring the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
 
@@
 
-If an apparent RV signal is induced by activity, generally a strong correlation will be observed between the RV and chromospheric activity indicators like \logrhk\,or H-$\alpha$ \citep{Boisse-2009,Dumusque-2012,Robertson-2014}, but also between the RV and the FWHM of the CCF or its BIS SPAN \citep[][]{Queloz-2001,Boisse-2009,Queloz-2009,Dumusque-2016a}.
-%
-It is therefore common now, that when fitting a Keplerian signal to a set of RVs to look for a planet, the model includes in addition linear dependancies with the \logrhk, the FWHM and the BIS SPAN \citep{Dumusque:2017aa,Feng:2017aa}.
+If a spurious RV signal is induced by activity, generally a strong correlation will be observed between the RV and chromospheric activity indicators like \logrhk\,or H-$\alpha$ \citep{Boisse-2009,Dumusque-2012,Robertson-2014}, but also between the RV and the FWHM of the CCF or its BIS SPAN \citep[][]{Queloz-2001,Boisse-2009,Queloz-2009,Dumusque-2016a}.
+%
+Therefore a common strategy nowadays used when fitting a Keplerian signal to a set of RVs searching for a planet consists in including in the model linear dependancies with the \logrhk, the FWHM and the BIS SPAN \citep{Dumusque:2017aa,Feng:2017aa}.
 %
@@
 Several indicators have been developed that are more sensitive to line asymmetry than the BIS SPAN.
-In \citet{Boisse-2011}, the authors develop $V_{span}$, which is the difference between the RV measured respectively by fitting a Normal density to the upper and the bottom part of the CCF.
+In \citet{Boisse-2011}, the authors developed $V_{span}$, which is the difference between the RV measured respectively by fitting a Normal density to the upper and the bottom part of the CCF.
 This CCF asymmetry parameter is shown to be more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR).
@@
 The authors were able to show that when using bi-Gauss, the amplitude in asymmetry is 30\% larger than when using BIS SPAN, therefore allowing the detection of lower levels of activity.
-They also demonstrated that $V_{asy}$ seems to be a better indicator of line asymmetry at high SNR, as its correlation with RV is more significant than any of the previously proposed asymmetry indictors.
+They also demonstrated that $V_{asy}$ seems to be a better indicator of line asymmetry at high SNR, as its correlation with RV is significantly stronger than any other correlation between the previously proposed asymmetry indicators and RV.
 
@@
 %
-In this paper we propose to use a Skew Normal (SN) density to estimate with a single fit of the CCF, the RV, the FWHM and the asymmetry of the CCF, as this function includes a skewness parameter \citep[][]{Azzalini1985}.
+In this paper we propose to use a Skew Normal (SN) density to estimate with a single fit of the CCF the RV, the FWHM and the asymmetry of the CCF, as this function includes a skewness parameter \citep[][]{Azzalini1985}.
 
@@
 The paper is organized as follow.
-In Sec.~\ref{sec:2} we introduce the SN density, describe its applicability for modeling the CCF, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF.
-%
-In Sec.~\ref{sec:31} we propose an expanded linear model to correct for stellar activity signals in RVs, which extends the linear models previously proposed for this purpose \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
+In Sec.~\ref{sec:2} we introduce the SN density, describe its applicability for modelling the CCF and study how the SN parameters relate to mean of the Normal density, the FWHM and the BIS SPAN of the CCF.
+%
+In Sec.~\ref{sec:31} we propose a linear model to correct for stellar activity signals in RVs, which extends the linear models previously proposed for this purpose \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
 %
@@
 %
-Sec.~\ref{sec:5} considers derived error bars for the different estimated CCF parameters, and finally a discussion of the results and conclusions are included in Secs.~\ref{sec:discu} and ~\ref{sec:conclu}, respectively.
+In Sec.~\ref{sec:5} error bars for the different estimated CCF parameters are retrieved.
+Finally the discussion of the results and the conclusions are presented, respectively, in Secs.~\ref{sec:discu} and ~\ref{sec:conclu}.
 
@@
 %
-where C is an unknown offset for the continuum of the CCF, A is the unknown amplitude of the CCF, some times referred to as the CCF contrast, and $\mu$, $\sigma^2$ and $\gamma$ are the mean, variance and skewness of the SN as defined above.
+where C is an unknown offset for the continuum of the CCF, A is the unknown amplitude of the CCF, sometimes referred to as the CCF contrast, and $\mu$, $\sigma^2$ and $\gamma$ are respectively the mean, the variance and the skewness of the SN as defined above.
 The values $x_1, \ldots, x_n$ are the different values of the x-axis of the CCF, generally in velocity units (e.g. \ms).
@@
 
-When fitting a Normal density to the CCF, the estimated mean of the model is used as the estimated RV, the FWHM of the Normal density\footnote{FWHM$=2\sqrt{2\ln2}\,\sigma$ with standard deviation $\sigma$} represents the width of the CCF.
-Because the Normal density is symmetric, the skewness is always equal to 0 so a separate approach is needed to estimate the skewness of the CCF.
+When fitting the commonly employed Normal density to the CCF, the estimated mean of the model is used as the estimated RV and the FWHM of the Normal density\footnote{FWHM$=2\sqrt{2\ln2}\,\sigma$ with standard deviation $\sigma$} represents the width of the CCF.
+Because the Normal density is symmetric, the skewness is not defined and therefore a separate approach is necessary to estimate the skewness of the CCF.
 An estimated skewness parameter is generally obtained by calculating the BIS SPAN of the CCF \citep[see Sect. \ref{intro}, and e.g.][]{Queloz-2001}. 
@@
 where $x$ and $y$ are two quantitative variables, $cov(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represent their standard deviations.
-A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided, along with a $95\%$ confidence interval for $R$ when needed.
+A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided.
 
@@
 Exoplanets only produce a pure RV signal.
-On the contrary, stellar activity, in particular the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.
+On the contrary, stellar activity, and in particular the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.
 To track these variations in the shape of the spectral lines, the general approach consists in using the FWHM, the BIS SPAN or other indicators such as those introduced in \citet{Boisse-2011} or \citet{Figueira-2013}, which provide information on the width and asymmetry of the CCF.
@@
 %Some people also include the \logrhk, however, \citet{Feng-2018} show that this is probably not a good choice as \logrhk and RV are not well correlated.
-We propose to add additional parameters in the model to correct for stellar activity: first the amplitude parameter A of the CCF, generally referred to as the CCF contrast, and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case).
+We propose to add additional parameters in the model to correct for stellar activity: first the amplitude parameter A of the CCF, generally referred to as the CCF contrast, and as second the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case).
 The stellar activity correction we propose can therefore be written as:
@@
 A detailed discussion of the topic can be found in the book by \citet{belsley1991}.
-In the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ between the asymmetry and width parameters and therefore, the problem of multicollinearity is avoided.
-Note that we investigated the statistical significant of the interaction term between $A$ and the width, and $A$ and the asymmetry of the CCF, however, those interaction were not relevant for accounting for stellar signal.
+In the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ between the asymmetry and width parameters and therefore the problem of multicollinearity is avoided.
+Note that we investigated the statistical significant of the interactions between respectively $A$ and the width of the CCF and $A$ and the asymmetry of the CCF; those two interactions were not relevant for accounting variations in $RV_{\text{activity}}$.
 
@@
 For a given configuration of spots and faculae on the stellar surface, SOAP 2.0 gives as output the simulated CCF as a function of rotational phase.
-The code also returns the RV and the FWHM by fitting a Normal density to the CCF, and the BIS SPAN by calculating the bisector of the CCF.
-SOAP 2.0 gives noiseless CCFs affected by stellar activity, which are used to compare the benefits of a SN density fit to the CCF compared to a Normal density fit.
+The code also returns the RV and the FWHM retrieved by fitting a Normal density to the CCF, and the BIS SPAN obtained by calculating the bisector of the CCF.
+SOAP 2.0 gives noiseless CCFs affected by stellar activity, which are used to compare the benefits of a SN density fit respect to a Normal density fit.
 
@@
 
-To see the impact of a facula on the different parameters of the CCF, we simulated the effect of an equatorial faculae
+To see the impact of a facula on the different parameters of the CCF, we simulated the effect of an equatorial facula
 %\jessi{Should a footnote be added here to explain that the SOAP 2.0 faculae are not simulated from actual faculae templates?} 
 of size 3\% relative to the visible stellar hemisphere.
-The faculae is face-on when the phase equals to 0.
+The facula is face-on when the phase equals to 0.
 Note that a 3\% faculae is relatively large for the Sun; at maximum activity, big faculae have generally a size of 1\% \citep[e.g.][]{Borgniet-2015}.
@@
 When looking at the statistical significance of the different parameters used for correcting activity in Table~\ref{table:alphacent.test}, we see that the intercept is not significant for any of the models, and BIS SPAN (coefficient $\beta_2$) does not statistically significantly help in explaining stellar activity when using the parameters derived from the Normal density fit.
-However all the other parameters in the Normal and SN cases are statistically significant for modeling stellar activity. 
+However all the other parameters in the Normal and SN cases are statistically significant for modelling stellar activity. 
 By analyzing the values of the coefficient of determination, $R^2$, we see that the model for the SN mean RV is able to capture the highest percentage of variability in the estimated RV. 

### 2018-06-13 manuscript.tex
Add files via upload
reviewed Secs. 1,2,3,4

@@
 
-For the simulations discussed below, a star similar to the Sun was modeled, with a solar disc of one solar radius seen equator-on, and with a stellar rotational period set to 25.0 days.
+For the simulations discussed below, a star similar to the Sun was modelled, with a solar disc of one solar radius seen equator-on, and with a stellar rotational period set to 25.0 days.
 The stellar effective temperature is set to 5778 K
@@
 Correlations between the different RV estimates and the different CCF asymmetry or width estimates are displayed in Fig.~\ref{fig:faculae.corr}.
-The strength of the correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are stronger than the correlations between BIS SPAN and RV, with Pearson correlation coefficient values of $R$=0.46, -0.67 and -0.09, respectively.
-For the width barycenter correlations, there is a stronger correlation between SN FWHM and SN mean RV compared to the one between FWHM and N mean RV, $R=0.98$ and 0.84, respectively.
-In this case however, the correlation between SN FWHM and SN median RV is smaller with $R=0.50$.
-This first analysis shows that in the case of a facula, using some parameters from the SN can lead to stronger correlation than the usual Normal parameters and therefore, the SN parameters may better probe stellar activity.
-We investigate this feature further in the next sections where we consider simulated data with a single spot and a spot plus a planet, and in Sec~\ref{sec:4} with real observations.
+The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are stronger than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of $R$=0.46, -0.67 and -0.09, respectively.
+Concerning the correlations between the different RV estimates and the different CCF width parameters, there is a stronger correlation between SN FWHM and SN mean RV ($R=0.98$) respect to the one between FWHM and N mean RV ($R=0.84$).
+In this case the correlation between SN FWHM and SN median RV is the weakest, with $R=0.50$.
+This first analysis shows that in the case of a facula, using some parameters from the SN can lead to stronger correlations than the ones obtained by the usual Normal parameters.
+Therefore, the SN parameters may better probe stellar activity.
+We investigate this feature further in the following two sections, where we consider simulated data with a single spot and a spot plus a planet, and in Sec~\ref{sec:4} with real observations.
 
@@
 
-Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a facula, we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its performance in this setting.
+Since the RV variations displayed in Fig.~\ref{fig:faculae} are caused only by stellar activity, in this case a facula, we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its performance in this setting.
 The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
-The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a $R^2$ of our model larger than 0.95.
+The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a $R^2$ of our model larger than $0.99$.
 In addition, the rms of the different estimates of the RV reduces from about 3 \ms before correction to values below 0.15 \ms after correction.
@@
 a linear combination of only the asymmetry and width parameter), we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2.
-Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that all the Sn or Normal parameters are relevant for the correction.
+Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that all the SN or Normal parameters are relevant for the correction.
 
@@
 Note that this is a large spot for the Sun, as in general large spots are more in the regime of 0.1\% \citep[e.g.][]{Borgniet-2015}.
-In Fig.~\ref{fig:spot}, we shows the barycentric variation of the CCF induced by this simulated spot.
+In Fig.~\ref{fig:spot}, we show the barycentric variations of the CCF induced by this simulated spot.
 In contrast to the case of the facula, all the different estimates of the CCF barycenter for the spot have the same shape in variation.
@@
 SN mean RV, SN median RV and N mean RV).
-The correlation between $\gamma$ and SN median RV is the strongest with a $R=0.94$, followed by the correlation BIS SPAN - N mean RV and $\gamma$ - SN mean RV, with $R=0.86$.
-Regarding the correlation between the width and the CCF barycenter, we note that the variation is seen as a circle in this parameter space and therefore no correlation is observed.
-Once again, like in the case of the facula, we see that some parameters of the SN gives stronger correlations than the Normal parameters.
+The correlation between $\gamma$ and SN median RV is the strongest ($R=-0.93$), followed by the correlation BIS SPAN - N mean RV ($R=-0.86$) and at last the correlation between $\gamma$ - SN mean RV ($R=-0.85$).
+Concerning the correlation between the width and the CCF barycenter, we note that the variations are seen as a circle in this parameter space and therefore no correlation is observed.
+Once again, like in the case of the facula, we see that some parameters of the SN gives stronger correlations respect to the Normal parameters.
 
@@
 
-As before, the originally RVs were corrected by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction} and in Table \ref{table:spot.test}. 
-Like for the faculae, the proposed correction is able, in the case of the spot, to almost model entirely the stellar activity signal when considering the SN or Normal parameters, with $R^2$ values for the linear combination larger than 0.99.
+As before, the originally RVs are corrected by using Eq.~\ref{eq:RV:correction}.
+The results of this correction are displayed in Fig.~\ref{fig:spot.correction}  and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:spot.test}.
+Like for the faculae, the proposed correction is able, in the case of the spot, to model almost entirely the stellar activity signal when considering the SN or Normal parameters, with $R^2$ values for the linear combination larger than 0.99.
 Looking at Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms, for any of the different RV estimates.
-When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.
-
-Looking at Table \ref{table:spot.test}, we see that the Normal or SN parameters appearing in Eq.~\ref{eq:RV:correction} are all statistically significant to explain the activity signal, except the width of the CCF when the RVs are derived with the mean or median of the SN density.
-This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
+When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the facula.
+
+Looking at Table \ref{table:spot.test}, we see that the Normal or SN parameters involved in Eq.~\ref{eq:RV:correction} are all statistically significant to explain the activity signal, except the width of the CCF when the RVs are derived with the mean or median of the SN density.
+%This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
 
@@
 
-The final simulation presented here includes a planetary signal influencing the CCF along with the 1\% spot modeled previously (see Sec.~\ref{sec:soap.spot}). 
-The purpose of this example is to check if we are able to disentangle these two different sources of variations when using the parameters derived using a Normal versus a SN fit to the CCF.
+The final simulation presented here includes a planetary signal influencing the CCF along with the 1\% spot modelled previously (see Sec.~\ref{sec:soap.spot}). 
+The purpose of this example is to check if we are able to disentangle these two different sources of variations when using the parameters derived using a Normal or a SN fit to the CCF.
 In this scenario the planet is injected with a semi-amplitude of 10 \ms with no eccentricity and with a period corresponding to one third of the stellar rotational period, i.e.
@@
 
-Fig.~\ref{fig:spot.plus.planet} shows the variation observed in the CCF barycenter parameters.
+Fig.~\ref{fig:spot.plus.planet} shows the variations observed in the CCF barycenter parameters.
 As in the case of the spot, all RV estimates show similar variations, with SN mean RV showing a slightly smaller amplitude.
@@
 The correlation between the different CCF parameters are displayed in Fig.~\ref{fig:spot.plus.planet.corr}. 
-The correlations are weaker than in the case of the spot due to the planet inducing changes in RV without affecting the width or asymmetry of the CCF.
-However, the strength of the correlations between the CCF asymmetry and RV are in the same order as with the spot-only model: $\gamma$--SN median RV has the highest correlation followed by BIS SPAN--N mean RV and then $\gamma$--SN mean RV, with $R$ values of $-0.84$, $-0.78$ and $-0.76$, respectively.
-The patterns seen in the width-RV phase space in Fig.~\ref{fig:spot.plus.planet.corr} follow a circle similar to the spot-only model, and no correlation is observed between those two parameters.
+The correlations are weaker than in the case of the spot due to the planet inducing changes in RV without affecting the width or the asymmetry of the CCF.
+However, the strength of the correlations between the CCF asymmetry parameters and RV are comparable with the ones obtained for the spot-only model: $\gamma$--SN median RV has the strongest correlation ($R=-0.84$), followed by the correlation between BIS SPAN--N mean RV (($R=-0.78$)) and finally by the correlation between $\gamma$--SN mean RV ($R=-0.75$).
+The patterns observed in the width-RV phase space correlations in Fig.~\ref{fig:spot.plus.planet.corr} follow a circle, similar to the spot-only model; no correlation is observed between those two parameters.
 
@@
 
-In order to correct the estimated RVs from the spurious variation caused by the spot, the proposed model for correcting the activity is added to a signal that takes into account the RV variation caused by a injected planet.
-The observed RV can therefore be modeled as a combination of the activity and planetary signals:
+In order to correct the estimated RVs from the spurious variation caused by the spot, the proposed model for correcting the activity is added to a signal that takes into account the RV variations caused by a injected planet.
+The observed RVs can therefore be modelled as a combination of the activity and the planetary signals:
 %
@@
 %
-where $RV_{\text{activity}}$ can be found in Eq.~\ref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case with no eccentricity, can be modeled by the following sinusoidal function:
+where $RV_{\text{activity}}$ can be found in Eq.~\ref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case with no eccentricity, can be modelled by the following sinusoidal function:
 %

### 2018-06-13 manuscript.tex
Add files via upload
reviewed Sections 1-5

@@
 In this Section we present the analysis conducted on the star Alpha Centauri B (Alpha Cen B), comparing the result of fitting a CCF using the SN density defined in Sec.
-\ref{sec:3} with the usual approach based on fitting a Normal density for estimating the RV and asymmetry of the CCF.
+\ref{sec:3} with the commonly employed approach based on fitting a Normal density for estimating the RV and retrieving the BIS SPAN for evaluating the asymmetry of the CCF.
 %to retrieve the RV and width of the CCF and calculating the bisector to derive the asymmetry parameter BIS SPAN. 
@@
 
-There were $1808$ CCFs analyzed that were derived from the spectra of Alpha Centauri B taken in 2010 by the HARPS spectrograph.
-Note that more observations were carried out this year, however only the data that were not significantly affected by contamination from Alpha Centauri A were used \citep[see][]{Dumusque-2012}.
+A total of $1808$ CCFs that were derived from the spectra of Alpha Centauri B taken in 2010 by the HARPS spectrograph have been analyzed.
+Note that more observations were carried out that year, however only the data that was not significantly affected by contamination from Alpha Centauri A was used \citep[see][]{Dumusque-2012}.
 The selected observations represent probably, among all RV data existing, the best sampled and most precise RV data set showing strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.
@@
 In the left panel of Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $720$ and a strong Pearson correlation coefficient of $R=0.95$.
-This strong correlation suggests that the $\gamma$ and BIS SPAN are measuring a similar asymmetry for the CCF.
+This strong correlation suggests that both $\gamma$ and BIS SPAN are measuring similar asymmetries for the CCFs.
 This strong correlation allows as well to convert the dimensionless $\gamma$ parameters into \ms\,using the slope of the correlation, in this case 720 \ms.
@@
 
-The right plot of Fig.~\ref{fig:alphacent:corr.gamma} displays the comparison between the RVs derived estimated using the SN density and the Normal density. 
-The amplitude of the activity signal is slightly stronger for the SN mean RV (in the top-right plot the black circles of the SN mean RV tend to be more extreme), while the signal measured using N mean RV or SN median RV tend to be similar.
-This behavior is similar to the faculae simulated with SOAP 2.0 in see Sec.~\ref{sec:soap.faculae}, suggesting that the activity signal could be due to faculae present on Alpha Centauri B.
+The right plot of Fig.~\ref{fig:alphacent:corr.gamma} displays the comparison between the RVs estimated using the SN density and the Normal density. 
+The amplitude of the activity signal is slightly stronger for the SN mean RV (in the top-right plot the black circles of the SN mean RV tend to show more variability), while the signal measured using N mean RV or SN median RV are comparable.
+This behavior is similar to the one observed for the facula simulated with SOAP 2.0 in see Sec.~\ref{sec:soap.faculae}, suggesting that the activity signal could be due to faculae present on Alpha Centauri B.
 Another argument that suggests the presence of faculae, is the strong positive measured correlation between $\gamma$ and SN mean RV and SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot}.
@@
 
-Similar to the analyses in Sec.~\ref{sec:soap}, we compare the correlation between the asymmetry or the width parameters of the CCF and the RV in Fig.~\ref{fig:alphacent:corrPlot}. 
+Similar to the analyses presented in Sec.~\ref{sec:soap}, looking at Fig.~\ref{fig:alphacent:corrPlot} we compare the correlations between the asymmetry or the width parameters of the CCF and the RV. 
 For this analysis, we also include the asymmetry parameters derived in \citet{Boisse-2011}, $V_{span}$ and in \citet{Figueira-2013}, BIS-, BIS+, Bi Gauss and $V_{asy}$, as these authors found those asymmetry parameters more correlated to the RVs than BIS SPAN.
@@
 The Pearson correlation coefficient is $R=0.74$, while it is at best $R=0.42$ for all the other asymmetry--RV correlations not derived using the SN density fit.
-When looking at the correlations between the width and the RV estimates for Alpha Cen B, again the correlation is strongest for the SN parameters with $R=0.82$ for SN FWHM-SN mean RV, while it is $R=0.70$ for FWHM and N mean RV.
+When looking at the correlations between the width and the RV estimates for Alpha Cen B, the correlation is strongest for the SN parameters, with $R=0.82$ for SN FWHM-SN mean RV, while it is $R=0.70$ for FWHM and N mean RV.
 %
@@
 
-Results illustrating the performance of the stellar activity correction proposed in Sec.~\ref{sec:31} is displayed in Fig~\ref{fig:alphacent:correctionRV}. 
+Results illustrating the performance of the stellar activity correction proposed in Sec.~\ref{sec:31} are displayed in Fig~\ref{fig:alphacent:correctionRV}. 
 For Alpha Cen B, the RV estimated with SN mean RV has a std that is 35\% larger than the std of the RV estimated with the N mean RV, and the std of SN median RV is 9\% larger than that of the N mean RV.
-Even though we see these differences in the estimated RV, once we correct for the stellar activity using Eq.~\ref{eq:RV:correction}, 
+Even though we see these differences in the estimated RV, once we correct for stellar activity by using Eq.~\ref{eq:RV:correction}, 
 the rms of the residuals are essentially the same for all three approaches.
@@
 
-When looking at the statistical significance of the different parameters used for correcting activity in Table~\ref{table:alphacent.test}, we see that the intercept is not significant for any of the models, and BIS SPAN (coefficient $\beta_2$) does not statistically significantly help in explaining stellar activity when using the parameters derived from the Normal density fit.
+When looking at the statistical tests of the different parameters used for correcting activity in Table~\ref{table:alphacent.test}, we see that the BIS SPAN (coefficient $\beta_2$) does not statistically helpful in explaining stellar activity when using the parameters derived from the Normal density fit.
 However all the other parameters in the Normal and SN cases are statistically significant for modelling stellar activity. 
@@
 The correlation between $\gamma$ and SN mean RV is the strongest among all the asymmetry-RV correlations.
-For the correlation between the width and the estimated RV, the strongest correlation is consistently between SN FWHM and SN mean RV.
+Concerning the correlations between the width parameters and the estimated RV, the strongest correlation often is between SN FWHM and SN mean RV.
 However, there is one exception in the case of HD10700 where the Pearson correlation coefficient between FWHM and N mean RV is equal to $R=0.53$, while it is $R=0.42$ between SN FWHM and SN mean RV.
@@
 
-In the previous section, we saw that the estimated RV measured when considering a SN or a Normal model resulted in different amplitudes, especially when using the SN mean RV.
+In the previous section, we saw that the estimated RV measured when considering a SN or a Normal density resulted in different amplitudes, especially when using the SN mean RV.
 However, once corrected for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, as shown in the bottom plots of Fig~\ref{fig:alphacent:correctionRV}, the rms of the residuals are essentially the same for all three approaches.
-In this section, we investigate the ability of the three different RV estimators' (N mean RV, SN mean RV, and SN median RV) ability to detect planetary signals among stellar activity.
+In this section, we investigate the ability of the three different RV estimators' (N mean RV, SN mean RV, and SN median RV) to detect planetary signals among stellar activity.
 To carryout this test, the minimum detected amplitude of a planetary signal is estimated at different orbital periods when considering data affected by stellar activity.

### 2018-06-13 manuscript.tex
Add files via upload
manuscript reviewed.

@@
 Note that because BIS SPAN and $\gamma$ do not have the same units, the estimated slopes of the correlation between those two parameters to transform $\gamma$ in \ms were used (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star).
-In the bottom plots show the ratio between the standard errors measured when using the SN parameters and the Normal parameters.
-Values smaller or larger than one will imply that standard errors from the SN parameters are more or less precise than the Normal parameters, respectively.
+The bottom plots show the ratio between the standard errors measured when using the SN parameters and the Normal parameters.
+Values smaller or larger than one will imply that standard errors from the SN parameters are respectively more or less precise than the Normal parameters.
 
@@
 Finally, for the asymmetry parameters, $\gamma$ has standard errors that are 15\% more precise than BIS SPAN. 
-In conclusion, when fitting a SN density to the CCF and using as RV estimates SN median RV, we are able to improve by 10\% the precision on the estimated RV, 15\% the precision on the estimated asymmetry, both without degrading the precision on the estimated width.
+In conclusion, when fitting a SN density to the CCF and using as RV estimate SN median RV, we are able to improve by 10\% the precision on the estimated RV.
+using the SN density we are also able to improve by 15\% the precision on the estimated asymmetry parameter of the CCF.
+Both these improvements do not lead to a worse precision on the estimated width of the CCF.
 SN mean RV should not be use to derive precise estimated RVs, except perhaps in specific conditions described below, as the precision on this parameter is 60\% worse than the precision on the RVs derived from N mean RV.
@@
 When fitting a SN density to the CCF, parameters that describe the RV (i.e.
-the CCF barycenter), the amplitude (sometimes called the CCF contrast), the width, and the asymmetry of the CCF can all be estimated in a single model framework.
-For the RV estimator, we investigated the use of the mean and the median of the SN density. 
-Then the width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry by using $\gamma$, the skewness parameter of the SN density.
-
-To analyze the performance the proposed SN framework, tests on both simulated and real data were carried out and compared to the usual approach of fitting a Normal density shape (for estimating the RV and FWHM) and the BIS SPAN (for estimating the asymmetry).
+the CCF barycenter), the amplitude (sometimes called the CCF contrast), the width and the asymmetry of the CCF can all be estimated in a single model framework.
+For the estimation of the RV, we investigated the use of the mean and the median of the SN density. 
+Then the width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry by using $\gamma$, the naturally available skewness parameter of the SN density.
+
+To evaluate the performance of the proposed SN framework, tests on both simulated and real data were carried out and compared to the commonly employed approach consisting of fitting a Normal density shape (for estimating the RV and FWHM) and then separately deriving the BIS SPAN (for estimating the asymmetry).
 The simulated CCFs were generated using the SOAP 2.0 code, which can simulate activity signals induced by a spot or a facula on a solar-like star.
 The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method.
-In this case, sensitivity was measured using the correlation between the asymmetry and the estimated RV's, and it turned out either SN mean RV or SN median RV had a stronger correlation with gamma than the correlation between N mean RV and BIS SPAN.
-Moreover, the correlation between the FWHM and the estimated RV's is also stronger when using the parameters from the SN compared to the parameters from the Normal. 
+In this case, sensitivity was measured using the correlation between the asymmetry and the estimated RVs; both SN mean RV and SN median RV had a stronger correlation with gamma than the correlation between N mean RV and BIS SPAN.
+Moreover, the correlation between the FWHM and the estimated RVs is also stronger when using the parameters from the SN compared to the parameters from the Normal. 
 The SN parameters continued to have stronger correlations than the Normal in the setting where a planetary signal was added the SOAP 2.0 with a single spot.
 
-We also propose a new model to correct estimated RV data for stellar activity signals. 
+We also propose a new model to correct the estimated RV data for stellar activity signals. 
 Generally, when fitting for planetary signals, it is common to use a model composed of one or several Keplerian signals to account for the planets, in addition to a linear combination of the FWHM and BIS SPAN to account for stellar activity signals.
 The proposed model adds an additional term to account for the amplitude of the CCF, and an interaction term between the estimated asymmetry and the width parameters. 
-Using the simulated data from SOAP 2.0, this new model reduces the effect of the stellar activity signal by a factor of 2 and 3.5 over the usual model, for the facula and spot, respectively.
-
-The conclusion found for the SOAP 2.0 simulations that the correlation between the CCF asymmetry and the estimated RV, as well as between the CCF width and the estimated RV, is stronger for the SN than the Normal parameters also holds when analyzing real data.
+Using the simulated data from SOAP 2.0, this new model reduces the effect of the stellar activity signal by a factor of 2 and 3.5 over the usual model, respectively for the facula and spot.
+
+The conclusion found for the SOAP 2.0 simulations that the correlation between the CCF asymmetry and the estimated RV, as well as between the CCF width and the estimated RV, is stronger for the SN parameters than the Normal ones also holds when using real data.
 %
@@
 Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region.
-\xavier{The fact that we also find significant differences between the simulated and real data for the correlations between BIS SPAN and N mean RV and between FWHM and N mean RV shows that the SOAP 2.0 simulation studied here are too simple to explain the complexity of stellar activity in real RV observations.}
-\jessi{What are these differences for Normal case?
+%\xavier{The fact that we also find significant differences between the simulated and real data for the correlations between BIS SPAN and N mean RV and between FWHM and N mean RV shows that the SOAP 2.0 simulation studied here are too simple to explain the complexity of stellar activity in real RV observations.}
+%\jessi{What are these differences for Normal case?
 The specific difference for the SN is the strength of the correlations with the SN mean RV compared to the SN median RV.
@@
 real data for the Normal, I do not notice anything specifically different other than different patterns, but that is not surprising.}
-\umberto{I suggest to comment only about the differences for the SN case, since for the Normal I do not see differences between the analyses with SOAP2.0 and real stars.}
+%\umberto{I suggest to comment only about the differences for the SN case, since for the Normal I do not see differences between the analyses with SOAP2.0 and real stars.}
 Nevertheless, in both the simulated and the real cases, the parameters derived from the SN are generally more sensitive to activity than the parameters derived from the Normal.
@@
 
-Considering the different RV estimates of the real data, the amplitude of stellar activity tends to be largest for the SN mean RV, followed by the SN median RV, and then N mean RV. 
+Considering the different RV estimates of the real data, the amplitude of stellar activity tends to be largest for the SN mean RV, followed by the SN median RV, and finally by N mean RV. 
 Although there appears to be a larger difference between the SN mean RV and the SN median RV, the SN median RV is similar to the N mean RV. 
@@
 Having an estimator of RV that is more sensitive to stellar activity, such as the SN mean RV, can help with better probing stellar rotational periods or better understanding the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}.
-We saw in the preceding section that the SN mean RV estimator is 60\% noisier than the N mean RV estimator. 
+We saw in the previous section that the SN mean RV estimator is 60\% noisier than the N mean RV estimator. 
 This is not necessarily a negative aspect. 
@@
 \jessi{Maybe to try another test to see if the proposed correction is helpful, the detection-limit test could be carried out with the usual correction and we can see if it does not performa s well.}
+\umberto{waiting for new results with usual correction.}
 Therefore it seems that any of the RV estimate can be used to search for planetary signals.
@@
 
-When searching for low-mass exoplanets using the RV technique, it is necessary to get precise estimates of the RV and also to account for variations induced by stellar activity in order to avoid false detections.
+When searching for low-mass exoplanets using the RV technique, it is necessary to retrieve precise estimates of the RV and also to account for variations induced by stellar activity in order to avoid false detections.
 Stellar activity such as spots and faculae can lead to shape variations in the spectra features, which then results in shape variations of the CCF.
-The correlations between the width or asymmetry of the CCF and the estimated RV are commonly used as way to detect if the RVs are affected by stellar activity signals.
-Because the presence of real planets would result in only a shift in the CCF (not a shape change), strong correlations between the shape features of the CCF and the estimated RVs suggest that stellar activity may be present.
-
-In this paper, a new approach for measuring shape changes in the CCF is proposed using the SN density to estimate the RV and shape of the CCF. 
+The correlations between the width or asymmetry of the CCF and the estimated RV are commonly used as a way to detect if the RVs are affected by stellar activity signals.
+Because the presence of real planets would result in only a shift in the CCF (not a change on its shape), strong correlations between the shape features of the CCF and the estimated RVs suggest that stellar activity may be present.
+
+In this paper, a new approach for measuring shape changes in the CCF is proposed using the SN density to estimate the RV and the shape of the CCF. 
 This new method is compared to a commonly used method based on a Normal density fit to the CCF.
 The mean of the Normal density is used as the estimated RV and the FWHM estimates the width of the CCF.
-Because the Normal density does not have any skewness, another method is need to estimate the asymmetry of the CCF, and the BIS SPAN is often employed.
+Because the Normal density does not have any skewness, another method is necessary to estimate the asymmetry of the CCF; for this goal the BIS SPAN is often employed.
 In addition, the proposed SN approach is compared to other parameterizations of the CCF asymmetry that have been shown to be sensitive to activity signals \citep[][]{Boisse-2011,Figueira-2013}.
 
-In the different tests carried out for this work, the SN parameters tended to perform at least as well (and sometimes better) as the parameters from the Normal approach with the BIS SPAN.
-The SN parameters $\gamma$, SN FWHM and SN mean RV always show stronger correlation than the correlations between any of the parameters derived by the Normal and the BIS SPAN, or the different asymmetry parametrization presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
+In the different tests carried out for this work, the SN parameters performed at least as well (and often times better) as the parameters from the Normal approach and the BIS SPAN.
+The SN parameters $\gamma$, SN FWHM and SN mean RV always show stronger correlation than the correlations between any of the parameters derived by the Normal and the BIS SPAN, or the different asymmetry parametrizations presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
 This suggests the SN parameters may be better at probing stellar activity signals than the other methods. 
-In addition, the precision measured on the SN median RV and the $\gamma$ are 10 and 15\% more precise than the N mean RV and the BIS SPAN, respectively.
-
-Because of the advantages of using the proposed SN approach compared to the Normal approach, BIS SPAN, and all the asymmetry parameters described in \citet{Boisse-2011} and \citet{Figueira-2013}, this new parametrization of the CCF may be more useful for detecting stellar activity than the previously proposed parametrizations.
+In addition, the uncertainties measured on SN median RV and $\gamma$ are respectively 10\% and 15\% smaller than the corresponding uncertainties on N mean RV and BIS SPAN.
+
+Because of the advantages of using the proposed SN approach over the commonly employed approach based on the Normal density fit to the CCF and the BIS SPAN or the asymmetry parameters described in \citet{Boisse-2011} and \citet{Figueira-2013}, to fit a SN density to the CCF may be more useful for detecting stellar activity than the previously proposed parametrizations.
 Correlations between $\gamma$ and the SN mean RV, and between the width and the SN mean RV can be used to probe stellar activity signals in RV data, and the SN median RV can be used to estimate RV.
@@
 
-In this Appendix, a similar analysis as presented in Sec.~\ref{sec:4} is discussed for four main-sequence stars: HD192310 (K2V), HD10700 (G8V), HD215152 (K3V) and finally Corot-7 (K0V).
+In this Appendix, a similar analysis as the one presented in Sec.~\ref{sec:4} is discussed for four main-sequence stars: HD192310 (K2V), HD10700 (G8V), HD215152 (K3V) and finally Corot-7 (K0V).
 \xavier{All those data are public and were found on the ESO archive.
@@
 
-Table~\ref{table:summaryStars} summarizes the results obtained by the SN and Normal models. 
+Table~\ref{table:summaryStars} summarizes the results obtained by the SN and Normal densities. 
 These results are consistent with those from the analysis of Alpha Centauri B. 
@@
 However, the rms of the residuals for $\text{HD}215152$ are 0.05\,\ms lower for the SN model than the Normal model, and the rms of the residuals for Corot-7 are 0.34\,\ms lower.
-\xavier{$\text{HD}215152$ and Corot-7 have in average a lower SNR at 550 nm than HD10700 and HD192310, 273, 207, 141 and 44, respectively.}
- \umberto{$\text{HD}215152$ and Corot-7 have in average a lower SNR at 550 nm than HD10700 and HD192310.
-The average SNR at 550 nm for the stars \text{HD}10700, \text{HD}192310, $\text{HD}215152$ and Corot-7 are respectively 273, 207, 141 and 44.} \umberto{I slightly modified this sentences.
-Can you please check Xavier it is correct?}
+%\xavier{$\text{HD}215152$ and Corot-7 have in average a lower SNR at 550 nm than HD10700 and HD192310, 273, 207, 141 and 44, respectively.}
+$\text{HD}215152$ and Corot-7 have in average a lower SNR at 550 nm than HD10700 and HD192310.
+The average SNR at 550 nm for the stars \text{HD}10700, \text{HD}192310, $\text{HD}215152$ and Corot-7 are respectively 273, 207, 141 and 44.
 

### 2018-06-19 manuscript.tex
added acknowledgement

@@
 XD is grateful to The Branco Weiss Fellowship--Society in Science for its financial support.
-
+JCK was partially supported by the National Science Foundation under Grant AST 1616086 and by the National Aeronautics and Space Administration under grant 80NSSC18K0443.
+\jessi{[Umberto - did you use the Yale HPC at any point during this project?
+If so, we should add something like the following:] We also thank the Yale Center for Research Computing for the resources used to carryout this work.}
 %-----------------------------------------------------------------------------------------------------------------------------------------------

### 2018-06-25 manuscript.tex
Add files via upload
just added a small comment

--- 2018-06-13 manuscript.tex
@@
 When using the new correction proposed in this paper to mitigate the effect from stellar activity and when assessing planetary detection based on a periodogram analysis, we find very similar detection limits for the three RV estimators presented in this paper.
-\jessi{Maybe to try another test to see if the proposed correction is helpful, the detection-limit test could be carried out with the usual correction and we can see if it does not performa s well.}
-\umberto{waiting for new results with usual correction.}
+\umberto{trying to understand why we get better results for P=20 days when using the usual correction}
 Therefore it seems that any of the RV estimate can be used to search for planetary signals.
@@
 XD is grateful to The Branco Weiss Fellowship--Society in Science for its financial support.
-
+JCK was partially supported by the National Science Foundation under Grant AST 1616086 and by the National Aeronautics and Space Administration under grant 80NSSC18K0443.
+US was partially supported by Fondazione CARIPARO. \umberto{check if there is a code or something}
 %-----------------------------------------------------------------------------------------------------------------------------------------------

### 2018-07-06 manuscript.tex
edited abstract

@@
 {When considering real observations, the correlation between the RV and the asymmetry of the CCF and the correlation between the RV and the width of the CCF are stronger when using the parameters estimated with the SN rather than the ones obtained with the commonly employed Normal density.
-In particular the strongest correlations have been obtained when using as estimate for the RV the mean of the SN.
+In particular the strongest correlations have been obtained when using the mean of the SN as an estimate for the RV. 
 This suggests that the asymmetry of the CCF and the width of the CCF estimated using a SN density may be more sensitive to stellar activity, which can be helpful when estimating stellar rotational periods and in general when characterizing stellar activity signals.
@@
 }
-{We strongly encourage the use of the SN density to retrieve the different parameters of the CCF since the correlations used to probe stellar activity are stronger than the ones retrieved by the common approach and because the uncertainties associated to the RV and the asymmetry of the CCF are both smaller than the ones retrieved by the commonly employed strategies.
+{The SN density shape appears to be useful for characterizing the CCF since the correlations used to probe stellar activity are stronger and the uncertainties associated of the estimates for RV and the asymmetry of the CCF are both smaller than those derived from other commonly employed strategies.
 }

### 2018-07-06 manuscript.tex
edited sec 1

@@
 
-When working with radial-velocities data (RVs), one of the main limitations to the detection of small-mass exoplanets is no longer the precision of the instruments used, but the different sources of variability induced by the stars \citep[e.g.][]{Feng:2017aa, Dumusque:2017aa, Rajpaul-2015, Robertson-2014}.
+When working with radial-velocities data (RVs), one of the main limitations to the detection of low-mass exoplanets is no longer the precision of the instruments used, but the different sources of variability induced by the stars \citep[e.g.][]{Feng:2017aa, Dumusque:2017aa, Rajpaul-2015, Robertson-2014}.
 Stellar oscillations, granulation phenomena, and stellar activity can all induce apparent RV signals that are above the meter-per-second (\ms) precision \citep[e.g.][]{Saar-1997b, Queloz-2001, Desort-2007, Dumusque-2011a, Dumusque-2016a} reached by the best high-resolution spectrographs \citep[HARPS, HARPS-N,][]{Mayor-2003,Cosentino-2012}.
@@
 It is therefore mandatory to better understand stellar signals and to develop methods to correct for them, if in the near future we want to detect or confirm an Earth-twin planet using the RV technique.
-This is even more true now that instruments like the Echelle SPectrograph for Rocky Exoplanet and Stable Spectroscopic Observations (ESPRESSO) \citep{Pepe-2014} and the EXtreme PREcision Spectrometer (EXPRES) \citep{fischer2016state} should reach the stability to detect such signals.
+This is even more true now that instruments like the Echelle SPectrograph for Rocky Exoplanet and Stable Spectroscopic Observations (ESPRESSO) \citep{Pepe-2014} and the EXtreme PREcision Spectrometer (EXPRES) \citep{fischer2016state} should reach the precision and stability to detect such signals.
 However, if solutions are not found to mitigate the impact of stellar activity, the detection or confirmation of potential Earth-twins will be extremely challenging and false detections could plague the field.
@@
 In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so creates a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}.
-However, on quiet GKM dwarfs, the main target for precise RVs measurements, stellar activity can induce signals of a few \ms.
-This corresponds physically to variations smaller than 1/100th of a pixel on the detector, making changing in the shape of the spectral lines challenging to detect.
+However, on quiet GKM dwarfs, the main targets for precise RVs measurements, stellar activity can induce signals of a few \ms. 
+This corresponds physically to variations smaller than 1/100th of a pixel on the detector, making changes in the shape of the spectral lines challenging to detect.
 In order to measure such tiny variations, a common approach is to average the information of all the lines in the spectrum by cross correlating the stellar spectrum with a synthetic or an observed stellar template \citep[][]{Baranne-1996,Pepe-2002a, Anglada-Escude-2012}.
@@
 %
-To measure the Doppler-shift between different spectra and therefore to retrieve the RVs of a star as a function of time, the variations of the CCF barycenter are calculated. 
-The barycenter is generally estimated by fitting a Normal density to the CCF and retaining its mean.
-Variations in line shape between different spectra, which indicate the presence of signals induced by stellar activity, are measured by analyzing the different parameters of the CCF.
+To measure the Doppler-shift between different spectra, and therefore to retrieve the RVs of a star as a function of time, the variations of the CCF barycenter are calculated. 
+The barycenter is generally estimated by the mean of  a Normal density shape fit to the CCF. 
+Variations in line shape between different spectra, which indicate the presence of signals induced by stellar activity, are measured by analyzing different parameters of models fit to the CCF.
 Usually the width of the CCF is estimated using the full-width half-maximum (FWHM) of the fitted Normal density and its asymmetry by calculating the CCF bisector and measuring the bisector inverse slope span \citep[BIS SPAN,][]{Queloz-2001}.
@@
 %
-Therefore a common strategy nowadays used when fitting a Keplerian signal to a set of RVs searching for a planet consists in including in the model linear dependancies with the \logrhk, the FWHM and the BIS SPAN \citep{Dumusque:2017aa,Feng:2017aa}.
+Therefore a common strategy when fitting a Keplerian signal to a set of estimated RVs in search of a planet is to include linear terms in the model to account for activity, such as the \logrhk, the FWHM, and the BIS SPAN \citep{Dumusque:2017aa,Feng:2017aa}.
 %
@@
 %\subsection{Figueira indicators of stellar activity + other}
-Several indicators have been developed that are more sensitive to line asymmetry than the BIS SPAN.
-In \citet{Boisse-2011}, the authors developed $V_{span}$, which is the difference between the RV measured respectively by fitting a Normal density to the upper and the bottom part of the CCF.
+Several indicators have been developed that can be more sensitive to line asymmetry than the BIS SPAN.
+In \citet{Boisse-2011}, the authors developed $V_{span}$, which is the difference between the RV measured by fitting a Normal density to the upper and the lower parts of the CCF.
 This CCF asymmetry parameter is shown to be more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR).
@@
 %\subsection{Why using a SN density?}
-In all the methods described above, except bi-Gauss, the RV and the FWHM are derived using a Normal density fitted to the CCF, and the asymmetry is estimated using another approach. 
+In all the methods described above, except bi-Gauss, the RV and the FWHM are derived using a Normal density fitted to the CCF, and the asymmetry is estimated using a separate approach. 
 %
@@
 %\subsection{Outline of paper}
-The paper is organized as follow.
-In Sec.~\ref{sec:2} we introduce the SN density, describe its applicability for modelling the CCF and study how the SN parameters relate to mean of the Normal density, the FWHM and the BIS SPAN of the CCF.
+The paper is organized as follows.
+In Sec.~\ref{sec:2} we introduce the SN density, describe its applicability for modelling the CCF and study how the SN parameters relate to the mean of the Normal density, the FWHM, and the BIS SPAN of the CCF.
 %
@@
 %
-In Sec.~\ref{sec:5} error bars for the different estimated CCF parameters are retrieved.
-Finally the discussion of the results and the conclusions are presented, respectively, in Secs.~\ref{sec:discu} and ~\ref{sec:conclu}.
+In Sec.~\ref{sec:5} error bars are computed for the different estimated CCF parameters.
+Finally the discussion of the results and the conclusions are presented in Secs.~\ref{sec:discu} and ~\ref{sec:conclu}, respectively.
 

### 2018-07-06 manuscript.tex
edited sec 2

@@
 \end{equation}
-where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution\footnote{A standard Normal distribution is a Normal distribution with a mean of 0 and a standard deviation of 1.}.
+where $\phi$ and $\Phi$ are, respectively, the density function and the distribution function of a standard Normal distribution\footnote{A standard Normal distribution is a Normal distribution with a mean of 0 and a standard deviation of 1.}.
 The skewness parameter $\alpha$ quantifies the asymmetry of the SN. 
@@
 \includegraphics[height = 2.3in]{Skew_Normal_densities_jjck.pdf} 
-   \caption{Density function of a random variable Y following the SN distribution $SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
+   \caption{Density function of a random variable $Y$ following the SN distribution $SN(\xi, \omega, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
 Note that the solid black line has an $\alpha = 0$ making it a Normal distribution.}
@@
 For the $\alpha$ values used in Fig.~\ref{fig:SN.plot}, the corresponding values of ($\mu$, $\sigma^2$, $\gamma$) are displayed in Table~\ref{tab:cp_values}.
-In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution, rather than simply a location and scale parameter, and $\gamma$ provides an measure of the skewness of the SN.
+In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution, rather than simply a location and scale parameter, and $\gamma$ provides a measure of the skewness of the SN.
 Along with the mean of the SN, we consider the median of the distribution as a measure of its barycenter.
@@
 %
-Further details about the parametrization from Eq.~\ref{def:snd_gen}, called the \emph{Direct Parametrization} or DP, the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
+Further details about the parametrization from Eq.~\ref{def:snd_gen}, called the \emph{Direct Parametrization} (DP), the CP, and general statistical properties of the SN can be found in \cite{Azzalini2014}.
 
@@
 %
-where C is an unknown offset for the continuum of the CCF, A is the unknown amplitude of the CCF, sometimes referred to as the CCF contrast, and $\mu$, $\sigma^2$ and $\gamma$ are respectively the mean, the variance and the skewness of the SN as defined above.
+where C is an unknown offset for the continuum of the CCF, A is the unknown amplitude of the CCF, sometimes referred to as the CCF contrast, and $\mu$, $\sigma^2$ and $\gamma$ are, respectively, the mean, the variance, and the skewness of the SN as defined above.
 The values $x_1, \ldots, x_n$ are the different values of the x-axis of the CCF, generally in velocity units (e.g. \ms).
@@
 
-When fitting the commonly employed Normal density to the CCF, the estimated mean of the model is used as the estimated RV and the FWHM of the Normal density\footnote{FWHM$=2\sqrt{2\ln2}\,\sigma$ with standard deviation $\sigma$} represents the width of the CCF.
+When using a Normal density shape model for the CCF, the estimated mean is used as the estimated RV and the FWHM\footnote{FWHM$=2\sqrt{2\ln2}\,\sigma$ with standard deviation $\sigma$} is used to quantify the width of the CCF.
 Because the Normal density is symmetric, the skewness is not defined and therefore a separate approach is necessary to estimate the skewness of the CCF.
@@
 \begin{equation}
-R (x,y)= \frac{cov(x,y)}{\sigma(x)\sigma(y)},
+R (x,y)= \frac{\text{cov}(x,y)}{\sigma(x)\sigma(y)},
 \label{eq:Pearson:corr}
@@
 %
-where $x$ and $y$ are two quantitative variables, $cov(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represent their standard deviations.
-A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided.
+where $x$ and $y$ are two quantitative variables, $\text{cov}(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represent their standard deviations.
+A $p$-value for the statistical test with null hypothesis $H_{0}: R=0$ is also generally provided.
 

### 2018-07-06 manuscript.tex
edited sec 3

@@
 Exoplanets only produce a pure RV signal.
-On the contrary, stellar activity, and in particular the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.
-To track these variations in the shape of the spectral lines, the general approach consists in using the FWHM, the BIS SPAN or other indicators such as those introduced in \citet{Boisse-2011} or \citet{Figueira-2013}, which provide information on the width and asymmetry of the CCF.
+On the contrary, stellar activity, and, in particular, the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.
+To track these variations in the shape of the spectral lines, a common approach consists in using the FWHM, the BIS SPAN, or other indicators such as those introduced in \citet{Boisse-2011} or \citet{Figueira-2013}, which provide information on the width and asymmetry of the CCF.
 A strong correlation between the estimated RVs and one or more of these parameters provides an indication that stellar activity signals may be affecting the measurements.
@@
 %Some people also include the \logrhk, however, \citet{Feng-2018} show that this is probably not a good choice as \logrhk and RV are not well correlated.
-We propose to add additional parameters in the model to correct for stellar activity: first the amplitude parameter A of the CCF, generally referred to as the CCF contrast, and as second the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case).
+We propose to add additional parameters in the model to correct for stellar activity: 
+(i) an amplitude parameter A of the CCF (referred to as the CCF contrast) and (ii) an interaction term for $\gamma$ and SN FWHM (or the BIS SPAN and the FWHM in the Normal case).
 The stellar activity correction we propose can therefore be written as:
@@
 %
-where $\beta_{0}$ is the intercept and $\epsilon$ is the error with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix). 
-The contrast parameter $A$ accounts for the presence of a spot on the stellar surface, which produces a change in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g.
+where $\beta_{0}$ is the intercept and $\epsilon$ is the random error with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix). 
+The contrast parameter $A$ accounts for the presence of a spot on the stellar surface, which produces a change in the amplitude of the CCF, in addition to changes in asymmetry or width \citep[see e.g.
 Fig.
@@
 The proposed function defined in Eq.~\ref{eq:RV:correction} is the result of statistical and astronomical considerations. 
-In particular we checked that the correlations between the proposed parameters were not approaching one: if it was the case, the matrix needed to calculate the estimates would be singular, hence non invertible.
-This problem is known in statistics with the term multicollinearity.
-A detailed discussion of the topic can be found in the book by \citet{belsley1991}.
-In the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ between the asymmetry and width parameters and therefore the problem of multicollinearity is avoided.
-Note that we investigated the statistical significant of the interactions between respectively $A$ and the width of the CCF and $A$ and the asymmetry of the CCF; those two interactions were not relevant for accounting variations in $RV_{\text{activity}}$.
+In particular, we considered issues with correlations between the model covariates, which can lead to issues because the matrix needed to calculate the estimates could be singular; this problem is known in statistics as \emph{multicollinearity} and more discussion can be found in \citet{belsley1991}.
+In the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ between the asymmetry and width parameters and therefore the problem of multicollinearity appeared to be mitigated.
+We also investigated the statistical significant of the interactions between $A$ and the width of the CCF, and $A$ and the asymmetry of the CCF; those two interactions were not statistically significant.
 

### 2018-07-06 manuscript.tex
edited sec 4.0

@@
 \section{Simulation Study} \label{sec:soap}
-In order to evaluate the performance of the proposed SN approach for modelling the CCF and the benefit of using the proposed correction for stellar activity (See Eq.~\ref{eq:RV:correction}), we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet 2.0 code \citep[SOAP 2.0,][]{Dumusque-2014b}.
-
-For a given configuration of spots and faculae on the stellar surface, SOAP 2.0 gives as output the simulated CCF as a function of rotational phase.
-The code also returns the RV and the FWHM retrieved by fitting a Normal density to the CCF, and the BIS SPAN obtained by calculating the bisector of the CCF.
-SOAP 2.0 gives noiseless CCFs affected by stellar activity, which are used to compare the benefits of a SN density fit respect to a Normal density fit.
-
-For the simulations discussed below, a star similar to the Sun was modelled, with a solar disc of one solar radius seen equator-on, and with a stellar rotational period set to 25.0 days.
-The stellar effective temperature is set to 5778 K
-, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34 are used, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
-In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generate with a width of 40 \kms\,and considering initial spectra with a spectral resolution of R=115'000.
-%\jessi{Is a resolution of ``115'000'' standard notation?  I'm not sure what it means.}
-%, so that those CCFs would have the same properties as the one returned by the HARPS data reduction.
+In order to evaluate the performance of the proposed SN approach for modelling the CCF and the benefit of using the proposed correction for stellar activity (see Eq.~\ref{eq:RV:correction}), we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet 2.0 code \citep[SOAP 2.0,][]{Dumusque-2014b}.
+
+For a given configuration of spots and faculae on the stellar surface, SOAP 2.0 outputs simulated CCF as a function of rotational phase.
+The code also returns the RV and the FWHM estimated using a Normal model for the CCF, and the BIS SPAN obtained by calculating the bisector of the CCF.
+SOAP 2.0 gives noiseless CCFs affected by stellar activity, which are used to compare the performances of a SN and Normal models of the CCF.
+
+For the simulations discussed below, a star similar to the Sun was modelled with a solar disc of one solar radius seen equator-on, and a stellar rotational period set to 25.0 days.
+The stellar effective temperature is set to 5778 K, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
+In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generate with a width of 40 \kms\, and considering initial spectra with a spectral resolution of R=115'000.
 

### 2018-07-06 manuscript.tex
edited sec 4.1 - 1

@@
 
-To see the impact of a facula on the different parameters of the CCF, we simulated the effect of an equatorial facula
+To see the impact of a facula on the parameters of different models of the CCF, we simulated the effect of an equatorial facula
 %\jessi{Should a footnote be added here to explain that the SOAP 2.0 faculae are not simulated from actual faculae templates?} 
-of size 3\% relative to the visible stellar hemisphere.
-The facula is face-on when the phase equals to 0.
-Note that a 3\% faculae is relatively large for the Sun; at maximum activity, big faculae have generally a size of 1\% \citep[e.g.][]{Borgniet-2015}.
-In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and using its mean (N mean RV), and when fitting a SN density and taking its mean (SN mean RV) or its median (SN median RV).
-We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is different from the two others with a maximum amplitude happening at a different phase.
+of size 3\% relative to the visible stellar hemisphere. The facula is face-on when the phase equals to 0. 
+Note that a 3\% faculae is relatively large for the Sun; at maximum activity, large faculae generally have a size of 1\% \citep[e.g.][]{Borgniet-2015}. 
+In Fig.~\ref{fig:faculae}, we compare the barycentric variation of the CCF as measured when fitting a Normal density and using its mean (N mean RV), and when fitting a SN density and taking its mean (SN mean RV) or median (SN median RV).
+We see that all the different estimates of the CCF barycenter present a signal of similar amplitude, however the signal obtained with SN mean RV is notably different from the two others with a maximum amplitude happening at a different phase.
 
@@
 The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are stronger than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of $R$=0.46, -0.67 and -0.09, respectively.
-Concerning the correlations between the different RV estimates and the different CCF width parameters, there is a stronger correlation between SN FWHM and SN mean RV ($R=0.98$) respect to the one between FWHM and N mean RV ($R=0.84$).
-In this case the correlation between SN FWHM and SN median RV is the weakest, with $R=0.50$.
+%
+There is a stronger correlation between SN FWHM and SN mean RV ($R=0.98$) than between FWHM and N mean RV ($R=0.84$), but the correlation between SN FWHM and SN median RV is the weakest ($R=0.50$). 
 This first analysis shows that in the case of a facula, using some parameters from the SN can lead to stronger correlations than the ones obtained by the usual Normal parameters.

### 2018-07-06 manuscript.tex
edited sec 4.1 - 2

@@
 
-Since the RV variations displayed in Fig.~\ref{fig:faculae} are caused only by stellar activity, in this case a facula, we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its performance in this setting.
+The RV variations displayed in Fig.~\ref{fig:faculae} are caused only by stellar activity, in this case a facula, so we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to evaluate the performance of the model in this setting.
 The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
-The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a $R^2$ of our model larger than $0.99$.
-In addition, the rms of the different estimates of the RV reduces from about 3 \ms before correction to values below 0.15 \ms after correction.
-We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters, however the different is probably not significant.
+The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a $R^2$ larger than $0.99$. 
+In addition, the rms of the different estimates of the RV reduces from about 3 \ms before correcting for stellar activity to values below 0.15 \ms after correcting for stellar activity.
+We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters.
 When comparing the correction proposed in Eq.~\ref{eq:RV:correction} with what is generally used (i.e.
-a linear combination of only the asymmetry and width parameter), we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2.
-Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that all the SN or Normal parameters are relevant for the correction.
+a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2.
+Looking at the significance of the coefficients in Table~\ref{table:faculae.test}, we observe that all the SN or Normal parameters are relevant for the correction.
 
@@
 \includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{(top) The spurious estimated RVs (black dots) caused by a facula in the simulated data using a Normal and a SN fit, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses), and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
-   %
- (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
-std, red crosses) and the residuals from the usual correction (Usual corr.
-std, green triangles).
-The residuals have a smaller systematic component when using the proposed model of
-  Eq.~\ref{eq:RV:correction} (red crosses) compared to the usual model (green triangles).
+   \caption{(top) The spurious estimated RVs (black dots) caused by a facula in the simulated data using a Normal and a SN model, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses), and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the Normal fit.
+   %
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (red crosses) and the residuals from the usual correction (green triangles).
+The std.
+are also reported in the legend, and the residuals have a smaller systematic component when using the proposed model of Eq.~\ref{eq:RV:correction} compared to the usual model.
 The tests of statistical significance on the parameters are presented in Table \ref{table:faculae.test}.
@@
 \begin{center}
-\caption{P--values for the estimated coefficients from the model in Eq.~\ref{eq:RV:correction} for correcting stellar activity induced by an equatorial 3\% facula on the simulated Sun.
-All the parameters corresponding to the Normal or SN variables are statistically significant to explain the spurious RV variations caused by the facula.
+\caption{P-values for the estimated coefficients from the model in Eq.~\ref{eq:RV:correction} for correcting stellar activity induced by an equatorial 3\% facula on the simulated Sun.
+All the parameters corresponding to the Normal or SN variables are statistically significant.
 The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability present in the different RV estimates.}

### 2018-07-06 manuscript.tex
edited sec 4.2

@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
-\caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line), and SN median RV (cyan dots-dashed line).
+\caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line), and SN median RV (cyan dotted-dashed line).
 In this case, the CCFs were generated using SOAP 2.0 with an equatorial 3\% facula on the simulated Sun.
@@
 
-In this section, we consider the effects on the CCF parameters of an equatorial spot of size 1\% relative to the visible stellar hemisphere.
-The spot is face on when the phase equals to 0.
-Note that this is a large spot for the Sun, as in general large spots are more in the regime of 0.1\% \citep[e.g.][]{Borgniet-2015}.
+Next we consider the effects on the CCF model parameters due to the presence of an equatorial spot of size 1\% relative to the visible stellar hemisphere. 
+The spot is face-on when the phase equals to 0. 
+Note that this is a large spot for the Sun, as large spots are generally on the order of 0.1\% \citep[e.g.][]{Borgniet-2015}. 
 In Fig.~\ref{fig:spot}, we show the barycentric variations of the CCF induced by this simulated spot. 
-In contrast to the case of the facula, all the different estimates of the CCF barycenter for the spot have the same shape in variation.
-The amplitude for SN mean RV is however slightly smaller.
-
-Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and the different estimates for the CCF barycenter (i.e.
+In contrast to the case of the facula, all the different estimates of the CCF barycenter for the spot have the same shape in variation; however, the amplitude for SN mean RV is slightly smaller.
+
+Fig.~\ref{fig:spot.corr} shows the correlations between the asymmetry parameters and the different estimates of the CCF barycenter (i.e.
 SN mean RV, SN median RV and N mean RV).
-The correlation between $\gamma$ and SN median RV is the strongest ($R=-0.93$), followed by the correlation BIS SPAN - N mean RV ($R=-0.86$) and at last the correlation between $\gamma$ - SN mean RV ($R=-0.85$).
-Concerning the correlation between the width and the CCF barycenter, we note that the variations are seen as a circle in this parameter space and therefore no correlation is observed.
-Once again, like in the case of the facula, we see that some parameters of the SN gives stronger correlations respect to the Normal parameters.
+The correlation between $\gamma$ and SN median RV is the strongest ($R=-0.93$), followed by the BIS SPAN - N mean RV correlation ($R=-0.86$) and the $\gamma$ - SN mean RV correlation ($R=-0.85$).
+The correlations between the width and the CCF barycenter are more circular and no substantial correlation is observed. 
+Similar to the case with a facula, some parameters of the SN gives stronger correlations compared to the Normal parameters.
 
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
-\caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line) or SN median RV (cyan dots-dashed line) using CCFs generated from SOAP 2.0 with an equatorial 1\% spot on the simulated Sun.
-The star does one full rotation between phase -0.5 and 0.5, with the spot being seen face-on for phase 0.
-SN mean RV seems to have the smallest spurious variations caused by the spot.}
+\caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line) or SN median RV (cyan dotted-dashed line) using CCFs generated from SOAP 2.0 with an equatorial 1\% spot on the simulated Sun.
+The star does one full rotation between phase -0.5 and 0.5, with the spot being seen face-on at phase 0.
+The SN mean RV seems to have the smallest spurious variations caused by the spot.}
    %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star.
@@
 However, only the asymmetry produces a statistically significant correlation with the different RV estimates.
-The width parameters and their corresponding RV estimates present weak correlations and in general much weaker correlations respect to the results obtained when an equatorial 3\% facula is present on the simulated Sun.}
+The width parameters and their corresponding RV estimates present weak correlations and, in general, much weaker correlations compared to the results obtained when an equatorial 3\% facula is present on the simulated Sun.}
     \label{fig:spot.corr}
@@
 
-As before, the originally RVs are corrected by using Eq.~\ref{eq:RV:correction}.
-The results of this correction are displayed in Fig.~\ref{fig:spot.correction}  and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:spot.test}.
-Like for the faculae, the proposed correction is able, in the case of the spot, to model almost entirely the stellar activity signal when considering the SN or Normal parameters, with $R^2$ values for the linear combination larger than 0.99.
-Looking at Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms, for any of the different RV estimates.
+As before, the original RV estimates are corrected using Eq.~\ref{eq:RV:correction}. 
+The results of this correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table~\ref{table:spot.test}.
+As with the facula, the proposed correction is able, in the case of the spot, to capture almost entirely the stellar activity signal when considering the SN or Normal parameters, with $R^2$ values for the linear combination larger than 0.99.
+
+In Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms, for any of the different RV estimates.
 When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the facula.
-
-Looking at Table \ref{table:spot.test}, we see that the Normal or SN parameters involved in Eq.~\ref{eq:RV:correction} are all statistically significant to explain the activity signal, except the width of the CCF when the RVs are derived with the mean or median of the SN density.
+The Normal or SN parameters involved in Eq.~\ref{eq:RV:correction} are all statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, except the width of the CCF when the RVs are derived with the mean or median of the SN density.
 %This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.

### 2018-07-06 manuscript.tex
edited sec 4.3

@@
    %
- (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
-std, red crosses) and the residuals from the usual correction (Usual corr.
-std, green triangles).
-The residuals have a smaller systematic component when using the proposed model of
-  Eq.~\ref{eq:RV:correction} (red crosses) compared to the usual model (green triangles).
-The tests of statistical significance on the parameters are presented in Table \ref{table:spot.test}.
+ (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (red crosses) and the residuals from the usual correction (green triangles). 
+ The std. are also reported in the legend, and the residuals have a smaller systematic component when using the proposed model compared to the usual model.
+The tests of statistical significance on the parameters are presented in Table~\ref{table:spot.test}.
 }
@@
 
-The final simulation presented here includes a planetary signal influencing the CCF along with the 1\% spot modelled previously (see Sec.~\ref{sec:soap.spot}). 
-The purpose of this example is to check if we are able to disentangle these two different sources of variations when using the parameters derived using a Normal or a SN fit to the CCF.
-In this scenario the planet is injected with a semi-amplitude of 10 \ms with no eccentricity and with a period corresponding to one third of the stellar rotational period, i.e.
+The final simulation includes a planetary signal influencing the CCF along with the 1\% spot modelled previously (see Sec.~\ref{sec:soap.spot}). 
+The purpose of this example is to check if we are able to disentangle these two different sources of variations when using the parameters derived using a Normal or a SN model for the CCF.
+In this scenario the planet is injected with a semi-amplitude of 10 \ms with no eccentricity and with a period corresponding to one-third of the stellar rotational period, i.e.
 one-third of 25 days.
@@
 The correlations are weaker than in the case of the spot due to the planet inducing changes in RV without affecting the width or the asymmetry of the CCF.
-However, the strength of the correlations between the CCF asymmetry parameters and RV are comparable with the ones obtained for the spot-only model: $\gamma$--SN median RV has the strongest correlation ($R=-0.84$), followed by the correlation between BIS SPAN--N mean RV (($R=-0.78$)) and finally by the correlation between $\gamma$--SN mean RV ($R=-0.75$).
-The patterns observed in the width-RV phase space correlations in Fig.~\ref{fig:spot.plus.planet.corr} follow a circle, similar to the spot-only model; no correlation is observed between those two parameters.
+However, the order of the strength of the correlations between the CCF asymmetry parameters and RV are comparable with the ones obtained for the spot-only model: $\gamma$--SN median RV has the strongest correlation ($R=-0.84$), followed by the correlation between BIS SPAN--N mean RV ($R=-0.78$) and finally by the correlation between $\gamma$--SN mean RV ($R=-0.75$).
+The patterns observed in the width-RV phase space correlations in Fig.~\ref{fig:spot.plus.planet.corr} follow a circle, similar to the spot-only model; no substantial correlation is observed between those two parameters.
 
@@
 %\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
- \caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line) or SN median RV (cyan dots-dashed line).
-In this case, the CCFs have been generated using SOAP 2.0, considering an equatorial 1\% spot on the simulated Sun in addition to a planet with a period of one third of the rotational period of the star and with an amplitude of 10\,\ms.
-The star do one full rotation between phase -0.5 and 0.5, with the spot being seen face-on for phase 0.}
+ \caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line) or SN median RV (cyan dotted-dashed line).
+In this case, the CCFs have been generated using SOAP 2.0, considering an equatorial 1\% spot on the simulated Sun in addition to a planet with a period of one-third of the rotational period of the star and with an amplitude of 10\,\ms.
+The star does one full rotation between phase -0.5 and 0.5, with the spot being seen face-on at phase 0.}
    %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected.
@@
 The shape of the CCF changes as the spot moves, producing statistically significant correlations only between the estimated RVs and the asymmetry parameter.
-The correlations between the estimated RVs and the width parameter of the CCF is weaker than the case with only a spot.}
+The correlations between the estimated RVs and the width parameter of the CCF are weaker than the case with only a spot.}
     \label{fig:spot.plus.planet.corr}
@@
 
-In order to correct the estimated RVs from the spurious variation caused by the spot, the proposed model for correcting the activity is added to a signal that takes into account the RV variations caused by a injected planet.
+In order to correct the estimated RVs from the spurious variation caused by the spot, the proposed model for correcting the activity is added to a planetary signal model that takes into account the RV variations caused by a planet.
 The observed RVs can therefore be modelled as a combination of the activity and the planetary signals:
@@
 We can see how in this case we are able to disentangle the spurious variations in RVs caused by stellar activity from the pure Doppler-shift due to the planet.
-The proposed model from Eq.~\ref{eq:RV:correction.overall} was fitted to the RV data and the results of the estimated model are summarized in Table \ref{table:spotplanet.test}.
+The proposed model from Eq.~\ref{eq:RV:correction.overall} was fitted to the RV data and the results of the estimated model are summarized in Table~\ref{table:spotplanet.test}.
 Except for the width parameters with coefficient $\beta_3$, all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet.
@@
 \begin{center}
-\caption{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun, and a planet with period one third of the rotational period and a semi-amplitude 10\,\ms.
-All the parameters corresponding to the Normal or SN variables are statistically significant to explain the spurious RV variations caused by this spot plus planet, except for the width of the CCF.
+\caption{P-values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun, and a planet with a period of one-third the rotational period of the star and a semi-amplitude  of 10\,\ms.
+All the parameters corresponding to the Normal or SN variables are statistically significant, except the width of the CCF.
 Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.}

### 2018-07-07 manuscript.tex
updated sec 5.1

@@
 
-In this Section we present the analysis conducted on the star Alpha Centauri B (Alpha Cen B), comparing the result of fitting a CCF using the SN density defined in Sec.
+The simulated SOAP data of the previous section were helpful in assessing the performance of the proposed methodology in a setting where the ground truth was known.
+In this section we present an analysis conducted on real observations, in particular, the star Alpha Centauri B (Alpha Cen B), and compare the performance when fitting a CCF using the SN density defined in Sec.
 \ref{sec:3} with the commonly employed approach based on fitting a Normal density for estimating the RV and retrieving the BIS SPAN for evaluating the asymmetry of the CCF.
@@
 Note that more observations were carried out that year, however only the data that was not significantly affected by contamination from Alpha Centauri A was used \citep[see][]{Dumusque-2012}.
-The selected observations represent probably, among all RV data existing, the best sampled and most precise RV data set showing strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.
+The selected observations represent arguably, among all RV data existing, the best sampled and most precise RV data set showing strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.
 
 First, the correlation between $\gamma$ and BIS SPAN is evaluated.
-In the left panel of Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $720$ and a strong Pearson correlation coefficient of $R=0.95$.
+In the left panel of Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to \jessi{See question in figure about this slope} $720$ and a strong Pearson correlation coefficient of $R=0.954$.
 This strong correlation suggests that both $\gamma$ and BIS SPAN are measuring similar asymmetries for the CCFs.
-This strong correlation allows as well to convert the dimensionless $\gamma$ parameters into \ms\,using the slope of the correlation, in this case 720 \ms.
+It also provides a conversion between the dimensionless $\gamma$ parameter into \ms\, using the slope of 720 \ms.
 %\xavier{As $\gamma$ has no units, this will allow us to compare the amplitude of the activity signal seen in $\gamma$ and in BIS SPAN, by using the slope of this correlation as a scaling factor}.
@@
 \includegraphics[height = 3.6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
-   \caption{(left) Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B. The strong correlation suggests these two parameters are similarly measuring the asymmetry.
+   \caption{(left) Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
+The strong correlation suggests these two parameters are similarly measuring the asymmetry.
+\jessi{How is the slope 720?
+It looks like it should be around 0.0005.}
 (top right) RVs as function of Julian Day for Alpha Centauri B in 2010.
-The RVs are estimated using the mean of a Normal fitted to the CCF (red triangles), or the mean (black circles) or median (cyan crosses) of a SN density fitted to the CCF.
-(bottom right) Differences between the RVs estimated with the SN density and those from the Normal density.}
+The RVs are estimated using the mean of a Normal fitted to the CCF (red triangles), or the mean (black circles) or median (cyan pluses) of a SN density fitted to the CCF.
+(bottom right) Differences between the RVs estimated with the Normal density and those from the SN density.}
    \label{fig:alphacent:corr.gamma}
@@
 The amplitude of the activity signal is slightly stronger for the SN mean RV (in the top-right plot the black circles of the SN mean RV tend to show more variability), while the signal measured using N mean RV or SN median RV are comparable.
+%
 This behavior is similar to the one observed for the facula simulated with SOAP 2.0 in see Sec.~\ref{sec:soap.faculae}, suggesting that the activity signal could be due to faculae present on Alpha Centauri B.
-Another argument that suggests the presence of faculae, is the strong positive measured correlation between $\gamma$ and SN mean RV and SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot}.
-In Sec.~\ref{sec:soap.spot}, we saw that a spot induces a negative correlation between $\gamma$ and SN mean RV, while weak correlations are measured between SN FWHM and SN mean RV.
+%
+Another feature that suggests the presence of faculae is the strong positive measured correlation between $\gamma$ and SN mean RV and  between SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot}.
+%
+In Sec.~\ref{sec:soap.spot}, we saw that a spot induces a negative correlation between $\gamma$ and SN mean RV and weak correlations are measured between SN FWHM and SN mean RV.
 \citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
@@
 
-Similar to the analyses presented in Sec.~\ref{sec:soap}, looking at Fig.~\ref{fig:alphacent:corrPlot} we compare the correlations between the asymmetry or the width parameters of the CCF and the RV. 
-For this analysis, we also include the asymmetry parameters derived in \citet{Boisse-2011}, $V_{span}$ and in \citet{Figueira-2013}, BIS-, BIS+, Bi Gauss and $V_{asy}$, as these authors found those asymmetry parameters more correlated to the RVs than BIS SPAN.
-It is clear in the case of Alpha Cen B, that the correlation found between $\gamma$ and SN mean RV is the strongest.
-The Pearson correlation coefficient is $R=0.74$, while it is at best $R=0.42$ for all the other asymmetry--RV correlations not derived using the SN density fit.
-When looking at the correlations between the width and the RV estimates for Alpha Cen B, the correlation is strongest for the SN parameters, with $R=0.82$ for SN FWHM-SN mean RV, while it is $R=0.70$ for FWHM and N mean RV.
+Similar to the analyses presented in Sec.~\ref{sec:soap}, in Fig.~\ref{fig:alphacent:corrPlot} we compare the correlations between the asymmetry or the width parameters of the CCF and the RV. 
+For this analysis, we also include the asymmetry parameters derived in \citet{Boisse-2011}, $V_{span}$ and in \citet{Figueira-2013}, BIS-, BIS+, Bi Gauss and $V_{asy}$, as these authors found those asymmetry parameters more correlated with the RVs than BIS SPAN.
+It is clear in the case of Alpha Centauri B that the correlation found between $\gamma$ and SN mean RV is the strongest.
+The Pearson correlation coefficient is $R=0.74$, while the next strongest is $R=0.42$ for all the other asymmetry-RV correlations (except the $\gamma$-SN median RV, which is $R=0.56$).
+The correlations between the width and the RV estimates for Alpha Centauri B, the correlation is strongest for the SN parameters, with $R=0.82$ for SN FWHM-SN mean RV, compared to $R=0.70$ for FWHM-N mean RV.
 %
@@
 \includegraphics[height = 6in]{HD12862_[4]Comparison_para.pdf}  
-   \caption{(top three rows) Correlations between the asymmetry parameters and their corresponding estimated RVs for Alpha Cen B. 
-(bottom row) The correlation between the FWHM and the estimated RVs for Alpha Centauri B.
+   \caption{(top three rows) Correlations between the asymmetry parameters and their corresponding estimated RVs for Alpha Centauri B. 
+(bottom row) The correlation between the FWHM and the estimated RVs.
 The correlations are stronger when using parameters derived from the SN fit than the Normal one.
@@
 Results illustrating the performance of the stellar activity correction proposed in Sec.~\ref{sec:31} are displayed in Fig~\ref{fig:alphacent:correctionRV}. 
-For Alpha Cen B, the RV estimated with SN mean RV has a std that is 35\% larger than the std of the RV estimated with the N mean RV, and the std of SN median RV is 9\% larger than that of the N mean RV.
-Even though we see these differences in the estimated RV, once we correct for stellar activity by using Eq.~\ref{eq:RV:correction}, 
+For Alpha Centauri B, the RV estimated with SN mean RV has a std that is 35\% larger than the std of the RV estimated with the N mean RV, and the std of SN median RV is 9\% larger than that of the N mean RV.
+Even though we see these differences in the estimated RV, once we correct for stellar activity using Eq.~\ref{eq:RV:correction}, 
 the rms of the residuals are essentially the same for all three approaches.
 %In the best case, for SN mean RV, we reduce the stellar activity signal by a factor of 2, while in the worst case, N mean RV, only by a factor 1.5. 
-Although when studying the correlations between the different parameters we see that the parameters retrieved by using the SN density are more sensitive to stellar activity than the ones obtained with a Normal density fit,
-the proposed linear model for correcting from stellar activity is not able to perform better in the SN case than in the Normal case.
-When comparing the new correction for stellar activity proposed in Sec.~\ref{sec:31} with the usual correction, that uses only a linear combination of the width and the asymmetry of the CCF, we end up with very similar results.
+Although the correlations between the different parameters from the SN density are more sensitive to stellar activity than those obtained with a Normal density fit,
+the proposed linear model that corrects for stellar activity does not necessarily perform better in the SN case than in the Normal case. 
+The new correction for stellar activity proposed in Sec.~\ref{sec:31} performed similarly to the usual correction that uses only a linear combination of the width and the asymmetry of the CCF, but has RV rms that are 6\,\cms\,smaller than the usual correction.
+\jessi{Should this be 8\cms?}
+
+%%with the usual correction that uses only a linear combination of the width and the asymmetry of the CCF, we end up with very similar results.
 The new correction is however able to get RV rms that are 6\,\cms\,smaller than the usual correction.
@@
 
-When looking at the statistical tests of the different parameters used for correcting activity in Table~\ref{table:alphacent.test}, we see that the BIS SPAN (coefficient $\beta_2$) does not statistically helpful in explaining stellar activity when using the parameters derived from the Normal density fit.
-However all the other parameters in the Normal and SN cases are statistically significant for modelling stellar activity. 
+The results of the statistical tests of the different parameters used for correcting activity can be found in Table~\ref{table:alphacent.test}.
+The BIS SPAN (coefficient $\beta_2$) is not statistically significant for the parameters derived from the Normal density fit.
+However, all the other parameters in the Normal and SN cases are statistically significant for modelling stellar activity. 
 By analyzing the values of the coefficient of determination, $R^2$, we see that the model for the SN mean RV is able to capture the highest percentage of variability in the estimated RV. 
-This is not a surprising result since for the three different RV estimates, we arrive to the same RV residual rms after correction for activity, but before correction, SN mean RV shows the largest RV rms (see Fig~\ref{fig:alphacent:correctionRV}).
+This is not a surprising result since the three different RV estimates have the same RV residual rms after correction for activity, but before correction, the SN mean RV had the largest RV rms (see Fig~\ref{fig:alphacent:correctionRV}).
 

### 2018-07-07 manuscript.tex
sec 5.2

@@
 std, blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
-The residuals have a smaller systematic component when using the proposed model of
-  Eq.~\ref{eq:RV:correction} (black dots) compared to the usual model (blue triangles).}
+The residuals have a smaller systematic component when using the proposed model of  Eq.~\ref{eq:RV:correction} (black dots) compared to the usual model (blue triangles).}
 \label{fig:alphacent:correctionRV}
@@
 \begin{center}
-\caption{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction from stellar activity in Alpha Cen B data.
+\caption{P-values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction from stellar activity in Alpha Centauri B data.
 All the variables corresponding to the Normal or SN parameters are statistically significant, except for the asymmetry of the CCF when using the BIS SPAN with the N mean RV.
-The evaluation of the $R^2$ shows that the proposed linear combination better explains variations in RVs due to the stellar activity when the RVs are derived using SN mean RV.}
+The $R^2$ shows that the proposed linear combination explains the most variability in RVs due to the stellar activity when the RVs are estimated with the SN mean RV.}
 \label{table:alphacent.test}
@@
 We carryout similar analyses for four other main sequence stars: HD192310, HD10700, HD215152 and Corot-7.
-The same correlations plots and activity--after--correction plots displayed in the previous section for Alpha Cen B can be found found for those new four stars in Appendix \ref{appendix}.
-
-The correlations between the parameters of these additional stars are similar to those obtained for Alpha Cen B.
+The same correlations plots and residual plots displayed in the previous section for Alpha Centauri B can be found found for those new four stars in Appendix~\ref{appendix}.
+\jessi{Add explicit references to the datasets}
+
+The correlations between the parameters of these additional stars are similar to those obtained for Alpha Centauri B.
 The correlation between $\gamma$ and SN mean RV is the strongest among all the asymmetry-RV correlations.
-Concerning the correlations between the width parameters and the estimated RV, the strongest correlation often is between SN FWHM and SN mean RV.
-However, there is one exception in the case of HD10700 where the Pearson correlation coefficient between FWHM and N mean RV is equal to $R=0.53$, while it is $R=0.42$ between SN FWHM and SN mean RV.
-
-Except for the special case discussed above for HD10700, the analyses of those four stars, in addition to the analyses on Alpha Cen B, shows that the parameters derived when using a SN density are more sensitive to activity.
-Therefore using the SN parameters, and in particular defining RV as SN mean RV, can lead to better detection of stellar activity over the Normal parameters.
-This is the case for the evaluation of the asymmetry-RV correlations for  Alpha Cen B, HD10700, HD215152, HD192310 and Corot-7, and the width-RV correlation for Alpha Cen B, HD215152, HD192310 and Corot-7 (see Appendix \ref{appendix}).
-
-In terms of correction for stellar activity, in the case of Alpha Cen B we see that although the RV rms is larger when measuring the RVs using SN mean RV (compared to the RVs obtained using N mean RV), once corrected for activity using the new model proposed in Sec.~\ref{sec:31}, both RVs estimates provides similar residuals.
-We also observe slight differences in the rms between the new proposed correction and the usual correction, which uses only a linear combination of the width and the asymmetry of the CCF.
-For Corot-7 the new correction is able to provide RV residual rms 30\,\cms smaller than the one obtained with the usual correction.
+%
+Between the width parameters and the estimated RV, the strongest correlation often is between SN FWHM and SN mean RV. 
+However, there is one exception in the case of HD10700 where the Pearson correlation coefficient between FWHM and N mean RV is equal to $R=0.53$, while it is $R=0.42$ between SN FWHM and SN mean RV, and $R=0.5$ between SN FWHM and SN median RV.
+
+Except for the special case discussed above for HD10700, the analyses of those four stars, in addition to the analyses on Alpha Centauri B, show that the parameters derived when using a SN density are generally more sensitive to activity.
+Therefore using the SN parameters, and in particular estimating RV using SN mean RV, can lead to better detection of stellar activity over the Normal parameters. 
+More specifically, this is the case for the evaluation of the asymmetry-RV correlations for Alpha Centauri B, HD10700, HD215152, HD192310 and Corot-7, and the width-RV correlation for Alpha Centauri B, HD215152, HD192310 and Corot-7 (see Appendix \ref{appendix}).
+
+When correcting for stellar activity for  Alpha Centauri B, although the uncorrected RV rms was larger for SN mean RV (compared to the RVs obtained using N mean RV), once corrected for activity using the new model proposed in Sec.~\ref{sec:31}, both RVs estimates had similar residuals.
+For HD10700, HD215152, and HD192310, the proposed and usual models had comparable corrected RV rms.
+%%%We also observe slight differences in the rms between the new proposed correction and the usual correction, which uses only a linear combination of the width and the asymmetry of the CCF.  
+However, for Corot-7, the new correction is able to provide RV residual rms 30\,\cms \jessi{Should this be 23?} smaller than the one obtained with the usual correction.
 

### 2018-07-07 manuscript.tex
sec 6

@@
 However, once corrected for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, as shown in the bottom plots of Fig~\ref{fig:alphacent:correctionRV}, the rms of the residuals are essentially the same for all three approaches.
-In this section, we investigate the ability of the three different RV estimators' (N mean RV, SN mean RV, and SN median RV) to detect planetary signals among stellar activity.
+In this section, we investigate the ability of the three different RV estimators (N mean RV, SN mean RV, and SN median RV) to detect planetary signals among stellar activity.
 To carryout this test, the minimum detected amplitude of a planetary signal is estimated at different orbital periods when considering data affected by stellar activity.
 
-In order to obtain CCFs affected by realistic stellar activity signals, the CCFs from Alpha Cen B used previously were considered. 
+In order to obtain CCFs affected by realistic stellar activity signals, the CCFs from Alpha Centauri B used previously were considered. 
 To simulate a planetary signal, the CCFs were blue- or red-shifted with the desired amplitude, period, and phase.
@@
 For each of the 4500 simulations considered, the activity correction presented in Eq.~\ref{eq:RV:correction} was applied, and signals in the residuals were investigated using a Generalized Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982, Zechmeister-2009}.
-If a signal with a p--value\footnote{The p--values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected.
+If a signal with a P-value\footnote{The P-values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected.
 Finally, for each period considered, the minimum amplitude at which at least 50\% of the planets with different phases were detected was found.
@@
 Therefore, we cannot simply vary each point in the CCF by their respective error bars and then recalculate the best SN or Normal density fit to see how the CCF noise influences the estimation of the parameters of interest (i.e., N mean RV, SN mean RV, SN median RV, FWHM, SN FWHM, BIS SPAN and $\gamma$).
-Instead, we go to the individual spectra where the individual measurements can be considered independent fo the other points.
+Instead, we go to the individual spectra where the individual measurements can be considered independent from the other points.
 The standard error on each point of a spectrum is given by the photon noise, which follows a Poisson distribution and is therefore estimated by taking the square-root of the measured flux.
@@
 We first modify the values of all the points in the spectrum given their respective error bars. 
-To do so random Gaussian noise centered on the value of the point and with standard deviation the square-root of the flux was added across each spectrum. 
-The CCF was calculated using this spectrum according to the method presented in \citet{Pepe-2002a}, then fitted either a Normal or SN density to this CCF and recorded the different parameters. 
-This process was repeated a hundred times in order to obtain a distribution for each CCF parameter. 
-The standard deviations of the resulting distributions provide standard errors for each CCF parameters.
-
-The standard errors were computed for each CCF parameter for all the HARPS measurements of HD215152, HD192310 and Corot-7.
+To do so random Gaussian noise with standard deviation the square-root of the flux was added across each spectrum. 
+The CCF was calculated using this spectrum according to the method presented in \citet{Pepe-2002a}, then fit by either a Normal or SN density with the parameters recorded. 
+This process was repeated a hundred times in order to obtain a distribution for each CCF parameter, and the standard deviations of the resulting distributions provide estimates of the standard errors for the CCF parameters.
+
+The standard errors were computed for each CCF parameter for the HARPS measurements of HD215152, HD192310 and Corot-7. 
 These three stars include measurements that cover the range of SNR measured at 550 nm (SNR550) from 10 to 500, which represent a very low SNR and the saturation limit of the HARPS detector, respectively.
-HD10700 and Alpha Cen B were not included because they have a large number of measurements, which would require a substantial computational effort.
+HD10700 and Alpha Centauri B were not included because they have a large number of measurements, which would require a substantial computational effort.
 The variation of the noise for each CCF parameter as a function of SNR550 is displayed in Fig.~\ref{fig:se}.
-The top plots show the standard errors of the three different estimated RV's, the width, and the asymmetry estimates. 
+The top row shows the standard errors of the three different estimated RV's, the width, and the asymmetry estimates. 
 Note that because BIS SPAN and $\gamma$ do not have the same units, the estimated slopes of the correlation between those two parameters to transform $\gamma$ in \ms were used (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star).
-The bottom plots show the ratio between the standard errors measured when using the SN parameters and the Normal parameters.
-Values smaller or larger than one will imply that standard errors from the SN parameters are respectively more or less precise than the Normal parameters.
+The bottom row shows the ratio between the standard errors measured when using the SN parameters and the Normal parameters.
+Values smaller (larger) than one will imply that standard errors from the SN parameters are more (less) precise than the Normal parameters.
 
@@
 This suggests that for the stars considered, the precision in each RV estimate may be driven by the SNR of the analyzed spectra.
-This is not surprising as the three stars studied have very similar spectral types.
-They are all main sequence K-dwarfs.
-
-When comparing the three different estimates for the RV, the SN mean RV presents standard errors that are 60\% larger than the N mean RV.
+This is not surprising as the three stars studied have very similar spectral types; they are all main sequence K-dwarfs.
+
+When comparing the three different estimates for the RV, the SN mean RV has standard errors that are 60\% larger than the N mean RV.
 However, the SN median RV gives errors 10\% more precise than N mean RV.
@@
 Finally, for the asymmetry parameters, $\gamma$ has standard errors that are 15\% more precise than BIS SPAN. 
-In conclusion, when fitting a SN density to the CCF and using as RV estimate SN median RV, we are able to improve by 10\% the precision on the estimated RV.
-using the SN density we are also able to improve by 15\% the precision on the estimated asymmetry parameter of the CCF.
-Both these improvements do not lead to a worse precision on the estimated width of the CCF.
-SN mean RV should not be use to derive precise estimated RVs, except perhaps in specific conditions described below, as the precision on this parameter is 60\% worse than the precision on the RVs derived from N mean RV.
+In conclusion, when fitting a SN density to the CCF and using SN median RV as the RV estimate, we are able to improve the precision on the estimated RV by 10\%, using the SN density we are also able to improve by 15\% the precision on the estimated asymmetry parameter of the CCF.
+However, the SN mean RV should not be use to derive precise RV estimates
+%%, except perhaps in specific conditions described below, 
+as the precision on this parameter is 60\% worse than the precision on the RVs derived from N mean RV.
 %

### 2018-07-09 manuscript.tex
added Yale HPC to acknowledgements

@@
 
-We are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
+The authors are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
+The authors also thank Yale's Center for Research Computing for their help and resources with some of the computational aspects of this work.
 XD is grateful to The Branco Weiss Fellowship--Society in Science for its financial support.
@@
 US was partially supported by Fondazione CARIPARO. \umberto{check if there is a code or something}
+
 %-----------------------------------------------------------------------------------------------------------------------------------------------

### 2018-07-10 manuscript.tex
updated discussion

@@
 
-When fitting a SN density to the CCF, parameters that describe the RV (i.e.
+When fitting a SN density shape to the CCF, parameters used to define the RV (i.e.
 the CCF barycenter), the amplitude (sometimes called the CCF contrast), the width and the asymmetry of the CCF can all be estimated in a single model framework.
 For the estimation of the RV, we investigated the use of the mean and the median of the SN density. 
-Then the width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry by using $\gamma$, the naturally available skewness parameter of the SN density.
-
-To evaluate the performance of the proposed SN framework, tests on both simulated and real data were carried out and compared to the commonly employed approach consisting of fitting a Normal density shape (for estimating the RV and FWHM) and then separately deriving the BIS SPAN (for estimating the asymmetry).
+The width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry by using $\gamma$, skewness parameter of the SN density.
+
+To evaluate the performance of the proposed SN framework, tests on both simulated and real data were carried out and compared to the commonly employed approach of fitting a Normal density shape (for estimating the RV and FWHM) and then separately deriving the BIS SPAN (for estimating the asymmetry).
 The simulated CCFs were generated using the SOAP 2.0 code, which can simulate activity signals induced by a spot or a facula on a solar-like star.
-The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method.
-In this case, sensitivity was measured using the correlation between the asymmetry and the estimated RVs; both SN mean RV and SN median RV had a stronger correlation with gamma than the correlation between N mean RV and BIS SPAN.
+The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method, making them more useful indicators of activity.
+In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; both SN mean RV and SN median RV had a stronger correlation with $\gamma$ than the correlation between N mean RV and BIS SPAN.
 Moreover, the correlation between the FWHM and the estimated RVs is also stronger when using the parameters from the SN compared to the parameters from the Normal. 
@@
 
-We also propose a new model to correct the estimated RV data for stellar activity signals. 
-Generally, when fitting for planetary signals, it is common to use a model composed of one or several Keplerian signals to account for the planets, in addition to a linear combination of the FWHM and BIS SPAN to account for stellar activity signals.
-The proposed model adds an additional term to account for the amplitude of the CCF, and an interaction term between the estimated asymmetry and the width parameters. 
-Using the simulated data from SOAP 2.0, this new model reduces the effect of the stellar activity signal by a factor of 2 and 3.5 over the usual model, respectively for the facula and spot.
-
 The conclusion found for the SOAP 2.0 simulations that the correlation between the CCF asymmetry and the estimated RV, as well as between the CCF width and the estimated RV, is stronger for the SN parameters than the Normal ones also holds when using real data.
 %
-However, the stronger asymmetry-RV correlation for the simulated data is between $\gamma$ and SN median RV, while it is between $\gamma$ and SN mean RV for the real data.
-There could be several reasons for this difference. It may be due to the fact that SOAP 2.0 uses the spectrum of a spot as input to model the stellar activity induced by a facula.
-Because the temperature between a spot and a faculae is significantly different, their spectra should be different. 
-Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region.
+However, the strongest asymmetry-RV correlation for the simulated data is between $\gamma$ and SN median RV, while it is between $\gamma$ and SN mean RV for the real data.
+There could be several reasons for this difference. 
+First, noting that the SOAP 2.0 is a simulation and, hence, is an imperfect representation of reality so it is not unexpected that there are differences between the simulated and real data.
+For example, some differences may be due to the fact that SOAP 2.0 uses the spectrum of a spot as input to model the activity induced by a facula.
+Because the temperature between a spot and a facula is significantly different, their spectra should be different. 
+Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region on the equator.
 %\xavier{The fact that we also find significant differences between the simulated and real data for the correlations between BIS SPAN and N mean RV and between FWHM and N mean RV shows that the SOAP 2.0 simulation studied here are too simple to explain the complexity of stellar activity in real RV observations.}
@@
 Nevertheless, in both the simulated and the real cases, the parameters derived from the SN are generally more sensitive to activity than the parameters derived from the Normal.
-Also, the correlation between the asymmetry and the SN mean RV is always stronger than the parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
-Since if an apparent RV signal is induced by activity generally a strong correlation will be observed between the RV and the FWHM of the CCF or its BIS SPAN, to use the SN density to fit the CCF leads to a better understanding of the spurious variations in RV caused by stellar activity.
+Also, the correlation between the asymmetry and the SN mean RV is consistently stronger than the parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
+Because the apparent RV signal induced by activity  
+results in a stronger correlation with the SN parameters
+than between the apparent RV signal and the FWHM of the CCF or its BIS SPAN, this suggests the SN model of the CCF can lead to a better understanding of the spurious variations in RV caused by stellar activity.
 
@@
 
-Having an estimator of RV that is more sensitive to stellar activity, such as the SN mean RV, can help with better probing stellar rotational periods or better understanding the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}.
-We saw in the previous section that the SN mean RV estimator is 60\% noisier than the N mean RV estimator. 
+Having an estimator of RV that is more sensitive to stellar activity, such as the SN mean RV, can also help to better probe stellar rotational periods or to better understand the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}.
+We saw that the SN mean RV estimator is 60\% noisier than the N mean RV estimator. 
 This is not necessarily a negative aspect. 
-Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring the SN mean RV, even if the uncertainties related to this parameter are increased by 60\%.
-
-Even if the different RV estimators generally have different amplitudes, once the new correction for stellar activity is applied, the residuals of the model have similar rms.
+For example, in the case where photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring the SN mean RV, even if the uncertainties related to this parameter are increased by 60\%.
+\jessi{I'm not sure I agree with the previous statements - more uncertainty means you would be less certain if the RV estimate is due to actual stellar activity or just photon noise}
+
+We also propose a new model to correct the estimated RV data for stellar activity signals. 
+Generally, when fitting for planetary signals, it is common to use a model composed of one or several Keplerian signals to account for the planets, in addition to a linear combination of the FWHM and BIS SPAN to account for stellar activity signals.
+The proposed model adds to the linear model a term to account for the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters. 
+Using the simulated data from SOAP 2.0, this new model reduces the effect of the stellar activity signal by factors of about 2 and 3.5 over the usual model for the facula and spot, respectively.
+
+Even if the different RV estimators result in different amplitudes, once the proposed correction for stellar activity is applied, the residuals of the model have similar rms.
 When comparing the activity correction proposed in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, for the simulations based on the presence of a facula or a spot the new proposed correction almost entirely explains the spurious variations in RV.
 However, when moving to real data, there is just a slight improvement by using the proposed correction function for stellar activity.
-Anyway, we encourage the community to use this new simple linear model if the goal is to reduce activity without considering the computationally expensive use of Gaussian Process.
-A further analysis of the p--value for each coefficient can be performed to see the ones that are not relevant and that can therefore be removed.
-
+A further analysis can be performed to see if certain components of the model are not relevant and that can therefore be removed.
+
+\jessi{The following paragraph needs to be updated with the new results}
 A test was carried out to see if some RV estimates were better at finding planets in RV data affected by observed stellar signals. 

### 2018-07-10 manuscript.tex
updated conclusion

@@
 For example, in the case where photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring the SN mean RV, even if the uncertainties related to this parameter are increased by 60\%.
-\jessi{I'm not sure I agree with the previous statements - more uncertainty means you would be less certain if the RV estimate is due to actual stellar activity or just photon noise}
+\jessi{I'm not sure I agree with the previous statements - more uncertainty means you would be less certain if the RV estimate is due to actual stellar activity or just photon noise.
+It is also stated throughout that precise estimates are needed (e.g.
+in the conclusion)}
 
@@
 The correlations between the width or asymmetry of the CCF and the estimated RV are commonly used as a way to detect if the RVs are affected by stellar activity signals.   
-Because the presence of real planets would result in only a shift in the CCF (not a change on its shape), strong correlations between the shape features of the CCF and the estimated RVs suggest that stellar activity may be present.
-
-In this paper, a new approach for measuring shape changes in the CCF is proposed using the SN density to estimate the RV and the shape of the CCF. 
+Because the presence of real planets would result in only a shift in the CCF (not a change of its shape), strong correlations between the shape features of the CCF and the estimated RVs suggest that stellar activity may be present.
+
+In this paper, a new approach for quantifying shape changes in the CCF is proposed using the SN density, which can be used to estimate the RV, and the width and skewness of the CCF. 
 This new method is compared to a commonly used method based on a Normal density fit to the CCF.
 The mean of the Normal density is used as the estimated RV and the FWHM estimates the width of the CCF.
-Because the Normal density does not have any skewness, another method is necessary to estimate the asymmetry of the CCF; for this goal the BIS SPAN is often employed.
+Because the Normal density does not have any skewness, another method is necessary to estimate the asymmetry of the CCF, such as the often employed BIS SPAN.
 In addition, the proposed SN approach is compared to other parameterizations of the CCF asymmetry that have been shown to be sensitive to activity signals \citep[][]{Boisse-2011,Figueira-2013}.
 
-In the different tests carried out for this work, the SN parameters performed at least as well (and often times better) as the parameters from the Normal approach and the BIS SPAN.
-The SN parameters $\gamma$, SN FWHM and SN mean RV always show stronger correlation than the correlations between any of the parameters derived by the Normal and the BIS SPAN, or the different asymmetry parametrizations presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
+In the different tests carried out for this work, the SN parameters performed at least as well as (and often times better than) the parameters from the Normal approach and the BIS SPAN.
+The SN parameters $\gamma$, SN FWHM, and SN mean RV consistently had stronger correlation than those between any of the parameters derived by the Normal and the BIS SPAN, or the different asymmetry parametrizations presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
 This suggests the SN parameters may be better at probing stellar activity signals than the other methods. 
-In addition, the uncertainties measured on SN median RV and $\gamma$ are respectively 10\% and 15\% smaller than the corresponding uncertainties on N mean RV and BIS SPAN.
-
-Because of the advantages of using the proposed SN approach over the commonly employed approach based on the Normal density fit to the CCF and the BIS SPAN or the asymmetry parameters described in \citet{Boisse-2011} and \citet{Figueira-2013}, to fit a SN density to the CCF may be more useful for detecting stellar activity than the previously proposed parametrizations.
+In addition, the uncertainties measured on SN median RV and $\gamma$ are respectively 10\% and 15\% smaller than the corresponding uncertainties on N mean RV and BIS SPAN, though the SN mean RV had uncertainties 60\% greater than the N mean RV.
+
+Because of the advantages of using the proposed SN approach over the commonly employed approach based on the Normal density fit to the CCF and the BIS SPAN or the asymmetry parameters described in \citet{Boisse-2011} and \citet{Figueira-2013}, a SN density model for the CCF may be more useful for detecting stellar activity than the previously proposed parametrizations.
 Correlations between $\gamma$ and the SN mean RV, and between the width and the SN mean RV can be used to probe stellar activity signals in RV data, and the SN median RV can be used to estimate RV.

### 2018-07-10 manuscript.tex
updated appendix

@@
 \xavier{All those data are public and were found on the ESO archive.
-We have an acknowledgement for that} \jessi{Are there papers that can/should be cited here for the datasets used?}
-
-Table~\ref{table:summaryStars} summarizes the results obtained by the SN and Normal densities. 
+We have an acknowledgement for that} \jessi{Are there papers that can/should be cited here for the datasets used?
+It is important for reproducibility.}
+
+Table~\ref{table:summaryStars} summarizes the results obtained by the SN and Normal density models of the CCF. 
 These results are consistent with those from the analysis of Alpha Centauri B. 
@@
 The correlation between SN FWHM and SN mean RV is stronger than the correlation between FWHM and N mean RV for three of the four stars.  
-Also for all these stars the originally estimated RVs were corrected from spurious variations in RVs caused by stellar activity using Eq.
-\ref{eq:RV:correction}.
-Fig. \ref{fig:HD192310:correctionRV}--\ref{fig:HD215152:correctionRV} show the resulting corrected RVs. 
+Also for all these stars, the originally estimated RVs were corrected from spurious variations caused by stellar activity using Eq.
+\ref{eq:RV:correction} and Fig.~\ref{fig:HD192310:correctionRV}, \ref{fig:HD10700:correctionRV}, \ref{fig:HD215152:correctionRV}, and \ref{fig:Corot-7:correctionRV}, show the corrected RVs.
 Once corrected from stellar activity, the Normal and SN residuals are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$.
@@
 %\xavier{$\text{HD}215152$ and Corot-7 have in average a lower SNR at 550 nm than HD10700 and HD192310, 273, 207, 141 and 44, respectively.}
-$\text{HD}215152$ and Corot-7 have in average a lower SNR at 550 nm than HD10700 and HD192310.
+$\text{HD}215152$ and Corot-7 have on average a lower SNR at 550 nm than HD10700 and HD192310.
 The average SNR at 550 nm for the stars \text{HD}10700, \text{HD}192310, $\text{HD}215152$ and Corot-7 are respectively 273, 207, 141 and 44.

### 2018-07-11 manuscript.tex
appendix fig references
Xavier's correction

@@
 Because the Normal density is symmetric, the skewness is not defined and therefore a separate approach is necessary to estimate the skewness of the CCF.
-An estimated skewness parameter is generally obtained by calculating the BIS SPAN of the CCF \citep[see Sect. \ref{intro}, and e.g.][]{Queloz-2001}. 
-%
-
-With the proposed SN approach, we propose two estimators of the RV: the mean and median of the SN model fit (referred to as SN mean RV and SN median RV, respectively), and present advantages and limitations for both of these choices in Sec.
-\ref{sec:4} and Sec.
-\ref{sec:5}.
+An estimated skewness parameter is generally obtained by calculating the BIS SPAN of the CCF \citep[see Sec.~\ref{intro}, and e.g.][]{Queloz-2001}. 
+%
+
+With the proposed SN approach, we propose two estimators of the RV: the mean and median of the SN model fit (referred to as SN mean RV and SN median RV, respectively), and present advantages and limitations for both of these choices in Sec.~\ref{sec:4} and Sec.~\ref{sec:5}.
 The width of the SN, SN FWHM, is defined in the same way as for the Normal density\footnote{Note that SN FWHM does not correspond to the width of the SN density at half maximum like in the Normal case.}, and finally the skewness of the CCF is estimated by the $\gamma$ parameter.
@@
 2 in ][]{Dumusque-2014b}.
-The benefits of including a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better understood through the results of the examples presented in Sec.\ref{sec:soap}.
+The benefits of including a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better understood through the results of the examples presented in Sec.~\ref{sec:soap}.
 This interaction term can account for possible interactions between SN FWHM (or FWHM) and $\gamma$ (or BIS SPAN), meaning that each  variables' association with the response, $RV_{\text{activity}}$, depends also on the other variable.
@@
 
-For a given configuration of spots and faculae on the stellar surface, SOAP 2.0 outputs simulated CCF as a function of rotational phase.
+For a given configuration of spots and faculae on the stellar surface, SOAP 2.0 outputs simulated CCFs as a function of rotational phase.
 The code also returns the RV and the FWHM estimated using a Normal model for the CCF, and the BIS SPAN obtained by calculating the bisector of the CCF.
@@
 The stellar effective temperature is set to 5778 K, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
-In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generate with a width of 40 \kms\, and considering initial spectra with a spectral resolution of R=115'000.
+In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with a spectral resolution of R=115'000.
 
@@
 Therefore, the SN parameters may better probe stellar activity.
-We investigate this feature further in the following two sections, where we consider simulated data with a single spot and a spot plus a planet, and in Sec~\ref{sec:4} with real observations.
+We investigate this feature further in the following two sections, where we consider simulated data with a single spot and a spot plus a planet, and in Sec.~\ref{sec:4} with real observations.
 
@@
 
-In Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms, for any of the different RV estimates.
+In Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms smaller than 0.38 \ms, for any of the different RV estimates.
 When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the facula.
@@
 A total of $1808$ CCFs that were derived from the spectra of Alpha Centauri B taken in 2010 by the HARPS spectrograph have been analyzed.
-Note that more observations were carried out that year, however only the data that was not significantly affected by contamination from Alpha Centauri A was used \citep[see][]{Dumusque-2012}.
+Note that more observations were carried out that year, however only the data that were not significantly affected by contamination from Alpha Centauri A were used \citep[see][]{Dumusque-2012}.
 The selected observations represent arguably, among all RV data existing, the best sampled and most precise RV data set showing strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.
@@
 \jessi{How is the slope 720?
-It looks like it should be around 0.0005.}
+It looks like it should be around 0.0005.} \xavier{Indeed, you can simply invert the x and y axis}
 (top right) RVs as function of Julian Day for Alpha Centauri B in 2010.
@@
 %
-Another feature that suggests the presence of faculae is the strong positive measured correlation between $\gamma$ and SN mean RV and  between SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot}.
-%
-In Sec.~\ref{sec:soap.spot}, we saw that a spot induces a negative correlation between $\gamma$ and SN mean RV and weak correlations are measured between SN FWHM and SN mean RV.
+Another feature that suggests the presence of faculae is the strong positive measured correlation between $\gamma$ and SN mean RV and  between SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot},
+as we saw in Sec.~\ref{sec:soap.spot} that a spot induces a negative correlation between $\gamma$ and SN mean RV and weak correlations are measured between SN FWHM and SN mean RV.
 \citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
@@
 It is clear in the case of Alpha Centauri B that the correlation found between $\gamma$ and SN mean RV is the strongest.
-The Pearson correlation coefficient is $R=0.74$, while the next strongest is $R=0.42$ for all the other asymmetry-RV correlations (except the $\gamma$-SN median RV, which is $R=0.56$).
-The correlations between the width and the RV estimates for Alpha Centauri B, the correlation is strongest for the SN parameters, with $R=0.82$ for SN FWHM-SN mean RV, compared to $R=0.70$ for FWHM-N mean RV.
+The Pearson correlation coefficient is $R=0.74$, while the next strongest is $R=0.42$ for all the other asymmetry-N mean RV correlations.
+The correlations between the width and the RV estimates for Alpha Centauri B is also the strongest for the SN parameters, with $R=0.82$ for SN FWHM-SN mean RV, compared to $R=0.70$ for FWHM-N mean RV.
 %
@@
 the proposed linear model that corrects for stellar activity does not necessarily perform better in the SN case than in the Normal case. 
-The new correction for stellar activity proposed in Sec.~\ref{sec:31} performed similarly to the usual correction that uses only a linear combination of the width and the asymmetry of the CCF, but has RV rms that are 6\,\cms\,smaller than the usual correction.
-\jessi{Should this be 8\cms?}
+The new correction for stellar activity proposed in Sec.~\ref{sec:31} performed similarly to the usual correction that uses only a linear combination of the width and the asymmetry of the CCF, however it still gives RV rms that are 8\,\cms\,smaller than the usual correction.
 
@@
 Except for the special case discussed above for HD10700, the analyses of those four stars, in addition to the analyses on Alpha Centauri B, show that the parameters derived when using a SN density are generally more sensitive to activity.
-Therefore using the SN parameters, and in particular estimating RV using SN mean RV, can lead to better detection of stellar activity over the Normal parameters. 
+Therefore using the SN parameters, and in particular estimating RV using SN mean RV, can carryout to better detection of stellar activity over the Normal parameters. 
 More specifically, this is the case for the evaluation of the asymmetry-RV correlations for Alpha Centauri B, HD10700, HD215152, HD192310 and Corot-7, and the width-RV correlation for Alpha Centauri B, HD215152, HD192310 and Corot-7 (see Appendix \ref{appendix}).
@@
 When correcting for stellar activity for  Alpha Centauri B, although the uncorrected RV rms was larger for SN mean RV (compared to the RVs obtained using N mean RV), once corrected for activity using the new model proposed in Sec.~\ref{sec:31}, both RVs estimates had similar residuals.
-For HD10700, HD215152, and HD192310, the proposed and usual models had comparable corrected RV rms.
+For HD10700, HD215152, and HD192310, the proposed and usual models were giving similar RV residual rms.
 %%%We also observe slight differences in the rms between the new proposed correction and the usual correction, which uses only a linear combination of the width and the asymmetry of the CCF.  
-However, for Corot-7, the new correction is able to provide RV residual rms 30\,\cms \jessi{Should this be 23?} smaller than the one obtained with the usual correction.
+However, for Corot-7, the new correction is able to provide RV residual rms 23\,\cms\,smaller than the one obtained with the usual correction.
 
@@
 To simulate a planetary signal, the CCFs were blue- or red-shifted with the desired amplitude, period, and phase.
-Several RV data sets with the same stellar signal, but different planetary signals were injected using parameters corresponding to the following grid:
+Several RV data sets with the same stellar signal, but different planetary signals were generated using parameters corresponding to the following grid:
 \begin{itemize}
@@
 If a signal with a P-value\footnote{The P-values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected.
-Finally, for each period considered, the minimum amplitude at which at least 50\% of the planets with different phases were detected was found.
+Finally, for each period considered, the minimum amplitude at which at least 80\% of the planets with different phases were detected was found.
 The results are shown in Fig.~\ref{fig:detection_limits}.
@@
 and therefore close to the semi-periodicity of the stellar activity signal. In such a case, the activity 
-correction absorbs part of the planetary signal and a stronger planetary signal is needed at these periods in order for them to be detectable.
+correction absorbs part of the planetary signal and a stronger planetary signal is needed at these periods in order for them to be detected.
 
@@
 Therefore, we cannot simply vary each point in the CCF by their respective error bars and then recalculate the best SN or Normal density fit to see how the CCF noise influences the estimation of the parameters of interest (i.e., N mean RV, SN mean RV, SN median RV, FWHM, SN FWHM, BIS SPAN and $\gamma$).
-Instead, we go to the individual spectra where the individual measurements can be considered independent from the other points.
+Instead, we go to the individual spectrum where each individual points can be considered independent from the others.
 The standard error on each point of a spectrum is given by the photon noise, which follows a Poisson distribution and is therefore estimated by taking the square-root of the measured flux.
@@
 The standard errors were computed for each CCF parameter for the HARPS measurements of HD215152, HD192310 and Corot-7. 
-These three stars include measurements that cover the range of SNR measured at 550 nm (SNR550) from 10 to 500, which represent a very low SNR and the saturation limit of the HARPS detector, respectively.
+These three stars include measurements that cover the range of SNR measured at 550 nm (SNR550) from 10 to 500, which represent the very low SNR limit and the saturation limit of the HARPS detector, respectively.
 HD10700 and Alpha Centauri B were not included because they have a large number of measurements, which would require a substantial computational effort.
@@
 Finally, for the asymmetry parameters, $\gamma$ has standard errors that are 15\% more precise than BIS SPAN. 
-In conclusion, when fitting a SN density to the CCF and using SN median RV as the RV estimate, we are able to improve the precision on the estimated RV by 10\%, using the SN density we are also able to improve by 15\% the precision on the estimated asymmetry parameter of the CCF.
+In conclusion, when fitting a SN density to the CCF and using SN median RV as the RV estimate, we are able to improve the precision on the estimated RV by 10\%.
+Using the SN density, we are also able to improve by 15\% the precision on the estimated asymmetry parameter of the CCF.
 However, the SN mean RV should not be use to derive precise RV estimates
@@
 The complete results of the analyses of the correlations for the four stars are presented in Fig.
-\ref{fig:Gliese785:corrPlot}--\ref{fig:Corot7:corrPlot}.}
+\ref{fig:Gliese785:corrPlot}, \ref{fig:Tau:corrPlot}, \ref{fig:HD215152:corrPlot}, and \ref{fig:Corot7:corrPlot}.}
 \label{table:summaryStars}

### 2018-07-12 manuscript.tex
Xavier Corrections
Went through all the paper, except the section on planetary detection limits, and modified the abstract to have something more concise and easier to read.

@@
 \abstract
+%% Context, Aims, Methods, Results, Conclu (not mandatory)
+%{Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
+%Stellar activity can be probed by measuring time dependent variations in the shape of the cross-correlation function (CCF), often estimated using different parameters of the modelled CCF.
+Therefore to estimate the parameters of the CCF with high precision is essential to de-correlate the signal of an exoplanet from spurious RV signals caused by stellar activity.}
+%%
+%{We propose to estimate the parameters of the CCF by fitting a Skew Normal (SN) density which, unlike the commonly employed Normal density, includes a skewness parameter to capture the asymmetry of the CCF induced by stellar activity and also the natural asymmetry induced by convective blueshift.}
+%%Moreover, the SN distribution allows for different location parameters beyond the mean, such as the median of the CCF.}
+%%
+%{The performances of the proposed method are compared to the commonly employed Normal density using both simulations and real observations, with different levels of activity and signal-to-noise ratio (SNR) levels.}
+%%We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (SNR) levels.
+In each case, we compare the results obtained by fitting to the CCF respectively a Normal and a SN.
+We also estimate rigorous errors for the different moments of the CCF using a bootstrap analysis.
+%%
+%{When considering real observations, the correlation between the RV and the asymmetry of the CCF and the correlation between the RV and the width of the CCF are stronger when using the parameters estimated with the SN rather than the ones obtained with the commonly employed Normal density.
+%In particular the strongest correlations have been obtained when using the mean of the SN as an estimate for the RV. 
+%This suggests that the asymmetry of the CCF and the width of the CCF estimated using a SN density may be more sensitive to stellar activity, which can be helpful when estimating stellar rotational periods and in general when characterizing stellar activity signals.
+%Using the proposed SN approach, the uncertainties estimated on the RV defined as the median of the SN are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal. 
+%The uncertainties estimated on the asymmetry parameter of the SN are on average $15\%$ smaller than the uncertainties measured on the Bisector Inverse Slope Span (BIS SPAN), which is the commonly used parameter to evaluate the asymmetry of the CCF.
+}
+%%
+%{The SN density shape appears to be useful for characterizing the CCF since the correlations used to probe stellar activity are stronger and the uncertainties associated of the estimates for RV and the asymmetry of the CCF are both smaller than those derived from other commonly employed strategies.
+%}
+%
 % Context, Aims, Methods, Results, Conclu (not mandatory)
 {Stellar activity is one of the primary limitations to the detection of low-mass exoplanets using the radial-velocity (RV) technique. 
-Stellar activity can be probed by measuring time dependent variations in the shape of the cross-correlation function (CCF), often estimated using different parameters of the modelled CCF.
-Therefore to estimate the parameters of the CCF with high precision is essential to de-correlate the signal of an exoplanet from spurious RV signals caused by stellar activity.}
-%
-{We propose to estimate the parameters of the CCF by fitting a Skew Normal (SN) density which, unlike the commonly employed Normal density, includes a skewness parameter to capture the asymmetry of the CCF induced by stellar activity and also the natural asymmetry induced by convective blueshift.}
-%Moreover, the SN distribution allows for different location parameters beyond the mean, such as the median of the CCF.}
+Stellar activity can be probed by measuring time-dependent variations in the shape of the cross-correlation function (CCF). It is therefore 
+critical to measure with high-precision these shape variations to de-correlate the signal of an exoplanet from spurious RV signals caused 
+by stellar activity.}
+%
+{We propose to estimate the variations in shape of the CCF by fitting a Skew Normal (SN) density which, unlike the commonly employed Normal density, includes a skewness parameter to capture the asymmetry of the CCF induced by stellar activity and the convective blueshift.}
 %
 {The performances of the proposed method are compared to the commonly employed Normal density using both simulations and real observations, with different levels of activity and signal-to-noise ratio (SNR) levels.}
-%We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (SNR) levels.
-In each case, we compare the results obtained by fitting to the CCF respectively a Normal and a SN.
-We also estimate rigorous errors for the different moments of the CCF using a bootstrap analysis.
-%
-{When considering real observations, the correlation between the RV and the asymmetry of the CCF and the correlation between the RV and the width of the CCF are stronger when using the parameters estimated with the SN rather than the ones obtained with the commonly employed Normal density.
+%
+{When considering real observations, the correlation between the RV and the asymmetry of the CCF and between the RV and the width of the CCF are stronger when using the parameters estimated with the SN density rather than the ones obtained with the commonly employed Normal density.
 In particular the strongest correlations have been obtained when using the mean of the SN as an estimate for the RV. 
-This suggests that the asymmetry of the CCF and the width of the CCF estimated using a SN density may be more sensitive to stellar activity, which can be helpful when estimating stellar rotational periods and in general when characterizing stellar activity signals.
+This suggests that the CCF parameters estimated using a SN density are more sensitive to stellar activity, which can be helpful 
+when estimating stellar rotational periods and more in general when characterizing stellar activity signals.
 Using the proposed SN approach, the uncertainties estimated on the RV defined as the median of the SN are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal. 
@@
 }
-{The SN density shape appears to be useful for characterizing the CCF since the correlations used to probe stellar activity are stronger and the uncertainties associated of the estimates for RV and the asymmetry of the CCF are both smaller than those derived from other commonly employed strategies.
+%
+{The SN density is a better model than the Normal density for characterizing the CCF since the correlations used to probe stellar activity are stronger and the uncertainties of the RV estimate and the asymmetry of the CCF are both smaller.
 }
-%{We strongly encourage the use of the SN distribution to retrieve the different parameters of the CCF.
-The correlation between the mean of the SN and the asymmetry parameter of the CCF and the correlation between the mean of the SN and the width parameter of the CCF probe better stellar activity signals than when using the parameters retrieved with the Normal distribution.
-Using the SN distribution leads to smaller uncertainties for both the median of the SN and the asymmetry of the CCF than using the commonly employed Normal density.
-Finally, all the parameters are available in one single fit to the CCF.
-%}
-%
-%{The derived benefits of using the proposed SN approach includes an asymmetry parameter along with several options for estimating the RV, while the Normal model only includes an RV estimate and requires a separate procedure for estimating the asymmetry.
-Furthermore, the estimated uncertainties on the RVs and the asymmetry parameter are smaller in the SN setting.}
-%The correlation between the RVs and the asymmetry of the CCF and the correlation between the RVs and the width of the CCF are always stronger when using the parameters derived from the SN in the case of real observations.
-Therefore the CCF asymmetry and the CCF width derived using a SN are more sensitive to stellar activity, which allows to probe with a better precision stellar rotational periods, in addition to characterize more precisely stellar activity signals.
-The precision on the estimated set of RVs, derived using the median of the fitted SN densities are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal.
-In addition, the uncertainties related to the asymmetry parameter derived from the SN are on average $15\%$ smaller than the ones calculated on the common Bisector Inverse Slope Span (BIS SPAN).
-We strongly encourage the use of the SN density rather than the Normal density, because this allows us to retrieve in one single fit the different moments of the CCF, because the derived moments better catch stellar activity signals and finally because the standard errors on the RVs and the the asymmetry parameter are smaller than the one estimated with the Normal fit.
 
@@
 There could be several reasons for this difference. 
-First, noting that the SOAP 2.0 is a simulation and, hence, is an imperfect representation of reality so it is not unexpected that there are differences between the simulated and real data.
+First, noting that SOAP 2.0 is a simulation and, hence, is an imperfect representation of reality so it is not unexpected that there are differences between the simulated and real data.
 For example, some differences may be due to the fact that SOAP 2.0 uses the spectrum of a spot as input to model the activity induced by a facula.
@@
 
-Considering the different RV estimates of the real data, the amplitude of stellar activity tends to be largest for the SN mean RV, followed by the SN median RV, and finally by N mean RV. 
-Although there appears to be a larger difference between the SN mean RV and the SN median RV, the SN median RV is similar to the N mean RV. 
-Hence, the mean of the SN density appears to be more sensitive to variation in the CCF shape than the median of the SN or the mean of the Normal.  
+Considering the different RV estimates of the real data, the amplitude of stellar activity tends to be largest for the SN mean RV, followed by the SN median RV and N mean RV that are extremely similar.
+This implies that the mean of the SN density appears to be more sensitive to variation in the CCF shape than the median of the SN or the mean of the Normal.  
 %This is not surprising as the SN density is able to model the asymmetry of the CCF, what the Normal density does not.
@@
 Finally, we investigated the precision of each of the SN and Normal parameters including the BIS SPAN.
-It turns out that the SN mean RV should not be used to get precise RVs as the standard errors on this parameter is 60\% greater than the N mean RV.
+It turns out that the SN mean RV should not be used to get precise RVs as the standard errors on this parameter is 60\% greater than for N mean RV.
 However, the SN median RV is 10\% more precise than the N mean RV. 
@@
 
-In this paper, a new approach for quantifying shape changes in the CCF is proposed using the SN density, which can be used to estimate the RV, and the width and skewness of the CCF. 
+In this paper, a new approach for quantifying shape changes in the CCF is proposed using the SN density, which can be used to estimate with a single fit the RV, the width and the skewness of the CCF. 
 This new method is compared to a commonly used method based on a Normal density fit to the CCF.
@@
 
-In the different tests carried out for this work, the SN parameters performed at least as well as (and often times better than) the parameters from the Normal approach and the BIS SPAN.
+In the different tests carried out for this work, the SN parameters performed at least as well as, and most of the times better than the parameters from the Normal approach and the BIS SPAN.
 The SN parameters $\gamma$, SN FWHM, and SN mean RV consistently had stronger correlation than those between any of the parameters derived by the Normal and the BIS SPAN, or the different asymmetry parametrizations presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
@@
 Correlations between $\gamma$ and the SN mean RV, and between the width and the SN mean RV can be used to probe stellar activity signals in RV data, and the SN median RV can be used to estimate RV.
+We therefore strongly encourage the community to use this proposed SN parametrisation of the CCF.
 
@@
 
-The authors are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
-The authors also thank Yale's Center for Research Computing for their help and resources with some of the computational aspects of this work.
+The authors thank Yale's Center for Research Computing for their help and resources with some of the computational aspects of this work.
 XD is grateful to The Branco Weiss Fellowship--Society in Science for its financial support.
@@
 US was partially supported by Fondazione CARIPARO. \umberto{check if there is a code or something}
+The authors are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.
 
@@
 
-In this Appendix, a similar analysis as the one presented in Sec.~\ref{sec:4} is discussed for four main-sequence stars: HD192310 (K2V), HD10700 (G8V), HD215152 (K3V) and finally Corot-7 (K0V).
-\xavier{All those data are public and were found on the ESO archive.
-We have an acknowledgement for that} \jessi{Are there papers that can/should be cited here for the datasets used?
-It is important for reproducibility.}
+In this Appendix, a similar analysis as the one presented in Sec.~\ref{sec:4} is discussed for four main-sequence stars: HD192310 \citep[K2V,][]{Pepe-2011}, HD10700 \citep[G8V,][]{Feng:2017ac}, HD215152 \citep[K3V,][]{Delisle:2018aa} and finally Corot-7 \citep[K0V,][]{Haywood-2014}.
+The latest HARPS data for these stars can be found on the ESO archive.
 
@@
 \ref{eq:RV:correction} and Fig.~\ref{fig:HD192310:correctionRV}, \ref{fig:HD10700:correctionRV}, \ref{fig:HD215152:correctionRV}, and \ref{fig:Corot-7:correctionRV}, show the corrected RVs.
-Once corrected from stellar activity, the Normal and SN residuals are comparable for the stars $\text{HD}192310$ and $\text{HD}10700$.
-However, the rms of the residuals for $\text{HD}215152$ are 0.05\,\ms  lower for the SN model than the Normal model, and the rms of the residuals for Corot-7 are 0.34\,\ms lower.
+Once corrected from stellar activity, the Normal and SN residuals are comparable for the stars $\text{HD}192310$, $\text{HD}10700$ and $\text{HD}215152$.
+However, the rms of the residuals for Corot-7 are 0.23\,\ms\,lower for the SN model than the Normal model.
 %\xavier{$\text{HD}215152$ and Corot-7 have in average a lower SNR at 550 nm than HD10700 and HD192310, 273, 207, 141 and 44, respectively.}
-$\text{HD}215152$ and Corot-7 have on average a lower SNR at 550 nm than HD10700 and HD192310.
 The average SNR at 550 nm for the stars \text{HD}10700, \text{HD}192310, $\text{HD}215152$ and Corot-7 are respectively 273, 207, 141 and 44.
+Corot-7 has therefore on average a much lower SNR at 550 nm than the others stars, which could be a potential explanation for this small improvement.
+However further tests on several stars should be perform to confirm this statement.
 

### 2018-07-16 manuscript.tex
Add files via upload
paragraph planetary detection limits updated

@@
 First, the correlation between $\gamma$ and BIS SPAN is evaluated.
-In the left panel of Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to \jessi{See question in figure about this slope} $720$ and a strong Pearson correlation coefficient of $R=0.954$.
+In the left panel of Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.00072$ and a strong Pearson correlation coefficient of $R=0.954$.
 This strong correlation suggests that both $\gamma$ and BIS SPAN are measuring similar asymmetries for the CCFs.
@@
 The strong correlation suggests these two parameters are similarly measuring the asymmetry.
-\jessi{How is the slope 720?
-It looks like it should be around 0.0005.} \xavier{Indeed, you can simply invert the x and y axis}
 (top right) RVs as function of Julian Day for Alpha Centauri B in 2010.
@@
 In the previous section we evaluated the improvement obtained by the SN parameters compared to the Normal parameters and the BIS SPAN.
-We carryout similar analyses for four other main sequence stars: HD192310, HD10700, HD215152 and Corot-7.
+We carryout similar analyses for four other main sequence stars: HD192310 \citep[K2V,][]{Pepe-2011}, HD10700 \citep[G8V,][]{Feng:2017ac}, HD215152 \citep[K3V,][]{Delisle:2018aa} and finally Corot-7 \citep[K0V,][]{Haywood-2014}.
 The same correlations plots and residual plots displayed in the previous section for Alpha Centauri B can be found found for those new four stars in Appendix~\ref{appendix}.
-\jessi{Add explicit references to the datasets}
 
@@
 
-For each of the 4500 simulations considered, the activity correction presented in Eq.~\ref{eq:RV:correction} was applied, and signals in the residuals were investigated using a Generalized Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982, Zechmeister-2009}.
+\umberto{For each of the 4500 simulations considered, Eq.
+\ref{eq:RV:correction.overall} was applied.
+The use of Eq.
+\ref{eq:RV:correction.overall} leads to some additional comments.
+First of all we note that both the function that corrects for stellar activity and the keplerian signal must be simultaneously considered, as shown in Sec.
+\ref{sec:soap.spot.planet}.
+Because of the non linearity of the model that defines the orbital parameters of the exoplanets, non linear least squares \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear} must be used.
+In order to run the algorithm, a set of initial values for the parameters of interest has to be provided.
+Concerning the parameters related to the activity correction, we have chosen as initial values the ones obtained by only considering Eq.~\ref{eq:RV:correction}.
+The selection of the initial values for the orbital parameters of the exoplanet is more challenging.
+In the present study we assumed the circularity of the orbit, hence the parameters to estimate are the amplitude $K$, the epoch at the periapsis $t_0$ and the orbital period $P$.
+As initial value for $K$ we selected the maximum measured RV.
+The epoch at the periapsis $t_0$ is defined as that epoch such that the distance between the planet and the star is the smallest.
+Since in our simulation study the orbit of the planet in circular, the distance star--planet does not change over time, making the choice for $t_0$ arbitrary.
+We selected as initial value for $t_0$ that epoch for which the largest RV was measured.
+When providing an initial value for the orbital period $P$, we note that an initial value far from the true one can result in the non linear least squares algorithm to get stuck in local modes  \citep[][]{levenberg1944method,marquardt1963algorithm}, providing a wrong set of estimates for all the parameters of Eq.
+\ref{eq:RV:correction.overall} We note that in  Sec.
+\ref{sec:soap.spot.planet}, because the amplitude was equal to $K=10 \ms$, a good initial guess for the orbital period was available and local modes were avoided.
+For this reason we selected as initial guess for $P$ a value close to the true orbital period.
+This simplification is motivated by the fact that we are mainly interested in evaluating the goodness of the activity correction function presented in Eq.~\ref{eq:RV:correction} respect to the usual one, based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+In order to properly do that, we need to correctly estimating the orbital parameters of the exoplanets as well.
+Because of the challenges related to the non linearity of the keplerian signal, we assumed to have a good initial guess for the orbital period.
+However, how to correctly estimating the orbital parameters of the extrasolar planet, in particular when no assumption on the eccentricity of the orbit are available, is something to investigate in future analyses.
+
+Once the parameters involved in Eq.
+\ref{eq:RV:correction.overall} have been estimated,  signals in the residuals, defined as $RV - RV_{\text{activity}}$, were investigated using a Generalized Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982, Zechmeister-2009}.
 If a signal with a P-value\footnote{The P-values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected.
 Finally, for each period considered, the minimum amplitude at which at least 80\% of the planets with different phases were detected was found.
-The results are shown in Fig.~\ref{fig:detection_limits}.
-All three of the different RV estimators give similar detection limits.
+The results are shown in Fig.~\ref{fig:detection_limits}, where we also considered the usual function that corrects for stellar activity.
+We can see that the new correction for stellar activity based on Eq.~\ref{eq:RV:correction} slightly improves the detection limit of the exoplanet.
+Concerning the type of location parameter that defines the RV, all three of the different RV estimators give similar detection limits.
 Though more investigations should be considered, these results suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity.
@@
 \includegraphics[height = 2.6in]{detection_limits.pdf} 
-   \caption{Detection limits of planetary signals once the stellar activity signal is removed from the raw RVs using the model proposed in  Eq.~\ref{eq:RV:correction}.
-\jessi{For the black-and-white versions, it would be helpful to have different line types plotted}
-The different RV estimators have similar detection limits.}
+   \caption{Detection limits of planetary signals once the stellar activity signal is removed from the raw RVs using the model proposed in Eq.~\ref{eq:RV:correction} (solid lines) or the usual correction based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit (dashed lines).
+The correction for stellar activity based on Eq.~\ref{eq:RV:correction} slightly improves the detection limit and the different RV estimators have similar detection limits.}
    \label{fig:detection_limits}
@@
 
-Although the detection limits remain relatively constant for the periods  $\leq$15 days, there is a notable increase in the detection limit at 20 and 30 days. 
-This is likely due to the periods of the simulated planets, 20 days and 30 days, are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012}
-and therefore close to the semi-periodicity of the stellar activity signal. In such a case, the activity 
-correction absorbs part of the planetary signal and a stronger planetary signal is needed at these periods in order for them to be detected.
+Although the detection limits remain relatively constant for the periods  $\leq$20 days, there is a notable increase in the detection limit at 25 days. 
+This is likely caused by the fact that the periods of the simulated planets at 25 days are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012} and therefore close to the semi-periodicity of the stellar activity signal.}
 
@@
 in the conclusion)}
+\umberto{Xavier, can you please develop a little bit this statement?
+If I understood correctly, since the correlation between the width and the asymmetry of the CCF with SN mean RV is almost always the strongest, if the star is particularly active we are willing to ``sacrifice'' the precision of the RV if we can end up with a clear indication of strong activity by the star.
+Is it correct?}
 
@@
 
-\jessi{The following paragraph needs to be updated with the new results}
 A test was carried out to see if some RV estimates were better at finding planets in RV data affected by observed stellar signals.
-When using the new correction proposed in this paper to mitigate the effect from stellar activity and when assessing planetary detection based on a periodogram analysis, we find very similar detection limits for the three RV estimators presented in this paper.
-\umberto{trying to understand why we get better results for P=20 days when using the usual correction}
+The new correction based on Eq.~\ref{eq:RV:correction} proposed in this paper to mitigate the effect from stellar activity slightly improves the detection limit respect to the usual one based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+Concerning the definition of the RV using the SN or the Normal fit, all three of the different RV estimators give similar detection limits.
 Therefore it seems that any of the RV estimate can be used to search for planetary signals.
@@
 Correlations between $\gamma$ and the SN mean RV, and between the width and the SN mean RV can be used to probe stellar activity signals in RV data, and the SN median RV can be used to estimate RV.
+\umberto{We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.
+Using simulated data from SOAP 2.0, this new proposed correction reduces the effect of the stellar activity signal by factors of about 2 and 3.5 over the usual model respectively for the facula and spot.
+When using real data and when injecting a fake planets, the detection limit slightly improved if using the new correction for stellar activity over the usual one.}
 We therefore strongly encourage the community to use this proposed SN parametrisation of the CCF.

### 2018-07-16 manuscript.tex
Add files via upload

@@
 This strong correlation suggests that both $\gamma$ and BIS SPAN are measuring similar asymmetries for the CCFs.
-It also provides a conversion between the dimensionless $\gamma$ parameter into \ms\, using the slope of 720 \ms.
+It also provides a conversion between the dimensionless $\gamma$ parameter into \ms\, using the slope of $0.00072$ \ms.
 %\xavier{As $\gamma$ has no units, this will allow us to compare the amplitude of the activity signal seen in $\gamma$ and in BIS SPAN, by using the slope of this correlation as a scaling factor}.
@@
 %
-This behavior is similar to the one observed for the facula simulated with SOAP 2.0 in see Sec.~\ref{sec:soap.faculae}, suggesting that the activity signal could be due to faculae present on Alpha Centauri B.
-%
-Another feature that suggests the presence of faculae is the strong positive measured correlation between $\gamma$ and SN mean RV and  between SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot},
-as we saw in Sec.~\ref{sec:soap.spot} that a spot induces a negative correlation between $\gamma$ and SN mean RV and weak correlations are measured between SN FWHM and SN mean RV.
+This behavior is similar to the one observed for the facula simulated with SOAP 2.0 in Sec.~\ref{sec:soap.faculae}, suggesting that the activity signal could be due to faculae present on Alpha Centauri B.
+%
+Another feature that suggests the presence of faculae is the strong positive measured correlation between $\gamma$ and SN mean RV and  between SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot};
+as we saw in Sec.~\ref{sec:soap.spot} a spot induces a negative correlation between $\gamma$ and SN mean RV and weak correlations are measured between SN FWHM and SN mean RV.
 \citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
@@
 \hline
- $\text{HD}192310  $          &    $1577$    & $0.888$ & $786$ & $0.669 (0.64; 0.695)$\\
-\hline
- $\text{HD}10700 $            &    $7928$    & $0.78$ & $604$ & $0.322 (0.302; 0.342)$\\
-\hline
- $\text{HD}215152 $          &     $273$   &  $ 0.763$ & $794$ & $0.571 (0.485; 0.646)$ \\
-\hline
- $\text{Corot }7$     &     $173$    &  $0.814$  & $607$ & $0.561 (0.450; 0.656)$  \\
+ $\text{HD}192310  $          &    $1577$    & $0.888$ & $0.000786$ & $0.669 (0.64; 0.695)$\\
+\hline
+ $\text{HD}10700 $            &    $7928$    & $0.78$ & $0.000604$ & $0.322 (0.302; 0.342)$\\
+\hline
+ $\text{HD}215152 $          &     $273$   &  $ 0.763$ & $0.000794$ & $0.571 (0.485; 0.646)$ \\
+\hline
+ $\text{Corot }7$     &     $173$    &  $0.814$  & $0.000607$ & $0.561 (0.450; 0.656)$  \\
 \hline

### 2018-07-16 manuscript.tex
Add files via upload
went through the paper, updated slopes in table A.1 and fixed minor typos

@@
 \ref{eq:RV:correction.overall} We note that in Sec.
-\ref{sec:soap.spot.planet}, because the amplitude was equal to $K=10 \ms$, a good initial guess for the orbital period was available and local modes were avoided.
+\ref{sec:soap.spot.planet}, because the semi-amplitude of the injected exoplanet was equal to 10 \ms, a good initial guess for the orbital period was available and local modes were avoided.
 For this reason we selected as initial guess for $P$ a value close to the true orbital period.

### 2018-07-16 manuscript.tex
some updates to 5.3

@@
 However, once corrected for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, as shown in the bottom plots of Fig~\ref{fig:alphacent:correctionRV}, the rms of the residuals are essentially the same for all three approaches.
-In this section, we investigate the ability of the three different RV estimators (N mean RV, SN mean RV, and SN median RV) to detect planetary signals among stellar activity.
-To carryout this test, the minimum detected amplitude of a planetary signal is estimated at different orbital periods when considering data affected by stellar activity.
+In this section, we investigate the ability of the three different RV estimators (N mean RV, SN mean RV, and SN median RV) to detect planetary signals among stellar activity, and also compare them when using the usual stellar activity correction with the proposed stellar activity model of Eq.~\eqref{eq:RV:correction}.
+To carryout this test, the minimum detected amplitude of an imputed planetary signal is estimated at different orbital periods when considering data affected by stellar activity.
 
@@
 
-\umberto{For each of the 4500 simulations considered, Eq.
+For each of the 4500 simulations considered, Eq.
 \ref{eq:RV:correction.overall} was applied.
@@
 Although the detection limits remain relatively constant for the periods  $\leq$20 days, there is a notable increase in the detection limit at 25 days. 
-This is likely caused by the fact that the periods of the simulated planets at 25 days are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012} and therefore close to the semi-periodicity of the stellar activity signal.}
+This is likely caused by the fact that the periods of the simulated planets at 25 days are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012} and therefore close to the semi-periodicity of the stellar activity signal.
 

### 2018-07-16 manuscript.tex
some updates to 5.3

@@
 In this section, we investigate the ability of the three different RV estimators (N mean RV, SN mean RV, and SN median RV) to detect planetary signals among stellar activity, and also compare them when using the usual stellar activity correction with the proposed stellar activity model of Eq.~\eqref{eq:RV:correction}.
-To carryout this test, the minimum detected amplitude of an imputed planetary signal is estimated at different orbital periods when considering data affected by stellar activity.
+To carryout this test, the minimum detected amplitude of an injected planetary signal is estimated at different orbital periods when considering data affected by stellar activity.
 
@@
 
-For each of the 4500 simulations considered, Eq.
-\ref{eq:RV:correction.overall} was applied.
-The use of Eq.
-\ref{eq:RV:correction.overall} leads to some additional comments.
-First of all we note that both the function that corrects for stellar activity and the keplerian signal must be simultaneously considered, as shown in Sec.
-\ref{sec:soap.spot.planet}.
-Because of the non linearity of the model that defines the orbital parameters of the exoplanets, non linear least squares \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear} must be used.
+For each of the 4500 simulations \jessi{please expand on how the above setting results in 4500 simulations} considered, the proposed model from Eq.~\eqref{eq:RV:correction.overall} was fit. 
+The use of Eq.~\eqref{eq:RV:correction.overall} leads to some additional comments.
+First, we note that both the function that corrects for stellar activity and the Keplerian signal must be simultaneously considered, as was carried out in Sec.~\ref{sec:soap.spot.planet}. 
+Because of the non-linearity of the model that defines the orbital parameters of the exoplanets, non-linear least squares \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear} was used.
+%
 In order to run the algorithm, a set of initial values for the parameters of interest has to be provided. 
-Concerning the parameters related to the activity correction, we have chosen as initial values the ones obtained by only considering Eq.~\ref{eq:RV:correction}.
+%
+For the stellar activity correction, the initial values were set at those obtained by only considering Eq.~\eqref{eq:RV:correction}. 
 The selection of the initial values for the orbital parameters of the exoplanet is more challenging. 
-In the present study we assumed the circularity of the orbit, hence the parameters to estimate are the amplitude $K$, the epoch at the periapsis $t_0$ and the orbital period $P$.
-As initial value for $K$ we selected the maximum measured RV.
-The epoch at the periapsis $t_0$ is defined as that epoch such that the distance between the planet and the star is the smallest.
-Since in our simulation study the orbit of the planet in circular, the distance star--planet does not change over time, making the choice for $t_0$ arbitrary.
-We selected as initial value for $t_0$ that epoch for which the largest RV was measured.
-When providing an initial value for the orbital period $P$, we note that an initial value far from the true one can result in the non linear least squares algorithm to get stuck in local modes  \citep[][]{levenberg1944method,marquardt1963algorithm}, providing a wrong set of estimates for all the parameters of Eq.
-\ref{eq:RV:correction.overall} We note that in Sec.
-\ref{sec:soap.spot.planet}, because the semi-amplitude of the injected exoplanet was equal to 10 \ms, a good initial guess for the orbital period was available and local modes were avoided.
+In the present study we assumed a circular orbit, hence the parameters to estimate are the amplitude $K$, the epoch at the periapsis $t_0$, and the orbital period $P$. 
+The initial value for $K$ was set to the maximum measured RV \jessi{what does this mean?  when was the rv measured?}. 
+The epoch at the periapsis $t_0$ is defined as that epoch such that the distance between the planet and the star is the smallest \jessi{how is this known?  where is this value coming from?}.
+%
+Since in our simulation study the orbit of the planet in circular, the distance between the star and planet does not change over time, making the choice for $t_0$ arbitrary \jessi{do you mean the choice of the initial $t_0$ arbitrary?}.
+%
+We selected as initial value for $t_0$ that epoch for which the largest RV was measured \jessi{again, when was the rv measured?}. 
+%
+When providing an initial value for the orbital period $P$, an initial value far from the true one can result in the non-linear least squares algorithm getting stuck in local modes \citep[][]{levenberg1944method,marquardt1963algorithm} and, hence, incorrect estimates for the parameters of Eq.~\eqref{eq:RV:correction.overall}.
+%
+In Sec.
+\ref{sec:soap.spot.planet}, because the semi-amplitude of the injected exoplanet was equal to 10 \ms, \jessi{how is this a reason?
+do you mean because the injected RV was large?} a good initial guess for the orbital period was available and local modes were avoided.
+
 For this reason we selected as initial guess for $P$ a value close to the true orbital period.

### 2018-07-16 manuscript.tex
some updates to 5.3

@@
 do you mean because the injected RV was large?} a good initial guess for the orbital period was available and local modes were avoided.
-
-For this reason we selected as initial guess for $P$ a value close to the true orbital period.
-This simplification is motivated by the fact that we are mainly interested in evaluating the goodness of the activity correction function presented in Eq.~\ref{eq:RV:correction} respect to the usual one, based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
-In order to properly do that, we need to correctly estimating the orbital parameters of the exoplanets as well.
-Because of the challenges related to the non linearity of the keplerian signal, we assumed to have a good initial guess for the orbital period.
-However, how to correctly estimating the orbital parameters of the extrasolar planet, in particular when no assumption on the eccentricity of the orbit are available, is something to investigate in future analyses.
-
-Once the parameters involved in Eq.
-\ref{eq:RV:correction.overall} have been estimated,  signals in the residuals, defined as $RV - RV_{\text{activity}}$, were investigated using a Generalized Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982, Zechmeister-2009}.
+%
+In order to avoid issues with the convergence of the algorithm, the initial guess for $P$ was set to be a value close to the true orbital period for all datasets and methods considered.
+%
+This simplification is reasonable in our setting because our main interest is in evaluating the goodness of the activity correction function presented in Eq.~\eqref{eq:RV:correction} compared to the usual one using $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit or  $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal model of the CCF.
+%
+This requires correct estimation of the orbital parameters of the exoplanets so to bypass one of the computational challenges related to the non-linearity of the Keplerian signal, we assumed to have a good initial guess for the orbital period.
+%
+Correctly estimating the orbital parameters of an extrasolar planet, in particular when no assumption on the eccentricity of the orbit are available, is something to investigate in future analyses.
+\jessi{I don't think the previous statement is necessary - all we are doing when fixing P close to the truth is avoiding computational issues...in practice with a single dataset, more work would be done to ensure the algorithm converged.}
+
+Once the parameters involved in Eq.~\eqref{eq:RV:correction.overall} have been estimated,  signals in the residuals, defined as $RV - RV_{\text{activity}}$, were investigated using a Generalized Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982, Zechmeister-2009}.
 If a signal with a P-value\footnote{The P-values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected.

### 2018-07-16 manuscript.tex
some updates to 5.3

@@
 
-Once the parameters involved in Eq.~\eqref{eq:RV:correction.overall} have been estimated,  signals in the residuals, defined as $RV - RV_{\text{activity}}$, were investigated using a Generalized Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982, Zechmeister-2009}.
+Once the parameters involved in Eq.~\eqref{eq:RV:correction.overall} have been estimated,  signals in the residuals, defined as $RV - RV_{\text{activity}}$, were analyzed using a Generalized Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982, Zechmeister-2009}.
 If a signal with a P-value\footnote{The P-values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected.
-Finally, for each period considered, the minimum amplitude at which at least 80\% of the planets with different phases were detected was found.
-The results are shown in Fig.~\ref{fig:detection_limits}, where we also considered the usual function that corrects for stellar activity.
-We can see that the new correction for stellar activity based on Eq.~\ref{eq:RV:correction} slightly improves the detection limit of the exoplanet.
-Concerning the type of location parameter that defines the RV, all three of the different RV estimators give similar detection limits.
-Though more investigations should be considered, these results suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity.
+For each period considered, the minimum amplitude at which at least 80\% of the planets with different phases were detected was found. 
+The results for the proposed and usual correction are shown in Fig.~\ref{fig:detection_limits}. 
+We can see that the new correction for stellar activity based on Eq.~\eqref{eq:RV:correction} slightly improves the detection limit of the exoplanet compared to the usual approach, and the three estimators of RV give similar detection limits.
+These results suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity, though additional investigation is needed.
 
@@
    \caption{Detection limits of planetary signals once the stellar activity signal is removed from the raw RVs using the model proposed in Eq.~\ref{eq:RV:correction} (solid lines) or the usual correction based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit (dashed lines).
-The correction for stellar activity based on Eq.~\ref{eq:RV:correction} slightly improves the detection limit and the different RV estimators have similar detection limits.}
+The correction for stellar activity based on Eq.~\ref{eq:RV:correction} slightly improves the detection limit and the different RV estimators have similar detection limits.
+ \jessi{to be consistent with other figures, "NEW" and "USUAL" should only have the first letter uppercase.}
+   }
    \label{fig:detection_limits}
@@
 This is likely caused by the fact that the periods of the simulated planets at 25 days are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012} and therefore close to the semi-periodicity of the stellar activity signal.
+\jessi{wouldn't a period of 30 be considered closer to the rotation period and so should also be higher based on this reasoning?}
 

### 2018-07-16 manuscript.tex
Add files via upload
addressed part of comments Sec.5.3

@@
 
-For each of the 4500 simulations \jessi{please expand on how the above setting results in 4500 simulations} considered, the proposed model from Eq.~\eqref{eq:RV:correction.overall} was fit. 
+For each of the 4500 simulations we derived at first the corresponding three set of RV, namely N mean RV, SN mean RV and SN median RV.
+Then, the proposed model from Eq.~\eqref{eq:RV:correction.overall} was fit.
 The use of Eq.~\eqref{eq:RV:correction.overall} leads to some additional comments.
@@
 In Sec.
-\ref{sec:soap.spot.planet}, because the semi-amplitude of the injected exoplanet was equal to 10 \ms, \jessi{how is this a reason?
-do you mean because the injected RV was large?} a good initial guess for the orbital period was available and local modes were avoided.
+\ref{sec:soap.spot.planet}, because the semi-amplitude of the injected exoplanet was equal to 10 \ms, the Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982} was able to detect a significant clear pick close to the true orbital period, allowing the procedure to achieve the global maximum.
 %
@@
 %
-Correctly estimating the orbital parameters of an extrasolar planet, in particular when no assumption on the eccentricity of the orbit are available, is something to investigate in future analyses.
+%Correctly estimating the orbital parameters of an extrasolar planet, in particular when no assumption on the eccentricity of the orbit are available, is something to investigate in future analyses.
 \jessi{I don't think the previous statement is necessary - all we are doing when fixing P close to the truth is avoiding computational issues...in practice with a single dataset, more work would be done to ensure the algorithm converged.}

### 2018-07-16 manuscript.tex
new figure detection limits and text corrections

@@
 For each of the 4500 simulations we derived at first the corresponding three set of RV, namely N mean RV, SN mean RV and SN median RV. 
-Then, the proposed model from Eq.~\eqref{eq:RV:correction.overall} was fit.
-The use of Eq.~\eqref{eq:RV:correction.overall} leads to some additional comments.
-First, we note that both the function that corrects for stellar activity and the Keplerian signal must be simultaneously considered, as was carried out in Sec.~\ref{sec:soap.spot.planet}. 
-Because of the non-linearity of the model that defines the orbital parameters of the exoplanets, non-linear least squares \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear} was used.
-%
-In order to run the algorithm, a set of initial values for the parameters of interest has to be provided. 
-%
-For the stellar activity correction, the initial values were set at those obtained by only considering Eq.~\eqref{eq:RV:correction}. 
-The selection of the initial values for the orbital parameters of the exoplanet is more challenging. 
-In the present study we assumed a circular orbit, hence the parameters to estimate are the amplitude $K$, the epoch at the periapsis $t_0$, and the orbital period $P$. 
-The initial value for $K$ was set to the maximum measured RV \jessi{what does this mean?  when was the rv measured?}. 
-The epoch at the periapsis $t_0$ is defined as that epoch such that the distance between the planet and the star is the smallest \jessi{how is this known?  where is this value coming from?}.
-%
-Since in our simulation study the orbit of the planet in circular, the distance between the star and planet does not change over time, making the choice for $t_0$ arbitrary \jessi{do you mean the choice of the initial $t_0$ arbitrary?}.
-%
-We selected as initial value for $t_0$ that epoch for which the largest RV was measured \jessi{again, when was the rv measured?}. 
-%
-When providing an initial value for the orbital period $P$, an initial value far from the true one can result in the non-linear least squares algorithm getting stuck in local modes \citep[][]{levenberg1944method,marquardt1963algorithm} and, hence, incorrect estimates for the parameters of Eq.~\eqref{eq:RV:correction.overall}.
-%
-In Sec.
+\xavier{On each of those RV sets, we performed an analysis similar to Sec.~\ref{sec:soap.spot.planet}, i.e. fitting the activity signal using Eq.~\eqref{eq:RV:correction}
+or the usual correction along with a circular planetary signal (see Eq.~\eqref{eq:RV:correction.overall}). Because of the non-linearity of the model to account for the
+planet, we used a non-linear least squares for the fit \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear}. Such a model requires
+initial conditions close to the real solution, otherwise the algorithm can converge to a local minimum. Because our goal here is to compare the planetary detection limits
+using the three different RV estimates and the two different activity model proposed, and not to discuss what is the best method to explore the parameter space, we 
+initialised the minimisation algorithm to the real period of the planetary signal injected to avoid being blocked in a local minimum.
+We also selected as initial amplitude the peak-to-peak amplitude of the RV data set.
+The argument of periapsis $t_0$ was initialised to the time when the RV were crossing 0 since we use a sinusoidal function to fit the planetary signal (see Eq.~\eqref{eq:RV:correction.planet}).}
+
+%Then, the proposed model from Eq.~\eqref{eq:RV:correction.overall} was fit. 
+%The use of Eq.~\eqref{eq:RV:correction.overall} leads to some additional comments.
+%First, we note that both the function that corrects for stellar activity and the Keplerian signal must be simultaneously considered, as was carried out in Sec.~\ref{sec:soap.spot.planet}. 
+%Because of the non-linearity of the model that defines the orbital parameters of the exoplanets, non-linear least squares \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear} was used.
+%%
+%In order to run the algorithm, a set of initial values for the parameters of interest has to be provided. 
+%%
+%For the stellar activity correction, the initial values were set at those obtained by only considering Eq.~\eqref{eq:RV:correction}. 
+%The selection of the initial values for the orbital parameters of the exoplanet is more challenging. 
+%In the present study we assumed a circular orbit, hence the parameters to estimate are the amplitude $K$, the epoch at the periapsis $t_0$, and the orbital period $P$. 
+%The initial value for $K$ was set to the maximum measured RV \jessi{what does this mean?  when was the rv measured?}. 
+%The epoch at the periapsis $t_0$ is defined as that epoch such that the distance between the planet and the star is the smallest \jessi{how is this known?  where is this value coming from?}.
+%%
+%Since in our simulation study the orbit of the planet in circular, the distance between the star and planet does not change over time, making the choice for $t_0$ arbitrary \jessi{do you mean the choice of the initial $t_0$ arbitrary?}.
+%%
+%We selected as initial value for $t_0$ that epoch for which the largest RV was measured \jessi{again, when was the rv measured?}. 
+%%
+%When providing an initial value for the orbital period $P$, an initial value far from the true one can result in the non-linear least squares algorithm getting stuck in local modes \citep[][]{levenberg1944method,marquardt1963algorithm} and, hence, incorrect estimates for the parameters of Eq.~\eqref{eq:RV:correction.overall}.
+%%
+%In Sec.
 \ref{sec:soap.spot.planet}, because the semi-amplitude of the injected exoplanet was equal to 10 \ms, the Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982} was able to detect a significant clear pick close to the true orbital period, allowing the procedure to achieve the global maximum.
-%
-In order to avoid issues with the convergence of the algorithm, the initial guess for $P$ was set to be a value close to the true orbital period for all datasets and methods considered.
-%
-This simplification is reasonable in our setting because our main interest is in evaluating the goodness of the activity correction function presented in Eq.~\eqref{eq:RV:correction} compared to the usual one using $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit or  $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal model of the CCF.
-%
-This requires correct estimation of the orbital parameters of the exoplanets so to bypass one of the computational challenges related to the non-linearity of the Keplerian signal, we assumed to have a good initial guess for the orbital period.
+%%
+%In order to avoid issues with the convergence of the algorithm, the initial guess for $P$ was set to be a value close to the true orbital period for all datasets and methods considered.
+%%
+%This simplification is reasonable in our setting because our main interest is in evaluating the goodness of the activity correction function presented in Eq.~\eqref{eq:RV:correction} compared to the usual one using $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit or  $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal model of the CCF.
+%%
+%This requires correct estimation of the orbital parameters of the exoplanets so to bypass one of the computational challenges related to the non-linearity of the Keplerian signal, we assumed to have a good initial guess for the orbital period.
 %
@@
 If a signal with a P-value\footnote{The P-values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected.
-For each period considered, the minimum amplitude at which at least 80\% of the planets with different phases were detected was found. 
-The results for the proposed and usual correction are shown in Fig.~\ref{fig:detection_limits}. 
+{\xavier{For each period considered, we searched for the minimum amplitude at which at least 80\% of the planets with different phases were detected.
+This minimum amplitude detected as a function of period is shown in Fig.~\ref{fig:detection_limits} for the three different RV estimates (N mean RV, SN mean RV, and SN median RV) when using the new stellar activity correction proposed in this paper (see Eq.~\eqref{eq:RV:correction}), and when using the usual activity correction.}
 We can see that the new correction for stellar activity based on Eq.~\eqref{eq:RV:correction} slightly improves the detection limit of the exoplanet compared to the usual approach, and the three estimators of RV give similar detection limits.

### 2018-07-16 manuscript.tex
Xavier's modifications

@@
 If a signal with a P-value\footnote{The P-values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected.
-{\xavier{For each period considered, we searched for the minimum amplitude at which at least 80\% of the planets with different phases were detected.
+\xavier{For each period considered, we searched for the minimum amplitude at which at least 80\% of the planets with different phases were detected.
 This minimum amplitude detected as a function of period is shown in Fig.~\ref{fig:detection_limits} for the three different RV estimates (N mean RV, SN mean RV, and SN median RV) when using the new stellar activity correction proposed in this paper (see Eq.~\eqref{eq:RV:correction}), and when using the usual activity correction.}
-We can see that the new correction for stellar activity based on Eq.~\eqref{eq:RV:correction} slightly improves the detection limit of the exoplanet compared to the usual approach, and the three estimators of RV give similar detection limits.
-These results suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity, though additional investigation is needed.
+We can see that the new correction for stellar activity based on Eq.~\eqref{eq:RV:correction} \xavier{improves by 12\% on average} the detection limit of the exoplanet compared to the usual approach, and the three estimators of RV give similar detection limits.
+These results therefore suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity, \xavier{and using our new model to account for stellar activity allows to detect planetary signals with a slightly smaller amplitude that the usual correction using only a linear correlation with the FWHM and BIS SPAN.}
 
@@
    \caption{Detection limits of planetary signals once the stellar activity signal is removed from the raw RVs using the model proposed in Eq.~\ref{eq:RV:correction} (solid lines) or the usual correction based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit (dashed lines).
-The correction for stellar activity based on Eq.~\ref{eq:RV:correction} slightly improves the detection limit and the different RV estimators have similar detection limits.
- \jessi{to be consistent with other figures, "NEW" and "USUAL" should only have the first letter uppercase.}
-   }
+The correction for stellar activity based on Eq.~\ref{eq:RV:correction} \xavier{improves by 12\% on average} the detection limit and the different RV estimators have similar detection limits.}
    \label{fig:detection_limits}
@@
 
-Although the detection limits remain relatively constant for the periods  $\leq$20 days, there is a notable increase in the detection limit at 25 days. 
-This is likely caused by the fact that the periods of the simulated planets at 25 days are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012} and therefore close to the semi-periodicity of the stellar activity signal.
+%Although the detection limits remain relatively constant for the periods  $\leq$20 days, there is a notable increase in the detection limit at 25 days. 
+%This is probably due to interaction between the planetary signal and the stellar activity, however 
+%
+%the fact that the simulated planets at 25 days are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012}.
+%However this reasoning 
+%This is likely caused by the fact that the periods of the simulated planets at 25 days are close to the first harmonic or to the rotational period of the star \citep[36.7 days,][]{Dumusque-2012} and therefore close to the semi-periodicity of the stellar activity signal.
 \jessi{wouldn't a period of 30 be considered closer to the rotation period and so should also be higher based on this reasoning?}
@@
 We saw that the SN mean RV estimator is 60\% noisier than the N mean RV estimator. 
-This is not necessarily a negative aspect. 
-For example, in the case where photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring the SN mean RV, even if the uncertainties related to this parameter are increased by 60\%.
-\jessi{I'm not sure I agree with the previous statements - more uncertainty means you would be less certain if the RV estimate is due to actual stellar activity or just photon noise.
+\xavier{This is of course a problem for photon-noise limited observations. However, when looking at bright
+stars like $\alpha$\,Centauri\,B or HD10700, increasing the photon noise by 60\% will not have any impact
+on the RV precision as the instrumental noise will dominate the data. Therefore, for bright targets, stellar activity 
+can be better characterized by using SN mean RV as this RV estimate is more sensitive to it.}
+%
+%This is not necessarily a negative aspect. 
+%For example, in the case where photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring the SN mean RV, even if the uncertainties related to this parameter are increased by 60\%.
+%\jessi{I'm not sure I agree with the previous statements - more uncertainty means you would be less certain if the RV estimate is due to actual stellar activity or just photon noise.
 It is also stated throughout that precise estimates are needed (e.g.
 in the conclusion)}
-\umberto{Xavier, can you please develop a little bit this statement?
+%\umberto{Xavier, can you please develop a little bit this statement?
 If I understood correctly, since the correlation between the width and the asymmetry of the CCF with SN mean RV is almost always the strongest, if the star is particularly active we are willing to ``sacrifice'' the precision of the RV if we can end up with a clear indication of strong activity by the star.
@@
 Correlations between $\gamma$ and the SN mean RV, and between the width and the SN mean RV can be used to probe stellar activity signals in RV data, and the SN median RV can be used to estimate RV.
-\umberto{We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.
+We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.
 Using simulated data from SOAP 2.0, this new proposed correction reduces the effect of the stellar activity signal by factors of about 2 and 3.5 over the usual model respectively for the facula and spot.
-When using real data and when injecting a fake planets, the detection limit slightly improved if using the new correction for stellar activity over the usual one.}
+\xavier{When applying this model on real data, the improvement is not as large, however, we still observe that planetary detection limits are improved by a non-negligible 12\%.}
 We therefore strongly encourage the community to use this proposed SN parametrisation of the CCF.

### 2018-07-17 manuscript.tex
Add files via upload
minor updates. Only one section in Sec.7 to be checked

@@
 For each of the 4500 simulations we derived at first the corresponding three set of RV, namely N mean RV, SN mean RV and SN median RV. 
-\xavier{On each of those RV sets, we performed an analysis similar to Sec.~\ref{sec:soap.spot.planet}, i.e. fitting the activity signal using Eq.~\eqref{eq:RV:correction}
+On each of those RV sets, we performed an analysis similar to Sec.~\ref{sec:soap.spot.planet}, i.e. fitting the activity signal using Eq.~\eqref{eq:RV:correction}
 or the usual correction along with a circular planetary signal (see Eq.~\eqref{eq:RV:correction.overall}). Because of the non-linearity of the model to account for the
@@
 We also selected as initial amplitude the peak-to-peak amplitude of the RV data set.
-The argument of periapsis $t_0$ was initialised to the time when the RV were crossing 0 since we use a sinusoidal function to fit the planetary signal (see Eq.~\eqref{eq:RV:correction.planet}).}
+The argument of periapsis $t_0$ was initialised to the time when the RV were crossing 0 since we use a sinusoidal function to fit the planetary signal (see Eq.~\eqref{eq:RV:correction.planet}).
 
@@
 If a signal with a P-value\footnote{The P-values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected.
-\xavier{For each period considered, we searched for the minimum amplitude at which at least 80\% of the planets with different phases were detected.
-This minimum amplitude detected as a function of period is shown in Fig.~\ref{fig:detection_limits} for the three different RV estimates (N mean RV, SN mean RV, and SN median RV) when using the new stellar activity correction proposed in this paper (see Eq.~\eqref{eq:RV:correction}), and when using the usual activity correction.}
-We can see that the new correction for stellar activity based on Eq.~\eqref{eq:RV:correction} \xavier{improves by 12\% on average} the detection limit of the exoplanet compared to the usual approach, and the three estimators of RV give similar detection limits.
-These results therefore suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity, \xavier{and using our new model to account for stellar activity allows to detect planetary signals with a slightly smaller amplitude that the usual correction using only a linear correlation with the FWHM and BIS SPAN.}
+For each period considered, we searched for the minimum amplitude at which at least 80\% of the planets with different phases were detected.
+This minimum amplitude detected as a function of period is shown in Fig.~\ref{fig:detection_limits} for the three different RV estimates (N mean RV, SN mean RV, and SN median RV) when using the new stellar activity correction proposed in this paper (see Eq.~\eqref{eq:RV:correction}), and when using the usual activity correction.
+We can see that the new correction for stellar activity based on Eq.~\eqref{eq:RV:correction} improves by 12\% on average the detection limit of the exoplanet compared to the usual approach, and the three estimators of RV give similar detection limits.
+These results therefore suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity, and using our new model to account for stellar activity allows to detect planetary signals with a slightly smaller amplitude that the usual correction using only a linear correlation with the FWHM and BIS SPAN.
 
@@
    \caption{Detection limits of planetary signals once the stellar activity signal is removed from the raw RVs using the model proposed in Eq.~\ref{eq:RV:correction} (solid lines) or the usual correction based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit (dashed lines).
-The correction for stellar activity based on Eq.~\ref{eq:RV:correction} \xavier{improves by 12\% on average} the detection limit and the different RV estimators have similar detection limits.}
+The correction for stellar activity based on Eq.~\ref{eq:RV:correction} improves by 12\% on average the detection limit and the different RV estimators have similar detection limits.}
    \label{fig:detection_limits}
@@
 Using simulated data from SOAP 2.0, this new proposed correction reduces the effect of the stellar activity signal by factors of about 2 and 3.5 over the usual model respectively for the facula and spot.
-\xavier{When applying this model on real data, the improvement is not as large, however, we still observe that planetary detection limits are improved by a non-negligible 12\%.}
+When applying this model on real data, the improvement is not as huge, however, we still observe that planetary detection limits are improved by a non-negligible 12\%.
 We therefore strongly encourage the community to use this proposed SN parametrisation of the CCF.
@@
 JCK was partially supported by the National Science Foundation under Grant AST 1616086 and by the National Aeronautics and Space Administration under grant 80NSSC18K0443.
-US was partially supported by Fondazione CARIPARO. \umberto{check if there is a code or something}
+US was partially supported by Fondazione CARIPARO and thanks the IT-University of Helsinki for the computational resources provided to execute part of the analyses of the present work.
 The authors are grateful to all technical and scientific collaborators of the HARPS Consortium, ESO Headquarters and ESO La Silla who have contributed with their extraordinary passion and valuable work to the success of the HARPS project.

### 2018-07-17 manuscript.tex
Add files via upload
minor updates. Only one last comment in Sec.7 to be checked.

@@
 using the three different RV estimates and the two different activity model proposed, and not to discuss what is the best method to explore the parameter space, we 
-initialised the minimisation algorithm to the real period of the planetary signal injected to avoid being blocked in a local minimum.
+initialised the minimisation algorithm to the real period of the planetary signal injected to avoid to get stuck in a local minimum.
 We also selected as initial amplitude the peak-to-peak amplitude of the RV data set.

### 2018-07-17 manuscript.tex
Add files via upload
updated Sec.7

@@
 We saw that the SN mean RV estimator is 60\% noisier than the N mean RV estimator. 
-\xavier{This is of course a problem for photon-noise limited observations. However, when looking at bright
+%\xavier{This is of course a problem for photon-noise limited observations.} 
+However, when looking at bright
 stars like $\alpha$\,Centauri\,B or HD10700, increasing the photon noise by 60\% will not have any impact
 on the RV precision as the instrumental noise will dominate the data. Therefore, for bright targets, stellar activity 
-can be better characterized by using SN mean RV as this RV estimate is more sensitive to it.}
+can be better characterized by using SN mean RV as this RV estimate is more sensitive to it.
 %

### 2018-07-17 manuscript.tex
updated Eq.~\ref{ to Eq.~\eqref{

@@
 Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Fig.~\ref{fig:SN.plot}.
-A usual Normal distribution is the special case of the SN distribution when the skewness parameter $\alpha$ is equal to zero\footnote{This can be seen from Eq.~\ref{def:snd_gen}.
+A usual Normal distribution is the special case of the SN distribution when the skewness parameter $\alpha$ is equal to zero\footnote{This can be seen from Eq.~\eqref{def:snd_gen}.
 If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0) = 0.5$ and therefore $SN(y;\xi, \omega, 0) = \frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$ which is the density of a Normal distribution.
@@
 %
-For reasons related to the interpretation of the parameters in Eq.~\ref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used in this work, which is referred to as the \emph{centered parametrization} (CP).
+For reasons related to the interpretation of the parameters in Eq.~\eqref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used in this work, which is referred to as the \emph{centered parametrization} (CP).
 This CP is much closer to the parametrization of a Normal distribution, as it uses a mean parameter $\mu$, a variance parameter $\sigma^2$ and a skewness parameter $\gamma$.
@@
 
-By using Eq.~\ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a clearer interpretation of the behavior of the SN distribution.
+By using Eq.~\eqref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a clearer interpretation of the behavior of the SN distribution.
 For the $\alpha$ values used in Fig.~\ref{fig:SN.plot}, the corresponding values of ($\mu$, $\sigma^2$, $\gamma$) are displayed in Table~\ref{tab:cp_values}.
@@
 %
-Further details about the parametrization from Eq.~\ref{def:snd_gen}, called the \emph{Direct Parametrization} (DP), the CP, and general statistical properties of the SN can be found in \cite{Azzalini2014}.
+Further details about the parametrization from Eq.~\eqref{def:snd_gen}, called the \emph{Direct Parametrization} (DP), the CP, and general statistical properties of the SN can be found in \cite{Azzalini2014}.
 
@@
 
-The proposed function defined in Eq.~\ref{eq:RV:correction} is the result of statistical and astronomical considerations. 
+The proposed function defined in Eq.~\eqref{eq:RV:correction} is the result of statistical and astronomical considerations. 
 In particular, we considered issues with correlations between the model covariates, which can lead to issues because the matrix needed to calculate the estimates could be singular; this problem is known in statistics as \emph{multicollinearity} and more discussion can be found in \citet{belsley1991}.
@@
 \section{Simulation Study} \label{sec:soap}
-In order to evaluate the performance of the proposed SN approach for modelling the CCF and the benefit of using the proposed correction for stellar activity (see Eq.~\ref{eq:RV:correction}), we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet 2.0 code \citep[SOAP 2.0,][]{Dumusque-2014b}.
+In order to evaluate the performance of the proposed SN approach for modelling the CCF and the benefit of using the proposed correction for stellar activity (see Eq.~\eqref{eq:RV:correction}), we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet 2.0 code \citep[SOAP 2.0,][]{Dumusque-2014b}.
 
@@
 
-The RV variations displayed in Fig.~\ref{fig:faculae} are caused only by stellar activity, in this case a facula, so we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to evaluate the performance of the model in this setting.
-The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
+The RV variations displayed in Fig.~\ref{fig:faculae} are caused only by stellar activity, in this case a facula, so we applied the activity correction proposed in Eq.~\eqref{eq:RV:correction} to evaluate the performance of the model in this setting.
+The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
 The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a $R^2$ larger than $0.99$. 
@@
 We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters.
-When comparing the correction proposed in Eq.~\ref{eq:RV:correction} with what is generally used (i.e.
+When comparing the correction proposed in Eq.~\eqref{eq:RV:correction} with what is generally used (i.e.
 a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2.
@@
 \includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{(top) The spurious estimated RVs (black dots) caused by a facula in the simulated data using a Normal and a SN model, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses), and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the Normal fit.
-   %
- (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (red crosses) and the residuals from the usual correction (green triangles).
+   \caption{(top) The spurious estimated RVs (black dots) caused by a facula in the simulated data using a Normal and a SN model, the estimated RVs using Eq.~\eqref{eq:RV:correction} (red crosses), and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the Normal fit.
+   %
+ (bottom) The residuals from the model fit using Eq.~\eqref{eq:RV:correction} (red crosses) and the residuals from the usual correction (green triangles).
 The std.
-are also reported in the legend, and the residuals have a smaller systematic component when using the proposed model of Eq.~\ref{eq:RV:correction} compared to the usual model.
+are also reported in the legend, and the residuals have a smaller systematic component when using the proposed model of Eq.~\eqref{eq:RV:correction} compared to the usual model.
 The tests of statistical significance on the parameters are presented in Table \ref{table:faculae.test}.
@@
 \begin{center}
-\caption{P-values for the estimated coefficients from the model in Eq.~\ref{eq:RV:correction} for correcting stellar activity induced by an equatorial 3\% facula on the simulated Sun.
+\caption{P-values for the estimated coefficients from the model in Eq.~\eqref{eq:RV:correction} for correcting stellar activity induced by an equatorial 3\% facula on the simulated Sun.
 All the parameters corresponding to the Normal or SN variables are statistically significant.
@@
 
-As before, the original RV estimates are corrected using Eq.~\ref{eq:RV:correction}. 
-The results of this correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table~\ref{table:spot.test}.
+As before, the original RV estimates are corrected using Eq.~\eqref{eq:RV:correction}. 
+The results of this correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table~\ref{table:spot.test}.
 As with the facula, the proposed correction is able, in the case of the spot, to capture almost entirely the stellar activity signal when considering the SN or Normal parameters, with $R^2$ values for the linear combination larger than 0.99.
@@
 When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the facula.
-The Normal or SN parameters involved in Eq.~\ref{eq:RV:correction} are all statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, except the width of the CCF when the RVs are derived with the mean or median of the SN density.
+The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are all statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, except the width of the CCF when the RVs are derived with the mean or median of the SN density.
 %This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
@@
 \includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{(top) The spurious estimated RVs (black dots) caused by a spot in the simulated data, the estimated RVs using Eq.~\ref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
-   %
- (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (red crosses) and the residuals from the usual correction (green triangles). 
+   \caption{(top) The spurious estimated RVs (black dots) caused by a spot in the simulated data, the estimated RVs using Eq.~\eqref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+   %
+ (bottom) The residuals from the model fit using Eq.~\eqref{eq:RV:correction} (red crosses) and the residuals from the usual correction (green triangles). 
  The std. are also reported in the legend, and the residuals have a smaller systematic component when using the proposed model compared to the usual model.
@@
 \begin{center}
-\caption{P--values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun.
+\caption{P--values for the different coefficients used in Eq.~\eqref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun.
 All the parameters corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by this spot, except for the width of the CCF when using SN mean RV or SN median RV as RV estimates.
@@
 %
-where $RV_{\text{activity}}$ can be found in Eq.~\ref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case with no eccentricity, can be modelled by the following sinusoidal function:
+where $RV_{\text{activity}}$ can be found in Eq.~\eqref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case with no eccentricity, can be modelled by the following sinusoidal function:
 %
@@
 %We note that the p--value associated with the amplitude parameter $K$ is particularly relevant for rejecting or not rejecting the assumption about the presence of an orbiting companion.
-Moreover we note also that Eq.~\ref{eq:RV:correction.planet} is highly non linear, meaning that the estimation of all the parameters involved in Eq.~\ref{eq:RV:correction.overall} has to be done numerically.
+Moreover we note also that Eq.~\eqref{eq:RV:correction.planet} is highly non linear, meaning that the estimation of all the parameters involved in Eq.~\eqref{eq:RV:correction.overall} has to be done numerically.
 %We used non linear least squares and the results are displayed in Fig.~\ref{fig:spotplanet.correction}.
 We can see how in this case we are able to disentangle the spurious variations in RVs caused by stellar activity from the pure Doppler-shift due to the planet.
-The proposed model from Eq.~\ref{eq:RV:correction.overall} was fitted to the RV data and the results of the estimated model are summarized in Table~\ref{table:spotplanet.test}.
+The proposed model from Eq.~\eqref{eq:RV:correction.overall} was fitted to the RV data and the results of the estimated model are summarized in Table~\ref{table:spotplanet.test}.
 Except for the width parameters with coefficient $\beta_3$, all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet.
@@
 In this case there are spurious variations caused by the spot and pure Doppler-shift due to the planet.
-The correction is done using Eq.~\ref{eq:RV:correction.overall} and the estimated parameters are presented in Table \ref{table:spotplanet.test}.
-In this case, by solving Eq.~\ref{eq:RV:correction.overall}, we are able to completely disentangle the spurious variations in RVs caused by the presence of the spot from the pure dopplershift caused by the exoplanet.}
+The correction is done using Eq.~\eqref{eq:RV:correction.overall} and the estimated parameters are presented in Table \ref{table:spotplanet.test}.
+In this case, by solving Eq.~\eqref{eq:RV:correction.overall}, we are able to completely disentangle the spurious variations in RVs caused by the presence of the spot from the pure dopplershift caused by the exoplanet.}
 %    \label{fig:spotplanet.correction}
@@
 \begin{center}
-\caption{P-values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun, and a planet with a period of one-third the rotational period of the star and a semi-amplitude  of 10\,\ms.
+\caption{P-values for the different coefficients used in Eq.~\eqref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun, and a planet with a period of one-third the rotational period of the star and a semi-amplitude  of 10\,\ms.
 All the parameters corresponding to the Normal or SN variables are statistically significant, except the width of the CCF.
@@
 For Alpha Centauri B, the RV estimated with SN mean RV has a std that is 35\% larger than the std of the RV estimated with the N mean RV, and the std of SN median RV is 9\% larger than that of the N mean RV.
-Even though we see these differences in the estimated RV, once we correct for stellar activity using Eq.~\ref{eq:RV:correction}, 
+Even though we see these differences in the estimated RV, once we correct for stellar activity using Eq.~\eqref{eq:RV:correction}, 
 the rms of the residuals are essentially the same for all three approaches.
@@
    %
- (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
+ (bottom) The residuals from the model fit using Eq.~\eqref{eq:RV:correction} (New corr.
 std, black dots) and the residuals from the usual correction (Usual corr.
 std, blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
-The residuals have a smaller systematic component when using the proposed model of  Eq.~\ref{eq:RV:correction} (black dots) compared to the usual model (blue triangles).}
+The residuals have a smaller systematic component when using the proposed model of  Eq.~\eqref{eq:RV:correction} (black dots) compared to the usual model (blue triangles).}
 \label{fig:alphacent:correctionRV}
@@
 \begin{center}
-\caption{P-values for the different coefficients used in Eq.~\ref{eq:RV:correction} for the correction from stellar activity in Alpha Centauri B data.
+\caption{P-values for the different coefficients used in Eq.~\eqref{eq:RV:correction} for the correction from stellar activity in Alpha Centauri B data.
 All the variables corresponding to the Normal or SN parameters are statistically significant, except for the asymmetry of the CCF when using the BIS SPAN with the N mean RV.
@@
 When using SN median RV, the final set of RVs is less affected by those spurious shifts caused by stellar activity, but at the same time this indicator is not able to catch as well as SN mean RV changes in the shape and in the width of the CCF.
-Once corrected from stellar activity using Eq.~\ref{eq:RV:correction}, the results are comparable.
+Once corrected from stellar activity using Eq.~\eqref{eq:RV:correction}, the results are comparable.
 Anyway, both SN mean RV and SN median RV are useful to catch different aspects of the CCF and our suggestion is to use SN mean RV when interested in retrieving information about changes in the shape and/or the width of the CCF.
 In order to provide a set of RVs containing the smallest amount of spurious contamination imputable to stellar activity (i.e.
-before to run Eq.~\ref{eq:RV:correction}), our suggestion is to use instead SN median RV.
+before to run Eq.~\eqref{eq:RV:correction}), our suggestion is to use instead SN median RV.
 
@@
 In the previous section, we saw that the estimated RV measured when considering a SN or a Normal density resulted in different amplitudes, especially when using the SN mean RV. 
-However, once corrected for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, as shown in the bottom plots of Fig~\ref{fig:alphacent:correctionRV}, the rms of the residuals are essentially the same for all three approaches.
+However, once corrected for stellar activity using the linear combination presented in Eq.~\eqref{eq:RV:correction}, as shown in the bottom plots of Fig~\ref{fig:alphacent:correctionRV}, the rms of the residuals are essentially the same for all three approaches.
 In this section, we investigate the ability of the three different RV estimators (N mean RV, SN mean RV, and SN median RV) to detect planetary signals among stellar activity, and also compare them when using the usual stellar activity correction with the proposed stellar activity model of Eq.~\eqref{eq:RV:correction}.
@@
 \includegraphics[height = 2.6in]{detection_limits.pdf} 
-   \caption{Detection limits of planetary signals once the stellar activity signal is removed from the raw RVs using the model proposed in Eq.~\ref{eq:RV:correction} (solid lines) or the usual correction based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit (dashed lines).
-The correction for stellar activity based on Eq.~\ref{eq:RV:correction} improves by 12\% on average the detection limit and the different RV estimators have similar detection limits.}
+   \caption{Detection limits of planetary signals once the stellar activity signal is removed from the raw RVs using the model proposed in Eq.~\eqref{eq:RV:correction} (solid lines) or the usual correction based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit (dashed lines).
+The correction for stellar activity based on Eq.~\eqref{eq:RV:correction} improves by 12\% on average the detection limit and the different RV estimators have similar detection limits.}
    \label{fig:detection_limits}
@@
 A test was carried out to see if some RV estimates were better at finding planets in RV data affected by observed stellar signals.
-The new correction based on Eq.~\ref{eq:RV:correction} proposed in this paper to mitigate the effect from stellar activity slightly improves the detection limit respect to the usual one based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+The new correction based on Eq.~\eqref{eq:RV:correction} proposed in this paper to mitigate the effect from stellar activity slightly improves the detection limit respect to the usual one based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
 Concerning the definition of the RV using the SN or the Normal fit, all three of the different RV estimators give similar detection limits.
@@
    %
- (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
+ (bottom) The residuals from the model fit using Eq.~\eqref{eq:RV:correction} (New corr.
 std--black dots) and the residuals from the usual correction (Usual corr.
@@
    %
- (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (New corr.
+ (bottom) The residuals from the model fit using Eq.~\eqref{eq:RV:correction} (New corr.
 std--black dots) and the residuals from the usual correction (Usual corr.
 std--blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
-The residuals have a smaller systematic component when using the proposed model of Eq.~\ref{eq:RV:correction} (black dots) compared to the usual model (blue triangles).
+The residuals have a smaller systematic component when using the proposed model of Eq.~\eqref{eq:RV:correction} (black dots) compared to the usual model (blue triangles).
 Moreover, once corrected for stellar activity using Eq.

### 2018-07-17 manuscript.tex
updated abstract

@@
 %
-{We propose to estimate the variations in shape of the CCF by fitting a Skew Normal (SN) density which, unlike the commonly employed Normal density, includes a skewness parameter to capture the asymmetry of the CCF induced by stellar activity and the convective blueshift.}
+{We propose to estimate the variations in shape of the CCF by fitting a Skew Normal (SN) density which, unlike the commonly employed Normal density, includes a skewness parameter to capture the asymmetry of the CCF induced by stellar activity and the convective blueshift.
+}
 %
@@
 The uncertainties estimated on the asymmetry parameter of the SN are on average $15\%$ smaller than the uncertainties measured on the Bisector Inverse Slope Span (BIS SPAN), which is the commonly used parameter to evaluate the asymmetry of the CCF.
+We also propose a new model to account for stellar activity when fitting a planetary signal to RV data.
+Based on simple simulations, we were able to demonstrate that this new model improves the planetary detection limits by 12\% 
+compared to the usual model used to account for stellar activity.
 }

### 2018-07-17 manuscript.tex
minor 4.1 update
minor 4.2 update

@@
 
-\subsection{Faculae} \label{sec:soap.faculae}
+\subsection{Facula} \label{sec:soap.faculae}
 
@@
 %\jessi{Should a footnote be added here to explain that the SOAP 2.0 faculae are not simulated from actual faculae templates?} 
-of size 3\% relative to the visible stellar hemisphere. The facula is face-on when the phase equals to 0. 
+of size 3\% relative to the visible stellar hemisphere. The facula is face-on when the phase is 0. 
 Note that a 3\% faculae is relatively large for the Sun; at maximum activity, large faculae generally have a size of 1\% \citep[e.g.][]{Borgniet-2015}. 
@@
 Next we consider the effects on the CCF model parameters due to the presence of an equatorial spot of size 1\% relative to the visible stellar hemisphere. 
-The spot is face-on when the phase equals to 0. 
+The spot is face-on when the phase is 0. 
 Note that this is a large spot for the Sun, as large spots are generally on the order of 0.1\% \citep[e.g.][]{Borgniet-2015}. 
@@
 The results of this correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table~\ref{table:spot.test}.
-As with the facula, the proposed correction is able, in the case of the spot, to capture almost entirely the stellar activity signal when considering the SN or Normal parameters, with $R^2$ values for the linear combination larger than 0.99.
+As with the facula, the proposed correction is able to capture almost entirely the spot signal when considering the SN or Normal parameters, with $R^2$ values for the linear combination larger than 0.99.
 

### 2018-07-17 manuscript.tex
updated the one Alpha Cen B reference to Alpha Centauri B

@@
 The simulated SOAP data of the previous section were helpful in assessing the performance of the proposed methodology in a setting where the ground truth was known.
-In this section we present an analysis conducted on real observations, in particular, the star Alpha Centauri B (Alpha Cen B), and compare the performance when fitting a CCF using the SN density defined in Sec.
+In this section we present an analysis conducted on real observations, in particular, the star Alpha Centauri B, and compare the performance when fitting a CCF using the SN density defined in Sec.
 \ref{sec:3} with the commonly employed approach based on fitting a Normal density for estimating the RV and retrieving the BIS SPAN for evaluating the asymmetry of the CCF.
@@
 
-\subsection{Comparison for Alpha Cen B of the different CCF parameters derived with the Normal and the Skew Normal} \label{sec:alphacentb}
+\subsection{Comparison for Alpha Centauri B of the different CCF parameters derived with the Normal and the Skew Normal} \label{sec:alphacentb}
 

### 2018-07-17 manuscript.tex
minor 5.2  update

@@
 Except for the special case discussed above for HD10700, the analyses of those four stars, in addition to the analyses on Alpha Centauri B, show that the parameters derived when using a SN density are generally more sensitive to activity.
-Therefore using the SN parameters, and in particular estimating RV using SN mean RV, can carryout to better detection of stellar activity over the Normal parameters. 
+Therefore using the SN parameters, and in particular estimating RV using SN mean RV, can result in better detection of stellar activity than the Normal parameters. 
 More specifically, this is the case for the evaluation of the asymmetry-RV correlations for Alpha Centauri B, HD10700, HD215152, HD192310 and Corot-7, and the width-RV correlation for Alpha Centauri B, HD215152, HD192310 and Corot-7 (see Appendix \ref{appendix}).

### 2018-07-17 manuscript.tex
minor 5.3  update

@@
 
-In the previous section, we saw that the estimated RV measured when considering a SN or a Normal density resulted in different amplitudes, especially when using the SN mean RV. 
+In the previous section, we saw that the estimated RV resulted in different amplitudes when considering a SN or a Normal density, especially when using the SN mean RV. 
 However, once corrected for stellar activity using the linear combination presented in Eq.~\eqref{eq:RV:correction}, as shown in the bottom plots of Fig~\ref{fig:alphacent:correctionRV}, the rms of the residuals are essentially the same for all three approaches.

### 2018-07-17 manuscript.tex
5.3 updates

@@
 
-For each of the 4500 simulations we derived at first the corresponding three set of RV, namely N mean RV, SN mean RV and SN median RV. 
-On each of those RV sets, we performed an analysis similar to Sec.~\ref{sec:soap.spot.planet}, i.e. fitting the activity signal using Eq.~\eqref{eq:RV:correction}
-or the usual correction along with a circular planetary signal (see Eq.~\eqref{eq:RV:correction.overall}). Because of the non-linearity of the model to account for the
-planet, we used a non-linear least squares for the fit \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear}. Such a model requires
+For each of the 4500 simulations we computed the three estimates of RV, namely N mean RV, SN mean RV and SN median RV. 
+On each set of RV estimates, we performed an analysis similar to Sec.~\ref{sec:soap.spot.planet}, i.e. fitting the activity signal using Eq.~\eqref{eq:RV:correction}
+or the usual correction along with a circular planetary signal (see Eq.~\eqref{eq:RV:correction.overall}). Because of the non-linearity of the model that includes a 
+planet, a non-linear least squares algorithm was used for the fit \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear}. Such a model requires
 initial conditions close to the real solution, otherwise the algorithm can converge to a local minimum. Because our goal here is to compare the planetary detection limits
 using the three different RV estimates and the two different activity model proposed, and not to discuss what is the best method to explore the parameter space, we 
-initialised the minimisation algorithm to the real period of the planetary signal injected to avoid to get stuck in a local minimum.
-We also selected as initial amplitude the peak-to-peak amplitude of the RV data set.
+initialised the minimisation algorithm to the real period of the planetary signal injected to avoid getting stuck in a local minimum.
+We also selected as initial amplitude the peak-to-peak amplitude of the estimated RVs.
 The argument of periapsis $t_0$ was initialised to the time when the RV were crossing 0 since we use a sinusoidal function to fit the planetary signal (see Eq.~\eqref{eq:RV:correction.planet}).
@@
 
-Once the parameters involved in Eq.~\eqref{eq:RV:correction.overall} have been estimated,  signals in the residuals, defined as $RV - RV_{\text{activity}}$, were analyzed using a Generalized Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982, Zechmeister-2009}.
+Once the parameters involved in Eq.~\eqref{eq:RV:correction.overall} were estimated,  signals in the residuals, defined as $RV - RV_{\text{activity}}$, were analyzed using a Generalized Lomb-Scargle periodogram \citep[][]{Lomb-1976a, Scargle-1982, Zechmeister-2009}.
 If a signal with a P-value\footnote{The P-values were estimated using a bootstrap procedure.} smaller than 1\% had a period compatible with the injected planetary period within an error budget of 20\%, the signal was considered significant and the corresponding planet considered detected.
@@
 This minimum amplitude detected as a function of period is shown in Fig.~\ref{fig:detection_limits} for the three different RV estimates (N mean RV, SN mean RV, and SN median RV) when using the new stellar activity correction proposed in this paper (see Eq.~\eqref{eq:RV:correction}), and when using the usual activity correction.
-We can see that the new correction for stellar activity based on Eq.~\eqref{eq:RV:correction} improves by 12\% on average the detection limit of the exoplanet compared to the usual approach, and the three estimators of RV give similar detection limits.
+We can see that the new correction for stellar activity based on Eq.~\eqref{eq:RV:correction} improves the detection limit of the exoplanet by 12\% on average compared to the usual approach, and the three estimators of RV give similar detection limits.
 These results therefore suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity, and using our new model to account for stellar activity allows to detect planetary signals with a slightly smaller amplitude that the usual correction using only a linear correlation with the FWHM and BIS SPAN.
@@
    \caption{Detection limits of planetary signals once the stellar activity signal is removed from the raw RVs using the model proposed in Eq.~\eqref{eq:RV:correction} (solid lines) or the usual correction based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit (dashed lines).
-The correction for stellar activity based on Eq.~\eqref{eq:RV:correction} improves by 12\% on average the detection limit and the different RV estimators have similar detection limits.}
+The correction for stellar activity based on Eq.~\eqref{eq:RV:correction} improves the detection limit by 12\% on average and the different RV estimators have similar detection limits.}
    \label{fig:detection_limits}

### 2018-07-17 manuscript.tex
updates

@@
 \includegraphics[height = 3.6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
-   \caption{(left) Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
+   \caption{\jessi{needs to be corrected} (left) Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
 The strong correlation suggests these two parameters are similarly measuring the asymmetry.
@@
 
-For each of the 4500 simulations we computed the three estimates of RV, namely N mean RV, SN mean RV and SN median RV. 
+For each of the 4590 simulations we computed the three estimates of RV, namely N mean RV, SN mean RV and SN median RV. 
 On each set of RV estimates, we performed an analysis similar to Sec.~\ref{sec:soap.spot.planet}, i.e. fitting the activity signal using Eq.~\eqref{eq:RV:correction}
@@
 The variation of the noise for each CCF parameter as a function of SNR550 is displayed in Fig.~\ref{fig:se}.
-The top row shows the standard errors of the three different estimated RV's, the width, and the asymmetry estimates. 
+The top row shows the standard errors of the three different estimated RVs, the width, and the asymmetry estimates. 
 Note that because BIS SPAN and $\gamma$ do not have the same units, the estimated slopes of the correlation between those two parameters to transform $\gamma$ in \ms were used (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star).

### 2018-07-17 manuscript.tex
updates

@@
 For the estimation of the RV, we investigated the use of the mean and the median of the SN density. 
-The width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry by using $\gamma$, skewness parameter of the SN density.
+The width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2\text{ln}(2)\sigma^2}$) and the asymmetry by using $\gamma$, skewness parameter of the SN density.
 
@@
 
-Considering the different RV estimates of the real data, the amplitude of stellar activity tends to be largest for the SN mean RV, followed by the SN median RV and N mean RV that are extremely similar.
+Considering the different RV estimates of the real data, the amplitude of stellar activity tends to be largest for the SN mean RV, followed by the SN median RV and N mean R, which behave similarly. 
 This implies that the mean of the SN density appears to be more sensitive to variation in the CCF shape than the median of the SN or the mean of the Normal.  
@@
 However, when looking at bright
-stars like $\alpha$\,Centauri\,B or HD10700, increasing the photon noise by 60\% will not have any impact
-on the RV precision as the instrumental noise will dominate the data. Therefore, for bright targets, stellar activity 
+stars like $\alpha$\,Centauri\,B or HD10700, increasing the photon noise by 60\% will not have significant impact
+on the RV precision as the instrumental noise will dominate the data. 
+\jessi{I modified the previous statement to read "significant impact" rather than "any impact" - "any" seems very extreme and unless we directly investigated this or have a good reference, I suggest this modification.}
+Therefore, for bright targets, stellar activity 
 can be better characterized by using SN mean RV as this RV estimate is more sensitive to it.

### 2018-07-17 manuscript.tex
updates

@@
 Generally, when fitting for planetary signals, it is common to use a model composed of one or several Keplerian signals to account for the planets, in addition to a linear combination of the FWHM and BIS SPAN to account for stellar activity signals.
-The proposed model adds to the linear model a term to account for the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters. 
+The proposed model adds a term to the linear model to account for the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters. 
 Using the simulated data from SOAP 2.0, this new model reduces the effect of the stellar activity signal by factors of about 2 and 3.5 over the usual model for the facula and spot, respectively.
@@
 However, when moving to real data, there is just a slight improvement by using the proposed correction function for stellar activity.
-A further analysis can be performed to see if certain components of the model are not relevant and that can therefore be removed.
+Additional analysis can be performed for new datasets to see if certain components of the model are not relevant and, therefore, could be removed.
 
 A test was carried out to see if some RV estimates were better at finding planets in RV data affected by observed stellar signals.
-The new correction based on Eq.~\eqref{eq:RV:correction} proposed in this paper to mitigate the effect from stellar activity slightly improves the detection limit respect to the usual one based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+The new correction based on Eq.~\eqref{eq:RV:correction} proposed in this paper to mitigate the effect from stellar activity slightly improves the detection limit respect to the usual one based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the Normal fit.
 Concerning the definition of the RV using the SN or the Normal fit, all three of the different RV estimators give similar detection limits.
-Therefore it seems that any of the RV estimate can be used to search for planetary signals.
+Therefore it seems that any of the RV estimators can be used to search for planetary signals.
 
@@
 This suggests the SN parameters may be better at probing stellar activity signals than the other methods. 
-In addition, the uncertainties measured on SN median RV and $\gamma$ are respectively 10\% and 15\% smaller than the corresponding uncertainties on N mean RV and BIS SPAN, though the SN mean RV had uncertainties 60\% greater than the N mean RV.
+In addition, the uncertainties measured on SN median RV and $\gamma$ are, respectively, 10\% and 15\% smaller than the corresponding uncertainties on N mean RV and BIS SPAN, though the SN mean RV had uncertainties 60\% greater than the N mean RV.
 
@@
 We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.
-Using simulated data from SOAP 2.0, this new proposed correction reduces the effect of the stellar activity signal by factors of about 2 and 3.5 over the usual model respectively for the facula and spot.
-When applying this model on real data, the improvement is not as huge, however, we still observe that planetary detection limits are improved by a non-negligible 12\%.
-We therefore strongly encourage the community to use this proposed SN parametrisation of the CCF.
+Using simulated data from SOAP 2.0, this new proposed correction reduces the effect of the stellar activity signal by factors of about 2 and 3.5 over the usual model, respectively, for the facula and spot.
+When applying this model on real data, the improvement is not as substantial, however, we still observe that planetary detection limits are improved by a non-negligible 12\%.
 
@@
 %\xavier{$\text{HD}215152$ and Corot-7 have in average a lower SNR at 550 nm than HD10700 and HD192310, 273, 207, 141 and 44, respectively.}
-The average SNR at 550 nm for the stars \text{HD}10700, \text{HD}192310, $\text{HD}215152$ and Corot-7 are respectively 273, 207, 141 and 44.
+The average SNR at 550 nm for the stars \text{HD}10700, \text{HD}192310, $\text{HD}215152$ and Corot-7 are, respectively, 273, 207, 141, and 44.
 Corot-7 has therefore on average a much lower SNR at 550 nm than the others stars, which could be a potential explanation for this small improvement.
-However further tests on several stars should be perform to confirm this statement.
+Additional tests should be performed to confirm this statement.
 

### 2018-07-17 manuscript.tex
updates

@@
 \includegraphics[height = 2.3in]{Skew_Normal_densities_jjck.pdf} 
-   \caption{Density function of a random variable $Y$ following the SN distribution $SN(\xi, \omega, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
+   \caption{Density function of a random variable $Y$ following a SN distribution $SN(\xi, \omega, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
 Note that the solid black line has an $\alpha = 0$ making it a Normal distribution.}
@@
 %%%\includegraphics[height = 2.5in]{[1]LRa01_E2Residuals.pdf} 
-%%%   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCF's from the star Alpha Centauri B (left) and Corot-7 (right).
+%%%   \caption{Comparison between the Normal (black circles) and the SN (red pluses) residuals using CCF's from the star Alpha Centauri B (left) and Corot-7 (right).
 When looking at the residuals corresponding to the center of the CCF, the SN fit leads to slightly better results for both stars.} %Moreover, as the SNR decreases, the SN density shows smaller residuals respect the Normal ones.}
@@
 (right) Correlations between the different width parameters and their corresponding RV estimates for the same facula.
-   In the presence of a facula, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations.}
+   In the presence of a facula, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations.
+   }
     \label{fig:faculae.corr}
@@
 \includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{(top) The spurious estimated RVs (black dots) caused by a facula in the simulated data using a Normal and a SN model, the estimated RVs using Eq.~\eqref{eq:RV:correction} (red crosses), and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the Normal fit.
-   %
- (bottom) The residuals from the model fit using Eq.~\eqref{eq:RV:correction} (red crosses) and the residuals from the usual correction (green triangles).
+   \caption{(top) The spurious estimated RVs (black dots) caused by a facula in the simulated data using a Normal and a SN model, the estimated RVs using Eq.~\eqref{eq:RV:correction} (red pluses), and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the Normal fit.
+   %
+ (bottom) The residuals from the model fit using Eq.~\eqref{eq:RV:correction} (red pluses) and the residuals from the usual correction (green triangles).
 The std.
@@
 \includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
-   \caption{(top) The spurious estimated RVs (black dots) caused by a spot in the simulated data, the estimated RVs using Eq.~\eqref{eq:RV:correction} (red crosses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
-   %
- (bottom) The residuals from the model fit using Eq.~\eqref{eq:RV:correction} (red crosses) and the residuals from the usual correction (green triangles). 
+   \caption{(top) The spurious estimated RVs (black dots) caused by a spot in the simulated data, the estimated RVs using Eq.~\eqref{eq:RV:correction} (red pluses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+   %
+ (bottom) The residuals from the model fit using Eq.~\eqref{eq:RV:correction} (red pluses) and the residuals from the usual correction (green triangles). 
  The std. are also reported in the legend, and the residuals have a smaller systematic component when using the proposed model compared to the usual model.
@@
 %   \caption{(top) RVs as function of Julian Day for Alpha Centauri B.
-The RVs are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan crosses).
-(bottom) RV differences between Normal RV and SN mean RV (black circles) and between Normal RV and a SN median RV (cyan crosses).}
+The RVs are retrieved using the mean of the Normal (red triangles), SN mean RV (black circles), SN median RV (cyan pluses).
+(bottom) RV differences between Normal RV and SN mean RV (black circles) and between Normal RV and a SN median RV (cyan pluses).}
 %   \label{fig:alphacent:diff:RV}
@@
 When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors of N mean RV (red triangles).
-However, the standard errors for SN median RV (cyan crosses) are on average $10\%$ smaller than the standard errors coming from the N mean RV.
+However, the standard errors for SN median RV (cyan pluses) are on average $10\%$ smaller than the standard errors coming from the N mean RV.
    The use of the asymmetry SN parameter $\gamma$ leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
@@
 %Fig.~\ref{fig:se.soap.faculae} shows the results of the bootstrap analysis performed when a faculae is present on the photosphere of the star.
-The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} shows the different errors for the RVs, defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan crosses), the width of the CCF, defined as FWHM (red triangles) or SN FWHM (black circles) and the asymmetry of the CCF, defined as $\gamma$ (black circles) or BIS SPAN (red triangles).
+The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} shows the different errors for the RVs, defined as RV (red triangles), SN mean RV (black circles) or SN median RV (cyan pluses), the width of the CCF, defined as FWHM (red triangles) or SN FWHM (black circles) and the asymmetry of the CCF, defined as $\gamma$ (black circles) or BIS SPAN (red triangles).
 In the series of three plots in the bottom of Fig.~\ref{fig:se.soap.faculae} we show the ratio between errors associated to the parameters derived from the bootstrap analysis fitting the SN and the errors associated to the parameters derived from the bootstrap analysis fitting the Normal density.
@@
 When using SN mean RV (black circles), the standard errors are in average $40\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using SN median RV (cyan crosses), the standard errors are in average $20\%$ smaller than the standard errors coming from the Normal fit.
+However, if using SN median RV (cyan pluses), the standard errors are in average $20\%$ smaller than the standard errors coming from the Normal fit.
 To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN.
@@
 When using SN mean RV (black circles), the standard errors are in average $30\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using SN median RV (cyan crosses), the standard errors are in average $20\%$ smaller than the standard errors coming from the Normal fit.
+However, if using SN median RV (cyan pluses), the standard errors are in average $20\%$ smaller than the standard errors coming from the Normal fit.
 To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN.
@@
 When using SN mean RV (black circles), the standard errors are in average $30\%$ larger than the standard errors retrieved fitting a Normal (red triangles).
-However, if using SN median RV (cyan crosses), the standard errors are in average $20\%$ smaller than the standard errors coming from the Normal fit.
+However, if using SN median RV (cyan pluses), the standard errors are in average $20\%$ smaller than the standard errors coming from the Normal fit.
 To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.

### 2018-07-17 manuscript.tex
updates

@@
    In the presence of a facula, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations.
+ \jessi{Are all these correlations statistically significant?  Even the bottom left?  If not, the previous statement should be modified}
    }
@@
 \includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
-   \caption{\textit{Bootstrap analyses on the stars HD215152, HD192310 and Corot-7}.
+   \caption{Results of the bootstrap analyses on the stars HD215152, HD192310 and Corot-7.
 (top) Comparison between the standard errors from the bootstrap analysis of the estimated RVs, FWHM, and asymmetry parameters using the SN fit and the common strategy (Normal fit and BIS SPAN).
-(bottom) Ratio between the standard errors retrieved on the parameters derived from the common strategy and the corresponding standard errors retrieved on the parameters derived from the SN fit.
+(bottom) Ratio between the standard errors estimated on the parameters derived from the common strategy and the corresponding standard errors estimated on the parameters derived from the SN fit.
 When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors of N mean RV (red triangles).
@@
    The use of the asymmetry SN parameter $\gamma$ leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN.
-Note that for the asymmetry, the error in BIS SPAN is in \ms.
+Note that for asymmetry, the error in BIS SPAN is in \ms.
 To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
@@
 \begin{table*}[!t]
-\caption{Notable correlations between the asymmetry or the FWHM parameters and the RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.
+\caption{Notable correlations between the asymmetry or the FWHM parameters and the estimated RVs for four stars: $\text{HD}192310$,  $\text{HD}10700$, $\text{HD}215152$ and $\text{Corot }7$.
 The complete results of the analyses of the correlations for the four stars are presented in Fig.
@@
 std--black dots) and the residuals from the usual correction (Usual corr.
-std--blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+std--blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the Normal fit.
 The residuals for both the proposed correction from stellar activity are comparable.
@@
 std--black dots) and the residuals from the usual correction (Usual corr.
-std--blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
+std--blue triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the Normal fit.
 The residuals for both the proposed correction from stellar activity are comparable.}

### 2018-07-17 manuscript.tex
Add files via upload
last comments addressed.

@@
 (right) Correlations between the different width parameters and their corresponding RV estimates for the same facula.
-   In the presence of a facula, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations.
- \jessi{Are all these correlations statistically significant?  Even the bottom left?  If not, the previous statement should be modified}
+   In the presence of a facula, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations for all the cases but the correlation between N mean RV and BIS SPAN (p--values=0.39).
    }
@@
 \includegraphics[height = 3.6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
-   \caption{\jessi{needs to be corrected} (left) Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
+   \caption{(left) Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.
 The strong correlation suggests these two parameters are similarly measuring the asymmetry.
@@
 on the RV precision as the instrumental noise will dominate the data. 
-\jessi{I modified the previous statement to read "significant impact" rather than "any impact" - "any" seems very extreme and unless we directly investigated this or have a good reference, I suggest this modification.}
 Therefore, for bright targets, stellar activity 

### 2018-07-17 manuscript.tex
minor updates

@@
 (right) Correlations between the different width parameters and their corresponding RV estimates for the same facula.
-   In the presence of a facula, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations for all the cases but the correlation between N mean RV and BIS SPAN (p--values=0.39).
+   In the presence of a facula, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations for all the cases except for the correlation between N mean RV and BIS SPAN (P-value = 0.39).
    }
@@
 However, when looking at bright
-stars like $\alpha$\,Centauri\,B or HD10700, increasing the photon noise by 60\% will not have significant impact
+stars like $\alpha$\,Centauri\,B or HD10700, increasing the photon noise by 60\% will not have a significant impact
 on the RV precision as the instrumental noise will dominate the data. 

### 2018-07-18 manuscript.tex
Add files via upload
final adjustments made.

@@
 %
-Therefore a common strategy when fitting a Keplerian signal to a set of estimated RVs in search of a planet is to include linear terms in the model to account for activity, such as the \logrhk, the FWHM, and the BIS SPAN \citep{Dumusque:2017aa,Feng:2017aa}.
+Therefore a common strategy when fitting a Keplerian signal to a set of estimated RVs when searching for a planet is to include linear terms in the model to account for activity, such as the \logrhk, the FWHM, and the BIS SPAN \citep{Dumusque:2017aa,Feng:2017aa}.
 %
@@
 In Sec.~\ref{sec:5} error bars are computed for the different estimated CCF parameters.
-Finally the discussion of the results and the conclusions are presented in Secs.~\ref{sec:discu} and ~\ref{sec:conclu}, respectively.
+Finally the discussion of the results and the conclusions are presented, respectively, in Secs.~\ref{sec:discu} and ~\ref{sec:conclu}.
 
@@
 Exoplanets only produce a pure RV signal.
-On the contrary, stellar activity, and, in particular, the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.
+On the contrary stellar activity and, in particular, the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.
 To track these variations in the shape of the spectral lines, a common approach consists in using the FWHM, the BIS SPAN, or other indicators such as those introduced in \citet{Boisse-2011} or \citet{Figueira-2013}, which provide information on the width and asymmetry of the CCF.
@@
 The code also returns the RV and the FWHM estimated using a Normal model for the CCF, and the BIS SPAN obtained by calculating the bisector of the CCF.
-SOAP 2.0 gives noiseless CCFs affected by stellar activity, which are used to compare the performances of a SN and Normal models of the CCF.
+SOAP 2.0 gives noiseless CCFs affected by stellar activity, which are used to compare the performances of SN and Normal models of the CCF.
 
@@
 The right plot of Fig.~\ref{fig:alphacent:corr.gamma} displays the comparison between the RVs estimated using the SN density and the Normal density. 
-The amplitude of the activity signal is slightly stronger for the SN mean RV (in the top-right plot the black circles of the SN mean RV tend to show more variability), while the signal measured using N mean RV or SN median RV are comparable.
+The amplitude of the activity signal is slightly stronger for SN mean RV (in the top-right plot the black circles of SN mean RV tend to show more variability), while the signal measured using N mean RV or SN median RV are comparable.
 %
@@
 However, all the other parameters in the Normal and SN cases are statistically significant for modelling stellar activity. 
-By analyzing the values of the coefficient of determination, $R^2$, we see that the model for the SN mean RV is able to capture the highest percentage of variability in the estimated RV. 
-This is not a surprising result since the three different RV estimates have the same RV residual rms after correction for activity, but before correction, the SN mean RV had the largest RV rms (see Fig~\ref{fig:alphacent:correctionRV}).
+By analyzing the values of the coefficient of determination, $R^2$, we see that the model for SN mean RV is able to capture the highest percentage of variability in the estimated RV. 
+This is not a surprising result since the three different RV estimates have the same RV residual rms after correction for activity, but before correction, SN mean RV had the largest RV rms (see Fig~\ref{fig:alphacent:correctionRV}).
 
@@
 \caption{P-values for the different coefficients used in Eq.~\eqref{eq:RV:correction} for the correction from stellar activity in Alpha Centauri B data.
-All the variables corresponding to the Normal or SN parameters are statistically significant, except for the asymmetry of the CCF when using the BIS SPAN with the N mean RV.
-The $R^2$ shows that the proposed linear combination explains the most variability in RVs due to the stellar activity when the RVs are estimated with the SN mean RV.}
+All the variables corresponding to the Normal or SN parameters are statistically significant, except for the asymmetry of the CCF when using the BIS SPAN with N mean RV.
+The estimated $R^2$ show that the proposed linear combination explains the most variability in RVs due to the stellar activity when the RVs are estimated with the SN mean RV.}
 \label{table:alphacent.test}
@@
 We carryout similar analyses for four other main sequence stars: HD192310 \citep[K2V,][]{Pepe-2011}, HD10700 \citep[G8V,][]{Feng:2017ac}, HD215152 \citep[K3V,][]{Delisle:2018aa} and finally Corot-7 \citep[K0V,][]{Haywood-2014}.
-The same correlations plots and residual plots displayed in the previous section for Alpha Centauri B can be found found for those new four stars in Appendix~\ref{appendix}.
+The same correlation plots and residual plots displayed in the previous section for Alpha Centauri B can be found for those new four stars in Appendix~\ref{appendix}.
 
@@
 
-In the previous section, we saw that the estimated RV resulted in different amplitudes when considering a SN or a Normal density, especially when using the SN mean RV. 
+In the previous section, we saw that the estimated RV resulted in different amplitudes when considering a SN or a Normal density, especially when using SN mean RV. 
 However, once corrected for stellar activity using the linear combination presented in Eq.~\eqref{eq:RV:correction}, as shown in the bottom plots of Fig~\ref{fig:alphacent:correctionRV}, the rms of the residuals are essentially the same for all three approaches.
@@
 initial conditions close to the real solution, otherwise the algorithm can converge to a local minimum. Because our goal here is to compare the planetary detection limits
-using the three different RV estimates and the two different activity model proposed, and not to discuss what is the best method to explore the parameter space, we 
+using the three different RV estimates and the two different activity models proposed, and not to discuss what is the best method to explore the parameter space, we 
 initialised the minimisation algorithm to the real period of the planetary signal injected to avoid getting stuck in a local minimum.
 We also selected as initial amplitude the peak-to-peak amplitude of the estimated RVs.
-The argument of periapsis $t_0$ was initialised to the time when the RV were crossing 0 since we use a sinusoidal function to fit the planetary signal (see Eq.~\eqref{eq:RV:correction.planet}).
+The argument of periapsis $t_0$ was initialised to the time when the RV was crossing 0 since we use a sinusoidal function to fit the planetary signal (see Eq.~\eqref{eq:RV:correction.planet}).
 
@@
 We can see that the new correction for stellar activity based on Eq.~\eqref{eq:RV:correction} improves the detection limit of the exoplanet by 12\% on average compared to the usual approach, and the three estimators of RV give similar detection limits.
-These results therefore suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity, and using our new model to account for stellar activity allows to detect planetary signals with a slightly smaller amplitude that the usual correction using only a linear correlation with the FWHM and BIS SPAN.
+These results therefore suggest that any of the RV estimators can be used when searching for a planetary signal in RV data contaminated by stellar activity, and using our new model to account for stellar activity allows to detect planetary signals with a slightly smaller amplitude that the usual correction that uses only a linear correlation with the FWHM and BIS SPAN.
 
@@
    \caption{Detection limits of planetary signals once the stellar activity signal is removed from the raw RVs using the model proposed in Eq.~\eqref{eq:RV:correction} (solid lines) or the usual correction based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit (dashed lines).
-The correction for stellar activity based on Eq.~\eqref{eq:RV:correction} improves the detection limit by 12\% on average and the different RV estimators have similar detection limits.}
+The correction for stellar activity based on Eq.~\eqref{eq:RV:correction} improves on average the detection limit by 12\% and the different RV estimators have similar detection limits.}
    \label{fig:detection_limits}
@@
 
-When comparing the three different estimates for the RV, the SN mean RV has standard errors that are 60\% larger than the N mean RV.
-However, the SN median RV gives errors 10\% more precise than N mean RV.
+When comparing the three different estimates for the RV, SN mean RV has standard errors that are 60\% larger than N mean RV. However, SN median RV gives errors 10\% more precise than N mean RV. 
 The parameters describing the width of the CCF, FWHM and SN FWHM, have comparable standard errors. 
 Finally, for the asymmetry parameters, $\gamma$ has standard errors that are 15\% more precise than BIS SPAN. 
-In conclusion, when fitting a SN density to the CCF and using SN median RV as the RV estimate, we are able to improve the precision on the estimated RV by 10\%.
+In conclusion, when fitting a SN density to the CCF and when using SN median RV as the RV estimate, we are able to improve the precision on the estimated RV by 10\%.
 Using the SN density, we are also able to improve by 15\% the precision on the estimated asymmetry parameter of the CCF.
-However, the SN mean RV should not be use to derive precise RV estimates
+However, SN mean RV should not be use to derive precise RV estimates
 %%, except perhaps in specific conditions described below, 
@@
 Nevertheless, in both the simulated and the real cases, the parameters derived from the SN are generally more sensitive to activity than the parameters derived from the Normal.
-Also, the correlation between the asymmetry and the SN mean RV is consistently stronger than the parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
+Also, the correlation between the asymmetry and SN mean RV is consistently stronger than the parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}.
 Because the apparent RV signal induced by activity  
@@
 
-Considering the different RV estimates of the real data, the amplitude of stellar activity tends to be largest for the SN mean RV, followed by the SN median RV and N mean R, which behave similarly. 
+Considering the different RV estimates of the real data, the amplitude of stellar activity tends to be largest for SN mean RV, followed by SN median RV and N mean RV, which behave similarly. 
 This implies that the mean of the SN density appears to be more sensitive to variation in the CCF shape than the median of the SN or the mean of the Normal.  
@@
 
-Having an estimator of RV that is more sensitive to stellar activity, such as the SN mean RV, can also help to better probe stellar rotational periods or to better understand the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}.
+Having an estimator of RV that is more sensitive to stellar activity, such as SN mean RV, can also help to better probe stellar rotational periods or to better understand the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}.
 We saw that the SN mean RV estimator is 60\% noisier than the N mean RV estimator. 
@@
 The proposed model adds a term to the linear model to account for the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters. 
-Using the simulated data from SOAP 2.0, this new model reduces the effect of the stellar activity signal by factors of about 2 and 3.5 over the usual model for the facula and spot, respectively.
+Using the simulated data from SOAP 2.0, this new model reduces the effect of the stellar activity signal by factors of about 2 and 3.5 over the usual model, respectively, for the facula and the spot.
 
@@
 Finally, we investigated the precision of each of the SN and Normal parameters including the BIS SPAN.
-It turns out that the SN mean RV should not be used to get precise RVs as the standard errors on this parameter is 60\% greater than for N mean RV.
-However, the SN median RV is 10\% more precise than the N mean RV. 
+It turns out that SN mean RV should not be used to get precise RVs as the standard errors on this parameter is 60\% greater than for N mean RV.
+However, SN median RV is 10\% more precise than N mean RV. 
 Regarding the asymmetry estimates, we observe that $\gamma$ has a precision 15\% better than the BIS SPAN.
@@
 This suggests the SN parameters may be better at probing stellar activity signals than the other methods. 
-In addition, the uncertainties measured on SN median RV and $\gamma$ are, respectively, 10\% and 15\% smaller than the corresponding uncertainties on N mean RV and BIS SPAN, though the SN mean RV had uncertainties 60\% greater than the N mean RV.
+In addition, the uncertainties measured on SN median RV and $\gamma$ are, respectively, 10\% and 15\% smaller than the corresponding uncertainties on N mean RV and BIS SPAN, though SN mean RV had uncertainties 60\% greater than N mean RV.
 
 Because of the advantages of using the proposed SN approach over the commonly employed approach based on the Normal density fit to the CCF and the BIS SPAN or the asymmetry parameters described in \citet{Boisse-2011} and \citet{Figueira-2013}, a SN density model for the CCF may be more useful for detecting stellar activity than the previously proposed parametrizations.
-Correlations between $\gamma$ and the SN mean RV, and between the width and the SN mean RV can be used to probe stellar activity signals in RV data, and the SN median RV can be used to estimate RV.
+Correlations between $\gamma$ and SN mean RV, and between the width and SN mean RV can be used to probe stellar activity signals in RV data, and SN median RV can be used to estimate RV.
 We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.

### 2018-09-18 manuscript_responses_v1.tex
updates

\documentclass[11pt]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage[margin = .75in]{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{url}
\usepackage{xcolor}

\begin{document}
\begin{center}
{\bf Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density (AA/2018/33895)\\
Response to reviewer comments}
\end{center}

Contained in this report are responses to comments made by the reviewer of the manuscript titled ``Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density'' (AA/2018/33895) by Simola, Dumusque, and Cisewski-Kehe.  We would like to begin by thanking the reviewer for the helpful comments both in this review and the original manuscript.  We are grateful for these helpful suggestions, and believe they have dramatically improved this work along with giving us an opportunity to clarify ambiguities.  Below we address the new comments individually.

%%%-----------------------------------------------------------------------
\section{Responses to Reviewer}
%%%-----------------------------------------------------------------------

{\bf This paper presents a new method for dealing with the activity signal - the Skew Normal (SN) distribution as opposed to the Normal (Gaussian) distribution for fitting the CCF. The basis for this technique is that stellar activity in the form of spots, plage, etc. will alter the shapes of the spectral line profiles and this mimics the signal of a planet. This activity introduces an asymmetry in the CCD, which traditionally is measured via line bisectors. Since the SN distribution can model this one can, in principle, achieve an RV measurement that is less sensitive to activity.

This is the second round at refereeing this paper and I must say that I am a bit more enthused about it. The basic premise of the SN starts out promising, but in the end I do not see it as a breakthrough method. It is like a book where the opening chapter draws you in, but the ending leaves you a bit unsatisfied.
I agree that the method is slightly more sensitive to activity. In the simulations their method also results in a better correction to the RV and they seem to improve the detection limit for low amplitude signals. But this is only a slight improvement. To my eye the SN and N derived RVs look very similar and produce virtually identical residual RVs. One exception is Alp Cen B where the SN method seems to produce residual that are more flat, not as much curvature as the traditional method. The detection limit is indeed decreased to lower amplitude, but only by about 10\%. But I guess if you are looking for low-amplitude signals, every improvement helps.

So, my conclusion after reading the paper is that it is an interesting method, but as a reader I would see no compelling reason why I should use it. Another reader may reach a different conclusion and for this reason I think that the paper should be published. I am always reluctant to prevent a paper from being published just because of my own bias or opinion. The readers are intelligent; they can draw their own conclusions. The authors have presented a new and novel method, carefully tested it on synthetic and real data, and drew a conclusion. We may disagree on the utility of the method, but in the final analysis it is each individual reader should decide on the merits of the method. My job as a referee is to check that there is nothing fundamentally wrong with the paper and as far as I can tell this is not the case.} 
\bigskip

\noindent RESPONSE:

\bigskip

\subsection{Detailed Comment Responses}

\begin{enumerate}
\item {\bf Reference for Arellano \& Azzalini 2010 has no journal or volume number in the references. Also Azallini 1985 has only ``171'' in the references. Is this volume or a page? One of these is missing.}
%
\item[]  RESPONSE:  Thank you for finding these typos.  Both references have been updated:  the Arellano \& Azzalini 2010 is XXX, and Azallini 1985 is Volume 12 with pages 171 -- 178 (we added the missing volume number).
\bigskip
%
%
\item {\bf Section 3 \\
``Exoplanets only produce a pure RV signal.'' What do you mean by pure? To me activity and pulsations also produces ``pure'' RV signals. Do you mean to say exoplanets generally produce an RV signal without an accompanying change in the spectral line shapes?}
%
\item[]  RESPONSE:  
\bigskip
%
%
\item {\bf The authors did a simulation using faculae or spots. The real situated is more complicated in that stars usually have both spots and faculae. Faculae seem to produce a gamma-SN mean RV correlation that is in the opposite sense to that for spots, i.e. they would cancel. Have the authors considered a more realistic case with a mixture of spots and faculae? [Editor note: also, I did not see the temperature of the spots/faculae mentioned; please add it if I didn't just miss it, or make it more prominent otherwise]}
%
\item[]  RESPONSE:  
\bigskip
%
%
\item {\bf The simulations are fine, but they appear to be due to data with no noise. I presume when you add noise slight differences in correlation will be more difficult to discern. You should consider adding some realistic level of noise to the data.}
%
\item[]  RESPONSE:  
\bigskip
%
%
\item {\bf I found that the suggestion that the correlation between gamma and SN RV is due primarily to faculae is an interesting one. Possibly this can emerge as a useful diagnostic for this.}
%
\item[]  RESPONSE:  
\bigskip
%
%
\item {\bf I am very puzzled by the ``circle'' correlation plots, especially for the one spot case(top right of Fig. 6). I can understand the effects of spots on the line width by thinking about line profile variations in rapidly rotating stars with large spots (e.g RS Cvn systems). When the spot is on the approaching limb the distortion in the line profile is in the blue wing of the line. This makes the line profile V-shaped (minimum FWHM) but the RV is at a maximum + velocity. At disk center the spot produces a bump in the core of the line profile (no RV), but makes the profile fat (maximum FWHM). When the spot is on the receding limb the line is narrow again (minimum FWHM) but now with a maximum negative velocity. So, I should expect some correlation, possibly a triangle shaped, not a circle. In fact in the appendix CoRoT-7 and HD 192310 doe show a nice correlation of the RV with fwhm. Do the authors have a plausible explanation as to why the correlation plots make a circle?}
%
\item[]  RESPONSE:  
\bigskip
%
%
\item {\bf Section 6, column 2 last paragraph\\

``This suggests that for the stars considered, the precision in each RV estimate may be driven by the SNR of the analyzed spectra. This is not surprising as the three stars studied have very similar spectral types; they are all main sequence K-dwarfs.'' \\

Excuse me, but for an instrument with no systematic errors isn't the RV error driven simply by the SNR? (And what is meant by ``estimate''? Don't you mean error?) If you have a component due to activity, that is not an error in you measurement, but simply a real (but unwanted) signal coming from your star. Yes, these are all main sequence dwarfs, but they have different levels of activity. In short, I am not sure what the authors are trying to say here, it is unclear.}
%
\item[]  RESPONSE:  
\bigskip
%
%
\item {\bf One final comment: The language of this version is vastly improved from the first version. I commend the authors for taking the effort to do this.}
%
\item[]  RESPONSE:  Thank you!
\bigskip
%
%
\end{enumerate}

\end{document}

### 2018-10-18 manuscript_responses_v1.tex
updated reviewer question 1
responded to questions 2 and 3

@@
 Contained in this report are responses to comments made by the reviewer of the manuscript titled ``Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density'' (AA/2018/33895) by Simola, Dumusque, and Cisewski-Kehe.
-We would like to begin by thanking the reviewer for the helpful comments both in this review and the original manuscript.
-We are grateful for these helpful suggestions, and believe they have dramatically improved this work along with giving us an opportunity to clarify ambiguities.
-Below we address the new comments individually.
 
@@
 
-\noindent RESPONSE:
+\noindent RESPONSE:  We would like to begin by thanking the reviewer for the helpful comments both in this review and the original manuscript.
+We are grateful for these helpful suggestions, and believe they have dramatically improved this work along with giving us an opportunity to clarify ambiguities.
+Below we address the new comments individually.
 
@@
 %
-\item[]  RESPONSE:  Thank you for finding these typos.
-Both references have been updated:  the Arellano \& Azzalini 2010 is XXX, and Azallini 1985 is Volume 12 with pages 171 -- 178 (we added the missing volume number).
+\item[]  RESPONSE:  Thank you for finding these typos.  Both references have been updated.
 \bigskip
@@
 %
-\item[]  RESPONSE:  
+\item[]  RESPONSE:  Yes, we mean the impact of an exoplanet on the host star's spectrum is a shift to the entire stellar spectrum.
+In the Introduction section of the paper, we note the following:  ``In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so creates a spurious shift of the stellar spectrum''  The referenced sentence from Section 3 has been clarified to now read, ``Exoplanets only produce a pure RV signal (i.e., exoplanets induce a Doppler shift of the entire stellar spectrum).''  The sentence following contrasts this with the impact of stellar activity to the line shape.
 \bigskip
@@
 %
-\item[]  RESPONSE:  
+\item[]  RESPONSE:  The purpose of the study using the SOAP simulations was to consider a simplified setting in which we can isolate the effects of a spot and a facula on the various activity measures.
+There are many different possible combinations of spots and faculae that could be considered, but we preferred to keep the activity level simple in order to aid in the interpretation of the results.
+The real observations used help to provide insight into how the various activity measures behave with realistic activity levels.
+The temperature of the spot and facula has now been added to the beginning of Section 4.
+The temperature of the spot is XXXX and the temperature of the facula is XXXX.
+{\color{magenta} Xavier, please address the Editor question about the temperature of the spot/facula - I added a place for it at the beginning of Section 4}
 \bigskip
@@
 %
-\item[]  RESPONSE:  
+\item[]  RESPONSE:  Yes, we agree that the correlation between gamma and the SN RV may prove to be a useful diagnostic.
 \bigskip

### 2018-10-18 manuscript_v2.tex
responded to questions 2 and 3

--- 2018-07-18 manuscript.tex
@@
 
-Exoplanets only produce a pure RV signal.
+Exoplanets only produce a pure RV signal (i.e., exoplanets induce a Doppler shift of the entire stellar spectrum).
 On the contrary stellar activity and, in particular, the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.
@@
 The stellar effective temperature is set to 5778 K, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
+{\color{magenta} The temperature of the facula is XXXX and the temperature of the spot is XXXX.}
 In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with a spectral resolution of R=115'000.

### 2018-10-31 manuscript_responses_v1.tex
update Xdumusque

@@
 The temperature of the spot and facula has now been added to the beginning of Section 4.
-The temperature of the spot is XXXX and the temperature of the facula is XXXX.
-{\color{magenta} Xavier, please address the Editor question about the temperature of the spot/facula - I added a place for it at the beginning of Section 4}
+The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula is dependant on the centre-to-limb angle $\theta$,  $\Delta T_{plage} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K (Meunier et al.
+2010).
 \bigskip

### 2018-10-31 manuscript_v2.tex
update Xdumusque

@@
 The stellar effective temperature is set to 5778 K, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
-{\color{magenta} The temperature of the facula is XXXX and the temperature of the spot is XXXX.}
-In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with a spectral resolution of R=115'000.
+{\bf The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula is dependant on the centre-to-limb angle $\theta$,  $\Delta T_{plage} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K \citep[][]{Meunier-2010a}}.
+In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of R=115'000.
 

### 2018-10-31 manuscript_responses_v1.tex
update XDumusque

@@
 %
-\item[]  RESPONSE:  
+\item[]  RESPONSE:  We considered the noise on the different parameters of the Normal and SN fit to the CCF for a SNR of 100, which is typical for high-precision RV measurements.
+The noise for the different parameters can be found in Figure 14
 \bigskip
@@
 %
-\item[]  RESPONSE:  
+\item[]  RESPONSE:  {\color{green} The RV error is driven by three different parameters.
+As can be seen in Bouchy et al.
+(2005, A\&A 431), $\sigma_{RV} = \frac{3\sqrt{FWHM}}{SNR\times C}$, where C is the CCF contrast.
+Therefore the RV error is not only dependant on SNR.
+For stars with a similar spectral type, FWHM and C are similar, therefore $\sigma_{RV}$ is mainly driven by the SNR.
+We changed the paragraph as follow:
+
+The standard errors for the different RV estimates all appear to follow a similar exponential decay as a function of S/N, even though the measurements are from three different stars.
+This suggests that for the stars considered, the precision in RV is mainly driven by the S/N of the analyzed spectra.
+As shown in Bouchy et al.
+2015, the RV precision when fitting a Normal to the CCF is proportional to the S/N, the FWHM of the CCF and its contrast.
+In out case, all the three stars studied are all main sequence K-dwarfs, which imply that their CCF FWHM and contrast is similar, which explains why the RV precision is driven by the S/N only.
+}
 \bigskip

### 2018-10-31 manuscript_v2.tex
update XDumusque

@@
 %%
-%{The performances of the proposed method are compared to the commonly employed Normal density using both simulations and real observations, with different levels of activity and signal-to-noise ratio (SNR) levels.}
-%%We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (SNR) levels.
+%{The performances of the proposed method are compared to the commonly employed Normal density using both simulations and real observations, with different levels of activity and signal-to-noise ratio (S/N) levels.}
+%%We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (S/N) levels.
 In each case, we compare the results obtained by fitting to the CCF respectively a Normal and a SN.
@@
 %
-{The performances of the proposed method are compared to the commonly employed Normal density using both simulations and real observations, with different levels of activity and signal-to-noise ratio (SNR) levels.}
+{The performances of the proposed method are compared to the commonly employed Normal density using both simulations and real observations, with different levels of activity and signal-to-noise ratio (S/N) levels.}
 %
@@
 In \citet{Boisse-2011}, the authors developed $V_{span}$, which is the difference between the RV measured by fitting a Normal density to the upper and the lower parts of the CCF.
-This CCF asymmetry parameter is shown to be more sensitive than the BIS SPAN at low signal-to-noise ratio (SNR).
+This CCF asymmetry parameter is shown to be more sensitive than the BIS SPAN at low signal-to-noise ratio (S/N).
 %
@@
 The authors were able to show that when using bi-Gauss, the amplitude in asymmetry is 30\% larger than when using BIS SPAN, therefore allowing the detection of lower levels of activity.
-They also demonstrated that $V_{asy}$ seems to be a better indicator of line asymmetry at high SNR, as its correlation with RV is significantly stronger than any other correlation between the previously proposed asymmetry indicators and RV.
+They also demonstrated that $V_{asy}$ seems to be a better indicator of line asymmetry at high S/N, as its correlation with RV is significantly stronger than any other correlation between the previously proposed asymmetry indicators and RV.
 
@@
 %%%To initially check this intuition, we compared the CCF residuals after fitting a Normal and a SN density for 2 stars.
-The first star is Alpha Centauri B, whose CCF's have high signal-to-noise ratio (SNR).
-The second star is Corot-7, whose CCF's have low SNR.
-Fig.~\ref{fig:Residual.comparison} shows that the SN seems to be a slightly better model to explain the shape of the CCF.%, in particular as the SNR decreases.
+The first star is Alpha Centauri B, whose CCF's have high signal-to-noise ratio (S/N).
+The second star is Corot-7, whose CCF's have low S/N.
+Fig.~\ref{fig:Residual.comparison} shows that the SN seems to be a slightly better model to explain the shape of the CCF.%, in particular as the S/N decreases.
 %%%%
@@
 %%%   \caption{Comparison between the Normal (black circles) and the SN (red pluses) residuals using CCF's from the star Alpha Centauri B (left) and Corot-7 (right).
-When looking at the residuals corresponding to the center of the CCF, the SN fit leads to slightly better results for both stars.} %Moreover, as the SNR decreases, the SN density shows smaller residuals respect the Normal ones.}
+When looking at the residuals corresponding to the center of the CCF, the SN fit leads to slightly better results for both stars.} %Moreover, as the S/N decreases, the SN density shows smaller residuals respect the Normal ones.}
 %%%    \label{fig:Residual.comparison}
@@
 Four other stars have been analyzed with the proposed method and details can be found in Appendix \ref{appendix}. 
-For all the stars considered in the presented work, only CCFs that were derived from spectra that had at least a SNR of 10 at 550 nm were selected.
+For all the stars considered in the presented work, only CCFs that were derived from spectra that had at least a S/N of 10 at 550 nm were selected.
 
@@
 The standard errors were computed for each CCF parameter for the HARPS measurements of HD215152, HD192310 and Corot-7. 
-These three stars include measurements that cover the range of SNR measured at 550 nm (SNR550) from 10 to 500, which represent the very low SNR limit and the saturation limit of the HARPS detector, respectively.
+These three stars include measurements that cover the range of S/N measured at 550 nm (S/N550) from 10 to 500, which represent the very low S/N limit and the saturation limit of the HARPS detector, respectively.
 HD10700 and Alpha Centauri B were not included because they have a large number of measurements, which would require a substantial computational effort.
-The variation of the noise for each CCF parameter as a function of SNR550 is displayed in Fig.~\ref{fig:se}.
+The variation of the noise for each CCF parameter as a function of S/N550 is displayed in Fig.~\ref{fig:se}.
 The top row shows the standard errors of the three different estimated RVs, the width, and the asymmetry estimates. 
@@
 
-The different RV estimates all appear to follow a similar exponential decay.
-Considering each RV estimate individually, it appears that all the measurements follow the same curve even though the measurements are from three different stars.
-This suggests that for the stars considered, the precision in each RV estimate may be driven by the SNR of the analyzed spectra.
-This is not surprising as the three stars studied have very similar spectral types; they are all main sequence K-dwarfs.
+{\bf The standard errors for the different RV estimates all appear to follow a similar exponential decay as a function of S/N, even though the measurements are from three different stars.
+This suggests that for the stars considered, the precision in RV is mainly driven by the S/N of the analyzed spectra.
+As shown in \citet{Bouchy:2005aa}, the RV precision when fitting a Normal to the CCF is proportional to the S/N, the FWHM of the CCF and its contrast.
+In out case, all the three stars studied are all main sequence K-dwarfs, which imply that their CCF FWHM and contrast is similar, which explains why the RV precision is driven by the S/N only.}
 
@@
 
-%Finally, we also encourage the use of bootstrapping to estimate more realistic errors on the different parameters of the Normal or SN fitted to the CCF, mainly in the low SNR regime where a gain of 50\% can be reached.
+%Finally, we also encourage the use of bootstrapping to estimate more realistic errors on the different parameters of the Normal or SN fitted to the CCF, mainly in the low S/N regime where a gain of 50\% can be reached.
 This takes significantly more time, but note that 100 bootstrapped dataset are enough to get a good estimation of errors.
@@
 However, the rms of the residuals for Corot-7 are 0.23\,\ms\,lower for the SN model than the Normal model.
-%\xavier{$\text{HD}215152$ and Corot-7 have in average a lower SNR at 550 nm than HD10700 and HD192310, 273, 207, 141 and 44, respectively.}
-The average SNR at 550 nm for the stars \text{HD}10700, \text{HD}192310, $\text{HD}215152$ and Corot-7 are, respectively, 273, 207, 141, and 44.
-Corot-7 has therefore on average a much lower SNR at 550 nm than the others stars, which could be a potential explanation for this small improvement.
+%\xavier{$\text{HD}215152$ and Corot-7 have in average a lower S/N at 550 nm than HD10700 and HD192310, 273, 207, 141 and 44, respectively.}
+The average S/N at 550 nm for the stars \text{HD}10700, \text{HD}192310, $\text{HD}215152$ and Corot-7 are, respectively, 273, 207, 141, and 44.
+Corot-7 has therefore on average a much lower S/N at 550 nm than the others stars, which could be a potential explanation for this small improvement.
 Additional tests should be performed to confirm this statement.

### 2018-10-31 manuscript_responses_v1.tex
Update XDumusque

@@
 The real observations used help to provide insight into how the various activity measures behave with realistic activity levels.
+
+Regarding the cancelation of the correlation between gamma and SN mean RV between spots and faculae, we do believe that faculae would take over and therefore create a positive correlation.
+If we compare the gamma - SN mean RV correlation in Figure 3 and 6, indeed the amplitude in gamma and RV are similar,
+
+This positive correlation is seen in all the stars in the Appendix. This is because the faculae over spot ratio on the Sun is about 10 (Chapman-2001). If we compare the correlation between
+
 The temperature of the spot and facula has now been added to the beginning of Section 4.
@@
 %
-\item[]  RESPONSE:  
+\item[]  RESPONSE:  {\color{blue} In the figures shown at the end of this report, we plot how the RV, FWHM and CCF asymmetry varies as a function of stellar rotation phase when a 1\% equatorial spot is present on the stellar surface.
+Phase 0 correspond to the spot on the center of the visible hemisphere.
+We also show the correlation between SN FWHM and SN mean RV.
+The number close to each circle goes from 0 to 100 and corresponds to phase -0.5 to 0.5.
+Looking at how the RV and the FWHM evolves as a function of phase, it is not surprising to see such a "circle" pattern in the correlation plot.
+
+We believe that your comparison with rapid rotating stars is similar to what is happening here.
+When the spot is on the approaching limb, we have a minimum FWHM and a maximum RV, as for point ~35, then when the spot is in the center, the FWHM is maximum, like for point 52, and finally when the spot is on the receding limb the velocity is minimum and the FWHM minimum as well, like for point ~64.
+The only difference is that in our case we are speaking about slow rotators and probably the limited resolution of the instruments plays a role in getting a shape that is slightly different.
+
+The fact that we see nice RV-FWHM correlations for HD192310 and Corot-7 is likely because faculae are dominating the stellar activity signal (see Fig.
+3).
+Note that on the Sun the filling factor of faculae is approximatively 10 times larger than the one of spots (Chapman-2001).
+In Figure 3 we show the results for a 3\% facula, and in Figure 6 the results for a 1\% spot.
+If we consider that the faculae/spots ratio is similar on HD192310 and Corot-7, then the faculae effect would largely dominate, therefore inducing a strong positive correlation.}
+
+\begin{figure*}[!h]
+\begin{center}
+\includegraphics[height = 3in]{SPOT_newPLOTS_comment6.pdf} 
+\includegraphics[height = 3in]{SPOT_new_corrPLOTS_comment6.pdf} 
+   \caption{\emph{Top:} SOAP 2.0 simulation for a 1\% equatorial spot.
+From top to bottom, we can see the CCF RV, the CCF asymmetry and the CCF width.
+Phase 0 correspond to the spot on the center of the visible hemisphere, In total, there is 100 simulated measurement, from phase -0.5 to 0.5.
+\emph{Bottom:} Correlation between SN FWHM and SN mean RV.
+The number around each circle corresponds to stellar rotation phase.
+Numbers goes from 0 to 100, which corresponds to phase -0.5 to 0.5.}
+   \label{fig:se}
+\end{center}
+\end{figure*}
 \bigskip
@@
 %
-\item[]  RESPONSE:  {\color{green} The RV error is driven by three different parameters.
+\item[]  RESPONSE:  {\color{blue} The RV error is driven by three different parameters.
 As can be seen in Bouchy et al.
@@
 As shown in Bouchy et al.
-2015, the RV precision when fitting a Normal to the CCF is proportional to the S/N, the FWHM of the CCF and its contrast.
-In out case, all the three stars studied are all main sequence K-dwarfs, which imply that their CCF FWHM and contrast is similar, which explains why the RV precision is driven by the S/N only.
+2015, the RV precision is proportional to the S/N, the FWHM of the CCF and its contrast.
+In our case, all three stars studied are all main sequence K-dwarfs, which imply that their CCF FWHM and contrast is similar, which explains why the RV precision is driven by the S/N only.
 }

### 2018-10-31 manuscript_v2.tex
Update XDumusque

@@
 This suggests that for the stars considered, the precision in RV is mainly driven by the S/N of the analyzed spectra.
-As shown in \citet{Bouchy:2005aa}, the RV precision when fitting a Normal to the CCF is proportional to the S/N, the FWHM of the CCF and its contrast.
-In out case, all the three stars studied are all main sequence K-dwarfs, which imply that their CCF FWHM and contrast is similar, which explains why the RV precision is driven by the S/N only.}
+As shown in \citet{Bouchy:2005aa}, the RV precision is proportional to the S/N, the FWHM of the CCF and its contrast.
+In our case, all three stars studied are all main sequence K-dwarfs, which imply that their CCF FWHM and contrast is similar, which explains why the RV precision is driven by the S/N only.}
 

### 2018-10-31 manuscript_responses_v1.tex
Final update XDumusque

@@
 
-Regarding the cancelation of the correlation between gamma and SN mean RV between spots and faculae, we do believe that faculae would take over and therefore create a positive correlation.
-If we compare the gamma - SN mean RV correlation in Figure 3 and 6, indeed the amplitude in gamma and RV are similar,
-
-This positive correlation is seen in all the stars in the Appendix. This is because the faculae over spot ratio on the Sun is about 10 (Chapman-2001). If we compare the correlation between
+{\color{blue} Regarding the cancelation of the correlation between gamma and SN mean RV between spots and faculae, we do believe that faculae would take over and therefore create a positive correlation.
+If we compare the gamma - SN mean RV correlation in Figure 3 and 6, indeed the amplitude in gamma and SN mean RV are similar, and we might think about cancelation.
+However the facula used in Figure 3 is 3\%, while the spot in Figure 6 is 1\%.
+We know on the Sun that the faculae over spots filling factor ratio on the Sun is about 10 (Chapman-2001), therefore we should compare a 1\% spot with a 10\% facula.
+In such a case the effect of the facula would dominate and we would see a positive correlation.
+Such a positive correlation is seen in all the stars in the Appendix, therefore it is likely that for the slow rotating stars analyzed in this paper, the effect of faculae dominates over spots.
 
@@
 2010).
+}
 \bigskip
@@
 In Figure 3 we show the results for a 3\% facula, and in Figure 6 the results for a 1\% spot.
-If we consider that the faculae/spots ratio is similar on HD192310 and Corot-7, then the faculae effect would largely dominate, therefore inducing a strong positive correlation.}
+If we consider that the faculae/spots filling factor ratio is similar on HD192310 and Corot-7 than on the Sun, then the faculae effect would largely dominate, therefore inducing a strong positive correlation.}
 

### 2018-10-31 manuscript_responses_v1.tex
revised some text in Xavier's responses to the reviewer

@@
 
-{\color{blue} Regarding the cancelation of the correlation between gamma and SN mean RV between spots and faculae, we do believe that faculae would take over and therefore create a positive correlation.
-If we compare the gamma - SN mean RV correlation in Figure 3 and 6, indeed the amplitude in gamma and SN mean RV are similar, and we might think about cancelation.
+{\color{blue} Regarding the cancelation of the correlation between gamma and SN mean RV between spots and faculae, we expect that faculae would dominate and therefore create a positive correlation. 
+If we compare the gamma - SN mean RV correlation in Figure 3 (facula) and 6 (spot), indeed the amplitude in gamma and SN mean RV are similar, and we might think about cancelation. 
 However the facula used in Figure 3 is 3\%, while the spot in Figure 6 is 1\%. 
-We know on the Sun that the faculae over spots filling factor ratio on the Sun is about 10 (Chapman-2001), therefore we should compare a 1\% spot with a 10\% facula.
+We know that on the Sun the faculae over spots filling factor ratio is about 10 (Chapman-2001), therefore it would be reasonable to compare a 1\% spot with a 10\% facula.
 In such a case the effect of the facula would dominate and we would see a positive correlation.
@@
 When the spot is on the approaching limb, we have a minimum FWHM and a maximum RV, as for point ~35, then when the spot is in the center, the FWHM is maximum, like for point 52, and finally when the spot is on the receding limb the velocity is minimum and the FWHM minimum as well, like for point ~64.
-The only difference is that in our case we are speaking about slow rotators and probably the limited resolution of the instruments plays a role in getting a shape that is slightly different.
+The only difference is that in our case we are speaking about slow rotators; also, the limited resolution of the instruments may play a role in getting a shape that is slightly different.
 
@@
 In Figure 3 we show the results for a 3\% facula, and in Figure 6 the results for a 1\% spot.
-If we consider that the faculae/spots filling factor ratio is similar on HD192310 and Corot-7 than on the Sun, then the faculae effect would largely dominate, therefore inducing a strong positive correlation.}
+If we consider that the faculae/spots filling factor ratio is similar on HD192310 and Corot-7 as on the Sun, then the faculae effect would largely dominate, therefore inducing a strong positive correlation.}
 
@@
 From top to bottom, we can see the CCF RV, the CCF asymmetry and the CCF width.
-Phase 0 correspond to the spot on the center of the visible hemisphere, In total, there is 100 simulated measurement, from phase -0.5 to 0.5.
+Phase 0 correspond to the spot on the center of the visible hemisphere, In total, there are 100 simulated measurement, from phase -0.5 to 0.5.
 \emph{Bottom:} Correlation between SN FWHM and SN mean RV.

### 2018-11-01 manuscript_responses_v1.tex
Add files via upload
manuscript and responses file

@@
 
-{\color{blue} Regarding the cancelation of the correlation between gamma and SN mean RV between spots and faculae, we expect that faculae would dominate and therefore create a positive correlation. 
+Regarding the cancelation of the correlation between gamma and SN mean RV between spots and faculae, we expect that faculae would dominate and therefore create a positive correlation. 
 If we compare the gamma - SN mean RV correlation in Figure 3 (facula) and 6 (spot), indeed the amplitude in gamma and SN mean RV are similar, and we might think about cancelation. 
@@
 The temperature of the spot and facula has now been added to the beginning of Section 4.
-The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula is dependant on the centre-to-limb angle $\theta$,  $\Delta T_{plage} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K (Meunier et al.
+The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula depends on the centre-to-limb angle $\theta$,  $\Delta T_{plage} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K (Meunier et al.
 2010).
-}
 \bigskip
@@
 %
-\item[]  RESPONSE:  {\color{blue} In the figures shown at the end of this report, we plot how the RV, FWHM and CCF asymmetry varies as a function of stellar rotation phase when a 1\% equatorial spot is present on the stellar surface.
+\item[]  RESPONSE:  In the figures shown at the end of this report, we plot how the RV, FWHM and CCF asymmetry varies as a function of stellar rotation phase when a 1\% equatorial spot is present on the stellar surface.
 Phase 0 correspond to the spot on the center of the visible hemisphere.
@@
 In Figure 3 we show the results for a 3\% facula, and in Figure 6 the results for a 1\% spot.
-If we consider that the faculae/spots filling factor ratio is similar on HD192310 and Corot-7 as on the Sun, then the faculae effect would largely dominate, therefore inducing a strong positive correlation.}
+If we consider that the faculae/spots filling factor ratio is similar on HD192310 and Corot-7 as on the Sun, then the faculae effect would largely dominate, therefore inducing a strong positive correlation.
 
@@
 %
-\item[]  RESPONSE:  {\color{blue} The RV error is driven by three different parameters.
+\item[]  RESPONSE:  The RV error is driven by three different parameters.
 As can be seen in Bouchy et al.
@@
 The standard errors for the different RV estimates all appear to follow a similar exponential decay as a function of S/N, even though the measurements are from three different stars.
-This suggests that for the stars considered, the precision in RV is mainly driven by the S/N of the analyzed spectra.
+This suggests that, for the considered stars, the precision in RV is mainly driven by the S/N of the analyzed spectra.
 As shown in Bouchy et al.
-2015, the RV precision is proportional to the S/N, the FWHM of the CCF and its contrast.
-In our case, all three stars studied are all main sequence K-dwarfs, which imply that their CCF FWHM and contrast is similar, which explains why the RV precision is driven by the S/N only.
-}
+(2005, A\&A 431), the RV precision is proportional to the S/N, the FWHM of the CCF and its contrast.
+In our case all three studied stars are main sequence K-dwarfs, which imply that their CCF FWHM and contrast are similar and explains why the RV precision is driven by the S/N only.
+
 \bigskip

### 2018-11-01 manuscript_v2.tex
Add files via upload
manuscript and responses file

@@
 \documentclass{aa}
-
 %\documentclass[referee]{aa}
@@
 
-Exoplanets only produce a pure RV signal (i.e., exoplanets induce a Doppler shift of the entire stellar spectrum).
+\textbf{Exoplanets only produce a pure RV signal (i.e., exoplanets induce a Doppler shift of the entire stellar spectrum)}.
 On the contrary stellar activity and, in particular, the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.
@@
 The stellar effective temperature is set to 5778 K, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
-{\bf The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula is dependant on the centre-to-limb angle $\theta$,  $\Delta T_{plage} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K \citep[][]{Meunier-2010a}}.
+{\bf The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula depends on the centre-to-limb angle $\theta$,  $\Delta T_{plage} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K \citep[][]{Meunier-2010a}}.
 In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of R=115'000.
@@
 {\bf The standard errors for the different RV estimates all appear to follow a similar exponential decay as a function of S/N, even though the measurements are from three different stars.
-This suggests that for the stars considered, the precision in RV is mainly driven by the S/N of the analyzed spectra.
+This suggests that, for the considered stars, the precision in RV is mainly driven by the S/N of the analyzed spectra.
 As shown in \citet{Bouchy:2005aa}, the RV precision is proportional to the S/N, the FWHM of the CCF and its contrast.
-In our case, all three stars studied are all main sequence K-dwarfs, which imply that their CCF FWHM and contrast is similar, which explains why the RV precision is driven by the S/N only.}
+In our case all three studied stars are main sequence K-dwarfs, which imply that their CCF FWHM and contrast are similar and explains why the RV precision is driven by the S/N only.}
 

### 2018-11-12 manuscript_responses_v1.tex
Add files via upload
added a small sentence at the end of Section 4 to address comment 3 and updated as well the manuscript
Add files via upload
new Section 4

@@
 \item[]  RESPONSE:  We considered the noise on the different parameters of the Normal and SN fit to the CCF for a SNR of 100, which is typical for high-precision RV measurements.
-The noise for the different parameters can be found in Figure 14
+We updated the entire Section 4 of the manuscript with the obtained results.
+
+We also accordingly rewritten a couple of sentences in the Discussions presented in Section 7 and in the Conclusions of Section 8:
+\begin{itemize}
+\item In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a stronger correlation with $\gamma$ than the correlation between N mean RV and BIS SPAN.}} Moreover, the correlation between the FWHM and the estimated RVs is also stronger, {\bf{for all the considered cases}}, when using the parameters from the SN compared to the parameters from the Normal.
+
+\item We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.
+Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by 15 \% and 6 \%}} over the usual model, respectively, for facula and spot.
+When applying this model on real data, the improvement is not as substantial, however, we still observe that planetary detection limits are improved by a non-negligible 12\%.
+\end{itemize}
+
 \bigskip

### 2018-11-12 manuscript_v2_noiseSim.tex
Add files via upload
new Section 4

--- 2018-11-01 manuscript_v2.tex
@@
 \documentclass{aa}
+%\documentclass[onecolumn]{aa}
 %\documentclass[referee]{aa}
-%
 \usepackage{pdflscape} % or {lscape}
@@
 In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of R=115'000.
+{\bf{ We consider for our simulations SNR=100.}}
 
@@
 \begin{center}
-\includegraphics[width=3.6in]{RV_comparison_FACULAE.pdf} 
-%\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
+%\includegraphics[width=3.6in]{RV_comparison_FACULAE.pdf} 
+\includegraphics[width=3.6in]{RV_comparison_FACULA_withNoise.pdf} 
 \caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line), and SN median RV (cyan dotted-dashed line).
@@
 Correlations between the different RV estimates and the different CCF asymmetry or width estimates are displayed in Fig.~\ref{fig:faculae.corr}. 
-The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are stronger than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of $R$=0.46, -0.67 and -0.09, respectively.
-%
-There is a stronger correlation between SN FWHM and SN mean RV ($R=0.98$) than between FWHM and N mean RV ($R=0.84$), but the correlation between SN FWHM and SN median RV is the weakest ($R=0.50$). 
+The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are {\bf{weaker}} than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of {\bf{$R$=-0.11, -0.55 and -0.81}}, respectively.
+%
+{\bf{There is a stronger correlation between SN FWHM and SN mean RV ($R=0.92$) than between SN FWHM and SN median RV ($R=0.65$), but the correlation between FWHM and N mean RV is the weakest ($R=0.47$).}}
 This first analysis shows that in the case of a facula, using some parameters from the SN can lead to stronger correlations than the ones obtained by the usual Normal parameters.
@@
 \begin{center}
-\includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
+%\includegraphics[height = 6in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
+\includegraphics[height = 6in]{SOAP_FACULA_Comparison_para_SN_woithNoise.pdf} 
    \caption{(left) Correlations between the different asymmetry parameters and their corresponding RV estimates in the case of an equatorial 3\% facula on the simulated Sun.
 (right) Correlations between the different width parameters and their corresponding RV estimates for the same facula.
-   In the presence of a facula, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations for all the cases except for the correlation between N mean RV and BIS SPAN (P-value = 0.39).
+   In the presence of a facula, both the shape and the width of the CCF change as the star rotates, producing statistically significant correlations for all the cases except for the correlation between {\bf{SN mean RV and SN GAMMA (P-value = 0.27)}}.
    }
@@
 The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
-The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a $R^2$ larger than $0.99$. 
-In addition, the rms of the different estimates of the RV reduces from about 3 \ms before correcting for stellar activity to values below 0.15 \ms after correcting for stellar activity.
+The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a {\bf{$R^2$ larger than $0.98$.}}
+In addition, the rms of the different estimates of the RV reduces from about {\bf{6 \ms}} before correcting for stellar activity to values below {\bf{1.2 \ms}} after correcting for stellar activity.
 We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters.
 When comparing the correction proposed in Eq.~\eqref{eq:RV:correction} with what is generally used (i.e.
-a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2.
-Looking at the significance of the coefficients in Table~\ref{table:faculae.test}, we observe that all the SN or Normal parameters are relevant for the correction.
+a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by  {\bf{15 \%}}.
+Looking at the significance of the coefficients in Table~\ref{table:faculae.test}, we observe that {\bf{all the parameters corresponding to the SN variables are statistically significant.
+When using the Normal variables, the parameters $\beta_{3}$ and $\beta_{4}$ are not statistically helpful for the correction.}}
 
@@
 \begin{center}
-\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+%\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+\includegraphics[height = 6in]{FACULA_COMPARISON_withNoise.pdf} 
    \caption{(top) The spurious estimated RVs (black dots) caused by a facula in the simulated data using a Normal and a SN model, the estimated RVs using Eq.~\eqref{eq:RV:correction} (red pluses), and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the Normal fit.
@@
 \caption{P-values for the estimated coefficients from the model in Eq.~\eqref{eq:RV:correction} for correcting stellar activity induced by an equatorial 3\% facula on the simulated Sun.
-All the parameters corresponding to the Normal or SN variables are statistically significant.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability present in the different RV estimates.}
+{\bf{All the parameters corresponding to the SN variables are statistically significant.
+When using the Normal variables, the parameters $\beta_{3}$ and $\beta_{4}$ are not statistically helpful for the correction.}} The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability present in the different RV estimates.}
 \label{table:faculae.test}
@@
 \hline
-$\beta_{0}$            &    $0.033$    & $0.00020$ & $0.61$ \\
-\hline
-$\beta_{1}$            &    $2.22e-16 $    & $2.22e-16 $ & $2.22e-16 $ \\
-\hline
-$\beta_{2}$            &     $0.0034$   &  $2.22e-16 $ & $2.22e-16 $\\
-\hline
-$\beta_{3}$            &     $0.00016$   &  $1.091e-6$ & $9.75e-7$\\
-\hline
-$\beta_{4}$            &     $2.22e-16$   &  $2.22e-16$ & $2.22e-16$\\
-\hline
-$R^{2}$      &     $0.9978$    &  $0.9985$ & $0.9981$  \\
+$\beta_{0}$            &    $0.3e-4$    & $0.081$ & $0.34e-3$ \\
+\hline
+$\beta_{1}$            &    $2.01e-8 $    & $5.11e-5 $ & $4.74e-5 $ \\
+\hline
+$\beta_{2}$            &     $2.22e-16$   &  $1.66e-5 $ & $2.22e-16 $\\
+\hline
+$\beta_{3}$            &     $0.48$   &  $0.013$ & $0.012$\\
+\hline
+$\beta_{4}$            &     $0.28$   &  $0.31e-3$ & $0.22e-3$\\
+\hline
+$R^{2}$      &     $0.9839$    &  $0.9801$ & $0.9844$  \\
 \hline
@@
 SN mean RV, SN median RV and N mean RV).
-The correlation between $\gamma$ and SN median RV is the strongest ($R=-0.93$), followed by the BIS SPAN - N mean RV correlation ($R=-0.86$) and the $\gamma$ - SN mean RV correlation ($R=-0.85$).
+{\bf{The correlation between $\gamma$ and SN median RV and the correlation between the BIS SPAN and N mean RV are the strongest ($R=-0.81$) followed by the $\gamma$ - SN mean RV correlation ($R=-0.76$).}}
 The correlations between the width and the CCF barycenter are more circular and no substantial correlation is observed. 
@@
 \begin{center}
-\includegraphics[width=3.6in]{RV_comparison_SPOT.pdf} 
-%\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
+%\includegraphics[width=3.6in]{RV_comparison_SPOT.pdf} 
+\includegraphics[width=3.6in]{RV_comparison_SPOT_withNoise.pdf} 
 \caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line) or SN median RV (cyan dotted-dashed line) using CCFs generated from SOAP 2.0 with an equatorial 1\% spot on the simulated Sun.
@@
 \begin{center}
-\includegraphics[height = 6in]{SOAP_SPOT_Comparison_para_SN.pdf} 
+%\includegraphics[height = 6in]{SOAP_SPOT_Comparison_para_SN.pdf} 
+\includegraphics[height = 6in]{SOAP_SPOT_Comparison_para_SN_woithNoise.pdf} 
    \caption{(left) Correlations between the different asymmetry parameters and their corresponding RV estimates in the case of an equatorial 1\% spot on the simulated Sun.
@@
 The results of this correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table~\ref{table:spot.test}.
-As with the facula, the proposed correction is able to capture almost entirely the spot signal when considering the SN or Normal parameters, with $R^2$ values for the linear combination larger than 0.99.
-
-In Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms smaller than 0.38 \ms, for any of the different RV estimates.
-When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the facula.
-The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are all statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, except the width of the CCF when the RVs are derived with the mean or median of the SN density.
+{\bf{In this case the proposed correction is not able to perform as well as for the facula, and $R^2$ values for the linear combination are smaller than 0.8}}.
+
+In Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than {\bf{6.14\ms}} down to a rms smaller than {\bf{3.05 \ms}}, for any of the different RV estimates.
+When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf{6 \%}}.
+The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are all statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, {\bf{except the width of the CCF and the variable that evaluates the interaction between the width and the asymmetry of the CCF.}}
 %This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
@@
 \begin{center}
-\includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
+%\includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf}
+\includegraphics[height = 6in]{SPOT_COMPARISON_withNoise.pdf}
    \caption{(top) The spurious estimated RVs (black dots) caused by a spot in the simulated data, the estimated RVs using Eq.~\eqref{eq:RV:correction} (red pluses) and the estimated RVs using the usual correction for stellar activity (green triangles), based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the normal fit.
@@
 \caption{P--values for the different coefficients used in Eq.~\eqref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun.
-All the parameters corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by this spot, except for the width of the CCF when using SN mean RV or SN median RV as RV estimates.
-The estimated $R^{2}$ show that the proposed correction for stellar activity explains the vast majority of the spurious variability seen in the different RV estimates.}
+All the parameters corresponding to the Normal or SN parameters are statistically significant to explain the spurious RV variations caused by this spot, {\bf{except for the width of the CCF and the variable that evaluates the interaction between the width and the asymmetry of the CCF.
+The proposed correction is not able to perform as well as for the facula, and $R^2$ values for the linear combination are smaller than 0.8.}}
+} 
 \label{table:spot.test}
@@
 \hline
-$\beta_{0}$            &    $0.4975$    & $0.21$ & $0.21$ \\
-\hline
-$\beta_{1}$            &    $2e-16$    & $2e-16$ & $2e-16$ \\
-\hline
-$\beta_{2}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
-\hline
-$\beta_{3}$            &     $0.017$   &  $0.13$ & $0.11$\\
-\hline
-$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
-\hline
-$R^{2}$      &     $0.9959$    &  $0.9936$ & $0.9952$  \\
+$\beta_{0}$            &    $0.0049$    & $0.012$ & $0.014$ \\
+\hline
+$\beta_{1}$            &    $0.0021$    & $0.0011$ & $0.0011$ \\
+\hline
+$\beta_{2}$            &     $2.22e-16$   &  $2.22e-16$ & $2.22e-16$\\
+\hline
+$\beta_{3}$            &     $0.92$   &  $0.76$ & $0.76$\\
+\hline
+$\beta_{4}$            &     $0.34$   &  $0.41$ & $0.41$\\
+\hline
+$R^{2}$      &     $0.7553$    &  $0.7283$ & $0.7799$  \\
 \hline
@@
 The correlations are weaker than in the case of the spot due to the planet inducing changes in RV without affecting the width or the asymmetry of the CCF.
-However, the order of the strength of the correlations between the CCF asymmetry parameters and RV are comparable with the ones obtained for the spot-only model: $\gamma$--SN median RV has the strongest correlation ($R=-0.84$), followed by the correlation between BIS SPAN--N mean RV ($R=-0.78$) and finally by the correlation between $\gamma$--SN mean RV ($R=-0.75$).
+However, the order of the strength of the correlations between the CCF asymmetry parameters and RV are comparable with the ones obtained for the spot-only model: $\gamma$--SN median RV has the strongest correlation {\bf{($R=-0.7$)}}, followed by the correlation between BIS SPAN--N mean RV {\bf{($R=-0.69$)}} and finally by the correlation between $\gamma$--SN mean RV {\bf{($R=-0.67$)}}.
 The patterns observed in the width-RV phase space correlations in Fig.~\ref{fig:spot.plus.planet.corr} follow a circle, similar to the spot-only model; no substantial correlation is observed between those two parameters.
@@
 \begin{center}
-\includegraphics[width = 3.6in]{RV_comparison_SPOT_PLANET.pdf} 
-%\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
+%\includegraphics[width = 3.6in]{RV_comparison_SPOT_PLANET.pdf} 
+\includegraphics[width = 3.6in]{RV_comparison_SPOTandPLANET_withNoise.pdf} 
  \caption{RV estimates for N mean RV (red dashed line),  SN mean RV (black line) or SN median RV (cyan dotted-dashed line).
@@
 \begin{center}
-\includegraphics[height = 6in]{SOAP_SPOT_PLANET_Comparison_para_SN.pdf} 
+%\includegraphics[height = 6in]{SOAP_SPOT_PLANET_Comparison_para_SN.pdf} 
+\includegraphics[height = 6in]{SOAP_SPOTandPLANET_Comparison_para_SN_withNoise.pdf} 
    \caption{Evaluation of the correlation between the RVs and the asymmetry parameters of the simulated data with a 1\% spot and an injected planetary signal.
@@
 The proposed model from Eq.~\eqref{eq:RV:correction.overall} was fitted to the RV data and the results of the estimated model are summarized in Table~\ref{table:spotplanet.test}.
-Except for the width parameters with coefficient $\beta_3$, all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet.
-We also observe that the RV residuals, once corrected for stellar activity and the presence of the planet, are comparable in terms of rms for all the three different RV estimates, with SN mean RV giving a slightly smaller value.
+{\bf{Except for the intercept (coefficient $\beta_0$), the width of the CCF (coefficient $\beta_3$), and the variable that evaluates the interaction between the width and the asymmetry of the CCF (coefficient $\beta_4$), all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet.
+We also observe that the RV residuals, once corrected for stellar activity and the presence of the planet, are smaller in terms of rms when using the SN variables (rms = 2.28 \ms) rather than the Normal ones (rms = 2.80 \ms).}}
 %\begin{figure*}[htbp]
@@
 \caption{P-values for the different coefficients used in Eq.~\eqref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun, and a planet with a period of one-third the rotational period of the star and a semi-amplitude  of 10\,\ms.
-All the parameters corresponding to the Normal or SN variables are statistically significant, except the width of the CCF.
+{\bf{All the parameters corresponding to the Normal or SN variables are statistically significant, except the intercept, the width of the CCF and the variable that evaluates the interaction between the width and the asymmetry of the CCF.
+Once corrected for stellar activity and the presence of the planet, the residuals are smaller in terms of rms when using the SN variables}}.
 Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.}
@@
 \hline
-$\beta_{0}$            &    $0.00063$    & $2e-16$  & $1.42e-09$ \\
-\hline
-$\beta_{1}$            &    $2e-16$    & $2e-16$  & $2e-16$ \\
-\hline
-$\beta_{2}$            &     $2e-16$   & $2e-16$ & $2e-16$\\
-\hline
-$\beta_{3}$            &     $0.067$   &  $0.40$  & $0.38$\\
-\hline
-$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
-\hline
-K            &     $2e-16$   &  $2e-16$   & $2e-16$ \\
-\hline
-P            &     $2e-16$   &  $2e-16$ & $2e-16$ \\
-\hline
-$t_{0}$            &     $2e-16$   &  $2e-16$ & $2e-16$ \\
-\hline
-$\text{Residuals}$      &     $0.71 \ms$    &  $ 0.66 \ms$ & $0.70 \ms$  \\
+$\beta_{0}$            &    $0.95$    & $0.076$  & $0.21$ \\
+\hline
+$\beta_{1}$            &    $0.0020$    & $0.11e-4$  & $0.12e-4$ \\
+\hline
+$\beta_{2}$            &     $2.22e-16$   & $2.22e-16$ & $2.22e-16$\\
+\hline
+$\beta_{3}$            &     $0.92$   &  $0.60$  & $0.61$\\
+\hline
+$\beta_{4}$            &     $0.34$   &  $0.27$ & $0.27$\\
+\hline
+K            &     $2.22e-16$   &  $2.22e-16$   & $2.22e-16$ \\
+\hline
+P            &     $2.22e-16$   &  $2.22e-16$ & $2.22e-16$ \\
+\hline
+$t_{0}$            &     $2.22e-16$   &  $2.22e-16$ & $2.22e-16$ \\
+\hline
+$\text{Residuals}$      &     $2.80 \ms$    &  $ 2.29 \ms$ & $2.29 \ms$  \\
 \hline
@@
 The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method, making them more useful indicators of activity.
-In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; both SN mean RV and SN median RV had a stronger correlation with $\gamma$ than the correlation between N mean RV and BIS SPAN.
-Moreover, the correlation between the FWHM and the estimated RVs is also stronger when using the parameters from the SN compared to the parameters from the Normal. 
+In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a stronger correlation with $\gamma$ than the correlation between N mean RV and BIS SPAN.}}
+Moreover, the correlation between the FWHM and the estimated RVs is also stronger, {\bf{for all the considered cases}}, when using the parameters from the SN compared to the parameters from the Normal.
 The SN parameters continued to have stronger correlations than the Normal in the setting where a planetary signal was added the SOAP 2.0 with a single spot.
@@
 We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.
-Using simulated data from SOAP 2.0, this new proposed correction reduces the effect of the stellar activity signal by factors of about 2 and 3.5 over the usual model, respectively, for the facula and spot.
+Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by 15 \% and 6 \%}} over the usual model, respectively, for facula and spot.
 When applying this model on real data, the improvement is not as substantial, however, we still observe that planetary detection limits are improved by a non-negligible 12\%.

### 2018-11-14 manuscript_v2_noiseSim.tex
Add files via upload
updated sentences Sec.4 on comparison before/after correction

@@
 The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a {\bf{$R^2$ larger than $0.98$.}}
-In addition, the rms of the different estimates of the RV reduces from about {\bf{6 \ms}} before correcting for stellar activity to values below {\bf{1.2 \ms}} after correcting for stellar activity.
-We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters.
+%In addition, the rms of the different estimates of the RV reduces from about {\bf{6 \ms}} before correcting for stellar activity to values below {\bf{1.2 \ms}} after correcting for stellar activity.
+%We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters.
+{\bf{In addition the rms for N mean RV reduces from 8.02 \ms before correcting for stellar activity to about 1.2 \ms after once corrected for stellar activity using the proposed linear model; the respective values for SN median RV are 7.07 \ms to 0.88 \ms and for SN mean RV are 5.9 \ms to 0.88 \ms.}}
 When comparing the correction proposed in Eq.~\eqref{eq:RV:correction} with what is generally used (i.e.
@@
 
-In Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than {\bf{6.14\ms}} down to a rms smaller than {\bf{3.05 \ms}}, for any of the different RV estimates.
+%In Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than {\bf{6.14\ms}} down to a rms smaller than {\bf{3.05 \ms}}, for any of the different RV estimates.
+{\bf{In addition the rms for N mean RV reduces from 6.14 \ms before correcting for stellar activity to about 3.04 \ms after once corrected for stellar activity using the proposed linear model; the respective values for SN median RV are 5.85 \ms to 2.74 \ms and for SN mean RV are 5.27 \ms to 2.74 \ms.}}
 When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf{6 \%}}.

### 2018-11-16 manuscript_responses_v1.tex
Add files via upload
updates with comment 4 and comment 5 addressed. still to check comment 3 and discuss comment 5

@@
 The real observations used help to provide insight into how the various activity measures behave with realistic activity levels.
+In the Discussions (Section 7, pag.
+15), we note: ``Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region on the equator in order to isolate the effects of those active regions.
+''
 
@@
 %
-\item[]  RESPONSE:  Yes, we agree that the correlation between gamma and the SN RV may prove to be a useful diagnostic.
+\item[]  RESPONSE:  With the new simulations that accounts for SNR=100 the correlations gamma--SN RV are negative both when a spot or a facula is considered.
+However we notice how the p--value associated to the interaction term used in the function that corrects for stellar activity is statistically significant only in the facula scenario.
+When moving to the star alpha centauri b, the p--value associated to the interaction term is as well statistically significant, suggesting that the star could be facula dominated.
+
+We changed the sentence at the end of page 9 (Section 5.1) in: 
+``Another feature that suggests the presence of faculae is the statistically significant p--value associated to the interaction term $\gamma \cdot$ SN FWHM used in the proposed function to correct from stellar activity, as summarized in Table 5; as we saw in Sec.
+4.1 a facula produces as well a statistically significant p--value associated to the  interaction term $\gamma \cdot$ SN FWHM (Table 2) while the same does not happen when a spot is considered (Table 3).''
+
 \bigskip

### 2018-11-16 manuscript_v2_noiseSim.tex
Add files via upload
updates with comment 4 and comment 5 addressed. still to check comment 3 and discuss comment 5

@@
 %
-Another feature that suggests the presence of faculae is the strong positive measured correlation between $\gamma$ and SN mean RV and  between SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot};
-as we saw in Sec.~\ref{sec:soap.spot} a spot induces a negative correlation between $\gamma$ and SN mean RV and weak correlations are measured between SN FWHM and SN mean RV.
+%Another feature that suggests the presence of faculae is the strong positive measured correlation between $\gamma$ and SN mean RV and  between SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot};
+%as we saw in Sec.~\ref{sec:soap.spot} a spot induces a negative correlation between $\gamma$ and SN mean RV and weak correlations are measured between SN FWHM and SN mean RV.
+{\bf{Another feature that suggests the presence of faculae is the statistically significant p--value associated to the interaction term $\gamma \cdot \text{SN FWHM}$ used in the proposed function to correct from stellar activity, as summarized in Table~\ref{table:alphacent.test};
+as we saw in Sec.~\ref{sec:soap.faculae} a facula produces as well a statistically significant p--value associated to the  interaction term $\gamma \cdot \text{SN FWHM}$ (Table~\ref{table:faculae.test}) while the same does not happen when a spot is considered (Table~\ref{table:spot.test}).}}
 \citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
@@
 Because the temperature between a spot and a facula is significantly different, their spectra should be different. 
-Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region on the equator.
+Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region on the equator {\bf{in order to isolate the effects of those active regions}}.
 %\xavier{The fact that we also find significant differences between the simulated and real data for the correlations between BIS SPAN and N mean RV and between FWHM and N mean RV shows that the SOAP 2.0 simulation studied here are too simple to explain the complexity of stellar activity in real RV observations.}

### 2018-11-16 manuscript_responses_v1.tex
Add files via upload
updated comment 5. Comment 3 to be updated only on file for referee

--- 2018-11-12 manuscript_responses_v1.tex
@@
 The real observations used help to provide insight into how the various activity measures behave with realistic activity levels.
+In the Discussions (Section 7, pag.
+15), we note: ``Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region on the equator in order to isolate the effects of those active regions.
+''
 
-Regarding the cancelation of the correlation between gamma and SN mean RV between spots and faculae, we expect that faculae would dominate and therefore create a positive correlation. 
+{\color{red}Regarding the cancelation of the correlation between gamma and SN mean RV between spots and faculae, we expect that faculae would dominate and therefore create a positive correlation. 
 If we compare the gamma - SN mean RV correlation in Figure 3 (facula) and 6 (spot), indeed the amplitude in gamma and SN mean RV are similar, and we might think about cancelation. 
@@
 In such a case the effect of the facula would dominate and we would see a positive correlation.
-Such a positive correlation is seen in all the stars in the Appendix, therefore it is likely that for the slow rotating stars analyzed in this paper, the effect of faculae dominates over spots.
+Such a positive correlation is seen in all the stars in the Appendix, therefore it is likely that for the slow rotating stars analyzed in this paper, the effect of faculae dominates over spots.}
 
@@
 %
-\item[]  RESPONSE:  Yes, we agree that the correlation between gamma and the SN RV may prove to be a useful diagnostic.
+\item[]  RESPONSE:  Yes, this is what we observe for example with Alpha Centauri b, where the correlation gamma -- SN RV is positive.
+When working with simulations and in particular for the case of a facula, we measured a negative gamma -- SN RV correlation.
+This might be cause by some of the limitations about SOAP 2.0 described in Section 7, and an interesting point for improving the software in the future.
+
 \bigskip

### 2018-11-16 manuscript_v2_noiseSim.tex
Add files via upload
updated comment 5. Comment 3 to be updated only on file for referee

@@
 %as we saw in Sec.~\ref{sec:soap.spot} a spot induces a negative correlation between $\gamma$ and SN mean RV and weak correlations are measured between SN FWHM and SN mean RV.
-{\bf{Another feature that suggests the presence of faculae is the statistically significant p--value associated to the interaction term $\gamma \cdot \text{SN FWHM}$ used in the proposed function to correct from stellar activity, as summarized in Table~\ref{table:alphacent.test};
-as we saw in Sec.~\ref{sec:soap.faculae} a facula produces as well a statistically significant p--value associated to the  interaction term $\gamma \cdot \text{SN FWHM}$ (Table~\ref{table:faculae.test}) while the same does not happen when a spot is considered (Table~\ref{table:spot.test}).}}
+%{\bf{Another feature that suggests the presence of faculae is the statistically significant p--value associated to the interaction term $\gamma \cdot \text{SN FWHM}$ used in the proposed function to correct from stellar activity, as summarized in Table~\ref{table:alphacent.test};
+%as we saw in Sec.~\ref{sec:soap.faculae} a facula produces as well a statistically significant p--value associated to the  interaction term $\gamma \cdot \text{SN FWHM}$ (Table~\ref{table:faculae.test}) while the same does not happen when a spot is considered (Table~\ref{table:spot.test}).}}
 \citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.

### 2018-11-19 manuscript_v2_noiseSim.tex
updates to facula and spot sections

@@
 \usepackage{afterpage}
+\usepackage{ulem}
 
@@
 In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of R=115'000.
-{\bf{ We consider for our simulations SNR=100.}}
+{\bf{ We consider an SNR=100 for our simulations.}}
 
@@
 %
-{\bf{There is a stronger correlation between SN FWHM and SN mean RV ($R=0.92$) than between SN FWHM and SN median RV ($R=0.65$), but the correlation between FWHM and N mean RV is the weakest ($R=0.47$).}}
+{\bf{There is a stronger correlation between SN FWHM and SN mean RV ($R=0.92$) than between SN FWHM and SN median RV ($R=0.65$).
+The correlation between FWHM and N mean RV is the weakest ($R=0.47$), and the correlation between FWHM and SN mean RV is the strongest ($R=0.92$).}}
 This first analysis shows that in the case of a facula, using some parameters from the SN can lead to stronger correlations than the ones obtained by the usual Normal parameters. 
-Therefore, the SN parameters may better probe stellar activity.
+{\bf Therefore, the SN parameters may better probe stellar activity that induces changes in the FWHM.}
 We investigate this feature further in the following two sections, where we consider simulated data with a single spot and a spot plus a planet, and in Sec.~\ref{sec:4} with real observations.
@@
 %We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters.
-{\bf{In addition the rms for N mean RV reduces from 8.02 \ms before correcting for stellar activity to about 1.2 \ms after once corrected for stellar activity using the proposed linear model; the respective values for SN median RV are 7.07 \ms to 0.88 \ms and for SN mean RV are 5.9 \ms to 0.88 \ms.}}
+{\bf{In addition the rms for N mean RV reduces from 8.02 \ms before correcting for stellar activity to {\color{red}1.02} \ms after correcting for stellar activity using the proposed linear model; the respective values for the SN median RV are 7.07 \ms to 0.88 \ms and for the SN mean RV are 5.9 \ms to 0.88 \ms.}}
 When comparing the correction proposed in Eq.~\eqref{eq:RV:correction} with what is generally used (i.e.
-a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by  {\bf{15 \%}}.
+a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by {\color{red} \bf an additional 14.5 -} {\bf{15\%}} {\color{red} \bf [I think we should emphasize the proposed correction is in addition to the usual correction, and it seems the range of improvement is actually 14.5-15\%]}.
 Looking at the significance of the coefficients in Table~\ref{table:faculae.test}, we observe that {\bf{all the parameters corresponding to the SN variables are statistically significant.
@@
 Similar to the case with a facula, some parameters of the SN gives stronger correlations compared to the Normal parameters.
+{\color{red} \bf I'm not sure the previous statement is correct anymore - the only correlations strong with the SN variables is described has having ``no substantial correlation'' in the previous statement...I suggest we delete the previous sentence, or revise to make it correct.]}
 
@@
 The results of this correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table~\ref{table:spot.test}.
-{\bf{In this case the proposed correction is not able to perform as well as for the facula, and $R^2$ values for the linear combination are smaller than 0.8}}.
+%{\bf{In this case the proposed correction is not able to perform as well as for the facula, and $R^2$ values for the linear combination are smaller than 0.8}}. 
+{\bf The $R^2$ values for the linear combination are between 0.72 and 0.78, which are not as strong as the setting with a facula.}
 
 %In Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than {\bf{6.14\ms}} down to a rms smaller than {\bf{3.05 \ms}}, for any of the different RV estimates.
-{\bf{In addition the rms for N mean RV reduces from 6.14 \ms before correcting for stellar activity to about 3.04 \ms after once corrected for stellar activity using the proposed linear model; the respective values for SN median RV are 5.85 \ms to 2.74 \ms and for SN mean RV are 5.27 \ms to 2.74 \ms.}}
-When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf{6 \%}}.
-The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are all statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, {\bf{except the width of the CCF and the variable that evaluates the interaction between the width and the asymmetry of the CCF.}}
+{\bf{In addition the rms for N mean RV reduces from 6.14 \ms before correcting for stellar activity to 3.04 \ms after  correcting for stellar activity using the proposed linear model; the respective values for the SN median RV are 5.85 \ms to 2.74 \ms and for the SN mean RV are 5.27 \ms to 2.74 \ms.}}
+When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf \color{red} and additional 5.3 - 5.8\% ]} \sout{\bf{6 \%}}.
+The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are all statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, {\bf{except the width of the CCF and the variable that captures the interaction between the width and the asymmetry of the CCF.}}
 %This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.

### 2018-11-19 manuscript_v2_noiseSim.tex
updated spot+planet, discussion, conclusion

@@
 
+{\color{red} \bf [should any of the following text be in bold indicating an update as was done in the previous sections?]}
 The correlation between the different CCF parameters are displayed in Fig.~\ref{fig:spot.plus.planet.corr}. 
@@
 The proposed model from Eq.~\eqref{eq:RV:correction.overall} was fitted to the RV data and the results of the estimated model are summarized in Table~\ref{table:spotplanet.test}.   
-{\bf{Except for the intercept (coefficient $\beta_0$), the width of the CCF (coefficient $\beta_3$), and the variable that evaluates the interaction between the width and the asymmetry of the CCF (coefficient $\beta_4$), all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet.
-We also observe that the RV residuals, once corrected for stellar activity and the presence of the planet, are smaller in terms of rms when using the SN variables (rms = 2.28 \ms) rather than the Normal ones (rms = 2.80 \ms).}}
+{\bf{Except for the intercept term (coefficient $\beta_0$), the width of the CCF (coefficient $\beta_3$), and the variable that captures the interaction between the width and the asymmetry of the CCF (coefficient $\beta_4$), all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet.
+We also observe that the RV residuals, after correcting for stellar activity and the presence of the planet, have smaller rms when using the SN variables (rms = {\color{red} 2.29} \ms) rather than the Normal ones (rms = 2.80 \ms).}}
 %\begin{figure*}[htbp]
@@
 The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method, making them more useful indicators of activity.
-In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a stronger correlation with $\gamma$ than the correlation between N mean RV and BIS SPAN.}}
+ {\bf \color{red} The previous sentence is not correct; this was not demonstrated once the noise was added.]}
+In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a stronger correlation with $\gamma$ than the correlation between N mean RV and BIS SPAN.}} {\bf \color{red} On this setting, they actually had the same correlations (-.81)...the previous sentence should be deleted or revised]}
 Moreover, the correlation between the FWHM and the estimated RVs is also stronger, {\bf{for all the considered cases}}, when using the parameters from the SN compared to the parameters from the Normal.
+ {\bf \color{red} The previous comment is only relevant for the facula setting...the other two showed no significant correlations]}
 The SN parameters continued to have stronger correlations than the Normal in the setting where a planetary signal was added the SOAP 2.0 with a single spot.
@@
 We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.
-Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by 15 \% and 6 \%}} over the usual model, respectively, for facula and spot.
+Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by {\color{red} an additional 14.5 -}15 \% and {\color{red} 5.3-5.8} \%}} over the usual model, respectively, for facula and spot.
 When applying this model on real data, the improvement is not as substantial, however, we still observe that planetary detection limits are improved by a non-negligible 12\%.

### 2018-11-19 manuscript_responses_v1.tex
updated responses

@@
 \item[]  RESPONSE:  Yes, we mean the impact of an exoplanet on the host star's spectrum is a shift to the entire stellar spectrum.
-In the Introduction section of the paper, we note the following:  ``In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so creates a spurious shift of the stellar spectrum''  The referenced sentence from Section 3 has been clarified to now read, ``Exoplanets only produce a pure RV signal (i.e., exoplanets induce a Doppler shift of the entire stellar spectrum).''  The sentence following contrasts this with the impact of stellar activity to the line shape.
+In the Introduction section of the paper, we note the following:  ``In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so creates a spurious shift of the stellar spectrum''  The referenced sentence from Section 3 has been clarified to now read, ``Exoplanets  produce only a pure RV signal (i.e., exoplanets induce a Doppler shift of the entire stellar spectrum).''  The sentence following contrasts this with the impact of stellar activity to the line shape.
 \bigskip
@@
 \end{itemize}
+{\color{red} \bf [Both of these updates have been revised in the main text - please update if you agree with the changes in the text]}
 
@@
 \item[]  RESPONSE:  Yes, this is what we observe for example with Alpha Centauri b, where the correlation gamma -- SN RV is positive. 
-When working with simulations and in particular for the case of a facula, we measured a negative gamma -- SN RV correlation.
-This might be cause by some of the limitations about SOAP 2.0 described in Section 7, and an interesting point for improving the software in the future.
-
+When working with simulations and, in particular, for the case of a facula, we measured a negative gamma -- SN RV correlation. 
+This may be due to the limitations of the SOAP 2.0 model described in Section 7, but provides an opportunity for improving the SOAP model in the future.
 \bigskip
@@
 %
-\item[]  RESPONSE:  In the figures shown at the end of this report, we plot how the RV, FWHM and CCF asymmetry varies as a function of stellar rotation phase when a 1\% equatorial spot is present on the stellar surface.
+\item[]  RESPONSE:  In the plots shown below (Figure~\ref{fig:se}), we plot how the RV, FWHM and CCF asymmetry varies as a function of stellar rotation phase when a 1\% equatorial spot is present on the stellar surface.
 Phase 0 correspond to the spot on the center of the visible hemisphere.
@@
 The fact that we see nice RV-FWHM correlations for HD192310 and Corot-7 is likely because faculae are dominating the stellar activity signal (see Fig.
-3).
+3 in the paper).
 Note that on the Sun the filling factor of faculae is approximatively 10 times larger than the one of spots (Chapman-2001).

### 2018-11-20 manuscript_responses_v1.tex
Add files via upload
Jessi's comments & suggestions implemented in the manuscript

@@
 \begin{itemize}
-\item In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a stronger correlation with $\gamma$ than the correlation between N mean RV and BIS SPAN.}} Moreover, the correlation between the FWHM and the estimated RVs is also stronger, {\bf{for all the considered cases}}, when using the parameters from the SN compared to the parameters from the Normal.
+\item In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a correlation with $\gamma$ as strong as the correlation between N mean RV and BIS SPAN (R=-0.81).}}
+Moreover,  {\bf{when considering the case of a facula on the photosphere of the star}}, the correlation between the FWHM and the estimated RVs is stronger when using the parameters from the SN compared to the parameters from the Normal.
+{\bf{For the other presented cases, no statistically significant difference on the correlation between FWHM and the estimated RVs is obtained.}}
 
 \item We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.
-Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by 15 \% and 6 \%}} over the usual model, respectively, for facula and spot.
+Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by an additional 14.5 -15 \% and 5.3-5.8 \%}} over the usual model, respectively, for facula and spot.
 When applying this model on real data, the improvement is not as substantial, however, we still observe that planetary detection limits are improved by a non-negligible 12\%.
 \end{itemize}
-{\color{red} \bf [Both of these updates have been revised in the main text - please update if you agree with the changes in the text]}
 

### 2018-11-20 manuscript_v2_noiseSim.tex
updated responses
Add files via upload
Jessi's comments & suggestions implemented in the manuscript

--- 2018-11-19 manuscript_v2_noiseSim.tex
@@
 where $x$ and $y$ are two quantitative variables, $\text{cov}(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represent their standard deviations.
-A $p$-value for the statistical test with null hypothesis $H_{0}: R=0$ is also generally provided.
+A $p$-value for the statistical test with null hypothesis $H_{0}: R= 0$ is also generally provided.
 
@@
 
-\textbf{Exoplanets only produce a pure RV signal (i.e., exoplanets induce a Doppler shift of the entire stellar spectrum)}.
+\textbf{Exoplanets produce only a pure RV signal (i.e., exoplanets induce a Doppler shift of the entire stellar spectrum)}.
 On the contrary stellar activity and, in particular, the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.
@@
 {\bf The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula depends on the centre-to-limb angle $\theta$,  $\Delta T_{plage} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K \citep[][]{Meunier-2010a}}.
-In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of R=115'000.
-{\bf{ We consider an SNR=100 for our simulations.}}
+In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of R= 115'000.
+{\bf{ We consider an SNR= 100 for our simulations.}}
 
@@
 %We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters.
-{\bf{In addition the rms for N mean RV reduces from 8.02 \ms before correcting for stellar activity to {\color{red}1.02} \ms after correcting for stellar activity using the proposed linear model; the respective values for the SN median RV are 7.07 \ms to 0.88 \ms and for the SN mean RV are 5.9 \ms to 0.88 \ms.}}
+{\bf{In addition the rms for N mean RV reduces from 8.02 \ms before correcting for stellar activity to 1.02 \ms after correcting for stellar activity using the proposed linear model; the respective values for the SN median RV are 7.07 \ms to 0.88 \ms and for the SN mean RV are 5.9 \ms to 0.88 \ms.}}
 When comparing the correction proposed in Eq.~\eqref{eq:RV:correction} with what is generally used (i.e.
-a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by {\color{red} \bf an additional 14.5 -} {\bf{15\%}} {\color{red} \bf [I think we should emphasize the proposed correction is in addition to the usual correction, and it seems the range of improvement is actually 14.5-15\%]}.
+a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by {\bf{an additional 14.5 - 15\%}}.
 Looking at the significance of the coefficients in Table~\ref{table:faculae.test}, we observe that {\bf{all the parameters corresponding to the SN variables are statistically significant.
@@
 The correlations between the width and the CCF barycenter are more circular and no substantial correlation is observed. 
-Similar to the case with a facula, some parameters of the SN gives stronger correlations compared to the Normal parameters.
+%Similar to the case with a facula, some parameters of the SN gives stronger correlations compared to the Normal parameters.
 {\color{red} \bf I'm not sure the previous statement is correct anymore - the only correlations strong with the SN variables is described has having ``no substantial correlation'' in the previous statement...I suggest we delete the previous sentence, or revise to make it correct.]}
@@
 {\bf{In addition the rms for N mean RV reduces from 6.14 \ms before correcting for stellar activity to 3.04 \ms after  correcting for stellar activity using the proposed linear model; the respective values for the SN median RV are 5.85 \ms to 2.74 \ms and for the SN mean RV are 5.27 \ms to 2.74 \ms.}}
-When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf \color{red} and additional 5.3 - 5.8\% ]} \sout{\bf{6 \%}}.
+When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf an additional 5.3 - 5.8\%}.
 The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are all statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, {\bf{except the width of the CCF and the variable that captures the interaction between the width and the asymmetry of the CCF.}}
@@
 The correlations are weaker than in the case of the spot due to the planet inducing changes in RV without affecting the width or the asymmetry of the CCF.
-However, the order of the strength of the correlations between the CCF asymmetry parameters and RV are comparable with the ones obtained for the spot-only model: $\gamma$--SN median RV has the strongest correlation {\bf{($R=-0.7$)}}, followed by the correlation between BIS SPAN--N mean RV {\bf{($R=-0.69$)}} and finally by the correlation between $\gamma$--SN mean RV {\bf{($R=-0.67$)}}.
+However, the order of the strength of the correlations between the CCF asymmetry parameters and RV are comparable with the ones obtained for the spot-only model: $\gamma$--SN median RV has the strongest correlation {\bf{(R= -0.7)}}, followed by the correlation between BIS SPAN--N mean RV {\bf{(R= -0.69)}} and finally by the correlation between $\gamma$--SN mean RV {\bf{(R= -0.67)}}.
 The patterns observed in the width-RV phase space correlations in Fig.~\ref{fig:spot.plus.planet.corr} follow a circle, similar to the spot-only model; no substantial correlation is observed between those two parameters.
@@
 The proposed model from Eq.~\eqref{eq:RV:correction.overall} was fitted to the RV data and the results of the estimated model are summarized in Table~\ref{table:spotplanet.test}.   
-{\bf{Except for the intercept (coefficient $\beta_0$), the width of the CCF (coefficient $\beta_3$), and the variable that evaluates the interaction between the width and the asymmetry of the CCF (coefficient $\beta_4$), all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet.
-We also observe that the RV residuals, once corrected for stellar activity and the presence of the planet, are smaller in terms of rms when using the SN variables (rms = 2.28 \ms) rather than the Normal ones (rms = 2.80 \ms).}}
+{\bf{Except for the intercept term (coefficient $\beta_0$), the width of the CCF (coefficient $\beta_3$), and the variable that captures the interaction between the width and the asymmetry of the CCF (coefficient $\beta_4$), all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet.
+We also observe that the RV residuals, after correcting for stellar activity and the presence of the planet, have smaller rms when using the SN variables (rms = 2.29 \ms) rather than the Normal ones (rms = 2.80 \ms).}}
 %\begin{figure*}[htbp]
@@
 The simulated CCFs were generated using the SOAP 2.0 code, which can simulate activity signals induced by a spot or a facula on a solar-like star. 
-The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method, making them more useful indicators of activity.
-In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a stronger correlation with $\gamma$ than the correlation between N mean RV and BIS SPAN.}}
-Moreover, the correlation between the FWHM and the estimated RVs is also stronger, {\bf{for all the considered cases}}, when using the parameters from the SN compared to the parameters from the Normal.
-The SN parameters continued to have stronger correlations than the Normal in the setting where a planetary signal was added the SOAP 2.0 with a single spot.
+%The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method, making them more useful indicators of activity.
+%{\bf \color{red} The previous sentence is not correct; this was not demonstrated once the noise was added.]}
+In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a correlation with $\gamma$ as strong as the correlation between N mean RV and BIS SPAN (R= -0.81).}}
+Moreover,  {\bf{when considering the case of a facula on the photosphere of the star}}, the correlation between the FWHM and the estimated RVs is stronger when using the parameters from the SN compared to the parameters from the Normal.
+{\bf{For the other presented cases, no statistically significant difference on the correlation between FWHM and the estimated RVs is obtained.}}
+
+%The SN parameters continued to have stronger correlations than the Normal in the setting where a planetary signal was added the SOAP 2.0 with a single spot.
 
@@
 We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.
-Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by 15 \% and 6 \%}} over the usual model, respectively, for facula and spot.
+Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by an additional 14.5 -15 \% and 5.3-5.8 \%}} over the usual model, respectively, for facula and spot.
 When applying this model on real data, the improvement is not as substantial, however, we still observe that planetary detection limits are improved by a non-negligible 12\%.

### 2018-11-20 manuscript_responses_v1.tex
fixed some updates

@@
 \begin{itemize}
-\item In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a correlation with $\gamma$ as strong as the correlation between N mean RV and BIS SPAN (R=-0.81).}}
-Moreover,  {\bf{when considering the case of a facula on the photosphere of the star}}, the correlation between the FWHM and the estimated RVs is stronger when using the parameters from the SN compared to the parameters from the Normal.
-{\bf{For the other presented cases, no statistically significant difference on the correlation between FWHM and the estimated RVs is obtained.}}
+\item Sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot setting the SN median RV had a correlation with $\gamma$ as strong as the correlation between N mean RV and BIS SPAN (R= -0.81), and}}
+{\bf{for the facula setting}}, the correlation between the FWHM and the estimated RVs is stronger when using the parameters from the SN compared to the parameters from the Normal.
+{\bf{For the spot and the spot plus a planet settings, no statistically significant difference on the correlation between FWHM and the estimated RVs were obtained.}}
 

### 2018-11-20 manuscript_v2_noiseSim.tex
fixed some updates

@@
 %{\bf \color{red} The previous sentence is not correct; this was not demonstrated once the noise was added.]}
-In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a correlation with $\gamma$ as strong as the correlation between N mean RV and BIS SPAN (R= -0.81).}}
-Moreover,  {\bf{when considering the case of a facula on the photosphere of the star}}, the correlation between the FWHM and the estimated RVs is stronger when using the parameters from the SN compared to the parameters from the Normal.
-{\bf{For the other presented cases, no statistically significant difference on the correlation between FWHM and the estimated RVs is obtained.}}
+Sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot setting the SN median RV had a correlation with $\gamma$ as strong as the correlation between N mean RV and BIS SPAN (R= -0.81), and}}
+{\bf{for the facula setting}}, the correlation between the FWHM and the estimated RVs is stronger when using the parameters from the SN compared to the parameters from the Normal.
+{\bf{For the spot and the spot plus a planet settings, no statistically significant difference on the correlation between FWHM and the estimated RVs were obtained.}}
 

### 2018-11-21 manuscript_responses_v1.tex
added comment about deleted statements in responses to referee
Add files via upload
updated manuscript

@@
 Below we address the new comments individually.
+Updated statements in the main text are presented in bold, and statements that are no longer relevant have been deleted.
 
@@
 \item[]  RESPONSE:  We considered the noise on the different parameters of the Normal and SN fit to the CCF for a SNR of 100, which is typical for high-precision RV measurements.
-We updated the entire Section 4 of the manuscript with the obtained results.
+At the beginning of Section 4 and in the Discussion of Section 7 we noted, respectively: ``We consider a S/N of 100 for our simulations'' and ``For our simulations we considered a S/N of 100''.
+We also updated the entire Section 4 of the manuscript with the obtained results.
 

### 2018-11-21 manuscript_v2_noiseSim.tex
Add files via upload
updated manuscript

@@
 The code also returns the RV and the FWHM estimated using a Normal model for the CCF, and the BIS SPAN obtained by calculating the bisector of the CCF. 
-SOAP 2.0 gives noiseless CCFs affected by stellar activity, which are used to compare the performances of SN and Normal models of the CCF.
+SOAP 2.0 gives {\color{red}noiseless} CCFs affected by stellar activity, which are used to compare the performances of SN and Normal models of the CCF.
 
@@
 In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of R= 115'000.
-{\bf{ We consider an SNR= 100 for our simulations.}}
+{\bf{ We consider a S/N of 100 for our simulations.}}
 
@@
 Correlations between the different RV estimates and the different CCF asymmetry or width estimates are displayed in Fig.~\ref{fig:faculae.corr}. 
-The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are {\bf{weaker}} than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of {\bf{$R$=-0.11, -0.55 and -0.81}}, respectively.
+The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are {\bf{weaker}} than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of {\bf{$R= -0.11, -0.55$ and $-0.61$}}, respectively.
 %
@@
 
-The simulated SOAP data of the previous section were helpful in assessing the performance of the proposed methodology in a setting where the ground truth was known.
+The simulated SOAP 2.0 data of the previous section were helpful in assessing the performance of the proposed methodology in a setting where the ground truth was known.
 In this section we present an analysis conducted on real observations, in particular, the star Alpha Centauri B, and compare the performance when fitting a CCF using the SN density defined in Sec.
@@
 The simulated CCFs were generated using the SOAP 2.0 code, which can simulate activity signals induced by a spot or a facula on a solar-like star.
+{\bf{For our simulations we considered a S/N of 100.}}
 %The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method, making them more useful indicators of activity.
@@
 
-The conclusion found for the SOAP 2.0 simulations that the correlation between the CCF asymmetry and the estimated RV, as well as between the CCF width and the estimated RV, is stronger for the SN parameters than the Normal ones also holds when using real data.
+The conclusion found for the SOAP 2.0 simulations showed that the correlation between the CCF asymmetry and the estimated RV, as well as between the CCF width and the estimated RV, is stronger for the SN parameters than the Normal ones also holds when using real data.
 %
@@
 Because the temperature between a spot and a facula is significantly different, their spectra should be different. 
-Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region on the equator {\bf{in order to isolate the effects of those active regions}}.
+{\bf{Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region on the equator in order to isolate the effects of those active regions}}.
 %\xavier{The fact that we also find significant differences between the simulated and real data for the correlations between BIS SPAN and N mean RV and between FWHM and N mean RV shows that the SOAP 2.0 simulation studied here are too simple to explain the complexity of stellar activity in real RV observations.}

### 2018-11-21 manuscript_v2_noiseSim.tex
edit Xav

--- 2018-11-20 manuscript_v2_noiseSim.tex
@@
 \usepackage{longtable}
+\usepackage[normalem]{ulem}
 
 \usepackage{afterpage}
-\usepackage{ulem}
 
@@
 %%
-%{The performances of the proposed method are compared to the commonly employed Normal density using both simulations and real observations, with different levels of activity and signal-to-noise ratio (S/N) levels.}
+%{The performances of the proposed method are compared to the commonly employed Normal density using both simulations and real observations, with different levels of activity and signal-to-noise ratio.}
 %%We analyze 5 stars with different activity levels and whose CCF's have different signal-to-noise ratio (S/N) levels.
@@
 %
-{The performances of the proposed method are compared to the commonly employed Normal density using both simulations and real observations, with different levels of activity and signal-to-noise ratio (S/N) levels.}
+{The performances of the proposed method are compared to the commonly employed Normal density using both simulations and real observations, with different levels of activity and signal-to-noise ratio.}
 %
@@
 This suggests that the CCF parameters estimated using a SN density are more sensitive to stellar activity, which can be helpful 
-when estimating stellar rotational periods and more in general when characterizing stellar activity signals.
+when estimating stellar rotational periods and when characterizing stellar activity signals.
 Using the proposed SN approach, the uncertainties estimated on the RV defined as the median of the SN are on average $10\%$ smaller than the uncertainties calculated on the mean of the Normal. 
@@
 Based on simple simulations, we were able to demonstrate that this new model improves the planetary detection limits by 12\% 
-compared to the usual model used to account for stellar activity.
+compared to the model commonly used to account for stellar activity.
 }
@@
 Stellar activity is responsible for creating magnetic regions on the surface of stars, and those regions change locally the temperature and the convection, which can induce spurious RVs variations \citep[e.g.][]{Meunier-2010a, Dumusque-2014b, Borgniet-2015}.
-In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so creates a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}.
+In theory, it should be easy to differentiate between the Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and the effect of stellar activity, which modifies the shape of spectral lines and by doing so creates a spurious shift of the stellar spectrum \citep{Saar-1997b,Hatzes-2002,Kurster2003,Lindegren-2003,Desort-2007,Lagrange-2010,Meunier-2010a,Dumusque-2014b}.
 However, on quiet GKM dwarfs, the main targets for precise RVs measurements, stellar activity can induce signals of a few \ms. 
@@
 where $x$ and $y$ are two quantitative variables, $\text{cov}(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represent their standard deviations.
-A $p$-value for the statistical test with null hypothesis $H_{0}: R= 0$ is also generally provided.
+A $p$-value for the statistical test with null hypothesis $H_{0}: R=0$ is also generally provided.
 
@@
 
-\textbf{Exoplanets produce only a pure RV signal (i.e., exoplanets induce a Doppler shift of the entire stellar spectrum)}.
+\textbf{Exoplanets produce a Doppler shift of the entire stellar spectrum}.
 On the contrary stellar activity and, in particular, the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.
@@
 The code also returns the RV and the FWHM estimated using a Normal model for the CCF, and the BIS SPAN obtained by calculating the bisector of the CCF. 
-SOAP 2.0 gives noiseless CCFs affected by stellar activity, which are used to compare the performances of SN and Normal models of the CCF.
+\sout{SOAP 2.0 gives noiseless CCFs affected by stellar activity, which are used to compare the performances of SN and Normal models of the CCF.}
 
@@
 The stellar effective temperature is set to 5778 K, and a quadratic limb-darkening relation with linear and quadratic coefficients 0.29 and 0.34, respectively \citep[][]{Oshagh-2013a, Claret-2011}.
-{\bf The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula depends on the centre-to-limb angle $\theta$,  $\Delta T_{plage} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K \citep[][]{Meunier-2010a}}.
-In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of R= 115'000.
-{\bf{ We consider an SNR= 100 for our simulations.}}
+{\bf The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula depends on the centre-to-limb angle $\theta$,  $\Delta T_{facula} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K \citep[][]{Meunier-2010a}}.
+In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of R=115'000.
+{\bf{ For the simulations presented in this section, we considered a S/N of 100.}}
 
@@
 Correlations between the different RV estimates and the different CCF asymmetry or width estimates are displayed in Fig.~\ref{fig:faculae.corr}. 
-The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are {\bf{weaker}} than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of {\bf{$R$=-0.11, -0.55 and -0.81}}, respectively.
-%
-{\bf{There is a stronger correlation between SN FWHM and SN mean RV ($R=0.92$) than between SN FWHM and SN median RV ($R=0.65$).
-The correlation between FWHM and N mean RV is the weakest ($R=0.47$), and the correlation between FWHM and SN mean RV is the strongest ($R=0.92$).}}
-This first analysis shows that in the case of a facula, using some parameters from the SN can lead to stronger correlations than the ones obtained by the usual Normal parameters. 
-{\bf Therefore, the SN parameters may better probe stellar activity that induces changes in the FWHM.}
-We investigate this feature further in the following two sections, where we consider simulated data with a single spot and a spot plus a planet, and in Sec.~\ref{sec:4} with real observations.
+{\bf The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are weaker than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of $R$=-0.11, -0.55 and -0.81, respectively.
+Therefore, it seems that when looking at the CCF asymmetry, fitting a SN density to the CCF does not help.
+However, when looking at the correlations between the width of the CCF and the RV, the stronger correlation can be found between SN FWHM and SN mean RV ($R=0.92$).
+Then follows the correlation between SN FWHM and SN median RV ($R=0.65$), and finally FWHM and N mean RV ($R=0.47$).
+Over all the different correlations in the case of a facule, the strongest one is found between SN FWHM and SN mean RV, which demonstrates that fitting a SN density to the CCF can be helpful to better probe stellar activity}
+%%
+%{\bf{There is a stronger correlation between SN FWHM and SN mean RV ($R=0.92$) than between SN FWHM and SN median RV ($R=0.65$), but the correlation between FWHM and N mean RV is the weakest ($R=0.47$).}}
+%This first analysis shows that in the case of a facula, using some parameters from the SN can lead to stronger correlations than the ones obtained by the usual Normal parameters.
+Therefore, the SN parameters may better probe stellar activity.
+%We investigate this feature further in the following two sections, where we consider simulated data with a single spot and a spot plus a planet, and in Sec.~\ref{sec:4} with real observations.
 
@@
 
-The RV variations displayed in Fig.~\ref{fig:faculae} are caused only by stellar activity, in this case a facula, so we applied the activity correction proposed in Eq.~\eqref{eq:RV:correction} to evaluate the performance of the model in this setting.
+The RV variations displayed in Fig.~\ref{fig:faculae} are caused only by stellar activity, in this case a facula.
+We applied the activity correction proposed in Eq.~\eqref{eq:RV:correction} to evaluate the performance of the model in this setting.
 The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}.
@@
 %We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters.
-{\bf{In addition the rms for N mean RV reduces from 8.02 \ms before correcting for stellar activity to 1.02 \ms after correcting for stellar activity using the proposed linear model; the respective values for the SN median RV are 7.07 \ms to 0.88 \ms and for the SN mean RV are 5.9 \ms to 0.88 \ms.}}
+{\bf In addition, the proposed linear model allows to reduce the activity effect from a RV rms of 8.02 \ms to 1.02 \ms when considering the CCF contrast and FWHM, and the BIS SPAN.
+When using the parameters derived from the SN, the improvements for SN median RV and SN mean RV are 7.07 \ms down to 0.88 \ms and 5.9 \ms down to 0.88 \ms, respectively}
 When comparing the correction proposed in Eq.~\eqref{eq:RV:correction} with what is generally used (i.e.
-a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by {\bf{an additional 14.5 - 15\%}}.
+a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by  {\bf{15 \%}}.
 Looking at the significance of the coefficients in Table~\ref{table:faculae.test}, we observe that {\bf{all the parameters corresponding to the SN variables are statistically significant.
@@
  (bottom) The residuals from the model fit using Eq.~\eqref{eq:RV:correction} (red pluses) and the residuals from the usual correction (green triangles).
-The std.
-are also reported in the legend, and the residuals have a smaller systematic component when using the proposed model of Eq.~\eqref{eq:RV:correction} compared to the usual model.
+The standard deviations are also reported in the legend, and the residuals have a smaller systematic component when using the proposed model of Eq.~\eqref{eq:RV:correction} compared to the usual model.
 The tests of statistical significance on the parameters are presented in Table \ref{table:faculae.test}.
@@
 {\bf{The correlation between $\gamma$ and SN median RV and the correlation between the BIS SPAN and N mean RV are the strongest ($R=-0.81$) followed by the $\gamma$ - SN mean RV correlation ($R=-0.76$).}}
-The correlations between the width and the CCF barycenter are more circular and no substantial correlation is observed. 
-%Similar to the case with a facula, some parameters of the SN gives stronger correlations compared to the Normal parameters.
-{\color{red} \bf I'm not sure the previous statement is correct anymore - the only correlations strong with the SN variables is described has having ``no substantial correlation'' in the previous statement...I suggest we delete the previous sentence, or revise to make it correct.]}
+The correlations between the width and the CCF barycenter draw circles and no significant correlation is observed. 
+{\bf Not like in the facula case, when considering a spot simulated with SAOP 2.0 and a S/N of 100, the SN fit to the CCF does not gives parameters that can probe better stellar activity.
+\sout{Similar to the case with a facula, some parameters of the SN gives stronger correlations compared to the Normal parameters.}}
 
@@
 The results of this correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table~\ref{table:spot.test}.
-%{\bf{In this case the proposed correction is not able to perform as well as for the facula, and $R^2$ values for the linear combination are smaller than 0.8}}. 
-{\bf The $R^2$ values for the linear combination are between 0.72 and 0.78, which are not as strong as the setting with a facula.}
-
-%In Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than {\bf{6.14\ms}} down to a rms smaller than {\bf{3.05 \ms}}, for any of the different RV estimates.
-{\bf{In addition the rms for N mean RV reduces from 6.14 \ms before correcting for stellar activity to 3.04 \ms after  correcting for stellar activity using the proposed linear model; the respective values for the SN median RV are 5.85 \ms to 2.74 \ms and for the SN mean RV are 5.27 \ms to 2.74 \ms.}}
-When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf an additional 5.3 - 5.8\%}.
-The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are all statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, {\bf{except the width of the CCF and the variable that captures the interaction between the width and the asymmetry of the CCF.}}
+{\bf In the case of a spot, the proposed correction is not able to perform as well as for the facula, and $R^2$ values for the linear combination are between 0.7 and 0.8}. 
+{\bf The correction is able to mitigate stellar activity from a N mean RV rms of 6.14\ms down to 3.04\ms.
+The corresponding values for SN median RV and SN mean RV are 5.85\ms down to 2.74 \ms and 5.27\ms down to 2.74\ms, respectively.}
+When comparing the activity correction proposed in this paper with what is commonly used, which means only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf{6 \%}}.
+The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, {\bf except the width of the CCF $\beta_3$ and the interaction term $\beta_4$}
 %This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
@@
  (bottom) The residuals from the model fit using Eq.~\eqref{eq:RV:correction} (red pluses) and the residuals from the usual correction (green triangles). 
- The std. are also reported in the legend, and the residuals have a smaller systematic component when using the proposed model compared to the usual model.
+ The standard deviations are also reported in the legend, and the residuals have a smaller systematic component when using the proposed model compared to the usual model.
 The tests of statistical significance on the parameters are presented in Table~\ref{table:spot.test}.
@@
 The correlations are weaker than in the case of the spot due to the planet inducing changes in RV without affecting the width or the asymmetry of the CCF.
-However, the order of the strength of the correlations between the CCF asymmetry parameters and RV are comparable with the ones obtained for the spot-only model: $\gamma$--SN median RV has the strongest correlation {\bf{(R= -0.7)}}, followed by the correlation between BIS SPAN--N mean RV {\bf{(R= -0.69)}} and finally by the correlation between $\gamma$--SN mean RV {\bf{(R= -0.67)}}.
+However, the order of the strength of the correlations between the CCF asymmetry parameters and RV are comparable with the ones obtained for the spot-only model: $\gamma$--SN median RV has the strongest correlation {\bf{($R=-0.7$)}}, followed by the correlation between BIS SPAN--N mean RV {\bf{($R=-0.69$)}} and finally by the correlation between $\gamma$--SN mean RV {\bf{($R=-0.67$)}}.
 The patterns observed in the width-RV phase space correlations in Fig.~\ref{fig:spot.plus.planet.corr} follow a circle, similar to the spot-only model; no substantial correlation is observed between those two parameters.
@@
 The proposed model from Eq.~\eqref{eq:RV:correction.overall} was fitted to the RV data and the results of the estimated model are summarized in Table~\ref{table:spotplanet.test}.
-{\bf{Except for the intercept term (coefficient $\beta_0$), the width of the CCF (coefficient $\beta_3$), and the variable that captures the interaction between the width and the asymmetry of the CCF (coefficient $\beta_4$), all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet.
-We also observe that the RV residuals, after correcting for stellar activity and the presence of the planet, have smaller rms when using the SN variables (rms = 2.29 \ms) rather than the Normal ones (rms = 2.80 \ms).}}
+{\bf{Except for the intercept $\beta_0$, the width of the CCF $\beta_3$, and the interaction term $\beta_4$ that evaluates the interaction between the width and the asymmetry of the CCF, all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet.
+We also observe that the RV residuals, once corrected for stellar activity and the presence of the planet, are smaller in terms of rms when using the SN variables (rms = 2.28 \ms) rather than the Normal ones (rms = 2.80 \ms).}}
 %\begin{figure*}[htbp]
@@
 \caption{P-values for the different coefficients used in Eq.~\eqref{eq:RV:correction} for the correction of stellar activity induced by an equatorial 1\% spot on the simulated Sun, and a planet with a period of one-third the rotational period of the star and a semi-amplitude  of 10\,\ms.
-{\bf{All the parameters corresponding to the Normal or SN variables are statistically significant, except the intercept, the width of the CCF and the variable that evaluates the interaction between the width and the asymmetry of the CCF.
-Once corrected for stellar activity and the presence of the planet, the residuals are smaller in terms of rms when using the SN variables}}.
-Note that since nonlinear least squares was required, the residual standard error rather than the $R^2$ is displayed as a reference.}
+{\bf All the parameters corresponding to the Normal or SN variables are statistically significant, except the intercept $\beta_0$, the width of the CCF $\beta_3$ and the interaction term $\beta_4$ that evaluates the interaction between the width and the asymmetry of the CCF.
+Once corrected for stellar activity and the presence of the planet, the residuals are smaller in terms of rms when using the SN variables.
+Note that because we used nonlinear least squares to fit the best model, the residual rms rather than the $R^2$ is displayed as a reference.}}
 \label{table:spotplanet.test}
@@
 %as we saw in Sec.~\ref{sec:soap.spot} a spot induces a negative correlation between $\gamma$ and SN mean RV and weak correlations are measured between SN FWHM and SN mean RV.
-%{\bf{Another feature that suggests the presence of faculae is the statistically significant p--value associated to the interaction term $\gamma \cdot \text{SN FWHM}$ used in the proposed function to correct from stellar activity, as summarized in Table~\ref{table:alphacent.test};
-%as we saw in Sec.~\ref{sec:soap.faculae} a facula produces as well a statistically significant p--value associated to the  interaction term $\gamma \cdot \text{SN FWHM}$ (Table~\ref{table:faculae.test}) while the same does not happen when a spot is considered (Table~\ref{table:spot.test}).}}
+{\bf{Another feature that suggests the presence of faculae is the statistically significant p--value associated to the interaction term $\gamma \cdot \text{SN FWHM}$ used in the proposed function to correct from stellar activity, as summarized in Table~\ref{table:alphacent.test};
+as we saw in Sec.~\ref{sec:soap.faculae} a facula produces as well a statistically significant p--value associated to the  interaction term $\gamma \cdot \text{SN FWHM}$ (Table~\ref{table:faculae.test}) while the same does not happen when a spot is considered (Table~\ref{table:spot.test}).}}
 \citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
@@
 Results illustrating the performance of the stellar activity correction proposed in Sec.~\ref{sec:31} are displayed in Fig~\ref{fig:alphacent:correctionRV}. 
-For Alpha Centauri B, the RV estimated with SN mean RV has a std that is 35\% larger than the std of the RV estimated with the N mean RV, and the std of SN median RV is 9\% larger than that of the N mean RV.
+For Alpha Centauri B, the RV estimated with SN mean RV has a rms that is 35\% larger than the rms of the RV estimated with the N mean RV, and the rms of SN median RV is 9\% larger than that of the N mean RV.
 Even though we see these differences in the estimated RV, once we correct for stellar activity using Eq.~\eqref{eq:RV:correction}, 
@@
 the proposed linear model that corrects for stellar activity does not necessarily perform better in the SN case than in the Normal case. 
-The new correction for stellar activity proposed in Sec.~\ref{sec:31} performed similarly to the usual correction that uses only a linear combination of the width and the asymmetry of the CCF, however it still gives RV rms that are 8\,\cms\,smaller than the usual correction.
+The new correction for stellar activity proposed in Sec.~\ref{sec:31} performed only slightly better than the usual correction that uses only a linear combination of the width and the asymmetry of the CCF.
 
@@
 
-In the previous section we evaluated the improvement obtained by the SN parameters compared to the Normal parameters and the BIS SPAN.
+In the previous section we evaluated for Alpha Centauri B the improvement obtained by the SN parameters compared to the Normal parameters and the BIS SPAN.
 We carryout similar analyses for four other main sequence stars: HD192310 \citep[K2V,][]{Pepe-2011}, HD10700 \citep[G8V,][]{Feng:2017ac}, HD215152 \citep[K3V,][]{Delisle:2018aa} and finally Corot-7 \citep[K0V,][]{Haywood-2014}.
-The same correlation plots and residual plots displayed in the previous section for Alpha Centauri B can be found for those new four stars in Appendix~\ref{appendix}.
+The same correlation and residual plots displayed in the previous section for Alpha Centauri B can be found for those new four stars in Appendix~\ref{appendix}.
 
@@
 
-When fitting a SN density shape to the CCF, parameters used to define the RV (i.e.
-the CCF barycenter), the amplitude (sometimes called the CCF contrast), the width and the asymmetry of the CCF can all be estimated in a single model framework.
+When fitting a SN density to the CCF, parameters used to estimate the RV, defined as the CCF barycenter, the amplitude, sometimes called the CCF contrast, the width and the asymmetry of the CCF can all be estimated in a single model framework.
 For the estimation of the RV, we investigated the use of the mean and the median of the SN density. 
@@
 
-To evaluate the performance of the proposed SN framework, tests on both simulated and real data were carried out and compared to the commonly employed approach of fitting a Normal density shape (for estimating the RV and FWHM) and then separately deriving the BIS SPAN (for estimating the asymmetry).
+To evaluate the performance of the proposed SN framework, tests on both simulated and real data were carried out and compared to the commonly employed approach of fitting a Normal density shape to get access to the RV and the CCF FWHM and then separately deriving the BIS SPAN to estimate the CCF the asymmetry.
 The simulated CCFs were generated using the SOAP 2.0 code, which can simulate activity signals induced by a spot or a facula on a solar-like star.
-%The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method, making them more useful indicators of activity.
-%{\bf \color{red} The previous sentence is not correct; this was not demonstrated once the noise was added.]}
-Sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot setting the SN median RV had a correlation with $\gamma$ as strong as the correlation between N mean RV and BIS SPAN (R= -0.81), and}}
-{\bf{for the facula setting}}, the correlation between the FWHM and the estimated RVs is stronger when using the parameters from the SN compared to the parameters from the Normal.
-{\bf{For the spot and the spot plus a planet settings, no statistically significant difference on the correlation between FWHM and the estimated RVs were obtained.}}
-
-%The SN parameters continued to have stronger correlations than the Normal in the setting where a planetary signal was added the SOAP 2.0 with a single spot.
+The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method, making them more useful indicators of activity.
+In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a stronger correlation with $\gamma$ than the correlation between N mean RV and BIS SPAN.}}
+Moreover, the correlation between the FWHM and the estimated RVs is also stronger, {\bf{for all the considered cases}}, when using the parameters from the SN compared to the parameters from the Normal.
+The SN parameters continued to have stronger correlations than the Normal in the setting where a planetary signal was added the SOAP 2.0 with a single spot.
 
@@
 We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.
-Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by an additional 14.5 -15 \% and 5.3-5.8 \%}} over the usual model, respectively, for facula and spot.
+Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by 15 \% and 6 \%}} over the usual model, respectively, for facula and spot.
 When applying this model on real data, the improvement is not as substantial, however, we still observe that planetary detection limits are improved by a non-negligible 12\%.
@@
 Moreover, once corrected for stellar activity using Eq.
-\ref{eq:RV:correction}, the remaining std from the SN models are $0.334$ \ms smaller than the remaining std of the Normal model.}
+\ref{eq:RV:correction}, the remaining standard deviation from the SN models are $0.334$ \ms smaller than the remaining standard deviation of the Normal model.}
    \label{fig:Corot-7:correctionRV}

### 2018-11-21 manuscript_v2_noiseSim.tex
Update Xavier

@@
 {\bf{Except for the intercept $\beta_0$, the width of the CCF $\beta_3$, and the interaction term $\beta_4$ that evaluates the interaction between the width and the asymmetry of the CCF, all the other Normal or SN parameters are significantly useful to explain the RV variation induced by a spot plus a planet.
-We also observe that the RV residuals, once corrected for stellar activity and the presence of the planet, are smaller in terms of rms when using the SN variables (rms = 2.28 \ms) rather than the Normal ones (rms = 2.80 \ms).}}
+We also observe that the RV residuals, once corrected for stellar activity and the presence of the planet, are smaller in terms of rms when using the SN variables (rms = 2.29 \ms) rather than the Normal ones (rms = 2.80 \ms).}}
 %\begin{figure*}[htbp]
@@
 
-The simulated SOAP data of the previous section were helpful in assessing the performance of the proposed methodology in a setting where the ground truth was known.
-In this section we present an analysis conducted on real observations, in particular, the star Alpha Centauri B, and compare the performance when fitting a CCF using the SN density defined in Sec.
+The analysis of the simulated SOAP 2.0 data in the previous section were helpful in assessing the performance of the proposed methodology in a setting where the ground truth was known.
+{\bf We found that the parameters derived by the SN were equally correlated or in the case of a facula even more when the data are only affected by stellar activity.} In this section we present an analysis conducted on real observations, in particular, the star Alpha Centauri B, and compare the performance when fitting a CCF using the SN density defined in Sec.
 \ref{sec:3} with the commonly employed approach based on fitting a Normal density for estimating the RV and retrieving the BIS SPAN for evaluating the asymmetry of the CCF.
@@
 Note that more observations were carried out that year, however only the data that were not significantly affected by contamination from Alpha Centauri A were used \citep[see][]{Dumusque-2012}.
-The selected observations represent arguably, among all RV data existing, the best sampled and most precise RV data set showing strong solar-like activity signal \citep{Thompson-2017, Dumusque-2012}.
+The selected observations represent arguably, among all RV data existing, the best sampled and most precise RV data set showing strong solar-like activity signal \citep{Dumusque:2018aa, Thompson-2017}.
 

### 2018-11-21 manuscript_v2_noiseSim.tex
Edit Xavier

@@
 %as we saw in Sec.~\ref{sec:soap.spot} a spot induces a negative correlation between $\gamma$ and SN mean RV and weak correlations are measured between SN FWHM and SN mean RV.
-{\bf{Another feature that suggests the presence of faculae is the statistically significant p--value associated to the interaction term $\gamma \cdot \text{SN FWHM}$ used in the proposed function to correct from stellar activity, as summarized in Table~\ref{table:alphacent.test};
-as we saw in Sec.~\ref{sec:soap.faculae} a facula produces as well a statistically significant p--value associated to the  interaction term $\gamma \cdot \text{SN FWHM}$ (Table~\ref{table:faculae.test}) while the same does not happen when a spot is considered (Table~\ref{table:spot.test}).}}
+{\bf Another feature that suggests the presence of faculae is the statistically significant p--value associated to the interaction term $\gamma \cdot \text{SN FWHM}$ used in the proposed function to correct from stellar activity, as summarized in Table~\ref{table:alphacent.test}.
+In Sec.~\ref{sec:soap.faculae}, we saw that the interaction term was only significant in the case of faculae.
+as we saw in Sec.~\ref{sec:soap.faculae} a facula produces as well a statistically significant p--value associated to the  interaction term $\gamma \cdot \text{SN FWHM}$}
 \citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.

### 2018-11-21 manuscript_v2_noiseSim.tex
Update Xavier

@@
 %
-This behavior is similar to the one observed for the facula simulated with SOAP 2.0 in Sec.~\ref{sec:soap.faculae}, suggesting that the activity signal could be due to faculae present on Alpha Centauri B.
-%
-%Another feature that suggests the presence of faculae is the strong positive measured correlation between $\gamma$ and SN mean RV and  between SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot};
-%as we saw in Sec.~\ref{sec:soap.spot} a spot induces a negative correlation between $\gamma$ and SN mean RV and weak correlations are measured between SN FWHM and SN mean RV.
-{\bf Another feature that suggests the presence of faculae is the statistically significant p--value associated to the interaction term $\gamma \cdot \text{SN FWHM}$ used in the proposed function to correct from stellar activity, as summarized in Table~\ref{table:alphacent.test}.
-In Sec.~\ref{sec:soap.faculae}, we saw that the interaction term was only significant in the case of faculae.
-as we saw in Sec.~\ref{sec:soap.faculae} a facula produces as well a statistically significant p--value associated to the  interaction term $\gamma \cdot \text{SN FWHM}$}
-\citet{Dumusque-2014c} had previously suggested that the activity of Alpha Centauri B could be due to faculae.
-%When using SN mean RV, it is possible to observe more variations than the ones measured by the Normal fitting.
-This happens because the mean of the SN is more sensitive to stellar activity.
-In fact, because the SN includes an asymmetry parameter, SN mean RV gets more shifted in the direction of the asymmetry induced by stellar activity.
-On the other hand, when using SN median RV, smaller variations in RV are caused by changes in the asymmetry of the CCF, because this second location parameter is a more robust indicator than the mean.
-The bottom plot of Fig.~\ref{fig:alphacent:diff:RV} captures this aspect.
-Both indicators can be used to capture and summarise the different information available in the CCF, as will be shown in the remainder of this work.
-%%
 %\begin{figure*}[htbp]
@@
 
+{\bf Comparing }
+
 Results illustrating the performance of the stellar activity correction proposed in Sec.~\ref{sec:31} are displayed in Fig~\ref{fig:alphacent:correctionRV}. 
@@
 This is not a surprising result since the three different RV estimates have the same RV residual rms after correction for activity, but before correction, SN mean RV had the largest RV rms (see Fig~\ref{fig:alphacent:correctionRV}).
+
+{\bf When looking at the results discussed in this section, it is likely that the activity signal of Alpha Centauri B is due to faculae. 
+Like observed for the simulated facula in Sec.~\ref{sec:soap.faculae}, the amplitude of the activity signal is slightly stronger for SN mean RV
+than for N mean RV or SN median RV; the amplitude of the two latest being comparable. In addition, when applying the proposed correction for
+activity in the case of the Alpha Centauri B data, the interaction term is significant, which was only the case for the simulated facula in 
+Sec.~\ref{sec:soap.faculae}. Those are arguments strengthen the findings of \citet{Dumusque-2014c} that also found evidence for faculae
+dominating the RV stellar signal of Alpha Centauri B.}
+%Another feature that suggests the presence of faculae is the strong positive measured correlation between $\gamma$ and SN mean RV and  between SN FWHM and SN mean RV, as displayed in Fig.~\ref{fig:alphacent:corrPlot};
+%as we saw in Sec.~\ref{sec:soap.spot} a spot induces a negative correlation between $\gamma$ and SN mean RV and weak correlations are measured between SN FWHM and SN mean RV.
+%When using SN mean RV, it is possible to observe more variations than the ones measured by the Normal fitting.
+This happens because the mean of the SN is more sensitive to stellar activity.
+In fact, because the SN includes an asymmetry parameter, SN mean RV gets more shifted in the direction of the asymmetry induced by stellar activity.
+On the other hand, when using SN median RV, smaller variations in RV are caused by changes in the asymmetry of the CCF, because this second location parameter is a more robust indicator than the mean.
+The bottom plot of Fig.~\ref{fig:alphacent:diff:RV} captures this aspect.
+Both indicators can be used to capture and summarise the different information available in the CCF, as will be shown in the remainder of this work.
+%%
 

### 2018-11-22 manuscript_v2_noiseSim.tex
Update Xavier

@@
 
-{\bf Comparing }
+{\bf When comparing the correlation between the different Normal and SN parameters in the case of the real data of Alpha Centauri B (see Fig.~\ref{fig:alphacent:corrPlot}) with the correlations obtained in the SOAP 2.0 simulations (see Sec.~\ref{sec:soap.spot.planet}), we observe some significant differences.
+The correlations between the different parametrisations of the CCF asymmetry and barycentre do not match between the real and simulated data.
+In the real case, the correlations between $\gamma$ and SN mean RV, $\gamma$ and SN median RV and BIS SPAN and N mean RV are all positives.
+In the case of the SOAP 2.0 simulated data for a facula or a spot, we always find negatives correlations.
+It is therefore not possible to reproduce with SOAP 2.0 the CCF asymmetry variations observed in real observations.
+On the contrary, the correlations between the CCF width and barycentre match between the real data and a SOAP 2.0 simulated facula.
+It seems therefore that SOAP 2.0 simulation are able to correctly model the width variation of the CCF, however not its asymmetry.
+This is probably because in the SOAP 2.0 simulation, a facula is modelled using the same spectrum as a spot, with only a different flux.
+It is well known that facula have a different temperature than spots, and therefore a spectrum that significantly differs \citep[e.g.][]{Cavallini-1985a}.
+Looking at other stellar activity simulation like StarSim \citep[][]{Herrero:2016aa}, it seems that simulating a positive correlation between the CCF asymmetry and barycentre is not possible with current tools, and some progress are still to be made.}
 
@@
 The correlation between $\gamma$ and SN mean RV is the strongest among all the asymmetry-RV correlations.
-%
 Between the width parameters and the estimated RV, the strongest correlation often is between SN FWHM and SN mean RV.
 However, there is one exception in the case of HD10700 where the Pearson correlation coefficient between FWHM and N mean RV is equal to $R=0.53$, while it is $R=0.42$ between SN FWHM and SN mean RV, and $R=0.5$ between SN FWHM and SN median RV.
+{\bf Like in the case of Alpha Centauri B, positive correlations are always observed between the asymmetry and barycentre of the CCF.
+This cannot be explained by SOAP 2.0 and to our knowledge by other stellar activity simulators, showing the limit of these tools.}
 
@@
 
-When fitting a SN density to the CCF, parameters used to estimate the RV, defined as the CCF barycenter, the amplitude, sometimes called the CCF contrast, the width and the asymmetry of the CCF can all be estimated in a single model framework.
+When fitting a SN density shape to the CCF, parameters used to estimate the RV, defined as the CCF barycenter, the amplitude, sometimes called the CCF contrast, the width and the asymmetry of the CCF can all be estimated in a single model framework.
 For the estimation of the RV, we investigated the use of the mean and the median of the SN density. 
@@
 
-To evaluate the performance of the proposed SN framework, tests on both simulated and real data were carried out and compared to the commonly employed approach of fitting a Normal density shape to get access to the RV and the CCF FWHM and then separately deriving the BIS SPAN to estimate the CCF the asymmetry.
+To evaluate the performance of the proposed SN framework, tests on both simulated and real data were carried out and compared to the commonly employed approach of fitting a Normal density shape to the CCF to get access to the RV and the FWHM, and then separately deriving the BIS SPAN to estimate the CCF asymmetry.
 The simulated CCFs were generated using the SOAP 2.0 code, which can simulate activity signals induced by a spot or a facula on a solar-like star.
-The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method, making them more useful indicators of activity.
-In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a stronger correlation with $\gamma$ than the correlation between N mean RV and BIS SPAN.}}
-Moreover, the correlation between the FWHM and the estimated RVs is also stronger, {\bf{for all the considered cases}}, when using the parameters from the SN compared to the parameters from the Normal.
-The SN parameters continued to have stronger correlations than the Normal in the setting where a planetary signal was added the SOAP 2.0 with a single spot.
+{\bf To simulate realistic data, we considered a S/N of 100, which is typical for high-precision RV observations.}
+
+The results of the simulation study suggest that {\bf at least one of the parameters} derived from the SN density fit is equally or more sensitive to activity than the parameters obtained by the usual Normal method, making this or these parameters more useful indicators of activity.
+{\bf Sensitivity was measured by the strength of the correlation between the different SN or Normal parameters.
+In the case of a spot, the strongest correlations are found between $\gamma$ and SN median RV and between BIS SPAN and N mean RV, therefore making the SN parameters equally sensitive to activity.
+For the facula case, the strongest correlation is between SN FWHM and SN mean RV with a correlation coefficient of R=0.92.
+The correlation between the parameters derived from the Normal fit are much weaker, with correlation coefficients  between BIS SPAN and N mean RV of R=-0.61 and between FWHM and N mean RV of R=0.47.}
+The SN parameters continued to have stronger correlations than the Normal ones in the setting where a planetary signal was added the SOAP 2.0 with a single spot.
+
+{\bf Looking at real data, we arrive to a similar conclusion that the SN parameters are more sensitive to activity.
+While real data confirms that the correlation between CCF width and barycentre is always stronger for the SN parameters, they also show that the correlation between the CCF asymmetry and barycentre is stronger
+
+However, in the real data case, we see that the correlations between the CCF asymmetry and barycentre, as well as the correlation between the CCF width and barycentre are always strong for the SN parameters.}
 
@@
 
-Even if the different RV estimators result in different amplitudes, once the proposed correction for stellar activity is applied, the residuals of the model have similar rms.
+Even if the different RV estimators {\bf derived by the Normal or SN fit} result in different amplitudes, once the proposed correction for stellar activity is applied, the residuals of the model have similar rms.
 When comparing the activity correction proposed in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, for the simulations based on the presence of a facula or a spot the new proposed correction almost entirely explains the spurious variations in RV.
 However, when moving to real data, there is just a slight improvement by using the proposed correction function for stellar activity.
-Additional analysis can be performed for new datasets to see if certain components of the model are not relevant and, therefore, could be removed.
+Additional analysis can be performed for new datasets to see if {\bf certain components of the model proposed here are not relevant and, therefore, could be removed.}
 
@@
 Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by 15 \% and 6 \%}} over the usual model, respectively, for facula and spot.
-When applying this model on real data, the improvement is not as substantial, however, we still observe that planetary detection limits are improved by a non-negligible 12\%.
+When applying this model on real data,\sout{the improvement is not as substantial, however, we still} we observe that planetary detection limits are improved by a non-negligible 12\%.
 

### 2018-11-22 manuscript_v2_noiseSim.tex
Update Xavier

@@
 {\bf Looking at real data, we arrive to a similar conclusion that the SN parameters are more sensitive to activity.
-While real data confirms that the correlation between CCF width and barycentre is always stronger for the SN parameters, they also show that the correlation between the CCF asymmetry and barycentre is stronger
-
-However, in the real data case, we see that the correlations between the CCF asymmetry and barycentre, as well as the correlation between the CCF width and barycentre are always strong for the SN parameters.}
-
-The conclusion found for the SOAP 2.0 simulations that the correlation between the CCF asymmetry and the estimated RV, as well as between the CCF width and the estimated RV, is stronger for the SN parameters than the Normal ones also holds when using real data.
-%
-However, the strongest asymmetry-RV correlation for the simulated data is between $\gamma$ and SN median RV, while it is between $\gamma$ and SN mean RV for the real data.
-There could be several reasons for this difference. 
-First, noting that SOAP 2.0 is a simulation and, hence, is an imperfect representation of reality so it is not unexpected that there are differences between the simulated and real data.
-For example, some differences may be due to the fact that SOAP 2.0 uses the spectrum of a spot as input to model the activity induced by a facula.
+While real data confirms that the correlation between CCF width and barycentre is always stronger for the SN parameters, they also show that it is the case for the correlations between the CCF asymmetry and barycentre.
+In this later case, all stars studied in this paper show a positive correlation, which cannot be explained by SOAP 2.0, as the spot and facula simulations only show negative correlations between the CCF asymmetry and barycentre.
+This discrepancy between simulations and real data could be} due to the fact that SOAP 2.0 uses the spectrum of a spot as input to model the activity induced by a facula.
 Because the temperature between a spot and a facula is significantly different, their spectra should be different. 
-Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region on the equator {\bf{in order to isolate the effects of those active regions}}.
+Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region on the equator {\bf in order to isolate the effects of those active regions}.
 %\xavier{The fact that we also find significant differences between the simulated and real data for the correlations between BIS SPAN and N mean RV and between FWHM and N mean RV shows that the SOAP 2.0 simulation studied here are too simple to explain the complexity of stellar activity in real RV observations.}
@@
 %\umberto{I suggest to comment only about the differences for the SN case, since for the Normal I do not see differences between the analyses with SOAP2.0 and real stars.}
-Nevertheless, in both the simulated and the real cases, the parameters derived from the SN are generally more sensitive to activity than the parameters derived from the Normal.
+
+In the real real cases, the parameters derived from the SN are always more sensitive to activity than the parameters derived from the Normal.  
+{\bf There is only one exception in the case of the width barycentre correlation for HD10700, however, the difference in correlation between the SN and Normal parameters is rather small, from R=0.42 to 0.53, respectively.}
 Also, the correlation between the asymmetry and SN mean RV is consistently stronger than the parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}. 

### 2018-11-22 manuscript_responses_v1.tex
Final update Xavier

--- 2018-11-20 manuscript_responses_v1.tex
@@
 \item[]  RESPONSE:  Yes, we mean the impact of an exoplanet on the host star's spectrum is a shift to the entire stellar spectrum.
-In the Introduction section of the paper, we note the following:  ``In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so creates a spurious shift of the stellar spectrum''  The referenced sentence from Section 3 has been clarified to now read, ``Exoplanets  produce only a pure RV signal (i.e., exoplanets induce a Doppler shift of the entire stellar spectrum).''  The sentence following contrasts this with the impact of stellar activity to the line shape.
+In the Introduction section of the paper, we note the following:  ``In theory, it should be easy to differentiate between the pure Doppler-shift induced by a planet, which shifts the entire stellar spectrum, and stellar activity, which modifies the shape of spectral lines and by doing so creates a spurious shift of the stellar spectrum''  The referenced sentence from Section 3 has been clarified to now read, ``Exoplanets produce a Doppler shift of the entire stellar spectrum.
+On the contrary stellar activity and, in particular, the presence of active regions on the stellar photosphere, do not produce blueshifts or redshifts of the entire stellar spectrum but can create spurious RV signals by modifying the shape of spectral lines.''
 \bigskip
@@
 
-{\color{red}Regarding the cancelation of the correlation between gamma and SN mean RV between spots and faculae, we expect that faculae would dominate and therefore create a positive correlation. 
-If we compare the gamma - SN mean RV correlation in Figure 3 (facula) and 6 (spot), indeed the amplitude in gamma and SN mean RV are similar, and we might think about cancelation. 
-However the facula used in Figure 3 is 3\%, while the spot in Figure 6 is 1\%. 
-We know that on the Sun the faculae over spots filling factor ratio is about 10 (Chapman-2001), therefore it would be reasonable to compare a 1\% spot with a 10\% facula.
-In such a case the effect of the facula would dominate and we would see a positive correlation.
-Such a positive correlation is seen in all the stars in the Appendix, therefore it is likely that for the slow rotating stars analyzed in this paper, the effect of faculae dominates over spots.}
+After redoing the SOAP 2.0 simulations and injecting some noise corresponding to a S/N of 100, it seems that both the spot and facula induce a negative correlation between the CCF asymmetry and its barycenter (i.e.
+the different RV estimators).
+Therefore we cannot have anymore a cancelation effect.
+Those negative correlations does not match the positive correlations always observed in the 5 stars studied in the paper.
+This implies that SOAP 2.0 is not able to model properly the CCF asymmetry variations.
+This could be due to the fact that SOAP 2.0 uses the spectrum of a spot to model the magnetic field effect inside a facula.
+However, we know that the temperature of a facula is significantly different that the one of a spot.
+We discussed this discrepancy in the text.
 
@@
 \item[]  RESPONSE:  We considered the noise on the different parameters of the Normal and SN fit to the CCF for a SNR of 100, which is typical for high-precision RV measurements.
-We updated the entire Section 4 of the manuscript with the obtained results.
 
-We also accordingly rewritten a couple of sentences in the Discussions presented in Section 7 and in the Conclusions of Section 8:
-\begin{itemize}
-\item Sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot setting the SN median RV had a correlation with $\gamma$ as strong as the correlation between N mean RV and BIS SPAN (R= -0.81), and}}
-{\bf{for the facula setting}}, the correlation between the FWHM and the estimated RVs is stronger when using the parameters from the SN compared to the parameters from the Normal.
+%We updated the entire Section 4 of the manuscript with the newly obtained results. 
+%
+%We also accordingly rewritten a couple of sentences in the Discussions presented in Section 7 and in the Conclusions of Section 8:
+%\begin{itemize}
+%\item Sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot setting the SN median RV had a correlation with $\gamma$ as strong as the correlation between N mean RV and BIS SPAN (R= -0.81), and}}
+%{\bf{for the facula setting}}, the correlation between the FWHM and the estimated RVs is stronger when using the parameters from the SN compared to the parameters from the Normal.
 {\bf{For the spot and the spot plus a planet settings, no statistically significant difference on the correlation between FWHM and the estimated RVs were obtained.}}
-
-\item We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.
+%
+%\item We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.
 Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by an additional 14.5 -15 \% and 5.3-5.8 \%}} over the usual model, respectively, for facula and spot.
 When applying this model on real data, the improvement is not as substantial, however, we still observe that planetary detection limits are improved by a non-negligible 12\%.
-\end{itemize}
+%\end{itemize}
 
@@
 %
-\item[]  RESPONSE:  Yes, this is what we observe for example with Alpha Centauri b, where the correlation gamma -- SN RV is positive. 
-When working with simulations and, in particular, for the case of a facula, we measured a negative gamma -- SN RV correlation. 
-This may be due to the limitations of the SOAP 2.0 model described in Section 7, but provides an opportunity for improving the SOAP model in the future.
+\item[]  RESPONSE:  For all the stars, we observe a similar positive gamma -- SN RV correlation.
+The signal on Alpha Centauri B is likely due to a facule (Dumusque 2014) so this would make sense.
+But we also see a positive correlation for Corot-7. This star is extremely active, rotates fast, and the activity signal
+should be mainly driven by spots. Therefore we are not sure that we can use this gamma -- SN RV correlation to differentiate between
+spots and faculae.
 \bigskip
@@
 
-The fact that we see nice RV-FWHM correlations for HD192310 and Corot-7 is likely because faculae are dominating the stellar activity signal (see Fig.
+%The fact that we see nice RV-FWHM correlations for HD192310 and Corot-7 is likely because faculae are dominating the stellar activity signal (see Fig.
 3 in the paper).

### 2018-11-22 manuscript_v2_noiseSim.tex
Final update Xavier

@@
 In the real real cases, the parameters derived from the SN are always more sensitive to activity than the parameters derived from the Normal.  
-{\bf There is only one exception in the case of the width barycentre correlation for HD10700, however, the difference in correlation between the SN and Normal parameters is rather small, from R=0.42 to 0.53, respectively.}
+{\bf There is only one exception in the case of the width-barycentre correlation for HD10700, however, the difference in correlation between the SN and Normal parameters is rather small, from R=0.42 to 0.53, respectively.}
 Also, the correlation between the asymmetry and SN mean RV is consistently stronger than the parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}. 
@@
 A test was carried out to see if some RV estimates were better at finding planets in RV data affected by observed stellar signals.
-The new correction based on Eq.~\eqref{eq:RV:correction} proposed in this paper to mitigate the effect from stellar activity slightly improves the detection limit respect to the usual one based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the Normal fit.
+The new correction based on Eq.~\eqref{eq:RV:correction} proposed in this paper to mitigate the effect from stellar activity slightly improves the detection limit with respect to the usual one based on $RV_{\text{activity}}=\beta_0+\beta_1 \gamma + \beta_2 \text{SN FWHM}$ for the SN fit and on $RV_{\text{activity}}=\beta_0+\beta_1 \text{BIS SPAN} + \beta_2 \text{FWHM}$ for the Normal fit.
 Concerning the definition of the RV using the SN or the Normal fit, all three of the different RV estimators give similar detection limits.

### 2018-11-23 manuscript_v2_noiseSim.tex
Xavier update
Final update Xavier

@@
 \usepackage{longtable}
-\usepackage[normalem]{ulem}
 
 \usepackage{afterpage}
+\usepackage{ulem}
 
@@
 %
-For reasons related to the interpretation of the parameters in Eq.~\eqref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used in this work, which is referred to as the \emph{centered parametrization} (CP).
+For reasons related to the interpretation of the parameters in Eq.~\eqref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used in this work, which is referred to as the \textit{centered parametrization} (CP).
 This CP is much closer to the parametrization of a Normal distribution, as it uses a mean parameter $\mu$, a variance parameter $\sigma^2$ and a skewness parameter $\gamma$.
@@
 %
-Further details about the parametrization from Eq.~\eqref{def:snd_gen}, called the \emph{Direct Parametrization} (DP), the CP, and general statistical properties of the SN can be found in \cite{Azzalini2014}.
+Further details about the parametrization from Eq.~\eqref{def:snd_gen}, called the \textit{Direct Parametrization} (DP), the CP, and general statistical properties of the SN can be found in \cite{Azzalini2014}.
 
@@
 The proposed function defined in Eq.~\eqref{eq:RV:correction} is the result of statistical and astronomical considerations. 
-In particular, we considered issues with correlations between the model covariates, which can lead to issues because the matrix needed to calculate the estimates could be singular; this problem is known in statistics as \emph{multicollinearity} and more discussion can be found in \citet{belsley1991}.
+In particular, we considered issues with correlations between the model covariates, which can lead to issues because the matrix needed to calculate the estimates could be singular; this problem is known in statistics as \textit{multicollinearity} and more discussion can be found in \citet{belsley1991}.
 In the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ between the asymmetry and width parameters and therefore the problem of multicollinearity appeared to be mitigated.
@@
 Correlations between the different RV estimates and the different CCF asymmetry or width estimates are displayed in Fig.~\ref{fig:faculae.corr}. 
-{\bf The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are weaker than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of $R$=-0.11, -0.55 and -0.81, respectively.
+{\bf The correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are weaker than the correlation between BIS SPAN and RV, with Pearson correlation coefficient values of $R$=-0.11, -0.55 and -0.61, respectively.
 Therefore, it seems that when looking at the CCF asymmetry, fitting a SN density to the CCF does not help.
@@
 When comparing the correction proposed in Eq.~\eqref{eq:RV:correction} with what is generally used (i.e.
-a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by  {\bf{15 \%}}.
+a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by {\bf{an additional 14.5 - 15\%}}.
 Looking at the significance of the coefficients in Table~\ref{table:faculae.test}, we observe that {\bf{all the parameters corresponding to the SN variables are statistically significant.
@@
 We also proposed a new model to correct the estimated RV data for stellar activity signals, by using the amplitude of the CCF and an interaction term between the estimated asymmetry and the width parameters.
-Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by 15 \% and 6 \%}} over the usual model, respectively, for facula and spot.
+Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by an additional 14.5 -15 \% and 5.3-5.8 \%}} over the usual model, respectively, for facula and spot.
 When applying this model on real data,\sout{the improvement is not as substantial, however, we still} we observe that planetary detection limits are improved by a non-negligible 12\%.

### 2018-11-23 manuscript_v2_final.tex
Add files via upload
final updates: the file is manuscript_v2_final.tex(pdf)

--- 2018-11-23 manuscript_v2_noiseSim.tex
@@
 The proposed function defined in Eq.~\eqref{eq:RV:correction} is the result of statistical and astronomical considerations. 
-In particular, we considered issues with correlations between the model covariates, which can lead to issues because the matrix needed to calculate the estimates could be singular; this problem is known in statistics as \textit{multicollinearity} and more discussion can be found in \citet{belsley1991}.
+{\bf{ In particular, we evaluated the correlations between the model covariates, since high correlations can lead to a non-invertible design matrix resulting in invalid parameter estimates.
+}}This problem is known in statistics as \textit{multicollinearity} and more discussion can be found in \citet{belsley1991}.
 In the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ between the asymmetry and width parameters and therefore the problem of multicollinearity appeared to be mitigated.
@@
 The code also returns the RV and the FWHM estimated using a Normal model for the CCF, and the BIS SPAN obtained by calculating the bisector of the CCF. 
-\sout{SOAP 2.0 gives noiseless CCFs affected by stellar activity, which are used to compare the performances of SN and Normal models of the CCF.}
+%\sout{SOAP 2.0 gives noiseless CCFs affected by stellar activity, which are used to compare the performances of SN and Normal models of the CCF.}
 
@@
 {\bf The temperature difference of the spot with the photosphere is $\Delta T_{spot} = -663$ K and the temperature difference of the facula depends on the centre-to-limb angle $\theta$,  $\Delta T_{facula} = 250.9 - 407.7\,\cos{\theta} + 190.9\,\cos^2 \theta$ K \citep[][]{Meunier-2010a}}.
-In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of R=115'000.
+In order to make the result of the simulations more comparable to real data obtained with the HARPS spectrograph discussed in Sect.~\ref{sec:4}, the SOAP 2.0 CCFs were generated with a width of 40 \kms\, and considering initial spectra with resolution of Res =115'000.
 {\bf{ For the simulations presented in this section, we considered a S/N of 100.}}
@@
 The correlations between the width and the CCF barycenter draw circles and no significant correlation is observed. 
-{\bf Not like in the facula case, when considering a spot simulated with SAOP 2.0 and a S/N of 100, the SN fit to the CCF does not gives parameters that can probe better stellar activity.
-\sout{Similar to the case with a facula, some parameters of the SN gives stronger correlations compared to the Normal parameters.}}
+{\bf Unlike the facula scenario, when considering a spot simulated from SOAP 2.0 and a S/N of 100 the SN parameters do not appear to better probe stellar activity than the Normal parameters.}
+%\sout{Similar to the case with a facula, some parameters of the SN gives stronger correlations compared to the Normal parameters.}}
 
@@
 The corresponding values for SN median RV and SN mean RV are 5.85\ms down to 2.74 \ms and 5.27\ms down to 2.74\ms, respectively.}
-When comparing the activity correction proposed in this paper with what is commonly used, which means only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf{6 \%}}.
-The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, {\bf except the width of the CCF $\beta_3$ and the interaction term $\beta_4$}
+When comparing the activity correction proposed in this paper with what is commonly used, which means only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf{5.3 - 5.8 \%}}.
+The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, {\bf except the width of the CCF $\beta_3$ and the interaction term $\beta_4$.}
 %This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
@@
 The analysis of the simulated SOAP 2.0 data in the previous section were helpful in assessing the performance of the proposed methodology in a setting where the ground truth was known.
-{\bf We found that the parameters derived by the SN were equally correlated or in the case of a facula even more when the data are only affected by stellar activity.} In this section we present an analysis conducted on real observations, in particular, the star Alpha Centauri B, and compare the performance when fitting a CCF using the SN density defined in Sec.
+{\bf We found with the simulated data that the parameters derived by the SN had correlations comparable to those derived by the Normal; in the case of a facula, the SN parameters had higher correlations for the FWHM than those of the Normal.} In this section we present an analysis conducted on real observations, in particular, the star Alpha Centauri B, and compare the performance when fitting a CCF using the SN density defined in Sec.
 \ref{sec:3} with the commonly employed approach based on fitting a Normal density for estimating the RV and retrieving the BIS SPAN for evaluating the asymmetry of the CCF.
@@
 Using simulated data from SOAP 2.0, {\bf{this new proposed correction reduces the effect of the stellar activity signal by an additional 14.5 -15 \% and 5.3-5.8 \%}} over the usual model, respectively, for facula and spot.
-When applying this model on real data,\sout{the improvement is not as substantial, however, we still} we observe that planetary detection limits are improved by a non-negligible 12\%.
+When applying this model on real data, we observe that planetary detection limits are improved by a non-negligible 12\%.
 
